\chapter{𐑒𐑩𐑥𐑐𐑺𐑦𐑙 ·𐑮𐑦𐑨𐑤𐑦𐑑𐑦 𐑑 𐑦𐑑𐑕 ·𐑷𐑤𐑑𐑻𐑯𐑩𐑑𐑦𐑝𐑟}

\begin{chapterOpeningAuthorNote}
𐑦𐑓 ·𐑡.~𐑒.~·𐑮𐑴𐑤𐑦𐑙 𐑭𐑕𐑒𐑕 𐑿 𐑩𐑚𐑬𐑑 𐑞𐑦𐑕 𐑕𐑑𐑹𐑦, 𐑿 𐑯𐑴 𐑯𐑳𐑔𐑦𐑙.
\end{chapterOpeningAuthorNote}
\begin{chapterOpeningQuote}
𐑚𐑳𐑑 𐑞𐑧𐑯 𐑞 𐑒𐑢𐑧𐑕𐑗𐑩𐑯 𐑦𐑟—𐑣𐑵?
\end{chapterOpeningQuote}

𐑜𐑫𐑛 𐑤𐑹𐑛,” 𐑕𐑧𐑛 𐑞 𐑚𐑸𐑥𐑩𐑯, 𐑐𐑽𐑦𐑙 𐑨𐑑 ·𐑣𐑨𐑮𐑦, “𐑦𐑟 𐑞𐑦𐑕—𐑒𐑨𐑯 𐑞𐑦𐑕 𐑚𐑰—?”

·𐑣𐑨𐑮𐑦 𐑤𐑰𐑯𐑛 𐑑𐑩𐑢𐑹𐑛𐑟 𐑞 𐑚𐑸 𐑝 𐑞 ·𐑤𐑰𐑒𐑦 ·𐑒𐑷𐑤𐑛𐑮𐑩𐑯 𐑨𐑟 𐑚𐑧𐑕𐑑 𐑣𐑰 𐑒𐑫𐑛, 𐑞𐑴 𐑦𐑑 𐑒𐑱𐑥 𐑳𐑐 𐑑 𐑕𐑳𐑥𐑢𐑺 𐑼𐑬𐑯𐑛 𐑞 𐑑𐑦𐑐𐑕 𐑝 𐑣𐑦𐑟 𐑲𐑚𐑮𐑬𐑟. 𐑩 𐑒𐑢𐑧𐑕𐑗𐑩𐑯 𐑤𐑲𐑒 \emph{𐑞𐑨𐑑} 𐑛𐑦𐑟𐑻𐑝𐑛 𐑣𐑦𐑟 𐑝𐑧𐑮𐑦 𐑚𐑧𐑕𐑑.

“𐑨𐑥 𐑲—𐑒𐑫𐑛 𐑲 𐑚𐑰—𐑥𐑱𐑚𐑰—𐑿 𐑯𐑧𐑝𐑼 𐑯𐑴—𐑦𐑓 𐑲'𐑥 \emph{𐑯𐑪𐑑}—𐑚𐑳𐑑 𐑞𐑧𐑯 𐑞 𐑒𐑢𐑧𐑕𐑗𐑩𐑯 𐑦𐑟—\emph{𐑣𐑵?}”

“𐑚𐑤𐑧𐑕 𐑥𐑲 𐑕𐑴𐑤,” 𐑢𐑦𐑕𐑐𐑼𐑛 𐑞 𐑴𐑤𐑛 𐑚𐑸𐑥𐑩𐑯. “·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼…𐑢𐑪𐑑 𐑩𐑯 𐑪𐑯𐑼.”

·𐑣𐑨𐑮𐑦 𐑚𐑤𐑦𐑙𐑒𐑑, 𐑞𐑧𐑯 𐑮𐑨𐑤𐑦𐑛. “𐑢𐑧𐑤, 𐑘𐑧𐑕, 𐑿'𐑼 𐑒𐑢𐑲𐑑 𐑐𐑼𐑕𐑧𐑐𐑑𐑦𐑝; 𐑥𐑴𐑕𐑑 𐑐𐑰𐑐𐑩𐑤 𐑛𐑴𐑯𐑑 𐑮𐑾𐑤𐑲𐑟 𐑞𐑨𐑑 𐑕𐑴 𐑒𐑢𐑦𐑒𐑤𐑦—”

“𐑞𐑨𐑑'𐑕 𐑦𐑯𐑳𐑓,” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛. 𐑣𐑻 𐑣𐑨𐑯𐑛 𐑑𐑲𐑑𐑩𐑯𐑛 𐑪𐑯 ·𐑣𐑨𐑮𐑦'𐑟 𐑖𐑴𐑤𐑛𐑼. “𐑛𐑴𐑯𐑑 𐑐𐑧𐑕𐑑𐑼 𐑞 𐑚𐑶, ·𐑑𐑪𐑥, 𐑣𐑰'𐑟 𐑯𐑿 𐑑 𐑷𐑤 𐑞𐑦𐑕.”

“𐑚𐑳𐑑 𐑦𐑑 𐑦𐑟 𐑣𐑦𐑥?” 𐑒𐑢𐑱𐑝𐑼𐑛 𐑩𐑯 𐑴𐑤𐑛 𐑢𐑫𐑥𐑩𐑯. “𐑦𐑑'𐑕 ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼?” 𐑢𐑦𐑞 𐑩 𐑕𐑒𐑮𐑱𐑐𐑦𐑙 𐑕𐑬𐑯𐑛, 𐑖𐑰 𐑜𐑪𐑑 𐑳𐑐 𐑓𐑮𐑪𐑥 𐑣𐑻 𐑗𐑺.

“·𐑛𐑪𐑮𐑦𐑕—” ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛 𐑢𐑹𐑯𐑦𐑙𐑤𐑦. 𐑞 𐑜𐑤𐑺 𐑖𐑰 𐑖𐑪𐑑 𐑼𐑬𐑯𐑛 𐑞 𐑮𐑵𐑥 𐑖𐑫𐑛 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑦𐑯𐑳𐑓 𐑑 𐑦𐑯𐑑𐑦𐑥𐑦𐑛𐑱𐑑 𐑧𐑯𐑦𐑢𐑳𐑯.

“𐑲 𐑴𐑯𐑤𐑦 𐑢𐑪𐑯𐑑 𐑑 𐑖𐑱𐑒 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛,” 𐑞 𐑢𐑫𐑥𐑩𐑯 𐑢𐑦𐑕𐑐𐑼𐑛. 𐑖𐑰 𐑚𐑧𐑯𐑑 𐑤𐑴 𐑯 𐑕𐑑𐑳𐑒 𐑬𐑑 𐑩 𐑮𐑦𐑙𐑒𐑩𐑤𐑛 𐑣𐑨𐑯𐑛, 𐑢𐑦𐑗 ·𐑣𐑨𐑮𐑦, 𐑓𐑰𐑤𐑦𐑙 𐑒𐑩𐑯𐑓𐑿𐑟𐑛 𐑯 𐑥𐑹 𐑳𐑯𐑒𐑳𐑥𐑓𐑼𐑑𐑩𐑚𐑩𐑤 𐑞𐑨𐑯 𐑣𐑰 𐑧𐑝𐑼 𐑣𐑨𐑛 𐑦𐑯 𐑣𐑦𐑟 𐑤𐑲𐑓, 𐑒𐑺𐑓𐑩𐑤𐑦 𐑖𐑫𐑒. 𐑑𐑽𐑟 𐑓𐑧𐑤 𐑓𐑮𐑪𐑥 𐑞 𐑢𐑫𐑥𐑩𐑯'𐑟 𐑲𐑟 𐑪𐑯𐑑𐑵 𐑞𐑺 𐑒𐑤𐑭𐑕𐑐𐑑 𐑣𐑨𐑯𐑛𐑟. “𐑥𐑲 𐑜𐑮𐑨𐑯𐑛𐑕𐑳𐑯 𐑢𐑪𐑟 𐑩𐑯 ·𐑹𐑹,” 𐑖𐑰 𐑢𐑦𐑕𐑐𐑼𐑛 𐑑 𐑣𐑦𐑥. “𐑛𐑲𐑛 𐑦𐑯 𐑕𐑧𐑝𐑩𐑯𐑑𐑦-𐑯𐑲𐑯. 𐑔𐑨𐑙𐑒 𐑿, ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼. 𐑔𐑨𐑙𐑒 𐑣𐑧𐑝𐑩𐑯𐑟 𐑓 𐑿.”

“𐑿'𐑼 𐑢𐑧𐑤𐑒𐑩𐑥,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑷𐑑𐑩𐑥𐑨𐑑𐑦𐑒𐑤𐑦, 𐑯 𐑞𐑧𐑯 𐑣𐑰 𐑑𐑻𐑯𐑛 𐑣𐑦𐑟 𐑣𐑧𐑛 𐑯 𐑖𐑪𐑑 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑩 𐑓𐑮𐑲𐑑𐑩𐑯𐑛, 𐑐𐑤𐑰𐑛𐑦𐑙 𐑤𐑫𐑒.

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑤𐑨𐑥𐑛 𐑣𐑻 𐑓𐑫𐑑 𐑛𐑬𐑯 𐑡𐑳𐑕𐑑 𐑨𐑟 𐑞 𐑡𐑧𐑯𐑼𐑩𐑤 𐑮𐑳𐑖 𐑢𐑪𐑟 𐑩𐑚𐑬𐑑 𐑑 𐑕𐑑𐑸𐑑. 𐑦𐑑 𐑥𐑱𐑛 𐑩 𐑯𐑶𐑟 𐑞𐑨𐑑 𐑜𐑱𐑝 ·𐑣𐑨𐑮𐑦 𐑩 𐑯𐑿 𐑮𐑧𐑓𐑼𐑩𐑯𐑑 𐑓 𐑞 𐑓𐑮𐑱𐑟 “·𐑒𐑮𐑨𐑒 𐑝 ·𐑛𐑵𐑥”, 𐑯 𐑧𐑝𐑮𐑦𐑢𐑳𐑯 𐑓𐑮𐑴𐑟 𐑦𐑯 𐑐𐑤𐑱𐑕.

“𐑢𐑰'𐑼 𐑦𐑯 𐑩 𐑣𐑳𐑮𐑦,” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛 𐑦𐑯 𐑩 𐑝𐑶𐑕 𐑞𐑨𐑑 𐑕𐑬𐑯𐑛𐑩𐑛 𐑐𐑻𐑓𐑦𐑒𐑑𐑤𐑦, 𐑳𐑑𐑼𐑤𐑦 𐑯𐑹𐑥𐑩𐑤.

𐑞𐑱 𐑤𐑧𐑓𐑑 𐑞 𐑚𐑸 𐑢𐑦𐑞𐑬𐑑 𐑧𐑯𐑦 𐑑𐑮𐑳𐑚𐑩𐑤.

“·𐑐𐑮𐑩𐑓𐑧𐑕𐑼?” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑢𐑳𐑯𐑕 𐑞𐑱 𐑢𐑻 𐑦𐑯 𐑞 𐑒𐑹𐑑𐑘𐑸𐑛. 𐑣𐑰 𐑣𐑨𐑛 𐑥𐑧𐑯𐑑 𐑑 𐑭𐑕𐑒 𐑢𐑪𐑑 𐑢𐑪𐑟 𐑜𐑴𐑦𐑙 𐑪𐑯, 𐑚𐑳𐑑 𐑪𐑛𐑤𐑦 𐑓𐑬𐑯𐑛 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑭𐑕𐑒𐑦𐑙 𐑩𐑯 𐑦𐑯𐑑𐑲𐑼𐑤𐑦 𐑛𐑦𐑓𐑼𐑩𐑯𐑑 𐑒𐑢𐑧𐑕𐑗𐑩𐑯 𐑦𐑯𐑕𐑑𐑧𐑛. “𐑣𐑵 𐑢𐑪𐑟 𐑞𐑨𐑑 𐑐𐑱𐑤 𐑥𐑨𐑯, 𐑚𐑲 𐑞 𐑒𐑹𐑯𐑼? 𐑞 𐑥𐑨𐑯 𐑢𐑦𐑞 𐑞 𐑑𐑢𐑦𐑗𐑦𐑙 𐑲?”

“𐑣𐑥?” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑕𐑬𐑯𐑛𐑦𐑙 𐑩 𐑚𐑦𐑑 𐑕𐑼𐑐𐑮𐑲𐑟𐑛; 𐑐𐑼𐑣𐑨𐑐𐑕 𐑖𐑰 𐑣𐑨𐑛𐑩𐑯𐑑 𐑦𐑒𐑕𐑐𐑧𐑒𐑑𐑩𐑛 𐑞𐑨𐑑 𐑒𐑢𐑧𐑕𐑗𐑩𐑯 𐑲𐑞𐑼. “𐑞𐑨𐑑 𐑢𐑪𐑟 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑒𐑢𐑦𐑮𐑦𐑯𐑩𐑕 ·𐑒𐑢𐑦𐑮𐑩𐑤. 𐑣𐑰'𐑤 𐑚𐑰 𐑑𐑰𐑗𐑦𐑙 ·𐑛𐑦𐑓𐑧𐑯𐑕 ·𐑩𐑜𐑱𐑯𐑕𐑑 𐑞 ·𐑛𐑸𐑒 ·𐑸𐑑𐑕 𐑞𐑦𐑕 𐑘𐑽 𐑨𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕.”

“𐑲 𐑣𐑨𐑛 𐑞 𐑕𐑑𐑮𐑱𐑯𐑡𐑩𐑕𐑑 𐑓𐑰𐑤𐑦𐑙 𐑞𐑨𐑑 𐑲 𐑯𐑿 𐑣𐑦𐑥…” ·𐑣𐑨𐑮𐑦 𐑮𐑳𐑚𐑛 𐑣𐑦𐑟 𐑓𐑪𐑮𐑦𐑛. “𐑯 𐑞𐑨𐑑 𐑲 𐑖𐑫𐑛𐑩𐑯𐑑 𐑖𐑱𐑒 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛.” 𐑤𐑲𐑒 𐑥𐑰𐑑𐑦𐑙 𐑕𐑳𐑥𐑢𐑳𐑯 𐑣𐑵 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑩 𐑓𐑮𐑧𐑯𐑛, 𐑢𐑳𐑯𐑕, 𐑚𐑦𐑓𐑹 𐑕𐑳𐑥𐑔𐑦𐑙 𐑢𐑧𐑯𐑑 𐑛𐑮𐑨𐑕𐑑𐑦𐑒𐑤𐑦 𐑮𐑪𐑙…𐑞𐑨𐑑 𐑢𐑪𐑟𐑩𐑯𐑑 𐑮𐑾𐑤𐑦 𐑦𐑑 𐑨𐑑 𐑷𐑤, 𐑚𐑳𐑑 ·𐑣𐑨𐑮𐑦 𐑒𐑫𐑛𐑩𐑯𐑑 𐑓𐑲𐑯𐑛 𐑢𐑻𐑛𐑟. “𐑯 𐑢𐑪𐑑 \emph{𐑢𐑪𐑟}…𐑷𐑤 𐑝 𐑞𐑨𐑑?”

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑢𐑪𐑟 𐑜𐑦𐑝𐑦𐑙 𐑣𐑦𐑥 𐑩𐑯 𐑪𐑛 𐑜𐑤𐑭𐑯𐑕. “·𐑥𐑼~·𐑐𐑪𐑑𐑼…𐑛𐑵 𐑿 𐑯𐑴…𐑣𐑬 \emph{𐑥𐑳𐑗} 𐑣𐑨𐑝 𐑿 𐑚𐑰𐑯 𐑑𐑴𐑤𐑛…𐑩𐑚𐑬𐑑 𐑣𐑬 𐑘𐑹 𐑐𐑺𐑩𐑯𐑑𐑕 𐑛𐑲𐑛?”

·𐑣𐑨𐑮𐑦 𐑮𐑦𐑑𐑻𐑯𐑛 𐑩 𐑕𐑑𐑧𐑛𐑦 𐑤𐑫𐑒. “𐑥𐑲 𐑐𐑺𐑩𐑯𐑑𐑕 𐑸 𐑩𐑤𐑲𐑝 𐑯 𐑢𐑧𐑤, 𐑯 𐑞𐑱 𐑷𐑤𐑢𐑱𐑟 𐑮𐑦𐑓𐑿𐑟𐑛 𐑑 𐑑𐑷𐑒 𐑩𐑚𐑬𐑑 𐑣𐑬 𐑥𐑲 \emph{𐑡𐑩𐑯𐑧𐑑𐑦𐑒} 𐑐𐑺𐑩𐑯𐑑𐑕 𐑛𐑲𐑛. 𐑓𐑮𐑪𐑥 𐑢𐑦𐑗 𐑲 𐑦𐑯𐑓𐑻 𐑞𐑨𐑑 𐑦𐑑 𐑢𐑪𐑟𐑩𐑯𐑑 𐑜𐑫𐑛.”

“𐑩𐑯 𐑨𐑛𐑥𐑼𐑩𐑚𐑩𐑤 𐑤𐑶𐑩𐑤𐑑𐑦,” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. 𐑣𐑻 𐑝𐑶𐑕 𐑢𐑧𐑯𐑑 𐑤𐑴. “𐑞𐑴 𐑦𐑑 𐑣𐑻𐑑𐑕 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑑 𐑣𐑽 𐑿 𐑕𐑱 𐑦𐑑 𐑤𐑲𐑒 𐑞𐑨𐑑. ·𐑤𐑦𐑤𐑦 𐑯 ·𐑡𐑱𐑥𐑟 𐑢𐑻 𐑓𐑮𐑧𐑯𐑛𐑟 𐑝 𐑥𐑲𐑯.”

·𐑣𐑨𐑮𐑦 𐑤𐑫𐑒𐑑 𐑩𐑢𐑱, 𐑕𐑳𐑛𐑩𐑯𐑤𐑦 𐑩𐑖𐑱𐑥𐑛. “𐑲'𐑥 𐑕𐑪𐑮𐑦,” 𐑣𐑰 𐑕𐑧𐑛 𐑦𐑯 𐑩 𐑕𐑥𐑷𐑤 𐑝𐑶𐑕. “𐑚𐑳𐑑 𐑲 \emph{𐑣𐑨𐑝} 𐑩 ·𐑥𐑳𐑥 𐑯 ·𐑛𐑨𐑛. 𐑯 𐑲 𐑯𐑴 𐑞𐑨𐑑 𐑲'𐑛 𐑡𐑳𐑕𐑑 𐑥𐑱𐑒 𐑥𐑲𐑕𐑧𐑤𐑓 𐑳𐑯𐑣𐑨𐑐𐑦 𐑚𐑲 𐑒𐑩𐑥𐑐𐑺𐑦𐑙 𐑞𐑨𐑑 𐑮𐑦𐑨𐑤𐑦𐑑𐑦 𐑑…𐑕𐑳𐑥𐑔𐑦𐑙 𐑐𐑻𐑓𐑦𐑒𐑑 𐑞𐑨𐑑 𐑲 𐑚𐑦𐑤𐑑 𐑳𐑐 𐑦𐑯 𐑥𐑲 𐑦𐑥𐑨𐑡𐑦𐑯𐑱𐑖𐑩𐑯.”

“𐑞𐑨𐑑 𐑦𐑟 𐑩𐑥𐑱𐑟𐑦𐑙𐑤𐑦 𐑢𐑲𐑟 𐑝 𐑿,” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛 𐑒𐑢𐑲𐑩𐑑𐑤𐑦. “𐑚𐑳𐑑 𐑘𐑹 \emph{𐑡𐑩𐑯𐑧𐑑𐑦𐑒} 𐑐𐑺𐑩𐑯𐑑𐑕 𐑛𐑲𐑛 𐑝𐑧𐑮𐑦 𐑢𐑧𐑤 𐑦𐑯𐑛𐑰𐑛, 𐑐𐑮𐑩𐑑𐑧𐑒𐑑𐑦𐑙 𐑿.”

\emph{𐑐𐑮𐑩𐑑𐑧𐑒𐑑𐑦𐑙 𐑥𐑰?}

𐑕𐑳𐑥𐑔𐑦𐑙 𐑕𐑑𐑮𐑱𐑯𐑡 𐑒𐑤𐑳𐑗𐑑 𐑨𐑑 ·𐑣𐑨𐑮𐑦'𐑟 𐑣𐑸𐑑. “𐑢𐑪𐑑…\emph{𐑛𐑦𐑛} 𐑣𐑨𐑐𐑩𐑯?”

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑲𐑛. 𐑣𐑻 𐑢𐑪𐑯𐑛 𐑑𐑨𐑐𐑑 ·𐑣𐑨𐑮𐑦'𐑟 𐑓𐑪𐑮𐑦𐑛, 𐑯 𐑣𐑦𐑟 𐑝𐑦𐑠𐑩𐑯 𐑚𐑤𐑻𐑛 𐑓 𐑩 𐑥𐑴𐑥𐑩𐑯𐑑. “𐑕𐑳𐑥𐑔𐑦𐑙 𐑝 𐑩 𐑛𐑦𐑕𐑜𐑲𐑟,” 𐑖𐑰 𐑕𐑧𐑛, “𐑕𐑴 𐑞𐑨𐑑 𐑞𐑦𐑕 𐑛𐑳𐑟𐑩𐑯𐑑 𐑣𐑨𐑐𐑩𐑯 𐑩𐑜𐑱𐑯, 𐑯𐑪𐑑 𐑩𐑯𐑑𐑦𐑤 𐑿'𐑼 𐑮𐑧𐑛𐑦.” 𐑞𐑧𐑯 𐑣𐑻 𐑢𐑪𐑯𐑛 𐑤𐑦𐑒𐑑 𐑬𐑑 𐑩𐑜𐑱𐑯, 𐑯 𐑑𐑨𐑐𐑑 𐑔𐑮𐑰 𐑑𐑲𐑥𐑟 𐑪𐑯 𐑩 𐑚𐑮𐑦𐑒 𐑢𐑷𐑤…

…𐑢𐑦𐑗 𐑣𐑪𐑤𐑴𐑛 𐑦𐑯𐑑𐑵 𐑩 𐑣𐑴𐑤, 𐑯 𐑛𐑲𐑤𐑱𐑑𐑩𐑛 𐑯 𐑦𐑒𐑕𐑐𐑨𐑯𐑛𐑩𐑛 𐑯 𐑖𐑦𐑝𐑼𐑛 𐑦𐑯𐑑𐑵 𐑩 𐑣𐑿𐑡 𐑸𐑗𐑢𐑱, 𐑮𐑦𐑝𐑰𐑤𐑦𐑙 𐑩 𐑤𐑪𐑙 𐑮𐑴 𐑝 𐑖𐑪𐑐𐑕 𐑢𐑦𐑞 𐑕𐑲𐑯𐑟 𐑨𐑛𐑝𐑻𐑑𐑲𐑟𐑦𐑙 𐑒𐑷𐑤𐑛𐑮𐑩𐑯𐑟 𐑯 𐑛𐑮𐑨𐑜𐑩𐑯 𐑤𐑦𐑝𐑼𐑟.

·𐑣𐑨𐑮𐑦 𐑛𐑦𐑛𐑩𐑯𐑑 𐑚𐑤𐑦𐑙𐑒. 𐑦𐑑 𐑢𐑪𐑟𐑩𐑯𐑑 𐑤𐑲𐑒 𐑧𐑯𐑦𐑢𐑳𐑯 𐑢𐑪𐑟 𐑑𐑻𐑯𐑦𐑙 𐑦𐑯𐑑𐑵 𐑩 𐑒𐑨𐑑.

𐑯 𐑞𐑱 𐑢𐑷𐑒𐑑 𐑓𐑹𐑢𐑼𐑛𐑟, 𐑑𐑩𐑜𐑧𐑞𐑼, 𐑦𐑯𐑑𐑵 𐑞 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑢𐑻𐑤𐑛.

𐑞𐑺 𐑢𐑻 𐑥𐑻𐑗𐑩𐑯𐑑𐑕 𐑣𐑷𐑒𐑦𐑙 ·𐑚𐑬𐑯𐑕 ·𐑚𐑵𐑑𐑕 (“𐑥𐑱𐑛 𐑢𐑦𐑞 𐑮𐑾𐑤 ·𐑓𐑤𐑳𐑚𐑼!”) 𐑯 “𐑯𐑲𐑝𐑟 +3! 𐑓𐑹𐑒𐑕 +2! 𐑕𐑐𐑵𐑯𐑟 𐑢𐑦𐑞 𐑩 +4 𐑚𐑴𐑯𐑩𐑕!” 𐑞𐑺 𐑢𐑻 𐑜𐑪𐑜𐑩𐑤𐑟 𐑞𐑨𐑑 𐑢𐑫𐑛 𐑑𐑻𐑯 𐑧𐑯𐑦𐑔𐑦𐑙 𐑿 𐑤𐑫𐑒𐑑 𐑨𐑑 𐑜𐑮𐑰𐑯, 𐑯 𐑩 𐑤𐑲𐑯-𐑳𐑐 𐑝 𐑒𐑳𐑥𐑓𐑦 𐑸𐑥𐑗𐑺𐑟 𐑢𐑦𐑞 𐑦𐑡𐑧𐑒𐑖𐑩𐑯 𐑕𐑰𐑑𐑕 𐑓 𐑦𐑥𐑻𐑡𐑩𐑯𐑕𐑦𐑟.

𐑣𐑨𐑮𐑦'𐑟 𐑣𐑧𐑛 𐑒𐑧𐑐𐑑 𐑮𐑴𐑑𐑱𐑑𐑦𐑙, 𐑮𐑴𐑑𐑱𐑑𐑦𐑙 𐑤𐑲𐑒 𐑦𐑑 𐑢𐑪𐑟 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑢𐑲𐑯𐑛 𐑦𐑑𐑕𐑧𐑤𐑓 𐑪𐑓 𐑣𐑦𐑟 𐑯𐑧𐑒. 𐑦𐑑 𐑢𐑪𐑟 𐑤𐑲𐑒 𐑢𐑷𐑒𐑦𐑙 𐑔𐑮𐑵 𐑞 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 𐑲𐑑𐑩𐑥𐑟 𐑕𐑧𐑒𐑖𐑩𐑯 𐑝 𐑩𐑯 \emph{·𐑩𐑛𐑝𐑭𐑯𐑕𐑑 ·𐑛𐑳𐑯𐑡𐑩𐑯𐑟 𐑯 ·𐑛𐑮𐑨𐑜𐑩𐑯𐑟} 𐑮𐑵𐑤𐑚𐑫𐑒 (𐑣𐑰 𐑛𐑦𐑛𐑩𐑯𐑑 𐑐𐑤𐑱 𐑞 𐑜𐑱𐑥, 𐑚𐑳𐑑 𐑣𐑰 𐑛𐑦𐑛 𐑦𐑯𐑡𐑶 𐑮𐑰𐑛𐑦𐑙 𐑞 𐑮𐑵𐑤𐑚𐑫𐑒𐑕). ·𐑣𐑨𐑮𐑦 𐑛𐑧𐑕𐑐𐑼𐑩𐑑𐑤𐑦 𐑛𐑦𐑛𐑩𐑯𐑑 𐑢𐑪𐑯𐑑 𐑑 𐑥𐑦𐑕 𐑩 𐑕𐑦𐑙𐑜𐑩𐑤 𐑲𐑑𐑩𐑥 𐑓 𐑕𐑱𐑤, 𐑦𐑯 𐑒𐑱𐑕 𐑦𐑑 𐑢𐑪𐑟 𐑢𐑳𐑯 𐑝 𐑞 𐑔𐑮𐑰 𐑿 𐑯𐑰𐑛𐑩𐑛 𐑑 𐑒𐑩𐑥𐑐𐑤𐑰𐑑 𐑞 𐑕𐑲𐑒𐑩𐑤 𐑝 𐑦𐑯𐑓𐑦𐑯𐑦𐑑 \emph{𐑢𐑦𐑖} 𐑕𐑐𐑧𐑤𐑟.

𐑞𐑧𐑯 ·𐑣𐑨𐑮𐑦 𐑕𐑐𐑪𐑑𐑩𐑛 𐑕𐑳𐑥𐑔𐑦𐑙 𐑞𐑨𐑑 𐑥𐑱𐑛 𐑣𐑦𐑥, 𐑦𐑯𐑑𐑲𐑼𐑤𐑦 𐑢𐑦𐑞𐑬𐑑 𐑔𐑦𐑙𐑒𐑦𐑙, 𐑝𐑽 𐑪𐑓 𐑓𐑮𐑪𐑥 𐑞 ·𐑛𐑧𐑐𐑿𐑑𐑦 ·𐑣𐑧𐑛𐑥𐑦𐑕𐑑𐑮𐑩𐑕 𐑯 𐑕𐑑𐑸𐑑 𐑣𐑧𐑛𐑦𐑙 𐑕𐑑𐑮𐑱𐑑 𐑦𐑯𐑑𐑵 𐑞 𐑖𐑪𐑐, 𐑩 𐑓𐑮𐑳𐑯𐑑 𐑝 𐑚𐑤𐑵 𐑚𐑮𐑦𐑒𐑕 𐑢𐑦𐑞 𐑚𐑮𐑪𐑯𐑟-𐑥𐑧𐑑𐑩𐑤 𐑑𐑮𐑦𐑥. 𐑣𐑰 𐑢𐑪𐑟 𐑚𐑮𐑷𐑑 𐑚𐑨𐑒 𐑑 𐑮𐑦𐑨𐑤𐑦𐑑𐑦 𐑴𐑯𐑤𐑦 𐑢𐑧𐑯 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑑𐑧𐑐𐑑 𐑮𐑲𐑑 𐑦𐑯 𐑓𐑮𐑳𐑯𐑑 𐑝 𐑣𐑦𐑥.

“·𐑥𐑼~·𐑐𐑪𐑑𐑼?” 𐑖𐑰 𐑕𐑧𐑛.

·𐑣𐑨𐑮𐑦 𐑚𐑤𐑦𐑙𐑒𐑑, 𐑞𐑧𐑯 𐑮𐑾𐑤𐑲𐑟𐑛 𐑢𐑪𐑑 𐑣𐑰'𐑛 𐑡𐑳𐑕𐑑 𐑛𐑳𐑯. “𐑲'𐑥 𐑕𐑪𐑮𐑦! 𐑲 𐑓𐑼𐑜𐑪𐑑 𐑓 𐑩 𐑥𐑴𐑥𐑩𐑯𐑑 𐑞𐑨𐑑 𐑲 𐑢𐑪𐑟 𐑢𐑦𐑞 𐑿 𐑦𐑯𐑕𐑑𐑧𐑛 𐑝 𐑥𐑲 𐑓𐑨𐑥𐑤𐑦.” ·𐑣𐑨𐑮𐑦 𐑡𐑧𐑕𐑗𐑼𐑛 𐑨𐑑 𐑞 𐑖𐑪𐑐 𐑢𐑦𐑯𐑛𐑴, 𐑢𐑦𐑗 𐑛𐑦𐑕𐑐𐑤𐑱𐑛 𐑓𐑲𐑼𐑦 𐑤𐑧𐑑𐑼𐑟 𐑞𐑨𐑑 𐑖𐑪𐑯 𐑐𐑽𐑕𐑦𐑙𐑤𐑦 𐑚𐑮𐑲𐑑 𐑯 𐑘𐑧𐑑 𐑮𐑦𐑥𐑴𐑑, 𐑕𐑐𐑧𐑤𐑦𐑙 𐑬𐑑 \emph{·𐑚𐑦𐑜𐑚𐑨𐑥'𐑟 ·𐑚𐑮𐑦𐑤𐑘𐑩𐑯𐑑 ·𐑚𐑫𐑒𐑕}. “𐑢𐑧𐑯 𐑿 𐑢𐑷𐑒 𐑐𐑭𐑕𐑑 𐑩 𐑚𐑫𐑒𐑖𐑪𐑐 𐑿 𐑣𐑨𐑝𐑩𐑯𐑑 𐑝𐑦𐑟𐑦𐑑𐑩𐑛 𐑚𐑦𐑓𐑹, 𐑿 𐑣𐑨𐑓 𐑑 𐑜𐑴 𐑦𐑯 𐑯 𐑤𐑫𐑒 𐑼𐑬𐑯𐑛. 𐑞𐑨𐑑'𐑕 𐑞 𐑓𐑨𐑥𐑤𐑦 𐑮𐑵𐑤.”

“𐑞𐑨𐑑 𐑦𐑟 𐑞 𐑥𐑴𐑕𐑑 ·𐑮𐑱𐑝𐑩𐑯𐑒𐑤𐑷 𐑔𐑦𐑙 𐑲 𐑣𐑨𐑝 𐑧𐑝𐑼 𐑣𐑻𐑛.”

“𐑢𐑪𐑑?”

“𐑯𐑳𐑔𐑦𐑙. ·𐑥𐑼~·𐑐𐑪𐑑𐑼, 𐑬𐑼 𐑓𐑻𐑕𐑑 𐑕𐑑𐑧𐑐 𐑦𐑟 𐑑 𐑝𐑦𐑟𐑦𐑑 ·𐑜𐑮𐑦𐑙𐑜𐑩𐑑𐑕, 𐑞 𐑚𐑨𐑙𐑒 𐑝 𐑞 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑢𐑻𐑤𐑛. 𐑘𐑹 \emph{𐑡𐑩𐑯𐑧𐑑𐑦𐑒} 𐑓𐑨𐑥𐑤𐑦 𐑝𐑷𐑤𐑑 𐑦𐑟 𐑞𐑺, 𐑢𐑦𐑞 𐑞 𐑦𐑯𐑣𐑧𐑮𐑦𐑑𐑩𐑯𐑕 𐑘𐑹 \emph{𐑡𐑩𐑯𐑧𐑑𐑦𐑒} 𐑐𐑺𐑩𐑯𐑑𐑕 𐑤𐑧𐑓𐑑 𐑿, 𐑯 𐑿'𐑤 𐑯𐑰𐑛 𐑥𐑳𐑯𐑦 𐑓 𐑕𐑒𐑵𐑤 𐑕𐑩𐑐𐑤𐑲𐑟.” 𐑖𐑰 𐑕𐑲𐑛. “𐑯, 𐑲 𐑕𐑩𐑐𐑴𐑟, 𐑩 𐑕𐑻𐑑𐑩𐑯 𐑩𐑥𐑬𐑯𐑑 𐑝 𐑕𐑐𐑧𐑯𐑛𐑦𐑙 𐑥𐑳𐑯𐑦 𐑓 𐑚𐑫𐑒𐑕 𐑒𐑫𐑛 𐑚𐑰 𐑦𐑒𐑕𐑒𐑿𐑟𐑛 𐑨𐑟 𐑢𐑧𐑤. 𐑞𐑴 𐑿 𐑥𐑲𐑑 𐑢𐑪𐑯𐑑 𐑑 𐑣𐑴𐑤𐑛 𐑪𐑓 𐑓 𐑩 𐑑𐑲𐑥. ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 𐑣𐑨𐑟 𐑒𐑢𐑲𐑑 𐑩 𐑤𐑸𐑡 𐑤𐑲𐑚𐑮𐑼𐑦 𐑪𐑯 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 𐑕𐑳𐑚𐑡𐑧𐑒𐑑𐑕. 𐑯 𐑞 𐑑𐑬𐑼 𐑦𐑯 𐑢𐑦𐑗, 𐑲 𐑕𐑑𐑮𐑪𐑙𐑤𐑦 𐑕𐑩𐑕𐑐𐑧𐑒𐑑, 𐑿 𐑢𐑦𐑤 𐑚𐑰 𐑤𐑦𐑝𐑦𐑙, 𐑣𐑨𐑟 𐑩 𐑥𐑹 𐑚𐑮𐑷𐑛-𐑮𐑱𐑯𐑡𐑦𐑙 𐑤𐑲𐑚𐑮𐑼𐑦 𐑝 𐑦𐑑𐑕 𐑴𐑯. 𐑧𐑯𐑦 𐑚𐑫𐑒 𐑿 𐑚𐑷𐑑 𐑯𐑬 𐑢𐑫𐑛 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑚𐑰 𐑩 𐑛𐑿𐑐𐑤𐑦𐑒𐑩𐑑.”

·𐑣𐑨𐑮𐑦 𐑯𐑪𐑛𐑩𐑛, 𐑯 𐑞𐑱 𐑢𐑷𐑒𐑑 𐑪𐑯.

“𐑛𐑴𐑯𐑑 𐑜𐑧𐑑 𐑥𐑰 𐑮𐑪𐑙, 𐑦𐑑'𐑕 𐑩 \emph{𐑜𐑮𐑱𐑑} 𐑛𐑦𐑕𐑑𐑮𐑨𐑒𐑖𐑩𐑯,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑨𐑟 𐑣𐑦𐑟 𐑣𐑧𐑛 𐑒𐑧𐑐𐑑 𐑕𐑢𐑦𐑝𐑩𐑤𐑦𐑙, “𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑞 𐑚𐑧𐑕𐑑 𐑛𐑦𐑕𐑑𐑮𐑨𐑒𐑖𐑩𐑯 𐑧𐑯𐑦𐑢𐑳𐑯 𐑣𐑨𐑟 𐑧𐑝𐑼 𐑑𐑮𐑲𐑛 𐑪𐑯 𐑥𐑰, 𐑚𐑳𐑑 𐑛𐑴𐑯𐑑 𐑔𐑦𐑙𐑒 𐑲'𐑝 𐑓𐑼𐑜𐑪𐑑𐑩𐑯 𐑩𐑚𐑬𐑑 𐑬𐑼 𐑐𐑧𐑯𐑛𐑦𐑙 𐑛𐑦𐑕𐑒𐑳𐑖𐑩𐑯.”

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑲𐑛. “𐑘𐑹 𐑐𐑺𐑩𐑯𐑑𐑕—𐑹 𐑘𐑹 𐑥𐑳𐑞𐑼 𐑨𐑑 𐑧𐑯𐑦 𐑮𐑱𐑑—𐑥𐑱 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑝𐑧𐑮𐑦 𐑢𐑲𐑟 𐑯𐑪𐑑 𐑑 𐑑𐑧𐑤 𐑿.”

“𐑕𐑴 𐑿 𐑢𐑦𐑖 𐑞𐑨𐑑 𐑲 𐑒𐑫𐑛 𐑒𐑩𐑯𐑑𐑦𐑯𐑿 𐑦𐑯 𐑚𐑤𐑦𐑕𐑓𐑩𐑤 𐑦𐑜𐑯𐑼𐑩𐑯𐑕? 𐑞𐑺 𐑦𐑟 𐑩 𐑕𐑻𐑑𐑩𐑯 𐑓𐑤𐑷 𐑦𐑯 𐑞𐑨𐑑 𐑐𐑤𐑨𐑯, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤.”

“𐑲 𐑕𐑩𐑐𐑴𐑟 𐑦𐑑 𐑢𐑫𐑛 𐑚𐑰 𐑮𐑭𐑞𐑼 𐑐𐑶𐑯𐑑𐑤𐑩𐑕,” 𐑞 𐑢𐑦𐑗 𐑕𐑧𐑛 𐑑𐑲𐑑𐑤𐑦, “𐑢𐑧𐑯 𐑧𐑯𐑦𐑢𐑳𐑯 𐑪𐑯 𐑞 𐑕𐑑𐑮𐑰𐑑 𐑒𐑫𐑛 𐑑𐑧𐑤 𐑿 𐑞 𐑕𐑑𐑹𐑦. 𐑝𐑧𐑮𐑦 𐑢𐑧𐑤.”

𐑯 𐑖𐑰 𐑑𐑴𐑤𐑛 𐑣𐑦𐑥 𐑝 ·𐑣𐑰-𐑣𐑵-·𐑥𐑳𐑕𐑑-𐑯𐑪𐑑-𐑚𐑰-·𐑯𐑱𐑥𐑛, 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛, ·𐑝𐑴𐑤𐑛𐑩𐑥𐑹𐑑.

“·𐑝𐑴𐑤𐑛𐑩𐑥𐑹𐑑?” ·𐑣𐑨𐑮𐑦 𐑢𐑦𐑕𐑐𐑼𐑛. 𐑦𐑑 𐑖𐑫𐑛 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑓𐑳𐑯𐑦, 𐑚𐑳𐑑 𐑦𐑑 𐑢𐑪𐑟𐑩𐑯𐑑. 𐑞 𐑯𐑱𐑥 𐑚𐑻𐑯𐑛 𐑢𐑦𐑞 𐑩 𐑒𐑴𐑤𐑛 𐑓𐑰𐑤𐑦𐑙, 𐑮𐑵𐑔𐑤𐑩𐑕𐑯𐑩𐑕, 𐑛𐑲𐑥𐑩𐑯𐑛 𐑒𐑤𐑨𐑮𐑦𐑑𐑦, 𐑩 𐑣𐑨𐑥𐑼 𐑝 𐑐𐑘𐑫𐑼 𐑑𐑲𐑑𐑱𐑯𐑾𐑥 𐑛𐑦𐑕𐑧𐑯𐑛𐑦𐑙 𐑩𐑐𐑪𐑯 𐑩𐑯 𐑨𐑯𐑝𐑦𐑤 𐑝 𐑘𐑰𐑤𐑛𐑦𐑙 𐑓𐑤𐑧𐑖. 𐑩 𐑗𐑦𐑤 𐑕𐑢𐑧𐑐𐑑 𐑴𐑝𐑼 ·𐑣𐑨𐑮𐑦 𐑰𐑝𐑩𐑯 𐑨𐑟 𐑣𐑰 𐑐𐑮𐑩𐑯𐑬𐑯𐑕𐑑 𐑞 𐑢𐑻𐑛, 𐑯 𐑣𐑰 𐑮𐑦𐑟𐑪𐑤𐑝𐑛 𐑞𐑧𐑯 𐑯 𐑞𐑺 𐑑 𐑿𐑟 𐑕𐑱𐑓𐑼 𐑑𐑻𐑥𐑟 𐑤𐑲𐑒 𐑿-𐑯𐑴-𐑣𐑵.

𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛 𐑣𐑨𐑛 𐑮𐑱𐑡𐑛 𐑩𐑐𐑪𐑯 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 ·𐑚𐑮𐑦𐑑𐑩𐑯 𐑤𐑲𐑒 𐑩 𐑢𐑲𐑤𐑛𐑦𐑙 𐑢𐑫𐑤𐑓, 𐑑𐑺𐑦𐑙 𐑯 𐑮𐑧𐑯𐑛𐑦𐑙 𐑨𐑑 𐑞 𐑓𐑨𐑚𐑮𐑦𐑒 𐑝 𐑞𐑺 𐑧𐑝𐑮𐑦𐑛𐑱 𐑤𐑲𐑝𐑟. 𐑳𐑞𐑼 𐑒𐑳𐑯𐑑𐑮𐑦𐑟 𐑣𐑨𐑛 𐑮𐑳𐑙 𐑞𐑺 𐑣𐑨𐑯𐑛𐑟 𐑚𐑳𐑑 𐑣𐑧𐑟𐑦𐑑𐑱𐑑𐑩𐑛 𐑑 𐑦𐑯𐑑𐑼𐑝𐑰𐑯, 𐑢𐑧𐑞𐑼 𐑬𐑑 𐑝 𐑨𐑐𐑩𐑔𐑧𐑑𐑦𐑒 𐑕𐑧𐑤𐑓𐑦𐑖𐑯𐑩𐑕 𐑹 𐑕𐑦𐑥𐑐𐑩𐑤 𐑓𐑽, 𐑓 𐑢𐑦𐑗𐑧𐑝𐑼 𐑢𐑪𐑟 𐑓𐑻𐑕𐑑 𐑩𐑥𐑳𐑙 𐑞𐑧𐑥 𐑑 𐑩𐑐𐑴𐑟 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛, 𐑞𐑺 𐑐𐑰𐑕 𐑢𐑫𐑛 𐑚𐑰 𐑞 𐑯𐑧𐑒𐑕𐑑 𐑑𐑸𐑜𐑩𐑑 𐑝 𐑣𐑦𐑟 𐑑𐑧𐑮𐑼.

(\emph{𐑞 𐑚𐑲𐑕𐑑𐑨𐑯𐑛𐑼 𐑦𐑓𐑧𐑒𐑑,} 𐑔𐑷𐑑 ·𐑣𐑨𐑮𐑦, 𐑔𐑦𐑙𐑒𐑦𐑙 𐑝 ·𐑤𐑭𐑑𐑭𐑯𐑧 𐑯 ·𐑛𐑸𐑤𐑦'𐑟 𐑦𐑒𐑕𐑐𐑧𐑮𐑦𐑥𐑧𐑯𐑑 𐑢𐑦𐑗 𐑣𐑨𐑛 𐑖𐑴𐑯 𐑞𐑨𐑑 𐑿 𐑢𐑻 𐑥𐑹 𐑤𐑲𐑒𐑤𐑦 𐑑 𐑜𐑧𐑑 𐑣𐑧𐑤𐑐 𐑦𐑓 𐑿 𐑣𐑨𐑛 𐑩𐑯 𐑧𐑐𐑦𐑤𐑧𐑐𐑑𐑦𐑒 𐑓𐑦𐑑 𐑦𐑯 𐑓𐑮𐑳𐑯𐑑 𐑝 𐑢𐑳𐑯 𐑐𐑻𐑕𐑩𐑯 𐑞𐑨𐑯 𐑦𐑯 𐑓𐑮𐑳𐑯𐑑 𐑝 𐑔𐑮𐑰. \emph{𐑛𐑦𐑓𐑿𐑠𐑩𐑯 𐑝 𐑮𐑦𐑕𐑐𐑪𐑯𐑕𐑩𐑚𐑦𐑤𐑦𐑑𐑦, 𐑧𐑝𐑮𐑦𐑢𐑳𐑯 𐑣𐑴𐑐𐑦𐑙 𐑞𐑨𐑑 𐑕𐑳𐑥𐑢𐑳𐑯 𐑧𐑤𐑕 𐑢𐑫𐑛 𐑜𐑴 𐑓𐑻𐑕𐑑.})

𐑞 ·𐑛𐑧𐑔 ·𐑰𐑑𐑼𐑟 𐑣𐑨𐑛 𐑓𐑪𐑤𐑴𐑛 𐑦𐑯 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛'𐑟 𐑢𐑱𐑒 𐑯 𐑦𐑯 𐑣𐑦𐑟 𐑝𐑨𐑯𐑜𐑸𐑛, 𐑒𐑨𐑮𐑾𐑯 𐑝𐑳𐑤𐑗𐑼𐑟 𐑑 𐑐𐑦𐑒 𐑨𐑑 𐑢𐑵𐑯𐑛𐑟, 𐑹 𐑕𐑯𐑱𐑒𐑕 𐑑 𐑚𐑲𐑑 𐑯 𐑢𐑰𐑒𐑩𐑯. 𐑞 ·𐑛𐑧𐑔 ·𐑰𐑑𐑼𐑟 𐑢𐑻 𐑯𐑪𐑑 𐑨𐑟 𐑑𐑧𐑮𐑦𐑚𐑩𐑤 𐑨𐑟 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛, 𐑚𐑳𐑑 𐑞𐑱 𐑢𐑻 𐑑𐑧𐑮𐑦𐑚𐑩𐑤, 𐑯 𐑞𐑱 𐑢𐑻 𐑥𐑧𐑯𐑦. 𐑯 𐑞 ·𐑛𐑧𐑔 ·𐑰𐑑𐑼𐑟 𐑢𐑰𐑤𐑛𐑩𐑛 𐑥𐑹 𐑞𐑨𐑯 𐑢𐑪𐑯𐑛𐑟; 𐑞𐑺 𐑢𐑪𐑟 𐑢𐑧𐑤𐑔 𐑢𐑦𐑞𐑦𐑯 𐑞𐑴𐑟 𐑥𐑭𐑕𐑒𐑑 𐑮𐑨𐑙𐑒𐑕, 𐑯 𐑐𐑪𐑤𐑦𐑑𐑦𐑒𐑩𐑤 𐑐𐑬𐑼, 𐑯 𐑕𐑰𐑒𐑮𐑩𐑑𐑕 𐑣𐑧𐑤𐑛 𐑦𐑯 𐑚𐑤𐑨𐑒𐑥𐑱𐑤, 𐑑 𐑐𐑨𐑮𐑩𐑤𐑲𐑟 𐑩 𐑕𐑩𐑕𐑲𐑩𐑑𐑦 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑐𐑮𐑩𐑑𐑧𐑒𐑑 𐑦𐑑𐑕𐑧𐑤𐑓.

𐑩𐑯 𐑴𐑤𐑛 𐑯 𐑮𐑦𐑕𐑐𐑧𐑒𐑑𐑩𐑛 𐑡𐑻𐑯𐑩𐑤𐑦𐑕𐑑, ·𐑘𐑧𐑮𐑥𐑦 ·𐑢𐑦𐑚𐑩𐑤, 𐑒𐑷𐑤𐑛 𐑓 𐑦𐑯𐑒𐑮𐑰𐑕𐑑 𐑑𐑨𐑒𐑕𐑩𐑟 𐑯 𐑒𐑩𐑯𐑕𐑒𐑮𐑦𐑐𐑖𐑩𐑯. 𐑣𐑰 𐑖𐑬𐑑𐑩𐑛 𐑞𐑨𐑑 𐑦𐑑 𐑢𐑪𐑟 𐑩𐑚𐑕𐑻𐑛 𐑓 𐑞 𐑥𐑧𐑯𐑦 𐑑 𐑒𐑬𐑼 𐑦𐑯 𐑓𐑽 𐑝 𐑞 𐑓𐑿. 𐑣𐑦𐑟 𐑕𐑒𐑦𐑯, 𐑴𐑯𐑤𐑦 𐑣𐑦𐑟 𐑕𐑒𐑦𐑯, 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑓𐑬𐑯𐑛 𐑯𐑱𐑤𐑛 𐑑 𐑞 𐑯𐑿𐑟𐑮𐑵𐑥 𐑢𐑷𐑤 𐑞𐑨𐑑 𐑯𐑧𐑒𐑕𐑑 𐑥𐑹𐑯𐑦𐑙, 𐑯𐑧𐑒𐑕𐑑 𐑑 𐑞 𐑕𐑒𐑦𐑯𐑟 𐑝 𐑣𐑦𐑟 𐑢𐑲𐑓 𐑯 𐑑𐑵 𐑛𐑷𐑑𐑼𐑟. 𐑧𐑝𐑮𐑦𐑢𐑳𐑯 𐑢𐑦𐑖𐑑 𐑓 𐑕𐑳𐑥𐑔𐑦𐑙 𐑥𐑹 𐑑 𐑚𐑰 𐑛𐑳𐑯, 𐑯 𐑯𐑴-𐑢𐑳𐑯 𐑛𐑺𐑛 𐑑𐑱𐑒 𐑞 𐑤𐑰𐑛 𐑑 𐑐𐑮𐑩𐑐𐑴𐑟 𐑦𐑑. 𐑣𐑵𐑧𐑝𐑼 𐑕𐑑𐑫𐑛 𐑬𐑑 𐑞 𐑥𐑴𐑕𐑑 𐑚𐑦𐑒𐑱𐑥 𐑞 𐑯𐑧𐑒𐑕𐑑 𐑦𐑜𐑟𐑭𐑥𐑐𐑩𐑤.

𐑩𐑯𐑑𐑦𐑤 𐑞 𐑯𐑱𐑥𐑟 𐑝 ·𐑡𐑱𐑥𐑟 𐑯 ·𐑤𐑦𐑤𐑦 ·𐑐𐑪𐑑𐑼 𐑮𐑴𐑟 𐑑 𐑞 𐑑𐑪𐑐 𐑝 𐑞𐑨𐑑 𐑤𐑦𐑕𐑑.

𐑯 𐑞𐑴𐑟 𐑑𐑵 𐑥𐑲𐑑 𐑣𐑨𐑝 𐑛𐑲𐑛 𐑢𐑦𐑞 𐑞𐑺 𐑢𐑪𐑯𐑛𐑟 𐑦𐑯 𐑞𐑺 𐑣𐑨𐑯𐑛𐑟 𐑯 𐑯𐑪𐑑 𐑮𐑦𐑜𐑮𐑧𐑑𐑩𐑛 𐑞𐑺 𐑗𐑶𐑕𐑩𐑟, 𐑓 𐑞𐑱 \emph{𐑢𐑻} 𐑣𐑽𐑴𐑟; 𐑚𐑳𐑑 𐑓 𐑞𐑨𐑑 𐑞𐑱 𐑣𐑨𐑛 𐑩𐑯 𐑦𐑯𐑓𐑩𐑯𐑑 𐑗𐑲𐑤𐑛, 𐑞𐑺 𐑕𐑳𐑯, ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼.

𐑑𐑽𐑟 𐑢𐑻 𐑒𐑳𐑥𐑦𐑙 𐑦𐑯𐑑𐑵 ·𐑣𐑨𐑮𐑦'𐑟 𐑲𐑟. 𐑣𐑰 𐑢𐑲𐑐𐑑 𐑞𐑧𐑥 𐑩𐑢𐑱 𐑦𐑯 𐑨𐑙𐑜𐑼 𐑹 𐑥𐑱𐑚𐑰 𐑛𐑧𐑕𐑐𐑼𐑱𐑖𐑩𐑯, \emph{𐑲 𐑛𐑦𐑛𐑩𐑯𐑑 𐑯𐑴 𐑞𐑴𐑟 𐑐𐑰𐑐𐑩𐑤, 𐑯𐑪𐑑 𐑮𐑾𐑤𐑦, 𐑞𐑱 𐑸𐑯𐑑 𐑥𐑲 𐑐𐑺𐑩𐑯𐑑𐑕 \emph{𐑯𐑬}, 𐑦𐑑 𐑢𐑫𐑛 𐑚𐑰 𐑐𐑶𐑯𐑑𐑤𐑩𐑕 𐑑 𐑓𐑰𐑤 𐑕𐑴 𐑕𐑨𐑛 𐑓 𐑞𐑧𐑥—}

𐑢𐑧𐑯 ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑛𐑳𐑯 𐑕𐑪𐑚𐑦𐑙 𐑦𐑯𐑑𐑵 𐑞 𐑢𐑦𐑗'𐑩𐑟 𐑮𐑴𐑚𐑟, 𐑣𐑰 𐑤𐑫𐑒𐑑 𐑳𐑐, 𐑯 𐑓𐑧𐑤𐑑 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑚𐑦𐑑 𐑚𐑧𐑑𐑼 𐑑 𐑕𐑰 𐑑𐑽𐑟 𐑦𐑯 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑲𐑟 𐑨𐑟 𐑢𐑧𐑤.

“𐑕𐑴 𐑢𐑪𐑑 𐑣𐑨𐑐𐑩𐑯𐑛?” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑣𐑦𐑟 𐑝𐑶𐑕 𐑑𐑮𐑧𐑥𐑚𐑩𐑤𐑦𐑙.

“𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛 𐑒𐑱𐑥 𐑑 ·𐑜𐑪𐑛𐑮𐑦𐑒'𐑕 ·𐑣𐑪𐑤𐑴,” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛 𐑦𐑯 𐑩 𐑢𐑦𐑕𐑐𐑼. “𐑿 𐑖𐑫𐑛 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑣𐑦𐑛𐑩𐑯, 𐑚𐑳𐑑 𐑿 𐑢𐑻 𐑚𐑦𐑑𐑮𐑱𐑛. 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛 𐑒𐑦𐑤𐑛 ·𐑡𐑱𐑥𐑟, 𐑯 𐑣𐑰 𐑒𐑦𐑤𐑛 ·𐑤𐑦𐑤𐑦, 𐑯 𐑣𐑰 𐑒𐑱𐑥 𐑦𐑯 𐑞 𐑧𐑯𐑛 𐑑 𐑿, 𐑑 𐑘𐑹 𐑒𐑪𐑑. 𐑣𐑰 𐑒𐑭𐑕𐑑 𐑞 ·𐑒𐑦𐑤𐑦𐑙 ·𐑒𐑻𐑕 𐑨𐑑 𐑿, 𐑯 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑢𐑺 𐑦𐑑 𐑧𐑯𐑛𐑩𐑛. 𐑞 ·𐑒𐑦𐑤𐑦𐑙 ·𐑒𐑻𐑕 𐑦𐑟 𐑓𐑹𐑥𐑛 𐑝 𐑐𐑘𐑫𐑼 𐑣𐑱𐑑, 𐑯 𐑕𐑑𐑮𐑲𐑒𐑕 𐑛𐑦𐑮𐑧𐑒𐑑𐑤𐑦 𐑨𐑑 𐑞 𐑕𐑴𐑤, 𐑕𐑧𐑝𐑼𐑦𐑙 𐑦𐑑 𐑓𐑮𐑪𐑥 𐑞 𐑚𐑪𐑛𐑦. 𐑦𐑑 𐑒𐑨𐑯𐑪𐑑 𐑚𐑰 𐑚𐑤𐑪𐑒𐑑, 𐑯 𐑣𐑵𐑥𐑧𐑝𐑼 𐑦𐑑 𐑕𐑑𐑮𐑲𐑒𐑕, 𐑞𐑱 𐑛𐑲. 𐑚𐑳𐑑 𐑿 𐑕𐑼𐑝𐑲𐑝𐑛. 𐑿 𐑸 𐑞 𐑴𐑯𐑤𐑦 𐑐𐑻𐑕𐑩𐑯 𐑧𐑝𐑼 𐑑 𐑕𐑼𐑝𐑲𐑝. 𐑞 ·𐑒𐑦𐑤𐑦𐑙 ·𐑒𐑻𐑕 𐑮𐑰𐑚𐑬𐑯𐑛𐑩𐑛 𐑯 𐑕𐑑𐑮𐑳𐑒 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛, 𐑤𐑰𐑝𐑦𐑙 𐑴𐑯𐑤𐑦 𐑞 𐑚𐑻𐑯𐑑 𐑣𐑳𐑤𐑒 𐑝 𐑣𐑦𐑟 𐑚𐑪𐑛𐑦 𐑯 𐑩 𐑕𐑒𐑸 𐑩𐑐𐑪𐑯 𐑘𐑹 𐑓𐑪𐑮𐑦𐑛. 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑞 𐑧𐑯𐑛 𐑝 𐑞 𐑑𐑧𐑮𐑼, 𐑯 𐑢𐑰 𐑢𐑻 𐑓𐑮𐑰. 𐑞𐑨𐑑, ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼, 𐑦𐑟 𐑢𐑲 𐑐𐑰𐑐𐑩𐑤 𐑢𐑪𐑯𐑑 𐑑 𐑕𐑰 𐑞 𐑕𐑒𐑸 𐑪𐑯 𐑘𐑹 𐑓𐑪𐑮𐑦𐑛, 𐑯 𐑢𐑲 𐑞𐑱 𐑢𐑪𐑯𐑑 𐑑 𐑖𐑱𐑒 𐑘𐑹 𐑣𐑨𐑯𐑛.”

𐑞 𐑕𐑑𐑹𐑥 𐑝 𐑢𐑰𐑐𐑦𐑙 𐑞𐑨𐑑 𐑣𐑨𐑛 𐑢𐑪𐑖𐑑 𐑔𐑮𐑵 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑿𐑟𐑛 𐑳𐑐 𐑷𐑤 𐑣𐑦𐑟 𐑑𐑽𐑟; 𐑣𐑰 𐑒𐑫𐑛 𐑯𐑪𐑑 𐑒𐑮𐑲 𐑩𐑜𐑱𐑯, 𐑣𐑰 𐑢𐑪𐑟 𐑛𐑳𐑯.

(𐑯 𐑕𐑳𐑥𐑢𐑺 𐑦𐑯 𐑞 𐑚𐑨𐑒 𐑝 𐑣𐑦𐑟 𐑥𐑲𐑯𐑛 𐑢𐑪𐑟 𐑩 𐑕𐑥𐑷𐑤, 𐑕𐑥𐑷𐑤 𐑯𐑴𐑑 𐑝 𐑒𐑩𐑯𐑓𐑿𐑠𐑩𐑯, 𐑩 𐑕𐑧𐑯𐑕 𐑝 𐑕𐑳𐑥𐑔𐑦𐑙 𐑮𐑪𐑙 𐑩𐑚𐑬𐑑 𐑞𐑨𐑑 𐑕𐑑𐑹𐑦; 𐑯 𐑦𐑑 𐑖𐑫𐑛 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑩 𐑐𐑸𐑑 𐑝 ·𐑣𐑨𐑮𐑦'𐑟 𐑸𐑑 𐑑 𐑯𐑴𐑑𐑦𐑕 𐑞𐑨𐑑 𐑑𐑲𐑯𐑦 𐑯𐑴𐑑, 𐑚𐑳𐑑 𐑣𐑰 𐑢𐑪𐑟 𐑛𐑦𐑕𐑑𐑮𐑨𐑒𐑑𐑩𐑛. 𐑓 𐑦𐑑 𐑦𐑟 𐑩 𐑕𐑨𐑛 𐑮𐑵𐑤 𐑞𐑨𐑑 𐑢𐑧𐑯𐑧𐑝𐑼 𐑿 𐑸 𐑥𐑴𐑕𐑑 𐑦𐑯 𐑯𐑰𐑛 𐑝 𐑘𐑹 𐑸𐑑 𐑨𐑟 𐑩 𐑮𐑨𐑖𐑩𐑯𐑩𐑤𐑦𐑕𐑑, 𐑞𐑨𐑑 𐑦𐑟 𐑢𐑧𐑯 𐑿 𐑸 𐑥𐑴𐑕𐑑 𐑤𐑲𐑒𐑤𐑦 𐑑 𐑓𐑼𐑜𐑧𐑑 𐑦𐑑.)

·𐑣𐑨𐑮𐑦 𐑛𐑦𐑑𐑨𐑗𐑑 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑓𐑮𐑪𐑥 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑕𐑲𐑛. “𐑲'𐑤—𐑣𐑨𐑓 𐑑 𐑔𐑦𐑙𐑒 𐑩𐑚𐑬𐑑 𐑞𐑦𐑕,” 𐑣𐑰 𐑕𐑧𐑛, 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑒𐑰𐑐 𐑣𐑦𐑟 𐑝𐑶𐑕 𐑳𐑯𐑛𐑼 𐑒𐑩𐑯𐑑𐑮𐑴𐑤. 𐑣𐑰 𐑕𐑑𐑺𐑛 𐑨𐑑 𐑣𐑦𐑟 𐑖𐑵𐑟. “𐑳𐑥. 𐑿 𐑒𐑨𐑯 𐑜𐑴 𐑩𐑣𐑧𐑛 𐑯 𐑒𐑷𐑤 𐑞𐑧𐑥 𐑥𐑲 𐑐𐑺𐑩𐑯𐑑𐑕, 𐑦𐑓 𐑿 𐑢𐑪𐑯𐑑, 𐑿 𐑛𐑴𐑯𐑑 𐑣𐑨𐑓 𐑑 𐑕𐑱 '𐑡𐑩𐑯𐑧𐑑𐑦𐑒 𐑐𐑺𐑩𐑯𐑑𐑕' 𐑹 𐑧𐑯𐑦𐑔𐑦𐑙. 𐑲 𐑜𐑧𐑕 𐑞𐑺'𐑟 𐑯𐑴 𐑮𐑰𐑟𐑩𐑯 𐑲 𐑒𐑭𐑯𐑑 𐑣𐑨𐑝 𐑑𐑵 𐑥𐑳𐑞𐑼𐑟 𐑯 𐑑𐑵 𐑓𐑭𐑞𐑼𐑟.”

𐑞𐑺 𐑢𐑪𐑟 𐑯𐑴 𐑕𐑬𐑯𐑛 𐑓𐑮𐑪𐑥 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤.

𐑯 𐑞𐑱 𐑢𐑷𐑒𐑑 𐑑𐑩𐑜𐑧𐑞𐑼 𐑦𐑯 𐑕𐑲𐑤𐑩𐑯𐑕, 𐑩𐑯𐑑𐑦𐑤 𐑞𐑱 𐑒𐑱𐑥 𐑚𐑦𐑓𐑹 𐑩 𐑜𐑮𐑱𐑑 𐑢𐑲𐑑 𐑚𐑦𐑤𐑛𐑦𐑙 𐑢𐑦𐑞 𐑝𐑭𐑕𐑑 𐑚𐑮𐑪𐑯𐑟 𐑛𐑹𐑟, 𐑯 𐑒𐑸𐑝𐑩𐑯 𐑢𐑻𐑛𐑟 𐑩𐑚𐑳𐑝 𐑕𐑱𐑦𐑙 \emph{·𐑜𐑮𐑦𐑙𐑜𐑩𐑑𐑕 ·𐑚𐑨𐑙𐑒.}

%  𐑤𐑴𐑒𐑩𐑤𐑢𐑻𐑛𐑟:  𐑵𐑛 ·𐑚𐑦𐑜𐑚𐑨𐑥'𐑟
