\chapter{𐑞 ·𐑓𐑳𐑯𐑛𐑩𐑥𐑧𐑯𐑑𐑩𐑤 ·𐑨𐑑𐑮𐑦𐑚𐑿𐑖𐑩𐑯 ·𐑧𐑮𐑼}

\begin{chapterOpeningAuthorNote}
·𐑡.~𐑒.~·𐑮𐑴𐑤𐑦𐑙 𐑦𐑟 𐑕𐑑𐑺𐑦𐑙 𐑨𐑑 𐑿. 𐑒𐑨𐑯 𐑿 𐑓𐑰𐑤 𐑣𐑻 𐑲𐑟 𐑪𐑯 𐑿? 𐑖𐑰'𐑟 𐑮𐑰𐑛𐑦𐑙 𐑘𐑹 𐑥𐑲𐑯𐑛 𐑿𐑟𐑦𐑙 𐑣𐑻 ·𐑮𐑴𐑤𐑦𐑙 ·𐑮𐑱𐑟.
\end{chapterOpeningAuthorNote}
\begin{chapterOpeningQuote}
𐑦𐑑 𐑢𐑫𐑛'𐑝 𐑮𐑦𐑒𐑢𐑲𐑼𐑛 𐑩 𐑕𐑵𐑐𐑼𐑯𐑨𐑗𐑼𐑩𐑤 𐑦𐑯𐑑𐑼𐑝𐑧𐑯𐑖𐑩𐑯 𐑓 𐑣𐑦𐑥 𐑑 𐑣𐑨𐑝 𐑘𐑹 𐑥𐑼𐑨𐑤𐑦𐑑𐑦 𐑜𐑦𐑝𐑩𐑯 𐑣𐑦𐑟 𐑦𐑯𐑝𐑲𐑮𐑩𐑯𐑥𐑩𐑯𐑑.
\end{chapterOpeningQuote}

\lettrine{𐑞}{} ·𐑥𐑴𐑒 ·𐑖𐑪𐑐 𐑢𐑪𐑟 𐑩 𐑒𐑢𐑱𐑯𐑑 𐑤𐑦𐑑𐑩𐑤 𐑖𐑪𐑐 (𐑕𐑳𐑥 𐑥𐑲𐑑 𐑰𐑝𐑩𐑯 𐑕𐑱 𐑒𐑿𐑑) 𐑦𐑯𐑕𐑒𐑪𐑯𐑕𐑑 𐑚𐑦𐑣𐑲𐑯𐑛 𐑩 𐑝𐑧𐑡𐑑𐑩𐑚𐑩𐑤 𐑕𐑑𐑷𐑤 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑚𐑦𐑣𐑲𐑯𐑛 𐑩 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 𐑜𐑤𐑳𐑝 𐑖𐑪𐑐 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑪𐑯 𐑩𐑯 𐑨𐑤𐑦𐑢𐑱 𐑪𐑓 𐑩 𐑕𐑲𐑛 𐑕𐑑𐑮𐑰𐑑 𐑝 ·𐑛𐑲𐑨𐑜𐑩𐑯 ·𐑨𐑤𐑦. 𐑛𐑦𐑕𐑩𐑐𐑶𐑯𐑑𐑦𐑙𐑤𐑦, 𐑞 𐑖𐑪𐑐𐑒𐑰𐑐𐑼 𐑢𐑪𐑟 𐑯𐑪𐑑 𐑩 𐑢𐑦𐑟𐑩𐑯𐑛 𐑱𐑯𐑖𐑩𐑯𐑑 𐑒𐑮𐑴𐑯; 𐑡𐑳𐑕𐑑 𐑩 𐑯𐑻𐑝𐑩𐑕-𐑤𐑫𐑒𐑦𐑙 𐑘𐑳𐑙 𐑢𐑫𐑥𐑩𐑯 𐑢𐑺𐑦𐑙 𐑓𐑱𐑛𐑩𐑛 𐑘𐑧𐑤𐑴 𐑮𐑴𐑚𐑟. 𐑮𐑲𐑑 𐑯𐑬 𐑖𐑰 𐑢𐑪𐑟 𐑣𐑴𐑤𐑛𐑦𐑙 𐑬𐑑 𐑩 ·𐑥𐑴𐑒 ·𐑕𐑵𐑐𐑼 ·𐑐𐑬𐑗 \abbrev{QX31}, 𐑣𐑵𐑟 𐑕𐑧𐑤𐑦𐑙 𐑐𐑶𐑯𐑑 𐑢𐑪𐑟 𐑞𐑨𐑑 𐑦𐑑 𐑣𐑨𐑛 𐑩 ·𐑢𐑲𐑛𐑩𐑯𐑦𐑙 ·𐑤𐑦𐑐 𐑨𐑟 𐑢𐑧𐑤 𐑨𐑟 𐑩𐑯 ·𐑳𐑯𐑛𐑦𐑑𐑧𐑒𐑑𐑩𐑚𐑩𐑤 ·𐑦𐑒𐑕𐑑𐑧𐑯𐑖𐑩𐑯 ·𐑗𐑸𐑥: 𐑿 𐑒𐑫𐑛 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑓𐑦𐑑 𐑚𐑦𐑜 𐑔𐑦𐑙𐑟 𐑦𐑯 𐑦𐑑, 𐑞𐑴 𐑞 𐑑𐑴𐑑𐑩𐑤 𐑝𐑪𐑤𐑿𐑥 𐑢𐑪𐑟 𐑕𐑑𐑦𐑤 𐑤𐑦𐑥𐑦𐑑𐑩𐑛.

·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 \emph{𐑦𐑯𐑕𐑦𐑕𐑑𐑩𐑛} 𐑪𐑯 𐑒𐑳𐑥𐑦𐑙 𐑣𐑽 𐑕𐑑𐑮𐑱𐑑 𐑩𐑢𐑱, 𐑓𐑻𐑕𐑑 𐑔𐑦𐑙—𐑦𐑯𐑕𐑦𐑕𐑑𐑩𐑛 𐑨𐑟 𐑣𐑸𐑛 𐑨𐑟 𐑣𐑰 𐑔𐑷𐑑 𐑣𐑰 𐑒𐑫𐑛 𐑢𐑦𐑞𐑬𐑑 𐑥𐑱𐑒𐑦𐑙 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑩𐑕𐑐𐑦𐑖𐑩𐑕. ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑕𐑳𐑥𐑔𐑦𐑙 𐑣𐑰 𐑯𐑰𐑛𐑩𐑛 𐑑 𐑐𐑫𐑑 𐑦𐑯𐑑𐑵 𐑞 𐑐𐑬𐑗 𐑨𐑟 𐑕𐑵𐑯 𐑨𐑟 𐑐𐑪𐑕𐑩𐑚𐑩𐑤. 𐑦𐑑 𐑢𐑪𐑟𐑩𐑯𐑑 𐑞 𐑚𐑨𐑜 𐑝 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑞𐑨𐑑 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑣𐑨𐑛 𐑩𐑤𐑬𐑛 𐑣𐑦𐑥 𐑑 𐑢𐑦𐑞𐑛𐑮𐑷 𐑓𐑮𐑪𐑥 ·𐑜𐑮𐑦𐑙𐑜𐑩𐑑𐑕. 𐑦𐑑 𐑢𐑪𐑟 𐑷𐑤 𐑞 𐑳𐑞𐑼 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑞𐑨𐑑 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑕𐑳𐑮𐑩𐑐𐑑𐑦𐑖𐑩𐑕𐑤𐑦 𐑖𐑳𐑝𐑛 𐑦𐑯𐑑𐑵 𐑣𐑦𐑟 𐑐𐑪𐑒𐑩𐑑 𐑭𐑓𐑑𐑼 𐑓𐑷𐑤𐑦𐑙 𐑦𐑯𐑑𐑵 𐑩 𐑣𐑰𐑐 𐑝 𐑜𐑴𐑤𐑛 𐑒𐑶𐑯𐑟. 𐑞𐑨𐑑 \emph{𐑣𐑨𐑛} 𐑚𐑰𐑯 𐑩 𐑮𐑾𐑤 𐑨𐑒𐑕𐑦𐑛𐑩𐑯𐑑, 𐑚𐑳𐑑 ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑯𐑧𐑝𐑼 𐑢𐑳𐑯 𐑑 𐑛𐑦𐑕𐑒𐑸𐑛 𐑩𐑯 𐑪𐑐𐑼𐑑𐑿𐑯𐑦𐑑𐑦…𐑞𐑴 𐑦𐑑'𐑩𐑛 𐑮𐑾𐑤𐑦 𐑚𐑰𐑯 𐑥𐑹 𐑝 𐑩 𐑕𐑐𐑻-𐑝-𐑞-𐑥𐑴𐑥𐑩𐑯𐑑 𐑔𐑦𐑙. 𐑧𐑝𐑼 𐑕𐑦𐑯𐑕 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑷𐑒𐑢𐑼𐑛𐑤𐑦 𐑒𐑨𐑮𐑦𐑦𐑙 𐑞 𐑩𐑤𐑬𐑛 𐑚𐑨𐑜 𐑝 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑯𐑧𐑒𐑕𐑑 𐑑 𐑣𐑦𐑟 𐑑𐑮𐑬𐑟𐑼 𐑐𐑪𐑒𐑩𐑑, 𐑕𐑴 𐑞𐑨𐑑 𐑧𐑯𐑦 𐑡𐑦𐑙𐑜𐑩𐑤𐑦𐑙 𐑢𐑫𐑛 𐑕𐑰𐑥 𐑑 𐑒𐑳𐑥 𐑓𐑮𐑪𐑥 𐑞 𐑮𐑲𐑑 𐑐𐑤𐑱𐑕.

𐑞𐑦𐑕 𐑕𐑑𐑦𐑤 𐑤𐑧𐑓𐑑 𐑞 𐑒𐑢𐑧𐑕𐑗𐑩𐑯 𐑝 𐑣𐑬 𐑣𐑰 𐑢𐑪𐑟 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑜𐑴𐑦𐑙 𐑑 𐑜𐑧𐑑 𐑞 \emph{𐑳𐑞𐑼} 𐑒𐑶𐑯𐑟 𐑦𐑯𐑑𐑵 𐑞 𐑐𐑬𐑗 𐑢𐑦𐑞𐑬𐑑 𐑜𐑧𐑑𐑦𐑙 𐑒𐑷𐑑. 𐑞 𐑜𐑴𐑤𐑛𐑩𐑯 𐑒𐑶𐑯𐑟 𐑥𐑲𐑑 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑣𐑦𐑟, 𐑚𐑳𐑑 𐑞𐑱 𐑢𐑻 𐑕𐑑𐑦𐑤 𐑕𐑑𐑴𐑤𐑩𐑯—𐑕𐑧𐑤𐑓-𐑕𐑑𐑴𐑤𐑩𐑯? 𐑷𐑑𐑴-𐑔𐑰𐑝𐑛?

·𐑣𐑨𐑮𐑦 𐑤𐑫𐑒𐑑 𐑳𐑐 𐑓𐑮𐑪𐑥 𐑞 ·𐑥𐑴𐑒 ·𐑕𐑵𐑐𐑼 ·𐑐𐑬𐑗 \abbrev{QX31} 𐑪𐑯 𐑞 𐑒𐑬𐑯𐑑𐑼 𐑦𐑯 𐑓𐑮𐑳𐑯𐑑 𐑝 𐑣𐑦𐑥. “𐑒𐑨𐑯 𐑲 𐑑𐑮𐑲 𐑞𐑦𐑕 𐑓 𐑩 𐑚𐑦𐑑? 𐑑 𐑥𐑱𐑒 𐑖𐑫𐑼 𐑦𐑑 𐑢𐑻𐑒𐑕, 𐑳𐑥, 𐑮𐑦𐑤𐑲𐑩𐑚𐑤𐑦?” 𐑣𐑰 𐑢𐑲𐑛𐑩𐑯𐑛 𐑣𐑦𐑟 𐑲𐑟 𐑦𐑯 𐑩𐑯 𐑦𐑒𐑕𐑐𐑮𐑧𐑖𐑩𐑯 𐑝 𐑚𐑶𐑦𐑖, 𐑐𐑤𐑱𐑓𐑩𐑤 𐑦𐑯𐑩𐑕𐑩𐑯𐑕.

𐑖𐑫𐑼 𐑦𐑯𐑳𐑓, 𐑭𐑓𐑑𐑼 𐑑𐑧𐑯 𐑮𐑧𐑐𐑦𐑑𐑦𐑖𐑩𐑯𐑟 𐑝 𐑐𐑫𐑑𐑦𐑙 𐑞 𐑒𐑶𐑯-𐑚𐑨𐑜 𐑦𐑯𐑑𐑵 𐑞 𐑐𐑬𐑗, 𐑮𐑰𐑗𐑦𐑙 𐑦𐑯, 𐑢𐑦𐑕𐑐𐑼𐑦𐑙 “𐑚𐑨𐑜 𐑝 𐑜𐑴𐑤𐑛”, 𐑯 𐑑𐑱𐑒𐑦𐑙 𐑦𐑑 𐑬𐑑, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑑𐑫𐑒 𐑩 𐑕𐑑𐑧𐑐 𐑩𐑢𐑱 𐑯 𐑚𐑦𐑜𐑨𐑯 𐑦𐑜𐑟𐑨𐑥𐑦𐑯𐑦𐑙 𐑕𐑳𐑥 𐑝 𐑞 𐑳𐑞𐑼 𐑲𐑑𐑩𐑥𐑟 𐑦𐑯 𐑞 𐑖𐑪𐑐, 𐑯 𐑞 𐑖𐑪𐑐𐑒𐑰𐑐𐑼 𐑑𐑻𐑯𐑛 𐑣𐑻 𐑣𐑧𐑛 𐑑 𐑢𐑪𐑗.

·𐑣𐑨𐑮𐑦 𐑛𐑮𐑪𐑐𐑑 𐑞 𐑚𐑨𐑜 𐑝 𐑜𐑴𐑤𐑛 𐑦𐑯𐑑𐑵 𐑞 𐑥𐑴𐑒𐑕𐑒𐑦𐑯 𐑐𐑬𐑗 𐑢𐑦𐑞 𐑣𐑦𐑟 \emph{𐑤𐑧𐑓𐑑} 𐑣𐑨𐑯𐑛; 𐑣𐑦𐑟 \emph{𐑮𐑲𐑑} 𐑣𐑨𐑯𐑛 𐑒𐑱𐑥 𐑬𐑑 𐑝 𐑣𐑦𐑟 𐑐𐑪𐑒𐑩𐑑 𐑑𐑲𐑑𐑤𐑦 𐑣𐑴𐑤𐑛𐑦𐑙 𐑕𐑳𐑥 𐑝 𐑞 𐑜𐑴𐑤𐑛 𐑒𐑶𐑯𐑟, 𐑮𐑰𐑗𐑑 𐑦𐑯𐑑𐑵 𐑞 𐑥𐑴𐑒𐑕𐑒𐑦𐑯 𐑐𐑬𐑗, 𐑛𐑮𐑪𐑐𐑑 𐑞 𐑤𐑵𐑕 ·𐑜𐑨𐑤𐑾𐑯𐑟, 𐑯 (𐑢𐑦𐑞 𐑩 𐑢𐑦𐑕𐑐𐑼 𐑝 “𐑚𐑨𐑜 𐑝 𐑜𐑴𐑤𐑛”) 𐑮𐑦𐑑𐑮𐑰𐑝𐑛 𐑞 𐑼𐑦𐑡𐑦𐑯𐑩𐑤 𐑚𐑨𐑜. 𐑞𐑧𐑯 𐑞 𐑚𐑨𐑜 𐑢𐑧𐑯𐑑 𐑚𐑨𐑒 𐑦𐑯𐑑𐑵 𐑣𐑦𐑟 \emph{𐑤𐑧𐑓𐑑} 𐑣𐑨𐑯𐑛, 𐑑 𐑚𐑰 𐑛𐑮𐑪𐑐𐑑 𐑦𐑯 𐑩𐑜𐑱𐑯, 𐑯 ·𐑣𐑨𐑮𐑦'𐑟 \emph{𐑮𐑲𐑑} 𐑣𐑨𐑯𐑛 𐑢𐑧𐑯𐑑 𐑚𐑨𐑒 𐑦𐑯𐑑𐑵 𐑣𐑦𐑟 𐑐𐑪𐑒𐑩𐑑…

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑤𐑫𐑒𐑑 𐑚𐑨𐑒 𐑨𐑑 𐑣𐑦𐑥 𐑢𐑳𐑯𐑕, 𐑚𐑳𐑑 ·𐑣𐑨𐑮𐑦 𐑥𐑨𐑯𐑦𐑡𐑛 𐑑 𐑩𐑝𐑶𐑛 𐑓𐑮𐑰𐑟𐑦𐑙 𐑹 𐑓𐑤𐑦𐑯𐑗𐑦𐑙, 𐑯 𐑖𐑰 𐑛𐑦𐑛𐑩𐑯𐑑 𐑕𐑰𐑥 𐑑 𐑯𐑴𐑑𐑦𐑕 𐑧𐑯𐑦𐑔𐑦𐑙. 𐑞𐑴 𐑿 𐑯𐑧𐑝𐑼 \emph{𐑛𐑦𐑛} 𐑒𐑢𐑲𐑑 𐑯𐑴, 𐑢𐑦𐑞 𐑞 𐑨𐑛𐑳𐑤𐑑𐑕 𐑞𐑨𐑑 𐑣𐑨𐑛 𐑩 𐑕𐑧𐑯𐑕 𐑝 𐑣𐑿𐑥𐑼. 𐑦𐑑 𐑑𐑫𐑒 𐑔𐑮𐑰 𐑦𐑑𐑼𐑱𐑖𐑩𐑯𐑟 𐑑 𐑜𐑧𐑑 𐑞 𐑡𐑪𐑚 𐑛𐑳𐑯, 𐑯 ·𐑣𐑨𐑮𐑦 𐑜𐑧𐑕𐑑 𐑣𐑰'𐑛 𐑥𐑨𐑯𐑦𐑡𐑛 𐑑 𐑕𐑑𐑰𐑤 𐑥𐑱𐑚𐑰 𐑔𐑻𐑑𐑦 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑓𐑮𐑪𐑥 𐑣𐑦𐑥𐑕𐑧𐑤𐑓.

·𐑣𐑨𐑮𐑦 𐑮𐑰𐑗𐑑 𐑳𐑐, 𐑢𐑲𐑐𐑑 𐑩 𐑚𐑦𐑑 𐑝 𐑕𐑢𐑧𐑑 𐑓𐑮𐑪𐑥 𐑣𐑦𐑟 𐑓𐑪𐑮𐑦𐑛, 𐑯 𐑧𐑒𐑕𐑣𐑱𐑤𐑛. “𐑲'𐑛 𐑤𐑲𐑒 𐑞𐑦𐑕 𐑢𐑳𐑯, 𐑐𐑤𐑰𐑟.”

𐑓𐑦𐑓𐑑𐑰𐑯 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑤𐑲𐑑𐑼 (𐑑𐑢𐑲𐑕 𐑞 𐑐𐑮𐑲𐑕 𐑝 𐑩 𐑢𐑦𐑟𐑼𐑛'𐑟 𐑢𐑪𐑯𐑛, 𐑩𐑐𐑨𐑮𐑩𐑯𐑑𐑤𐑦) 𐑯 𐑢𐑳𐑯 ·𐑥𐑴𐑒 ·𐑕𐑵𐑐𐑼 ·𐑐𐑬𐑗 \abbrev{QX31} 𐑣𐑧𐑝𐑽, ·𐑣𐑨𐑮𐑦 𐑯 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑐𐑫𐑖𐑑 𐑞𐑺 𐑢𐑱 𐑬𐑑 𐑝 𐑞 𐑛𐑹. 𐑞 𐑛𐑹 𐑓𐑹𐑥𐑛 𐑩 𐑣𐑨𐑯𐑛 𐑯 𐑢𐑱𐑝𐑛 𐑜𐑫𐑛𐑚𐑲 𐑑 𐑞𐑧𐑥 𐑨𐑟 𐑞𐑱 𐑤𐑧𐑓𐑑, 𐑦𐑒𐑕𐑑𐑮𐑵𐑛𐑦𐑙 𐑦𐑑𐑕 𐑸𐑥 𐑦𐑯 𐑩 𐑢𐑱 𐑞𐑨𐑑 𐑥𐑱𐑛 ·𐑣𐑨𐑮𐑦 𐑓𐑰𐑤 𐑩 𐑚𐑦𐑑 𐑒𐑢𐑰𐑟𐑦.

𐑯 𐑞𐑧𐑯, 𐑳𐑯𐑓𐑹𐑗𐑩𐑯𐑩𐑑𐑤𐑦…

“𐑸 𐑿 \emph{𐑮𐑾𐑤𐑦} ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼?” 𐑢𐑦𐑕𐑐𐑼𐑛 𐑞 𐑴𐑤𐑛 𐑥𐑨𐑯, 𐑢𐑳𐑯 𐑣𐑿𐑡 𐑑𐑺@𐑑𐑽 𐑕𐑤𐑲𐑛𐑦𐑙 𐑛𐑬𐑯 𐑣𐑦𐑟 𐑗𐑰𐑒. “𐑿 𐑢𐑫𐑛𐑩𐑯𐑑 𐑤𐑲 𐑩𐑚𐑬𐑑 𐑞𐑨𐑑, 𐑢𐑫𐑛 𐑿? 𐑴𐑯𐑤𐑦 𐑲'𐑛 𐑣𐑻𐑛 𐑮𐑵𐑥𐑼𐑟 𐑞𐑨𐑑 𐑿 𐑛𐑦𐑛𐑩𐑯𐑑 \emph{𐑮𐑾𐑤𐑦} 𐑕𐑼𐑝𐑲𐑝 𐑞 ·𐑒𐑦𐑤𐑦𐑙 ·𐑒𐑻𐑕 𐑯 𐑞𐑨𐑑'𐑕 𐑢𐑲 𐑯𐑴-𐑢𐑳𐑯 𐑧𐑝𐑼 𐑣𐑻𐑛 𐑓𐑮𐑪𐑥 𐑿 𐑩𐑜𐑱𐑯.”

…𐑦𐑑 𐑕𐑰𐑥𐑛 𐑞𐑨𐑑 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑛𐑦𐑕𐑜𐑲𐑟 𐑕𐑐𐑧𐑤 𐑢𐑪𐑟 𐑤𐑧𐑕 𐑞𐑨𐑯 𐑐𐑻𐑓𐑦𐑒𐑑𐑤𐑦 𐑦𐑓𐑧𐑒𐑑𐑦𐑝 𐑩𐑜𐑱𐑯𐑕𐑑 𐑥𐑹 𐑦𐑒𐑕𐑐𐑽𐑾𐑯𐑕𐑑 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 𐑐𐑮𐑨𐑒𐑑𐑦𐑖𐑩𐑯𐑼𐑟.

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑣𐑨𐑛 𐑤𐑱𐑛 𐑩 𐑣𐑨𐑯𐑛 𐑪𐑯 ·𐑣𐑨𐑮𐑦'𐑟 𐑖𐑴𐑤𐑛𐑼 𐑯 𐑘𐑨𐑙𐑒𐑑 𐑣𐑦𐑥 𐑦𐑯𐑑𐑵 𐑞 𐑯𐑽𐑩𐑕𐑑 𐑨𐑤𐑦𐑢𐑱 𐑞 𐑥𐑴𐑥𐑩𐑯𐑑 𐑖𐑰'𐑛 𐑣𐑻𐑛 “·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼?” 𐑞 𐑴𐑤𐑛 𐑥𐑨𐑯 𐑣𐑨𐑛 𐑓𐑪𐑤𐑴𐑛, 𐑚𐑳𐑑 𐑨𐑑 𐑤𐑰𐑕𐑑 𐑦𐑑 𐑤𐑫𐑒𐑑 𐑤𐑲𐑒 𐑯𐑴-𐑢𐑳𐑯 𐑧𐑤𐑕 𐑣𐑨𐑛 𐑣𐑻𐑛.

·𐑣𐑨𐑮𐑦 𐑒𐑩𐑯𐑕𐑦𐑛𐑼𐑛 𐑞 𐑒𐑢𐑧𐑕𐑗𐑩𐑯. \emph{𐑢𐑪𐑟} 𐑣𐑰 𐑮𐑾𐑤𐑦 ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼? “𐑲 𐑴𐑯𐑤𐑦 𐑯𐑴 𐑢𐑪𐑑 𐑳𐑞𐑼 𐑐𐑰𐑐𐑩𐑤 𐑣𐑨𐑝 𐑑𐑴𐑤𐑛 𐑥𐑰,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. “𐑦𐑑'𐑕 𐑯𐑪𐑑 𐑤𐑲𐑒 𐑲 𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑚𐑰𐑦𐑙 𐑚𐑹𐑯.” 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛 𐑚𐑮𐑳𐑖𐑑 𐑣𐑦𐑟 𐑓𐑪𐑮𐑦𐑛. “𐑲'𐑝 𐑣𐑨𐑛 𐑞𐑦𐑕 𐑕𐑒𐑸 𐑨𐑟 𐑤𐑪𐑙 𐑨𐑟 𐑲 𐑮𐑦𐑥𐑧𐑥𐑚𐑼, 𐑯 𐑲'𐑝 𐑚𐑰𐑯 𐑑𐑴𐑤𐑛 𐑥𐑲 𐑯𐑱𐑥 𐑢𐑪𐑟 ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼 𐑨𐑟 𐑤𐑪𐑙 𐑨𐑟 𐑲 𐑮𐑦𐑥𐑧𐑥𐑚𐑼. 𐑚𐑳𐑑,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑔𐑷𐑑𐑓𐑩𐑤𐑦, “𐑦𐑓 𐑞𐑺'𐑟 𐑷𐑤𐑮𐑧𐑛𐑦 𐑕𐑩𐑓𐑦𐑖𐑩𐑯𐑑 𐑒𐑷𐑟 𐑑 𐑐𐑪𐑕𐑗𐑩𐑤𐑱𐑑 𐑩 𐑒𐑩𐑯𐑕𐑐𐑦𐑮𐑩𐑕𐑦, 𐑞𐑺'𐑟 𐑯𐑴 𐑮𐑰𐑟𐑩𐑯 𐑢𐑲 𐑞𐑱 𐑢𐑫𐑛𐑩𐑯𐑑 𐑡𐑳𐑕𐑑 𐑓𐑲𐑯𐑛 𐑩𐑯𐑳𐑞𐑼 𐑹𐑓𐑩𐑯 𐑯 𐑮𐑱𐑟 𐑣𐑦𐑥 𐑑 𐑚𐑦𐑤𐑰𐑝 𐑞𐑨𐑑 \emph{𐑣𐑰} 𐑢𐑪𐑟 ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼—”

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑛𐑮𐑵 𐑣𐑻 𐑣𐑨𐑯𐑛 𐑴𐑝𐑼 𐑣𐑻 𐑓𐑱𐑕 𐑦𐑯 𐑦𐑜𐑟𐑨𐑕𐑐𐑼𐑱𐑖𐑩𐑯. “𐑿 𐑤𐑫𐑒 𐑡𐑳𐑕𐑑 𐑩𐑚𐑬𐑑 𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦 𐑤𐑲𐑒 𐑘𐑹 𐑓𐑭𐑞𐑼, ·𐑡𐑱𐑥𐑟, 𐑞 𐑘𐑽 𐑣𐑰 𐑓𐑻𐑕𐑑 𐑩𐑑𐑧𐑯𐑛𐑩𐑛 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕. 𐑯 𐑲 𐑒𐑨𐑯 𐑩𐑑𐑧𐑕𐑑 𐑪𐑯 𐑞 𐑚𐑱𐑕𐑦𐑕 𐑝 \emph{𐑐𐑻𐑕𐑩𐑯𐑨𐑤𐑦𐑑𐑦 𐑩𐑤𐑴𐑯} 𐑞𐑨𐑑 𐑿 𐑸 𐑮𐑦𐑤𐑱𐑑𐑩𐑛 𐑑 𐑞 ·𐑕𐑒𐑻𐑡 𐑝 ·𐑜𐑮𐑦𐑓𐑦𐑯𐑛𐑹.”

“\emph{𐑖𐑰} 𐑒𐑫𐑛 𐑚𐑰 𐑦𐑯 𐑪𐑯 𐑦𐑑 𐑑𐑵,” ·𐑣𐑨𐑮𐑦 𐑩𐑚𐑟𐑻𐑝𐑛.

“𐑯𐑴,” 𐑒𐑢𐑱𐑝𐑼𐑛 𐑞 𐑴𐑤𐑛 𐑥𐑨𐑯. “𐑖𐑰'𐑟 𐑮𐑲𐑑. 𐑿 𐑣𐑨𐑝 𐑘𐑹 𐑥𐑳𐑞𐑼'𐑟 𐑲𐑟.”

“𐑣𐑥𐑥,” ·𐑣𐑨𐑮𐑦 𐑓𐑮𐑬𐑯𐑛. “𐑲 𐑕𐑩𐑐𐑴𐑟 \emph{𐑿} 𐑒𐑫𐑛 𐑚𐑰 𐑦𐑯 𐑪𐑯 𐑦𐑑 𐑑𐑵—”

“𐑦𐑯𐑳𐑓, ·𐑥𐑼~·𐑐𐑪𐑑𐑼.”

𐑞 𐑴𐑤𐑛 𐑥𐑨𐑯 𐑮𐑱𐑟𐑛 𐑳𐑐 𐑩 𐑣𐑨𐑯𐑛 𐑨𐑟 𐑦𐑓 𐑑 𐑑𐑳𐑗 ·𐑣𐑨𐑮𐑦, 𐑚𐑳𐑑 𐑞𐑧𐑯 𐑤𐑧𐑑 𐑦𐑑 𐑓𐑷𐑤. “𐑲'𐑥 𐑡𐑳𐑕𐑑 𐑜𐑤𐑨𐑛 𐑞𐑨𐑑 𐑿'𐑼 𐑩𐑤𐑲𐑝,” 𐑣𐑰 𐑥𐑻𐑥𐑼𐑛. “𐑔𐑨𐑙𐑒 𐑿, ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼. 𐑔𐑨𐑙𐑒 𐑿 𐑓 𐑢𐑪𐑑 𐑿 𐑛𐑦𐑛…𐑲'𐑤 𐑤𐑰𐑝 𐑿 𐑩𐑤𐑴𐑯 𐑯𐑬.”

𐑯 𐑣𐑦𐑟 𐑒𐑱𐑯 𐑕𐑤𐑴𐑤𐑦 𐑑𐑨𐑐𐑑 𐑩𐑢𐑱, 𐑬𐑑 𐑞 𐑨𐑤𐑦 𐑯 𐑛𐑬𐑯 𐑞 𐑥𐑱𐑯 𐑕𐑑𐑮𐑰𐑑 𐑝 ·𐑛𐑲𐑨𐑜𐑩𐑯 ·𐑨𐑤𐑦.

𐑞 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑤𐑫𐑒𐑑 𐑼𐑬𐑯𐑛, 𐑣𐑻 𐑦𐑒𐑕𐑐𐑮𐑧𐑖𐑩𐑯 𐑑𐑧𐑯𐑕 𐑯 𐑜𐑮𐑦𐑥. ·𐑣𐑨𐑮𐑦 𐑷𐑑𐑩𐑥𐑨𐑑𐑦𐑒𐑤𐑦 𐑤𐑫𐑒𐑑 𐑼𐑬𐑯𐑛 𐑣𐑦𐑥𐑕𐑧𐑤𐑓. 𐑚𐑳𐑑 𐑞 𐑨𐑤𐑦 𐑕𐑰𐑥𐑛 𐑧𐑥𐑐𐑑𐑦 𐑝 𐑷𐑤 𐑚𐑳𐑑 𐑴𐑤𐑛 𐑤𐑰𐑝𐑟, 𐑯 𐑓𐑮𐑪𐑥 𐑞 𐑥𐑬𐑔 𐑤𐑰𐑛𐑦𐑙 𐑬𐑑 𐑦𐑯𐑑𐑵 ·𐑛𐑲𐑨𐑜𐑩𐑯 ·𐑨𐑤𐑦, 𐑴𐑯𐑤𐑦 𐑕𐑢𐑦𐑓𐑑𐑤𐑦 𐑕𐑑𐑮𐑲𐑛𐑦𐑙 𐑐𐑭𐑕𐑼𐑟-𐑚𐑲 𐑒𐑫𐑛 𐑚𐑰 𐑕𐑰𐑯.

𐑓𐑲𐑯𐑩𐑤𐑦 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑰𐑥𐑛 𐑑 𐑮𐑦𐑤𐑨𐑒𐑕. “𐑞𐑨𐑑 𐑢𐑪𐑟 𐑯𐑪𐑑 𐑢𐑧𐑤 𐑛𐑳𐑯,” 𐑖𐑰 𐑕𐑧𐑛 𐑦𐑯 𐑩 𐑤𐑴 𐑝𐑶𐑕. “𐑲 𐑯𐑴 𐑿'𐑼 𐑯𐑪𐑑 𐑿𐑕𐑑 𐑑 𐑞𐑦𐑕, ·𐑥𐑼~·𐑐𐑪𐑑𐑼, 𐑚𐑳𐑑 𐑐𐑰𐑐𐑩𐑤 𐑛𐑵 𐑒𐑺 𐑩𐑚𐑬𐑑 𐑿. 𐑐𐑤𐑰𐑟 𐑚𐑰 𐑒𐑲𐑯𐑛 𐑑 𐑞𐑧𐑥.”

·𐑣𐑨𐑮𐑦 𐑤𐑫𐑒𐑑 𐑛𐑬𐑯 𐑨𐑑 𐑣𐑦𐑟 𐑖𐑵𐑟. “𐑞𐑱 𐑖𐑫𐑛𐑩𐑯𐑑,” 𐑣𐑰 𐑕𐑧𐑛 𐑢𐑦𐑞 𐑩 𐑑𐑦𐑯𐑡 𐑝 𐑚𐑦𐑑𐑼𐑯𐑩𐑕. “𐑒𐑺 𐑩𐑚𐑬𐑑 𐑥𐑰, 𐑲 𐑥𐑰𐑯.”

“𐑿 𐑕𐑱𐑝𐑛 𐑞𐑧𐑥 𐑓𐑮𐑪𐑥 𐑿-𐑯𐑴-𐑣𐑵,” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. “𐑣𐑬 𐑖𐑫𐑛 𐑞𐑱 𐑯𐑪𐑑 𐑒𐑺?”

·𐑣𐑨𐑮𐑦 𐑤𐑫𐑒𐑑 𐑳𐑐 𐑨𐑑 𐑞 𐑢𐑦𐑗-𐑤𐑱𐑛𐑦'𐑟 𐑕𐑑𐑮𐑦𐑒𐑑 𐑦𐑒𐑕𐑐𐑮𐑧𐑖𐑩𐑯 𐑚𐑦𐑯𐑰𐑔 𐑣𐑻 𐑐𐑶𐑯𐑑𐑩𐑛 𐑣𐑨𐑑, 𐑯 𐑕𐑲𐑛. “𐑲 𐑕𐑩𐑐𐑴𐑟 𐑞𐑺'𐑟 𐑯𐑴 𐑗𐑭𐑯𐑕 𐑞𐑨𐑑 𐑦𐑓 𐑲 𐑕𐑧𐑛 \emph{𐑓𐑳𐑯𐑛𐑩𐑥𐑧𐑯𐑑𐑩𐑤 𐑨𐑑𐑮𐑦𐑚𐑿𐑖𐑩𐑯 𐑧𐑮𐑼} 𐑿'𐑛 𐑣𐑨𐑝 𐑧𐑯𐑦 𐑲𐑛𐑾 𐑢𐑪𐑑 𐑞𐑨𐑑 𐑥𐑧𐑯𐑑.”

“𐑯𐑴,” 𐑕𐑧𐑛 𐑞 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑦𐑯 𐑣𐑻 𐑐𐑮𐑦𐑕𐑲𐑕 ·𐑕𐑒𐑪𐑑𐑦𐑖 𐑨𐑒𐑕𐑧𐑯𐑑, “𐑚𐑳𐑑 𐑐𐑤𐑰𐑟 𐑦𐑒𐑕𐑐𐑤𐑱𐑯, ·𐑥𐑼~·𐑐𐑪𐑑𐑼, 𐑦𐑓 𐑿 𐑢𐑫𐑛 𐑚𐑰 𐑕𐑴 𐑒𐑲𐑯𐑛.”

“𐑢𐑧𐑤…” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑓𐑦𐑜𐑼 𐑬𐑑 𐑣𐑬 𐑑 𐑛𐑦𐑕𐑒𐑮𐑲𐑚 𐑞𐑨𐑑 𐑐𐑼𐑑𐑦𐑒𐑿𐑤𐑼 𐑚𐑦𐑑 𐑝 ·𐑥𐑳𐑜𐑩𐑤 𐑕𐑲𐑩𐑯𐑕. “𐑕𐑩𐑐𐑴𐑟 𐑿 𐑒𐑳𐑥 𐑦𐑯𐑑𐑵 𐑢𐑻𐑒 𐑯 𐑕𐑰 𐑘𐑹 𐑒𐑪𐑤𐑰𐑜 𐑒𐑦𐑒𐑦𐑙 𐑣𐑦𐑟 𐑛𐑧𐑕𐑒. 𐑿 𐑔𐑦𐑙𐑒, '𐑢𐑪𐑑 𐑩𐑯 𐑨𐑙𐑜𐑮𐑦 𐑐𐑻𐑕𐑩𐑯 𐑣𐑰 𐑥𐑳𐑕𐑑 𐑚𐑰'. 𐑘𐑹 𐑒𐑪𐑤𐑰𐑜 𐑦𐑟 𐑔𐑦𐑙𐑒𐑦𐑙 𐑩𐑚𐑬𐑑 𐑣𐑬 𐑕𐑳𐑥𐑢𐑳𐑯 𐑚𐑳𐑥𐑐𐑑 𐑣𐑦𐑥 𐑦𐑯𐑑𐑵 𐑩 𐑢𐑷𐑤 𐑪𐑯 𐑞 𐑢𐑱 𐑑 𐑢𐑻𐑒 𐑯 𐑞𐑧𐑯 𐑖𐑬𐑑𐑩𐑛 𐑨𐑑 𐑣𐑦𐑥. \emph{𐑧𐑯𐑦𐑢𐑳𐑯} 𐑢𐑫𐑛 𐑚𐑰 𐑨𐑙𐑜𐑮𐑦 𐑨𐑑 𐑞𐑨𐑑, 𐑣𐑰 𐑔𐑦𐑙𐑒𐑕. 𐑢𐑧𐑯 𐑢𐑰 𐑤𐑫𐑒 𐑨𐑑 𐑳𐑞𐑼𐑟 𐑢𐑰 𐑕𐑰 𐑐𐑻𐑕𐑩𐑯𐑨𐑤𐑦𐑑𐑦 𐑑𐑮𐑱𐑑𐑕 𐑞𐑨𐑑 𐑦𐑒𐑕𐑐𐑤𐑱𐑯 𐑞𐑺 𐑚𐑦𐑣𐑱𐑝𐑘𐑼, 𐑚𐑳𐑑 𐑢𐑧𐑯 𐑢𐑰 𐑤𐑫𐑒 𐑨𐑑 𐑬𐑼𐑕𐑧𐑤𐑝𐑟 𐑢𐑰 𐑕𐑰 𐑕𐑻𐑒𐑩𐑥𐑕𐑑𐑨𐑯𐑕𐑩𐑟 𐑞𐑨𐑑 𐑦𐑒𐑕𐑐𐑤𐑱𐑯 𐑬𐑼 𐑚𐑦𐑣𐑱𐑝𐑘𐑼. 𐑐𐑰𐑐𐑩𐑤'𐑟 𐑕𐑑𐑹𐑦𐑟 𐑥𐑱𐑒 𐑦𐑯𐑑𐑻𐑯𐑩𐑤 𐑕𐑧𐑯𐑕 𐑑 𐑞𐑧𐑥, 𐑓𐑮𐑪𐑥 𐑞 𐑦𐑯𐑕𐑲𐑛, 𐑚𐑳𐑑 𐑢𐑰 𐑛𐑴𐑯𐑑 𐑕𐑰 𐑐𐑰𐑐𐑩𐑤'𐑟 𐑣𐑦𐑕𐑑𐑼𐑦𐑟 𐑑𐑮𐑱𐑤𐑦𐑙 𐑚𐑦𐑣𐑲𐑯𐑛 𐑞𐑧𐑥 𐑦𐑯 𐑞 𐑺. 𐑢𐑰 𐑴𐑯𐑤𐑦 𐑕𐑰 𐑞𐑧𐑥 𐑦𐑯 𐑢𐑳𐑯 𐑕𐑦𐑗𐑵𐑱𐑖𐑩𐑯, 𐑯 𐑢𐑰 𐑛𐑴𐑯𐑑 𐑕𐑰 𐑢𐑪𐑑 𐑞𐑱 𐑢𐑫𐑛 𐑚𐑰 𐑤𐑲𐑒 𐑦𐑯 𐑩 𐑛𐑦𐑓𐑼𐑩𐑯𐑑 𐑕𐑦𐑗𐑵𐑱𐑖𐑩𐑯. 𐑕𐑴 𐑞 𐑓𐑳𐑯𐑛𐑩𐑥𐑧𐑯𐑑𐑩𐑤 𐑨𐑑𐑮𐑦𐑚𐑿𐑖𐑩𐑯 𐑧𐑮𐑼 𐑦𐑟 𐑞𐑨𐑑 𐑢𐑰 𐑦𐑒𐑕𐑐𐑤𐑱𐑯 𐑚𐑲 𐑐𐑻𐑥𐑩𐑯𐑩𐑯𐑑, 𐑦𐑯𐑛𐑘𐑫𐑼𐑦𐑙 𐑑𐑮𐑱𐑑𐑕 𐑢𐑪𐑑 𐑢𐑫𐑛 𐑚𐑰 𐑚𐑧𐑑𐑼 𐑦𐑒𐑕𐑐𐑤𐑱𐑯𐑛 𐑚𐑲 𐑕𐑻𐑒𐑩𐑥𐑕𐑑𐑨𐑯𐑕 𐑯 𐑒𐑪𐑯𐑑𐑧𐑒𐑕𐑑.” 𐑞𐑺 𐑢𐑻 𐑕𐑳𐑥 𐑧𐑤𐑦𐑜𐑩𐑯𐑑 𐑦𐑒𐑕𐑐𐑧𐑮𐑦𐑥𐑧𐑯𐑑𐑕 𐑢𐑦𐑗 𐑒𐑩𐑯𐑓𐑻𐑥𐑛 𐑞𐑦𐑕, 𐑚𐑳𐑑 ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟𐑩𐑯𐑑 𐑩𐑚𐑬𐑑 𐑑 𐑜𐑴 𐑦𐑯𐑑𐑵 𐑞𐑧𐑥.

𐑞 𐑢𐑦𐑗'𐑩𐑟 𐑲𐑚𐑮𐑬𐑟 𐑛𐑮𐑵 𐑳𐑐 𐑚𐑦𐑯𐑰𐑔 𐑣𐑻 𐑣𐑨𐑑'𐑕 𐑚𐑮𐑦𐑥. “𐑲 𐑔𐑦𐑙𐑒 𐑲 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛…” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛 𐑕𐑤𐑴𐑤𐑦. “𐑚𐑳𐑑 𐑢𐑪𐑑 𐑛𐑳𐑟 𐑞𐑨𐑑 𐑣𐑨𐑓 𐑑 𐑛𐑵 𐑢𐑦𐑞 𐑿?”

·𐑣𐑨𐑮𐑦 𐑒𐑦𐑒𐑑 𐑞 𐑚𐑮𐑦𐑒 𐑢𐑷𐑤 𐑝 𐑞 𐑨𐑤𐑦 𐑣𐑸𐑛 𐑦𐑯𐑳𐑓 𐑑 𐑥𐑱𐑒 𐑣𐑦𐑟 𐑓𐑫𐑑 𐑣𐑻𐑑. “𐑐𐑰𐑐𐑩𐑤 𐑔𐑦𐑙𐑒 𐑞𐑨𐑑 𐑲 𐑕𐑱𐑝𐑛 𐑞𐑧𐑥 𐑓𐑮𐑪𐑥 𐑿-𐑯𐑴-𐑣𐑵 𐑚𐑦𐑒𐑪𐑟 𐑲'𐑥 𐑕𐑳𐑥 𐑒𐑲𐑯𐑛 𐑝 𐑜𐑮𐑱𐑑 𐑢𐑹𐑽 𐑝 𐑞 ·𐑤𐑲𐑑.”

“𐑞 𐑢𐑳𐑯 𐑢𐑦𐑞 𐑐𐑬𐑼 𐑑 𐑝𐑨𐑙𐑒𐑢𐑦𐑖 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛…” 𐑥𐑻𐑥𐑼𐑛 𐑞 𐑢𐑦𐑗, 𐑩 𐑕𐑑𐑮𐑱𐑯𐑡 𐑲𐑮𐑩𐑯𐑦 𐑤𐑧𐑝𐑩𐑯𐑦𐑙 𐑣𐑻 𐑝𐑶𐑕.

“𐑘𐑧𐑕,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑩𐑯𐑶𐑩𐑯𐑕 𐑯 𐑓𐑮𐑳𐑕𐑑𐑮𐑱𐑖𐑩𐑯 𐑢𐑹𐑦𐑙 𐑦𐑯 𐑣𐑦𐑥, “𐑤𐑲𐑒 𐑲 𐑛𐑦𐑕𐑑𐑮𐑶𐑛 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛 𐑚𐑦𐑒𐑪𐑟 𐑲 𐑣𐑨𐑝 𐑕𐑳𐑥 𐑒𐑲𐑯𐑛 𐑝 𐑐𐑻𐑥𐑩𐑯𐑩𐑯𐑑, 𐑦𐑯𐑛𐑘𐑫𐑼𐑦𐑙 𐑛𐑦𐑕𐑑𐑮𐑶-𐑞-·𐑛𐑸𐑒-·𐑤𐑹𐑛 𐑑𐑮𐑱𐑑. 𐑲 𐑢𐑪𐑟 𐑓𐑦𐑓𐑑𐑰𐑯 𐑥𐑳𐑯𐑔𐑕 𐑴𐑤𐑛 𐑨𐑑 𐑞 𐑑𐑲𐑥! 𐑲 𐑛𐑴𐑯𐑑 \emph{𐑯𐑴} 𐑢𐑪𐑑 𐑣𐑨𐑐𐑩𐑯𐑛, 𐑚𐑳𐑑 𐑲 𐑢𐑫𐑛 \emph{𐑕𐑩𐑐𐑴𐑟} 𐑦𐑑 𐑣𐑨𐑛 𐑕𐑳𐑥𐑔𐑦𐑙 𐑑 𐑛𐑵 𐑢𐑦𐑞, 𐑨𐑟 𐑞 𐑕𐑱𐑦𐑙 𐑜𐑴𐑟, 𐑒𐑩𐑯𐑑𐑦𐑯𐑡𐑩𐑯𐑑 𐑦𐑯𐑝𐑲𐑮𐑩𐑯𐑥𐑧𐑯𐑑𐑩𐑤 𐑕𐑻𐑒𐑩𐑥𐑕𐑑𐑨𐑯𐑕𐑩𐑟. 𐑯 𐑕𐑻𐑑𐑩𐑯𐑤𐑦 𐑯𐑳𐑔𐑦𐑙 𐑑 𐑛𐑵 𐑢𐑦𐑞 𐑥𐑲 𐑐𐑻𐑕𐑩𐑯𐑨𐑤𐑦𐑑𐑦. 𐑐𐑰𐑐𐑩𐑤 𐑛𐑴𐑯𐑑 𐑒𐑺 𐑩𐑚𐑬𐑑 \emph{𐑥𐑰}, 𐑞𐑱 𐑸𐑯𐑑 𐑰𐑝𐑩𐑯 𐑐𐑱𐑦𐑙 𐑩𐑑𐑧𐑯𐑖𐑩𐑯 𐑑 \emph{𐑥𐑰}, 𐑞𐑱 𐑢𐑪𐑯𐑑 𐑑 𐑖𐑱𐑒 𐑣𐑨𐑯𐑛𐑟 𐑢𐑦𐑞 𐑩 \emph{𐑚𐑨𐑛 𐑧𐑒𐑕𐑐𐑤𐑩𐑯𐑱𐑖𐑩𐑯}.” ·𐑣𐑨𐑮𐑦 𐑐𐑷𐑟𐑛, 𐑯 𐑤𐑫𐑒𐑑 𐑨𐑑 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. “𐑛𐑵 \emph{𐑿} 𐑯𐑴 𐑢𐑪𐑑 𐑮𐑾𐑤𐑦 𐑣𐑨𐑐𐑩𐑯𐑛?”

“𐑲 \emph{𐑣𐑨𐑝} 𐑓𐑹𐑥𐑛 𐑩𐑯 𐑲𐑛𐑾…” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. “𐑭𐑓𐑑𐑼 𐑥𐑰𐑑𐑦𐑙 𐑿, 𐑞𐑨𐑑 𐑦𐑟.”

“𐑘𐑧𐑕?”

“𐑿 𐑑𐑮𐑲𐑳𐑥𐑓𐑑 𐑴𐑝𐑼 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛 𐑚𐑲 𐑚𐑰𐑦𐑙 𐑥𐑹 𐑷𐑓𐑩𐑤 𐑞𐑨𐑯 \emph{𐑣𐑰} 𐑢𐑪𐑟, 𐑯 𐑕𐑼𐑝𐑲𐑝𐑛 𐑞 ·𐑒𐑦𐑤𐑦𐑙 ·𐑒𐑻𐑕 𐑚𐑲 𐑚𐑰𐑦𐑙 𐑥𐑹 𐑑𐑧𐑮𐑦𐑚𐑩𐑤 𐑞𐑨𐑯 ·𐑛𐑧𐑔.”

“𐑣𐑭. 𐑣𐑭. 𐑣𐑭.” ·𐑣𐑨𐑮𐑦 𐑒𐑦𐑒𐑑 𐑞 𐑢𐑷𐑤 𐑩𐑜𐑱𐑯.

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑗𐑳𐑒𐑩𐑤𐑛. “𐑤𐑧𐑑'𐑕 𐑜𐑧𐑑 𐑿 𐑑 ·𐑥𐑨𐑛𐑩𐑥 ·𐑥𐑨𐑤𐑒𐑦𐑯'𐑟 𐑯𐑧𐑒𐑕𐑑. 𐑲 𐑓𐑽 𐑘𐑹 ·𐑥𐑳𐑜𐑩𐑤 𐑒𐑤𐑴𐑞𐑦𐑙 𐑥𐑱 𐑚𐑰 𐑩𐑑𐑮𐑨𐑒𐑑𐑦𐑙 𐑩𐑑𐑧𐑯𐑖𐑩𐑯.”

𐑞𐑱 𐑮𐑨𐑯 𐑦𐑯𐑑𐑵 𐑑𐑵 𐑥𐑹 𐑢𐑧𐑤-𐑢𐑦𐑖𐑼𐑟 𐑩𐑤𐑪𐑙 𐑞 𐑢𐑱.

·𐑥𐑨𐑛𐑩𐑥 ·𐑥𐑨𐑤𐑒𐑦𐑯'𐑟 ·𐑮𐑴𐑚𐑟 𐑣𐑨𐑛 𐑩 𐑡𐑧𐑯𐑿𐑦𐑯𐑤𐑦 𐑚𐑹𐑦𐑙 𐑖𐑪𐑐 𐑓𐑮𐑳𐑯𐑑, 𐑮𐑧𐑛 𐑹𐑛𐑦𐑯𐑼𐑦 𐑚𐑮𐑦𐑒, 𐑯 𐑜𐑤𐑭𐑕 𐑢𐑦𐑯𐑛𐑴𐑟 𐑖𐑴𐑦𐑙 𐑐𐑤𐑱𐑯 𐑚𐑤𐑨𐑒 𐑮𐑴𐑚𐑟 𐑢𐑦𐑞𐑦𐑯. 𐑯𐑪𐑑 𐑮𐑴𐑚𐑟 𐑞𐑨𐑑 𐑖𐑪𐑯 𐑹 𐑗𐑱𐑯𐑡𐑛 𐑹 𐑕𐑐𐑳𐑯, 𐑹 𐑮𐑱𐑛𐑦𐑱𐑑𐑩𐑛 𐑕𐑑𐑮𐑱𐑯𐑡 𐑮𐑱𐑟 𐑞𐑨𐑑 𐑕𐑰𐑥𐑛 𐑑 𐑜𐑴 𐑮𐑲𐑑 𐑔𐑮𐑵 𐑘𐑹 𐑖𐑻𐑑 𐑯 𐑑𐑦𐑒𐑩𐑤 𐑿. 𐑡𐑳𐑕𐑑 𐑐𐑤𐑱𐑯 𐑚𐑤𐑨𐑒 𐑮𐑴𐑚𐑟, 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑷𐑤 𐑿 𐑒𐑫𐑛 𐑕𐑰 𐑔𐑮𐑵 𐑞 𐑢𐑦𐑯𐑛𐑴. 𐑞 𐑛𐑹 𐑢𐑪𐑟 𐑐𐑮𐑪𐑐𐑑 𐑢𐑲𐑛 𐑴𐑐𐑩𐑯, 𐑨𐑟 𐑦𐑓 𐑑 𐑨𐑛𐑝𐑻𐑑𐑲𐑟 𐑞𐑨𐑑 𐑞𐑺 𐑢𐑻 𐑯𐑴 𐑕𐑰𐑒𐑮𐑩𐑑𐑕 𐑣𐑽 𐑯 𐑯𐑳𐑔𐑦𐑙 𐑑 𐑣𐑲𐑛.

“𐑲'𐑥 𐑜𐑴𐑦𐑙 𐑑 𐑜𐑴 𐑪𐑓 𐑓 𐑩 𐑓𐑿 𐑥𐑦𐑯𐑦𐑑𐑕 𐑢𐑲𐑤 𐑿 𐑜𐑧𐑑 𐑓𐑦𐑑𐑩𐑛 𐑓 𐑘𐑹 𐑮𐑴𐑚𐑟,” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. “𐑢𐑦𐑤 𐑿 𐑚𐑰 𐑷𐑤 𐑮𐑲𐑑 𐑢𐑦𐑞 𐑞𐑨𐑑, ·𐑥𐑼~·𐑐𐑪𐑑𐑼?”

·𐑣𐑨𐑮𐑦 𐑯𐑪𐑛𐑩𐑛. 𐑣𐑰 𐑣𐑱𐑑𐑩𐑛 𐑒𐑤𐑴𐑞𐑟 𐑖𐑪𐑐𐑦𐑙 𐑢𐑦𐑞 𐑩 𐑓𐑲𐑼𐑦 𐑐𐑨𐑖𐑩𐑯 𐑯 𐑒𐑫𐑛𐑩𐑯𐑑 𐑚𐑤𐑱𐑥 𐑞 𐑴𐑤𐑛𐑼 𐑢𐑦𐑗 𐑓 𐑓𐑰𐑤𐑦𐑙 𐑞 𐑕𐑱𐑥 𐑢𐑱.

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑢𐑪𐑯𐑛 𐑒𐑱𐑥 𐑬𐑑 𐑝 𐑣𐑻 𐑕𐑤𐑰𐑝, 𐑑𐑨𐑐𐑑 ·𐑣𐑨𐑮𐑦'𐑟 𐑣𐑧𐑛 𐑤𐑲𐑑𐑤𐑦. “𐑯 𐑨𐑟 𐑿'𐑤 𐑯𐑰𐑛 𐑑 𐑚𐑰 𐑒𐑤𐑽 𐑑 ·𐑥𐑨𐑛𐑩𐑥 ·𐑥𐑨𐑤𐑒𐑦𐑯'𐑟 𐑕𐑧𐑯𐑕𐑩𐑟, 𐑲 𐑨𐑥 𐑮𐑦𐑥𐑵𐑝𐑦𐑙 𐑞 ·𐑪𐑚𐑓𐑩𐑕𐑒𐑱𐑖𐑩𐑯.”

“𐑳…” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. 𐑞𐑨𐑑 𐑛𐑦𐑛 𐑢𐑳𐑮𐑦 𐑣𐑦𐑥 𐑩 𐑤𐑦𐑑𐑩𐑤; 𐑣𐑰 𐑕𐑑𐑦𐑤 𐑢𐑪𐑟𐑩𐑯𐑑 𐑿𐑕𐑑 𐑑 𐑞 '·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼' 𐑔𐑦𐑙.

“𐑲 𐑢𐑧𐑯𐑑 𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 𐑢𐑦𐑞 ·𐑥𐑨𐑛𐑩𐑥 ·𐑥𐑨𐑤𐑒𐑦𐑯,” ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛. “𐑰𐑝𐑩𐑯 𐑞𐑧𐑯, 𐑖𐑰 𐑢𐑪𐑟 𐑢𐑳𐑯 𐑝 𐑞 𐑥𐑴𐑕𐑑 \emph{𐑒𐑩𐑥𐑐𐑴𐑟𐑛} 𐑐𐑰𐑐𐑩𐑤 𐑲 𐑯𐑿. 𐑖𐑰 𐑢𐑫𐑛𐑩𐑯𐑑 𐑑𐑻𐑯 𐑩 𐑣𐑺 𐑦𐑓 𐑿-𐑯𐑴-𐑣𐑵 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑢𐑷𐑒𐑑 𐑦𐑯𐑑𐑵 𐑣𐑻 𐑖𐑪𐑐.” ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑝𐑶𐑕 𐑢𐑪𐑟 𐑮𐑧𐑥𐑦𐑯𐑦𐑕𐑩𐑯𐑑, 𐑯 𐑝𐑧𐑮𐑦 𐑩𐑐𐑮𐑵𐑝𐑦𐑙. “·𐑥𐑨𐑛𐑩𐑥 ·𐑥𐑨𐑤𐑒𐑦𐑯 𐑢𐑴𐑯𐑑 𐑚𐑪𐑞𐑼 𐑿, 𐑯 𐑖𐑰 𐑢𐑴𐑯𐑑 𐑤𐑧𐑑 𐑧𐑯𐑦𐑢𐑳𐑯 𐑧𐑤𐑕 𐑚𐑪𐑞𐑼 𐑿.”

“𐑢𐑺 \emph{𐑸} 𐑿 𐑜𐑴𐑦𐑙?” ·𐑣𐑨𐑮𐑦 𐑦𐑯𐑒𐑢𐑲𐑼𐑛. “𐑡𐑳𐑕𐑑 𐑦𐑯 𐑒𐑱𐑕, 𐑿 𐑯𐑴, 𐑕𐑳𐑥𐑔𐑦𐑙 \emph{𐑛𐑳𐑟} 𐑣𐑨𐑐𐑩𐑯.”

·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑜𐑱𐑝 ·𐑣𐑨𐑮𐑦 𐑩 𐑣𐑸𐑛 𐑤𐑫𐑒. “𐑲 𐑨𐑥 𐑜𐑴𐑦𐑙 \emph{𐑞𐑺},” 𐑖𐑰 𐑕𐑧𐑛, 𐑐𐑶𐑯𐑑𐑦𐑙 𐑨𐑑 𐑩 𐑚𐑦𐑤𐑛𐑦𐑙 𐑩𐑒𐑮𐑪𐑕 𐑞 𐑕𐑑𐑮𐑰𐑑 𐑢𐑦𐑗 𐑖𐑴𐑛 𐑞 𐑕𐑲𐑯 𐑝 𐑩 𐑢𐑫𐑛𐑩𐑯 𐑒𐑧𐑜, “𐑯 𐑚𐑲𐑦𐑙 𐑩 𐑛𐑮𐑦𐑙𐑒, 𐑢𐑦𐑗 𐑲 𐑛𐑧𐑕𐑐𐑼𐑩𐑑𐑤𐑦 𐑯𐑰𐑛. \emph{𐑿} 𐑸 𐑑 𐑜𐑧𐑑 𐑓𐑦𐑑𐑩𐑛 𐑓 𐑘𐑹 𐑮𐑴𐑚𐑟, \emph{𐑯𐑳𐑔𐑦𐑙 𐑧𐑤𐑕}. 𐑲 𐑢𐑦𐑤 𐑒𐑳𐑥 𐑚𐑨𐑒 𐑑 𐑗𐑧𐑒 𐑳𐑐 𐑪𐑯 𐑿 \emph{𐑖𐑹𐑑𐑤𐑦}, 𐑯 𐑲 \emph{𐑦𐑒𐑕𐑐𐑧𐑒𐑑} 𐑑 𐑓𐑲𐑯𐑛 ·𐑥𐑨𐑛𐑩𐑥 ·𐑥𐑨𐑤𐑒𐑦𐑯'𐑟 𐑖𐑪𐑐 𐑕𐑑𐑦𐑤 𐑕𐑑𐑨𐑯𐑛𐑦𐑙 𐑯 𐑯𐑪𐑑 𐑦𐑯 𐑧𐑯𐑦 𐑢𐑱 𐑪𐑯 𐑓𐑲𐑼.”

·𐑥𐑨𐑛𐑩𐑥 ·𐑥𐑨𐑤𐑒𐑦𐑯 𐑢𐑪𐑟 𐑩 𐑚𐑳𐑕𐑩𐑤𐑦𐑙 𐑴𐑤𐑛 𐑢𐑫𐑥𐑩𐑯 𐑣𐑵 𐑛𐑦𐑛𐑩𐑯𐑑 𐑕𐑱 𐑩 𐑢𐑻𐑛 𐑩𐑚𐑬𐑑 ·𐑣𐑨𐑮𐑦 𐑢𐑧𐑯 𐑖𐑰 𐑕𐑷 𐑞 𐑕𐑒𐑸 𐑪𐑯 𐑣𐑦𐑟 𐑓𐑪𐑮𐑦𐑛, 𐑯 𐑖𐑰 𐑖𐑪𐑑 𐑩 𐑖𐑸𐑐 𐑤𐑫𐑒 𐑨𐑑 𐑩𐑯 𐑩𐑕𐑦𐑕𐑑𐑩𐑯𐑑 𐑢𐑧𐑯 𐑞𐑨𐑑 𐑜𐑻𐑤 𐑕𐑰𐑥𐑛 𐑩𐑚𐑬𐑑 𐑑 𐑕𐑱 𐑕𐑳𐑥𐑔𐑦𐑙. ·𐑥𐑨𐑛𐑩𐑥 ·𐑥𐑨𐑤𐑒𐑦𐑯 𐑜𐑪𐑑 𐑬𐑑 𐑩 𐑕𐑧𐑑 𐑝 𐑨𐑯𐑦𐑥𐑱𐑑𐑩𐑛, 𐑮𐑲𐑞𐑦𐑙 𐑚𐑦𐑑𐑕 𐑝 𐑒𐑤𐑪𐑔 𐑞𐑨𐑑 𐑕𐑰𐑥𐑛 𐑑 𐑕𐑻𐑝 𐑨𐑟 𐑑𐑱𐑐 𐑥𐑧𐑠𐑼𐑟 𐑯 𐑕𐑧𐑑 𐑑 𐑢𐑻𐑒 𐑦𐑜𐑟𐑨𐑥𐑦𐑯𐑦𐑙 𐑞 𐑥𐑰𐑛𐑾𐑥 𐑝 𐑣𐑻 𐑸𐑑.

𐑯𐑧𐑒𐑕𐑑 𐑑 ·𐑣𐑨𐑮𐑦, 𐑩 𐑐𐑱𐑤 𐑘𐑳𐑙 𐑚𐑶 𐑢𐑦𐑞 𐑩 𐑐𐑶𐑯𐑑𐑩𐑛 𐑓𐑱𐑕 𐑯 \emph{𐑷𐑕𐑩𐑥𐑒𐑵𐑤} 𐑚𐑤𐑪𐑯𐑛-𐑢𐑲𐑑 𐑣𐑺 𐑕𐑰𐑥𐑛 𐑑 𐑚𐑰 𐑜𐑴𐑦𐑙 𐑔𐑮𐑵 𐑞 𐑓𐑲𐑯𐑩𐑤 𐑕𐑑𐑱𐑡𐑩𐑟 𐑝 𐑩 𐑕𐑦𐑥𐑦𐑤𐑼 𐑐𐑮𐑴𐑕𐑧𐑕. 𐑢𐑳𐑯 𐑝 ·𐑥𐑨𐑤𐑒𐑦𐑯'𐑟 𐑑𐑵 𐑩𐑕𐑦𐑕𐑑𐑩𐑯𐑑𐑕 𐑢𐑪𐑟 𐑦𐑜𐑟𐑨𐑥𐑦𐑯𐑦𐑙 𐑞 𐑢𐑲𐑑-𐑣𐑺𐑛 𐑚𐑶 𐑯 𐑞 𐑗𐑧𐑒𐑼𐑚𐑹𐑛-𐑜𐑮𐑦𐑛𐑩𐑛 𐑮𐑴𐑚 𐑣𐑰 𐑢𐑪𐑟 𐑢𐑺𐑦𐑙; 𐑩𐑒𐑱𐑠𐑩𐑯𐑩𐑤𐑦 𐑖𐑰 𐑢𐑫𐑛 𐑑𐑨𐑐 𐑩 𐑒𐑹𐑯𐑼 𐑝 𐑞 𐑮𐑴𐑚 𐑢𐑦𐑞 𐑣𐑻 𐑢𐑪𐑯𐑛, 𐑯 𐑞 𐑮𐑴𐑚 𐑢𐑫𐑛 𐑤𐑵𐑕𐑩𐑯 𐑹 𐑑𐑲𐑑𐑩𐑯.

“𐑣𐑧𐑤𐑴,” 𐑕𐑧𐑛 𐑞 𐑚𐑶. “·𐑣𐑪𐑜𐑢𐑹𐑑𐑕, 𐑑𐑵?”

·𐑣𐑨𐑮𐑦 𐑒𐑫𐑛 𐑐𐑮𐑦𐑛𐑦𐑒𐑑 𐑢𐑺 𐑞𐑦𐑕 𐑒𐑪𐑯𐑝𐑼𐑕𐑱𐑖𐑩𐑯 𐑢𐑪𐑟 𐑩𐑚𐑬𐑑 𐑑 𐑜𐑴, 𐑯 𐑣𐑰 𐑛𐑦𐑕𐑲𐑛𐑩𐑛 𐑦𐑯 𐑩 𐑕𐑐𐑤𐑦𐑑 𐑕𐑱𐑒𐑪𐑯𐑛 𐑝 𐑓𐑮𐑳𐑕𐑑𐑮𐑱𐑖𐑩𐑯 𐑞𐑨𐑑 𐑦𐑯𐑳𐑓 𐑢𐑪𐑟 𐑦𐑯𐑳𐑓.

“𐑜𐑫𐑛 𐑣𐑧𐑝𐑩𐑯𐑟,” 𐑢𐑦𐑕𐑐𐑼𐑛 ·𐑣𐑨𐑮𐑦, “𐑦𐑑 𐑒𐑫𐑛𐑩𐑯𐑑 𐑚𐑰.” 𐑣𐑰 𐑤𐑧𐑑 𐑣𐑦𐑟 𐑲𐑟 𐑢𐑲𐑛𐑩𐑯. “𐑘𐑹…𐑯𐑱𐑥, 𐑕𐑻?”

“·𐑛𐑮𐑱𐑒𐑴 ·𐑥𐑨𐑤𐑓𐑶,” 𐑕𐑧𐑛 ·𐑛𐑮𐑱𐑒𐑴 ·𐑥𐑨𐑤𐑓𐑶, 𐑤𐑫𐑒𐑦𐑙 𐑕𐑤𐑲𐑑𐑤𐑦 𐑐𐑳𐑟𐑩𐑤𐑛.

“𐑦𐑑 \emph{𐑦𐑟} 𐑿! ·𐑛𐑮𐑱𐑒𐑴 ·𐑥𐑨𐑤𐑓𐑶. 𐑲—𐑲 𐑯𐑧𐑝𐑼 𐑔𐑷𐑑 𐑲'𐑛 𐑚𐑰 𐑕𐑴 𐑪𐑯𐑼𐑛, 𐑕𐑻.” ·𐑣𐑨𐑮𐑦 𐑢𐑦𐑖𐑑 𐑣𐑰 𐑒𐑫𐑛 𐑥𐑱𐑒 𐑑𐑺@𐑑𐑽𐑟 𐑒𐑳𐑥 𐑬𐑑 𐑝 𐑣𐑦𐑟 𐑲𐑟. 𐑞 𐑳𐑞𐑼𐑟 𐑿𐑠𐑵𐑩𐑤𐑦 𐑕𐑑𐑸𐑑𐑩𐑛 𐑒𐑮𐑲𐑦𐑙 𐑨𐑑 𐑼𐑬𐑯𐑛 𐑞𐑦𐑕 𐑐𐑶𐑯𐑑.

“𐑴,” 𐑕𐑧𐑛 ·𐑛𐑮𐑱𐑒𐑴, 𐑕𐑬𐑯𐑛𐑦𐑙 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑒𐑩𐑯𐑓𐑿𐑟𐑛. 𐑞𐑧𐑯 𐑣𐑦𐑟 𐑤𐑦𐑐𐑕 𐑕𐑑𐑮𐑧𐑗𐑑 𐑦𐑯 𐑩 𐑕𐑥𐑳𐑜 𐑕𐑥𐑲𐑤. “𐑦𐑑'𐑕 𐑜𐑫𐑛 𐑑 𐑥𐑰𐑑 𐑕𐑳𐑥𐑢𐑳𐑯 𐑣𐑵 𐑯𐑴𐑟 𐑣𐑦𐑟 𐑐𐑤𐑱𐑕.”

𐑢𐑳𐑯 𐑝 𐑞 𐑩𐑕𐑦𐑕𐑑𐑩𐑯𐑑𐑕, 𐑞 𐑢𐑳𐑯 𐑣𐑵'𐑛 𐑕𐑰𐑥𐑛 𐑑 𐑮𐑧𐑒𐑩𐑜𐑯𐑲𐑟 ·𐑣𐑨𐑮𐑦, 𐑥𐑱𐑛 𐑩 𐑥𐑳𐑓𐑩𐑤𐑛 𐑗𐑴𐑒𐑦𐑙 𐑕𐑬𐑯𐑛.

·𐑣𐑨𐑮𐑦 𐑚𐑻𐑚𐑩𐑤𐑛 𐑪𐑯. “𐑲'𐑥 𐑛𐑦𐑤𐑲𐑑𐑩𐑛 𐑑 𐑥𐑰𐑑 𐑿, ·𐑥𐑼~·𐑥𐑨𐑤𐑓𐑶. 𐑡𐑳𐑕𐑑 𐑳𐑯𐑳𐑑𐑼𐑩𐑚𐑤𐑦 𐑛𐑦𐑤𐑲𐑑𐑩𐑛. 𐑯 𐑑 𐑚𐑰 𐑩𐑑𐑧𐑯𐑛𐑦𐑙 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 𐑦𐑯 𐑘𐑹 𐑝𐑧𐑮𐑦 𐑘𐑽! 𐑦𐑑 𐑥𐑱𐑒𐑕 𐑥𐑲 𐑣𐑸𐑑 𐑕𐑢𐑵𐑯.”

·𐑵𐑐𐑕. 𐑞𐑨𐑑 𐑤𐑭𐑕𐑑 𐑐𐑸𐑑 𐑥𐑲𐑑 𐑣𐑨𐑝 𐑕𐑬𐑯𐑛𐑩𐑛 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑪𐑛, 𐑤𐑲𐑒 𐑣𐑰 𐑢𐑪𐑟 𐑓𐑤𐑻𐑑𐑦𐑙 𐑢𐑦𐑞 ·𐑛𐑮𐑱𐑒𐑴 𐑹 𐑕𐑳𐑥𐑔𐑦𐑙.

“𐑯 \emph{𐑲} 𐑨𐑥 𐑐𐑤𐑰𐑟𐑛 𐑑 𐑤𐑻𐑯 𐑞𐑨𐑑 𐑲 𐑖𐑨𐑤 𐑚𐑰 𐑑𐑮𐑰𐑑𐑩𐑛 𐑢𐑦𐑞 𐑞 𐑮𐑦𐑕𐑐𐑧𐑒𐑑 𐑛𐑿 𐑑 𐑞 𐑓𐑨𐑥𐑤𐑦 𐑝 ·𐑥𐑨𐑤𐑓𐑶,” 𐑞 𐑳𐑞𐑼 𐑚𐑶 𐑤𐑪𐑚𐑛 𐑚𐑨𐑒, 𐑩𐑒𐑳𐑥𐑐𐑩𐑯𐑦𐑛 𐑚𐑲 𐑩 𐑕𐑥𐑲𐑤 𐑕𐑳𐑗 𐑨𐑟 𐑞 𐑣𐑲𐑩𐑕𐑑 𐑝 𐑒𐑦𐑙𐑟 𐑥𐑲𐑑 𐑚𐑦𐑕𐑑𐑴 𐑩𐑐𐑪𐑯 𐑞 𐑤𐑰𐑕𐑑 𐑝 𐑣𐑦𐑟 𐑕𐑳𐑚𐑡𐑧𐑒𐑑𐑕, 𐑦𐑓 𐑞𐑨𐑑 𐑕𐑳𐑚𐑡𐑧𐑒𐑑 𐑢𐑻 𐑪𐑯𐑩𐑕𐑑, 𐑞𐑴 𐑐𐑫𐑼.

𐑱…·𐑛𐑨𐑥, ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑣𐑨𐑝𐑦𐑙 𐑑𐑮𐑳𐑚𐑩𐑤 𐑔𐑦𐑙𐑒𐑦𐑙 𐑳𐑐 𐑣𐑦𐑟 𐑯𐑧𐑒𐑕𐑑 𐑤𐑲𐑯. 𐑢𐑧𐑤, 𐑧𐑝𐑮𐑦𐑢𐑳𐑯 \emph{𐑛𐑦𐑛} 𐑢𐑪𐑯𐑑 𐑑 𐑖𐑱𐑒 𐑞 𐑣𐑨𐑯𐑛 𐑝 ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼, 𐑕𐑴—“𐑢𐑧𐑯 𐑥𐑲 𐑒𐑤𐑴𐑞𐑟 𐑸 𐑓𐑦𐑑𐑩𐑛, 𐑕𐑻, 𐑥𐑲𐑑 𐑿 𐑛𐑱𐑯 𐑑 𐑖𐑱𐑒 𐑥𐑲 𐑣𐑨𐑯𐑛? 𐑲 𐑖𐑫𐑛 𐑢𐑦𐑖 𐑯𐑳𐑔𐑦𐑙 𐑥𐑹 𐑑 𐑐𐑫𐑑 𐑞 𐑒𐑨𐑐𐑼 𐑩𐑐𐑪𐑯 𐑞𐑦𐑕 𐑛𐑱, 𐑯𐑱, 𐑞𐑦𐑕 𐑥𐑳𐑯𐑔, 𐑦𐑯𐑛𐑰𐑛, 𐑥𐑲 𐑣𐑴𐑤 𐑤𐑲𐑓𐑑𐑲𐑥.”

𐑞 𐑢𐑲𐑑-𐑚𐑤𐑪𐑯𐑛-𐑣𐑺𐑛 𐑚𐑶 𐑜𐑤𐑺𐑛 𐑦𐑯 𐑮𐑦𐑑𐑻𐑯. “𐑯 𐑢𐑪𐑑 𐑣𐑨𐑝 \emph{𐑿} 𐑛𐑳𐑯 𐑓 𐑞 ·𐑥𐑨𐑤𐑓𐑶𐑟 𐑞𐑨𐑑 𐑦𐑯𐑑𐑲𐑑𐑩𐑤𐑟 𐑿 𐑑 𐑕𐑳𐑗 𐑩 𐑓𐑱𐑝𐑼?”

\emph{𐑴, 𐑲 𐑨𐑥 𐑕𐑴 𐑑𐑴𐑑𐑩𐑤𐑦 𐑑𐑮𐑲𐑦𐑙 𐑞𐑦𐑕 𐑮𐑵𐑑𐑰𐑯 𐑪𐑯 𐑞 𐑯𐑧𐑒𐑕𐑑 𐑐𐑻𐑕𐑩𐑯 𐑣𐑵 𐑢𐑪𐑯𐑑𐑕 𐑑 𐑖𐑱𐑒 𐑥𐑲 𐑣𐑨𐑯𐑛.} ·𐑣𐑨𐑮𐑦 𐑚𐑬𐑛@𐑚𐑴𐑛 𐑣𐑦𐑟 𐑣𐑧𐑛. “𐑯𐑴, 𐑯𐑴, 𐑕𐑻, 𐑲 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛. 𐑲'𐑥 𐑕𐑪𐑮𐑦 𐑓 𐑭𐑕𐑒𐑦𐑙. 𐑲 𐑖𐑫𐑛 𐑚𐑰 𐑪𐑯𐑼𐑛 𐑑 𐑒𐑤𐑰𐑯 𐑘𐑹 𐑚𐑵𐑑𐑕, 𐑮𐑭𐑞𐑼.”

“𐑦𐑯𐑛𐑰𐑛,” 𐑕𐑯𐑨𐑐𐑑 𐑞 𐑳𐑞𐑼 𐑚𐑶. 𐑣𐑦𐑟 𐑕𐑑𐑻𐑯 𐑓𐑱𐑕 𐑤𐑲𐑑𐑩𐑯𐑛 𐑕𐑳𐑥𐑢𐑪𐑑. “𐑑𐑧𐑤 𐑥𐑰, 𐑢𐑪𐑑 ·𐑣𐑬𐑕 𐑛𐑵 𐑿 𐑔𐑦𐑙𐑒 𐑿 𐑥𐑲𐑑 𐑚𐑰 𐑕𐑹𐑑𐑩𐑛 𐑦𐑯𐑑𐑵? 𐑲'𐑥 𐑚𐑬𐑯𐑛 𐑓 ·𐑕𐑤𐑲𐑔𐑼𐑦𐑯 ·𐑣𐑬𐑕, 𐑝 𐑒𐑹𐑕, 𐑤𐑲𐑒 𐑥𐑲 𐑓𐑭𐑞𐑼 ·𐑤𐑵𐑕𐑾𐑕 𐑚𐑦𐑓𐑹 𐑥𐑰. 𐑯 𐑓 𐑿, 𐑲'𐑛 𐑜𐑧𐑕 ·𐑣𐑬𐑕 ·𐑣𐑳𐑓𐑩𐑤𐑐𐑳𐑓, 𐑹 𐑐𐑪𐑕𐑩𐑚𐑤𐑦 ·𐑣𐑬𐑕 ·𐑧𐑤𐑓.”

·𐑣𐑨𐑮𐑦 𐑜𐑮𐑦𐑯𐑛 𐑖𐑰𐑐𐑦𐑖𐑤𐑦. “·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑟 𐑞𐑨𐑑 𐑲'𐑥 𐑞 𐑥𐑴𐑕𐑑 ·𐑮𐑱𐑝𐑩𐑯𐑒𐑤𐑷 𐑐𐑻𐑕𐑩𐑯 𐑖𐑰'𐑟 𐑧𐑝𐑼 𐑕𐑰𐑯 𐑹 𐑣𐑻𐑛 𐑑𐑧𐑤 𐑝 𐑦𐑯 𐑤𐑧𐑡𐑩𐑯𐑛, 𐑕𐑴 𐑥𐑳𐑗 𐑕𐑴 𐑞𐑨𐑑 ·𐑮𐑴𐑢𐑰𐑯𐑩 𐑣𐑻𐑕𐑧𐑤𐑓 𐑢𐑫𐑛 𐑑𐑧𐑤 𐑥𐑰 𐑑 𐑜𐑧𐑑 𐑬𐑑 𐑥𐑹, 𐑢𐑪𐑑𐑧𐑝𐑼 \emph{𐑞𐑨𐑑} 𐑥𐑰𐑯𐑟, 𐑯 𐑞𐑨𐑑 𐑲'𐑤 𐑳𐑯𐑛𐑬𐑑𐑩𐑛𐑤𐑦 𐑧𐑯𐑛 𐑳𐑐 𐑦𐑯 ·𐑮𐑱𐑝𐑩𐑯𐑒𐑤𐑷 ·𐑣𐑬𐑕 𐑦𐑓 𐑞 𐑣𐑨𐑑 𐑦𐑟𐑩𐑯𐑑 𐑕𐑒𐑮𐑰𐑥𐑦𐑙 𐑑𐑵 𐑤𐑬𐑛𐑤𐑦 𐑓 𐑞 𐑮𐑧𐑕𐑑 𐑝 𐑳𐑕 𐑑 𐑥𐑱𐑒 𐑬𐑑 𐑧𐑯𐑦 𐑢𐑻𐑛𐑟, 𐑧𐑯𐑛 𐑒𐑢𐑴𐑑.”

“𐑢𐑬,” 𐑕𐑧𐑛 ·𐑛𐑮𐑱𐑒𐑴 ·𐑥𐑨𐑤𐑓𐑶, 𐑕𐑬𐑯𐑛𐑦𐑙 𐑕𐑤𐑲𐑑𐑤𐑦 𐑦𐑥𐑐𐑮𐑧𐑕𐑑. 𐑞 𐑚𐑶 𐑜𐑱𐑝 𐑩 𐑕𐑹𐑑 𐑝 𐑢𐑦𐑕𐑑𐑓𐑩𐑤 𐑕𐑲. “𐑘𐑹 𐑓𐑤𐑨𐑑𐑼𐑦 𐑢𐑪𐑟 𐑜𐑮𐑱𐑑, 𐑹 𐑲 𐑔𐑷𐑑 𐑕𐑴, 𐑧𐑯𐑦𐑢𐑱—𐑿'𐑛 𐑛𐑵 𐑢𐑧𐑤 𐑦𐑯 ·𐑕𐑤𐑲𐑔𐑼𐑦𐑯 ·𐑣𐑬𐑕, 𐑑𐑵. 𐑿𐑠𐑵𐑩𐑤𐑦 𐑦𐑑'𐑕 𐑴𐑯𐑤𐑦 𐑥𐑲 𐑓𐑭𐑞𐑼 𐑣𐑵 𐑜𐑧𐑑𐑕 𐑞𐑨𐑑 𐑕𐑹𐑑 𐑝 𐑜𐑮𐑪𐑝𐑩𐑤𐑦𐑙. 𐑲'𐑥 \emph{𐑣𐑴𐑐𐑦𐑙} 𐑞 𐑳𐑞𐑼 ·𐑕𐑤𐑲𐑔𐑼𐑦𐑯𐑟 𐑢𐑦𐑤 𐑕𐑳𐑒 𐑳𐑐 𐑑 𐑥𐑰 𐑯𐑬 𐑲'𐑥 𐑨𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕…𐑲 𐑜𐑧𐑕 𐑞𐑦𐑕 𐑦𐑟 𐑩 𐑜𐑫𐑛 𐑕𐑲𐑯, 𐑞𐑧𐑯.”

·𐑣𐑨𐑮𐑦 𐑒𐑪𐑓𐑑. “𐑨𐑒𐑗𐑵𐑩𐑤𐑦, 𐑕𐑪𐑮𐑦, 𐑲'𐑝 𐑜𐑪𐑑 𐑯𐑴 𐑲𐑛𐑾 𐑣𐑵 𐑿 𐑸 𐑮𐑾𐑤𐑦.”

“\emph{𐑴 𐑒𐑳𐑥 𐑪𐑯!}” 𐑞 𐑚𐑶 𐑕𐑧𐑛 𐑢𐑦𐑞 𐑓𐑽𐑕 𐑛𐑦𐑕𐑩𐑐𐑶𐑯𐑑𐑥𐑩𐑯𐑑. “𐑢𐑲'𐑛 𐑿 𐑜𐑴 𐑯 𐑛𐑵 𐑞𐑨𐑑, 𐑞𐑧𐑯?” ·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑲𐑟 𐑢𐑲𐑛𐑩𐑯𐑛 𐑢𐑦𐑞 𐑕𐑳𐑛𐑩𐑯 𐑕𐑩𐑕𐑐𐑦𐑖𐑩𐑯. “𐑯 𐑣𐑬 𐑛𐑵 𐑿 \emph{𐑯𐑪𐑑} 𐑯𐑴 𐑩𐑚𐑬𐑑 𐑞 ·𐑥𐑨𐑤𐑓𐑶𐑟? 𐑯 𐑢𐑪𐑑 𐑸 𐑞𐑴𐑟 \emph{𐑒𐑤𐑴𐑞𐑟} 𐑿'𐑼 𐑢𐑺𐑦𐑙? 𐑸 𐑘𐑹 𐑐𐑺𐑩𐑯𐑑𐑕 \emph{·𐑥𐑳𐑜𐑩𐑤𐑟?}”

“𐑑𐑵 𐑝 𐑥𐑲 𐑐𐑺𐑩𐑯𐑑𐑕 𐑸 𐑛𐑧𐑛,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. 𐑣𐑦𐑟 𐑣𐑸𐑑 𐑑𐑢𐑦𐑯𐑡𐑛. 𐑢𐑧𐑯 𐑣𐑰 𐑐𐑫𐑑 𐑦𐑑 𐑞𐑨𐑑 𐑢𐑱—“𐑥𐑲 𐑳𐑞𐑼 𐑑𐑵 𐑐𐑺𐑩𐑯𐑑𐑕 𐑸 ·𐑥𐑳𐑜𐑩𐑤𐑟, 𐑯 𐑞𐑱'𐑼 𐑞 𐑢𐑳𐑯𐑟 𐑞𐑨𐑑 𐑮𐑱𐑟𐑛 𐑥𐑰.”

“\emph{𐑢𐑪𐑑?}” 𐑕𐑧𐑛 ·𐑛𐑮𐑱𐑒𐑴. “𐑣𐑵 \emph{𐑸} 𐑿?”

“·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼, 𐑐𐑤𐑰𐑟𐑛 𐑑 𐑥𐑰𐑑 𐑿.”

“\emph{·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼?}” 𐑜𐑭𐑕𐑐𐑑 ·𐑛𐑮𐑱𐑒𐑴. “\emph{𐑞} ·𐑣𐑨𐑮𐑦—” 𐑯 𐑞 𐑚𐑶 𐑒𐑳𐑑 𐑪𐑓 𐑩𐑚𐑮𐑳𐑐𐑑𐑤𐑦.

𐑞𐑺 𐑢𐑪𐑟 𐑩 𐑚𐑮𐑰𐑓 𐑕𐑲𐑤𐑩𐑯𐑕.

𐑞𐑧𐑯, 𐑢𐑦𐑞 𐑚𐑮𐑲𐑑 𐑦𐑯𐑔𐑿𐑟𐑦𐑨𐑟𐑩𐑥, “·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼? \emph{𐑞} ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼? 𐑜𐑪𐑖, 𐑲'𐑝 𐑷𐑤𐑢𐑱𐑟 𐑢𐑪𐑯𐑑𐑩𐑛 𐑑 𐑥𐑰𐑑 𐑿!”

·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑩𐑑𐑧𐑯𐑛𐑩𐑯𐑑 𐑦𐑥𐑦𐑑𐑩𐑛 𐑩 𐑕𐑬𐑯𐑛 𐑤𐑲𐑒 𐑖𐑰 𐑢𐑪𐑟 𐑕𐑑𐑮𐑨𐑙𐑜𐑩𐑤𐑦𐑙 𐑚𐑳𐑑 𐑒𐑧𐑐𐑑 𐑪𐑯 𐑢𐑦𐑞 𐑣𐑻 𐑢𐑻𐑒, 𐑤𐑦𐑓𐑑𐑦𐑙 ·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑸𐑥𐑟 𐑑 𐑒𐑺𐑓𐑩𐑤𐑦 𐑮𐑦𐑥𐑵𐑝 𐑞 𐑗𐑧𐑒𐑼𐑛 𐑮𐑴𐑚.

“𐑖𐑳𐑑 𐑳𐑐,” ·𐑣𐑨𐑮𐑦 𐑕𐑩𐑡𐑧𐑕𐑑𐑩𐑛.

“𐑒𐑨𐑯 𐑲 𐑣𐑨𐑝 𐑘𐑹 𐑷𐑑𐑩𐑜𐑮𐑭𐑓? 𐑯𐑴, 𐑢𐑱𐑑, 𐑲 𐑢𐑪𐑯𐑑 𐑩 𐑐𐑦𐑒𐑗𐑼 𐑢𐑦𐑞 𐑿 𐑓𐑻𐑕𐑑!”

“𐑖𐑳𐑑\emph{𐑳𐑐}𐑖𐑳𐑑\emph{𐑳𐑐}𐑖𐑳𐑑\emph{𐑳𐑐.}”

“𐑲'𐑥 𐑡𐑳𐑕𐑑 𐑕𐑴 \emph{𐑛𐑦𐑤𐑲𐑑𐑩𐑛} 𐑑 𐑥𐑰𐑑 𐑿!”

“𐑚𐑻𐑕𐑑 𐑦𐑯𐑑𐑵 𐑓𐑤𐑱𐑥𐑟 𐑯 𐑛𐑲.”

“𐑚𐑳𐑑 𐑿'𐑼 ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼, 𐑞 𐑜𐑤𐑹𐑾𐑕 𐑕𐑱𐑝𐑘𐑼 𐑝 𐑞 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑢𐑻𐑤𐑛! 𐑧𐑝𐑮𐑦𐑢𐑳𐑯'𐑟 𐑣𐑽𐑴, ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼! 𐑲'𐑝 𐑷𐑤𐑢𐑱𐑟 𐑢𐑪𐑯𐑑𐑩𐑛 𐑑 𐑚𐑰 𐑡𐑳𐑕𐑑 𐑤𐑲𐑒 𐑿 𐑢𐑧𐑯 𐑲 𐑜𐑮𐑴 𐑳𐑐 𐑕𐑴 𐑲 𐑒𐑨𐑯—”

·𐑛𐑮𐑱𐑒𐑴 𐑒𐑳𐑑 𐑪𐑓 𐑞 𐑢𐑻𐑛𐑟 𐑦𐑯 𐑥𐑦𐑛-𐑕𐑧𐑯𐑑𐑩𐑯𐑕, 𐑣𐑦𐑟 𐑓𐑱𐑕 𐑓𐑮𐑰𐑟𐑦𐑙 𐑦𐑯 𐑨𐑚𐑕𐑩𐑤𐑵𐑑 𐑣𐑪𐑮𐑼.

𐑑𐑷𐑤, 𐑢𐑲𐑑-𐑣𐑺𐑛, 𐑒𐑴𐑤𐑛𐑤𐑦 𐑧𐑤𐑦𐑜𐑩𐑯𐑑 𐑦𐑯 𐑚𐑤𐑨𐑒 𐑮𐑴𐑚𐑟 𐑝 𐑞 𐑓𐑲𐑯𐑩𐑕𐑑 𐑒𐑢𐑪𐑤𐑦𐑑𐑦. 𐑢𐑳𐑯 𐑣𐑨𐑯𐑛 𐑜𐑮𐑦𐑐𐑦𐑙 𐑩 𐑕𐑦𐑤𐑝𐑼-𐑣𐑨𐑯𐑛𐑩𐑤𐑛 𐑒𐑱𐑯 𐑢𐑦𐑗 𐑑𐑫𐑒 𐑪𐑯 𐑞 𐑒𐑨𐑮𐑩𐑒𐑑𐑼 𐑝 𐑩 𐑛𐑧𐑛𐑤𐑦 𐑢𐑧𐑐𐑩𐑯 𐑡𐑳𐑕𐑑 𐑚𐑲 𐑚𐑰𐑦𐑙 𐑦𐑯 𐑞𐑨𐑑 𐑣𐑨𐑯𐑛. 𐑣𐑦𐑟 𐑲𐑟 𐑮𐑦𐑜𐑸𐑛𐑩𐑛 𐑞 𐑮𐑵𐑥 𐑢𐑦𐑞 𐑞 𐑛𐑦𐑕𐑐𐑨𐑖𐑩𐑯𐑩𐑑 𐑒𐑢𐑪𐑤𐑦𐑑𐑦 𐑝 𐑩𐑯 𐑧𐑒𐑕𐑦𐑒𐑿𐑖𐑩𐑯𐑼, 𐑩 𐑥𐑨𐑯 𐑑 𐑣𐑵𐑥 𐑒𐑦𐑤𐑦𐑙 𐑢𐑪𐑟 𐑯𐑪𐑑 𐑐𐑱𐑯𐑓𐑩𐑤, 𐑹 𐑰𐑝𐑩𐑯 𐑛𐑦𐑤𐑦𐑖𐑩𐑕𐑤𐑦 𐑓𐑼𐑚𐑦𐑛𐑩𐑯, 𐑚𐑳𐑑 𐑡𐑳𐑕𐑑 𐑩 𐑮𐑵𐑑𐑰𐑯 𐑨𐑒𐑑𐑦𐑝𐑦𐑑𐑦 𐑤𐑲𐑒 𐑚𐑮𐑰𐑞𐑦𐑙.

𐑞𐑨𐑑 𐑢𐑪𐑟 𐑞 𐑥𐑨𐑯 𐑣𐑵 𐑣𐑨𐑛, 𐑡𐑳𐑕𐑑 𐑞𐑨𐑑 𐑥𐑴𐑥𐑩𐑯𐑑, 𐑕𐑑𐑮𐑴𐑤𐑛 𐑦𐑯 𐑔𐑮𐑵 𐑞 𐑴𐑐𐑩𐑯 𐑛𐑹.

“·𐑛𐑮𐑱𐑒𐑴,” 𐑕𐑧𐑛 𐑞 𐑥𐑨𐑯, 𐑤𐑴 𐑯 𐑝𐑧𐑮𐑦 𐑨𐑙𐑜𐑮𐑦, “\emph{𐑢𐑪𐑑} 𐑸 𐑿 \emph{𐑕𐑱𐑦𐑙}?”

𐑦𐑯 𐑢𐑳𐑯 𐑕𐑐𐑤𐑦𐑑 𐑕𐑱𐑒𐑪𐑯𐑛 𐑝 𐑕𐑦𐑥𐑐𐑩𐑔𐑧𐑑𐑦𐑒 𐑐𐑨𐑯𐑦𐑒, ·𐑣𐑨𐑮𐑦 𐑓𐑹𐑥𐑿𐑤𐑱𐑑𐑩𐑛 𐑩 𐑮𐑧𐑕𐑒𐑿 𐑐𐑤𐑨𐑯.

“·𐑤𐑵𐑕𐑾𐑕 ·𐑥𐑨𐑤𐑓𐑶!” 𐑜𐑭𐑕𐑐𐑑 ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼. “\emph{𐑞} ·𐑤𐑵𐑕𐑾𐑕 ·𐑥𐑨𐑤𐑓𐑶?”

𐑢𐑳𐑯 𐑝 ·𐑥𐑨𐑤𐑒𐑦𐑯'𐑟 𐑩𐑕𐑦𐑕𐑑𐑩𐑯𐑑𐑕 𐑣𐑨𐑛 𐑑 𐑑𐑻𐑯 𐑩𐑢𐑱 𐑯 𐑓𐑱𐑕 𐑞 𐑢𐑷𐑤.

𐑒𐑵𐑤𐑦 𐑥𐑻𐑛𐑼𐑩𐑕 𐑲𐑟 𐑮𐑦𐑜𐑸𐑛𐑩𐑛 𐑣𐑦𐑥. “·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼.”

“𐑲 𐑨𐑥 𐑕𐑴, 𐑕𐑴 𐑪𐑯𐑼𐑛 𐑑 𐑥𐑰𐑑 𐑿!”

𐑞 𐑛𐑸𐑒 𐑲𐑟 𐑢𐑲𐑛𐑩𐑯𐑛, 𐑖𐑪𐑒𐑑 𐑕𐑼𐑐𐑮𐑲𐑟 𐑮𐑦𐑐𐑤𐑱𐑕𐑦𐑙 𐑛𐑧𐑛𐑤𐑦 𐑔𐑮𐑧𐑑.

“𐑘𐑹 𐑕𐑳𐑯 𐑣𐑨𐑟 𐑚𐑰𐑯 𐑑𐑧𐑤𐑦𐑙 𐑥𐑰 \emph{𐑷𐑤} 𐑩𐑚𐑬𐑑 𐑿,” ·𐑣𐑨𐑮𐑦 𐑜𐑳𐑖𐑑 𐑪𐑯, 𐑣𐑸𐑛𐑤𐑦 𐑰𐑝𐑩𐑯 𐑯𐑴𐑦𐑙 𐑢𐑪𐑑 𐑢𐑪𐑟 𐑒𐑳𐑥𐑦𐑙 𐑬𐑑 𐑝 𐑣𐑦𐑟 𐑥𐑬𐑔 𐑚𐑳𐑑 𐑡𐑳𐑕𐑑 𐑑𐑷𐑒𐑦𐑙 𐑨𐑟 𐑓𐑭𐑕𐑑 𐑨𐑟 𐑐𐑪𐑕𐑩𐑚𐑩𐑤. “𐑚𐑳𐑑 𐑝 𐑒𐑹𐑕 𐑲 𐑯𐑿 𐑩𐑚𐑬𐑑 𐑿 𐑚𐑦𐑓𐑹 𐑞𐑧𐑯, 𐑧𐑝𐑮𐑦𐑢𐑳𐑯 𐑯𐑴𐑟 𐑩𐑚𐑬𐑑 𐑿, 𐑞 𐑜𐑮𐑱𐑑 ·𐑤𐑵𐑕𐑾𐑕 ·𐑥𐑨𐑤𐑓𐑶! 𐑞 𐑥𐑴𐑕𐑑 𐑪𐑯𐑼𐑛 𐑤𐑹𐑾𐑑 𐑝 𐑷𐑤 𐑞 ·𐑣𐑬𐑕 𐑝 ·𐑕𐑤𐑲𐑔𐑼𐑦𐑯, 𐑲'𐑝 𐑚𐑰𐑯 𐑔𐑦𐑙𐑒𐑦𐑙 𐑩𐑚𐑬𐑑 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑜𐑧𐑑 𐑦𐑯𐑑𐑵 ·𐑕𐑤𐑲𐑔𐑼𐑦𐑯 ·𐑣𐑬𐑕 𐑥𐑲𐑕𐑧𐑤𐑓 𐑡𐑳𐑕𐑑 𐑚𐑦𐑒𐑪𐑟 𐑲 𐑣𐑻𐑛 𐑿 𐑢𐑻 𐑦𐑯 𐑦𐑑 𐑨𐑟 𐑩 𐑗𐑲𐑤𐑛—”

“\emph{𐑢𐑪𐑑 𐑸 𐑿 𐑕𐑱𐑦𐑙, ·𐑥𐑼~·𐑐𐑪𐑑𐑼?}” 𐑒𐑱𐑥 𐑩 𐑯𐑽-𐑕𐑒𐑮𐑰𐑥 𐑓𐑮𐑪𐑥 𐑬𐑑𐑕𐑲𐑛 𐑞 𐑖𐑪𐑐, 𐑯 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑚𐑻𐑕𐑑 𐑦𐑯 𐑩 𐑕𐑱𐑒𐑪𐑯𐑛 𐑤𐑱𐑑𐑼.

𐑞𐑺 𐑢𐑪𐑟 𐑕𐑳𐑗 𐑐𐑘𐑫𐑼 𐑣𐑪𐑮𐑼 𐑪𐑯 𐑣𐑻 𐑓𐑱𐑕 𐑞𐑨𐑑 ·𐑣𐑨𐑮𐑦'𐑟 𐑥𐑬𐑔 𐑴𐑐𐑩𐑯𐑛 𐑷𐑑𐑩𐑥𐑨𐑑𐑦𐑒𐑤𐑦, 𐑯 𐑞𐑧𐑯 𐑚𐑤𐑪𐑒𐑑 𐑪𐑯 𐑯𐑳𐑔𐑦𐑙-𐑑-𐑕𐑱.

“·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤!” 𐑒𐑮𐑲𐑛 ·𐑛𐑮𐑱𐑒𐑴. “𐑦𐑟 𐑦𐑑 𐑮𐑾𐑤𐑦 𐑿? 𐑲'𐑝 𐑣𐑻𐑛 𐑕𐑴 𐑥𐑳𐑗 𐑩𐑚𐑬𐑑 𐑿 𐑓𐑮𐑪𐑥 𐑥𐑲 𐑓𐑭𐑞𐑼, 𐑲'𐑝 𐑚𐑰𐑯 𐑔𐑦𐑙𐑒𐑦𐑙 𐑝 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑜𐑧𐑑 ·𐑕𐑹𐑑𐑩𐑛 𐑦𐑯𐑑𐑵 ·𐑜𐑮𐑦𐑓𐑦𐑯𐑛𐑹 𐑕𐑴 𐑲 𐑒𐑨𐑯—”

“\emph{𐑢𐑪𐑑?}” 𐑚𐑧𐑤𐑴𐑛 ·𐑤𐑵𐑕𐑾𐑕 ·𐑥𐑨𐑤𐑓𐑶 𐑯 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑦𐑯 𐑐𐑻𐑓𐑦𐑒𐑑 𐑿𐑯𐑦𐑕𐑩𐑯, 𐑕𐑑𐑨𐑯𐑛𐑦𐑙 𐑕𐑲𐑛-𐑚𐑲-𐑕𐑲𐑛. 𐑞𐑺 𐑣𐑧𐑛𐑟 𐑕𐑢𐑦𐑝𐑩𐑤𐑛 𐑑 𐑤𐑫𐑒 𐑨𐑑 𐑰𐑗 𐑳𐑞𐑼 𐑦𐑯 𐑛𐑿𐑐𐑤𐑦𐑒𐑩𐑑 𐑥𐑴𐑖𐑩𐑯𐑟, 𐑯 𐑞𐑧𐑯 𐑞 𐑑𐑵 𐑮𐑦𐑒𐑶𐑤𐑛 𐑓𐑮𐑪𐑥 𐑢𐑳𐑯 𐑩𐑯𐑳𐑞𐑼 𐑨𐑟 𐑞𐑴 𐑐𐑼𐑓𐑹𐑥𐑦𐑙 𐑩 𐑕𐑦𐑙𐑒𐑮𐑩𐑯𐑲𐑟𐑛 𐑛𐑭𐑯𐑕.

𐑞𐑺 𐑢𐑪𐑟 𐑩 𐑕𐑳𐑛𐑩𐑯 𐑓𐑤𐑳𐑮𐑦 𐑝 𐑨𐑒𐑖𐑩𐑯 𐑨𐑟 ·𐑤𐑵𐑕𐑾𐑕 𐑕𐑰𐑟𐑛 ·𐑛𐑮𐑱𐑒𐑴 𐑯 𐑛𐑮𐑨𐑜𐑛 𐑣𐑦𐑥 𐑬𐑑 𐑝 𐑞 𐑖𐑪𐑐.

𐑯 𐑞𐑧𐑯 𐑞𐑺 𐑢𐑪𐑟 𐑕𐑲𐑤𐑩𐑯𐑕.

𐑦𐑯 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑤𐑧𐑓𐑑 𐑣𐑨𐑯𐑛 𐑤𐑱 𐑩 𐑕𐑥𐑷𐑤 𐑛𐑮𐑦𐑙𐑒𐑦𐑙-𐑜𐑤𐑭𐑕, 𐑑𐑦𐑤𐑑𐑩𐑛 𐑴𐑝𐑼 𐑑 𐑢𐑳𐑯 𐑕𐑲𐑛 𐑦𐑯 𐑞 𐑓𐑼𐑜𐑪𐑑𐑩𐑯 𐑮𐑳𐑖, 𐑯𐑬 𐑕𐑤𐑴𐑤𐑦 𐑛𐑮𐑦𐑐𐑦𐑙 𐑛𐑮𐑪𐑐𐑕 𐑝 𐑨𐑤𐑒𐑩𐑣𐑪𐑤 𐑦𐑯𐑑𐑵 𐑞 𐑑𐑲𐑯𐑦 𐑐𐑳𐑛𐑩𐑤 𐑝 𐑮𐑧𐑛 𐑢𐑲𐑯 𐑞𐑨𐑑 𐑣𐑨𐑛 𐑩𐑐𐑽𐑛 𐑪𐑯 𐑞 𐑓𐑤𐑹.

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑑𐑮𐑴𐑛 𐑓𐑹𐑢𐑼𐑛 𐑦𐑯𐑑𐑵 𐑞 𐑖𐑪𐑐 𐑩𐑯𐑑𐑦𐑤 𐑖𐑰 𐑢𐑪𐑟 𐑪𐑐𐑩𐑟𐑦𐑑 ·𐑥𐑨𐑛𐑩𐑥 ·𐑥𐑨𐑤𐑒𐑦𐑯.

“·𐑥𐑨𐑛𐑩𐑥 ·𐑥𐑨𐑤𐑒𐑦𐑯,” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑣𐑻 𐑝𐑶𐑕 𐑒𐑭𐑥. “𐑢𐑪𐑑 𐑣𐑨𐑟 𐑚𐑰𐑯 𐑣𐑨𐑐𐑩𐑯𐑦𐑙 𐑣𐑽?”

·𐑥𐑨𐑛𐑩𐑥 ·𐑥𐑨𐑤𐑒𐑦𐑯 𐑤𐑫𐑒𐑑 𐑚𐑨𐑒 𐑕𐑲𐑤𐑩𐑯𐑑𐑤𐑦 𐑓 𐑓𐑹 𐑕𐑱𐑒𐑪𐑯𐑛𐑟, 𐑯 𐑞𐑧𐑯 𐑒𐑮𐑨𐑒𐑑 𐑳𐑐. 𐑖𐑰 𐑓𐑧𐑤 𐑩𐑜𐑱𐑯𐑕𐑑 𐑞 𐑢𐑷𐑤, 𐑢𐑰𐑟𐑦𐑙 𐑬𐑑 𐑤𐑭𐑓𐑑𐑼, 𐑯 𐑞𐑨𐑑 𐑕𐑧𐑑 𐑪𐑓 𐑚𐑴𐑔 𐑝 𐑣𐑻 𐑩𐑕𐑦𐑕𐑑𐑩𐑯𐑑𐑕, 𐑢𐑳𐑯 𐑝 𐑣𐑵𐑥 𐑓𐑧𐑤 𐑑 𐑣𐑻 𐑣𐑨𐑯𐑛𐑟 𐑯 𐑯𐑰𐑟 𐑪𐑯 𐑞 𐑓𐑤𐑹, 𐑜𐑦𐑜𐑩𐑤𐑦𐑙 𐑣𐑦𐑕𐑑𐑧𐑮𐑦𐑒𐑤𐑦.

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑤𐑴𐑤𐑦 𐑑𐑻𐑯𐑛 𐑑 𐑤𐑫𐑒 𐑨𐑑 ·𐑣𐑨𐑮𐑦, 𐑣𐑻 𐑦𐑒𐑕𐑐𐑮𐑧𐑖𐑩𐑯 𐑗𐑦𐑤𐑦. “𐑲 𐑤𐑰𐑝 𐑿 𐑩𐑤𐑴𐑯 𐑓 𐑕𐑦𐑒𐑕 𐑥𐑦𐑯𐑦𐑑𐑕. 𐑕𐑦𐑒𐑕 𐑥𐑦𐑯𐑦𐑑𐑕, ·𐑥𐑼~·𐑐𐑪𐑑𐑼, 𐑚𐑲 𐑞 𐑝𐑧𐑮𐑦 𐑒𐑤𐑪𐑒.”

“𐑲 𐑢𐑪𐑟 𐑴𐑯𐑤𐑦 𐑡𐑴𐑒𐑦𐑙 𐑼𐑬𐑯𐑛,” ·𐑣𐑨𐑮𐑦 𐑐𐑮𐑴𐑑𐑧𐑕𐑑𐑩𐑛, 𐑨𐑟 𐑞 𐑕𐑬𐑯𐑛𐑟 𐑝 𐑣𐑦𐑕𐑑𐑧𐑮𐑦𐑒𐑩𐑤 𐑤𐑭𐑓𐑑𐑼 𐑢𐑧𐑯𐑑 𐑪𐑯 𐑯𐑽𐑚𐑲.

“\emph{·𐑛𐑮𐑱𐑒𐑴 ·𐑥𐑨𐑤𐑓𐑶 𐑕𐑧𐑛 𐑦𐑯 𐑓𐑮𐑳𐑯𐑑 𐑝 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑞𐑨𐑑 𐑣𐑰 𐑢𐑪𐑯𐑑𐑩𐑛 𐑑 𐑚𐑰 𐑕𐑹𐑑𐑩𐑛 𐑦𐑯𐑑𐑵 ·𐑜𐑮𐑦𐑓𐑦𐑯𐑛𐑹!} 𐑡𐑴𐑒𐑦𐑙 𐑼𐑬𐑯𐑛 \emph{𐑦𐑟𐑩𐑯𐑑 𐑦𐑯𐑳𐑓} 𐑑 \emph{𐑛𐑵} 𐑞𐑨𐑑!” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑐𐑷𐑟𐑛, 𐑝𐑦𐑟𐑩𐑚𐑤𐑦 𐑑𐑱𐑒𐑦𐑙 𐑚𐑮𐑧𐑔𐑕. “𐑢𐑪𐑑 𐑐𐑸𐑑 𐑝 '𐑜𐑧𐑑 𐑓𐑦𐑑𐑩𐑛 𐑓 𐑮𐑴𐑚𐑟' 𐑕𐑬𐑯𐑛𐑩𐑛 𐑑 𐑿 𐑤𐑲𐑒 \emph{𐑐𐑤𐑰𐑟 𐑒𐑭𐑕𐑑 𐑩 ·𐑒𐑪𐑯𐑓𐑳𐑯𐑛𐑩𐑕 ·𐑗𐑸𐑥 𐑪𐑯 𐑞 𐑦𐑯𐑑𐑲𐑼 𐑿𐑯𐑦𐑝𐑻𐑕!}”

“𐑣𐑰 𐑢𐑪𐑟 𐑦𐑯 𐑩 𐑕𐑦𐑗𐑵𐑱𐑖𐑩𐑯𐑩𐑤 𐑒𐑪𐑯𐑑𐑧𐑒𐑕𐑑 𐑢𐑺 𐑞𐑴𐑟 𐑨𐑒𐑖𐑩𐑯𐑟 𐑥𐑱𐑛 𐑦𐑯𐑑𐑻𐑯𐑩𐑤 𐑕𐑧𐑯𐑕—”

“𐑯𐑴. 𐑛𐑴𐑯𐑑 𐑦𐑒𐑕𐑐𐑤𐑱𐑯. 𐑲 𐑛𐑴𐑯𐑑 𐑢𐑪𐑯𐑑 𐑑 𐑯𐑴 𐑢𐑪𐑑 𐑣𐑨𐑐𐑩𐑯𐑛 𐑦𐑯 𐑣𐑽, 𐑧𐑝𐑼. 𐑢𐑪𐑑𐑧𐑝𐑼 𐑛𐑸𐑒 𐑐𐑬𐑼 𐑦𐑯𐑣𐑨𐑚𐑦𐑑𐑕 𐑿, 𐑦𐑑 𐑦𐑟 \emph{𐑒𐑩𐑯𐑑𐑱𐑡𐑩𐑕}, 𐑯 𐑲 𐑛𐑴𐑯𐑑 𐑢𐑪𐑯𐑑 𐑑 𐑧𐑯𐑛 𐑳𐑐 𐑤𐑲𐑒 𐑐𐑫𐑼 ·𐑛𐑮𐑱𐑒𐑴 ·𐑥𐑨𐑤𐑓𐑶, 𐑐𐑫𐑼 ·𐑥𐑨𐑛𐑩𐑥 ·𐑥𐑨𐑤𐑒𐑦𐑯 𐑯 𐑣𐑻 𐑑𐑵 𐑐𐑫𐑼 𐑩𐑕𐑦𐑕𐑑𐑩𐑯𐑑𐑕.”

·𐑣𐑨𐑮𐑦 𐑕𐑲𐑛. 𐑦𐑑 𐑢𐑪𐑟 𐑒𐑤𐑽 𐑞𐑨𐑑 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑢𐑪𐑟𐑩𐑯𐑑 𐑦𐑯 𐑩 𐑥𐑵𐑛 𐑑 𐑤𐑦𐑕𐑩𐑯 𐑑 𐑮𐑰𐑟𐑩𐑯𐑩𐑚𐑩𐑤 𐑧𐑒𐑕𐑐𐑤𐑩𐑯𐑱𐑖𐑩𐑯𐑟. 𐑣𐑰 𐑤𐑫𐑒𐑑 𐑨𐑑 ·𐑥𐑨𐑛𐑩𐑥 ·𐑥𐑨𐑤𐑒𐑦𐑯, 𐑣𐑵 𐑢𐑪𐑟 𐑕𐑑𐑦𐑤 𐑢𐑰𐑟𐑦𐑙 𐑩𐑜𐑱𐑯𐑕𐑑 𐑞 𐑢𐑷𐑤, 𐑯 ·𐑥𐑨𐑤𐑒𐑦𐑯'𐑟 𐑑𐑵 𐑩𐑕𐑦𐑕𐑑𐑩𐑯𐑑𐑕, 𐑣𐑵 𐑣𐑨𐑛 𐑯𐑬 \emph{𐑚𐑴𐑔} 𐑓𐑷𐑤𐑩𐑯 𐑑 𐑞𐑺 𐑯𐑰𐑟, 𐑯 𐑓𐑲𐑯𐑩𐑤𐑦 𐑛𐑬𐑯 𐑨𐑑 𐑣𐑦𐑟 𐑴𐑯 𐑑𐑱𐑐-𐑥𐑧𐑠𐑼-𐑛𐑮𐑱𐑐𐑑 𐑚𐑪𐑛𐑦.

“𐑲'𐑥 𐑯𐑪𐑑 𐑒𐑢𐑲𐑑 𐑛𐑳𐑯 𐑚𐑰𐑦𐑙 𐑓𐑦𐑑𐑩𐑛 𐑓 𐑒𐑤𐑴𐑞𐑟,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑒𐑲𐑯𐑛𐑤𐑦. “𐑢𐑲 𐑛𐑴𐑯𐑑 𐑿 𐑜𐑴 𐑚𐑨𐑒 𐑯 𐑣𐑨𐑝 𐑩𐑯𐑳𐑞𐑼 𐑛𐑮𐑦𐑙𐑒?”

%  LocalWords:  QX31 awesomecool
