\chapter[The Efficient Market Hypothesis]{𐑞 ·𐑦𐑓𐑦𐑖𐑩𐑯𐑑 ·𐑥𐑸𐑒𐑩𐑑 ·𐑣𐑲𐑐𐑪𐑔𐑦𐑕𐑦𐑕\protect\authorsnotefootnotemark}

\begin{chapterOpeningAuthorNote}
𐑛𐑦𐑕𐑒𐑤𐑱𐑥𐑼: ·𐑡.~𐑒.~·𐑮𐑴𐑤𐑦𐑙 𐑦𐑟 𐑢𐑪𐑗𐑦𐑙 𐑿 𐑓𐑮𐑪𐑥 𐑢𐑺 𐑖𐑰 𐑢𐑱𐑑𐑕, 𐑦𐑑𐑻𐑯𐑩𐑤𐑦 𐑦𐑯 𐑞 𐑝𐑶𐑛 𐑚𐑦𐑑𐑢𐑰𐑯 𐑢𐑻𐑤𐑛𐑟.
\end{chapterOpeningAuthorNote}
\begin{chapterOpeningQuote}
𐑢𐑻𐑤𐑛 𐑛𐑪𐑥𐑦𐑯𐑱𐑖𐑩𐑯 𐑦𐑟 𐑕𐑳𐑗 𐑩𐑯 𐑳𐑜𐑤𐑦 𐑓𐑮𐑱𐑟. 𐑲 𐑐𐑮𐑦𐑓𐑻 𐑑 𐑒𐑷𐑤 𐑦𐑑 𐑢𐑻𐑤𐑛 𐑪𐑐𐑑𐑦𐑥𐑲𐑟𐑱𐑖𐑩𐑯.
\end{chapterOpeningQuote}

\authorsnotetext{𐑨𐑟 𐑳𐑞𐑼𐑟 𐑣𐑨𐑝 𐑯𐑴𐑑𐑩𐑛, 𐑞 𐑯𐑪𐑝𐑩𐑤𐑟 𐑕𐑰𐑥 𐑦𐑯𐑒𐑩𐑯𐑕𐑦𐑕𐑑𐑩𐑯𐑑 𐑦𐑯 𐑞 𐑩𐑐𐑨𐑮𐑩𐑯𐑑 𐑐𐑻𐑗𐑩𐑕𐑦𐑙 𐑐𐑬𐑼 𐑝 𐑩 ·𐑜𐑨𐑤𐑾𐑯; 𐑲'𐑥 𐑐𐑦𐑒𐑦𐑙 𐑩 𐑒𐑩𐑯𐑕𐑦𐑕𐑑𐑩𐑯𐑑 𐑝𐑨𐑤𐑿 𐑯 𐑕𐑑𐑦𐑒𐑦𐑙 𐑢𐑦𐑞 𐑦𐑑. 𐑓𐑲𐑝 𐑐𐑬𐑯𐑛𐑟 𐑕𐑑𐑻𐑤𐑦𐑙 𐑑 𐑞 ·𐑜𐑨𐑤𐑾𐑯 𐑛𐑳𐑟𐑩𐑯𐑑 𐑕𐑒𐑢𐑺 𐑢𐑦𐑞 𐑕𐑧𐑝𐑩𐑯 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑓 𐑩 𐑢𐑪𐑯𐑛 𐑯 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑿𐑟𐑦𐑙 𐑣𐑨𐑯𐑛-𐑥𐑰-𐑛𐑬𐑯 𐑢𐑪𐑯𐑛𐑟.}

\lettrinepara{𐑣}{𐑰𐑐𐑕} 𐑝 𐑜𐑴𐑤𐑛 ·𐑜𐑨𐑤𐑾𐑯𐑟. 𐑕𐑑𐑨𐑒𐑕 𐑝 𐑕𐑦𐑤𐑝𐑼 ·𐑕𐑦𐑒𐑩𐑤𐑟. 𐑐𐑲𐑤𐑟 𐑝 𐑚𐑮𐑪𐑯𐑟 ·𐑯𐑳𐑑𐑕.

\hplettrineextrapara
·𐑣𐑨𐑮𐑦 𐑕𐑑𐑫𐑛 𐑞𐑺, 𐑯 𐑕𐑑𐑺𐑛 𐑢𐑦𐑞 𐑣𐑦𐑟 𐑥𐑬𐑔 𐑴𐑐𐑩𐑯 𐑨𐑑 𐑞 𐑓𐑨𐑥𐑤𐑦 𐑝𐑷𐑤𐑑. 𐑣𐑰 𐑣𐑨𐑛 𐑕𐑴 𐑥𐑧𐑯𐑦 𐑒𐑢𐑧𐑕𐑗𐑩𐑯𐑟 𐑣𐑰 𐑛𐑦𐑛𐑩𐑯𐑑 𐑯𐑴 \emph{𐑢𐑺} 𐑑 𐑕𐑑𐑸𐑑.

𐑓𐑮𐑪𐑥 𐑡𐑳𐑕𐑑 𐑬𐑑𐑕𐑲𐑛 𐑞 𐑛𐑹 𐑝 𐑞 𐑝𐑷𐑤𐑑, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑢𐑪𐑗𐑑 𐑣𐑦𐑥, 𐑕𐑰𐑥𐑦𐑙 𐑑 𐑤𐑰𐑯 𐑒𐑨𐑠𐑵𐑩𐑤𐑦 𐑩𐑜𐑱𐑯𐑕𐑑 𐑞 𐑢𐑷𐑤, 𐑚𐑳𐑑 𐑣𐑻 𐑲𐑟 𐑦𐑯𐑑𐑧𐑯𐑑. 𐑢𐑧𐑤, 𐑞𐑨𐑑 𐑥𐑱𐑛 𐑕𐑧𐑯𐑕. 𐑚𐑰𐑦𐑙 𐑐𐑤𐑪𐑐𐑑 𐑦𐑯 𐑓𐑮𐑳𐑯𐑑 𐑝 𐑩 𐑡𐑲𐑩𐑯𐑑 𐑣𐑰𐑐 𐑝 𐑜𐑴𐑤𐑛 𐑒𐑶𐑯𐑟 𐑢𐑪𐑟 𐑩 𐑑𐑧𐑕𐑑 𐑝 𐑒𐑨𐑮𐑩𐑒𐑑𐑼 𐑕𐑴 𐑐𐑘𐑫𐑼 𐑦𐑑 𐑢𐑪𐑟 𐑸𐑒𐑦𐑑𐑲𐑐𐑩𐑤.

“𐑸 𐑞𐑰𐑟 𐑒𐑶𐑯𐑟 𐑞 𐑐𐑘𐑫𐑼 𐑥𐑧𐑑𐑩𐑤?” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑓𐑲𐑯𐑩𐑤𐑦.

“𐑢𐑪𐑑?” 𐑣𐑦𐑕𐑑 𐑞 𐑜𐑪𐑚𐑤𐑦𐑯 ·𐑜𐑮𐑦𐑐𐑣𐑫𐑒, 𐑣𐑵 𐑢𐑪𐑟 𐑢𐑱𐑑𐑦𐑙 𐑯𐑽 𐑞 𐑛𐑹. “𐑸 𐑿 𐑒𐑢𐑧𐑕𐑗𐑩𐑯𐑦𐑙 𐑞 𐑦𐑯𐑑𐑧𐑜𐑮𐑦𐑑𐑦 𐑝 ·𐑜𐑮𐑦𐑙𐑜𐑩𐑑𐑕, ·𐑥𐑼~·𐑐𐑪𐑑𐑼-·𐑧𐑝𐑩𐑯𐑟-·𐑝𐑧𐑮𐑟?”

“𐑯𐑴,” 𐑕𐑧𐑛 ·𐑣𐑨𐑮𐑦 𐑨𐑚𐑕𐑩𐑯𐑑𐑤𐑦, “𐑯𐑪𐑑 𐑨𐑑 𐑷𐑤, 𐑕𐑪𐑮𐑦 𐑦𐑓 𐑞𐑨𐑑 𐑒𐑱𐑥 𐑬𐑑 𐑮𐑪𐑙, 𐑕𐑻. 𐑲 𐑡𐑳𐑕𐑑 𐑣𐑨𐑝 𐑯𐑴 𐑲𐑛𐑾 𐑨𐑑 𐑷𐑤 𐑣𐑬 𐑘𐑹 𐑓𐑲𐑯𐑨𐑯𐑖𐑩𐑤 𐑕𐑦𐑕𐑑𐑩𐑥 𐑢𐑻𐑒𐑕. 𐑲'𐑥 𐑭𐑕𐑒𐑦𐑙 𐑦𐑓 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑦𐑯 𐑡𐑧𐑯𐑼𐑩𐑤 𐑸 𐑥𐑱𐑛 𐑝 𐑐𐑘𐑫𐑼 𐑜𐑴𐑤𐑛.”

“𐑝 𐑒𐑹𐑕,” 𐑕𐑧𐑛 ·𐑜𐑮𐑦𐑐𐑣𐑫𐑒.

“𐑯 𐑒𐑨𐑯 𐑧𐑯𐑦𐑢𐑳𐑯 𐑒𐑶𐑯 𐑞𐑧𐑥, 𐑹 𐑸 𐑞𐑱 𐑦𐑖𐑵𐑛 𐑚𐑲 𐑩 𐑥𐑩𐑯𐑪𐑐𐑩𐑤𐑦 𐑞𐑨𐑑 𐑞𐑺𐑚𐑲 𐑒𐑩𐑤𐑧𐑒𐑑𐑕 𐑕𐑱𐑯𐑘𐑼𐑦𐑡?”

“𐑢𐑪𐑑?” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤.

·𐑜𐑮𐑦𐑐𐑣𐑫𐑒 𐑜𐑮𐑦𐑯𐑛, 𐑖𐑴𐑦𐑙 𐑖𐑸𐑐 𐑑𐑰𐑔. “𐑴𐑯𐑤𐑦 𐑩 𐑓𐑵𐑤 𐑢𐑫𐑛 𐑑𐑮𐑳𐑕𐑑 𐑧𐑯𐑦 𐑚𐑳𐑑 𐑜𐑪𐑚𐑤𐑦𐑯 𐑒𐑶𐑯!”

“𐑦𐑯 𐑳𐑞𐑼 𐑢𐑻𐑛𐑟,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, “𐑞 𐑒𐑶𐑯𐑟 𐑸𐑯𐑑 𐑕𐑩𐑐𐑴𐑕𐑑 𐑑 𐑚𐑰 𐑢𐑻𐑔 𐑧𐑯𐑦 𐑥𐑹 𐑞𐑨𐑯 𐑞 𐑥𐑧𐑑𐑩𐑤 𐑥𐑱𐑒𐑦𐑙 𐑞𐑧𐑥 𐑳𐑐?”

·𐑜𐑮𐑦𐑐𐑣𐑫𐑒 𐑕𐑑𐑺𐑛 𐑨𐑑 ·𐑣𐑨𐑮𐑦. ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑤𐑫𐑒𐑑 𐑚𐑦𐑥𐑿𐑟𐑛.

“𐑲 𐑥𐑰𐑯, 𐑕𐑩𐑐𐑴𐑟 𐑲 𐑒𐑱𐑥 𐑦𐑯 𐑣𐑽 𐑢𐑦𐑞 𐑩 𐑑𐑳𐑯 𐑝 𐑕𐑦𐑤𐑝𐑼. 𐑒𐑫𐑛 𐑲 𐑜𐑧𐑑 𐑩 𐑑𐑳𐑯 𐑝 ·𐑕𐑦𐑒𐑩𐑤𐑟 𐑥𐑱𐑛 𐑓𐑮𐑪𐑥 𐑦𐑑?”

“𐑓 𐑩 𐑓𐑰, ·𐑥𐑼~·𐑐𐑪𐑑𐑼-·𐑧𐑝𐑩𐑯𐑟-·𐑝𐑧𐑮𐑟.” 𐑞 𐑜𐑪𐑚𐑤𐑦𐑯 𐑢𐑪𐑗𐑑 𐑣𐑦𐑥 𐑢𐑦𐑞 𐑜𐑤𐑦𐑑𐑼𐑦𐑙 𐑲𐑟. “𐑓 𐑩 𐑕𐑻𐑑𐑩𐑯 𐑓𐑰. 𐑢𐑺 𐑢𐑫𐑛 𐑿 𐑓𐑲𐑯𐑛 𐑩 𐑑𐑳𐑯 𐑝 𐑕𐑦𐑤𐑝𐑼, 𐑲 𐑢𐑳𐑯𐑛𐑼?”

“𐑲 𐑢𐑪𐑟 𐑕𐑐𐑰𐑒𐑦𐑙 𐑣𐑲𐑐𐑩𐑔𐑧𐑑𐑦𐑒𐑤𐑦,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. \emph{𐑓 𐑯𐑬, 𐑨𐑑 𐑧𐑯𐑦 𐑮𐑱𐑑.} “𐑕𐑴…𐑣𐑬 𐑥𐑳𐑗 𐑢𐑫𐑛 𐑿 𐑗𐑸𐑡 𐑦𐑯 𐑓𐑰𐑟, 𐑨𐑟 𐑩 𐑓𐑮𐑨𐑒𐑖𐑩𐑯 𐑝 𐑞 𐑣𐑴𐑤 𐑢𐑱𐑑?”

·𐑜𐑮𐑦𐑐𐑣𐑫𐑒'𐑕 𐑲𐑟 𐑢𐑻 𐑦𐑯𐑑𐑧𐑯𐑑. “𐑲 𐑢𐑫𐑛 𐑣𐑨𐑓 𐑑 𐑒𐑩𐑯𐑕𐑳𐑤𐑑 𐑥𐑲 𐑕𐑵𐑐𐑽𐑽𐑟…”

“𐑜𐑦𐑝 𐑥𐑰 𐑩 𐑢𐑲𐑤𐑛 𐑜𐑧𐑕. 𐑲 𐑢𐑴𐑯𐑑 𐑣𐑴𐑤𐑛 ·𐑜𐑮𐑦𐑙𐑜𐑩𐑑𐑕 𐑑 𐑦𐑑.”

“𐑩 𐑑𐑢𐑧𐑯𐑑𐑾𐑔 𐑐𐑸𐑑 𐑝 𐑞 𐑥𐑧𐑑𐑩𐑤 𐑢𐑫𐑛 𐑢𐑧𐑤 𐑐𐑱 𐑓 𐑞 𐑒𐑶𐑯𐑦𐑙.”

·𐑣𐑨𐑮𐑦 𐑯𐑪𐑛𐑩𐑛. “𐑔𐑨𐑙𐑒 𐑿 𐑝𐑧𐑮𐑦 𐑥𐑳𐑗, ·𐑥𐑼~·𐑜𐑮𐑦𐑐𐑣𐑫𐑒.”

\emph{𐑕𐑴 𐑯𐑪𐑑 𐑴𐑯𐑤𐑦 𐑦𐑟 𐑞 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑦𐑒𐑪𐑯𐑩𐑥𐑦 𐑷𐑤𐑥𐑴𐑕𐑑 𐑒𐑩𐑥𐑐𐑤𐑰𐑑𐑤𐑦 𐑛𐑰𐑒𐑳𐑐𐑩𐑤𐑛 𐑓𐑮𐑪𐑥 𐑞 ·𐑥𐑳𐑜𐑩𐑤 𐑦𐑒𐑪𐑯𐑩𐑥𐑦, 𐑯𐑴-𐑢𐑳𐑯 𐑣𐑽 𐑣𐑨𐑟 𐑧𐑝𐑼 𐑣𐑻𐑛 𐑝 𐑸𐑚𐑦𐑑𐑮𐑭𐑠.} 𐑞 𐑤𐑸𐑡𐑼 ·𐑥𐑳𐑜𐑩𐑤 𐑦𐑒𐑪𐑯𐑩𐑥𐑦 𐑣𐑨𐑛 𐑩 𐑓𐑤𐑳𐑒𐑗𐑵𐑱𐑑𐑦𐑙 𐑑𐑮𐑱𐑛𐑦𐑙 𐑮𐑱𐑯𐑡 𐑝 𐑜𐑴𐑤𐑛 𐑑 𐑕𐑦𐑤𐑝𐑼, 𐑕𐑴 𐑧𐑝𐑮𐑦 𐑑𐑲𐑥 𐑞 ·𐑥𐑳𐑜𐑩𐑤 𐑜𐑴𐑤𐑛-𐑑-𐑕𐑦𐑤𐑝𐑼 𐑮𐑱𐑖𐑦𐑴 𐑜𐑪𐑑 𐑥𐑹 𐑞𐑨𐑯 5\% 𐑩𐑢𐑱 𐑓𐑮𐑪𐑥 𐑞 𐑢𐑱𐑑 𐑝 𐑕𐑧𐑝𐑩𐑯𐑑𐑰𐑯 ·𐑕𐑦𐑒𐑩𐑤𐑟 𐑑 𐑢𐑳𐑯 ·𐑜𐑨𐑤𐑾𐑯, 𐑲𐑞𐑼 𐑜𐑴𐑤𐑛 𐑹 𐑕𐑦𐑤𐑝𐑼 𐑖𐑫𐑛 𐑣𐑨𐑝 𐑛𐑮𐑱𐑯𐑛 𐑓𐑮𐑪𐑥 𐑞 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑦𐑒𐑪𐑯𐑩𐑥𐑦 𐑩𐑯𐑑𐑦𐑤 𐑦𐑑 𐑚𐑦𐑒𐑱𐑥 𐑦𐑥𐑐𐑪𐑕𐑩𐑚𐑩𐑤 𐑑 𐑥𐑱𐑯𐑑𐑱𐑯 𐑞 𐑦𐑒𐑕𐑗𐑱𐑯𐑡 𐑮𐑱𐑑. 𐑚𐑮𐑦𐑙 𐑦𐑯 𐑩 𐑑𐑳𐑯 𐑝 𐑕𐑦𐑤𐑝𐑼, 𐑗𐑱𐑯𐑡 𐑑 ·𐑕𐑦𐑒𐑩𐑤𐑟 (𐑯 𐑐𐑱 5\%), 𐑗𐑱𐑯𐑡 𐑞 ·𐑕𐑦𐑒𐑩𐑤𐑟 𐑓 ·𐑜𐑨𐑤𐑾𐑯𐑟, 𐑑𐑱𐑒 𐑞 𐑜𐑴𐑤𐑛 𐑑 𐑞 ·𐑥𐑳𐑜𐑩𐑤 𐑢𐑻𐑤𐑛, 𐑦𐑒𐑕𐑗𐑱𐑯𐑡 𐑦𐑑 𐑓 𐑥𐑹 𐑕𐑦𐑤𐑝𐑼 𐑞𐑨𐑯 𐑿 𐑕𐑑𐑸𐑑𐑩𐑛 𐑢𐑦𐑞, 𐑯 𐑮𐑦𐑐𐑰𐑑.

𐑢𐑪𐑟𐑩𐑯𐑑 𐑞 ·𐑥𐑳𐑜𐑩𐑤 𐑜𐑴𐑤𐑛-𐑑-𐑕𐑦𐑤𐑝𐑼 𐑮𐑱𐑖𐑦𐑴 𐑕𐑳𐑥𐑢𐑺 𐑼𐑬𐑯𐑛 𐑓𐑦𐑓𐑑𐑦 𐑑 𐑢𐑳𐑯? ·𐑣𐑨𐑮𐑦 𐑛𐑦𐑛𐑩𐑯𐑑 𐑔𐑦𐑙𐑒 𐑦𐑑 𐑢𐑪𐑟 𐑕𐑧𐑝𐑩𐑯𐑑𐑰𐑯, 𐑧𐑯𐑦𐑢𐑱. 𐑯 𐑦𐑑 𐑤𐑫𐑒𐑑 𐑤𐑲𐑒 𐑞 𐑕𐑦𐑤𐑝𐑼 𐑒𐑶𐑯𐑟 𐑢𐑻 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 \emph{𐑕𐑥𐑷𐑤𐑼} 𐑞𐑨𐑯 𐑞 𐑜𐑴𐑤𐑛 𐑒𐑶𐑯𐑟.

𐑞𐑧𐑯 𐑩𐑜𐑱𐑯, ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑕𐑑𐑨𐑯𐑛𐑦𐑙 𐑦𐑯 𐑩 𐑚𐑨𐑙𐑒 𐑞𐑨𐑑 \emph{𐑤𐑦𐑑𐑼𐑩𐑤𐑦} 𐑕𐑑𐑹𐑛 𐑘𐑹 𐑥𐑳𐑯𐑦 𐑦𐑯 𐑝𐑷𐑤𐑑𐑕 𐑓𐑫𐑤 𐑝 𐑜𐑴𐑤𐑛 𐑒𐑶𐑯𐑟 𐑜𐑸𐑛𐑩𐑛 𐑚𐑲 𐑛𐑮𐑨𐑜𐑩𐑯𐑟, 𐑢𐑺 𐑿 𐑣𐑨𐑛 𐑑 𐑜𐑴 𐑦𐑯 𐑯 𐑑𐑱𐑒 𐑒𐑶𐑯𐑟 𐑬𐑑 𐑝 𐑘𐑹 𐑝𐑷𐑤𐑑 𐑢𐑧𐑯𐑧𐑝𐑼 𐑿 𐑢𐑪𐑯𐑑𐑩𐑛 𐑑 𐑕𐑐𐑧𐑯𐑛 𐑥𐑳𐑯𐑦. 𐑞 𐑓𐑲𐑯𐑼 𐑐𐑶𐑯𐑑𐑕 𐑝 𐑸𐑚𐑦𐑑𐑮𐑭𐑠𐑦𐑙 𐑩𐑢𐑱 𐑥𐑸𐑒𐑩𐑑 𐑦𐑯𐑦𐑓𐑦𐑖𐑩𐑯𐑕𐑦𐑟 𐑥𐑲𐑑 𐑢𐑧𐑤 𐑚𐑰 𐑤𐑪𐑕𐑑 𐑪𐑯 𐑞𐑧𐑥. 𐑣𐑰'𐑛 𐑚𐑰𐑯 𐑑𐑧𐑥𐑐𐑑𐑩𐑛 𐑑 𐑥𐑱𐑒 𐑕𐑯𐑲𐑛 𐑮𐑦𐑥𐑸𐑒𐑕 𐑩𐑚𐑬𐑑 𐑞 𐑒𐑮𐑵𐑛𐑦𐑑𐑦 𐑝 𐑞𐑺 𐑓𐑲𐑯𐑨𐑯𐑖𐑩𐑤 𐑕𐑦𐑕𐑑𐑩𐑥…

\emph{𐑚𐑳𐑑 𐑞 𐑕𐑨𐑛 𐑔𐑦𐑙 𐑦𐑟, 𐑞𐑺 𐑢𐑱 𐑦𐑟 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑚𐑧𐑑𐑼.}

𐑪𐑯 𐑞 𐑳𐑞𐑼 𐑣𐑨𐑯𐑛, 𐑢𐑳𐑯 𐑒𐑪𐑥𐑐𐑦𐑑𐑩𐑯𐑑 𐑣𐑧𐑡 𐑓𐑳𐑯𐑛𐑦 𐑒𐑫𐑛 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑴𐑯 𐑞 𐑣𐑴𐑤 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑢𐑻𐑤𐑛 𐑢𐑦𐑞𐑦𐑯 𐑩 𐑢𐑰𐑒. ·𐑣𐑨𐑮𐑦 𐑓𐑲𐑤𐑛 𐑩𐑢𐑱 𐑞𐑦𐑕 𐑯𐑴𐑖𐑩𐑯 𐑦𐑯 𐑒𐑱𐑕 𐑣𐑰 𐑧𐑝𐑼 𐑮𐑨𐑯 𐑬𐑑 𐑝 𐑥𐑳𐑯𐑦, 𐑹 𐑣𐑨𐑛 𐑩 𐑢𐑰𐑒 𐑓𐑮𐑰.

𐑥𐑰𐑯𐑢𐑲𐑤, 𐑞 𐑡𐑲𐑩𐑯𐑑 𐑣𐑰𐑐𐑕 𐑝 𐑜𐑴𐑤𐑛 𐑒𐑶𐑯𐑟 𐑢𐑦𐑞𐑦𐑯 𐑞 ·𐑐𐑪𐑑𐑼 𐑝𐑷𐑤𐑑 𐑷𐑑 𐑑 𐑕𐑵𐑑 𐑣𐑦𐑟 𐑯𐑽-𐑑𐑻𐑥 𐑮𐑦𐑒𐑢𐑲𐑼𐑥𐑩𐑯𐑑𐑕.

·𐑣𐑨𐑮𐑦 𐑕𐑑𐑳𐑥𐑐𐑑 𐑓𐑹𐑢𐑼𐑛, 𐑯 𐑚𐑦𐑜𐑨𐑯 𐑐𐑦𐑒𐑦𐑙 𐑳𐑐 𐑜𐑴𐑤𐑛 𐑒𐑶𐑯𐑟 𐑢𐑦𐑞 𐑢𐑳𐑯 𐑣𐑨𐑯𐑛 𐑯 𐑛𐑳𐑥𐑐𐑦𐑙 𐑞𐑧𐑥 𐑦𐑯𐑑𐑵 𐑞 𐑳𐑞𐑼.

𐑢𐑧𐑯 𐑣𐑰 𐑣𐑨𐑛 𐑮𐑰𐑗𐑑 𐑑𐑢𐑧𐑯𐑑𐑦, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑒𐑪𐑓𐑑. “𐑲 𐑔𐑦𐑙𐑒 𐑞𐑨𐑑 𐑢𐑦𐑤 𐑚𐑰 𐑥𐑹 𐑞𐑨𐑯 𐑦𐑯𐑳𐑓 𐑑 𐑐𐑱 𐑓 𐑘𐑹 𐑕𐑒𐑵𐑤 𐑕𐑩𐑐𐑤𐑲𐑟, ·𐑥𐑼~·𐑐𐑪𐑑𐑼.”

“𐑣𐑥?” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑣𐑦𐑟 𐑥𐑲𐑯𐑛 𐑧𐑤𐑕𐑢𐑺. “𐑣𐑴𐑤𐑛 𐑪𐑯, 𐑲'𐑥 𐑛𐑵𐑦𐑙 𐑩 ·𐑓𐑻𐑥𐑦 𐑒𐑨𐑤𐑒𐑿𐑤𐑱𐑖𐑩𐑯.”

“𐑩 \emph{𐑢𐑪𐑑}?” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑕𐑬𐑯𐑛𐑦𐑙 𐑕𐑳𐑥𐑢𐑪𐑑 𐑩𐑤𐑸𐑥𐑛.

“𐑦𐑑'𐑕 𐑩 𐑥𐑨𐑔𐑩𐑥𐑨𐑑𐑦𐑒𐑩𐑤 𐑔𐑦𐑙. 𐑯𐑱𐑥𐑛 𐑭𐑓𐑑𐑼 ·𐑧𐑯𐑮𐑰𐑒𐑴 ·𐑓𐑻𐑥𐑦. 𐑩 𐑢𐑱 𐑝 𐑜𐑧𐑑𐑦𐑙 𐑮𐑳𐑓 𐑯𐑳𐑥𐑚𐑼𐑟 𐑒𐑢𐑦𐑒𐑤𐑦 𐑦𐑯 𐑘𐑹 𐑣𐑧𐑛…”

𐑑𐑢𐑧𐑯𐑑𐑦 𐑜𐑴𐑤𐑛 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑢𐑱𐑛 𐑩 𐑑𐑧𐑯𐑔 𐑝 𐑩 𐑒𐑦𐑤𐑩𐑜𐑮𐑨𐑥, 𐑥𐑱𐑚𐑰? 𐑯 𐑜𐑴𐑤𐑛 𐑢𐑪𐑟, 𐑢𐑪𐑑, 𐑑𐑧𐑯 𐑔𐑬𐑟𐑩𐑯𐑛 ·𐑚𐑮𐑦𐑑𐑦𐑖 𐑐𐑬𐑯𐑛𐑟 𐑩 𐑒𐑦𐑤𐑩𐑜𐑮𐑨𐑥? 𐑕𐑴 𐑩 ·𐑜𐑨𐑤𐑾𐑯 𐑢𐑫𐑛 𐑚𐑰 𐑢𐑻𐑔 𐑩𐑚𐑬𐑑 𐑓𐑦𐑓𐑑𐑦 𐑐𐑬𐑯𐑛𐑟…𐑞 𐑥𐑬𐑯𐑛𐑟 𐑝 𐑜𐑴𐑤𐑛 𐑒𐑶𐑯𐑟 𐑤𐑫𐑒𐑑 𐑑 𐑚𐑰 𐑩𐑚𐑬𐑑 𐑕𐑦𐑒𐑕𐑑𐑦 𐑒𐑶𐑯𐑟 𐑣𐑲 𐑯 𐑑𐑢𐑧𐑯𐑑𐑦 𐑒𐑶𐑯𐑟 𐑢𐑲𐑛 𐑦𐑯 𐑲𐑞𐑼 𐑛𐑦𐑥𐑧𐑯𐑖𐑩𐑯 𐑝 𐑞 𐑚𐑱𐑕, 𐑯 𐑩 𐑥𐑬𐑯𐑛 𐑢𐑪𐑟 𐑐𐑦𐑮𐑩𐑥𐑦𐑛𐑩𐑤, 𐑕𐑴 𐑦𐑑 𐑢𐑫𐑛 𐑚𐑰 𐑼𐑬𐑯𐑛 𐑢𐑳𐑯-𐑔𐑻𐑛 𐑝 𐑞 𐑒𐑿𐑚. 𐑱𐑑 𐑔𐑬𐑟𐑩𐑯𐑛 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑐𐑻 𐑥𐑬𐑯𐑛, 𐑮𐑳𐑓𐑤𐑦, 𐑯 𐑞𐑺 𐑢𐑻 𐑼𐑬𐑯𐑛 𐑓𐑲𐑝 𐑥𐑬𐑯𐑛𐑟 𐑝 𐑞𐑨𐑑 𐑕𐑲𐑟, 𐑕𐑴 𐑓𐑹𐑑𐑦 𐑔𐑬𐑟𐑩𐑯𐑛 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑹 2 𐑥𐑦𐑤𐑘𐑩𐑯 𐑐𐑬𐑯𐑛𐑟 𐑕𐑑𐑻𐑤𐑦𐑙.

𐑯𐑪𐑑 𐑚𐑨𐑛. ·𐑣𐑨𐑮𐑦 𐑕𐑥𐑲𐑤𐑛 𐑢𐑦𐑞 𐑩 𐑕𐑻𐑑𐑩𐑯 𐑜𐑮𐑦𐑥 𐑕𐑨𐑑𐑦𐑕𐑓𐑨𐑒𐑖𐑩𐑯. 𐑦𐑑 𐑢𐑪𐑟 𐑑𐑵 𐑚𐑨𐑛 𐑞𐑨𐑑 𐑣𐑰 𐑢𐑪𐑟 𐑮𐑲𐑑 𐑦𐑯 𐑞 𐑥𐑦𐑛𐑩𐑤 𐑝 𐑛𐑦𐑕𐑒𐑳𐑝𐑼𐑦𐑙 𐑞 𐑩𐑥𐑱𐑟𐑦𐑙 𐑯𐑿 𐑢𐑻𐑤𐑛 𐑝 𐑥𐑨𐑡𐑦𐑒, 𐑯 𐑒𐑫𐑛𐑩𐑯𐑑 𐑑𐑱𐑒 𐑑𐑲𐑥 𐑬𐑑 𐑑 𐑦𐑒𐑕𐑐𐑤𐑹 𐑞 𐑩𐑥𐑱𐑟𐑦𐑙 𐑯𐑿 𐑢𐑻𐑤𐑛 𐑝 𐑚𐑰𐑦𐑙 𐑮𐑦𐑗, 𐑢𐑦𐑗 𐑩 𐑒𐑢𐑦𐑒 ·𐑓𐑻𐑥𐑦 𐑧𐑕𐑑𐑦𐑥𐑩𐑑 𐑕𐑧𐑛 𐑢𐑪𐑟 𐑮𐑳𐑓𐑤𐑦 𐑩 𐑚𐑦𐑤𐑘𐑩𐑯 𐑑𐑲𐑥𐑟 𐑤𐑧𐑕 𐑦𐑯𐑑𐑼𐑩𐑕𐑑𐑦𐑙.

\emph{𐑕𐑑𐑦𐑤, 𐑞𐑨𐑑'𐑕 𐑞 𐑤𐑭𐑕𐑑 𐑑𐑲𐑥 𐑲 𐑧𐑝𐑼 𐑥𐑴 𐑩 𐑤𐑷𐑯 𐑓 𐑢𐑳𐑯 𐑤𐑬𐑟𐑦 𐑐𐑬𐑯𐑛.}

·𐑣𐑨𐑮𐑦 𐑢𐑰𐑤𐑛 𐑓𐑮𐑪𐑥 𐑞 𐑡𐑲𐑩𐑯𐑑 𐑣𐑰𐑐 𐑝 𐑥𐑳𐑯𐑦. “𐑐𐑸𐑛𐑩𐑯 𐑥𐑰 𐑓 𐑭𐑕𐑒𐑦𐑙, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑚𐑳𐑑 𐑲 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑞𐑨𐑑 𐑥𐑲 𐑐𐑺𐑩𐑯𐑑𐑕 𐑢𐑻 𐑦𐑯 𐑞𐑺 𐑑𐑢𐑧𐑯𐑑𐑦𐑟 𐑢𐑧𐑯 𐑞𐑱 𐑛𐑲𐑛. 𐑦𐑟 𐑞𐑦𐑕 𐑩 \emph{𐑿𐑠𐑵𐑩𐑤} 𐑩𐑥𐑬𐑯𐑑 𐑝 𐑥𐑳𐑯𐑦 𐑓 𐑩 𐑘𐑳𐑙 𐑒𐑳𐑐𐑩𐑤 𐑑 𐑣𐑨𐑝 𐑦𐑯 𐑞𐑺 𐑝𐑷𐑤𐑑, 𐑦𐑯 𐑞 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑢𐑻𐑤𐑛?” 𐑦𐑓 𐑦𐑑 𐑢𐑪𐑟, 𐑩 𐑒𐑳𐑐 𐑝 𐑑𐑰 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑒𐑪𐑕𐑑 𐑓𐑲𐑝 𐑔𐑬𐑟𐑩𐑯𐑛 𐑐𐑬𐑯𐑛𐑟. 𐑮𐑵𐑤 𐑢𐑳𐑯 𐑝 𐑰𐑒𐑩𐑯𐑪𐑥𐑦𐑒𐑕: 𐑿 𐑒𐑭𐑯𐑑 𐑰𐑑 𐑥𐑳𐑯𐑦.

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑖𐑫𐑒 𐑣𐑻 𐑣𐑧𐑛. “𐑘𐑹 𐑓𐑭𐑞𐑼 𐑢𐑪𐑟 𐑞 𐑤𐑭𐑕𐑑 𐑺 𐑝 𐑩𐑯 𐑴𐑤𐑛 𐑓𐑨𐑥𐑤𐑦, ·𐑥𐑼~·𐑐𐑪𐑑𐑼. 𐑦𐑑'𐑕 𐑷𐑤𐑕𐑴 𐑐𐑪𐑕𐑩𐑚𐑩𐑤…” 𐑞 𐑢𐑦𐑗 𐑣𐑧𐑟𐑦𐑑𐑱𐑑𐑩𐑛. “𐑕𐑳𐑥 𐑝 𐑞𐑦𐑕 𐑥𐑳𐑯𐑦 𐑥𐑱 𐑚𐑰 𐑓𐑮𐑪𐑥 𐑚𐑬𐑯𐑑𐑦𐑟 𐑐𐑤𐑱𐑕𐑑 𐑪𐑯 𐑿-𐑯𐑴-𐑣𐑵, 𐑐𐑱𐑩𐑚𐑩𐑤 𐑑 𐑣𐑦𐑟 𐑒𐑦—𐑭, 𐑑 𐑣𐑵𐑧𐑝𐑼 𐑥𐑲𐑑 𐑛𐑦𐑓𐑰𐑑 𐑣𐑦𐑥. 𐑹 𐑞𐑴𐑟 𐑚𐑬𐑯𐑑𐑦𐑟 𐑥𐑲𐑑 𐑯𐑪𐑑 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑒𐑩𐑤𐑧𐑒𐑑𐑩𐑛 𐑘𐑧𐑑. 𐑲 𐑨𐑥 𐑯𐑪𐑑 𐑖𐑫𐑼.”

“𐑦𐑯𐑑𐑼𐑩𐑕𐑑𐑦𐑙…” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑕𐑤𐑴𐑤𐑦. “𐑕𐑴 𐑕𐑳𐑥 𐑝 𐑞𐑦𐑕 𐑮𐑾𐑤𐑦 𐑦𐑟, 𐑦𐑯 𐑩 𐑕𐑧𐑯𐑕, 𐑥𐑲𐑯. 𐑞𐑨𐑑 𐑦𐑟, 𐑻𐑯𐑛 𐑚𐑲 𐑥𐑰. 𐑕𐑹𐑑 𐑝. 𐑐𐑪𐑕𐑩𐑚𐑤𐑦. 𐑰𐑝𐑩𐑯 𐑦𐑓 𐑲 𐑛𐑴𐑯𐑑 𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑞 𐑩𐑒𐑱𐑠𐑩𐑯.” 𐑣𐑨𐑮𐑦'𐑟 𐑓𐑦𐑙𐑜𐑼𐑟 𐑑𐑨𐑐𐑑 𐑩𐑜𐑱𐑯𐑕𐑑 𐑣𐑦𐑟 𐑑𐑮𐑬𐑟𐑼-𐑤𐑧𐑜. “𐑞𐑨𐑑 𐑥𐑱𐑒𐑕 𐑥𐑰 𐑓𐑰𐑤 𐑤𐑧𐑕 𐑜𐑦𐑤𐑑𐑦 𐑩𐑚𐑬𐑑 𐑕𐑐𐑧𐑯𐑛𐑦𐑙 \emph{𐑩 𐑝𐑧𐑮𐑦 𐑑𐑲𐑯𐑦 𐑓𐑮𐑨𐑒𐑖𐑩𐑯 𐑝 𐑦𐑑! 𐑛𐑴𐑯𐑑 𐑐𐑨𐑯𐑦𐑒, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤!}”

“·𐑥𐑼~·𐑐𐑪𐑑𐑼! 𐑿 𐑸 𐑩 𐑥𐑲𐑯𐑼, 𐑯 𐑨𐑟 𐑕𐑳𐑗, 𐑿 𐑢𐑦𐑤 𐑴𐑯𐑤𐑦 𐑚𐑰 𐑩𐑤𐑬𐑛 𐑑 𐑥𐑱𐑒 \emph{𐑮𐑰𐑟𐑩𐑯𐑩𐑚𐑩𐑤} 𐑢𐑦𐑞𐑛𐑮𐑷𐑩𐑤𐑟 𐑓𐑮𐑪𐑥—”

“𐑲 𐑨𐑥 \emph{𐑷𐑤 𐑩𐑚𐑬𐑑} 𐑮𐑰𐑟𐑩𐑯𐑩𐑚𐑩𐑤! 𐑲 𐑨𐑥 𐑑𐑴𐑑𐑩𐑤𐑦 𐑪𐑯 𐑚𐑹𐑛 𐑢𐑦𐑞 𐑓𐑦𐑕𐑒𐑩𐑤 𐑐𐑮𐑵𐑛𐑩𐑯𐑕 𐑯 𐑦𐑥𐑐𐑳𐑤𐑕 𐑒𐑩𐑯𐑑𐑮𐑴𐑤! 𐑚𐑳𐑑 𐑲 \emph{𐑛𐑦𐑛} 𐑕𐑰 𐑕𐑳𐑥 𐑔𐑦𐑙𐑟 𐑪𐑯 𐑞 𐑢𐑱 𐑣𐑽 𐑢𐑦𐑗 𐑢𐑫𐑛 𐑒𐑪𐑯𐑕𐑑𐑦𐑑𐑿𐑑 \emph{𐑕𐑧𐑯𐑕𐑩𐑚𐑩𐑤, 𐑜𐑮𐑴𐑯-𐑳𐑐} 𐑐𐑻𐑗𐑩𐑕𐑩𐑟…”

·𐑣𐑨𐑮𐑦 𐑤𐑪𐑒𐑑 𐑜𐑱𐑟𐑩𐑟 𐑢𐑦𐑞 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑦𐑯𐑜𐑱𐑡𐑦𐑙 𐑦𐑯 𐑩 𐑕𐑲𐑤𐑩𐑯𐑑 𐑕𐑑𐑺𐑦𐑙 𐑒𐑪𐑯𐑑𐑧𐑕𐑑.

“𐑤𐑲𐑒 𐑢𐑪𐑑?” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛 𐑓𐑲𐑯𐑩𐑤𐑦.

“𐑑𐑮𐑳𐑙𐑒𐑕 𐑣𐑵𐑟 𐑦𐑯𐑕𐑲𐑛𐑟 𐑣𐑴𐑤𐑛 𐑥𐑹 𐑞𐑨𐑯 𐑞𐑺 𐑬𐑑𐑕𐑲𐑛𐑟?”

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑓𐑱𐑕 𐑜𐑮𐑵 𐑕𐑑𐑻𐑯. “𐑞𐑴𐑟 𐑸 \emph{𐑝𐑧𐑮𐑦} 𐑦𐑒𐑕𐑐𐑧𐑯𐑕𐑦𐑝, ·𐑥𐑼~·𐑐𐑪𐑑𐑼!”

“𐑘𐑧𐑕, 𐑚𐑳𐑑—” ·𐑣𐑨𐑮𐑦 𐑐𐑤𐑰𐑛𐑩𐑛. “𐑲'𐑥 𐑖𐑫𐑼 𐑞𐑨𐑑 𐑢𐑧𐑯 𐑲'𐑥 𐑩𐑯 𐑨𐑛𐑳𐑤𐑑 𐑲'𐑤 𐑢𐑪𐑯𐑑 𐑢𐑳𐑯. 𐑯 𐑲 \emph{𐑒𐑨𐑯} 𐑩𐑓𐑹𐑛 𐑢𐑳𐑯. 𐑤𐑪𐑡𐑦𐑒𐑤𐑦, 𐑦𐑑 𐑢𐑫𐑛 𐑥𐑱𐑒 𐑡𐑳𐑕𐑑 𐑨𐑟 𐑥𐑳𐑗 𐑕𐑧𐑯𐑕 𐑑 𐑚𐑲 𐑦𐑑 𐑯𐑬 𐑦𐑯𐑕𐑑𐑧𐑛 𐑝 𐑤𐑱𐑑𐑼, 𐑯 𐑜𐑧𐑑 𐑞 𐑿𐑕 𐑝 𐑦𐑑 𐑮𐑲𐑑 𐑩𐑢𐑱. 𐑦𐑑'𐑕 𐑞 𐑕𐑱𐑥 𐑥𐑳𐑯𐑦 𐑲𐑞𐑼 𐑢𐑱, 𐑮𐑲𐑑? 𐑲 𐑥𐑰𐑯, 𐑲 \emph{𐑢𐑫𐑛} 𐑢𐑪𐑯𐑑 𐑩 𐑜𐑫𐑛 𐑢𐑳𐑯, 𐑢𐑦𐑞 \emph{𐑤𐑪𐑑𐑕} 𐑝 𐑮𐑵𐑥 𐑦𐑯𐑕𐑲𐑛, 𐑜𐑫𐑛 𐑦𐑯𐑳𐑓 𐑞𐑨𐑑 𐑲 𐑢𐑫𐑛𐑩𐑯𐑑 𐑣𐑨𐑓 𐑑 𐑡𐑳𐑕𐑑 𐑜𐑧𐑑 𐑩 𐑚𐑧𐑑𐑼 𐑢𐑳𐑯 𐑤𐑱𐑑𐑼…” ·𐑣𐑨𐑮𐑦 𐑑𐑮𐑱𐑤𐑛 𐑪𐑓 𐑣𐑴𐑐𐑓𐑩𐑤𐑦.

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑜𐑱𐑟 𐑛𐑦𐑛𐑩𐑯𐑑 𐑢𐑱𐑝𐑼. “𐑯 𐑡𐑳𐑕𐑑 𐑢𐑪𐑑 𐑢𐑫𐑛 𐑿 \emph{𐑒𐑰𐑐} 𐑦𐑯 𐑩 𐑑𐑮𐑳𐑙𐑒 𐑤𐑲𐑒 𐑞𐑨𐑑, ·𐑥𐑼~·𐑐𐑪𐑑𐑼—”

“·𐑚𐑫𐑒𐑕.”

“𐑝 𐑒𐑹𐑕,” 𐑕𐑲𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤.

“𐑿 𐑖𐑫𐑛 𐑣𐑨𐑝 𐑑𐑴𐑤𐑛 𐑥𐑰 \emph{𐑥𐑳𐑗 𐑻𐑤𐑽} 𐑞𐑨𐑑 𐑕𐑹𐑑 𐑝 𐑥𐑨𐑡𐑦𐑒 𐑲𐑑𐑩𐑥 𐑦𐑜𐑟𐑦𐑕𐑑𐑩𐑛! 𐑯 𐑞𐑨𐑑 𐑲 𐑒𐑫𐑛 𐑩𐑓𐑹𐑛 𐑢𐑳𐑯! 𐑯𐑬 𐑥𐑲 𐑓𐑭𐑞𐑼 𐑯 𐑲 𐑸 𐑜𐑴𐑦𐑙 𐑑 𐑣𐑨𐑓 𐑑 𐑕𐑐𐑧𐑯𐑛 𐑞 𐑯𐑧𐑒𐑕𐑑 𐑑𐑵 𐑛𐑱𐑟 \emph{𐑓𐑮𐑨𐑯𐑑𐑦𐑒𐑤𐑦} 𐑣𐑦𐑑𐑦𐑙 𐑳𐑐 𐑷𐑤 𐑞 𐑕𐑱𐑒𐑪𐑯𐑛-𐑣𐑨𐑯𐑛 𐑚𐑫𐑒𐑖𐑪𐑐𐑕 𐑓 𐑴𐑤𐑛 𐑑𐑧𐑒𐑕𐑑𐑚𐑫𐑒𐑕, 𐑕𐑴 𐑲 𐑒𐑨𐑯 𐑣𐑨𐑝 𐑩 𐑛𐑰𐑕𐑩𐑯𐑑 𐑕𐑲𐑩𐑯𐑕 𐑤𐑲𐑚𐑮𐑼𐑦 𐑢𐑦𐑞 𐑥𐑰 𐑨𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕—𐑯 𐑥𐑱𐑚𐑰 𐑩 𐑕𐑥𐑷𐑤 𐑕𐑲𐑩𐑯𐑕-𐑓𐑦𐑒𐑖𐑩𐑯 𐑒𐑩𐑤𐑧𐑒𐑖𐑩𐑯, 𐑦𐑓 𐑲 𐑒𐑨𐑯 𐑩𐑕𐑧𐑥𐑚𐑩𐑤 𐑕𐑳𐑥𐑔𐑦𐑙 𐑛𐑰𐑕𐑩𐑯𐑑 𐑬𐑑 𐑝 𐑞 𐑚𐑸𐑜𐑦𐑯 𐑚𐑦𐑯𐑟. 𐑹 𐑚𐑧𐑑𐑼 𐑘𐑧𐑑, 𐑲'𐑤 𐑥𐑱𐑒 𐑞 𐑛𐑰𐑤 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑕𐑢𐑰𐑑𐑼 𐑓 𐑿, 𐑴𐑒𐑱? 𐑡𐑳𐑕𐑑 𐑤𐑧𐑑 𐑥𐑰 𐑚𐑲—”

“\emph{·𐑥𐑼~·𐑐𐑪𐑑𐑼!} 𐑿 𐑔𐑦𐑙𐑒 𐑿 𐑒𐑨𐑯 \emph{𐑚𐑮𐑲𐑚} 𐑥𐑰?”

“𐑢𐑪𐑑? \emph{𐑯𐑴!} 𐑯𐑪𐑑 𐑤𐑲𐑒 𐑞𐑨𐑑! 𐑲'𐑥 𐑕𐑱𐑦𐑙, ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 𐑒𐑨𐑯 𐑒𐑰𐑐 𐑕𐑳𐑥 𐑝 𐑞 𐑚𐑫𐑒𐑕 𐑲 𐑚𐑮𐑦𐑙, 𐑦𐑓 𐑿 𐑔𐑦𐑙𐑒 𐑞𐑨𐑑 𐑧𐑯𐑦 𐑝 𐑞𐑧𐑥 𐑢𐑫𐑛 𐑥𐑱𐑒 𐑜𐑫𐑛 𐑩𐑛𐑦𐑖𐑩𐑯𐑟 𐑑 𐑞 𐑤𐑲𐑚𐑮𐑼𐑦. 𐑲'𐑥 𐑜𐑴𐑦𐑙 𐑑 𐑚𐑰 𐑜𐑧𐑑𐑦𐑙 𐑞𐑧𐑥 𐑗𐑰𐑐, 𐑯 \emph{𐑲} 𐑡𐑳𐑕𐑑 𐑢𐑪𐑯𐑑 𐑑 𐑣𐑨𐑝 𐑞𐑧𐑥 𐑼𐑬𐑯𐑛 𐑕𐑳𐑥𐑢𐑺 𐑹 𐑳𐑞𐑼. 𐑦𐑑'𐑕 𐑴𐑒𐑱 𐑑 𐑚𐑮𐑲𐑚 𐑐𐑰𐑐𐑩𐑤 𐑢𐑦𐑞 \emph{𐑚𐑫𐑒𐑕}, 𐑮𐑲𐑑? 𐑞𐑨𐑑'𐑕 𐑩—”

“·𐑓𐑨𐑥𐑤𐑦 𐑑𐑮𐑩𐑛𐑦𐑖𐑩𐑯.”

“𐑘𐑧𐑕, 𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦.”

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑚𐑪𐑛𐑦 𐑕𐑰𐑥𐑛 𐑑 𐑕𐑤𐑳𐑥𐑐, 𐑞 𐑖𐑴𐑤𐑛𐑼𐑟 𐑤𐑴𐑼𐑦𐑙 𐑢𐑦𐑞𐑦𐑯 𐑣𐑻 𐑚𐑤𐑨𐑒 𐑮𐑴𐑚𐑟. “𐑲 𐑒𐑨𐑯𐑪𐑑 𐑛𐑦𐑯𐑲 𐑞 𐑕𐑧𐑯𐑕 𐑝 𐑘𐑹 𐑢𐑻𐑛𐑟, 𐑞𐑴 𐑲 𐑥𐑳𐑗 𐑢𐑦𐑖 𐑲 𐑒𐑫𐑛. 𐑲 𐑢𐑦𐑤 𐑩𐑤𐑬 𐑿 𐑑 𐑢𐑦𐑞𐑛𐑮𐑷 𐑩𐑯 𐑩𐑛𐑦𐑖𐑩𐑯𐑩𐑤 𐑣𐑳𐑯𐑛𐑮𐑩𐑛 ·𐑜𐑨𐑤𐑾𐑯𐑟, ·𐑥𐑼~·𐑐𐑪𐑑𐑼.” 𐑖𐑰 𐑕𐑲𐑛 𐑩𐑜𐑱𐑯. “𐑲 \emph{𐑯𐑴} 𐑞𐑨𐑑 𐑲 𐑖𐑨𐑤 𐑮𐑦𐑜𐑮𐑧𐑑 𐑞𐑦𐑕, 𐑯 𐑲 𐑨𐑥 𐑛𐑵𐑦𐑙 𐑦𐑑 𐑧𐑯𐑦𐑢𐑱.”

“𐑞𐑨𐑑'𐑕 𐑞 𐑕𐑐𐑦𐑮𐑦𐑑! 𐑯 𐑛𐑳𐑟 𐑩 '𐑥𐑴𐑒𐑕𐑒𐑦𐑯 𐑐𐑬𐑗' 𐑛𐑵 𐑢𐑪𐑑 𐑲 𐑔𐑦𐑙𐑒 𐑦𐑑 𐑛𐑳𐑟?”

“𐑦𐑑 𐑒𐑭𐑯𐑑 𐑛𐑵 𐑨𐑟 𐑥𐑳𐑗 𐑨𐑟 𐑩 𐑑𐑮𐑳𐑙𐑒,” 𐑞 𐑢𐑦𐑗 𐑕𐑧𐑛 𐑢𐑦𐑞 𐑝𐑦𐑟𐑩𐑚𐑩𐑤 𐑮𐑦𐑤𐑳𐑒𐑑𐑩𐑯𐑕, “𐑚𐑳𐑑…𐑩 𐑥𐑴𐑒𐑕𐑒𐑦𐑯 𐑐𐑬𐑗 𐑢𐑦𐑞 𐑩 ·𐑮𐑦𐑑𐑮𐑰𐑝𐑩𐑤 ·𐑗𐑸𐑥 𐑯 ·𐑳𐑯𐑛𐑦𐑑𐑧𐑒𐑑𐑩𐑚𐑩𐑤 ·𐑦𐑒𐑕𐑑𐑧𐑯𐑖𐑩𐑯 ·𐑗𐑸𐑥 𐑒𐑨𐑯 𐑣𐑴𐑤𐑛 𐑩 𐑯𐑳𐑥𐑚𐑼 𐑝 𐑲𐑑𐑩𐑥𐑟 𐑩𐑯𐑑𐑦𐑤 𐑞𐑱 𐑸 𐑒𐑷𐑤𐑛 𐑓𐑹𐑔 𐑚𐑲 𐑞 𐑢𐑳𐑯 𐑣𐑵 𐑦𐑥𐑐𐑤𐑱𐑕𐑑 𐑞𐑧𐑥—”

“𐑘𐑧𐑕! 𐑲 𐑛𐑧𐑓𐑦𐑯𐑦𐑑𐑤𐑦 𐑯𐑰𐑛 𐑢𐑳𐑯 𐑝 𐑞𐑴𐑟 𐑑𐑵! 𐑦𐑑 𐑢𐑫𐑛 𐑚𐑰 𐑤𐑲𐑒 𐑞 𐑕𐑵𐑐𐑼 𐑚𐑧𐑤𐑑 𐑐𐑨𐑒 𐑝 𐑳𐑤𐑑𐑦𐑥𐑩𐑑 𐑷𐑕𐑩𐑥𐑯𐑩𐑕! 𐑚𐑨𐑑𐑥𐑩𐑯'𐑟 𐑿𐑑𐑦𐑤𐑦𐑑𐑦 𐑚𐑧𐑤𐑑 𐑝 𐑣𐑴𐑤𐑛𐑦𐑙! 𐑯𐑧𐑝𐑼 𐑥𐑲𐑯𐑛 𐑥𐑲 ·𐑕𐑢𐑦𐑕 𐑸𐑥𐑦 𐑯𐑲𐑓, 𐑲 𐑒𐑫𐑛 𐑒𐑨𐑮𐑦 𐑩 𐑣𐑴𐑤 𐑑𐑵𐑤 𐑕𐑧𐑑 𐑦𐑯 𐑞𐑺! 𐑹 \emph{𐑚𐑫𐑒𐑕}! 𐑲 𐑒𐑫𐑛 𐑣𐑨𐑝 𐑞 𐑑𐑪𐑐 𐑔𐑮𐑰 𐑚𐑫𐑒𐑕 𐑲 𐑢𐑪𐑟 𐑮𐑰𐑛𐑦𐑙 𐑪𐑯 𐑥𐑰 𐑨𐑑 𐑷𐑤 𐑑𐑲𐑥𐑟, 𐑯 𐑡𐑳𐑕𐑑 𐑐𐑫𐑤 𐑢𐑳𐑯 𐑬𐑑 𐑧𐑯𐑦𐑢𐑺! 𐑲'𐑤 𐑯𐑧𐑝𐑼 𐑣𐑨𐑓 𐑑 𐑢𐑱𐑕𐑑 𐑩𐑯𐑳𐑞𐑼 𐑥𐑦𐑯𐑦𐑑 𐑝 𐑥𐑲 𐑤𐑲𐑓! 𐑢𐑪𐑑 𐑛𐑵 𐑿 𐑕𐑱, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤? 𐑦𐑑'𐑕 𐑓 𐑞 𐑕𐑱𐑒 𐑝 𐑗𐑦𐑤𐑛𐑮𐑩𐑯'𐑟 𐑮𐑰𐑛𐑦𐑙, 𐑞 𐑚𐑧𐑕𐑑 𐑝 𐑷𐑤 𐑐𐑪𐑕𐑩𐑚𐑩𐑤 𐑒𐑷𐑟𐑩𐑟.”

“…𐑲 𐑕𐑩𐑐𐑴𐑟 𐑿 𐑥𐑱 𐑨𐑛 𐑩𐑯𐑳𐑞𐑼 𐑑𐑧𐑯 ·𐑜𐑨𐑤𐑾𐑯𐑟.”

·𐑜𐑮𐑦𐑐𐑣𐑫𐑒 𐑢𐑪𐑟 𐑓𐑱𐑝𐑼𐑦𐑙 ·𐑣𐑨𐑮𐑦 𐑢𐑦𐑞 𐑩 𐑜𐑱𐑟 𐑝 𐑓𐑮𐑨𐑙𐑒 𐑮𐑦𐑕𐑐𐑧𐑒𐑑, 𐑐𐑪𐑕𐑩𐑚𐑤𐑦 𐑰𐑝𐑩𐑯 𐑬𐑑𐑮𐑲𐑑 𐑨𐑛𐑥𐑼𐑱𐑖𐑩𐑯.

“𐑯 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑕𐑐𐑧𐑯𐑛𐑦𐑙 𐑥𐑳𐑯𐑦, 𐑤𐑲𐑒 𐑿 𐑥𐑧𐑯𐑖𐑩𐑯𐑛 𐑻𐑤𐑽. 𐑲 𐑔𐑦𐑙𐑒 𐑲 𐑒𐑨𐑯 𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑕𐑰𐑦𐑙 𐑢𐑳𐑯 𐑹 𐑑𐑵 𐑳𐑞𐑼 𐑔𐑦𐑙𐑟 𐑲 𐑥𐑲𐑑 𐑢𐑪𐑯𐑑 𐑑 𐑕𐑑𐑹 𐑦𐑯 𐑞𐑨𐑑 𐑐𐑬𐑗.”

“\emph{𐑛𐑴𐑯𐑑 𐑐𐑫𐑖 𐑦𐑑, ·𐑥𐑼~·𐑐𐑪𐑑𐑼.}”

“𐑚𐑳𐑑 𐑴, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑢𐑲 𐑮𐑱𐑯 𐑪𐑯 𐑥𐑲 𐑐𐑼𐑱𐑛? 𐑖𐑫𐑼𐑤𐑦 𐑞𐑦𐑕 𐑦𐑟 𐑩 \emph{𐑣𐑨𐑐𐑦} 𐑛𐑱, 𐑢𐑧𐑯 𐑲 𐑛𐑦𐑕𐑒𐑳𐑝𐑼 𐑷𐑤 𐑔𐑦𐑙𐑟 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑓 𐑞 𐑓𐑻𐑕𐑑 𐑑𐑲𐑥! 𐑢𐑲 𐑨𐑒𐑑 𐑞 𐑐𐑸𐑑 𐑝 𐑞 𐑜𐑮𐑳𐑥𐑐𐑦 𐑜𐑮𐑴𐑯-𐑳𐑐 𐑢𐑧𐑯 𐑦𐑯𐑕𐑑𐑧𐑛 𐑿 𐑒𐑫𐑛 𐑕𐑥𐑲𐑤 𐑯 𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑘𐑹 𐑴𐑯 𐑦𐑯𐑩𐑕𐑩𐑯𐑑 𐑗𐑲𐑤𐑛𐑣𐑫𐑛, 𐑢𐑪𐑗𐑦𐑙 𐑞 𐑤𐑫𐑒 𐑝 𐑛𐑦𐑤𐑲𐑑 𐑩𐑐𐑪𐑯 𐑥𐑲 𐑘𐑳𐑙 𐑓𐑱𐑕 𐑨𐑟 𐑲 𐑚𐑲 𐑩 𐑓𐑿 𐑑𐑶𐑟 𐑿𐑟𐑦𐑙 𐑩𐑯 𐑦𐑯𐑕𐑦𐑜𐑯𐑦𐑓𐑦𐑒𐑩𐑯𐑑 𐑓𐑮𐑨𐑒𐑖𐑩𐑯 𐑝 𐑞 𐑢𐑧𐑤𐑔 𐑞𐑨𐑑 𐑲 𐑻𐑯𐑛 𐑚𐑲 𐑛𐑦𐑓𐑰𐑑𐑦𐑙 𐑞 𐑥𐑴𐑕𐑑 𐑑𐑧𐑮𐑦𐑚𐑩𐑤 𐑢𐑦𐑟𐑼𐑛 ·𐑚𐑮𐑦𐑑𐑩𐑯 𐑣𐑨𐑟 𐑧𐑝𐑼 𐑯𐑴𐑯, 𐑯𐑪𐑑 𐑞𐑨𐑑 𐑲'𐑥 𐑩𐑒𐑿𐑟𐑦𐑙 𐑿 𐑝 𐑚𐑰𐑦𐑙 𐑳𐑯𐑜𐑮𐑱𐑑𐑓𐑩𐑤 𐑹 𐑧𐑯𐑦𐑔𐑦𐑙, 𐑚𐑳𐑑 𐑕𐑑𐑦𐑤, 𐑢𐑪𐑑 𐑸 𐑩 𐑓𐑿 𐑑𐑶𐑟 𐑒𐑩𐑥𐑐𐑺𐑛 𐑑 𐑞𐑨𐑑?”

“\emph{𐑿,}” 𐑜𐑮𐑬𐑤𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. 𐑞𐑺 𐑢𐑪𐑟 𐑩 𐑤𐑫𐑒 𐑪𐑯 𐑣𐑻 𐑓𐑱𐑕 𐑕𐑴 𐑓𐑽𐑕𐑩𐑥 𐑯 𐑑𐑧𐑮𐑦𐑚𐑩𐑤 𐑞𐑨𐑑 ·𐑣𐑨𐑮𐑦 𐑕𐑒𐑢𐑰𐑒𐑑 𐑯 𐑕𐑑𐑧𐑐𐑑 𐑚𐑨𐑒, 𐑯𐑪𐑒𐑦𐑙 𐑴𐑝𐑼 𐑩 𐑐𐑲𐑤 𐑝 𐑜𐑴𐑤𐑛 𐑒𐑶𐑯𐑟 𐑢𐑦𐑞 𐑩 𐑜𐑮𐑱𐑑 𐑡𐑦𐑙𐑜𐑩𐑤𐑦𐑙 𐑯𐑶𐑟 𐑯 𐑕𐑐𐑮𐑷𐑤𐑦𐑙 𐑚𐑨𐑒𐑢𐑼𐑛𐑟 𐑦𐑯𐑑𐑵 𐑩 𐑣𐑰𐑐 𐑝 𐑥𐑳𐑯𐑦. ·𐑜𐑮𐑦𐑐𐑣𐑫𐑒 𐑕𐑲𐑛 𐑯 𐑐𐑫𐑑 𐑩 𐑐𐑭𐑥 𐑴𐑝𐑼 𐑣𐑦𐑟 𐑓𐑱𐑕. “𐑲 𐑢𐑫𐑛 𐑚𐑰 𐑛𐑵𐑦𐑙 𐑩 𐑜𐑮𐑱𐑑 𐑕𐑻𐑝𐑦𐑕 𐑑 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 ·𐑚𐑮𐑦𐑑𐑩𐑯, ·𐑥𐑼~·𐑐𐑪𐑑𐑼, 𐑦𐑓 𐑲 𐑤𐑪𐑒𐑑 𐑿 𐑦𐑯 𐑞𐑦𐑕 𐑝𐑷𐑤𐑑 𐑯 𐑤𐑧𐑓𐑑 𐑿 𐑣𐑽.”

𐑯 𐑞𐑱 𐑤𐑧𐑓𐑑 𐑢𐑦𐑞𐑬𐑑 𐑧𐑯𐑦 𐑥𐑹 𐑑𐑮𐑳𐑚𐑩𐑤.

%  LocalWords:  eaps fundie ki
