\chapter*{𐑐𐑮𐑧𐑓𐑦𐑕}
% from https://www.hpmor.com/chapter/1
% 𐑞𐑦𐑕 𐑦𐑟 𐑯𐑪𐑑 𐑩 𐑕𐑑𐑮𐑦𐑒𐑑 𐑕𐑦𐑙𐑜𐑩𐑤-𐑐𐑶𐑯𐑑-𐑝-𐑛𐑦𐑐𐑸𐑗𐑼 𐑓𐑦𐑒—𐑞𐑺 𐑦𐑜𐑟𐑦𐑕𐑑𐑕 𐑩 𐑐𐑮𐑲𐑥𐑼𐑦 𐑐𐑶𐑯𐑑 𐑝 𐑛𐑦𐑐𐑸𐑗𐑼, 𐑨𐑑 𐑕𐑳𐑥 𐑐𐑶𐑯𐑑 𐑦𐑯 𐑞 𐑐𐑭𐑕𐑑, 𐑚𐑳𐑑 𐑷𐑤𐑕𐑴 𐑳𐑞𐑼 𐑷𐑤𐑑𐑼𐑱𐑖𐑩𐑯𐑟. 𐑞 𐑚𐑧𐑕𐑑 𐑑𐑻𐑥 𐑲'𐑝 𐑣𐑻𐑛 𐑓 𐑞𐑦𐑕 𐑓𐑦𐑒 𐑦𐑟 “𐑐𐑨𐑮𐑩𐑤𐑧𐑤 𐑿𐑯𐑦𐑝𐑻𐑕”.

𐑞 𐑑𐑧𐑒𐑕𐑑 𐑒𐑩𐑯𐑑𐑱𐑯𐑟 𐑥𐑧𐑯𐑦 𐑒𐑤𐑵𐑟: 𐑪𐑚𐑝𐑾𐑕 𐑒𐑤𐑵𐑟, 𐑯𐑪𐑑-𐑕𐑴-𐑪𐑚𐑝𐑾𐑕 𐑒𐑤𐑵𐑟, 𐑑𐑮𐑵𐑤𐑦 𐑩𐑚𐑕𐑒𐑘𐑫𐑼 𐑣𐑦𐑯𐑑𐑕 𐑢𐑦𐑗 𐑲 𐑢𐑪𐑟 𐑖𐑪𐑒𐑑 𐑑 𐑕𐑰 𐑕𐑳𐑥 𐑮𐑰𐑛𐑼𐑟 𐑕𐑩𐑒𐑕𐑧𐑕𐑓𐑩𐑤𐑦 𐑛𐑰𐑒𐑴𐑛, 𐑯 𐑥𐑨𐑕𐑦𐑝 𐑧𐑝𐑦𐑛𐑩𐑯𐑕 𐑤𐑧𐑓𐑑 𐑬𐑑 𐑦𐑯 𐑐𐑤𐑱𐑯 𐑕𐑲𐑑. 𐑞𐑦𐑕 𐑦𐑟 𐑩 𐑮𐑨𐑖𐑩𐑯𐑩𐑤𐑦𐑕𐑑 𐑕𐑑𐑹𐑦; 𐑦𐑑𐑕 𐑥𐑦𐑕𐑑𐑼𐑦𐑟 𐑸 𐑕𐑪𐑤𐑝𐑩𐑚𐑩𐑤, 𐑯 𐑥𐑧𐑯𐑑 𐑑 𐑚𐑰 𐑕𐑪𐑤𐑝𐑛.

𐑞 𐑐𐑱𐑕𐑦𐑙 𐑝 𐑞 𐑕𐑑𐑹𐑦 𐑦𐑟 𐑞𐑨𐑑 𐑝 𐑕𐑽𐑾𐑤 𐑓𐑦𐑒𐑖𐑩𐑯, 𐑲𐑰, 𐑞𐑨𐑑 𐑝 𐑩 𐑑𐑰𐑝𐑰 𐑖𐑴 𐑮𐑳𐑯𐑦𐑙 𐑓 𐑩 𐑐𐑮𐑰𐑛𐑦𐑑𐑻𐑥𐑦𐑯𐑛 𐑯𐑳𐑥𐑚𐑼 𐑝 𐑕𐑰𐑟𐑩𐑯𐑟, 𐑣𐑵𐑟 𐑧𐑐𐑦𐑕𐑴𐑛𐑟 𐑸 𐑦𐑯𐑛𐑦𐑝𐑦𐑡𐑵𐑩𐑤𐑦 𐑐𐑤𐑪𐑑𐑩𐑛 𐑚𐑳𐑑 𐑢𐑦𐑞 𐑩𐑯 𐑴𐑝𐑼𐑷𐑤 𐑸𐑒 𐑚𐑦𐑤𐑛𐑦𐑙 𐑑 𐑩 𐑓𐑲𐑯𐑩𐑤 𐑒𐑩𐑯𐑒𐑤𐑵𐑠𐑩𐑯.

% The story has been corrected to British English up to Ch. 17, and further Britpicking is currently in progress (see the /HPMOR subreddit).

𐑷𐑤 𐑕𐑲𐑩𐑯𐑕 𐑥𐑧𐑯𐑖𐑩𐑯𐑛 𐑦𐑟 𐑮𐑾𐑤 𐑕𐑲𐑩𐑯𐑕. 𐑚𐑳𐑑 𐑐𐑤𐑰𐑟 𐑒𐑰𐑐 𐑦𐑯 𐑥𐑲𐑯𐑛 𐑞𐑨𐑑, 𐑚𐑦𐑘𐑪𐑯𐑛 𐑞 𐑮𐑧𐑤𐑥 𐑝 𐑕𐑲𐑩𐑯𐑕, 𐑞 𐑝𐑿𐑟 𐑝 𐑞 𐑒𐑨𐑮𐑩𐑒𐑑𐑼𐑟 𐑥𐑱 𐑯𐑪𐑑 𐑚𐑰 𐑞𐑴𐑟 𐑝 𐑞 𐑷𐑔𐑼. 𐑯𐑪𐑑 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑞 𐑐𐑮𐑴𐑑𐑨𐑜𐑩𐑯𐑦𐑕𐑑 𐑛𐑳𐑟 𐑦𐑟 𐑩 𐑤𐑧𐑕𐑩𐑯 𐑦𐑯 𐑢𐑦𐑟𐑛𐑩𐑥, 𐑯 𐑩𐑛𐑝𐑲𐑕 𐑪𐑓𐑼𐑛 𐑚𐑲 𐑛𐑸𐑒𐑼 𐑒𐑨𐑮𐑩𐑒𐑑𐑼𐑟 𐑥𐑱 𐑚𐑰 𐑳𐑯𐑑𐑮𐑳𐑕𐑑𐑢𐑻𐑞𐑦 𐑹 𐑛𐑱𐑯𐑡𐑼𐑩𐑕𐑤𐑦 𐑛𐑳𐑚𐑩𐑤-𐑧𐑡𐑛.

\chapter*{𐑷𐑔𐑼'𐑟 𐑦𐑯𐑑𐑮𐑩𐑛𐑳𐑒𐑖𐑩𐑯}
% from https://www.hpmor.com/chapter/22

\section*{𐑕𐑳𐑥𐑔𐑦𐑙, 𐑕𐑳𐑥𐑢𐑺, 𐑕𐑳𐑥𐑢𐑧𐑯, 𐑥𐑳𐑕𐑑 𐑣𐑨𐑝 𐑣𐑨𐑐𐑩𐑯𐑛 𐑛𐑦𐑓𐑼𐑩𐑯𐑑𐑤𐑦…}

\begin{itemize}
\item \textsc{·𐑐𐑩𐑑𐑿𐑯𐑾 ·𐑧𐑝𐑩𐑯𐑟} 𐑥𐑨𐑮𐑦𐑛 ·𐑥𐑲𐑒𐑩𐑤 ·𐑝𐑧𐑮𐑟, 𐑩 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑝 ·𐑚𐑲𐑴𐑒𐑧𐑥𐑦𐑕𐑑𐑮𐑦 𐑨𐑑 ·𐑪𐑒𐑕𐑓𐑼𐑛.
\item \textsc{𐑣𐑨𐑮𐑦 ·𐑡𐑱𐑥𐑟 ·𐑐𐑪𐑑𐑼-·𐑧𐑝𐑩𐑯𐑟-·𐑝𐑧𐑮𐑟} 𐑜𐑮𐑵 𐑳𐑐 𐑦𐑯 𐑩 𐑣𐑬𐑕 𐑓𐑦𐑤𐑛 𐑑 𐑞 𐑚𐑮𐑦𐑥 𐑢𐑦𐑞 𐑚𐑫𐑒𐑕. 𐑣𐑰 𐑢𐑳𐑯𐑕 𐑚𐑦𐑑 𐑩 𐑥𐑨𐑔 𐑑𐑰𐑗𐑼 𐑣𐑵 𐑛𐑦𐑛𐑩𐑯𐑑 𐑯𐑴 𐑢𐑪𐑑 𐑩 𐑤𐑪𐑜𐑼𐑦𐑞𐑩𐑥 𐑢𐑪𐑟. 𐑣𐑰'𐑟 𐑮𐑰𐑛 \emph{·𐑜𐑻︀𐑛𐑩𐑤, ·𐑧𐑖𐑼, ·𐑚𐑭𐑒} 𐑯 \emph{·𐑡𐑳𐑡𐑥𐑩𐑯𐑑 ·𐑳𐑯𐑛𐑼 ·𐑳𐑯𐑕𐑻𐑑𐑩𐑯𐑑𐑦: 𐑣𐑘𐑫𐑼𐑦𐑕𐑑𐑦𐑒𐑕 𐑯 ·𐑚𐑲𐑩𐑕𐑩𐑟} 𐑯 𐑝𐑪𐑤𐑿𐑥 𐑢𐑳𐑯 𐑝 \emph{𐑞 ·𐑓𐑲𐑯𐑥𐑩𐑯 ·𐑤𐑧𐑒𐑗𐑼𐑟 𐑪𐑯 ·𐑓𐑦𐑟𐑦𐑒𐑕}. 𐑯 𐑛𐑦𐑕𐑐𐑲𐑑 𐑢𐑪𐑑 𐑧𐑝𐑮𐑦𐑢𐑳𐑯 𐑣𐑵'𐑟 𐑥𐑧𐑑 𐑣𐑦𐑥 𐑕𐑰𐑥𐑟 𐑑 𐑓𐑽, 𐑣𐑰 𐑛𐑳𐑟𐑩𐑯𐑑 𐑢𐑪𐑯𐑑 𐑑 𐑚𐑦𐑒𐑳𐑥 𐑞 𐑯𐑧𐑒𐑕𐑑 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛. 𐑣𐑰 𐑢𐑪𐑟 𐑮𐑱𐑟𐑛 𐑚𐑧𐑑𐑼 𐑞𐑨𐑯 𐑞𐑨𐑑. 𐑣𐑰 𐑢𐑪𐑯𐑑𐑕 𐑑 𐑛𐑦𐑕𐑒𐑳𐑝𐑼 𐑞 𐑤𐑷𐑟 𐑝 𐑥𐑨𐑡𐑦𐑒 𐑯 𐑚𐑦𐑒𐑳𐑥 𐑩 𐑜𐑪𐑛.
\item \textsc{·𐑣𐑼𐑥𐑲𐑩𐑯𐑦 ·𐑜𐑮𐑱𐑯𐑡𐑼} 𐑦𐑟 𐑛𐑵𐑦𐑙 𐑚𐑧𐑑𐑼 𐑞𐑨𐑯 𐑣𐑦𐑥 𐑦𐑯 𐑧𐑝𐑮𐑦 𐑒𐑤𐑭𐑕 𐑦𐑒𐑕𐑧𐑐𐑑 𐑚𐑮𐑵𐑥𐑕𐑑𐑦𐑒 𐑮𐑲𐑛𐑦𐑙.
\item \textsc{·𐑛𐑮𐑱𐑒𐑴 ·𐑥𐑨𐑤𐑓𐑶} 𐑦𐑟 𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦 𐑢𐑪𐑑 𐑿 𐑢𐑫𐑛 𐑦𐑒𐑕𐑐𐑧𐑒𐑑 𐑩𐑯 𐑦𐑤𐑧𐑝𐑩𐑯-𐑘𐑽-𐑴𐑤𐑛 𐑚𐑶 𐑑 𐑚𐑰 𐑤𐑲𐑒 𐑦𐑓 ·𐑛𐑸𐑔 ·𐑝𐑱𐑛𐑼 𐑢𐑻 𐑣𐑦𐑟 𐑛𐑴𐑑𐑦𐑙 𐑓𐑭𐑞𐑼.
\item \textsc{𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑒𐑢𐑦𐑮𐑩𐑤} 𐑦𐑟 𐑤𐑦𐑝𐑦𐑙 𐑣𐑦𐑟 𐑤𐑲𐑓𐑤𐑪𐑙 𐑛𐑮𐑰𐑥 𐑝 𐑑𐑰𐑗𐑦𐑙 ·𐑛𐑦𐑓𐑧𐑯𐑕 ·𐑩𐑜𐑱𐑯𐑕𐑑 𐑞 ·𐑛𐑸𐑒 ·𐑸𐑑𐑕, 𐑹 𐑨𐑟 𐑣𐑰 𐑐𐑮𐑦𐑓𐑻𐑟 𐑑 𐑒𐑷𐑤 𐑣𐑦𐑟 𐑒𐑤𐑭𐑕, ·𐑚𐑨𐑑𐑩𐑤 ·𐑥𐑨𐑡𐑦𐑒. 𐑣𐑦𐑟 𐑕𐑑𐑿𐑛𐑩𐑯𐑑𐑕 𐑸 𐑷𐑤 𐑢𐑳𐑯𐑛𐑼𐑦𐑙 𐑢𐑪𐑑'𐑕 𐑜𐑴𐑦𐑙 𐑑 𐑜𐑴 𐑮𐑪𐑙 𐑢𐑦𐑞 𐑞 ·𐑛𐑦𐑓𐑧𐑯𐑕 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑞𐑦𐑕 𐑑𐑲𐑥.
\item \textsc{·𐑛𐑳𐑥𐑚𐑩𐑤𐑛𐑹} 𐑦𐑟 𐑲𐑞𐑼 𐑦𐑯𐑕𐑱𐑯, 𐑹 𐑐𐑤𐑱𐑦𐑙 𐑕𐑳𐑥 𐑝𐑭𐑕𐑑𐑤𐑦 𐑛𐑰𐑐𐑼 𐑜𐑱𐑥 𐑢𐑦𐑗 𐑦𐑯𐑝𐑪𐑤𐑝𐑛 𐑕𐑧𐑑𐑦𐑙 𐑓𐑲𐑼 𐑑 𐑩 𐑗𐑦𐑒𐑦𐑯.
\item \textsc{·𐑥𐑦𐑯𐑻𐑝𐑩 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤} 𐑯𐑰𐑛𐑟 𐑑 𐑜𐑴 𐑪𐑓 𐑕𐑳𐑥𐑢𐑺 𐑐𐑮𐑲𐑝𐑩𐑑 𐑯 𐑕𐑒𐑮𐑰𐑥 𐑓 𐑩 𐑢𐑲𐑤.
\end{itemize}

% \begin{center}
% Presenting:
%
% \textsc{Harry Potter and the Methods of Rationality}
%
% You ain't guessin' where this one's going.
% \end{center}

\section*{𐑕𐑳𐑥 𐑯𐑴𐑑𐑕}
𐑞 𐑩𐑐𐑦𐑯𐑘𐑩𐑯𐑟 𐑝 𐑒𐑨𐑮𐑩𐑒𐑑𐑼𐑟 𐑦𐑯 𐑞𐑦𐑕 𐑕𐑑𐑹𐑦 𐑸 𐑯𐑪𐑑 𐑯𐑧𐑕𐑦𐑕𐑼𐑦𐑤𐑦 𐑞𐑴𐑟 𐑝 𐑞 𐑷𐑔𐑼. 𐑢𐑪𐑑 𐑢𐑹𐑥!𐑣𐑨𐑮𐑦 𐑔𐑦𐑙𐑒𐑕 𐑦𐑟 \emph{𐑪𐑓𐑑𐑩𐑯} 𐑥𐑧𐑯𐑑 𐑨𐑟 𐑩 𐑜𐑫𐑛 𐑐𐑨𐑑𐑼𐑯 𐑑 𐑓𐑪𐑤𐑴, 𐑦𐑕𐑐𐑧𐑖𐑩𐑤𐑦 𐑦𐑓 ·𐑣𐑨𐑮𐑦 𐑔𐑦𐑙𐑒𐑕 𐑩𐑚𐑬𐑑 𐑣𐑬 𐑣𐑰 𐑒𐑨𐑯 𐑕𐑲𐑑 𐑕𐑲𐑩𐑯𐑑𐑦𐑓𐑦𐑒 𐑕𐑑𐑳𐑛𐑦𐑟 𐑑 𐑚𐑨𐑒 𐑳𐑐 𐑩 𐑐𐑼𐑑𐑦𐑒𐑿𐑤𐑼 𐑐𐑮𐑦𐑯𐑕𐑩𐑐𐑩𐑤. 𐑚𐑳𐑑 𐑯𐑪𐑑 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 ·𐑣𐑨𐑮𐑦 𐑛𐑳𐑟 𐑹 𐑔𐑦𐑙𐑒𐑕 𐑦𐑟 𐑩 𐑜𐑫𐑛 𐑲𐑛𐑾. 𐑞𐑨𐑑 𐑢𐑫𐑛𐑩𐑯𐑑 𐑢𐑻𐑒 𐑨𐑟 𐑩 𐑕𐑑𐑹𐑦. 𐑯 𐑞 𐑤𐑧𐑕 𐑢𐑹𐑥 𐑒𐑨𐑮𐑩𐑒𐑑𐑼𐑟 𐑥𐑱 𐑕𐑳𐑥𐑑𐑲𐑥𐑟 𐑣𐑨𐑝 𐑝𐑨𐑤𐑿𐑩𐑚𐑩𐑤 𐑤𐑧𐑕𐑩𐑯𐑟 𐑑 𐑪𐑓𐑼, 𐑚𐑳𐑑 𐑞𐑴𐑟 𐑤𐑧𐑕𐑩𐑯𐑟 𐑥𐑱 𐑷𐑤𐑕𐑴 𐑚𐑰 𐑛𐑱𐑯𐑡𐑼𐑩𐑕𐑤𐑦 𐑛𐑳𐑚𐑩𐑤-𐑧𐑡𐑛.

𐑦𐑓 𐑿 𐑣𐑨𐑝𐑩𐑯𐑑 𐑝𐑦𐑟𐑦𐑑𐑩𐑛 \url{https://hpmor.com}, 𐑛𐑴𐑯𐑑 𐑓𐑼𐑜𐑧𐑑 𐑑 𐑛𐑵 𐑞𐑨𐑑 𐑨𐑑 𐑕𐑳𐑥 𐑐𐑶𐑯𐑑; 𐑳𐑞𐑼𐑢𐑲𐑟 𐑿'𐑤 𐑥𐑦𐑕 𐑬𐑑 𐑪𐑯 𐑞 𐑓𐑨𐑯 𐑸𐑑, 𐑣𐑬 𐑑 𐑤𐑻𐑯 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 ·𐑣𐑨𐑮𐑦 𐑯𐑴𐑟, 𐑯 𐑥𐑹.

𐑦𐑓 𐑿 𐑛𐑴𐑯𐑑 𐑡𐑳𐑕𐑑 𐑦𐑯𐑡𐑶 𐑞𐑦𐑕 𐑓𐑦𐑒, 𐑚𐑳𐑑 𐑤𐑻𐑯 𐑕𐑳𐑥𐑔𐑦𐑙 𐑓𐑮𐑪𐑥 𐑦𐑑, 𐑞𐑧𐑯 𐑐𐑤𐑰𐑟 𐑒𐑩𐑯𐑕𐑦𐑛𐑼 𐑚𐑤𐑪𐑜𐑦𐑙 𐑦𐑑 𐑹 𐑑𐑢𐑰𐑑𐑦𐑙 𐑦𐑑. 𐑩 𐑢𐑻𐑒 𐑤𐑲𐑒 𐑞𐑦𐑕 𐑴𐑯𐑤𐑦 𐑛𐑳𐑟 𐑨𐑟 𐑥𐑳𐑗 𐑜𐑫𐑛 𐑨𐑟 𐑞𐑺 𐑸 𐑐𐑰𐑐𐑩𐑤 𐑣𐑵 𐑮𐑰𐑛 𐑦𐑑.

%  LocalWords:
