\chapter{𐑞 ·𐑐𐑤𐑨𐑯𐑦𐑙 ·𐑓𐑨𐑤𐑩𐑕𐑦}

\begin{chapterOpeningAuthorNote}
    ·𐑚𐑤𐑭 𐑚𐑤𐑭 𐑛𐑦𐑕𐑒𐑤𐑱𐑥𐑼 𐑚𐑤𐑭 𐑚𐑤𐑭 ·𐑮𐑴𐑤𐑦𐑙 𐑚𐑤𐑭 𐑚𐑤𐑭 𐑴𐑯𐑼𐑖𐑦𐑐.

    𐑞 “·𐑭𐑓𐑑𐑼𐑥𐑨𐑔” 𐑕𐑧𐑒𐑖𐑩𐑯 𐑝 𐑞𐑦𐑕 𐑗𐑨𐑐𐑑𐑼 𐑦𐑟 𐑐𐑸𐑑 𐑝 𐑞 𐑕𐑑𐑹𐑦, \emph{𐑯𐑪𐑑} ·𐑴𐑥𐑭𐑒𐑧.
\end{chapterOpeningAuthorNote}
\begin{chapterOpeningQuote}
    𐑿 𐑔𐑦𐑙𐑒 𐑘𐑹 𐑛𐑱 𐑢𐑪𐑟 𐑕𐑼𐑾𐑤? 𐑑𐑮𐑲 𐑥𐑲𐑯.
\end{chapterOpeningQuote}

\lettrine{𐑕}{\emph{𐑳𐑥}} 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑢𐑫𐑛 𐑣𐑨𐑝 𐑢𐑱𐑑𐑩𐑛 𐑩𐑯𐑑𐑦𐑤 \emph{𐑭𐑓𐑑𐑼} 𐑞𐑺 𐑓𐑻𐑕𐑑 𐑑𐑮𐑦𐑐 𐑑 ·𐑛𐑲𐑨𐑜𐑩𐑯 ·𐑨𐑤𐑦.

“·𐑚𐑨𐑜 𐑝 𐑧𐑤𐑦𐑥𐑩𐑯𐑑 79,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑯 𐑢𐑦𐑞𐑛𐑮𐑵 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛, 𐑧𐑥𐑐𐑑𐑦, 𐑓𐑮𐑪𐑥 𐑞 𐑥𐑴𐑒𐑕𐑒𐑦𐑯 𐑐𐑬𐑗.
aʃð
𐑥𐑴𐑕𐑑 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑢𐑫𐑛 𐑣𐑨𐑝 𐑨𐑑 𐑤𐑰𐑕𐑑 𐑢𐑱𐑑𐑩𐑛 𐑑 𐑜𐑧𐑑 𐑞𐑺 \emph{𐑢𐑪𐑯𐑛𐑟} 𐑓𐑻𐑕𐑑.

“·𐑚𐑨𐑜 𐑝 \emph{𐑪𐑒𐑭𐑯𐑧},” 𐑕𐑧𐑛 ·𐑣𐑨𐑮𐑦. 𐑞 𐑣𐑧𐑝𐑦 𐑚𐑨𐑜 𐑝 𐑜𐑴𐑤𐑛 𐑐𐑪𐑐𐑑 𐑳𐑐 𐑦𐑯𐑑𐑵 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛.

·𐑣𐑨𐑮𐑦 𐑢𐑦𐑞𐑛𐑮𐑵 𐑞 𐑚𐑨𐑜, 𐑞𐑧𐑯 𐑐𐑤𐑳𐑯𐑡𐑛 𐑦𐑑 𐑩𐑜𐑱𐑯 𐑦𐑯𐑑𐑵 𐑞 𐑥𐑴𐑒𐑕𐑒𐑦𐑯 𐑐𐑬𐑗. 𐑣𐑰 𐑑𐑫𐑒 𐑬𐑑 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛, 𐑐𐑫𐑑 𐑦𐑑 𐑚𐑨𐑒 𐑦𐑯, 𐑯 𐑕𐑧𐑛, “·𐑚𐑨𐑜 𐑝 𐑑𐑴𐑒𐑩𐑯𐑟 𐑝 𐑰𐑒𐑩𐑯𐑪𐑥𐑦𐑒 𐑦𐑒𐑕𐑗𐑱𐑯𐑡.” 𐑞𐑨𐑑 𐑑𐑲𐑥 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛 𐑒𐑱𐑥 𐑬𐑑 𐑧𐑥𐑐𐑑𐑦.

“𐑜𐑦𐑝 𐑥𐑰 𐑚𐑨𐑒 𐑞 𐑚𐑨𐑜 𐑞𐑨𐑑 𐑲 𐑡𐑳𐑕𐑑 𐑐𐑫𐑑 𐑦𐑯.” 𐑬𐑑 𐑒𐑱𐑥 𐑞 𐑚𐑨𐑜 𐑝 𐑜𐑴𐑤𐑛 𐑢𐑳𐑯𐑕 𐑥𐑹.

·𐑣𐑨𐑮𐑦 ·𐑡𐑱𐑥𐑟 ·𐑐𐑪𐑑𐑼-·𐑧𐑝𐑩𐑯𐑟-·𐑝𐑧𐑮𐑟 𐑣𐑨𐑛 𐑜𐑪𐑑 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛𐑟 𐑪𐑯 𐑨𐑑 𐑤𐑰𐑕𐑑 𐑢𐑳𐑯 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 𐑲𐑑𐑩𐑥. 𐑢𐑲 𐑢𐑱𐑑?

“·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑑 𐑞 𐑚𐑦𐑥𐑿𐑟𐑛 𐑢𐑦𐑗 𐑕𐑑𐑮𐑴𐑤𐑦𐑙 𐑚𐑦𐑕𐑲𐑛 𐑣𐑦𐑥, “𐑒𐑨𐑯 𐑿 𐑜𐑦𐑝 𐑥𐑰 𐑑𐑵 𐑢𐑻𐑛𐑟, 𐑢𐑳𐑯 𐑢𐑻𐑛 𐑓 𐑜𐑴𐑤𐑛, 𐑯 𐑢𐑳𐑯 𐑢𐑻𐑛 𐑓 𐑕𐑳𐑥𐑔𐑦𐑙 𐑧𐑤𐑕 𐑞𐑨𐑑 𐑦𐑟𐑩𐑯𐑑 𐑥𐑳𐑯𐑦, 𐑦𐑯 𐑩 𐑤𐑨𐑙𐑜𐑢𐑦𐑡 𐑞𐑨𐑑 𐑲 𐑢𐑫𐑛𐑩𐑯𐑑 𐑯𐑴? 𐑚𐑳𐑑 𐑛𐑴𐑯𐑑 𐑑𐑧𐑤 𐑥𐑰 𐑢𐑦𐑗 𐑦𐑟 𐑢𐑦𐑗.”

“\emph{𐑭𐑣𐑭𐑝𐑩} 𐑯 \emph{𐑟𐑭𐑣𐑩𐑝},” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. “𐑞𐑨𐑑'𐑕 ·𐑣𐑰𐑚𐑮𐑵, 𐑯 𐑞 𐑳𐑞𐑼 𐑢𐑻𐑛 𐑥𐑰𐑯𐑟 𐑤𐑳𐑝.”

“𐑔𐑨𐑙𐑒 𐑿, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼. ·𐑚𐑨𐑜 𐑝 \emph{𐑭𐑣𐑭𐑝𐑩}.” 𐑧𐑥𐑐𐑑𐑦.

“·𐑚𐑨𐑜 𐑝 \emph{𐑟𐑭𐑣𐑩𐑝}.” 𐑯 𐑦𐑑 𐑐𐑪𐑐𐑑 𐑳𐑐 𐑦𐑯𐑑𐑵 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛.

“𐑟𐑭𐑣𐑩𐑝 𐑦𐑟 𐑜𐑴𐑤𐑛?” ·𐑣𐑨𐑮𐑦 𐑒𐑢𐑧𐑕𐑗𐑩𐑯𐑛, 𐑯 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑯𐑪𐑛𐑩𐑛.

·𐑣𐑨𐑮𐑦 𐑔𐑷𐑑 𐑴𐑝𐑼 𐑣𐑦𐑟 𐑒𐑩𐑤𐑧𐑒𐑑𐑩𐑛 𐑦𐑒𐑕𐑐𐑧𐑮𐑦𐑥𐑧𐑯𐑑𐑩𐑤 𐑛𐑱𐑑𐑩. 𐑦𐑑 𐑢𐑪𐑟 𐑴𐑯𐑤𐑦 𐑞 𐑥𐑴𐑕𐑑 𐑒𐑮𐑵𐑛 𐑯 𐑐𐑮𐑦𐑤𐑦𐑥𐑦𐑯𐑼𐑦 𐑕𐑹𐑑 𐑝 𐑧𐑓𐑼𐑑, 𐑚𐑳𐑑 𐑦𐑑 𐑢𐑪𐑟 𐑦𐑯𐑳𐑓 𐑑 𐑕𐑩𐑐𐑹𐑑 𐑨𐑑 𐑤𐑰𐑕𐑑 𐑢𐑳𐑯 𐑒𐑩𐑯𐑒𐑤𐑵𐑠𐑩𐑯:

“\emph{𐑭𐑭𐑭𐑭𐑮𐑜𐑣 𐑞𐑦𐑕 𐑛𐑳𐑟𐑩𐑯𐑑 𐑥𐑱𐑒 𐑧𐑯𐑦 𐑕𐑧𐑯𐑕!}”

𐑞 𐑢𐑦𐑗 𐑚𐑦𐑕𐑲𐑛 𐑣𐑦𐑥 𐑤𐑦𐑓𐑑𐑩𐑛 𐑩 𐑤𐑪𐑓𐑑𐑦 𐑲𐑚𐑮𐑬. “𐑐𐑮𐑪𐑚𐑤𐑩𐑥𐑟, ·𐑥𐑼~·𐑐𐑪𐑑𐑼?”

“𐑲 𐑡𐑳𐑕𐑑 𐑓𐑷𐑤𐑕𐑦𐑓𐑲𐑛 𐑧𐑝𐑮𐑦 𐑕𐑦𐑙𐑜𐑩𐑤 𐑣𐑲𐑐𐑪𐑔𐑦𐑕𐑦𐑕 𐑲 𐑣𐑨𐑛! 𐑣𐑬 𐑒𐑨𐑯 𐑦𐑑 𐑯𐑴 𐑞𐑨𐑑 '𐑚𐑨𐑜 𐑝 115 ·𐑜𐑨𐑤𐑾𐑯𐑟' 𐑦𐑟 𐑴𐑒𐑱 𐑚𐑳𐑑 𐑯𐑪𐑑 '𐑚𐑨𐑜 𐑝 90 𐑐𐑤𐑳𐑕 25 ·𐑜𐑨𐑤𐑾𐑯𐑟'? 𐑦𐑑 𐑒𐑨𐑯 \emph{𐑒𐑬𐑯𐑑} 𐑚𐑳𐑑 𐑦𐑑 𐑒𐑭𐑯𐑑 \emph{𐑨𐑛}? 𐑦𐑑 𐑒𐑨𐑯 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑯𐑬𐑯𐑟, 𐑚𐑳𐑑 𐑯𐑪𐑑 𐑕𐑳𐑥 𐑯𐑬𐑯 𐑓𐑮𐑱𐑟𐑩𐑟 𐑞𐑨𐑑 𐑥𐑰𐑯 𐑞 𐑕𐑱𐑥 𐑔𐑦𐑙? 𐑞 𐑐𐑻𐑕𐑩𐑯 𐑣𐑵 𐑥𐑱𐑛 𐑞𐑦𐑕 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑛𐑦𐑛𐑩𐑯𐑑 𐑕𐑐𐑰𐑒 ·𐑡𐑨𐑐𐑩𐑯𐑰𐑟 𐑯 \emph{𐑲} 𐑛𐑴𐑯𐑑 𐑕𐑐𐑰𐑒 𐑧𐑯𐑦 ·𐑣𐑰𐑚𐑮𐑵, 𐑕𐑴 𐑦𐑑'𐑕 𐑯𐑪𐑑 𐑿𐑟𐑦𐑙 \emph{𐑞𐑺} 𐑯𐑪𐑤𐑦𐑡, 𐑯 𐑦𐑑'𐑕 𐑯𐑪𐑑 𐑿𐑟𐑦𐑙 \emph{𐑥𐑲} 𐑯𐑪𐑤𐑦𐑡—” ·𐑣𐑨𐑮𐑦 𐑢𐑱𐑝𐑛 𐑩 𐑣𐑨𐑯𐑛 𐑣𐑧𐑤𐑐𐑤𐑩𐑕𐑤𐑦. “𐑞 𐑮𐑵𐑤𐑟 𐑕𐑰𐑥 \emph{𐑕𐑹𐑑𐑩} 𐑒𐑩𐑯𐑕𐑦𐑕𐑑𐑩𐑯𐑑 𐑚𐑳𐑑 𐑞𐑱 𐑛𐑴𐑯𐑑 \emph{𐑥𐑰𐑯} 𐑧𐑯𐑦𐑔𐑦𐑙! 𐑲'𐑥 𐑯𐑪𐑑 𐑰𐑝𐑩𐑯 𐑜𐑴𐑦𐑙 𐑑 𐑭𐑕𐑒 𐑣𐑬 𐑩 \emph{𐑐𐑬𐑗} 𐑧𐑯𐑛𐑟 𐑳𐑐 𐑢𐑦𐑞 𐑝𐑶𐑕 𐑮𐑧𐑒𐑩𐑜𐑯𐑦𐑖𐑩𐑯 𐑯 𐑯𐑨𐑗𐑼𐑩𐑤 𐑤𐑨𐑙𐑜𐑢𐑦𐑡 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛𐑦𐑙 𐑢𐑧𐑯 𐑞 𐑚𐑧𐑕𐑑 ·𐑸𐑑𐑦𐑓𐑦𐑖𐑩𐑤 ·𐑦𐑯𐑑𐑧𐑤𐑦𐑡𐑩𐑯𐑕 𐑐𐑮𐑴𐑜𐑮𐑨𐑥𐑼𐑟 𐑒𐑭𐑯𐑑 𐑜𐑧𐑑 𐑞 𐑓𐑭𐑕𐑑𐑩𐑕𐑑 𐑕𐑵𐑐𐑼𐑒𐑩𐑥𐑐𐑿𐑑𐑼𐑟 𐑑 𐑛𐑵 𐑦𐑑 𐑭𐑓𐑑𐑼 𐑔𐑻𐑑𐑦-𐑓𐑲𐑝 𐑘𐑽𐑟 𐑝 𐑣𐑸𐑛 𐑢𐑻𐑒,” ·𐑣𐑨𐑮𐑦 𐑜𐑭𐑕𐑐𐑑 𐑓 𐑚𐑮𐑧𐑔, “𐑚𐑳𐑑 \emph{𐑢𐑪𐑑} 𐑦𐑟 𐑜𐑴𐑦𐑙 \emph{𐑪𐑯}?”

“·𐑥𐑨𐑡𐑦𐑒,” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤.

“𐑞𐑨𐑑'𐑕 𐑡𐑳𐑕𐑑 𐑩 \emph{𐑢𐑻𐑛}! 𐑰𐑝𐑩𐑯 𐑭𐑓𐑑𐑼 𐑿 𐑑𐑧𐑤 𐑥𐑰 𐑞𐑨𐑑, 𐑲 𐑒𐑭𐑯𐑑 𐑥𐑱𐑒 𐑧𐑯𐑦 𐑯𐑿 𐑐𐑮𐑦𐑛𐑦𐑒𐑖𐑩𐑯𐑟! 𐑦𐑑'𐑕 𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦 𐑤𐑲𐑒 𐑕𐑱𐑦𐑙 '𐑓𐑤𐑴𐑡𐑦𐑕𐑑𐑪𐑯' 𐑹 '𐑱𐑤𐑭𐑯 𐑝𐑲𐑑𐑩𐑤' 𐑹 '𐑦𐑥𐑻𐑡𐑩𐑯𐑕' 𐑹 '𐑒𐑩𐑥𐑐𐑤𐑧𐑒𐑕𐑦𐑑𐑦'!”

𐑞 𐑚𐑤𐑨𐑒-𐑮𐑴𐑚𐑛 𐑢𐑦𐑗 𐑤𐑭𐑓𐑑 𐑩𐑤𐑬𐑛. “𐑚𐑳𐑑 𐑦𐑑 \emph{𐑦𐑟} 𐑥𐑨𐑡𐑦𐑒, ·𐑥𐑼~·𐑐𐑪𐑑𐑼.”

·𐑣𐑨𐑮𐑦 𐑕𐑤𐑳𐑥𐑐𐑑 𐑴𐑝𐑼 𐑩 𐑤𐑦𐑑𐑩𐑤. “𐑢𐑦𐑞 𐑮𐑦𐑕𐑐𐑧𐑒𐑑, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑲'𐑥 𐑯𐑪𐑑 𐑒𐑢𐑲𐑑 𐑖𐑫𐑼 𐑿 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑢𐑪𐑑 𐑲'𐑥 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑛𐑵 𐑣𐑽.”

“𐑢𐑦𐑞 𐑮𐑦𐑕𐑐𐑧𐑒𐑑, ·𐑥𐑼~·𐑐𐑪𐑑𐑼, 𐑲'𐑥 𐑒𐑢𐑲𐑑 𐑖𐑫𐑼 𐑲 𐑛𐑴𐑯𐑑. 𐑩𐑯𐑤𐑧𐑕—𐑞𐑦𐑕 𐑦𐑟 𐑡𐑳𐑕𐑑 𐑩 𐑜𐑧𐑕, 𐑥𐑲𐑯𐑛—𐑿'𐑼 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑑𐑱𐑒 𐑴𐑝𐑼 𐑞 𐑢𐑻𐑤𐑛?”

“𐑯𐑴! 𐑲 𐑥𐑰𐑯 𐑘𐑧𐑕—𐑢𐑧𐑤, \emph{𐑯𐑴}!”

“𐑲 𐑔𐑦𐑙𐑒 𐑲 𐑖𐑫𐑛 𐑐𐑼𐑣𐑨𐑐𐑕 𐑚𐑰 𐑩𐑤𐑸𐑥𐑛 𐑞𐑨𐑑 𐑿 𐑣𐑨𐑝 𐑑𐑮𐑳𐑚𐑩𐑤 𐑭𐑯𐑕𐑼𐑦𐑙 𐑞 𐑒𐑢𐑧𐑕𐑗𐑩𐑯.”

·𐑣𐑨𐑮𐑦 𐑜𐑤𐑳𐑥𐑤𐑦 𐑒𐑩𐑯𐑕𐑦𐑛𐑼𐑛 𐑞 ·𐑛𐑸𐑑𐑥𐑩𐑔 ·𐑒𐑪𐑯𐑓𐑼𐑩𐑯𐑕 𐑪𐑯 ·𐑸𐑑𐑦𐑓𐑦𐑖𐑩𐑤 ·𐑦𐑯𐑑𐑧𐑤𐑦𐑡𐑩𐑯𐑕 𐑦𐑯 1956. 𐑦𐑑 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑞 𐑓𐑻𐑕𐑑 𐑒𐑪𐑯𐑓𐑼𐑩𐑯𐑕 𐑧𐑝𐑼 𐑪𐑯 𐑞 𐑑𐑪𐑐𐑦𐑒, 𐑞 𐑢𐑳𐑯 𐑞𐑨𐑑 𐑣𐑨𐑛 𐑒𐑶𐑯𐑛 𐑞 𐑓𐑮𐑱𐑟 “·𐑸𐑑𐑦𐑓𐑦𐑖𐑩𐑤 ·𐑦𐑯𐑑𐑧𐑤𐑦𐑡𐑩𐑯𐑕”. 𐑞𐑱 𐑣𐑨𐑛 𐑲𐑛𐑧𐑯𐑑𐑦𐑓𐑲𐑛 𐑒𐑰 𐑐𐑮𐑪𐑚𐑤𐑩𐑥𐑟 𐑕𐑳𐑗 𐑨𐑟 𐑥𐑱𐑒𐑦𐑙 𐑒𐑩𐑥𐑐𐑿𐑑𐑼𐑟 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑤𐑨𐑙𐑜𐑢𐑦𐑡, 𐑤𐑻𐑯, 𐑯 𐑦𐑥𐑐𐑮𐑵𐑝 𐑞𐑧𐑥𐑕𐑧𐑤𐑝𐑟. 𐑞𐑱 𐑣𐑨𐑛 𐑕𐑩𐑡𐑧𐑕𐑑𐑩𐑛, 𐑦𐑯 𐑐𐑻𐑓𐑦𐑒𐑑 𐑕𐑽𐑾𐑕𐑯𐑩𐑕, 𐑞𐑨𐑑 𐑕𐑦𐑜𐑯𐑦𐑓𐑦𐑒𐑩𐑯𐑑 𐑩𐑛𐑝𐑭𐑯𐑕𐑩𐑟 𐑪𐑯 𐑞𐑰𐑟 𐑐𐑮𐑪𐑚𐑤𐑩𐑥𐑟 𐑥𐑲𐑑 𐑚𐑰 𐑥𐑱𐑛 𐑚𐑲 𐑑𐑧𐑯 𐑕𐑲𐑩𐑯𐑑𐑦𐑕𐑑𐑕 𐑢𐑻𐑒𐑦𐑙 𐑑𐑩𐑜𐑧𐑞𐑼 𐑓 𐑑𐑵 𐑥𐑳𐑯𐑔𐑕.

\emph{𐑯𐑴. ·𐑗𐑦𐑯 𐑳𐑐. 𐑿'𐑼 𐑡𐑳𐑕𐑑 \emph{𐑕𐑑𐑸𐑑𐑦𐑙} 𐑪𐑯 𐑞 𐑐𐑮𐑪𐑚𐑤𐑩𐑥 𐑝 𐑳𐑯𐑮𐑨𐑝𐑩𐑤𐑦𐑙 𐑷𐑤 𐑞 𐑕𐑰𐑒𐑮𐑩𐑑𐑕 𐑝 𐑥𐑨𐑡𐑦𐑒. 𐑿 𐑛𐑴𐑯𐑑 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 \emph{𐑯𐑴} 𐑢𐑧𐑞𐑼 𐑦𐑑'𐑕 𐑜𐑴𐑦𐑙 𐑑 𐑚𐑰 𐑑𐑵 𐑛𐑦𐑓𐑦𐑒𐑳𐑤𐑑 𐑑 𐑛𐑵 𐑦𐑯 𐑑𐑵 𐑥𐑳𐑯𐑔𐑕.}

“𐑯 𐑿 \emph{𐑮𐑾𐑤𐑦} 𐑣𐑨𐑝𐑩𐑯𐑑 𐑣𐑻𐑛 𐑝 𐑳𐑞𐑼 𐑢𐑦𐑟𐑼𐑛𐑟 𐑭𐑕𐑒𐑦𐑙 𐑞𐑰𐑟 𐑕𐑹𐑑𐑕 𐑝 𐑒𐑢𐑧𐑕𐑗𐑩𐑯𐑟 𐑹 𐑛𐑵𐑦𐑙 𐑞𐑦𐑕 𐑕𐑹𐑑 𐑝 𐑕𐑲𐑩𐑯𐑑𐑦𐑓𐑦𐑒 𐑦𐑒𐑕𐑐𐑧𐑮𐑦𐑥𐑧𐑯𐑑𐑦𐑙?” ·𐑣𐑨𐑮𐑦 𐑭𐑕𐑒𐑑 𐑩𐑜𐑱𐑯. 𐑦𐑑 𐑡𐑳𐑕𐑑 𐑕𐑰𐑥𐑛 𐑕𐑴 \emph{𐑪𐑚𐑝𐑾𐑕} 𐑑 𐑣𐑦𐑥.

𐑞𐑧𐑯 𐑩𐑜𐑱𐑯, 𐑦𐑑'𐑩𐑛 𐑑𐑱𐑒𐑩𐑯 𐑥𐑹 𐑞𐑨𐑯 𐑑𐑵 𐑣𐑳𐑯𐑛𐑮𐑩𐑛 𐑘𐑽𐑟 \emph{𐑭𐑓𐑑𐑼} 𐑞 𐑦𐑯𐑝𐑧𐑯𐑖𐑩𐑯 𐑝 𐑞 𐑕𐑲𐑩𐑯𐑑𐑦𐑓𐑦𐑒 𐑥𐑧𐑔𐑩𐑛 𐑚𐑦𐑓𐑹 𐑧𐑯𐑦 ·𐑥𐑳𐑜𐑩𐑤 𐑕𐑲𐑩𐑯𐑑𐑦𐑕𐑑𐑕 𐑣𐑨𐑛 𐑔𐑷𐑑 𐑑 𐑕𐑦𐑕𐑑𐑩𐑥𐑨𐑑𐑦𐑒𐑤𐑦 𐑦𐑯𐑝𐑧𐑕𐑑𐑦𐑜𐑱𐑑 𐑢𐑦𐑗 𐑕𐑧𐑯𐑑𐑩𐑯𐑕𐑩𐑟 𐑩 \emph{𐑣𐑿𐑥𐑩𐑯 𐑓𐑹-𐑘𐑽-𐑴𐑤𐑛} 𐑒𐑫𐑛 𐑹 𐑒𐑫𐑛𐑩𐑯𐑑 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛. 𐑞 𐑛𐑦𐑝𐑧𐑤𐑩𐑐𐑥𐑧𐑯𐑑𐑩𐑤 𐑕𐑲𐑒𐑪𐑤𐑩𐑡𐑦 𐑝 𐑤𐑦𐑙𐑜𐑢𐑦𐑕𐑑𐑦𐑒𐑕 𐑒𐑫𐑛'𐑝 𐑚𐑰𐑯 𐑛𐑦𐑕𐑒𐑳𐑝𐑼𐑛 𐑦𐑯 𐑞 𐑱𐑑𐑰𐑯𐑔 𐑕𐑧𐑯𐑗𐑼𐑦, 𐑦𐑯 𐑐𐑮𐑦𐑯𐑕𐑩𐑐𐑩𐑤, 𐑚𐑳𐑑 𐑯𐑴-𐑢𐑳𐑯 𐑣𐑨𐑛 𐑰𐑝𐑩𐑯 𐑔𐑷𐑑 𐑑 𐑤𐑫𐑒 𐑩𐑯𐑑𐑦𐑤 𐑞 𐑑𐑢𐑧𐑯𐑑𐑾𐑔. 𐑕𐑴 𐑿 𐑒𐑫𐑛𐑩𐑯𐑑 𐑮𐑾𐑤𐑦 𐑚𐑤𐑱𐑥 𐑞 𐑥𐑳𐑗 𐑕𐑥𐑷𐑤𐑼 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑢𐑻𐑤𐑛 𐑓 𐑯𐑪𐑑 𐑦𐑯𐑝𐑧𐑕𐑑𐑦𐑜𐑱𐑑𐑦𐑙 𐑞 ·𐑮𐑦𐑑𐑮𐑰𐑝𐑩𐑤 ·𐑗𐑸𐑥.

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑐𐑻𐑕𐑑 𐑣𐑻 𐑤𐑦𐑐𐑕, 𐑞𐑧𐑯 𐑖𐑮𐑳𐑜𐑛. “𐑲'𐑥 𐑕𐑑𐑦𐑤 𐑯𐑪𐑑 𐑖𐑫𐑼 𐑢𐑪𐑑 𐑿 𐑥𐑰𐑯 𐑚𐑲 '𐑕𐑲𐑩𐑯𐑑𐑦𐑓𐑦𐑒 𐑦𐑒𐑕𐑐𐑧𐑮𐑦𐑥𐑧𐑯𐑑𐑦𐑙', ·𐑥𐑼~·𐑐𐑪𐑑𐑼. 𐑨𐑟 𐑲 𐑕𐑧𐑛, 𐑲'𐑝 𐑕𐑰𐑯 ·𐑥𐑳𐑜𐑩𐑤-𐑚𐑹𐑯 𐑕𐑑𐑿𐑛𐑩𐑯𐑑𐑕 𐑑𐑮𐑲 𐑑 𐑜𐑧𐑑 ·𐑥𐑳𐑜𐑩𐑤 𐑕𐑲𐑩𐑯𐑕 𐑑 𐑢𐑻𐑒 𐑦𐑯𐑕𐑲𐑛 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕, 𐑯 𐑐𐑰𐑐𐑩𐑤 𐑦𐑯𐑝𐑧𐑯𐑑 𐑯𐑿 ·𐑗𐑸𐑥𐑟 𐑯 ·𐑐𐑴𐑖𐑩𐑯𐑟 𐑧𐑝𐑮𐑦 𐑘𐑽.”

·𐑣𐑨𐑮𐑦 𐑖𐑫𐑒 𐑣𐑦𐑟 𐑣𐑧𐑛. “𐑑𐑧𐑒𐑯𐑪𐑤𐑩𐑡𐑦 𐑦𐑟𐑩𐑯𐑑 𐑞 𐑕𐑱𐑥 𐑔𐑦𐑙 𐑨𐑟 𐑕𐑲𐑩𐑯𐑕 𐑨𐑑 𐑷𐑤. 𐑯 𐑑𐑮𐑲𐑦𐑙 𐑤𐑪𐑑𐑕 𐑝 𐑛𐑦𐑓𐑼𐑩𐑯𐑑 𐑢𐑱𐑟 𐑑 𐑛𐑵 𐑕𐑳𐑥𐑔𐑦𐑙 𐑦𐑟𐑩𐑯𐑑 𐑞 𐑕𐑱𐑥 𐑨𐑟 𐑦𐑒𐑕𐑐𐑧𐑮𐑦𐑥𐑧𐑯𐑑𐑦𐑙 𐑑 𐑓𐑦𐑜𐑼 𐑬𐑑 𐑞 𐑮𐑵𐑤𐑟.” 𐑞𐑺 𐑢𐑻 𐑐𐑤𐑧𐑯𐑑𐑦 𐑝 𐑐𐑰𐑐𐑩𐑤 𐑣𐑵'𐑛 𐑑𐑮𐑲𐑛 𐑑 𐑦𐑯𐑝𐑧𐑯𐑑 𐑓𐑤𐑲𐑦𐑙 𐑥𐑩𐑖𐑰𐑯𐑟 𐑚𐑲 𐑑𐑮𐑲𐑦𐑙 𐑬𐑑 𐑤𐑪𐑑𐑕 𐑝 𐑔𐑦𐑙𐑟-𐑢𐑦𐑞-𐑢𐑦𐑙𐑟, 𐑚𐑳𐑑 𐑴𐑯𐑤𐑦 𐑞 ·𐑮𐑲𐑑 ·𐑚𐑮𐑳𐑞𐑼𐑟 𐑣𐑨𐑛 𐑚𐑦𐑤𐑑 𐑩 𐑢𐑦𐑯𐑛 𐑑𐑳𐑯𐑩𐑤 𐑑 𐑥𐑧𐑠𐑼 𐑤𐑦𐑓𐑑…“𐑳𐑥, 𐑣𐑬 𐑥𐑧𐑯𐑦 ·𐑥𐑳𐑜𐑩𐑤-𐑮𐑱𐑟𐑛 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 \emph{𐑛𐑵} 𐑿 𐑜𐑧𐑑 𐑨𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 𐑧𐑝𐑮𐑦 𐑘𐑽?”

“𐑐𐑼𐑣𐑨𐑐𐑕 𐑑𐑧𐑯 𐑹 𐑕𐑴?”

·𐑣𐑨𐑮𐑦 𐑥𐑦𐑕𐑑 𐑩 𐑕𐑑𐑧𐑐 𐑯 𐑷𐑤𐑥𐑴𐑕𐑑 𐑑𐑮𐑦𐑐𐑑 𐑴𐑝𐑼 𐑣𐑦𐑟 𐑴𐑯 𐑓𐑰𐑑. “\emph{𐑑𐑧𐑯?}”

𐑞 ·𐑥𐑳𐑜𐑩𐑤 𐑢𐑻𐑤𐑛 𐑣𐑨𐑛 𐑩 𐑐𐑪𐑐𐑿𐑤𐑱𐑖𐑩𐑯 𐑝 𐑕𐑦𐑒𐑕 𐑚𐑦𐑤𐑘𐑩𐑯 𐑯 𐑒𐑬𐑯𐑑𐑦𐑙. 𐑦𐑓 𐑿 𐑢𐑻 𐑢𐑳𐑯 𐑦𐑯 𐑩 𐑥𐑦𐑤𐑘𐑩𐑯, 𐑞𐑺 𐑢𐑻 𐑕𐑧𐑝𐑩𐑯 𐑝 𐑿 𐑦𐑯 ·𐑤𐑳𐑯𐑛𐑩𐑯 𐑯 𐑩 𐑔𐑬𐑟𐑩𐑯𐑛 𐑥𐑹 𐑦𐑯 ·𐑗𐑲𐑯𐑩. 𐑦𐑑 𐑢𐑪𐑟 𐑦𐑯𐑧𐑝𐑦𐑑𐑩𐑚𐑩𐑤 𐑞𐑨𐑑 𐑞 ·𐑥𐑳𐑜𐑩𐑤 𐑐𐑪𐑐𐑿𐑤𐑱𐑖𐑩𐑯 𐑢𐑫𐑛 𐑐𐑮𐑩𐑛𐑿𐑕 \emph{𐑕𐑳𐑥} 𐑦𐑤𐑧𐑝𐑩𐑯-𐑘𐑽-𐑴𐑤𐑛𐑟 𐑣𐑵 𐑒𐑫𐑛 𐑛𐑵 𐑒𐑨𐑤𐑒𐑿𐑤𐑩𐑕—·𐑣𐑨𐑮𐑦 𐑯𐑿 𐑣𐑰 𐑢𐑪𐑟𐑩𐑯𐑑 𐑞 𐑴𐑯𐑤𐑦 𐑢𐑳𐑯. 𐑣𐑰'𐑛 𐑥𐑧𐑑 𐑳𐑞𐑼 𐑐𐑮𐑪𐑛𐑦𐑡𐑦𐑟 𐑦𐑯 𐑥𐑨𐑔𐑩𐑥𐑨𐑑𐑦𐑒𐑩𐑤 𐑒𐑪𐑥𐑐𐑩𐑑𐑦𐑖𐑩𐑯𐑟. 𐑦𐑯 𐑓𐑨𐑒𐑑 𐑣𐑰'𐑛 𐑚𐑰𐑯 𐑔𐑳𐑮𐑴𐑤𐑦 𐑑𐑮𐑬𐑯𐑕𐑑 𐑚𐑲 𐑒𐑩𐑥𐑐𐑧𐑑𐑦𐑑𐑼𐑟 𐑣𐑵 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑕𐑐𐑧𐑯𐑑 𐑤𐑦𐑑𐑼𐑩𐑤𐑦 \emph{𐑷𐑤 𐑛𐑱} 𐑐𐑮𐑨𐑒𐑑𐑦𐑕𐑦𐑙 𐑥𐑨𐑔𐑕 𐑐𐑮𐑪𐑚𐑤𐑩𐑥𐑟 𐑯 𐑣𐑵'𐑛 \emph{𐑯𐑧𐑝𐑼} 𐑮𐑰𐑛 𐑩 𐑕𐑲𐑩𐑯𐑕-𐑓𐑦𐑒𐑖𐑩𐑯 𐑚𐑫𐑒 𐑯 𐑣𐑵 𐑢𐑫𐑛 𐑚𐑻𐑯 𐑬𐑑 \emph{𐑒𐑩𐑥𐑐𐑤𐑰𐑑𐑤𐑦} 𐑚𐑦𐑓𐑹 \emph{𐑐𐑿𐑚𐑼𐑑𐑦} 𐑯 \emph{𐑯𐑧𐑝𐑼} 𐑩𐑥𐑬𐑯𐑑 𐑑 \emph{𐑧𐑯𐑦𐑔𐑦𐑙} 𐑦𐑯 𐑞𐑺 𐑓𐑿𐑗𐑼 𐑤𐑲𐑝𐑟 𐑚𐑦𐑒𐑪𐑟 𐑞𐑱'𐑛 𐑡𐑳𐑕𐑑 𐑐𐑮𐑨𐑒𐑑𐑦𐑕𐑑 \emph{𐑯𐑴𐑯} 𐑑𐑧𐑒𐑯𐑰𐑒𐑕 𐑦𐑯𐑕𐑑𐑧𐑛 𐑝 𐑤𐑻𐑯𐑦𐑙 𐑑 𐑔𐑦𐑙𐑒 \emph{𐑒𐑮𐑦𐑱𐑑𐑦𐑝𐑤𐑦}. (·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑕𐑳𐑥𐑔𐑦𐑙 𐑝 𐑩 𐑕𐑹 𐑤𐑵𐑟𐑼.)

𐑚𐑳𐑑…𐑦𐑯 𐑞 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑢𐑻𐑤𐑛…

·𐑑𐑧𐑯 ·𐑥𐑳𐑜𐑩𐑤-𐑮𐑱𐑟𐑛 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑐𐑻 𐑘𐑽, 𐑣𐑵'𐑛 𐑷𐑤 𐑧𐑯𐑛𐑩𐑛 𐑞𐑺 ·𐑥𐑳𐑜𐑩𐑤 𐑧𐑡𐑩𐑒𐑱𐑖𐑩𐑯𐑟 𐑨𐑑 𐑞 𐑱𐑡 𐑝 𐑦𐑤𐑧𐑝𐑩𐑯? 𐑯 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑥𐑲𐑑 𐑚𐑰 𐑚𐑲𐑩𐑕𐑑, 𐑚𐑳𐑑 𐑖𐑰 𐑣𐑨𐑛 𐑒𐑤𐑱𐑥𐑛 𐑞𐑨𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 𐑢𐑪𐑟 𐑞 𐑤𐑸𐑡𐑩𐑕𐑑 𐑯 𐑥𐑴𐑕𐑑 𐑧𐑥𐑦𐑯𐑩𐑯𐑑 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑕𐑒𐑵𐑤 𐑦𐑯 𐑞 𐑢𐑻𐑤𐑛…𐑯 𐑦𐑑 𐑴𐑯𐑤𐑦 𐑧𐑡𐑩𐑒𐑱𐑑𐑩𐑛 𐑳𐑐 𐑑 𐑞 𐑱𐑡 𐑝 𐑕𐑧𐑝𐑩𐑯𐑑𐑰𐑯.

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑳𐑯𐑛𐑬𐑑𐑩𐑛𐑤𐑦 𐑯𐑿 𐑧𐑝𐑮𐑦 𐑤𐑭𐑕𐑑 𐑛𐑰𐑑𐑱𐑤 𐑝 𐑣𐑬 𐑿 𐑢𐑧𐑯𐑑 𐑩𐑚𐑬𐑑 𐑑𐑻𐑯𐑦𐑙 𐑦𐑯𐑑𐑵 𐑩 𐑒𐑨𐑑. 𐑚𐑳𐑑 𐑖𐑰 𐑕𐑰𐑥𐑛 𐑑 𐑣𐑨𐑝 𐑤𐑦𐑑𐑼𐑩𐑤𐑦 𐑯𐑧𐑝𐑼 \emph{𐑣𐑻𐑛} 𐑝 𐑞 𐑕𐑲𐑩𐑯𐑑𐑦𐑓𐑦𐑒 𐑥𐑧𐑔𐑩𐑛. 𐑑 𐑣𐑻 𐑦𐑑 𐑢𐑪𐑟 𐑡𐑳𐑕𐑑 ·𐑥𐑳𐑜𐑩𐑤 𐑥𐑨𐑡𐑦𐑒. 𐑯 𐑖𐑰 𐑛𐑦𐑛𐑩𐑯𐑑 𐑰𐑝𐑩𐑯 𐑕𐑰𐑥 \emph{𐑒𐑘𐑫𐑼𐑾𐑕} 𐑩𐑚𐑬𐑑 𐑢𐑪𐑑 𐑕𐑰𐑒𐑮𐑩𐑑𐑕 𐑥𐑲𐑑 𐑚𐑰 𐑣𐑲𐑛𐑦𐑙 𐑚𐑦𐑣𐑲𐑯𐑛 𐑞 𐑯𐑨𐑗𐑼𐑩𐑤 𐑤𐑨𐑙𐑜𐑢𐑦𐑡 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛𐑦𐑙 𐑝 𐑞 ·𐑮𐑦𐑑𐑮𐑰𐑝𐑩𐑤 ·𐑗𐑸𐑥.

𐑞𐑨𐑑 𐑤𐑧𐑓𐑑 𐑑𐑵 𐑐𐑪𐑕𐑩𐑚𐑦𐑤𐑦𐑑𐑦𐑟, 𐑮𐑾𐑤𐑦.

𐑐𐑪𐑕𐑩𐑚𐑦𐑤𐑦𐑑𐑦 𐑢𐑳𐑯: ·𐑥𐑨𐑡𐑦𐑒 𐑢𐑪𐑟 𐑕𐑴 𐑦𐑯𐑒𐑮𐑧𐑛𐑩𐑚𐑤𐑦 𐑴𐑐𐑱𐑒, 𐑒𐑪𐑯𐑝𐑩𐑤𐑵𐑑𐑩𐑛, 𐑯 𐑦𐑥𐑐𐑧𐑯𐑦𐑑𐑮𐑩𐑚𐑩𐑤, 𐑞𐑨𐑑 𐑰𐑝𐑩𐑯 𐑞𐑴 𐑢𐑦𐑟𐑼𐑛𐑟 𐑯 𐑢𐑦𐑗𐑩𐑟 𐑣𐑨𐑛 𐑑𐑮𐑲𐑛 𐑞𐑺 𐑚𐑧𐑕𐑑 𐑑 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛, 𐑞𐑱'𐑛 𐑥𐑱𐑛 𐑤𐑦𐑑𐑩𐑤 𐑹 𐑯𐑴 𐑐𐑮𐑴𐑜𐑮𐑧𐑕 𐑯 𐑦𐑝𐑧𐑯𐑗𐑵𐑩𐑤𐑦 𐑜𐑦𐑝𐑩𐑯 𐑳𐑐; 𐑯 ·𐑣𐑨𐑮𐑦 𐑢𐑫𐑛 𐑛𐑵 𐑯𐑴 𐑚𐑧𐑑𐑼.

\emph{𐑹}…

·𐑣𐑨𐑮𐑦 𐑒𐑮𐑨𐑒𐑑 𐑣𐑦𐑟 𐑯𐑳𐑒𐑩𐑤𐑟 𐑦𐑯 𐑛𐑦𐑑𐑻𐑥𐑦𐑯𐑱𐑖𐑩𐑯, 𐑚𐑳𐑑 𐑞𐑱 𐑴𐑯𐑤𐑦 𐑥𐑱𐑛 𐑩 𐑒𐑢𐑲𐑩𐑑 𐑕𐑹𐑑 𐑝 𐑒𐑤𐑦𐑒𐑦𐑙 𐑕𐑬𐑯𐑛, 𐑮𐑭𐑞𐑼 𐑞𐑨𐑯 𐑧𐑒𐑴𐑦𐑙 𐑪𐑥𐑦𐑯𐑩𐑕𐑤𐑦 𐑪𐑓 𐑞 𐑢𐑷𐑤𐑟 𐑝 ·𐑛𐑲𐑨𐑜𐑩𐑯 ·𐑨𐑤𐑦.

𐑐𐑪𐑕𐑩𐑚𐑦𐑤𐑦𐑑𐑦 𐑑𐑵: 𐑣𐑰'𐑛 𐑚𐑰 𐑑𐑱𐑒𐑦𐑙 𐑴𐑝𐑼 𐑞 𐑢𐑻𐑤𐑛.

𐑦𐑝𐑧𐑯𐑗𐑵𐑩𐑤𐑦. 𐑐𐑼𐑣𐑨𐑐𐑕 𐑯𐑪𐑑 𐑮𐑲𐑑 𐑩𐑢𐑱.

𐑞𐑨𐑑 𐑕𐑹𐑑 𐑝 𐑔𐑦𐑙 \emph{𐑛𐑦𐑛} 𐑕𐑳𐑥𐑑𐑲𐑥𐑟 𐑑𐑱𐑒 𐑤𐑪𐑙𐑜𐑼 𐑞𐑨𐑯 𐑑𐑵 𐑥𐑳𐑯𐑔𐑕. ·𐑥𐑳𐑜𐑩𐑤 𐑕𐑲𐑩𐑯𐑕 𐑣𐑨𐑛𐑩𐑯𐑑 𐑜𐑪𐑯 𐑑 𐑞 𐑥𐑵𐑯 𐑦𐑯 𐑞 𐑓𐑻𐑕𐑑 𐑢𐑰𐑒 𐑭𐑓𐑑𐑼 ·𐑜𐑨𐑤𐑦𐑤𐑱𐑴.

𐑚𐑳𐑑 ·𐑣𐑨𐑮𐑦 𐑕𐑑𐑦𐑤 𐑒𐑫𐑛𐑩𐑯𐑑 𐑕𐑑𐑪𐑐 𐑞 𐑣𐑿𐑡 𐑕𐑥𐑲𐑤 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑕𐑑𐑮𐑧𐑗𐑦𐑙 𐑣𐑦𐑟 𐑗𐑰𐑒𐑕 𐑕𐑴 𐑢𐑲𐑛 𐑞𐑱 𐑢𐑻 𐑕𐑑𐑸𐑑𐑦𐑙 𐑑 𐑣𐑻𐑑.

·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑷𐑤𐑢𐑱𐑟 𐑚𐑰𐑯 𐑓𐑮𐑲𐑑𐑩𐑯𐑛 𐑝 𐑧𐑯𐑛𐑦𐑙 𐑳𐑐 𐑨𐑟 𐑢𐑳𐑯 𐑝 𐑞𐑴𐑟 𐑗𐑲𐑤𐑛 𐑐𐑮𐑪𐑛𐑦𐑡𐑦𐑟 𐑞𐑨𐑑 𐑯𐑧𐑝𐑼 𐑩𐑥𐑬𐑯𐑑𐑩𐑛 𐑑 𐑧𐑯𐑦𐑔𐑦𐑙 𐑯 𐑕𐑐𐑧𐑯𐑑 𐑞 𐑮𐑧𐑕𐑑 𐑝 𐑞𐑺 𐑤𐑲𐑝𐑟 𐑚𐑴𐑕𐑑𐑦𐑙 𐑩𐑚𐑬𐑑 𐑣𐑬 𐑓𐑸 𐑩𐑣𐑧𐑛 𐑞𐑱'𐑛 𐑚𐑰𐑯 𐑨𐑑 𐑱𐑡 𐑑𐑧𐑯. 𐑚𐑳𐑑 𐑞𐑧𐑯 𐑥𐑴𐑕𐑑 𐑨𐑛𐑳𐑤𐑑 𐑡𐑰𐑯𐑾𐑕𐑩𐑟 𐑯𐑧𐑝𐑼 𐑩𐑥𐑬𐑯𐑑𐑩𐑛 𐑑 𐑧𐑯𐑦𐑔𐑦𐑙 𐑲𐑞𐑼. 𐑞𐑺 𐑢𐑻 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑩 𐑔𐑬𐑟𐑩𐑯𐑛 𐑐𐑰𐑐𐑩𐑤 𐑨𐑟 𐑦𐑯𐑑𐑧𐑤𐑦𐑡𐑩𐑯𐑑 𐑨𐑟 ·𐑲𐑯𐑕𐑑𐑲𐑯 𐑓 𐑧𐑝𐑮𐑦 𐑨𐑒𐑗𐑵𐑩𐑤 ·𐑲𐑯𐑕𐑑𐑲𐑯 𐑦𐑯 𐑣𐑦𐑕𐑑𐑼𐑦. 𐑚𐑦𐑒𐑪𐑟 𐑞𐑴𐑟 𐑳𐑞𐑼 𐑡𐑰𐑯𐑾𐑕𐑩𐑟 𐑣𐑨𐑛𐑩𐑯𐑑 𐑜𐑪𐑑 𐑞𐑺 𐑣𐑨𐑯𐑛𐑟 𐑪𐑯 𐑞 𐑢𐑳𐑯 𐑔𐑦𐑙 𐑿 𐑨𐑚𐑕𐑩𐑤𐑵𐑑𐑤𐑦 𐑯𐑰𐑛𐑩𐑛 𐑑 𐑩𐑗𐑰𐑝 𐑜𐑮𐑱𐑑𐑯𐑩𐑕. 𐑞𐑱'𐑛 𐑯𐑧𐑝𐑼 𐑓𐑬𐑯𐑛 𐑩𐑯 𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑 𐑐𐑮𐑪𐑚𐑤𐑩𐑥.

\emph{𐑿'𐑼 𐑥𐑲𐑯 𐑯𐑬,} ·𐑣𐑨𐑮𐑦 𐑔𐑷𐑑 𐑨𐑑 𐑞 𐑢𐑷𐑤𐑟 𐑝 ·𐑛𐑲𐑨𐑜𐑩𐑯 ·𐑨𐑤𐑦, 𐑯 𐑷𐑤 𐑞 𐑖𐑪𐑐𐑕 𐑯 𐑲𐑑𐑩𐑥𐑟, 𐑯 𐑷𐑤 𐑞 𐑖𐑪𐑐𐑒𐑰𐑐𐑼𐑟 𐑯 𐑒𐑳𐑕𐑑𐑩𐑥𐑼𐑟; 𐑯 𐑷𐑤 𐑞 𐑤𐑨𐑯𐑛𐑟 𐑯 𐑐𐑰𐑐𐑩𐑤 𐑝 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 ·𐑚𐑮𐑦𐑑𐑩𐑯, 𐑯 𐑷𐑤 𐑞 𐑢𐑲𐑛𐑼 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑢𐑻𐑤𐑛; 𐑯 𐑞 𐑦𐑯𐑑𐑲𐑼 𐑜𐑮𐑱𐑑𐑼 𐑿𐑯𐑦𐑝𐑻𐑕 𐑝 𐑢𐑦𐑗 ·𐑥𐑳𐑜𐑩𐑤 𐑕𐑲𐑩𐑯𐑑𐑦𐑕𐑑𐑕 𐑳𐑯𐑛𐑼𐑕𐑑𐑫𐑛 𐑕𐑴 𐑥𐑳𐑗 𐑤𐑧𐑕 𐑞𐑨𐑯 𐑞𐑱 𐑚𐑦𐑤𐑰𐑝𐑛. \emph{𐑲, ·𐑣𐑨𐑮𐑦 ·𐑡𐑱𐑥𐑟 ·𐑐𐑪𐑑𐑼-·𐑧𐑝𐑩𐑯𐑟-·𐑝𐑧𐑮𐑟, 𐑛𐑵 𐑯𐑬 𐑒𐑤𐑱𐑥 𐑞𐑦𐑕 𐑑𐑧𐑮𐑦𐑑𐑼𐑦 𐑦𐑯 𐑞 𐑯𐑱𐑥 𐑝 ·𐑕𐑲𐑩𐑯𐑕.}

𐑤𐑲𐑑𐑯𐑦𐑙 𐑯 𐑔𐑳𐑯𐑛𐑼 𐑒𐑩𐑥𐑐𐑤𐑰𐑑𐑤𐑦 𐑓𐑱𐑤𐑛 𐑑 𐑓𐑤𐑨𐑖 𐑯 𐑚𐑵𐑥 𐑦𐑯 𐑞 𐑒𐑤𐑬𐑛𐑤𐑩𐑕 𐑕𐑒𐑲𐑟.

“𐑢𐑪𐑑 𐑸 𐑿 𐑕𐑥𐑲𐑤𐑦𐑙 𐑩𐑚𐑬𐑑?” 𐑦𐑯𐑒𐑢𐑲𐑼𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑢𐑺𐑦𐑤𐑦 𐑯 𐑢𐑽𐑦𐑤𐑦.

“𐑲'𐑥 𐑢𐑳𐑯𐑛𐑼𐑦𐑙 𐑦𐑓 𐑞𐑺'𐑟 𐑩 𐑕𐑐𐑧𐑤 𐑑 𐑥𐑱𐑒 𐑤𐑲𐑑𐑯𐑦𐑙 𐑓𐑤𐑨𐑖 𐑦𐑯 𐑞 𐑚𐑨𐑒𐑜𐑮𐑬𐑯𐑛 𐑢𐑧𐑯𐑧𐑝𐑼 𐑲 𐑥𐑱𐑒 𐑩𐑯 𐑪𐑥𐑦𐑯𐑩𐑕 𐑮𐑧𐑟𐑩𐑤𐑵𐑖𐑩𐑯,” 𐑦𐑒𐑕𐑐𐑤𐑱𐑯𐑛 ·𐑣𐑨𐑮𐑦. 𐑣𐑰 𐑢𐑪𐑟 𐑒𐑺𐑓𐑩𐑤𐑦 𐑥𐑧𐑥𐑼𐑲𐑟𐑦𐑙 𐑞 𐑦𐑜𐑟𐑨𐑒𐑑 𐑢𐑻𐑛𐑟 𐑝 𐑣𐑦𐑟 𐑪𐑥𐑦𐑯𐑩𐑕 𐑮𐑧𐑟𐑩𐑤𐑵𐑖𐑩𐑯 𐑕𐑴 𐑞𐑨𐑑 𐑓𐑿𐑗𐑼 𐑣𐑦𐑕𐑑𐑼𐑦 𐑚𐑫𐑒𐑕 𐑢𐑫𐑛 𐑜𐑧𐑑 𐑦𐑑 𐑮𐑲𐑑.

“𐑲 𐑣𐑨𐑝 𐑞 𐑛𐑦𐑕𐑑𐑦𐑙𐑒𐑑 𐑓𐑰𐑤𐑦𐑙 𐑞𐑨𐑑 𐑲 𐑷𐑑 𐑑 𐑚𐑰 𐑛𐑵𐑦𐑙 𐑕𐑳𐑥𐑔𐑦𐑙 𐑩𐑚𐑬𐑑 𐑞𐑦𐑕,” 𐑕𐑲𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤.

“𐑦𐑜𐑯𐑹 𐑦𐑑, 𐑦𐑑'𐑤 𐑜𐑴 𐑩𐑢𐑱. 𐑵, 𐑖𐑲𐑯𐑦!” ·𐑣𐑨𐑮𐑦 𐑐𐑫𐑑 𐑣𐑦𐑟 𐑔𐑷𐑑𐑕 𐑝 𐑢𐑻𐑤𐑛 𐑒𐑪𐑙𐑒𐑢𐑧𐑕𐑑 𐑑𐑧𐑥𐑐𐑼𐑼𐑦𐑤𐑦 𐑪𐑯 𐑣𐑴𐑤𐑛 𐑯 𐑕𐑒𐑦𐑐𐑑 𐑴𐑝𐑼 𐑑 𐑩 𐑖𐑪𐑐 𐑢𐑦𐑞 𐑩𐑯 𐑴𐑐𐑩𐑯 𐑛𐑦𐑕𐑐𐑤𐑱, 𐑯 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑓𐑪𐑤𐑴𐑛.

\later

·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑯𐑬 𐑚𐑷𐑑 𐑣𐑦𐑟 𐑐𐑴𐑖𐑩𐑯𐑟 𐑦𐑯𐑜𐑮𐑰𐑛𐑾𐑯𐑑𐑕 𐑯 𐑒𐑷𐑤𐑛𐑮𐑩𐑯, 𐑯, 𐑴, 𐑩 𐑓𐑿 𐑥𐑹 𐑔𐑦𐑙𐑟. 𐑲𐑑𐑩𐑥𐑟 𐑞𐑨𐑑 𐑕𐑰𐑥𐑛 𐑤𐑲𐑒 𐑜𐑫𐑛 𐑔𐑦𐑙𐑟 𐑑 𐑒𐑨𐑮𐑦 𐑦𐑯 ·𐑣𐑨𐑮𐑦'𐑟 ·𐑚𐑨𐑜 𐑝 ·𐑣𐑴𐑤𐑛𐑦𐑙 (·𐑱𐑒𐑩 ·𐑥𐑴𐑒 ·𐑕𐑵𐑐𐑼 ·𐑐𐑬𐑗 QX31 𐑢𐑦𐑞 ·𐑳𐑯𐑛𐑦𐑑𐑧𐑒𐑑𐑩𐑚𐑩𐑤 ·𐑦𐑒𐑕𐑑𐑧𐑯𐑖𐑩𐑯 ·𐑗𐑸𐑥, ·𐑮𐑦𐑑𐑮𐑰𐑝𐑩𐑤 ·𐑗𐑸𐑥, 𐑯 ·𐑢𐑲𐑛𐑩𐑯𐑦𐑙 ·𐑤𐑦𐑐). 𐑕𐑥𐑸𐑑, 𐑕𐑧𐑯𐑕𐑩𐑚𐑩𐑤 𐑐𐑻𐑗𐑩𐑕𐑩𐑟.

·𐑣𐑨𐑮𐑦 𐑡𐑧𐑯𐑿𐑦𐑯𐑤𐑦 𐑛𐑦𐑛𐑩𐑯𐑑 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑢𐑲 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑢𐑪𐑟 𐑤𐑫𐑒𐑦𐑙 𐑕𐑴 \emph{𐑕𐑩𐑕𐑐𐑦𐑖𐑩𐑕}.

𐑮𐑲𐑑 𐑯𐑬, ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑦𐑯 𐑩 𐑖𐑪𐑐 𐑦𐑒𐑕𐑐𐑧𐑯𐑕𐑦𐑝 𐑦𐑯𐑳𐑓 𐑑 𐑛𐑦𐑕𐑐𐑤𐑱 𐑦𐑯 𐑞 𐑑𐑢𐑦𐑕𐑑𐑦𐑙 𐑥𐑱𐑯 𐑕𐑑𐑮𐑰𐑑 𐑝 ·𐑛𐑲𐑨𐑜𐑩𐑯 ·𐑨𐑤𐑦. 𐑞 𐑖𐑪𐑐 𐑣𐑨𐑛 𐑩𐑯 𐑴𐑐𐑩𐑯 𐑓𐑮𐑳𐑯𐑑 𐑢𐑦𐑞 𐑥𐑻𐑗𐑩𐑯𐑛𐑲𐑟 𐑤𐑱𐑛 𐑬𐑑 𐑪𐑯 𐑕𐑤𐑭𐑯𐑑𐑩𐑛 𐑢𐑫𐑛𐑩𐑯 𐑮𐑴𐑟, 𐑜𐑸𐑛𐑩𐑛 𐑴𐑯𐑤𐑦 𐑚𐑲 𐑕𐑤𐑲𐑑 𐑜𐑮𐑱 𐑜𐑤𐑴𐑟 𐑯 𐑩 𐑘𐑳𐑙-𐑤𐑫𐑒𐑦𐑙 𐑕𐑱𐑤𐑟𐑜𐑻𐑤 𐑦𐑯 𐑩 𐑥𐑳𐑗-𐑖𐑹𐑑𐑩𐑯𐑛 𐑝𐑻𐑠𐑩𐑯 𐑝 𐑢𐑦𐑗'𐑩𐑟 𐑮𐑴𐑚𐑟 𐑞𐑨𐑑 𐑦𐑒𐑕𐑐𐑴𐑟𐑛 𐑣𐑻 𐑯𐑰𐑟 𐑯 𐑧𐑤𐑚𐑴𐑟.

·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑦𐑜𐑟𐑨𐑥𐑦𐑯𐑦𐑙 𐑞 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑦𐑒𐑢𐑦𐑝𐑩𐑤𐑩𐑯𐑑 𐑝 𐑩 𐑓𐑻𐑕𐑑-𐑱𐑛 𐑒𐑦𐑑, 𐑞 ·𐑦𐑥𐑻𐑡𐑩𐑯𐑕𐑦 ·𐑣𐑰𐑤𐑦𐑙 ·𐑐𐑨𐑒 ·𐑐𐑤𐑳𐑕. 𐑞𐑺 𐑢𐑻 𐑑𐑵 𐑕𐑧𐑤𐑓-𐑑𐑲𐑑𐑩𐑯𐑦𐑙 𐑑𐑫𐑼𐑯𐑦𐑒𐑱𐑟. 𐑩 𐑕𐑦𐑮𐑦𐑯𐑡 𐑝 𐑢𐑪𐑑 𐑤𐑫𐑒𐑑 𐑤𐑲𐑒 𐑤𐑦𐑒𐑢𐑦𐑛 𐑓𐑲𐑼, 𐑢𐑦𐑗 𐑢𐑪𐑟 𐑕𐑩𐑐𐑴𐑕𐑑 𐑑 𐑛𐑮𐑨𐑕𐑑𐑦𐑒𐑤𐑦 𐑕𐑤𐑴 𐑕𐑻𐑒𐑿𐑤𐑱𐑖𐑩𐑯 𐑦𐑯 𐑩 𐑑𐑮𐑰𐑑𐑩𐑛 𐑺𐑾 𐑢𐑲𐑤 𐑥𐑱𐑯𐑑𐑱𐑯𐑦𐑙 𐑪𐑒𐑕𐑦𐑡𐑩𐑯𐑱𐑖𐑩𐑯 𐑝 𐑞 𐑚𐑤𐑳𐑛 𐑓 𐑳𐑐 𐑑 𐑔𐑮𐑰 𐑥𐑦𐑯𐑦𐑑𐑕, 𐑦𐑓 𐑿 𐑯𐑰𐑛𐑩𐑛 𐑑 𐑐𐑮𐑦𐑝𐑧𐑯𐑑 𐑩 𐑐𐑶𐑟𐑩𐑯 𐑓𐑮𐑪𐑥 𐑕𐑐𐑮𐑧𐑛𐑦𐑙 𐑔𐑮𐑵 𐑞 𐑚𐑪𐑛𐑦. 𐑢𐑲𐑑 𐑒𐑤𐑪𐑔 𐑞𐑨𐑑 𐑒𐑫𐑛 𐑚𐑰 𐑮𐑨𐑐𐑑 𐑴𐑝𐑼 𐑩 𐑐𐑸𐑑 𐑝 𐑞 𐑚𐑪𐑛𐑦 𐑑 𐑑𐑧𐑥𐑐𐑼𐑼𐑦𐑤𐑦 𐑯𐑳𐑥 𐑐𐑱𐑯. 𐑐𐑤𐑳𐑕 𐑧𐑯𐑦 𐑯𐑳𐑥𐑚𐑼 𐑝 𐑳𐑞𐑼 𐑲𐑑𐑩𐑥𐑟 𐑞𐑨𐑑 ·𐑣𐑨𐑮𐑦 𐑑𐑴𐑑𐑩𐑤𐑦 𐑓𐑱𐑤𐑛 𐑑 𐑒𐑪𐑥𐑐𐑮𐑦𐑣𐑧𐑯𐑛, 𐑤𐑲𐑒 𐑞 “·𐑛𐑦𐑥𐑧𐑯𐑑𐑼 ·𐑦𐑒𐑕𐑐𐑴𐑠𐑼 ·𐑑𐑮𐑰𐑑𐑥𐑩𐑯𐑑”, 𐑢𐑦𐑗 𐑤𐑫𐑒𐑑 𐑯 𐑕𐑥𐑧𐑤𐑛 𐑤𐑲𐑒 𐑹𐑛𐑦𐑯𐑼𐑦 𐑗𐑪𐑒𐑩𐑤𐑩𐑑. 𐑹 𐑞 “·𐑚𐑨𐑓𐑩𐑤𐑕𐑯𐑨𐑓𐑩𐑤 ·𐑒𐑬𐑯𐑑𐑼”, 𐑢𐑦𐑗 𐑤𐑫𐑒𐑑 𐑤𐑲𐑒 𐑩 𐑕𐑥𐑷𐑤 𐑒𐑢𐑦𐑝𐑼𐑦𐑙 𐑧𐑜 𐑯 𐑒𐑨𐑮𐑦𐑛 𐑩 𐑐𐑤𐑨𐑒𐑸𐑛 𐑖𐑴𐑦𐑙 𐑣𐑬 𐑑 𐑡𐑨𐑥 𐑦𐑑 𐑳𐑐 𐑕𐑳𐑥𐑢𐑳𐑯'𐑟 𐑯𐑪𐑕𐑑𐑮𐑩𐑤.

“𐑩 𐑛𐑧𐑓𐑦𐑯𐑦𐑑 𐑚𐑲 𐑨𐑑 𐑓𐑲𐑝 ·𐑜𐑨𐑤𐑾𐑯𐑟, 𐑢𐑫𐑛𐑩𐑯𐑑 𐑿 𐑩𐑜𐑮𐑰?” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑑 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑯 𐑞 𐑑𐑰𐑯𐑱𐑡 𐑕𐑱𐑤𐑟𐑜𐑻𐑤 𐑣𐑪𐑝𐑼𐑦𐑙 𐑯𐑽𐑚𐑲 𐑯𐑪𐑛𐑩𐑛 𐑰𐑜𐑼𐑤𐑦.

·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑦𐑒𐑕𐑐𐑧𐑒𐑑𐑩𐑛 𐑞 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑑 𐑥𐑱𐑒 𐑕𐑳𐑥 𐑕𐑹𐑑 𐑝 𐑩𐑐𐑮𐑵𐑝𐑦𐑙 𐑮𐑦𐑥𐑸𐑒 𐑩𐑚𐑬𐑑 𐑣𐑦𐑟 𐑐𐑮𐑵𐑛𐑩𐑯𐑕 𐑯 𐑐𐑮𐑦𐑐𐑺𐑩𐑛𐑯𐑩𐑕.

𐑢𐑪𐑑 𐑣𐑰 𐑢𐑪𐑟 𐑜𐑧𐑑𐑦𐑙 𐑦𐑯𐑕𐑑𐑧𐑛 𐑒𐑫𐑛 𐑴𐑯𐑤𐑦 𐑚𐑰 𐑛𐑦𐑕𐑒𐑮𐑲𐑚𐑛 𐑨𐑟 𐑞 ·𐑰𐑝𐑩𐑤 ·𐑲.

“𐑯 𐑡𐑳𐑕𐑑 \emph{𐑢𐑲},” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛 𐑢𐑦𐑞 𐑣𐑧𐑝𐑦 𐑕𐑒𐑧𐑐𐑑𐑦𐑕𐑦𐑟𐑩𐑥, “𐑛𐑵 𐑿 𐑦𐑒𐑕𐑐𐑧𐑒𐑑 𐑑 \emph{𐑯𐑰𐑛} 𐑩 𐑣𐑰𐑤𐑼'𐑟 𐑒𐑦𐑑, 𐑘𐑳𐑙 𐑥𐑨𐑯?” (𐑭𐑓𐑑𐑼 𐑞 𐑳𐑯𐑓𐑹𐑗𐑩𐑯𐑩𐑑 𐑦𐑯𐑕𐑦𐑛𐑩𐑯𐑑 𐑨𐑑 𐑞 ·𐑐𐑴𐑖𐑩𐑯𐑟 𐑖𐑪𐑐, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑢𐑪𐑟 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑩𐑝𐑶𐑛 𐑕𐑱𐑦𐑙 “·𐑥𐑼~·𐑐𐑪𐑑𐑼” 𐑢𐑲𐑤 𐑧𐑯𐑦𐑢𐑳𐑯 𐑧𐑤𐑕 𐑢𐑪𐑟 𐑯𐑽𐑚𐑲.)

𐑣𐑨𐑮𐑦'𐑟 𐑥𐑬𐑔 𐑴𐑐𐑩𐑯𐑛 𐑯 𐑒𐑤𐑴𐑟𐑛. “𐑲 𐑛𐑴𐑯𐑑 \emph{𐑦𐑒𐑕𐑐𐑧𐑒𐑑} 𐑑 𐑯𐑰𐑛 𐑦𐑑! 𐑦𐑑'𐑕 𐑡𐑳𐑕𐑑 𐑦𐑯 𐑒𐑱𐑕!”

“𐑡𐑳𐑕𐑑 𐑦𐑯 𐑒𐑱𐑕 𐑝 \emph{𐑢𐑪𐑑}?”

𐑣𐑨𐑮𐑦'𐑟 𐑲𐑟 𐑢𐑲𐑛𐑩𐑯𐑛. “𐑿 𐑔𐑦𐑙𐑒 𐑲'𐑥 \emph{𐑐𐑤𐑨𐑯𐑦𐑙} 𐑑 𐑛𐑵 𐑕𐑳𐑥𐑔𐑦𐑙 𐑛𐑱𐑯𐑡𐑼𐑩𐑕 𐑯 \emph{𐑞𐑨𐑑'𐑕} 𐑢𐑲 𐑲 𐑢𐑪𐑯𐑑 𐑩 𐑥𐑧𐑛𐑦𐑒𐑩𐑤 𐑒𐑦𐑑?”

𐑩 𐑤𐑫𐑒 𐑝 𐑜𐑮𐑦𐑥 𐑕𐑩𐑕𐑐𐑦𐑖𐑩𐑯 𐑯 𐑲𐑮𐑪𐑯𐑦𐑒 𐑛𐑦𐑕𐑚𐑦𐑤𐑰𐑓 𐑢𐑪𐑟 𐑞 𐑭𐑯𐑕𐑼.

“𐑜𐑮𐑱𐑑 ·𐑕𐑒𐑪𐑑!” 𐑕𐑧𐑛 ·𐑣𐑨𐑮𐑦. (𐑞𐑦𐑕 𐑢𐑪𐑟 𐑩𐑯 𐑦𐑒𐑕𐑐𐑮𐑧𐑖𐑩𐑯 𐑣𐑰'𐑛 𐑤𐑻𐑯𐑛 𐑓𐑮𐑪𐑥 𐑞 𐑥𐑨𐑛 𐑕𐑲𐑩𐑯𐑑𐑦𐑕𐑑 ·𐑛𐑪𐑒 ·𐑚𐑮𐑬𐑯 𐑦𐑯 \emph{𐑚𐑨𐑒 𐑑 𐑞 ·𐑓𐑿𐑗𐑼}.) “𐑢𐑻 𐑿 𐑷𐑤𐑕𐑴 𐑔𐑦𐑙𐑒𐑦𐑙 𐑞𐑨𐑑 𐑢𐑧𐑯 𐑲 𐑚𐑷𐑑 𐑞 ·𐑓𐑧𐑞𐑼-·𐑓𐑷𐑤𐑦𐑙 ·𐑐𐑴𐑖𐑩𐑯, 𐑞 ·𐑜𐑦𐑤𐑦𐑢𐑰𐑛, 𐑯 𐑞 𐑚𐑪𐑑𐑩𐑤 𐑝 ·𐑓𐑵𐑛 𐑯 ·𐑢𐑷𐑑𐑼 ·𐑐𐑦𐑤𐑟?”

“𐑘𐑧𐑕.”

·𐑣𐑨𐑮𐑦 𐑖𐑫𐑒 𐑣𐑦𐑟 𐑣𐑧𐑛 𐑦𐑯 𐑩𐑥𐑱𐑟𐑥𐑩𐑯𐑑. “𐑡𐑳𐑕𐑑 𐑢𐑪𐑑 𐑕𐑹𐑑 𐑝 𐑐𐑤𐑨𐑯 𐑛𐑵 𐑿 𐑔𐑦𐑙𐑒 𐑲 𐑣𐑨𐑝 \emph{𐑜𐑴𐑦𐑙}, 𐑣𐑽?”

“𐑲 𐑛𐑴𐑯𐑑 𐑯𐑴,” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛 𐑛𐑸𐑒𐑤𐑦, “𐑚𐑳𐑑 𐑦𐑑 𐑧𐑯𐑛𐑟 𐑲𐑞𐑼 𐑦𐑯 𐑿 𐑛𐑦𐑤𐑦𐑝𐑼𐑦𐑙 𐑩 𐑑𐑳𐑯 𐑝 𐑕𐑦𐑤𐑝𐑼 𐑑 ·𐑜𐑮𐑦𐑙𐑜𐑩𐑑𐑕, 𐑹 𐑦𐑯 𐑢𐑻𐑤𐑛 𐑛𐑪𐑥𐑦𐑯𐑱𐑖𐑩𐑯.”

“𐑢𐑻𐑤𐑛 𐑛𐑪𐑥𐑦𐑯𐑱𐑖𐑩𐑯 𐑦𐑟 𐑕𐑳𐑗 𐑩𐑯 𐑳𐑜𐑤𐑦 𐑓𐑮𐑱𐑟. 𐑲 𐑐𐑮𐑦𐑓𐑻 𐑑 𐑒𐑷𐑤 𐑦𐑑 𐑢𐑻𐑤𐑛 𐑪𐑐𐑑𐑦𐑥𐑲𐑟𐑱𐑖𐑩𐑯.”

𐑞𐑦𐑕 𐑣𐑦𐑤𐑺𐑾𐑕 𐑡𐑴𐑒 𐑓𐑱𐑤𐑛 𐑑 𐑮𐑰𐑩𐑖𐑫𐑼 𐑞 𐑢𐑦𐑗 𐑜𐑦𐑝𐑦𐑙 𐑣𐑦𐑥 𐑞 𐑤𐑫𐑒 𐑝 ·𐑛𐑵𐑥.

“𐑢𐑬,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑨𐑟 𐑣𐑰 𐑮𐑾𐑤𐑲𐑟𐑛 𐑞𐑨𐑑 𐑖𐑰 𐑢𐑪𐑟 𐑕𐑽𐑾𐑕. “𐑿 𐑮𐑾𐑤𐑦 𐑔𐑦𐑙𐑒 𐑞𐑨𐑑. 𐑿 𐑮𐑾𐑤𐑦 𐑔𐑦𐑙𐑒 𐑲'𐑥 𐑐𐑤𐑨𐑯𐑦𐑙 𐑑 𐑛𐑵 𐑕𐑳𐑥𐑔𐑦𐑙 𐑛𐑱𐑯𐑡𐑼𐑩𐑕.”

“𐑘𐑧𐑕.”

“𐑤𐑲𐑒 𐑞𐑨𐑑'𐑕 𐑞 \emph{𐑴𐑯𐑤𐑦} 𐑮𐑰𐑟𐑩𐑯 𐑧𐑯𐑦𐑢𐑳𐑯 𐑢𐑫𐑛 𐑧𐑝𐑼 𐑚𐑲 𐑩 𐑓𐑻𐑕𐑑-𐑱𐑛 𐑒𐑦𐑑? 𐑛𐑴𐑯𐑑 𐑑𐑱𐑒 𐑞𐑦𐑕 𐑞 𐑮𐑪𐑙 𐑢𐑱, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑚𐑳𐑑 \emph{𐑢𐑪𐑑 𐑕𐑹𐑑 𐑝 𐑒𐑮𐑱𐑟𐑦 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑸 𐑿 𐑿𐑕𐑑 𐑑 𐑛𐑰𐑤𐑦𐑙 𐑢𐑦𐑞}?”

“·𐑜𐑮𐑦𐑓𐑦𐑯𐑛𐑹𐑟,” 𐑕𐑐𐑨𐑑 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑞 𐑢𐑻𐑛 𐑒𐑨𐑮𐑦𐑦𐑙 𐑩 𐑓𐑮𐑱𐑑 𐑝 𐑚𐑦𐑑𐑼𐑯𐑩𐑕 𐑯 𐑛𐑦𐑕𐑐𐑺 𐑞𐑨𐑑 𐑓𐑧𐑤 𐑤𐑲𐑒 𐑩𐑯 𐑦𐑑𐑻𐑯𐑩𐑤 𐑒𐑻𐑕 𐑪𐑯 𐑷𐑤 𐑿𐑔𐑓𐑩𐑤 𐑦𐑯𐑔𐑿𐑟𐑦𐑨𐑟𐑩𐑥 𐑯 𐑣𐑲 𐑕𐑐𐑦𐑮𐑦𐑑𐑕.

“·𐑛𐑧𐑐𐑿𐑑𐑦 ·𐑣𐑧𐑛𐑥𐑦𐑕𐑑𐑮𐑩𐑕 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑦𐑯𐑻𐑝𐑩 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑐𐑫𐑑𐑦𐑙 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛𐑟 𐑕𐑑𐑻𐑯𐑤𐑦 𐑪𐑯 𐑣𐑦𐑟 𐑣𐑦𐑐𐑕. “𐑲 𐑨𐑥 𐑯𐑪𐑑 𐑜𐑴𐑦𐑙 𐑑 𐑚𐑰 𐑦𐑯 ·𐑜𐑮𐑦𐑓𐑦𐑯𐑛𐑹…”

𐑨𐑑 𐑞𐑦𐑕 𐑐𐑶𐑯𐑑 𐑞 ·𐑛𐑧𐑐𐑿𐑑𐑦 ·𐑣𐑧𐑛𐑥𐑦𐑕𐑑𐑮𐑩𐑕 𐑦𐑯𐑑𐑼𐑡𐑧𐑒𐑑𐑩𐑛 𐑕𐑳𐑥𐑔𐑦𐑙 𐑩𐑚𐑬𐑑 𐑣𐑬 𐑦𐑓 𐑣𐑰 \emph{𐑢𐑪𐑟} 𐑖𐑰 𐑢𐑫𐑛 𐑓𐑦𐑜𐑼 𐑬𐑑 𐑣𐑬 𐑑 𐑒𐑦𐑤 𐑩 𐑣𐑨𐑑, 𐑢𐑦𐑗 𐑪𐑛 𐑮𐑦𐑥𐑸𐑒 ·𐑣𐑨𐑮𐑦 𐑤𐑧𐑑 𐑐𐑭𐑕 𐑢𐑦𐑞𐑬𐑑 𐑒𐑪𐑥𐑧𐑯𐑑, 𐑞𐑴 𐑞 𐑕𐑱𐑤𐑟𐑜𐑻𐑤 𐑕𐑰𐑥𐑛 𐑑 𐑚𐑰 𐑣𐑨𐑝𐑦𐑙 𐑩 𐑕𐑳𐑛𐑩𐑯 𐑒𐑪𐑓𐑦𐑙 𐑓𐑦𐑑.

“…𐑲 𐑨𐑥 𐑜𐑴𐑦𐑙 𐑑 𐑚𐑰 𐑦𐑯 ·𐑮𐑱𐑝𐑩𐑯𐑒𐑤𐑷. 𐑯 𐑦𐑓 𐑿 𐑮𐑾𐑤𐑦 𐑔𐑦𐑙𐑒 𐑞𐑨𐑑 𐑲'𐑥 𐑐𐑤𐑨𐑯𐑦𐑙 𐑑 𐑛𐑵 𐑕𐑳𐑥𐑔𐑦𐑙 𐑛𐑱𐑯𐑡𐑼𐑩𐑕, 𐑞𐑧𐑯, 𐑪𐑯𐑩𐑕𐑑𐑤𐑦, 𐑿 𐑛𐑴𐑯𐑑 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑥𐑰 \emph{𐑨𐑑 𐑷𐑤}. 𐑲 𐑛𐑴𐑯𐑑 \emph{𐑤𐑲𐑒} 𐑛𐑱𐑯𐑡𐑼, 𐑦𐑑 𐑦𐑟 \emph{𐑕𐑒𐑺𐑦}. 𐑲 𐑨𐑥 𐑚𐑰𐑦𐑙 \emph{𐑐𐑮𐑵𐑛𐑩𐑯𐑑}. 𐑲 𐑨𐑥 𐑚𐑰𐑦𐑙 \emph{𐑒𐑷𐑖𐑩𐑕}. 𐑲 𐑨𐑥 𐑐𐑮𐑦𐑐𐑺𐑦𐑙 𐑓 \emph{𐑳𐑯𐑓𐑹𐑕𐑰𐑯 𐑒𐑩𐑯𐑑𐑦𐑯𐑡𐑩𐑯𐑕𐑦𐑟}. 𐑤𐑲𐑒 𐑥𐑲 𐑐𐑺𐑩𐑯𐑑𐑕 𐑿𐑕𐑑 𐑑 𐑕𐑦𐑙 𐑑 𐑥𐑰: \emph{𐑚𐑰 𐑐𐑮𐑦𐑐𐑺𐑛! 𐑞𐑨𐑑'𐑕 𐑞 ·𐑚𐑶 ·𐑕𐑒𐑬𐑑'𐑕 𐑥𐑸𐑗𐑦𐑙 𐑕𐑪𐑙! 𐑚𐑰 𐑐𐑮𐑦𐑐𐑺𐑛! 𐑨𐑟 𐑔𐑮𐑵 𐑤𐑲𐑓 𐑿 𐑥𐑸𐑗 𐑩𐑤𐑪𐑙! 𐑛𐑴𐑯𐑑 𐑚𐑰 𐑯𐑻𐑝𐑩𐑕, 𐑛𐑴𐑯𐑑 𐑚𐑰 𐑓𐑤𐑳𐑕𐑑𐑼𐑛, 𐑛𐑴𐑯𐑑 𐑚𐑰 𐑕𐑒𐑺𐑛—𐑚𐑰 𐑐𐑮𐑦𐑐𐑺𐑛!}”

(𐑣𐑨𐑮𐑦'𐑟 𐑐𐑺𐑩𐑯𐑑𐑕 𐑣𐑨𐑛 𐑦𐑯 𐑓𐑨𐑒𐑑 𐑴𐑯𐑤𐑦 𐑧𐑝𐑼 𐑕𐑳𐑙 𐑣𐑦𐑥 𐑞𐑴𐑟 \emph{𐑐𐑼𐑑𐑦𐑒𐑿𐑤𐑼} 𐑤𐑲𐑯𐑟 𐑝 𐑞𐑨𐑑 ·𐑑𐑪𐑥 ·𐑤𐑧𐑮𐑩𐑼 𐑕𐑪𐑙, 𐑯 ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑚𐑤𐑦𐑕𐑓𐑩𐑤𐑦 𐑳𐑯𐑩𐑢𐑺 𐑝 𐑞 𐑮𐑧𐑕𐑑.)

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑕𐑑𐑨𐑯𐑕 𐑣𐑨𐑛 𐑕𐑤𐑲𐑑𐑤𐑦 𐑕𐑪𐑓𐑩𐑯𐑛—𐑞𐑴 𐑥𐑴𐑕𐑑𐑤𐑦 𐑢𐑧𐑯 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑕𐑧𐑛 𐑞𐑨𐑑 𐑣𐑰 𐑢𐑪𐑟 𐑣𐑧𐑛𐑦𐑙 𐑓 ·𐑮𐑱𐑝𐑩𐑯𐑒𐑤𐑷. “𐑢𐑪𐑑 𐑕𐑹𐑑 𐑝\linebreak\ \emph{𐑒𐑩𐑯𐑑𐑦𐑯𐑡𐑩𐑯𐑕𐑦} 𐑛𐑵 𐑿 𐑦𐑥𐑨𐑡𐑦𐑯 𐑞𐑦𐑕 𐑒𐑦𐑑 𐑥𐑲𐑑 𐑐𐑮𐑦𐑐𐑺 𐑿 𐑓, \emph{𐑘𐑳𐑙 𐑥𐑨𐑯?}”

“𐑢𐑳𐑯 𐑝 𐑥𐑲 𐑒𐑤𐑭𐑕𐑥𐑱𐑑𐑕 𐑜𐑧𐑑𐑕 𐑚𐑦𐑑𐑩𐑯 𐑚𐑲 𐑩 𐑣𐑪𐑮𐑦𐑚𐑩𐑤 𐑥𐑪𐑯𐑕𐑑𐑼, 𐑯 𐑨𐑟 𐑲 𐑕𐑒𐑮𐑨𐑚𐑩𐑤 𐑓𐑮𐑨𐑯𐑑𐑦𐑒𐑤𐑦 𐑦𐑯 𐑥𐑲 𐑥𐑴𐑒𐑕𐑒𐑦𐑯 𐑐𐑬𐑗 𐑓 𐑕𐑳𐑥𐑔𐑦𐑙 𐑞𐑨𐑑 𐑒𐑫𐑛 𐑣𐑧𐑤𐑐 𐑣𐑻, 𐑖𐑰 𐑤𐑫𐑒𐑕 𐑨𐑑 𐑥𐑰 𐑕𐑨𐑛𐑤𐑦 𐑯 𐑢𐑦𐑞 𐑣𐑻 𐑤𐑭𐑕𐑑 𐑚𐑮𐑧𐑔 𐑕𐑧𐑟, '𐑢𐑲 𐑢𐑻𐑯𐑑 𐑿 𐑐𐑮𐑦𐑐𐑺𐑛?' 𐑯 𐑞𐑧𐑯 𐑖𐑰 𐑛𐑲𐑟, 𐑯 𐑲 𐑯𐑴 𐑨𐑟 𐑣𐑻 𐑲𐑟 𐑒𐑤𐑴𐑕 𐑞𐑨𐑑 𐑖𐑰 𐑢𐑴𐑯𐑑 𐑧𐑝𐑼 𐑓𐑼𐑜𐑦𐑝 𐑥𐑰—”

·𐑣𐑨𐑮𐑦 𐑣𐑻𐑛 𐑞 𐑕𐑱𐑤𐑟𐑜𐑻𐑤 𐑜𐑭𐑕𐑐, 𐑯 𐑣𐑰 𐑤𐑫𐑒𐑑 𐑳𐑐 𐑑 𐑕𐑰 𐑣𐑻 𐑕𐑑𐑺𐑦𐑙 𐑨𐑑 𐑣𐑦𐑥 𐑢𐑦𐑞 𐑣𐑻 𐑤𐑦𐑐𐑕 𐑐𐑮𐑧𐑕𐑑 𐑑𐑲𐑑. 𐑞𐑧𐑯 𐑞 𐑘𐑳𐑙 𐑢𐑫𐑥𐑩𐑯 𐑢𐑻𐑤𐑛 𐑯 𐑓𐑤𐑧𐑛 𐑦𐑯𐑑𐑵 𐑞 𐑛𐑰𐑐𐑼 𐑮𐑦𐑕𐑧𐑕𐑩𐑟 𐑝 𐑞 𐑖𐑪𐑐.

\emph{𐑢𐑪𐑑…?}

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑮𐑰𐑗𐑑 𐑛𐑬𐑯, 𐑯 𐑑𐑫𐑒 ·𐑣𐑨𐑮𐑦'𐑟 𐑣𐑨𐑯𐑛 𐑦𐑯 𐑣𐑻𐑟, 𐑡𐑧𐑯𐑑𐑤𐑦 𐑚𐑳𐑑 𐑓𐑻𐑥𐑤𐑦, 𐑯 𐑐𐑫𐑤𐑛 ·𐑣𐑨𐑮𐑦 𐑬𐑑 𐑝 𐑞 𐑥𐑱𐑯 𐑕𐑑𐑮𐑰𐑑 𐑝 ·𐑛𐑲𐑨𐑜𐑩𐑯 ·𐑨𐑤𐑦, 𐑤𐑰𐑛𐑦𐑙 𐑣𐑦𐑥 𐑦𐑯𐑑𐑵 𐑩𐑯 𐑨𐑤𐑦𐑢𐑱 𐑚𐑦𐑑𐑢𐑰𐑯 𐑑𐑵 𐑖𐑪𐑐𐑕 𐑢𐑦𐑗 𐑢𐑪𐑟 𐑐𐑱𐑝𐑛 𐑦𐑯 𐑛𐑻𐑑𐑦 𐑚𐑮𐑦𐑒𐑕 𐑯 𐑛𐑧𐑛-𐑧𐑯𐑛𐑩𐑛 𐑦𐑯 𐑩 𐑢𐑷𐑤 𐑝 𐑕𐑪𐑤𐑦𐑛 𐑚𐑤𐑨𐑒 𐑛𐑻𐑑.

𐑞 𐑑𐑷𐑤 𐑢𐑦𐑗 𐑐𐑶𐑯𐑑𐑩𐑛 𐑣𐑻 𐑢𐑪𐑯𐑛 𐑨𐑑 𐑞 𐑥𐑱𐑯 𐑕𐑑𐑮𐑰𐑑 𐑯 𐑕𐑐𐑴𐑒, “\emph{·𐑒𐑢𐑲𐑰𐑑𐑩𐑕}” 𐑖𐑰 𐑕𐑧𐑛, 𐑯 𐑩 𐑕𐑒𐑮𐑰𐑯 𐑝 𐑕𐑲𐑤𐑩𐑯𐑕 𐑛𐑦𐑕𐑧𐑯𐑛𐑩𐑛 𐑼𐑬𐑯𐑛 𐑞𐑧𐑥, 𐑚𐑤𐑪𐑒𐑦𐑙 𐑬𐑑 𐑷𐑤 𐑞 𐑕𐑑𐑮𐑰𐑑 𐑯𐑶𐑟𐑩𐑟.

\emph{𐑢𐑪𐑑 𐑛𐑦𐑛 𐑲 𐑛𐑵 𐑮𐑪𐑙…}

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑑𐑻𐑯𐑛 𐑑 𐑮𐑦𐑜𐑸𐑛 ·𐑣𐑨𐑮𐑦. 𐑖𐑰 𐑛𐑦𐑛𐑩𐑯𐑑 𐑣𐑨𐑝 𐑩 𐑓𐑫𐑤 𐑨𐑛𐑳𐑤𐑑 ·𐑮𐑪𐑙𐑛𐑵𐑦𐑙 ·𐑓𐑱𐑕, 𐑚𐑳𐑑 𐑣𐑻 𐑦𐑒𐑕𐑐𐑮𐑧𐑖𐑩𐑯 𐑢𐑪𐑟 𐑓𐑤𐑨𐑑, 𐑒𐑩𐑯𐑑𐑮𐑴𐑤𐑛. “𐑿 𐑥𐑳𐑕𐑑 𐑮𐑦𐑥𐑧𐑥𐑚𐑼, ·𐑥𐑼~·𐑐𐑪𐑑𐑼,” 𐑖𐑰 𐑕𐑧𐑛, “𐑞𐑨𐑑 𐑞𐑺 𐑢𐑪𐑟 𐑩 𐑢𐑹 𐑦𐑯 𐑞𐑦𐑕 𐑒𐑳𐑯𐑑𐑮𐑦 𐑯𐑪𐑑 𐑑𐑧𐑯 𐑘𐑽𐑟 𐑩𐑜𐑴. 𐑧𐑝𐑮𐑦𐑢𐑳𐑯 𐑣𐑨𐑟 𐑤𐑪𐑕𐑑 𐑕𐑳𐑥𐑢𐑳𐑯, 𐑯 𐑑 𐑕𐑐𐑰𐑒 𐑝 𐑓𐑮𐑧𐑯𐑛𐑟 𐑛𐑲𐑦𐑙 𐑦𐑯 𐑘𐑹 𐑸𐑥𐑟—𐑦𐑟 𐑯𐑪𐑑 𐑛𐑳𐑯 𐑤𐑲𐑑𐑤𐑦.”

“𐑲—𐑲 𐑛𐑦𐑛𐑩𐑯𐑑 𐑥𐑰𐑯 𐑑—” 𐑞 𐑦𐑯𐑓𐑼𐑩𐑯𐑕 𐑛𐑮𐑪𐑐𐑑 𐑤𐑲𐑒 𐑩 𐑓𐑷𐑤𐑦𐑙 𐑕𐑑𐑴𐑯 𐑦𐑯𐑑𐑵 ·𐑣𐑨𐑮𐑦'𐑟 𐑦𐑒𐑕𐑧𐑐𐑖𐑩𐑯𐑩𐑤𐑦 𐑝𐑦𐑝𐑦𐑛 𐑦𐑥𐑨𐑡𐑦𐑯𐑱𐑖𐑩𐑯. 𐑣𐑰'𐑛 𐑑𐑷𐑒𐑑 𐑩𐑚𐑬𐑑 𐑕𐑳𐑥𐑢𐑳𐑯 𐑚𐑮𐑰𐑞𐑦𐑙 𐑞𐑺 𐑤𐑭𐑕𐑑 𐑚𐑮𐑧𐑔—𐑯 𐑞𐑧𐑯 𐑞 𐑕𐑱𐑤𐑟𐑜𐑻𐑤 𐑣𐑨𐑛 𐑮𐑳𐑯 𐑩𐑢𐑱—𐑯 𐑞 𐑢𐑹 𐑣𐑨𐑛 𐑧𐑯𐑛𐑩𐑛 𐑑𐑧𐑯 𐑘𐑽𐑟 𐑩𐑜𐑴 𐑕𐑴 𐑞𐑨𐑑 𐑜𐑻𐑤 𐑢𐑫𐑛 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑨𐑑 𐑥𐑴𐑕𐑑 𐑱𐑑 𐑹 𐑯𐑲𐑯 𐑘𐑽𐑟 𐑴𐑤𐑛, 𐑢𐑧𐑯, 𐑢𐑧𐑯, “𐑲'𐑥 𐑕𐑪𐑮𐑦, 𐑲 𐑛𐑦𐑛𐑩𐑯𐑑 𐑥𐑰𐑯 𐑑…” ·𐑣𐑨𐑮𐑦 𐑗𐑴𐑒𐑑 𐑳𐑐, 𐑯 𐑑𐑻𐑯𐑛 𐑩𐑢𐑱 𐑑 𐑮𐑳𐑯 𐑓𐑮𐑪𐑥 𐑞 𐑴𐑤𐑛𐑼 𐑢𐑦𐑗'𐑩𐑟 𐑜𐑱𐑟 𐑚𐑳𐑑 𐑞𐑺 𐑢𐑪𐑟 𐑩 𐑢𐑷𐑤 𐑝 𐑛𐑻𐑑 𐑚𐑤𐑪𐑒𐑦𐑙 𐑣𐑦𐑟 𐑢𐑱 𐑯 𐑣𐑰 𐑛𐑦𐑛𐑩𐑯𐑑 𐑣𐑨𐑝 𐑣𐑦𐑟 𐑢𐑪𐑯𐑛 𐑘𐑧𐑑. “𐑲'𐑥 𐑕𐑪𐑮𐑦, 𐑲'𐑥 𐑕𐑪𐑮𐑦, 𐑲'𐑥 \emph{𐑕𐑪𐑮𐑦}!”

𐑞𐑺 𐑒𐑱𐑥 𐑩 𐑣𐑧𐑝𐑦 𐑕𐑲 𐑓𐑮𐑪𐑥 𐑚𐑦𐑣𐑲𐑯𐑛 𐑣𐑦𐑥. “𐑲 𐑯𐑴 𐑿 𐑸, ·𐑥𐑼~·𐑐𐑪𐑑𐑼.”

·𐑣𐑨𐑮𐑦 𐑛𐑺𐑛 𐑑 𐑐𐑰𐑒 𐑚𐑦𐑣𐑲𐑯𐑛 𐑣𐑦𐑥. ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑴𐑯𐑤𐑦 𐑕𐑰𐑥𐑛 𐑕𐑨𐑛, 𐑯𐑬. “𐑲'𐑥 𐑕𐑪𐑮𐑦,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑩𐑜𐑱𐑯, 𐑓𐑰𐑤𐑦𐑙 𐑮𐑧𐑗𐑩𐑛. “𐑛𐑦𐑛 𐑧𐑯𐑦𐑔𐑦𐑙 𐑤𐑲𐑒 𐑞𐑨𐑑 𐑣𐑨𐑐𐑩𐑯 𐑑—” 𐑯 𐑞𐑧𐑯 ·𐑣𐑨𐑮𐑦 𐑖𐑳𐑑 𐑣𐑦𐑟 𐑤𐑦𐑐𐑕 𐑯 𐑕𐑤𐑨𐑐𐑑 𐑩 𐑣𐑨𐑯𐑛 𐑴𐑝𐑼 𐑣𐑦𐑟 𐑥𐑬𐑔 𐑓 𐑜𐑫𐑛 𐑥𐑧𐑠𐑼.

𐑞 𐑴𐑤𐑛𐑼 𐑢𐑦𐑗'𐑩𐑟 𐑓𐑱𐑕 𐑜𐑮𐑵 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑕𐑨𐑛𐑼. “𐑿 𐑥𐑳𐑕𐑑 𐑤𐑻𐑯 𐑑 𐑔𐑦𐑙𐑒 𐑚𐑦𐑓𐑹 𐑿 𐑕𐑐𐑰𐑒, ·𐑥𐑼~·𐑐𐑪𐑑𐑼, 𐑹 𐑧𐑤𐑕 𐑜𐑴 𐑔𐑮𐑵 𐑤𐑲𐑓 𐑢𐑦𐑞𐑬𐑑 𐑥𐑧𐑯𐑦 𐑓𐑮𐑧𐑯𐑛𐑟. 𐑞𐑨𐑑 𐑣𐑨𐑟 𐑚𐑰𐑯 𐑞 𐑓𐑱𐑑 𐑝 𐑥𐑧𐑯𐑦 𐑩 ·𐑮𐑱𐑝𐑩𐑯𐑒𐑤𐑷, 𐑯 𐑲 𐑣𐑴𐑐 𐑦𐑑 𐑢𐑦𐑤 𐑯𐑪𐑑 𐑚𐑰 𐑘𐑹𐑟.”

·𐑣𐑨𐑮𐑦 𐑢𐑪𐑯𐑑𐑩𐑛 𐑑 𐑡𐑳𐑕𐑑 𐑮𐑳𐑯 𐑩𐑢𐑱. 𐑣𐑰 𐑢𐑪𐑯𐑑𐑩𐑛 𐑑 𐑐𐑫𐑤 𐑬𐑑 𐑩 𐑢𐑪𐑯𐑛 𐑯 𐑦𐑮𐑱𐑟 𐑞 𐑣𐑴𐑤 𐑔𐑦𐑙 𐑓𐑮𐑪𐑥 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑥𐑧𐑥𐑼𐑦, 𐑚𐑰 𐑚𐑨𐑒 𐑢𐑦𐑞 𐑣𐑻 𐑬𐑑𐑕𐑲𐑛 𐑞 𐑖𐑪𐑐 𐑩𐑜𐑱𐑯, \emph{𐑥𐑱𐑒 𐑦𐑑 𐑕𐑴 𐑦𐑑 𐑛𐑦𐑛𐑩𐑯𐑑 𐑣𐑨𐑐𐑩𐑯—}

“𐑚𐑳𐑑 𐑑 𐑭𐑯𐑕𐑼 𐑘𐑹 𐑒𐑢𐑧𐑕𐑗𐑩𐑯, ·𐑥𐑼~·𐑐𐑪𐑑𐑼, 𐑯𐑴, 𐑯𐑳𐑔𐑦𐑙 𐑤𐑲𐑒 \emph{𐑞𐑨𐑑} 𐑣𐑨𐑟 𐑧𐑝𐑼 𐑣𐑨𐑐𐑩𐑯𐑛 𐑑 𐑥𐑰. 𐑕𐑻𐑑𐑩𐑯𐑤𐑦 𐑲'𐑝 𐑢𐑪𐑗𐑑 𐑩 𐑓𐑮𐑧𐑯𐑛 𐑚𐑮𐑰𐑞 𐑞𐑺 𐑤𐑭𐑕𐑑, 𐑢𐑳𐑯𐑕 𐑹 𐑕𐑧𐑝𐑩𐑯 𐑑𐑲𐑥𐑟. 𐑚𐑳𐑑 𐑯𐑪𐑑 𐑢𐑳𐑯 𐑝 𐑞𐑧𐑥 𐑧𐑝𐑼 𐑒𐑻𐑕𐑑 𐑥𐑰 𐑨𐑟 𐑞𐑱 𐑛𐑲𐑛, 𐑯 𐑲 𐑯𐑧𐑝𐑼 𐑔𐑷𐑑 𐑞𐑨𐑑 𐑞𐑱 𐑢𐑫𐑛𐑩𐑯𐑑 𐑓𐑼𐑜𐑦𐑝 𐑥𐑰. 𐑢𐑲 𐑢𐑫𐑛 𐑿 \emph{𐑕𐑱} 𐑕𐑳𐑗 𐑩 𐑔𐑦𐑙, ·𐑥𐑼~·𐑐𐑪𐑑𐑼? 𐑢𐑲 𐑢𐑫𐑛 𐑿 𐑰𐑝𐑩𐑯 \emph{𐑔𐑦𐑙𐑒} 𐑦𐑑?”

“𐑲, 𐑲, 𐑲,” ·𐑣𐑨𐑮𐑦 𐑕𐑢𐑪𐑤𐑴𐑛. “𐑦𐑑'𐑕 𐑡𐑳𐑕𐑑 𐑞𐑨𐑑 𐑲 𐑷𐑤𐑢𐑱𐑟 𐑑𐑮𐑲 𐑑 𐑦𐑥𐑨𐑡𐑦𐑯 𐑞 𐑢𐑻𐑕𐑑 𐑔𐑦𐑙 𐑞𐑨𐑑 𐑒𐑫𐑛 𐑣𐑨𐑐𐑩𐑯,” 𐑯 𐑥𐑱𐑚𐑰 𐑣𐑰'𐑛 𐑷𐑤𐑕𐑴 𐑚𐑰𐑯 𐑡𐑴𐑒𐑦𐑙 𐑼𐑬𐑯𐑛 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑚𐑳𐑑 𐑣𐑰 𐑢𐑫𐑛 𐑮𐑭𐑞𐑼 𐑣𐑨𐑝 𐑚𐑦𐑑𐑩𐑯 𐑪𐑓 𐑣𐑦𐑟 𐑴𐑯 𐑑𐑳𐑙 𐑞𐑨𐑯 𐑕𐑱 𐑞𐑨𐑑 𐑯𐑬.

“𐑢𐑪𐑑?” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. “𐑚𐑳𐑑 \emph{𐑢𐑲}?”

“𐑕𐑴 𐑲 𐑒𐑨𐑯 𐑕𐑑𐑪𐑐 𐑦𐑑 𐑓𐑮𐑪𐑥 𐑣𐑨𐑐𐑩𐑯𐑦𐑙!”

“·𐑥𐑼~·𐑐𐑪𐑑𐑼…” 𐑞 𐑴𐑤𐑛𐑼 𐑢𐑦𐑗'𐑩𐑟 𐑝𐑶𐑕 𐑑𐑮𐑱𐑤𐑛 𐑪𐑓. 𐑞𐑧𐑯 𐑖𐑰 𐑕𐑲𐑛, 𐑯 𐑯𐑧𐑤𐑑 𐑛𐑬𐑯 𐑚𐑦𐑕𐑲𐑛 𐑣𐑦𐑥. “·𐑥𐑼~·𐑐𐑪𐑑𐑼,” 𐑖𐑰 𐑕𐑧𐑛, 𐑡𐑧𐑯𐑑𐑤𐑦 𐑯𐑬, “𐑦𐑑'𐑕 𐑯𐑪𐑑 𐑘𐑹 𐑮𐑦𐑕𐑐𐑪𐑯𐑕𐑩𐑚𐑦𐑤𐑦𐑑𐑦 𐑑 𐑑𐑱𐑒 𐑒𐑺 𐑝 𐑞 𐑕𐑑𐑿𐑛𐑩𐑯𐑑𐑕 𐑨𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕. 𐑦𐑑'𐑕 𐑥𐑲𐑯. 𐑲 𐑢𐑴𐑯𐑑 𐑤𐑧𐑑 𐑧𐑯𐑦𐑔𐑦𐑙 𐑚𐑨𐑛 𐑣𐑨𐑐𐑩𐑯 𐑑 𐑿 𐑹 𐑧𐑯𐑦𐑢𐑳𐑯 𐑧𐑤𐑕. ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 𐑦𐑟 𐑞 𐑕𐑱𐑓𐑩𐑕𐑑 𐑐𐑤𐑱𐑕 𐑓 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑦𐑯 𐑷𐑤 𐑞 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑢𐑻𐑤𐑛, 𐑯 ·𐑥𐑨𐑛𐑩𐑥 ·𐑐𐑪𐑥𐑓𐑮𐑦 𐑣𐑨𐑟 𐑩 𐑓𐑫𐑤 𐑣𐑰𐑤𐑼'𐑟 𐑪𐑓𐑦𐑕. 𐑿 𐑢𐑴𐑯𐑑 𐑯𐑰𐑛 𐑩 𐑣𐑰𐑤𐑼'𐑟 𐑒𐑦𐑑 𐑨𐑑 𐑷𐑤, 𐑤𐑧𐑑 𐑩𐑤𐑴𐑯 𐑩 𐑓𐑲𐑝-·𐑜𐑨𐑤𐑾𐑯 𐑢𐑳𐑯.”

“𐑚𐑳𐑑 𐑲 \emph{𐑛𐑵}!” ·𐑣𐑨𐑮𐑦 𐑚𐑻𐑕𐑑 𐑬𐑑. “\emph{·𐑯𐑴𐑢𐑺} 𐑦𐑟 𐑐𐑻𐑓𐑦𐑒𐑑𐑤𐑦 𐑕𐑱𐑓! 𐑯 𐑢𐑪𐑑 𐑦𐑓 𐑥𐑲 𐑐𐑺𐑩𐑯𐑑𐑕 𐑣𐑨𐑝 𐑩 𐑣𐑸𐑑 𐑩𐑑𐑨𐑒 𐑹 𐑜𐑧𐑑 𐑦𐑯 𐑩𐑯 𐑨𐑒𐑕𐑦𐑛𐑩𐑯𐑑 𐑢𐑧𐑯 𐑲 𐑜𐑴 𐑣𐑴𐑥 𐑓 ·𐑒𐑮𐑦𐑕𐑥𐑩𐑕—·𐑥𐑨𐑛𐑩𐑥 ·𐑐𐑪𐑥𐑓𐑮𐑦 𐑢𐑴𐑯𐑑 𐑚𐑰 𐑞𐑺, 𐑲'𐑤 𐑯𐑰𐑛 𐑩 𐑣𐑰𐑤𐑼'𐑟 𐑒𐑦𐑑 𐑝 𐑥𐑲 𐑴𐑯—”

“\emph{𐑢𐑪𐑑} 𐑦𐑯 ·𐑥𐑻𐑤𐑦𐑯'𐑟 𐑯𐑱𐑥…” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛. 𐑖𐑰 𐑕𐑑𐑫𐑛 𐑳𐑐, 𐑯 𐑤𐑫𐑒𐑑 𐑛𐑬𐑯 𐑨𐑑 ·𐑣𐑨𐑮𐑦 𐑩𐑯 𐑦𐑒𐑕𐑐𐑮𐑧𐑖𐑩𐑯 𐑑𐑹𐑯 𐑚𐑦𐑑𐑢𐑰𐑯 𐑩𐑯𐑶𐑩𐑯𐑕 𐑯 𐑒𐑩𐑯𐑕𐑻𐑯. “𐑞𐑺'𐑟 𐑯𐑴 𐑯𐑰𐑛 𐑑 𐑔𐑦𐑙𐑒 𐑩𐑚𐑬𐑑 𐑕𐑳𐑗 𐑑𐑧𐑮𐑦𐑚𐑩𐑤 𐑔𐑦𐑙𐑟, ·𐑥𐑼~·𐑐𐑪𐑑𐑼!”

𐑣𐑨𐑮𐑦'𐑟 𐑦𐑒𐑕𐑐𐑮𐑧𐑖𐑩𐑯 𐑑𐑢𐑦𐑕𐑑𐑩𐑛 𐑳𐑐 𐑦𐑯𐑑𐑵 𐑚𐑦𐑑𐑼𐑯𐑩𐑕, 𐑣𐑽𐑦𐑙 𐑞𐑨𐑑. “𐑘𐑧𐑕 𐑞𐑺 \emph{𐑦𐑟}! 𐑦𐑓 𐑿 𐑛𐑴𐑯𐑑 𐑔𐑦𐑙𐑒, 𐑿 𐑛𐑴𐑯𐑑 𐑡𐑳𐑕𐑑 𐑜𐑧𐑑 𐑣𐑻𐑑 𐑘𐑹𐑕𐑧𐑤𐑓, 𐑿 𐑧𐑯𐑛 𐑳𐑐 𐑣𐑻𐑑𐑦𐑙 𐑳𐑞𐑼 𐑐𐑰𐑐𐑩𐑤!”

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑴𐑐𐑩𐑯𐑛 𐑣𐑻 𐑥𐑬𐑔, 𐑞𐑧𐑯 𐑒𐑤𐑴𐑟𐑛 𐑦𐑑. 𐑞 𐑢𐑦𐑗 𐑮𐑳𐑚𐑛 𐑞 𐑚𐑮𐑦𐑡 𐑝 𐑣𐑻 𐑯𐑴𐑟, 𐑤𐑫𐑒𐑦𐑙 𐑔𐑷𐑑𐑓𐑩𐑤. “·𐑥𐑼~·𐑐𐑪𐑑𐑼…𐑦𐑓 𐑲 𐑢𐑻 𐑑 𐑪𐑓𐑼 𐑑 𐑤𐑦𐑕𐑩𐑯 𐑑 𐑿 𐑓 𐑩 𐑢𐑲𐑤…𐑦𐑟 𐑞𐑺 𐑧𐑯𐑦𐑔𐑦𐑙 𐑿'𐑛 𐑤𐑲𐑒 𐑑 𐑑𐑷𐑒 𐑑 𐑥𐑰 𐑩𐑚𐑬𐑑?”

“𐑩𐑚𐑬𐑑 𐑢𐑪𐑑?”

“𐑩𐑚𐑬𐑑 𐑢𐑲 𐑿'𐑼 𐑒𐑩𐑯𐑝𐑦𐑯𐑕𐑑 𐑿 𐑥𐑳𐑕𐑑 𐑷𐑤𐑢𐑱𐑟 𐑚𐑰 𐑪𐑯 𐑘𐑹 𐑜𐑸𐑛 𐑩𐑜𐑱𐑯𐑕𐑑 𐑑𐑧𐑮𐑦𐑚𐑩𐑤 𐑔𐑦𐑙𐑟 𐑣𐑨𐑐𐑩𐑯𐑦𐑙 𐑑 𐑿.”

·𐑣𐑨𐑮𐑦 𐑕𐑑𐑺𐑛 𐑨𐑑 𐑣𐑻 𐑦𐑯 𐑐𐑳𐑟𐑩𐑤𐑥𐑩𐑯𐑑. 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑩 𐑕𐑧𐑤𐑓-𐑧𐑝𐑦𐑛𐑩𐑯𐑑 𐑨𐑒𐑕𐑾𐑥. “𐑢𐑧𐑤…” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑕𐑤𐑴𐑤𐑦. 𐑣𐑰 𐑑𐑮𐑲𐑛 𐑑 𐑹𐑜𐑩𐑯𐑲𐑟 𐑣𐑦𐑟 𐑔𐑷𐑑𐑕. 𐑣𐑬 \emph{𐑒𐑫𐑛} 𐑣𐑰 𐑦𐑒𐑕𐑐𐑤𐑱𐑯 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑑 𐑩 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼-𐑢𐑦𐑗, 𐑢𐑧𐑯 𐑖𐑰 𐑛𐑦𐑛𐑩𐑯𐑑 𐑰𐑝𐑩𐑯 𐑯𐑴 𐑞 𐑚𐑱𐑕𐑦𐑒𐑕? “·𐑥𐑳𐑜𐑩𐑤 𐑮𐑰𐑕𐑻𐑗𐑼𐑟 𐑣𐑨𐑝 𐑓𐑬𐑯𐑛 𐑞𐑨𐑑 𐑐𐑰𐑐𐑩𐑤 𐑸 𐑷𐑤𐑢𐑱𐑟 𐑝𐑧𐑮𐑦 𐑪𐑐𐑑𐑦𐑥𐑦𐑕𐑑𐑦𐑒, 𐑒𐑩𐑥𐑐𐑺𐑛 𐑑 𐑮𐑦𐑨𐑤𐑦𐑑𐑦. 𐑤𐑲𐑒 𐑞𐑱 𐑕𐑱 𐑕𐑳𐑥𐑔𐑦𐑙 𐑢𐑦𐑤 𐑑𐑱𐑒 𐑑𐑵 𐑛𐑱𐑟 𐑯 𐑦𐑑 𐑑𐑱𐑒𐑕 𐑑𐑧𐑯 𐑛𐑱𐑟, 𐑹 𐑞𐑱 𐑕𐑱 𐑦𐑑'𐑤 𐑑𐑱𐑒 𐑑𐑵 𐑥𐑳𐑯𐑔𐑕 𐑯 𐑦𐑑 𐑑𐑱𐑒𐑕 𐑴𐑝𐑼 𐑔𐑻𐑑𐑦-𐑓𐑲𐑝 𐑘𐑽𐑟. 𐑓 𐑦𐑜𐑟𐑭𐑥𐑐𐑩𐑤, 𐑦𐑯 𐑢𐑳𐑯 𐑦𐑒𐑕𐑐𐑧𐑮𐑦𐑥𐑧𐑯𐑑, 𐑞𐑱 𐑭𐑕𐑒𐑑 𐑕𐑑𐑿𐑛𐑩𐑯𐑑𐑕 𐑓 𐑑𐑲𐑥𐑟 𐑚𐑲 𐑢𐑦𐑗 𐑞𐑱 𐑢𐑻 50\% 𐑖𐑫𐑼, 75\% 𐑖𐑫𐑼, 𐑯 99\% 𐑖𐑫𐑼 𐑞𐑱'𐑛 𐑒𐑩𐑥𐑐𐑤𐑰𐑑 𐑞𐑺 𐑣𐑴𐑥𐑢𐑻𐑒, 𐑯 𐑴𐑯𐑤𐑦 13\%, 19\%, 𐑯 45\% 𐑝 𐑞 𐑕𐑑𐑿𐑛𐑩𐑯𐑑𐑕 𐑓𐑦𐑯𐑦𐑖𐑑 𐑚𐑲 𐑞𐑴𐑟 𐑑𐑲𐑥𐑟. 𐑯 𐑞𐑱 𐑓𐑬𐑯𐑛 𐑞𐑨𐑑 𐑞 𐑮𐑰𐑟𐑩𐑯 𐑢𐑪𐑟 𐑞𐑨𐑑 𐑢𐑧𐑯 𐑞𐑱 𐑭𐑕𐑒𐑑 𐑢𐑳𐑯 𐑜𐑮𐑵𐑐 𐑓 𐑞𐑺 𐑚𐑧𐑕𐑑-𐑒𐑱𐑕 𐑧𐑕𐑑𐑦𐑥𐑩𐑑𐑕 𐑦𐑓 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑢𐑧𐑯𐑑 𐑨𐑟 𐑢𐑧𐑤 𐑨𐑟 𐑐𐑪𐑕𐑩𐑚𐑩𐑤, 𐑯 𐑩𐑯𐑳𐑞𐑼 𐑜𐑮𐑵𐑐 𐑓 𐑞𐑺 𐑨𐑝𐑼𐑦𐑡-𐑒𐑱𐑕 𐑧𐑕𐑑𐑦𐑥𐑩𐑑𐑕 𐑦𐑓 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑢𐑧𐑯𐑑 𐑨𐑟 𐑿𐑠𐑵𐑩𐑤, 𐑞𐑱 𐑜𐑪𐑑 𐑚𐑨𐑒 𐑭𐑯𐑕𐑼𐑟 𐑞𐑨𐑑 𐑢𐑻 𐑕𐑑𐑩𐑑𐑦𐑕𐑑𐑦𐑒𐑤𐑦 𐑦𐑯𐑛𐑦𐑕𐑑𐑦𐑙𐑜𐑢𐑦𐑖𐑩𐑚𐑩𐑤. 𐑕𐑰, 𐑦𐑓 𐑿 𐑭𐑕𐑒 𐑕𐑳𐑥𐑢𐑳𐑯 𐑢𐑪𐑑 𐑞𐑱 𐑦𐑒𐑕𐑐𐑧𐑒𐑑 𐑦𐑯 𐑞 \emph{𐑯𐑹𐑥𐑩𐑤} 𐑒𐑱𐑕, 𐑞𐑱 𐑝𐑦𐑠𐑵𐑩𐑤𐑲𐑟 𐑢𐑪𐑑 𐑤𐑫𐑒𐑕 𐑤𐑲𐑒 𐑞 𐑤𐑲𐑯 𐑝 𐑥𐑨𐑒𐑕𐑦𐑥𐑩𐑥 𐑐𐑮𐑪𐑚𐑩𐑚𐑦𐑤𐑦𐑑𐑦 𐑨𐑑 𐑰𐑗 𐑕𐑑𐑧𐑐 𐑩𐑤𐑪𐑙 𐑞 𐑢𐑱—𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑜𐑴𐑦𐑙 𐑩𐑒𐑹𐑛𐑦𐑙 𐑑 𐑐𐑤𐑨𐑯, 𐑢𐑦𐑞 𐑯𐑴 𐑕𐑼𐑐𐑮𐑲𐑟𐑩𐑟. 𐑚𐑳𐑑 𐑨𐑒𐑗𐑵𐑩𐑤𐑦, 𐑕𐑦𐑯𐑕 𐑥𐑹 𐑞𐑨𐑯 𐑣𐑭𐑓 𐑞 𐑕𐑑𐑿𐑛𐑩𐑯𐑑𐑕 𐑛𐑦𐑛𐑩𐑯𐑑 𐑓𐑦𐑯𐑦𐑖 𐑚𐑲 𐑞 𐑑𐑲𐑥 𐑞𐑱 𐑢𐑻 99\% 𐑖𐑫𐑼 𐑞𐑱'𐑛 𐑚𐑰 𐑛𐑳𐑯, 𐑮𐑦𐑨𐑤𐑦𐑑𐑦 𐑿𐑠𐑵𐑩𐑤𐑦 𐑛𐑦𐑤𐑦𐑝𐑼𐑟 𐑮𐑦𐑟𐑳𐑤𐑑𐑕 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑢𐑻𐑕 𐑞𐑨𐑯 𐑞 '𐑢𐑻𐑕𐑑-𐑒𐑱𐑕 𐑕𐑦𐑯𐑸𐑦𐑴'. 𐑦𐑑'𐑕 𐑒𐑷𐑤𐑛 𐑞 𐑐𐑤𐑨𐑯𐑦𐑙 𐑓𐑨𐑤𐑩𐑕𐑦, 𐑯 𐑞 𐑚𐑧𐑕𐑑 𐑢𐑱 𐑑 𐑓𐑦𐑒𐑕 𐑦𐑑 𐑦𐑟 𐑑 𐑭𐑕𐑒 𐑣𐑬 𐑤𐑪𐑙 𐑔𐑦𐑙𐑟 𐑑𐑫𐑒 𐑞 𐑤𐑭𐑕𐑑 𐑑𐑲𐑥 𐑿 𐑑𐑮𐑲𐑛 𐑞𐑧𐑥. 𐑞𐑨𐑑'𐑕 𐑒𐑷𐑤𐑛 𐑿𐑟𐑦𐑙 𐑞 𐑬𐑑𐑕𐑲𐑛 𐑝𐑿 𐑦𐑯𐑕𐑑𐑧𐑛 𐑝 𐑞 𐑦𐑯𐑕𐑲𐑛 𐑝𐑿. 𐑚𐑳𐑑 𐑢𐑧𐑯 𐑿'𐑼 𐑛𐑵𐑦𐑙 𐑕𐑳𐑥𐑔𐑦𐑙 𐑯𐑿 𐑯 𐑒𐑭𐑯𐑑 𐑛𐑵 𐑞𐑨𐑑, 𐑿 𐑡𐑳𐑕𐑑 𐑣𐑨𐑓 𐑑 𐑚𐑰 𐑮𐑾𐑤𐑦, 𐑮𐑾𐑤𐑦, 𐑮𐑾𐑤𐑦 𐑐𐑧𐑕𐑦𐑥𐑦𐑕𐑑𐑦𐑒. 𐑤𐑲𐑒, 𐑕𐑴 𐑐𐑧𐑕𐑦𐑥𐑦𐑕𐑑𐑦𐑒 𐑞𐑨𐑑 𐑮𐑦𐑨𐑤𐑦𐑑𐑦 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑒𐑳𐑥𐑟 𐑬𐑑 \emph{𐑚𐑧𐑑𐑼} 𐑞𐑨𐑯 𐑿 𐑦𐑒𐑕𐑐𐑧𐑒𐑑𐑩𐑛 𐑼𐑬𐑯𐑛 𐑨𐑟 𐑪𐑓𐑑𐑩𐑯 𐑯 𐑨𐑟 𐑥𐑳𐑗 𐑨𐑟 𐑦𐑑 𐑒𐑳𐑥𐑟 𐑬𐑑 𐑢𐑻𐑕. 𐑦𐑑'𐑕 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 \emph{𐑮𐑾𐑤𐑦 𐑣𐑸𐑛} 𐑑 𐑚𐑰 \emph{𐑕𐑴} 𐑐𐑧𐑕𐑦𐑥𐑦𐑕𐑑𐑦𐑒 𐑞𐑨𐑑 𐑿 𐑕𐑑𐑨𐑯𐑛 𐑩 𐑛𐑰𐑕𐑩𐑯𐑑 𐑗𐑭𐑯𐑕 𐑝 \emph{𐑳𐑯𐑛𐑼𐑖𐑵𐑑𐑦𐑙} 𐑮𐑾𐑤 𐑤𐑲𐑓. 𐑤𐑲𐑒 𐑲 𐑥𐑱𐑒 𐑞𐑦𐑕 𐑚𐑦𐑜 𐑧𐑓𐑼𐑑 𐑑 𐑚𐑰 𐑜𐑤𐑵𐑥𐑦 𐑯 𐑲 𐑦𐑥𐑨𐑡𐑦𐑯 𐑢𐑳𐑯 𐑝 𐑥𐑲 𐑒𐑤𐑭𐑕𐑥𐑱𐑑𐑕 𐑜𐑧𐑑𐑦𐑙 𐑚𐑦𐑑𐑩𐑯, 𐑚𐑳𐑑 𐑢𐑪𐑑 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑣𐑨𐑐𐑩𐑯𐑟 𐑦𐑟 𐑞𐑨𐑑 𐑞 𐑕𐑼𐑝𐑲𐑝𐑦𐑙 ·𐑛𐑧𐑔 ·𐑰𐑑𐑼𐑟 𐑩𐑑𐑨𐑒 𐑞 𐑣𐑴𐑤 𐑕𐑒𐑵𐑤 𐑑 𐑜𐑧𐑑 𐑨𐑑 𐑥𐑰. 𐑚𐑳𐑑 𐑪𐑯 𐑩 𐑣𐑨𐑐𐑽 𐑯𐑴𐑑—”

“𐑕𐑑𐑪𐑐,” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤.

·𐑣𐑨𐑮𐑦 𐑕𐑑𐑪𐑐𐑑. 𐑣𐑰 𐑣𐑨𐑛 𐑡𐑳𐑕𐑑 𐑚𐑰𐑯 𐑩𐑚𐑬𐑑 𐑑 𐑐𐑶𐑯𐑑 𐑬𐑑 𐑞𐑨𐑑 𐑨𐑑 𐑤𐑰𐑕𐑑 𐑞𐑱 𐑯𐑿 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛 𐑢𐑫𐑛𐑩𐑯𐑑 𐑩𐑑𐑨𐑒, 𐑕𐑦𐑯𐑕 𐑣𐑰 𐑢𐑪𐑟 𐑛𐑧𐑛.

“𐑲 𐑔𐑦𐑙𐑒 𐑲 𐑥𐑲𐑑 𐑯𐑪𐑑 𐑣𐑨𐑝 𐑥𐑱𐑛 𐑥𐑲𐑕𐑧𐑤𐑓 𐑒𐑤𐑽,” 𐑞 𐑢𐑦𐑗 𐑕𐑧𐑛, 𐑣𐑻 𐑐𐑮𐑦𐑕𐑲𐑕 ·𐑕𐑒𐑪𐑑𐑦𐑖 𐑝𐑶𐑕 𐑕𐑬𐑯𐑛𐑦𐑙 𐑰𐑝𐑩𐑯 𐑥𐑹 𐑒𐑺𐑓𐑩𐑤. “𐑛𐑦𐑛 𐑧𐑯𐑦𐑔𐑦𐑙 𐑣𐑨𐑐𐑩𐑯 𐑑 \emph{𐑿 𐑐𐑻𐑕𐑩𐑯𐑩𐑤𐑦} 𐑞𐑨𐑑 𐑓𐑮𐑲𐑑𐑩𐑯𐑛 𐑿, ·𐑥𐑼~·𐑐𐑪𐑑𐑼?”

“𐑢𐑪𐑑 𐑣𐑨𐑐𐑩𐑯𐑛 𐑑 𐑥𐑰 𐑐𐑻𐑕𐑩𐑯𐑩𐑤𐑦 𐑦𐑟 𐑴𐑯𐑤𐑦 𐑨𐑯𐑦𐑒𐑛𐑴𐑑𐑩𐑤 𐑧𐑝𐑦𐑛𐑩𐑯𐑕,” ·𐑣𐑨𐑮𐑦 𐑦𐑒𐑕𐑐𐑤𐑱𐑯𐑛. “𐑦𐑑 𐑛𐑳𐑟𐑩𐑯𐑑 𐑒𐑨𐑮𐑦 𐑞 𐑕𐑱𐑥 𐑢𐑱𐑑 𐑨𐑟 𐑩 𐑮𐑧𐑐𐑤𐑦𐑒𐑱𐑑𐑩𐑛, 𐑐𐑽-𐑮𐑦𐑝𐑿𐑛 𐑡𐑻𐑯𐑩𐑤 𐑸𐑑𐑦𐑒𐑩𐑤 𐑩𐑚𐑬𐑑 𐑩 𐑒𐑩𐑯𐑑𐑮𐑴𐑤𐑛 𐑕𐑑𐑳𐑛𐑦 𐑢𐑦𐑞 𐑮𐑨𐑯𐑛𐑩𐑥 𐑩𐑕𐑲𐑯𐑥𐑩𐑯𐑑, 𐑥𐑧𐑯𐑦 𐑕𐑳𐑚𐑡𐑧𐑒𐑑𐑕, 𐑤𐑸𐑡 𐑦𐑓𐑧𐑒𐑑 𐑕𐑲𐑟𐑩𐑟 𐑯 𐑕𐑑𐑮𐑪𐑙 𐑕𐑑𐑩𐑑𐑦𐑕𐑑𐑦𐑒𐑩𐑤 𐑕𐑦𐑜𐑯𐑦𐑓𐑦𐑒𐑩𐑯𐑕.”

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑐𐑦𐑯𐑗𐑑 𐑞 𐑚𐑮𐑦𐑡 𐑝 𐑣𐑻 𐑯𐑴𐑟, 𐑦𐑯𐑣𐑱𐑤𐑛, 𐑯 𐑧𐑒𐑕𐑣𐑱𐑤𐑛. “𐑲 𐑢𐑫𐑛 𐑕𐑑𐑦𐑤 𐑤𐑲𐑒 𐑑 𐑣𐑽 𐑩𐑚𐑬𐑑 𐑦𐑑,” 𐑖𐑰 𐑕𐑧𐑛.

“𐑳𐑥…” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. 𐑣𐑰 𐑑𐑫𐑒 𐑩 𐑛𐑰𐑐 𐑚𐑮𐑧𐑔. “𐑞𐑺'𐑛 𐑚𐑰𐑯 𐑕𐑳𐑥 𐑥𐑳𐑜𐑦𐑙𐑟 𐑦𐑯 𐑬𐑼 𐑯𐑱𐑚𐑼𐑣𐑫𐑛, 𐑯 𐑥𐑲 𐑥𐑳𐑞𐑼 𐑭𐑕𐑒𐑑 𐑥𐑰 𐑑 𐑮𐑦𐑑𐑻𐑯 𐑩 𐑐𐑨𐑯 𐑖𐑰'𐑛 𐑚𐑪𐑮𐑴𐑛 𐑑 𐑩 𐑯𐑱𐑚𐑼 𐑑𐑵 𐑕𐑑𐑮𐑰𐑑𐑕 𐑩𐑢𐑱, 𐑯 𐑲 𐑕𐑧𐑛 𐑲 𐑛𐑦𐑛𐑩𐑯𐑑 𐑢𐑪𐑯𐑑 𐑑 𐑚𐑦𐑒𐑪𐑟 𐑲 𐑥𐑲𐑑 𐑜𐑧𐑑 𐑥𐑳𐑜𐑛, 𐑯 𐑖𐑰 𐑕𐑧𐑛, '·𐑣𐑨𐑮𐑦, 𐑛𐑴𐑯𐑑 𐑕𐑱 𐑔𐑦𐑙𐑟 𐑤𐑲𐑒 𐑞𐑨𐑑!' 𐑤𐑲𐑒 𐑔𐑦𐑙𐑒𐑦𐑙 𐑩𐑚𐑬𐑑 𐑦𐑑 𐑢𐑫𐑛 \emph{𐑥𐑱𐑒} 𐑦𐑑 𐑣𐑨𐑐𐑩𐑯, 𐑕𐑴 𐑦𐑓 𐑲 𐑛𐑦𐑛𐑩𐑯𐑑 𐑑𐑷𐑒 𐑩𐑚𐑬𐑑 𐑦𐑑, 𐑲 𐑢𐑫𐑛 𐑚𐑰 𐑕𐑱𐑓. 𐑲 𐑑𐑮𐑲𐑛 𐑑 𐑦𐑒𐑕𐑐𐑤𐑱𐑯 𐑢𐑲 𐑲 𐑢𐑪𐑟𐑩𐑯𐑑 𐑮𐑰𐑩𐑖𐑫𐑼𐑛, 𐑯 𐑖𐑰 𐑥𐑱𐑛 𐑥𐑰 𐑒𐑨𐑮𐑦 𐑴𐑝𐑼 𐑞 𐑐𐑨𐑯 𐑧𐑯𐑦𐑢𐑱. 𐑲 𐑢𐑪𐑟 𐑑𐑵 𐑘𐑳𐑙 𐑑 𐑯𐑴 𐑣𐑬 𐑕𐑑𐑩𐑑𐑦𐑕𐑑𐑦𐑒𐑤𐑦 𐑳𐑯𐑤𐑲𐑒𐑤𐑦 𐑦𐑑 𐑢𐑪𐑟 𐑓 𐑩 𐑥𐑳𐑜𐑼 𐑑 𐑑𐑸𐑜𐑩𐑑 𐑥𐑰, 𐑚𐑳𐑑 𐑲 𐑢𐑪𐑟 𐑴𐑤𐑛 𐑦𐑯𐑳𐑓 𐑑 𐑯𐑴 𐑞𐑨𐑑 𐑯𐑪𐑑 𐑔𐑦𐑙𐑒𐑦𐑙 𐑩𐑚𐑬𐑑 𐑕𐑳𐑥𐑔𐑦𐑙 𐑛𐑳𐑟𐑩𐑯𐑑 𐑕𐑑𐑪𐑐 𐑦𐑑 𐑓𐑮𐑪𐑥 𐑣𐑨𐑐𐑩𐑯𐑦𐑙, 𐑕𐑴 𐑲 𐑢𐑪𐑟 𐑮𐑾𐑤𐑦 𐑕𐑒𐑺𐑛.”

“𐑯𐑳𐑔𐑦𐑙 𐑧𐑤𐑕?” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛 𐑭𐑓𐑑𐑼 𐑩 𐑐𐑷𐑟, 𐑢𐑧𐑯 𐑦𐑑 𐑚𐑦𐑒𐑱𐑥 𐑒𐑤𐑽 𐑞𐑨𐑑 ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑛𐑳𐑯. “𐑞𐑺 𐑦𐑟𐑩𐑯𐑑 𐑧𐑯𐑦𐑔𐑦𐑙 \emph{𐑧𐑤𐑕} 𐑞𐑨𐑑 𐑣𐑨𐑐𐑩𐑯𐑛 𐑑 𐑿?”

“𐑲 𐑯𐑴 𐑦𐑑 𐑛𐑳𐑟𐑩𐑯𐑑 \emph{𐑕𐑬𐑯𐑛} 𐑤𐑲𐑒 𐑥𐑳𐑗,” ·𐑣𐑨𐑮𐑦 𐑛𐑦𐑓𐑧𐑯𐑛𐑩𐑛. “𐑚𐑳𐑑 𐑦𐑑 𐑢𐑪𐑟 𐑡𐑳𐑕𐑑 𐑢𐑳𐑯 𐑝 𐑞𐑴𐑟 𐑒𐑮𐑦𐑑𐑦𐑒𐑩𐑤 𐑤𐑲𐑓 𐑥𐑴𐑥𐑩𐑯𐑑𐑕, 𐑿 𐑕𐑰? 𐑲 𐑥𐑰𐑯, 𐑲 \emph{𐑯𐑿} 𐑞𐑨𐑑 𐑯𐑪𐑑 𐑔𐑦𐑙𐑒𐑦𐑙 𐑩𐑚𐑬𐑑 𐑕𐑳𐑥𐑔𐑦𐑙 𐑛𐑳𐑟𐑩𐑯𐑑 𐑕𐑑𐑪𐑐 𐑦𐑑 𐑓𐑮𐑪𐑥 𐑣𐑨𐑐𐑩𐑯𐑦𐑙, 𐑲 \emph{𐑯𐑿} 𐑞𐑨𐑑, 𐑚𐑳𐑑 𐑲 𐑒𐑫𐑛 𐑕𐑰 𐑞𐑨𐑑 ·𐑥𐑳𐑥 𐑮𐑾𐑤𐑦 𐑔𐑷𐑑 𐑞𐑨𐑑 𐑢𐑱.” ·𐑣𐑨𐑮𐑦 𐑕𐑑𐑪𐑐𐑑, 𐑕𐑑𐑮𐑳𐑜𐑩𐑤𐑦𐑙 𐑢𐑦𐑞 𐑞 𐑨𐑙𐑜𐑼 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑕𐑑𐑸𐑑𐑦𐑙 𐑑 𐑮𐑲𐑟 𐑳𐑐 𐑩𐑜𐑱𐑯 𐑢𐑧𐑯 𐑣𐑰 𐑔𐑷𐑑 𐑩𐑚𐑬𐑑 𐑦𐑑. “𐑖𐑰 \emph{𐑢𐑫𐑛𐑩𐑯𐑑 𐑤𐑦𐑕𐑩𐑯}. 𐑲 𐑑𐑮𐑲𐑛 𐑑 𐑑𐑧𐑤 𐑣𐑻, 𐑲 \emph{𐑚𐑧𐑜𐑛} 𐑣𐑻 𐑯𐑪𐑑 𐑑 𐑕𐑧𐑯𐑛 𐑥𐑰 𐑬𐑑, 𐑯 𐑖𐑰 \emph{𐑤𐑭𐑓𐑑 𐑦𐑑 𐑪𐑓}. 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑲 𐑕𐑧𐑛, 𐑖𐑰 𐑑𐑮𐑰𐑑𐑩𐑛 𐑤𐑲𐑒 𐑕𐑳𐑥 𐑕𐑹𐑑 𐑝 𐑚𐑦𐑜 𐑡𐑴𐑒…” ·𐑣𐑨𐑮𐑦 𐑓𐑹𐑕𐑑 𐑞 𐑚𐑤𐑨𐑒 𐑮𐑱𐑡 𐑚𐑨𐑒 𐑛𐑬𐑯 𐑩𐑜𐑱𐑯. “𐑞𐑨𐑑'𐑕 𐑢𐑧𐑯 𐑲 𐑮𐑾𐑤𐑲𐑟𐑛 𐑞𐑨𐑑 𐑧𐑝𐑮𐑦𐑢𐑳𐑯 𐑣𐑵 𐑢𐑪𐑟 𐑕𐑩𐑐𐑴𐑕𐑑 𐑑 𐑐𐑮𐑩𐑑𐑧𐑒𐑑 𐑥𐑰 𐑢𐑪𐑟 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑒𐑮𐑱𐑟𐑦, 𐑯 𐑞𐑨𐑑 𐑞𐑱 𐑢𐑫𐑛𐑩𐑯𐑑 𐑤𐑦𐑕𐑩𐑯 𐑑 𐑥𐑰 𐑯𐑴 𐑥𐑨𐑑𐑼 𐑣𐑬 𐑥𐑳𐑗 𐑲 𐑚𐑧𐑜𐑛 𐑞𐑧𐑥, 𐑯 𐑞𐑨𐑑 𐑲 𐑒𐑫𐑛𐑩𐑯𐑑 𐑧𐑝𐑼 𐑮𐑦𐑤𐑲 𐑪𐑯 𐑞𐑧𐑥 𐑑 𐑜𐑧𐑑 𐑧𐑯𐑦𐑔𐑦𐑙 𐑮𐑲𐑑.” 𐑕𐑳𐑥𐑑𐑲𐑥𐑟 𐑜𐑫𐑛 𐑦𐑯𐑑𐑧𐑯𐑖𐑩𐑯𐑟 𐑢𐑻𐑯𐑑 𐑦𐑯𐑳𐑓, 𐑕𐑳𐑥𐑑𐑲𐑥𐑟 𐑿 𐑣𐑨𐑛 𐑑 𐑚𐑰 𐑕𐑱𐑯…

𐑞𐑺 𐑢𐑪𐑟 𐑩 𐑤𐑪𐑙 𐑕𐑲𐑤𐑩𐑯𐑕.

·𐑣𐑨𐑮𐑦 𐑑𐑫𐑒 𐑞 𐑑𐑲𐑥 𐑑 𐑚𐑮𐑰𐑞 𐑛𐑰𐑐𐑤𐑦 𐑯 𐑒𐑭𐑥 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑛𐑬𐑯. 𐑞𐑺 𐑢𐑪𐑟 𐑯𐑴 𐑐𐑶𐑯𐑑 𐑦𐑯 𐑜𐑧𐑑𐑦𐑙 𐑨𐑙𐑜𐑮𐑦. 𐑞𐑺 𐑢𐑪𐑟 𐑯𐑴 𐑐𐑶𐑯𐑑 𐑦𐑯 𐑜𐑧𐑑𐑦𐑙 𐑨𐑙𐑜𐑮𐑦. \emph{𐑷𐑤} 𐑐𐑺𐑩𐑯𐑑𐑕 𐑢𐑻 𐑤𐑲𐑒 𐑞𐑨𐑑, \emph{𐑯𐑴} 𐑨𐑛𐑳𐑤𐑑 𐑢𐑫𐑛 𐑤𐑴𐑼 𐑞𐑧𐑥𐑕𐑧𐑤𐑝𐑟 𐑓𐑸 𐑦𐑯𐑳𐑓 𐑑 𐑐𐑤𐑱𐑕 𐑞𐑧𐑥𐑕𐑧𐑤𐑝𐑟 𐑪𐑯 𐑤𐑧𐑝𐑩𐑤 𐑜𐑮𐑬𐑯𐑛 𐑢𐑦𐑞 𐑩 𐑗𐑲𐑤𐑛 𐑯 𐑤𐑦𐑕𐑩𐑯, 𐑣𐑦𐑟 𐑡𐑩𐑯𐑧𐑑𐑦𐑒 𐑐𐑺𐑩𐑯𐑑𐑕 𐑢𐑫𐑛 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑯𐑴 𐑛𐑦𐑓𐑼𐑩𐑯𐑑. ·𐑕𐑨𐑯𐑦𐑑𐑦 𐑢𐑪𐑟 𐑩 𐑑𐑲𐑯𐑦 𐑕𐑐𐑸𐑒 𐑦𐑯 𐑞 𐑯𐑲𐑑, 𐑩𐑯 𐑦𐑯𐑓𐑦𐑯𐑦𐑑𐑧𐑕𐑦𐑥𐑩𐑤𐑦 𐑮𐑺 𐑦𐑒𐑕𐑧𐑐𐑖𐑩𐑯 𐑑 𐑞 𐑮𐑵𐑤 𐑝 𐑥𐑨𐑛𐑯𐑩𐑕, 𐑕𐑴 𐑞𐑺 𐑢𐑪𐑟 𐑯𐑴 𐑐𐑶𐑯𐑑 𐑦𐑯 𐑜𐑧𐑑𐑦𐑙 𐑨𐑙𐑜𐑮𐑦.

·𐑣𐑨𐑮𐑦 𐑛𐑦𐑛𐑩𐑯𐑑 𐑤𐑲𐑒 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑢𐑧𐑯 𐑣𐑰 𐑢𐑪𐑟 𐑨𐑙𐑜𐑮𐑦.

“𐑔𐑨𐑙𐑒 𐑿 𐑓 𐑖𐑺𐑦𐑙 𐑞𐑨𐑑, ·𐑥𐑼~·𐑐𐑪𐑑𐑼,” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑭𐑓𐑑𐑼 𐑩 𐑢𐑲𐑤. 𐑞𐑺 𐑢𐑪𐑟 𐑩𐑯 𐑨𐑚𐑕𐑑𐑮𐑨𐑒𐑑𐑩𐑛 𐑤𐑫𐑒 𐑪𐑯 𐑣𐑻 𐑓𐑱𐑕 (𐑷𐑤𐑥𐑴𐑕𐑑 𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦 𐑞 𐑕𐑱𐑥 𐑤𐑫𐑒 𐑞𐑨𐑑 𐑣𐑨𐑛 𐑩𐑐𐑽𐑛 𐑪𐑯 ·𐑣𐑨𐑮𐑦'𐑟 𐑴𐑯 𐑓𐑱𐑕 𐑢𐑲𐑤 𐑦𐑒𐑕𐑐𐑧𐑮𐑦𐑥𐑧𐑯𐑑𐑦𐑙 𐑪𐑯 𐑞 𐑐𐑬𐑗, 𐑦𐑓 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑴𐑯𐑤𐑦 𐑕𐑰𐑯 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑦𐑯 𐑩 𐑥𐑦𐑮𐑼 𐑑 𐑮𐑾𐑤𐑲𐑟 𐑞𐑨𐑑). “𐑲 𐑖𐑨𐑤 𐑣𐑨𐑓 𐑑 𐑔𐑦𐑙𐑒 𐑩𐑚𐑬𐑑 𐑞𐑦𐑕.” 𐑖𐑰 𐑑𐑻𐑯𐑛 𐑑𐑩𐑢𐑹𐑛𐑟 𐑞 𐑨𐑤𐑦 𐑥𐑬𐑔, 𐑯 𐑮𐑱𐑟𐑛 𐑣𐑻 𐑢𐑪𐑯𐑛—

“𐑳𐑥,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, “𐑒𐑨𐑯 𐑢𐑰 𐑜𐑴 𐑜𐑧𐑑 𐑞 𐑣𐑰𐑤𐑼'𐑟 𐑒𐑦𐑑 𐑯𐑬?”

𐑞 𐑢𐑦𐑗 𐑐𐑷𐑟𐑛, 𐑯 𐑤𐑫𐑒𐑑 𐑚𐑨𐑒 𐑨𐑑 𐑣𐑦𐑥 𐑕𐑑𐑧𐑛𐑦𐑤𐑦. “𐑯 𐑦𐑓 𐑲 𐑕𐑱 𐑯𐑴—𐑞𐑨𐑑 𐑦𐑑 𐑦𐑟 𐑑𐑵 𐑦𐑒𐑕𐑐𐑧𐑯𐑕𐑦𐑝 𐑯 𐑿 𐑢𐑴𐑯𐑑 𐑯𐑰𐑛 𐑦𐑑—𐑞𐑧𐑯 𐑢𐑪𐑑?”

𐑣𐑨𐑮𐑦'𐑟 𐑓𐑱𐑕 𐑑𐑢𐑦𐑕𐑑𐑩𐑛 𐑦𐑯 𐑚𐑦𐑑𐑼𐑯𐑩𐑕. “𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦 𐑢𐑪𐑑 𐑿'𐑼 𐑔𐑦𐑙𐑒𐑦𐑙, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. \emph{𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦} 𐑢𐑪𐑑 𐑿'𐑼 𐑔𐑦𐑙𐑒𐑦𐑙. 𐑲 𐑒𐑩𐑯𐑒𐑤𐑵𐑛 𐑿'𐑼 𐑩𐑯𐑳𐑞𐑼 𐑒𐑮𐑱𐑟𐑦 𐑨𐑛𐑳𐑤𐑑 𐑲 𐑒𐑭𐑯𐑑 𐑑𐑷𐑒 𐑑, 𐑯 𐑲 𐑕𐑑𐑸𐑑 𐑐𐑤𐑨𐑯𐑦𐑙 𐑣𐑬 𐑑 𐑜𐑧𐑑 𐑥𐑲 𐑣𐑨𐑯𐑛𐑟 𐑪𐑯 𐑩 𐑣𐑰𐑤𐑼'𐑟 𐑒𐑦𐑑 𐑧𐑯𐑦𐑢𐑱.”

“𐑲 𐑨𐑥 𐑘𐑹 𐑜𐑸𐑛𐑾𐑯 𐑪𐑯 𐑞𐑦𐑕 𐑑𐑮𐑦𐑐,” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛 𐑢𐑦𐑞 𐑩 𐑑𐑦𐑯𐑡 𐑝 𐑛𐑱𐑯𐑡𐑼. “𐑲 \emph{𐑢𐑦𐑤 𐑯𐑪𐑑} 𐑩𐑤𐑬 𐑿 𐑑 𐑐𐑫𐑖 𐑥𐑰 𐑼𐑬𐑯𐑛.”

“𐑲 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. 𐑣𐑰 𐑒𐑧𐑐𐑑 𐑞 𐑮𐑦𐑟𐑧𐑯𐑑𐑥𐑩𐑯𐑑 𐑬𐑑 𐑝 𐑣𐑦𐑟 𐑝𐑶𐑕, 𐑯 𐑛𐑦𐑛𐑩𐑯𐑑 𐑕𐑱 𐑧𐑯𐑦 𐑝 𐑞 𐑳𐑞𐑼 𐑔𐑦𐑙𐑟 𐑞𐑨𐑑 𐑒𐑱𐑥 𐑑 𐑥𐑲𐑯𐑛. ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑣𐑨𐑛 𐑑𐑴𐑤𐑛 𐑣𐑦𐑥 𐑑 𐑔𐑦𐑙𐑒 𐑚𐑦𐑓𐑹 𐑣𐑰 𐑕𐑐𐑴𐑒. 𐑣𐑰 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑢𐑫𐑛𐑩𐑯𐑑 𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑞𐑨𐑑 𐑑𐑩𐑥𐑪𐑮𐑴, 𐑚𐑳𐑑 𐑣𐑰 𐑒𐑫𐑛 𐑨𐑑 𐑤𐑰𐑕𐑑 𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑦𐑑 𐑓 𐑓𐑲𐑝 𐑥𐑦𐑯𐑦𐑑𐑕.

𐑞 𐑢𐑦𐑗'𐑩𐑟 𐑢𐑪𐑯𐑛 𐑥𐑱𐑛 𐑩 𐑕𐑤𐑲𐑑 𐑕𐑻𐑒𐑩𐑤 𐑦𐑯 𐑣𐑻 𐑣𐑨𐑯𐑛, 𐑯 𐑞 𐑯𐑶𐑟𐑩𐑟 𐑝 ·𐑛𐑲𐑨𐑜𐑩𐑯 ·𐑨𐑤𐑦 𐑒𐑱𐑥 𐑚𐑨𐑒. “𐑷𐑤 𐑮𐑲𐑑, 𐑘𐑳𐑙 𐑥𐑨𐑯,” 𐑖𐑰 𐑕𐑧𐑛. “𐑤𐑧𐑑'𐑕 𐑜𐑴 𐑜𐑧𐑑 𐑞𐑨𐑑 𐑣𐑰𐑤𐑼'𐑟 𐑒𐑦𐑑.”

𐑣𐑨𐑮𐑦'𐑟 𐑡𐑷 𐑛𐑮𐑪𐑐𐑑 𐑦𐑯 𐑕𐑼𐑐𐑮𐑲𐑟. 𐑞𐑧𐑯 𐑣𐑰 𐑣𐑳𐑮𐑦𐑛 𐑭𐑓𐑑𐑼 𐑣𐑻, 𐑷𐑤𐑥𐑴𐑕𐑑 𐑕𐑑𐑳𐑥𐑚𐑩𐑤𐑦𐑙 𐑦𐑯 𐑣𐑦𐑟 𐑕𐑳𐑛𐑩𐑯 𐑮𐑳𐑖.

\later

𐑞 𐑖𐑪𐑐 𐑢𐑪𐑟 𐑞 𐑕𐑱𐑥 𐑨𐑟 𐑞𐑱 𐑣𐑨𐑛 𐑤𐑧𐑓𐑑 𐑦𐑑, 𐑮𐑧𐑒𐑩𐑜𐑯𐑲𐑟𐑩𐑚𐑩𐑤 𐑯 𐑳𐑯𐑮𐑧𐑒𐑩𐑜𐑯𐑲𐑟𐑩𐑚𐑩𐑤 𐑲𐑑𐑩𐑥𐑟 𐑕𐑑𐑦𐑤 𐑤𐑱𐑛 𐑬𐑑 𐑪𐑯 𐑞 𐑕𐑤𐑭𐑯𐑑𐑩𐑛 𐑢𐑫𐑛𐑩𐑯 𐑛𐑦𐑕𐑐𐑤𐑱, 𐑞 𐑜𐑮𐑱 𐑜𐑤𐑴 𐑕𐑑𐑦𐑤 𐑐𐑮𐑩𐑑𐑧𐑒𐑑𐑦𐑙 𐑯 𐑞 𐑕𐑱𐑤𐑟𐑜𐑻𐑤 𐑚𐑨𐑒 𐑦𐑯 𐑣𐑻 𐑴𐑤𐑛 𐑐𐑩𐑟𐑦𐑖𐑩𐑯. 𐑞 𐑕𐑱𐑤𐑟𐑜𐑻𐑤 𐑤𐑫𐑒𐑑 𐑳𐑐 𐑨𐑟 𐑞𐑱 𐑩𐑐𐑮𐑴𐑗𐑑, 𐑣𐑻 𐑓𐑱𐑕 𐑖𐑴𐑦𐑙 𐑕𐑼𐑐𐑮𐑲𐑟.

“𐑲'𐑥 𐑕𐑪𐑮𐑦,” 𐑖𐑰 𐑕𐑧𐑛 𐑨𐑟 𐑞𐑱 𐑜𐑪𐑑 𐑒𐑤𐑴𐑕𐑼, 𐑯 ·𐑣𐑨𐑮𐑦 𐑕𐑐𐑴𐑒 𐑨𐑑 𐑷𐑤𐑥𐑴𐑕𐑑 𐑞 𐑕𐑱𐑥 𐑥𐑴𐑥𐑩𐑯𐑑, “𐑲 𐑩𐑐𐑪𐑤𐑩𐑡𐑲𐑟 𐑓—”

𐑞𐑱 𐑚𐑮𐑴𐑒 𐑪𐑓 𐑯 𐑤𐑫𐑒𐑑 𐑨𐑑 𐑰𐑗 𐑳𐑞𐑼, 𐑯 𐑞𐑧𐑯 𐑞 𐑕𐑱𐑤𐑟𐑜𐑻𐑤 𐑤𐑭𐑓𐑑 𐑩 𐑤𐑦𐑑𐑩𐑤. “𐑲 𐑛𐑦𐑛𐑩𐑯𐑑 𐑥𐑰𐑯 𐑑 𐑜𐑧𐑑 𐑿 𐑦𐑯 𐑑𐑮𐑳𐑚𐑩𐑤 𐑢𐑦𐑞 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤,” 𐑖𐑰 𐑕𐑧𐑛. 𐑣𐑻 𐑝𐑶𐑕 𐑤𐑴𐑼𐑛 𐑒𐑩𐑯𐑕𐑐𐑦𐑮𐑩𐑑𐑹𐑾𐑤𐑦. “𐑲 𐑣𐑴𐑐 𐑖𐑰 𐑢𐑪𐑟𐑩𐑯𐑑 \emph{𐑑𐑵} 𐑷𐑓𐑩𐑤 𐑑 𐑿.”

“\emph{·𐑛𐑧𐑤𐑩!}” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑕𐑬𐑯𐑛𐑦𐑙 𐑕𐑒𐑨𐑯𐑛𐑩𐑤𐑲𐑟𐑛.

“·𐑚𐑨𐑜 𐑝 𐑜𐑴𐑤𐑛,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑑 𐑣𐑦𐑟 𐑐𐑬𐑗, 𐑯 𐑞𐑧𐑯 𐑤𐑫𐑒𐑑 𐑚𐑨𐑒 𐑳𐑐 𐑨𐑑 𐑞 𐑕𐑱𐑤𐑟𐑜𐑻𐑤 𐑢𐑲𐑤 𐑣𐑰 𐑒𐑬𐑯𐑑𐑩𐑛 𐑬𐑑 𐑓𐑲𐑝 ·𐑜𐑨𐑤𐑾𐑯𐑟. “𐑛𐑴𐑯𐑑 𐑢𐑳𐑮𐑦, 𐑲 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑞𐑨𐑑 𐑖𐑰'𐑟 𐑴𐑯𐑤𐑦 𐑷𐑓𐑩𐑤 𐑑 𐑥𐑰 𐑚𐑦𐑒𐑪𐑟 𐑖𐑰 𐑤𐑳𐑝𐑟 𐑥𐑰.”

𐑣𐑰 𐑒𐑬𐑯𐑑𐑩𐑛 𐑬𐑑 𐑓𐑲𐑝 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑑 𐑞 𐑕𐑱𐑤𐑟𐑜𐑻𐑤 𐑢𐑲𐑤 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑢𐑪𐑟 𐑕𐑐𐑤𐑳𐑑𐑼𐑦𐑙 𐑕𐑳𐑥𐑔𐑦𐑙 𐑳𐑯𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑. “𐑢𐑳𐑯 ·𐑦𐑥𐑻𐑡𐑩𐑯𐑕𐑦 ·𐑣𐑰𐑤𐑦𐑙 ·𐑐𐑨𐑒 ·𐑐𐑤𐑳𐑕, 𐑐𐑤𐑰𐑟.”

𐑦𐑑 𐑢𐑪𐑟 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑕𐑹𐑑 𐑝 𐑳𐑯𐑯𐑻𐑝𐑦𐑙 𐑑 𐑕𐑰 𐑣𐑬 𐑞 ·𐑢𐑲𐑛𐑩𐑯𐑦𐑙 ·𐑤𐑦𐑐 𐑕𐑢𐑪𐑤𐑴𐑛 𐑞 𐑚𐑮𐑰𐑓𐑒𐑱𐑕-𐑕𐑲𐑟𐑛 𐑥𐑧𐑛𐑦𐑒𐑩𐑤 𐑒𐑦𐑑. ·𐑣𐑨𐑮𐑦 𐑒𐑫𐑛𐑩𐑯𐑑 𐑣𐑧𐑤𐑐 𐑢𐑳𐑯𐑛𐑼𐑦𐑙 𐑢𐑪𐑑 𐑢𐑫𐑛 𐑣𐑨𐑐𐑩𐑯 𐑦𐑓 𐑣𐑰 𐑑𐑮𐑲𐑛 𐑒𐑤𐑲𐑥𐑦𐑙 𐑦𐑯𐑑𐑵 𐑞 𐑥𐑴𐑒𐑕𐑒𐑦𐑯 𐑐𐑬𐑗 𐑣𐑦𐑥𐑕𐑧𐑤𐑓, 𐑜𐑦𐑝𐑩𐑯 𐑞𐑨𐑑 𐑴𐑯𐑤𐑦 𐑞 𐑐𐑻𐑕𐑩𐑯 𐑣𐑵 𐑐𐑫𐑑 𐑕𐑳𐑥𐑔𐑦𐑙 𐑦𐑯 𐑢𐑪𐑟 𐑕𐑩𐑐𐑴𐑕𐑑 𐑑 𐑚𐑰 𐑱𐑚𐑩𐑤 𐑑 𐑑𐑱𐑒 𐑦𐑑 𐑬𐑑 𐑩𐑜𐑱𐑯.

𐑢𐑧𐑯 𐑞 𐑐𐑬𐑗 𐑢𐑪𐑟 𐑛𐑳𐑯…𐑰𐑑𐑦𐑙…𐑣𐑦𐑟 𐑣𐑸𐑛-𐑢𐑳𐑯 𐑐𐑻𐑗𐑩𐑕, ·𐑣𐑨𐑮𐑦 𐑕𐑢𐑹 𐑣𐑰 𐑣𐑻𐑛 𐑩 𐑕𐑥𐑷𐑤 𐑚𐑻𐑐𐑦𐑙 𐑕𐑬𐑯𐑛 𐑭𐑓𐑑𐑼𐑢𐑼𐑛𐑟. 𐑞𐑨𐑑 \emph{𐑣𐑨𐑛} 𐑑 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑕𐑐𐑧𐑤𐑛 𐑦𐑯 𐑪𐑯 𐑐𐑻𐑐𐑩𐑕. 𐑞 𐑷𐑤𐑑𐑻𐑯𐑩𐑑𐑦𐑝 𐑣𐑲𐑐𐑪𐑔𐑦𐑕𐑦𐑕 𐑢𐑪𐑟 𐑑𐑵 𐑣𐑪𐑮𐑦𐑓𐑲𐑦𐑙 𐑑 𐑒𐑪𐑯𐑑𐑩𐑥𐑐𐑤𐑱𐑑…𐑦𐑯 𐑓𐑨𐑒𐑑 ·𐑣𐑨𐑮𐑦 𐑒𐑫𐑛𐑩𐑯𐑑 𐑰𐑝𐑩𐑯 \emph{𐑔𐑦𐑙𐑒} 𐑝 𐑧𐑯𐑦 𐑷𐑤𐑑𐑻𐑯𐑩𐑑𐑦𐑝 𐑣𐑲𐑐𐑪𐑔𐑦𐑕𐑰𐑟. ·𐑣𐑨𐑮𐑦 𐑤𐑫𐑒𐑑 𐑚𐑨𐑒 𐑳𐑐 𐑨𐑑 𐑞 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼, 𐑨𐑟 𐑞𐑱 𐑚𐑦𐑜𐑨𐑯 𐑢𐑷𐑒𐑦𐑙 𐑔𐑮𐑵 ·𐑛𐑲𐑨𐑜𐑩𐑯 ·𐑨𐑤𐑦 𐑢𐑳𐑯𐑕 𐑥𐑹. “𐑢𐑺 𐑑 𐑯𐑧𐑒𐑕𐑑?”

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑐𐑶𐑯𐑑𐑩𐑛 𐑑𐑩𐑢𐑹𐑛 𐑩 𐑖𐑪𐑐 𐑞𐑨𐑑 𐑤𐑫𐑒𐑑 𐑨𐑟 𐑦𐑓 𐑦𐑑 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑥𐑱𐑛 𐑓𐑮𐑪𐑥 𐑓𐑤𐑧𐑖 𐑦𐑯𐑕𐑑𐑧𐑛 𐑝 𐑚𐑮𐑦𐑒𐑕 𐑯 𐑒𐑳𐑝𐑼𐑛 𐑦𐑯 𐑓𐑻 𐑦𐑯𐑕𐑑𐑧𐑛 𐑝 𐑐𐑱𐑯𐑑. “𐑕𐑥𐑷𐑤 𐑐𐑧𐑑𐑕 𐑸 𐑐𐑼𐑥𐑦𐑑𐑩𐑛 𐑨𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕—𐑿 𐑒𐑫𐑛 𐑜𐑧𐑑 𐑩𐑯 𐑬𐑤 𐑑 𐑕𐑧𐑯𐑛 𐑤𐑧𐑑𐑼𐑟, 𐑓 𐑦𐑜𐑟𐑭𐑥𐑐𐑩𐑤—”

“𐑒𐑨𐑯 𐑲 𐑐𐑱 𐑩 ·𐑯𐑳𐑑 𐑹 𐑕𐑳𐑥𐑔𐑦𐑙 𐑯 \emph{𐑮𐑧𐑯𐑑} 𐑩𐑯 𐑬𐑤 𐑢𐑧𐑯 𐑲 𐑯𐑰𐑛 𐑑 𐑕𐑧𐑯𐑛 𐑥𐑱𐑤?”

“𐑘𐑧𐑕,” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤.

“𐑞𐑧𐑯 𐑲 𐑔𐑦𐑙𐑒 𐑦𐑥𐑓𐑨𐑑𐑦𐑒𐑤𐑦 \emph{𐑯𐑴}.”

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑯𐑪𐑛𐑩𐑛, 𐑨𐑟 𐑞𐑴 𐑑𐑦𐑒𐑦𐑙 𐑪𐑓 𐑩 𐑐𐑶𐑯𐑑. “𐑥𐑲𐑑 𐑲 𐑭𐑕𐑒 𐑢𐑲 𐑯𐑪𐑑?”

“𐑲 𐑣𐑨𐑛 𐑩 𐑐𐑧𐑑 𐑮𐑪𐑒 𐑢𐑳𐑯𐑕. 𐑦𐑑 𐑛𐑲𐑛.”

“𐑿 𐑛𐑴𐑯𐑑 𐑔𐑦𐑙𐑒 𐑿 𐑒𐑫𐑛 𐑑𐑱𐑒 𐑒𐑺 𐑝 𐑩 𐑐𐑧𐑑?”

“𐑲 \emph{𐑒𐑫𐑛},” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, “𐑚𐑳𐑑 𐑲 𐑢𐑫𐑛 𐑧𐑯𐑛 𐑳𐑐 𐑩𐑚𐑕𐑧𐑕𐑦𐑙 𐑷𐑤 𐑛𐑱 𐑤𐑪𐑙 𐑩𐑚𐑬𐑑 𐑢𐑧𐑞𐑼 𐑲'𐑛 𐑮𐑦𐑥𐑧𐑥𐑚𐑼𐑛 𐑑 𐑓𐑰𐑛 𐑦𐑑 𐑞𐑨𐑑 𐑛𐑱 𐑹 𐑦𐑓 𐑦𐑑 𐑢𐑪𐑟 𐑕𐑤𐑴𐑤𐑦 𐑕𐑑𐑸𐑝𐑦𐑙 𐑦𐑯 𐑦𐑑𐑕 𐑒𐑱𐑡, 𐑢𐑳𐑯𐑛𐑼𐑦𐑙 𐑢𐑺 𐑦𐑑𐑕 𐑥𐑭𐑕𐑑𐑼 𐑢𐑪𐑟 𐑯 𐑢𐑲 𐑞𐑺 𐑢𐑪𐑟𐑩𐑯𐑑 𐑧𐑯𐑦 𐑓𐑵𐑛.”

“𐑞𐑨𐑑 𐑐𐑫𐑼 𐑬𐑤,” 𐑞 𐑴𐑤𐑛𐑼 𐑢𐑦𐑗 𐑕𐑧𐑛 𐑦𐑯 𐑩 𐑕𐑪𐑓𐑑 𐑝𐑶𐑕. “𐑩𐑚𐑨𐑯𐑛𐑩𐑯𐑛 𐑤𐑲𐑒 𐑞𐑨𐑑. 𐑲 𐑢𐑳𐑯𐑛𐑼 𐑢𐑪𐑑 𐑦𐑑 𐑢𐑫𐑛 𐑛𐑵.”

“𐑢𐑧𐑤, 𐑲 𐑦𐑒𐑕𐑐𐑧𐑒𐑑 𐑦𐑑'𐑩𐑛 𐑜𐑧𐑑 𐑮𐑾𐑤𐑦 𐑣𐑳𐑙𐑜𐑮𐑦 𐑯 𐑕𐑑𐑸𐑑 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑒𐑤𐑷 𐑦𐑑𐑕 𐑢𐑱 𐑬𐑑 𐑝 𐑞 𐑒𐑱𐑡 𐑹 𐑞 𐑚𐑪𐑒𐑕 𐑹 𐑢𐑪𐑑𐑧𐑝𐑼, 𐑞𐑴 𐑦𐑑 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑢𐑫𐑛𐑩𐑯𐑑 𐑣𐑨𐑝 𐑥𐑳𐑗 𐑤𐑳𐑒 𐑢𐑦𐑞 𐑞𐑨𐑑—” ·𐑣𐑨𐑮𐑦 𐑕𐑑𐑪𐑐𐑑 𐑖𐑹𐑑.

𐑞 𐑢𐑦𐑗 𐑢𐑧𐑯𐑑 𐑪𐑯, 𐑕𐑑𐑦𐑤 𐑦𐑯 𐑞𐑨𐑑 𐑕𐑪𐑓𐑑 𐑝𐑶𐑕. “𐑯 𐑢𐑪𐑑 𐑢𐑫𐑛 𐑣𐑨𐑐𐑩𐑯 𐑑 𐑦𐑑 𐑭𐑓𐑑𐑼𐑢𐑼𐑛𐑟?”

“𐑦𐑒𐑕𐑒𐑿𐑟 𐑥𐑰,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑯 𐑣𐑰 𐑮𐑰𐑗𐑑 𐑳𐑐 𐑑 𐑑𐑱𐑒 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑚𐑲 𐑞 𐑣𐑨𐑯𐑛, 𐑡𐑧𐑯𐑑𐑤𐑦 𐑚𐑳𐑑 𐑓𐑻𐑥𐑤𐑦, 𐑯 𐑕𐑑𐑽𐑛 𐑣𐑻 𐑦𐑯𐑑𐑵 𐑘𐑧𐑑 𐑩𐑯𐑳𐑞𐑼 𐑨𐑤𐑦𐑢𐑱; 𐑭𐑓𐑑𐑼 𐑛𐑳𐑒𐑦𐑙 𐑕𐑴 𐑥𐑧𐑯𐑦 𐑢𐑧𐑤-𐑢𐑦𐑖𐑼𐑟 𐑞 𐑐𐑮𐑴𐑕𐑧𐑕 𐑣𐑨𐑛 𐑚𐑦𐑒𐑳𐑥 𐑷𐑤𐑥𐑴𐑕𐑑 𐑳𐑯𐑯𐑴𐑑𐑦𐑕𐑩𐑚𐑤𐑦 𐑮𐑵𐑑𐑰𐑯. “𐑐𐑤𐑰𐑟 𐑒𐑭𐑕𐑑 𐑞𐑨𐑑 𐑕𐑲𐑤𐑩𐑯𐑕𐑦𐑙 𐑕𐑐𐑧𐑤.”

“\emph{·𐑒𐑢𐑲𐑰𐑑𐑩𐑕.}”

𐑣𐑨𐑮𐑦'𐑟 𐑝𐑶𐑕 𐑢𐑪𐑟 𐑖𐑱𐑒𐑦𐑙. “𐑞𐑨𐑑 𐑬𐑤 𐑛𐑳𐑟 \emph{𐑯𐑪𐑑} 𐑮𐑧𐑐𐑮𐑦𐑟𐑧𐑯𐑑 𐑥𐑰, 𐑥𐑲 𐑐𐑺𐑩𐑯𐑑𐑕 \emph{𐑯𐑧𐑝𐑼} 𐑤𐑪𐑒𐑑 𐑥𐑰 𐑦𐑯 𐑩 𐑒𐑳𐑚𐑼𐑛 𐑯 𐑤𐑧𐑓𐑑 𐑥𐑰 𐑑 𐑕𐑑𐑸𐑝, 𐑲 𐑛𐑵 \emph{𐑯𐑪𐑑} 𐑣𐑨𐑝 𐑩𐑚𐑨𐑯𐑛𐑩𐑯𐑥𐑩𐑯𐑑 𐑓𐑽𐑟 𐑯 𐑲 \emph{𐑛𐑴𐑯𐑑 𐑤𐑲𐑒 𐑞 𐑑𐑮𐑧𐑯𐑛 𐑝 𐑘𐑹 𐑔𐑷𐑑𐑕, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤!}”

𐑞 𐑢𐑦𐑗 𐑤𐑫𐑒𐑑 𐑛𐑬𐑯 𐑨𐑑 𐑣𐑦𐑥 𐑜𐑮𐑱𐑝𐑤𐑦. “𐑯 𐑢𐑪𐑑 𐑔𐑷𐑑𐑕 𐑢𐑫𐑛 𐑞𐑴𐑟 𐑚𐑰, ·𐑥𐑼~·𐑐𐑪𐑑𐑼?”

“𐑿 𐑔𐑦𐑙𐑒 𐑲 𐑢𐑪𐑟,” ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑣𐑨𐑝𐑦𐑙 𐑑𐑮𐑳𐑚𐑩𐑤 𐑕𐑱𐑦𐑙 𐑦𐑑, “𐑲 𐑢𐑪𐑟 \emph{𐑩𐑚𐑿𐑟𐑛}?”

“𐑢𐑻 𐑿?”

“\emph{𐑯𐑴!}” ·𐑣𐑨𐑮𐑦 𐑖𐑬𐑑𐑩𐑛. “𐑯𐑴, 𐑲 𐑯𐑧𐑝𐑼 𐑢𐑪𐑟! 𐑛𐑵 𐑿 𐑔𐑦𐑙𐑒 𐑲'𐑥 \emph{𐑕𐑑𐑿𐑐𐑦𐑛}? 𐑲 \emph{𐑯𐑴} 𐑩𐑚𐑬𐑑 𐑞 𐑒𐑪𐑯𐑕𐑧𐑐𐑑 𐑝 𐑗𐑲𐑤𐑛 𐑩𐑚𐑿𐑕, 𐑲 \emph{𐑯𐑴} 𐑩𐑚𐑬𐑑 𐑦𐑯𐑩𐑐𐑮𐑴𐑐𐑮𐑾𐑑 𐑑𐑳𐑗𐑦𐑙 𐑯 𐑷𐑤 𐑝 𐑞𐑨𐑑 𐑯 𐑦𐑓 𐑧𐑯𐑦𐑔𐑦𐑙 𐑤𐑲𐑒 𐑞𐑨𐑑 𐑣𐑨𐑐𐑩𐑯𐑛 𐑲 𐑢𐑫𐑛 𐑒𐑷𐑤 𐑞 𐑐𐑩𐑤𐑰𐑕! 𐑯 𐑮𐑦𐑐𐑹𐑑 𐑦𐑑 𐑑 𐑞 𐑣𐑧𐑛 𐑑𐑰𐑗𐑼! 𐑯 𐑤𐑫𐑒 𐑳𐑐 𐑕𐑴𐑖𐑩𐑤 𐑕𐑻𐑝𐑦𐑕𐑩𐑟 𐑦𐑯 𐑞 𐑓𐑴𐑯 𐑚𐑫𐑒! 𐑯 𐑑𐑧𐑤 ·𐑜𐑮𐑨𐑯𐑛𐑐𐑭 𐑯 ·𐑜𐑮𐑨𐑯𐑛𐑥𐑩 𐑯 ·𐑥𐑕𐑟~·𐑓𐑦𐑜! 𐑚𐑳𐑑 𐑥𐑲 𐑐𐑺𐑩𐑯𐑑𐑕 \emph{𐑯𐑧𐑝𐑼} 𐑛𐑦𐑛 𐑧𐑯𐑦𐑔𐑦𐑙 𐑤𐑲𐑒 𐑞𐑨𐑑, 𐑯𐑧𐑝𐑼 𐑧𐑝𐑼 \emph{𐑧𐑝𐑼}! 𐑣𐑬 \emph{𐑛𐑺} 𐑿 𐑕𐑩𐑡𐑧𐑕𐑑 𐑕𐑳𐑗 𐑩 𐑔𐑦𐑙!”

𐑞 𐑴𐑤𐑛𐑼 𐑢𐑦𐑗 𐑜𐑱𐑟𐑛 𐑨𐑑 𐑣𐑦𐑥 𐑕𐑑𐑧𐑛𐑦𐑤𐑦. “𐑦𐑑 𐑦𐑟 𐑥𐑲 𐑛𐑿𐑑𐑦 𐑨𐑟 ·𐑛𐑧𐑐𐑿𐑑𐑦 ·𐑣𐑧𐑛𐑥𐑦𐑕𐑑𐑮𐑩𐑕 𐑑 𐑦𐑯𐑝𐑧𐑕𐑑𐑦𐑜𐑱𐑑 𐑐𐑪𐑕𐑩𐑚𐑩𐑤 𐑕𐑲𐑯𐑟 𐑝 𐑩𐑚𐑿𐑕 𐑦𐑯 𐑞 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑳𐑯𐑛𐑼 𐑥𐑲 𐑒𐑺.”

𐑣𐑨𐑮𐑦'𐑟 𐑨𐑙𐑜𐑼 𐑢𐑪𐑟 𐑕𐑐𐑲𐑮𐑩𐑤𐑦𐑙 𐑬𐑑 𐑝 𐑒𐑩𐑯𐑑𐑮𐑴𐑤 𐑦𐑯𐑑𐑵 𐑐𐑘𐑫𐑼, 𐑚𐑤𐑨𐑒 𐑓𐑘𐑫𐑼𐑦. “𐑛𐑴𐑯𐑑 𐑿 𐑧𐑝𐑼 \emph{𐑛𐑺} 𐑚𐑮𐑰𐑞 𐑩 𐑢𐑻𐑛 𐑝 𐑞𐑰𐑟, 𐑞𐑰𐑟 \emph{𐑦𐑯𐑕𐑦𐑯𐑿𐑱𐑖𐑩𐑯𐑟} 𐑑 𐑧𐑯𐑦𐑢𐑳𐑯 𐑧𐑤𐑕! \emph{𐑯𐑴-𐑢𐑳𐑯}, 𐑛𐑵 𐑿 𐑣𐑽 𐑥𐑰, ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤? 𐑩𐑯 𐑨𐑒𐑿𐑟𐑱𐑖𐑩𐑯 𐑤𐑲𐑒 𐑞𐑨𐑑 𐑒𐑨𐑯 𐑮𐑵𐑦𐑯 𐑐𐑰𐑐𐑩𐑤 𐑯 𐑛𐑦𐑕𐑑𐑮𐑶 𐑓𐑨𐑥𐑤𐑦𐑟 𐑰𐑝𐑩𐑯 𐑢𐑧𐑯 𐑞 𐑐𐑺𐑩𐑯𐑑𐑕 𐑸 𐑒𐑩𐑥𐑐𐑤𐑰𐑑𐑤𐑦 𐑦𐑯𐑩𐑕𐑩𐑯𐑑! 𐑲'𐑝 𐑮𐑧𐑛 𐑩𐑚𐑬𐑑 𐑦𐑑 𐑦𐑯 𐑞 𐑯𐑿𐑟𐑐𐑱𐑐𐑼𐑟!” 𐑣𐑨𐑮𐑦'𐑟 𐑝𐑶𐑕 𐑢𐑪𐑟 𐑒𐑤𐑲𐑥𐑦𐑙 𐑑 𐑩 𐑣𐑲-𐑐𐑦𐑗𐑑 𐑕𐑒𐑮𐑰𐑥. “𐑞 \emph{𐑕𐑦𐑕𐑑𐑩𐑥} 𐑛𐑳𐑟𐑩𐑯𐑑 𐑯𐑴 𐑣𐑬 𐑑 \emph{𐑕𐑑𐑪𐑐}, 𐑦𐑑 𐑛𐑳𐑟𐑩𐑯𐑑 𐑚𐑦𐑤𐑰𐑝 𐑞 𐑐𐑺𐑩𐑯𐑑𐑕 \emph{𐑹} 𐑞 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑢𐑧𐑯 𐑞𐑱 𐑕𐑱 𐑯𐑳𐑔𐑦𐑙 𐑣𐑨𐑐𐑩𐑯𐑛! \emph{𐑛𐑴𐑯𐑑 𐑿 𐑛𐑺 𐑔𐑮𐑧𐑑𐑩𐑯 𐑥𐑲 𐑓𐑨𐑥𐑤𐑦 𐑢𐑦𐑞 𐑞𐑨𐑑! 𐑲 𐑢𐑴𐑯𐑑 𐑤𐑧𐑑 𐑿 𐑛𐑦𐑕𐑑𐑮𐑶 𐑥𐑲 𐑣𐑴𐑥!}”

“·𐑣𐑨𐑮𐑦,” 𐑞 𐑴𐑤𐑛𐑼 𐑢𐑦𐑗 𐑕𐑧𐑛 𐑕𐑪𐑓𐑑𐑤𐑦, 𐑯 𐑖𐑰 𐑮𐑰𐑗𐑑 𐑬𐑑 𐑩 𐑣𐑨𐑯𐑛 𐑑𐑩𐑢𐑹𐑛𐑟 𐑣𐑦𐑥—

·𐑣𐑨𐑮𐑦 𐑑𐑫𐑒 𐑩 𐑓𐑭𐑕𐑑 𐑕𐑑𐑧𐑐 𐑚𐑨𐑒, 𐑯 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛 𐑕𐑯𐑨𐑐𐑑 𐑳𐑐 𐑯 𐑯𐑪𐑒𐑑 𐑣𐑻𐑟 𐑩𐑢𐑱.

·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑓𐑮𐑴𐑟, 𐑞𐑧𐑯 𐑖𐑰 𐑐𐑫𐑤𐑛 𐑣𐑻 𐑣𐑨𐑯𐑛 𐑚𐑨𐑒, 𐑯 𐑑𐑫𐑒 𐑩 𐑕𐑑𐑧𐑐 𐑚𐑨𐑒𐑢𐑼𐑛𐑟. “·𐑣𐑨𐑮𐑦, 𐑦𐑑'𐑕 𐑷𐑤 𐑮𐑲𐑑,” 𐑖𐑰 𐑕𐑧𐑛. “𐑲 𐑚𐑦𐑤𐑰𐑝 𐑿.”

“\emph{𐑛𐑵 𐑿,}” ·𐑣𐑨𐑮𐑦 𐑣𐑦𐑕𐑑. 𐑞 𐑓𐑘𐑫𐑼𐑦 𐑕𐑑𐑦𐑤 𐑮𐑹𐑦𐑙 𐑔𐑮𐑵 𐑣𐑦𐑟 𐑚𐑤𐑳𐑛. “𐑹 𐑸 𐑿 𐑡𐑳𐑕𐑑 𐑢𐑱𐑑𐑦𐑙 𐑑 𐑜𐑧𐑑 𐑩𐑢𐑱 𐑓𐑮𐑪𐑥 𐑥𐑰 𐑕𐑴 𐑿 𐑒𐑨𐑯 𐑓𐑲𐑤 𐑞 𐑐𐑱𐑐𐑼𐑟?”

“·𐑣𐑨𐑮𐑦, 𐑲 𐑕𐑷 𐑘𐑹 𐑣𐑬𐑕. 𐑲 𐑕𐑷 𐑿 𐑢𐑦𐑞 𐑘𐑹 𐑐𐑺𐑩𐑯𐑑𐑕. 𐑞𐑱 𐑤𐑳𐑝 𐑿. 𐑿 𐑤𐑳𐑝 𐑞𐑧𐑥. 𐑲 𐑛𐑵 𐑚𐑦𐑤𐑰𐑝 𐑿 𐑢𐑧𐑯 𐑿 𐑕𐑱 𐑞𐑨𐑑 𐑘𐑹 𐑐𐑺𐑩𐑯𐑑𐑕 𐑸 𐑯𐑪𐑑 𐑩𐑚𐑿𐑟𐑦𐑙 𐑿. 𐑚𐑳𐑑 𐑲 \emph{𐑣𐑨𐑛} 𐑑 𐑭𐑕𐑒, 𐑚𐑦𐑒𐑪𐑟 𐑞𐑺 𐑦𐑟 𐑕𐑳𐑥𐑔𐑦𐑙 𐑕𐑑𐑮𐑱𐑯𐑡 𐑨𐑑 𐑢𐑻𐑒 𐑣𐑽.”

·𐑣𐑨𐑮𐑦 𐑕𐑑𐑺𐑛 𐑨𐑑 𐑣𐑻 𐑒𐑴𐑤𐑛𐑤𐑦. “𐑤𐑲𐑒 𐑢𐑪𐑑?”

“·𐑣𐑨𐑮𐑦, 𐑲'𐑝 𐑕𐑰𐑯 𐑥𐑧𐑯𐑦 𐑩𐑚𐑿𐑟𐑛 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑦𐑯 𐑥𐑲 𐑑𐑲𐑥 𐑨𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕, 𐑦𐑑 𐑢𐑫𐑛 𐑚𐑮𐑱𐑒 𐑘𐑹 𐑣𐑸𐑑 𐑑 𐑯𐑴 𐑣𐑬 𐑥𐑧𐑯𐑦. 𐑯, 𐑢𐑧𐑯 𐑿'𐑼 𐑣𐑨𐑐𐑦, 𐑿 𐑛𐑴𐑯𐑑 𐑚𐑦𐑣𐑱𐑝 𐑤𐑲𐑒 𐑢𐑳𐑯 𐑝 𐑞𐑴𐑟 𐑗𐑦𐑤𐑛𐑮𐑩𐑯, 𐑯𐑪𐑑 𐑨𐑑 \emph{𐑷𐑤}. 𐑿 𐑕𐑥𐑲𐑤 𐑨𐑑 𐑕𐑑𐑮𐑱𐑯𐑡𐑼𐑟, 𐑿 𐑣𐑳𐑜 𐑐𐑰𐑐𐑩𐑤, 𐑲 𐑐𐑫𐑑 𐑥𐑲 𐑣𐑨𐑯𐑛 𐑪𐑯 𐑘𐑹 𐑖𐑴𐑤𐑛𐑼 𐑯 𐑿 𐑛𐑦𐑛𐑩𐑯𐑑 𐑓𐑤𐑦𐑯𐑗. 𐑚𐑳𐑑 𐑕𐑳𐑥𐑑𐑲𐑥𐑟, 𐑴𐑯𐑤𐑦 𐑕𐑳𐑥𐑑𐑲𐑥𐑟, 𐑿 𐑕𐑱 𐑹 𐑛𐑵 𐑕𐑳𐑥𐑔𐑦𐑙 𐑞𐑨𐑑 𐑕𐑰𐑥𐑟 \emph{𐑝𐑧𐑮𐑦} 𐑥𐑳𐑗 𐑤𐑲𐑒…𐑕𐑳𐑥𐑢𐑳𐑯 𐑣𐑵 𐑕𐑐𐑧𐑯𐑑 𐑣𐑦𐑟 𐑓𐑻𐑕𐑑 𐑦𐑤𐑧𐑝𐑩𐑯 𐑘𐑽𐑟 𐑤𐑪𐑒𐑑 𐑦𐑯 𐑩 𐑕𐑧𐑤𐑼. 𐑯𐑪𐑑 𐑞 𐑤𐑳𐑝𐑦𐑙 𐑓𐑨𐑥𐑤𐑦 𐑞𐑨𐑑 𐑲 𐑕𐑷.” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑑𐑦𐑤𐑑𐑩𐑛 𐑣𐑻 𐑣𐑧𐑛, 𐑣𐑻 𐑦𐑒𐑕𐑐𐑮𐑧𐑖𐑩𐑯 𐑜𐑮𐑴𐑦𐑙 𐑐𐑳𐑟𐑩𐑤𐑛 𐑩𐑜𐑱𐑯.

·𐑣𐑨𐑮𐑦 𐑑𐑫𐑒 𐑞𐑦𐑕 𐑦𐑯, 𐑐𐑮𐑴𐑕𐑧𐑕𐑦𐑙 𐑦𐑑. 𐑞 𐑚𐑤𐑨𐑒 𐑮𐑱𐑡 𐑚𐑦𐑜𐑨𐑯 𐑑 𐑛𐑮𐑱𐑯 𐑩𐑢𐑱, 𐑨𐑟 𐑦𐑑 𐑛𐑷𐑯𐑛 𐑪𐑯 𐑣𐑦𐑥 𐑞𐑨𐑑 𐑣𐑰 𐑢𐑪𐑟 𐑚𐑰𐑦𐑙 𐑤𐑦𐑕𐑩𐑯𐑛 𐑑 𐑮𐑦𐑕𐑐𐑧𐑒𐑑𐑓𐑩𐑤𐑦, 𐑯 𐑞𐑨𐑑 𐑣𐑦𐑟 𐑓𐑨𐑥𐑤𐑦 𐑢𐑪𐑟𐑩𐑯𐑑 𐑦𐑯 𐑛𐑱𐑯𐑡𐑼.

“𐑯 𐑣𐑬 \emph{𐑛𐑵} 𐑿 𐑦𐑒𐑕𐑐𐑤𐑱𐑯 𐑘𐑹 𐑪𐑚𐑟𐑼𐑝𐑱𐑖𐑩𐑯𐑟, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤?”

“𐑲 𐑛𐑴𐑯𐑑 𐑯𐑴,” 𐑖𐑰 𐑕𐑧𐑛. “𐑚𐑳𐑑 𐑦𐑑'𐑕 𐑐𐑪𐑕𐑩𐑚𐑩𐑤 𐑞𐑨𐑑 𐑕𐑳𐑥𐑔𐑦𐑙 𐑒𐑫𐑛 𐑣𐑨𐑝 𐑣𐑨𐑐𐑩𐑯𐑛 𐑑 𐑿 𐑞𐑨𐑑 𐑿 𐑛𐑴𐑯𐑑 𐑮𐑦𐑥𐑧𐑥𐑚𐑼.”

·𐑓𐑘𐑫𐑼𐑦 𐑮𐑴𐑟 𐑳𐑐 𐑩𐑜𐑱𐑯 𐑦𐑯 ·𐑣𐑨𐑮𐑦. 𐑞𐑨𐑑 𐑕𐑬𐑯𐑛𐑩𐑛 𐑷𐑤 𐑑𐑵 𐑥𐑳𐑗 𐑤𐑲𐑒 𐑢𐑪𐑑 𐑣𐑰'𐑛 𐑮𐑧𐑛 𐑦𐑯 𐑞 𐑯𐑿𐑟𐑐𐑱𐑐𐑼 𐑕𐑑𐑹𐑦𐑟 𐑝 𐑖𐑨𐑑𐑼𐑛 𐑓𐑨𐑥𐑤𐑦𐑟. “𐑕𐑩𐑐𐑮𐑧𐑕𐑑 𐑥𐑧𐑥𐑼𐑦 𐑦𐑟 𐑩 𐑤𐑴𐑛 𐑝 \emph{𐑕𐑿𐑛𐑴-𐑕𐑲𐑩𐑯𐑕}! 𐑐𐑰𐑐𐑩𐑤 𐑛𐑵 \emph{𐑯𐑪𐑑} 𐑮𐑦𐑐𐑮𐑧𐑕 𐑑𐑮𐑷𐑥𐑨𐑑𐑦𐑒 𐑥𐑧𐑥𐑼𐑦𐑟, 𐑞𐑱 𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑞𐑧𐑥 𐑷𐑤 \emph{𐑑𐑵} 𐑢𐑧𐑤 𐑓 𐑞 𐑮𐑧𐑕𐑑 𐑝 𐑞𐑺 𐑤𐑲𐑝𐑟!”

“𐑯𐑴, ·𐑥𐑼~·𐑐𐑪𐑑𐑼. 𐑞𐑺 𐑦𐑟 𐑩 ·𐑗𐑸𐑥 𐑒𐑷𐑤𐑛 ·𐑩𐑚𐑤𐑦𐑝𐑦𐑱𐑖𐑩𐑯.”

·𐑣𐑨𐑮𐑦 𐑓𐑮𐑴𐑟 𐑦𐑯 𐑐𐑤𐑱𐑕. “𐑩 𐑕𐑐𐑧𐑤 𐑞𐑨𐑑 𐑦𐑮𐑱𐑟𐑩𐑟 𐑥𐑧𐑥𐑼𐑦𐑟?”

𐑞 𐑴𐑤𐑛𐑼 𐑢𐑦𐑗 𐑯𐑪𐑛𐑩𐑛. “𐑚𐑳𐑑 𐑯𐑪𐑑 𐑷𐑤 𐑞 𐑦𐑓𐑧𐑒𐑑𐑕 𐑝 𐑞 𐑦𐑒𐑕𐑐𐑽𐑾𐑯𐑕, 𐑦𐑓 𐑿 𐑕𐑰 𐑢𐑪𐑑 𐑲'𐑥 𐑕𐑱𐑦𐑙, ·𐑥𐑼~·𐑐𐑪𐑑𐑼.”

𐑩 𐑗𐑦𐑤 𐑢𐑧𐑯𐑑 𐑛𐑬𐑯 ·𐑣𐑨𐑮𐑦'𐑟 𐑕𐑐𐑲𐑯. \emph{𐑞𐑨𐑑} 𐑣𐑲𐑐𐑪𐑔𐑦𐑕𐑦𐑕…𐑒𐑫𐑛 \emph{𐑯𐑪𐑑} 𐑚𐑰 𐑰𐑟𐑦𐑤𐑦 𐑮𐑦𐑓𐑿𐑑𐑩𐑛. “𐑚𐑳𐑑 𐑥𐑲 𐑐𐑺𐑩𐑯𐑑𐑕 𐑒𐑫𐑛𐑩𐑯𐑑 𐑛𐑵 𐑞𐑨𐑑!”

“𐑦𐑯𐑛𐑰𐑛 𐑯𐑪𐑑,” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. “𐑦𐑑 𐑢𐑫𐑛 𐑣𐑨𐑝 𐑑𐑱𐑒𐑩𐑯 𐑕𐑳𐑥𐑢𐑳𐑯 𐑓𐑮𐑪𐑥 𐑞 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑢𐑻𐑤𐑛. 𐑞𐑺'𐑟…𐑯𐑴 𐑢𐑱 𐑑 𐑚𐑰 𐑕𐑻𐑑𐑩𐑯, 𐑲'𐑥 𐑩𐑓𐑮𐑱𐑛.”

𐑣𐑨𐑮𐑦'𐑟 𐑮𐑨𐑖𐑩𐑯𐑩𐑤𐑦𐑕𐑑 𐑕𐑒𐑦𐑤𐑟 𐑚𐑦𐑜𐑨𐑯 𐑑 𐑚𐑵𐑑 𐑳𐑐 𐑩𐑜𐑱𐑯. “·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑣𐑬 𐑖𐑫𐑼 𐑸 𐑿 𐑝 𐑘𐑹 𐑪𐑚𐑟𐑼𐑝𐑱𐑖𐑩𐑯𐑟, 𐑯 𐑢𐑪𐑑 𐑷𐑤𐑑𐑻𐑯𐑩𐑑𐑦𐑝 𐑧𐑒𐑕𐑐𐑤𐑩𐑯𐑱𐑖𐑩𐑯𐑟 𐑒𐑫𐑛 𐑞𐑺 𐑷𐑤𐑕𐑴 𐑚𐑰?”

𐑞 𐑢𐑦𐑗 𐑴𐑐𐑩𐑯𐑛 𐑣𐑻 𐑣𐑨𐑯𐑛𐑟, 𐑨𐑟 𐑞𐑴 𐑑 𐑖𐑴 𐑞𐑺 𐑧𐑥𐑐𐑑𐑦𐑯𐑩𐑕. “𐑖𐑫𐑼? 𐑲'𐑥 𐑖𐑫𐑼 𐑝 \emph{𐑯𐑳𐑔𐑦𐑙}, ·𐑥𐑼~·𐑐𐑪𐑑𐑼. 𐑦𐑯 𐑷𐑤 𐑥𐑲 𐑤𐑲𐑓 𐑲'𐑝 𐑯𐑧𐑝𐑼 𐑥𐑧𐑑 𐑧𐑯𐑦𐑢𐑳𐑯 𐑧𐑤𐑕 𐑤𐑲𐑒 𐑿. 𐑕𐑳𐑥𐑑𐑲𐑥𐑟 𐑿 𐑡𐑳𐑕𐑑 𐑛𐑴𐑯𐑑 𐑕𐑰𐑥 𐑦𐑤𐑧𐑝𐑩𐑯 𐑘𐑽𐑟 𐑴𐑤𐑛 𐑹 𐑰𐑝𐑩𐑯 𐑷𐑤 𐑞𐑨𐑑 \emph{𐑣𐑿𐑥𐑩𐑯}.”

𐑣𐑨𐑮𐑦'𐑟 𐑲𐑚𐑮𐑬𐑟 𐑮𐑴𐑟 𐑑𐑩𐑢𐑹𐑛 𐑞 𐑕𐑒𐑲—

“𐑲'𐑥 𐑕𐑪𐑮𐑦!” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛 𐑒𐑢𐑦𐑒𐑤𐑦. “𐑲'𐑥 𐑝𐑧𐑮𐑦 𐑕𐑪𐑮𐑦, ·𐑥𐑼~·𐑐𐑪𐑑𐑼. 𐑲 𐑢𐑪𐑟 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑥𐑱𐑒 𐑩 𐑐𐑶𐑯𐑑 𐑯 𐑲'𐑥 𐑩𐑓𐑮𐑱𐑛 𐑞𐑨𐑑 𐑒𐑱𐑥 𐑬𐑑 𐑕𐑬𐑯𐑛𐑦𐑙 𐑛𐑦𐑓𐑼𐑩𐑯𐑑 𐑓𐑮𐑪𐑥 𐑢𐑪𐑑 𐑲 𐑣𐑨𐑛 𐑦𐑯 𐑥𐑲𐑯𐑛—”

“𐑪𐑯 𐑞 𐑒𐑪𐑯𐑑𐑮𐑺𐑦, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑯 𐑕𐑤𐑴𐑤𐑦 𐑕𐑥𐑲𐑤𐑛. “𐑲 𐑖𐑨𐑤 𐑑𐑱𐑒 𐑦𐑑 𐑨𐑟 𐑩 𐑝𐑧𐑮𐑦 𐑜𐑮𐑱𐑑 𐑒𐑪𐑥𐑐𐑤𐑦𐑥𐑧𐑯𐑑. 𐑚𐑳𐑑 𐑢𐑫𐑛 𐑿 𐑥𐑲𐑯𐑛 𐑦𐑓 𐑲 𐑪𐑓𐑼𐑛 𐑩𐑯 𐑷𐑤𐑑𐑻𐑯𐑩𐑑𐑦𐑝 𐑧𐑒𐑕𐑐𐑤𐑩𐑯𐑱𐑖𐑩𐑯?”

“𐑐𐑤𐑰𐑟 𐑛𐑵.”

“𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑸𐑯𐑑 𐑥𐑧𐑯𐑑 𐑑 𐑚𐑰 𐑑𐑵 𐑥𐑳𐑗 𐑕𐑥𐑸𐑑𐑼 𐑞𐑨𐑯 𐑞𐑺 𐑐𐑺𐑩𐑯𐑑𐑕,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. “𐑹 𐑑𐑵 𐑥𐑳𐑗 𐑕𐑱𐑯𐑼, 𐑥𐑱𐑚𐑰—𐑥𐑲 𐑓𐑭𐑞𐑼 𐑒𐑫𐑛 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑬𐑑𐑕𐑥𐑸𐑑 𐑥𐑰 𐑦𐑓 𐑣𐑰 𐑢𐑪𐑟, 𐑿 𐑯𐑴, 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 \emph{𐑑𐑮𐑲𐑦𐑙}, 𐑦𐑯𐑕𐑑𐑧𐑛 𐑝 𐑿𐑟𐑦𐑙 𐑣𐑦𐑟 𐑨𐑛𐑳𐑤𐑑 𐑦𐑯𐑑𐑧𐑤𐑦𐑡𐑩𐑯𐑕 𐑥𐑱𐑯𐑤𐑦 𐑑 𐑒𐑳𐑥 𐑳𐑐 𐑢𐑦𐑞 𐑯𐑿 𐑮𐑰𐑟𐑩𐑯𐑟 𐑯𐑪𐑑 𐑑 𐑗𐑱𐑯𐑡 𐑣𐑦𐑟 𐑥𐑲𐑯𐑛—” ·𐑣𐑨𐑮𐑦 𐑕𐑑𐑪𐑐𐑑. “𐑲'𐑥 𐑑𐑵 𐑕𐑥𐑸𐑑, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼. 𐑲'𐑝 𐑜𐑪𐑑 𐑯𐑳𐑔𐑦𐑙 𐑑 𐑕𐑱 𐑑 𐑯𐑹𐑥𐑩𐑤 𐑗𐑦𐑤𐑛𐑮𐑩𐑯. 𐑨𐑛𐑳𐑤𐑑𐑕 𐑛𐑴𐑯𐑑 𐑮𐑦𐑕𐑐𐑧𐑒𐑑 𐑥𐑰 𐑦𐑯𐑳𐑓 𐑑 𐑮𐑾𐑤𐑦 𐑑𐑷𐑒 𐑑 𐑥𐑰. 𐑯 𐑓𐑮𐑨𐑙𐑒𐑤𐑦, 𐑰𐑝𐑩𐑯 𐑦𐑓 𐑞𐑱 𐑛𐑦𐑛, 𐑞𐑱 𐑢𐑫𐑛𐑩𐑯𐑑 𐑕𐑬𐑯𐑛 𐑨𐑟 𐑕𐑥𐑸𐑑 𐑨𐑟 ·𐑮𐑦𐑗𐑼𐑛 ·𐑓𐑲𐑯𐑥𐑩𐑯, 𐑕𐑴 𐑲 𐑥𐑲𐑑 𐑨𐑟 𐑢𐑧𐑤 𐑮𐑰𐑛 𐑕𐑳𐑥𐑔𐑦𐑙 ·𐑮𐑦𐑗𐑼𐑛 ·𐑓𐑲𐑯𐑥𐑩𐑯 𐑮𐑴𐑑 𐑦𐑯𐑕𐑑𐑧𐑛. 𐑲'𐑥 \emph{𐑲𐑕𐑩𐑤𐑱𐑑𐑩𐑛}, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. 𐑲'𐑝 𐑚𐑰𐑯 𐑲𐑕𐑩𐑤𐑱𐑑𐑩𐑛 𐑥𐑲 𐑣𐑴𐑤 𐑤𐑲𐑓. 𐑥𐑱𐑚𐑰 𐑞𐑨𐑑 𐑣𐑨𐑟 𐑕𐑳𐑥 𐑝 𐑞 𐑕𐑱𐑥 𐑦𐑓𐑧𐑒𐑑𐑕 𐑨𐑟 𐑚𐑰𐑦𐑙 𐑤𐑪𐑒𐑑 𐑦𐑯 𐑩 𐑕𐑧𐑤𐑼. 𐑯 𐑲'𐑥 𐑑𐑵 𐑦𐑯𐑑𐑧𐑤𐑦𐑡𐑩𐑯𐑑 𐑑 𐑤𐑫𐑒 𐑳𐑐 𐑑 𐑥𐑲 𐑐𐑺𐑩𐑯𐑑𐑕 𐑞 𐑢𐑱 𐑞𐑨𐑑 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑸 𐑛𐑦𐑟𐑲𐑯𐑛 𐑑 𐑛𐑵. 𐑥𐑲 𐑐𐑺𐑩𐑯𐑑𐑕 𐑤𐑳𐑝 𐑥𐑰, 𐑚𐑳𐑑 𐑞𐑱 𐑛𐑴𐑯𐑑 𐑓𐑰𐑤 𐑩𐑚𐑤𐑲𐑡𐑛 𐑑 𐑮𐑦𐑕𐑐𐑪𐑯𐑛 𐑑 𐑮𐑰𐑟𐑩𐑯, 𐑯 𐑕𐑳𐑥𐑑𐑲𐑥𐑟 𐑲 𐑓𐑰𐑤 𐑤𐑲𐑒 𐑞𐑱'𐑼 𐑞 𐑗𐑦𐑤𐑛𐑮𐑩𐑯—𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑣𐑵 \emph{𐑢𐑴𐑯𐑑 𐑤𐑦𐑕𐑩𐑯} 𐑯 𐑣𐑨𐑝 𐑨𐑚𐑕𐑩𐑤𐑵𐑑 𐑷𐑔𐑪𐑮𐑦𐑑𐑦 𐑴𐑝𐑼 𐑥𐑲 𐑣𐑴𐑤 𐑦𐑜𐑟𐑦𐑕𐑑𐑩𐑯𐑕. 𐑲 𐑑𐑮𐑲 𐑯𐑪𐑑 𐑑 𐑚𐑰 𐑑𐑵 𐑚𐑦𐑑𐑼 𐑩𐑚𐑬𐑑 𐑦𐑑, 𐑚𐑳𐑑 𐑲 𐑷𐑤𐑕𐑴 𐑑𐑮𐑲 𐑑 𐑚𐑰 \emph{𐑪𐑯𐑩𐑕𐑑} 𐑢𐑦𐑞 𐑥𐑲𐑕𐑧𐑤𐑓, 𐑕𐑴, 𐑘𐑧𐑕, 𐑲'𐑥 𐑚𐑦𐑑𐑼. 𐑯 𐑲 𐑷𐑤𐑕𐑴 𐑣𐑨𐑝 𐑩𐑯 𐑨𐑙𐑜𐑼 𐑥𐑨𐑯𐑦𐑡𐑥𐑩𐑯𐑑 𐑐𐑮𐑪𐑚𐑤𐑩𐑥, 𐑚𐑳𐑑 𐑲'𐑥 𐑢𐑻𐑒𐑦𐑙 𐑪𐑯 𐑦𐑑. 𐑞𐑨𐑑'𐑕 𐑷𐑤.”

“\emph{𐑞𐑨𐑑'𐑕 𐑷𐑤?}”

·𐑣𐑨𐑮𐑦 𐑯𐑪𐑛𐑩𐑛 𐑓𐑻𐑥𐑤𐑦. “𐑞𐑨𐑑'𐑕 𐑷𐑤. 𐑖𐑫𐑼𐑤𐑦, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑰𐑝𐑩𐑯 𐑦𐑯 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 ·𐑚𐑮𐑦𐑑𐑩𐑯, 𐑞 𐑯𐑹𐑥𐑩𐑤 𐑧𐑒𐑕𐑐𐑤𐑩𐑯𐑱𐑖𐑩𐑯 𐑦𐑟 𐑷𐑤𐑢𐑱𐑟 𐑢𐑻𐑔 \emph{𐑒𐑩𐑯𐑕𐑦𐑛𐑼𐑦𐑙}?”

\later

𐑦𐑑 𐑢𐑪𐑟 𐑤𐑱𐑑𐑼 𐑦𐑯 𐑞 𐑛𐑱, 𐑞 𐑕𐑳𐑯 𐑤𐑴𐑼𐑦𐑙 𐑦𐑯 𐑞 𐑕𐑳𐑥𐑼 𐑕𐑒𐑲 𐑯 𐑖𐑪𐑐𐑼𐑟 𐑚𐑦𐑜𐑦𐑯𐑦𐑙 𐑑 𐑐𐑰𐑑𐑼 𐑬𐑑 𐑓𐑮𐑪𐑥 𐑞 𐑕𐑑𐑮𐑰𐑑𐑕. 𐑕𐑳𐑥 𐑖𐑪𐑐𐑕 𐑣𐑨𐑛 𐑷𐑤𐑮𐑧𐑛𐑦 𐑒𐑤𐑴𐑟𐑛; ·𐑣𐑨𐑮𐑦 𐑯 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑣𐑨𐑛 𐑚𐑷𐑑 𐑣𐑦𐑟 𐑑𐑧𐑒𐑕𐑑𐑚𐑫𐑒𐑕 𐑓𐑮𐑪𐑥 ·𐑓𐑤𐑳𐑮𐑦𐑖 𐑯 ·𐑚𐑤𐑪𐑑𐑕 𐑡𐑳𐑕𐑑 𐑳𐑯𐑛𐑼 𐑞 𐑛𐑧𐑛𐑤𐑲𐑯. 𐑢𐑦𐑞 𐑴𐑯𐑤𐑦 𐑩 𐑕𐑤𐑲𐑑 𐑦𐑒𐑕𐑐𐑤𐑴𐑠𐑩𐑯 𐑢𐑧𐑯 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑥𐑱𐑛 𐑩 𐑚𐑰𐑤𐑲𐑯 𐑓 𐑞 𐑒𐑰𐑢𐑻𐑛 “·𐑸𐑦𐑔𐑥𐑩𐑯𐑕𐑦” 𐑯 𐑛𐑦𐑕𐑒𐑳𐑝𐑼𐑛 𐑞𐑨𐑑 𐑞 𐑕𐑧𐑝𐑩𐑯𐑔-𐑘𐑽 𐑑𐑧𐑒𐑕𐑑𐑚𐑫𐑒𐑕 𐑦𐑯𐑝𐑴𐑒𐑑 𐑯𐑳𐑔𐑦𐑙 𐑥𐑹 𐑥𐑨𐑔𐑩𐑥𐑨𐑑𐑦𐑒𐑤𐑦 𐑩𐑛𐑝𐑭𐑯𐑕𐑑 𐑞𐑨𐑯 𐑑𐑮𐑦𐑜𐑩𐑯𐑪𐑥𐑩𐑑𐑮𐑦.

𐑨𐑑 𐑞𐑦𐑕 𐑥𐑴𐑥𐑩𐑯𐑑, 𐑞𐑴, 𐑛𐑮𐑰𐑥𐑟 𐑝 𐑤𐑴-𐑣𐑨𐑙𐑦𐑙 𐑮𐑰𐑕𐑻𐑗 𐑓𐑮𐑵𐑑 𐑢𐑻 𐑓𐑸 𐑓𐑮𐑪𐑥 ·𐑣𐑨𐑮𐑦'𐑟 𐑥𐑲𐑯𐑛.

𐑨𐑑 𐑞𐑦𐑕 𐑥𐑴𐑥𐑩𐑯𐑑, 𐑞 𐑑𐑵 𐑝 𐑞𐑧𐑥 𐑢𐑻 𐑢𐑷𐑒𐑦𐑙 𐑬𐑑 𐑝 ·𐑪𐑤𐑦𐑝𐑨𐑯𐑛𐑼'𐑟, 𐑯 ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑕𐑑𐑺𐑦𐑙 𐑨𐑑 𐑣𐑦𐑟 𐑢𐑪𐑯𐑛. 𐑣𐑰'𐑛 𐑢𐑱𐑝𐑛 𐑦𐑑, 𐑯 𐑐𐑮𐑩𐑛𐑿𐑕𐑑 𐑥𐑳𐑤𐑑𐑦𐑒𐑳𐑤𐑼𐑛 𐑕𐑐𐑸𐑒𐑕, 𐑢𐑦𐑗 𐑮𐑾𐑤𐑦 𐑖𐑫𐑛𐑩𐑯𐑑 𐑣𐑨𐑝 𐑒𐑳𐑥 𐑨𐑟 𐑕𐑳𐑗 𐑩𐑯 𐑧𐑒𐑕𐑑𐑮𐑩 𐑖𐑪𐑒 𐑭𐑓𐑑𐑼 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑧𐑤𐑕 𐑣𐑰'𐑛 𐑕𐑰𐑯, 𐑚𐑳𐑑 𐑕𐑳𐑥𐑣𐑬—

\emph{𐑲 𐑒𐑨𐑯 𐑛𐑵 𐑥𐑨𐑡𐑦𐑒.}

\emph{𐑥𐑰. 𐑨𐑟 𐑦𐑯, 𐑥𐑰 𐑐𐑻𐑕𐑩𐑯𐑩𐑤𐑦. 𐑲 𐑨𐑥 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤; 𐑲 𐑨𐑥 𐑩 𐑢𐑦𐑟𐑼𐑛.}

𐑣𐑰 𐑣𐑨𐑛 \emph{𐑓𐑧𐑤𐑑} 𐑞 𐑥𐑨𐑡𐑦𐑒 𐑐𐑹𐑦𐑙 𐑳𐑐 𐑣𐑦𐑟 𐑸𐑥, 𐑯 𐑦𐑯 𐑞𐑨𐑑 𐑦𐑯𐑕𐑑𐑩𐑯𐑑, 𐑮𐑾𐑤𐑲𐑟𐑛 𐑞𐑨𐑑 𐑣𐑰 𐑣𐑨𐑛 𐑷𐑤𐑢𐑱𐑟 𐑣𐑨𐑛 𐑞𐑨𐑑 𐑕𐑧𐑯𐑕, 𐑞𐑨𐑑 𐑣𐑰 𐑣𐑨𐑛 𐑐𐑩𐑟𐑧𐑕𐑑 𐑦𐑑 𐑣𐑦𐑟 𐑣𐑴𐑤 𐑤𐑲𐑓, 𐑞 𐑕𐑧𐑯𐑕 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑯𐑪𐑑 𐑕𐑲𐑑 𐑹 𐑕𐑬𐑯𐑛 𐑹 𐑕𐑥𐑧𐑤 𐑹 𐑑𐑱𐑕𐑑 𐑹 𐑑𐑳𐑗 𐑚𐑳𐑑 𐑴𐑯𐑤𐑦 𐑥𐑨𐑡𐑦𐑒. 𐑤𐑲𐑒 𐑣𐑨𐑝𐑦𐑙 𐑲𐑟 𐑚𐑳𐑑 𐑒𐑰𐑐𐑦𐑙 𐑞𐑧𐑥 𐑷𐑤𐑢𐑱𐑟 𐑒𐑤𐑴𐑟𐑛, 𐑕𐑴 𐑞𐑨𐑑 𐑿 𐑛𐑦𐑛𐑩𐑯𐑑 𐑰𐑝𐑩𐑯 𐑮𐑾𐑤𐑲𐑟 𐑞𐑨𐑑 𐑿 𐑢𐑻 𐑕𐑰𐑦𐑙 𐑛𐑸𐑒𐑯𐑩𐑕; 𐑯 𐑞𐑧𐑯 𐑢𐑳𐑯 𐑛𐑱 𐑞 𐑲 𐑴𐑐𐑩𐑯𐑛, 𐑯 𐑕𐑷 𐑞 𐑢𐑻𐑤𐑛. 𐑞 𐑖𐑪𐑒 𐑝 𐑦𐑑 𐑣𐑨𐑛 𐑐𐑹𐑛 𐑔𐑮𐑵 𐑣𐑦𐑥, 𐑑𐑳𐑗𐑦𐑙 𐑐𐑰𐑕𐑩𐑟 𐑝 𐑣𐑦𐑥𐑕𐑧𐑤𐑓, 𐑩𐑢𐑱𐑒𐑩𐑯𐑦𐑙 𐑞𐑧𐑥, 𐑯 𐑞𐑧𐑯 𐑛𐑲𐑛 𐑩𐑢𐑱 𐑦𐑯 𐑕𐑱𐑒𐑪𐑯𐑛𐑟; 𐑤𐑰𐑝𐑦𐑙 𐑴𐑯𐑤𐑦 𐑞 𐑕𐑻𐑑𐑩𐑯 𐑯𐑪𐑤𐑦𐑡 𐑞𐑨𐑑 𐑣𐑰 𐑢𐑪𐑟 𐑯𐑬 𐑩 𐑢𐑦𐑟𐑼𐑛, 𐑯 𐑷𐑤𐑢𐑱𐑟 𐑣𐑨𐑛 𐑚𐑰𐑯, 𐑯 𐑣𐑨𐑛 𐑰𐑝𐑩𐑯, 𐑦𐑯 𐑕𐑳𐑥 𐑕𐑑𐑮𐑱𐑯𐑡 𐑢𐑱, 𐑷𐑤𐑢𐑱𐑟 𐑯𐑴𐑯 𐑦𐑑.

𐑯—

“\emph{𐑦𐑑 𐑦𐑟 𐑝𐑧𐑮𐑦 𐑒𐑘𐑫𐑼𐑾𐑕 𐑦𐑯𐑛𐑰𐑛 𐑞𐑨𐑑 𐑿 𐑖𐑫𐑛 𐑚𐑰 𐑛𐑧𐑕𐑑𐑦𐑯𐑛 𐑓 𐑞𐑦𐑕 𐑢𐑪𐑯𐑛 𐑢𐑧𐑯 𐑦𐑑𐑕 𐑚𐑮𐑳𐑞𐑼 𐑢𐑲, 𐑦𐑑𐑕 𐑚𐑮𐑳𐑞𐑼 𐑜𐑱𐑝 𐑿 𐑞𐑨𐑑 𐑕𐑒𐑸.}”

𐑞𐑨𐑑 𐑒𐑫𐑛 𐑯𐑪𐑑 \emph{𐑐𐑪𐑕𐑩𐑚𐑤𐑦} 𐑚𐑰 𐑒𐑴𐑦𐑯𐑕𐑦𐑛𐑩𐑯𐑕. 𐑞𐑺 𐑣𐑨𐑛 𐑚𐑰𐑯 \emph{𐑔𐑬𐑟𐑩𐑯𐑛𐑟} 𐑝 𐑢𐑪𐑯𐑛𐑟 𐑦𐑯 𐑞𐑨𐑑 𐑖𐑪𐑐. 𐑢𐑧𐑤, 𐑴𐑒𐑱, 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑦𐑑 \emph{𐑒𐑫𐑛} 𐑚𐑰 𐑒𐑴𐑦𐑯𐑕𐑦𐑛𐑩𐑯𐑕, 𐑞𐑺 𐑢𐑻 𐑕𐑦𐑒𐑕 𐑚𐑦𐑤𐑘𐑩𐑯 𐑐𐑰𐑐𐑩𐑤 𐑦𐑯 𐑞 𐑢𐑻𐑤𐑛 𐑯 𐑔𐑬𐑟𐑩𐑯𐑛-𐑑-𐑢𐑳𐑯 𐑒𐑴𐑦𐑯𐑕𐑦𐑛𐑩𐑯𐑕𐑩𐑟 𐑣𐑨𐑐𐑩𐑯𐑛 𐑧𐑝𐑮𐑦 𐑛𐑱. 𐑚𐑳𐑑 ·𐑚𐑱𐑟'𐑩𐑟 ·𐑔𐑽𐑩𐑥 𐑕𐑧𐑛 𐑞𐑨𐑑 𐑧𐑯𐑦 𐑮𐑰𐑟𐑩𐑯𐑩𐑚𐑩𐑤 𐑣𐑲𐑐𐑪𐑔𐑦𐑕𐑦𐑕 𐑢𐑦𐑗 𐑥𐑱𐑛 𐑦𐑑 \emph{𐑥𐑹} 𐑤𐑲𐑒𐑤𐑦 𐑞𐑨𐑯 𐑩 𐑔𐑬𐑟𐑩𐑯𐑛-𐑑-𐑢𐑳𐑯 𐑞𐑨𐑑 𐑣𐑰'𐑛 𐑧𐑯𐑛 𐑳𐑐 𐑢𐑦𐑞 𐑞 𐑚𐑮𐑳𐑞𐑼 𐑑 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛'𐑟 𐑢𐑪𐑯𐑛, 𐑢𐑪𐑟 𐑜𐑴𐑦𐑙 𐑑 𐑣𐑨𐑝 𐑩𐑯 𐑩𐑛𐑝𐑭𐑯𐑑𐑦𐑡.

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑣𐑨𐑛 𐑕𐑦𐑥𐑐𐑤𐑦 𐑕𐑧𐑛 \emph{𐑣𐑬 𐑐𐑦𐑒𐑿𐑤𐑽} 𐑯 𐑤𐑧𐑓𐑑 𐑦𐑑 𐑨𐑑 𐑞𐑨𐑑, 𐑢𐑦𐑗 𐑣𐑨𐑛 𐑐𐑫𐑑 ·𐑣𐑨𐑮𐑦 𐑦𐑯𐑑𐑵 𐑩 𐑕𐑑𐑱𐑑 𐑝 𐑖𐑪𐑒 𐑨𐑑 𐑞 𐑖𐑽, 𐑴𐑝𐑼𐑢𐑧𐑤𐑥𐑦𐑙 \emph{𐑦𐑯𐑒𐑘𐑫𐑼𐑦𐑪𐑕𐑦𐑑𐑦} 𐑝 𐑢𐑦𐑟𐑼𐑛𐑟 𐑯 𐑢𐑦𐑗𐑩𐑟. 𐑦𐑯 𐑯𐑴 \emph{𐑦𐑥𐑨𐑡𐑦𐑯𐑩𐑚𐑩𐑤} 𐑢𐑻𐑤𐑛 𐑢𐑫𐑛 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑝 𐑡𐑳𐑕𐑑 𐑜𐑪𐑯 “·𐑣𐑥” 𐑯 𐑢𐑷𐑒𐑑 𐑬𐑑 𐑝 𐑞 𐑖𐑪𐑐 𐑢𐑦𐑞𐑬𐑑 𐑰𐑝𐑩𐑯 \emph{𐑑𐑮𐑲𐑦𐑙} 𐑑 𐑒𐑳𐑥 𐑳𐑐 𐑢𐑦𐑞 𐑩 𐑣𐑲𐑐𐑪𐑔𐑦𐑕𐑦𐑕 𐑓 𐑢𐑪𐑑 𐑢𐑪𐑟 𐑜𐑴𐑦𐑙 𐑪𐑯.

𐑣𐑦𐑟 𐑤𐑧𐑓𐑑 𐑣𐑨𐑯𐑛 𐑮𐑴𐑟 𐑯 𐑑𐑳𐑗𐑑 𐑣𐑦𐑟 𐑕𐑒𐑸.

𐑢𐑪𐑑…\emph{𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦…}

“𐑿'𐑼 𐑩 𐑓𐑫𐑤 𐑢𐑦𐑟𐑼𐑛 𐑯𐑬,” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. “𐑒𐑩𐑯𐑜𐑮𐑨𐑗𐑩𐑤𐑱𐑖𐑩𐑯𐑟.”

·𐑣𐑨𐑮𐑦 𐑯𐑪𐑛𐑩𐑛.

“𐑯 𐑢𐑪𐑑 𐑛𐑵 𐑿 𐑔𐑦𐑙𐑒 𐑝 𐑞 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑢𐑻𐑤𐑛?” 𐑕𐑧𐑛 𐑖𐑰.

“𐑦𐑑'𐑕 𐑕𐑑𐑮𐑱𐑯𐑡,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. “𐑲 𐑷𐑑 𐑑 𐑚𐑰 𐑔𐑦𐑙𐑒𐑦𐑙 𐑩𐑚𐑬𐑑 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑲'𐑝 𐑕𐑰𐑯 𐑝 𐑥𐑨𐑡𐑦𐑒…𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑞𐑨𐑑 𐑲 𐑯𐑬 𐑯𐑴 𐑦𐑟 𐑐𐑪𐑕𐑩𐑚𐑩𐑤, 𐑯 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑲 𐑯𐑬 𐑯𐑴 𐑑 𐑚𐑰 𐑩 𐑤𐑲, 𐑯 𐑷𐑤 𐑞 𐑢𐑻𐑒 𐑤𐑧𐑓𐑑 𐑚𐑦𐑓𐑹 𐑥𐑰 𐑑 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑦𐑑. 𐑯 𐑘𐑧𐑑 𐑲 𐑓𐑲𐑯𐑛 𐑥𐑲𐑕𐑧𐑤𐑓 𐑛𐑦𐑕𐑑𐑮𐑨𐑒𐑑𐑩𐑛 𐑚𐑲 𐑮𐑧𐑤𐑩𐑑𐑦𐑝 𐑑𐑮𐑦𐑝𐑦𐑨𐑤𐑦𐑑𐑦𐑟 𐑤𐑲𐑒,” ·𐑣𐑨𐑮𐑦 𐑤𐑴𐑼𐑛 𐑣𐑦𐑟 𐑝𐑶𐑕, “𐑞 𐑣𐑴𐑤 ·𐑚𐑶-𐑣𐑵-·𐑤𐑦𐑝𐑛 𐑔𐑦𐑙.” 𐑞𐑺 𐑛𐑦𐑛𐑩𐑯𐑑 𐑕𐑰𐑥 𐑑 𐑚𐑰 𐑧𐑯𐑦𐑢𐑳𐑯 𐑯𐑽𐑚𐑲, 𐑚𐑳𐑑 𐑯𐑴 𐑐𐑶𐑯𐑑 𐑑𐑧𐑥𐑐𐑑𐑦𐑙 𐑓𐑱𐑑.

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 \emph{𐑩𐑣𐑧𐑥𐑛}. “𐑮𐑾𐑤𐑦? 𐑿 𐑛𐑴𐑯𐑑 𐑕𐑱.”

·𐑣𐑨𐑮𐑦 𐑯𐑪𐑛𐑩𐑛. “𐑘𐑧𐑕. 𐑦𐑑'𐑕 𐑡𐑳𐑕𐑑…\emph{𐑪𐑛}. 𐑑 𐑓𐑲𐑯𐑛 𐑬𐑑 𐑞𐑨𐑑 𐑿 𐑢𐑻 𐑐𐑸𐑑 𐑝 𐑞𐑦𐑕 𐑜𐑮𐑨𐑯𐑛 𐑕𐑑𐑹𐑦, 𐑞 𐑒𐑢𐑧𐑕𐑑 𐑑 𐑛𐑦𐑓𐑰𐑑 𐑞 𐑜𐑮𐑱𐑑 𐑯 𐑑𐑧𐑮𐑦𐑚𐑩𐑤 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛, 𐑯 𐑦𐑑'𐑕 𐑷𐑤𐑮𐑧𐑛𐑦 \emph{𐑛𐑳𐑯}. 𐑓𐑦𐑯𐑦𐑖𐑑. 𐑒𐑩𐑥𐑐𐑤𐑰𐑑𐑤𐑦 𐑴𐑝𐑼 𐑢𐑦𐑞. 𐑤𐑲𐑒 𐑿'𐑼 ·𐑓𐑮𐑴𐑛𐑴 ·𐑚𐑨𐑜𐑦𐑯𐑟 𐑯 𐑿 𐑓𐑲𐑯𐑛 𐑬𐑑 𐑞𐑨𐑑 𐑘𐑹 𐑐𐑺𐑩𐑯𐑑𐑕 𐑑𐑫𐑒 𐑿 𐑑 ·𐑥𐑬𐑯𐑑 ·𐑛𐑵𐑥 𐑯 𐑣𐑨𐑛 𐑿 𐑑𐑪𐑕 𐑦𐑯 𐑞 ·𐑮𐑦𐑙 𐑢𐑧𐑯 𐑿 𐑢𐑻 𐑢𐑳𐑯 𐑘𐑽 𐑴𐑤𐑛 𐑯 𐑿 𐑛𐑴𐑯𐑑 𐑰𐑝𐑩𐑯 𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑦𐑑.”

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑕𐑥𐑲𐑤 𐑣𐑨𐑛 𐑜𐑮𐑴𐑯 𐑕𐑳𐑥𐑢𐑪𐑑 𐑓𐑦𐑒𐑕𐑑.

“𐑿 𐑯𐑴, 𐑦𐑓 𐑲 𐑢𐑻 𐑧𐑯𐑦𐑢𐑳𐑯 𐑧𐑤𐑕, 𐑧𐑯𐑦𐑢𐑳𐑯 𐑧𐑤𐑕 𐑨𐑑 𐑷𐑤, 𐑲'𐑛 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑚𐑰 𐑐𐑮𐑦𐑑𐑦 𐑢𐑳𐑮𐑦𐑛 𐑩𐑚𐑬𐑑 𐑤𐑦𐑝𐑦𐑙 𐑳𐑐 𐑑 𐑞𐑨𐑑 𐑕𐑑𐑸𐑑. \emph{𐑜𐑪𐑖, ·𐑣𐑨𐑮𐑦, 𐑢𐑪𐑑 𐑣𐑨𐑝 𐑿 𐑛𐑳𐑯 𐑕𐑦𐑯𐑕 𐑿 𐑛𐑦𐑓𐑰𐑑𐑩𐑛 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛? 𐑘𐑹 𐑴𐑯 𐑚𐑫𐑒𐑖𐑪𐑐? 𐑞𐑨𐑑'𐑕 𐑜𐑮𐑱𐑑! 𐑕𐑱, 𐑛𐑦𐑛 𐑿 𐑯𐑴 𐑲 𐑯𐑱𐑥𐑛 𐑥𐑲 𐑗𐑲𐑤𐑛 𐑭𐑓𐑑𐑼 𐑿?} 𐑚𐑳𐑑 𐑲 𐑣𐑨𐑝 𐑣𐑴𐑐𐑕 𐑞𐑨𐑑 𐑞𐑦𐑕 𐑢𐑦𐑤 𐑯𐑪𐑑 𐑐𐑮𐑵𐑝 𐑑 𐑚𐑰 𐑩 𐑐𐑮𐑪𐑚𐑤𐑩𐑥.” ·𐑣𐑨𐑮𐑦 𐑕𐑲𐑛. “𐑕𐑑𐑦𐑤…𐑦𐑑'𐑕 𐑷𐑤𐑥𐑴𐑕𐑑 𐑦𐑯𐑳𐑓 𐑑 𐑥𐑱𐑒 𐑥𐑰 𐑢𐑦𐑖 𐑞𐑨𐑑 𐑞𐑺 𐑢𐑻 \emph{𐑕𐑳𐑥} 𐑤𐑵𐑕 𐑧𐑯𐑛𐑟 𐑓𐑮𐑪𐑥 𐑞 𐑒𐑢𐑧𐑕𐑑, 𐑡𐑳𐑕𐑑 𐑕𐑴 𐑲 𐑒𐑫𐑛 𐑕𐑱 𐑞𐑨𐑑 𐑲 𐑮𐑾𐑤𐑦, 𐑿 𐑯𐑴, \emph{𐑐𐑸𐑑𐑦𐑕𐑦𐑐𐑱𐑑𐑩𐑛} 𐑕𐑳𐑥𐑣𐑬.”

“𐑴?” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑦𐑯 𐑩𐑯 𐑪𐑛 𐑑𐑴𐑯. “𐑢𐑪𐑑 𐑛𐑦𐑛 𐑿 𐑣𐑨𐑝 𐑦𐑯 𐑥𐑲𐑯𐑛?”

“𐑢𐑧𐑤, 𐑓 𐑦𐑜𐑟𐑭𐑥𐑐𐑩𐑤, 𐑿 𐑥𐑧𐑯𐑖𐑩𐑯𐑛 𐑞𐑨𐑑 𐑥𐑲 𐑐𐑺𐑩𐑯𐑑𐑕 𐑢𐑻 𐑚𐑦𐑑𐑮𐑱𐑛. 𐑣𐑵 𐑚𐑦𐑑𐑮𐑱𐑛 𐑞𐑧𐑥?”

“·𐑕𐑦𐑮𐑾𐑕 ·𐑚𐑤𐑨𐑒,” 𐑞 𐑢𐑦𐑗 𐑕𐑧𐑛, 𐑷𐑤𐑥𐑴𐑕𐑑 𐑣𐑦𐑕𐑦𐑙 𐑞 𐑯𐑱𐑥. “𐑣𐑰'𐑟 𐑦𐑯 ·𐑨𐑟𐑒𐑩𐑚𐑨𐑯. 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑐𐑮𐑦𐑟𐑩𐑯.”

“𐑣𐑬 𐑐𐑮𐑪𐑚𐑩𐑚𐑩𐑤 𐑦𐑟 𐑦𐑑 𐑞𐑨𐑑 ·𐑕𐑦𐑮𐑾𐑕 ·𐑚𐑤𐑨𐑒 𐑢𐑦𐑤 𐑚𐑮𐑱𐑒 𐑬𐑑 𐑝 𐑐𐑮𐑦𐑟𐑩𐑯 𐑯 𐑲'𐑤 𐑣𐑨𐑓 𐑑 𐑑𐑮𐑨𐑒 𐑣𐑦𐑥 𐑛𐑬𐑯 𐑯 𐑛𐑦𐑓𐑰𐑑 𐑣𐑦𐑥 𐑦𐑯 𐑕𐑳𐑥 𐑕𐑹𐑑 𐑝 𐑕𐑐𐑧𐑒𐑑𐑨𐑒𐑿𐑤𐑼 𐑛𐑿𐑩𐑤, 𐑹 𐑚𐑧𐑑𐑼 𐑘𐑧𐑑 𐑐𐑫𐑑 𐑩 𐑤𐑸𐑡 𐑚𐑬𐑯𐑑𐑦 𐑪𐑯 𐑣𐑦𐑟 𐑣𐑧𐑛 𐑯 𐑣𐑲𐑛 𐑬𐑑 𐑦𐑯 ·𐑪𐑕𐑑𐑮𐑱𐑤𐑾 𐑢𐑲𐑤 𐑲 𐑢𐑱𐑑 𐑓 𐑞 𐑮𐑦𐑟𐑳𐑤𐑑𐑕?”

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑚𐑤𐑦𐑙𐑒𐑑. 𐑑𐑢𐑲𐑕. “𐑯𐑪𐑑 𐑤𐑲𐑒𐑤𐑦. 𐑯𐑴-𐑢𐑳𐑯 𐑣𐑨𐑟 𐑧𐑝𐑼 𐑦𐑕𐑒𐑱𐑐𐑑 𐑓𐑮𐑪𐑥 ·𐑨𐑟𐑒𐑩𐑚𐑨𐑯, 𐑯 𐑲 𐑛𐑬𐑑 𐑞𐑨𐑑 \emph{𐑣𐑰} 𐑢𐑦𐑤 𐑚𐑰 𐑞 𐑓𐑻𐑕𐑑.”

·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑩 𐑚𐑦𐑑 𐑕𐑒𐑧𐑐𐑑𐑦𐑒𐑩𐑤 𐑝 𐑞𐑨𐑑 “\emph{𐑯𐑴-𐑢𐑳𐑯} 𐑣𐑨𐑟 \emph{𐑧𐑝𐑼} 𐑦𐑕𐑒𐑱𐑐𐑑 𐑓𐑮𐑪𐑥 ·𐑨𐑟𐑒𐑩𐑚𐑨𐑯” 𐑤𐑲𐑯. 𐑕𐑑𐑦𐑤, 𐑥𐑱𐑚𐑰 𐑢𐑦𐑞 𐑥𐑨𐑡𐑦𐑒 𐑿 𐑒𐑫𐑛 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑜𐑧𐑑 𐑒𐑤𐑴𐑕 𐑑 𐑩 100\% 𐑐𐑻𐑓𐑦𐑒𐑑 𐑐𐑮𐑦𐑟𐑩𐑯, 𐑦𐑕𐑐𐑧𐑖𐑩𐑤𐑦 𐑦𐑓 𐑿 𐑣𐑨𐑛 𐑩 𐑢𐑪𐑯𐑛 𐑯 𐑞𐑱 𐑛𐑦𐑛 𐑯𐑪𐑑. 𐑞 𐑚𐑧𐑕𐑑 𐑢𐑱 𐑑 𐑜𐑧𐑑 𐑬𐑑 𐑢𐑫𐑛 𐑚𐑰 𐑑 𐑯𐑪𐑑 𐑜𐑴 𐑞𐑺 𐑦𐑯 𐑞 𐑓𐑻𐑕𐑑 𐑐𐑤𐑱𐑕.

“𐑷𐑤 𐑮𐑲𐑑 𐑞𐑧𐑯,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. “𐑕𐑬𐑯𐑛𐑟 𐑤𐑲𐑒 𐑦𐑑'𐑕 𐑚𐑰𐑯 𐑯𐑲𐑕𐑤𐑦 𐑮𐑨𐑐𐑑 𐑳𐑐.” 𐑣𐑰 𐑕𐑲𐑛, 𐑕𐑒𐑮𐑳𐑚𐑦𐑙 𐑣𐑦𐑟 𐑐𐑭𐑥 𐑴𐑝𐑼 𐑣𐑦𐑟 𐑣𐑧𐑛. “𐑹 𐑥𐑱𐑚𐑰 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛 𐑛𐑦𐑛𐑩𐑯𐑑 \emph{𐑮𐑾𐑤𐑦} 𐑛𐑲 𐑞𐑨𐑑 𐑯𐑲𐑑. 𐑯𐑪𐑑 𐑒𐑩𐑥𐑐𐑤𐑰𐑑𐑤𐑦. 𐑣𐑦𐑟 𐑕𐑐𐑦𐑮𐑦𐑑 𐑤𐑦𐑙𐑜𐑼𐑟, 𐑢𐑦𐑕𐑐𐑼𐑦𐑙 𐑑 𐑐𐑰𐑐𐑩𐑤 𐑦𐑯 𐑯𐑲𐑑𐑥𐑺𐑟 𐑞𐑨𐑑 𐑚𐑤𐑰𐑛 𐑴𐑝𐑼 𐑦𐑯𐑑𐑵 𐑞 𐑢𐑱𐑒𐑦𐑙 𐑢𐑻𐑤𐑛, 𐑕𐑻𐑗𐑦𐑙 𐑓 𐑩 𐑢𐑱 𐑚𐑨𐑒 𐑦𐑯𐑑𐑵 𐑞 𐑤𐑦𐑝𐑦𐑙 𐑤𐑨𐑯𐑛𐑟 𐑣𐑰 𐑕𐑢𐑹 𐑑 𐑛𐑦𐑕𐑑𐑮𐑶, 𐑯 𐑯𐑬, 𐑦𐑯 𐑩𐑒𐑹𐑛𐑩𐑯𐑕 𐑢𐑦𐑞 𐑞 𐑱𐑯𐑖𐑩𐑯𐑑 𐑐𐑮𐑪𐑓𐑩𐑕𐑦, 𐑣𐑰 𐑯 𐑲 𐑸 𐑤𐑪𐑒𐑑 𐑦𐑯 𐑩 𐑛𐑧𐑛𐑤𐑦 𐑛𐑿𐑩𐑤 𐑢𐑺 𐑞 𐑢𐑦𐑯𐑼 𐑖𐑨𐑤 𐑤𐑵𐑟 𐑯 𐑞 𐑤𐑵𐑟𐑼 𐑖𐑨𐑤 𐑢𐑦𐑯—”

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑣𐑧𐑛 𐑕𐑢𐑦𐑝𐑩𐑤𐑛, 𐑯 𐑣𐑻 𐑲𐑟 𐑛𐑸𐑑𐑩𐑛 𐑼𐑬𐑯𐑛, 𐑨𐑟 𐑞𐑴 𐑑 𐑕𐑻𐑗 𐑞 𐑕𐑑𐑮𐑰𐑑 𐑓 𐑤𐑦𐑕𐑩𐑯𐑼𐑟.

“𐑲'𐑥 \emph{𐑡𐑴𐑒𐑦𐑙}, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑢𐑦𐑞 𐑕𐑳𐑥 𐑩𐑯𐑶𐑩𐑯𐑕. ·𐑖𐑰𐑖, 𐑢𐑲 𐑛𐑦𐑛 𐑖𐑰 𐑷𐑤𐑢𐑱𐑟 𐑑𐑱𐑒 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑕𐑴 𐑕𐑽𐑾𐑕𐑤𐑦—

𐑩 𐑕𐑤𐑴 𐑕𐑦𐑙𐑒𐑦𐑙 𐑕𐑧𐑯𐑕𐑱𐑖𐑩𐑯 𐑚𐑦𐑜𐑨𐑯 𐑑 𐑛𐑷𐑯 𐑦𐑯 𐑞 𐑐𐑦𐑑 𐑝 ·𐑣𐑨𐑮𐑦'𐑟 𐑕𐑑𐑳𐑥𐑩𐑒.

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑤𐑫𐑒𐑑 𐑨𐑑 ·𐑣𐑨𐑮𐑦 𐑢𐑦𐑞 𐑩 𐑒𐑭𐑥 𐑦𐑒𐑕𐑐𐑮𐑧𐑖𐑩𐑯. 𐑩 𐑝𐑧𐑮𐑦, \emph{𐑝𐑧𐑮𐑦} 𐑒𐑭𐑥 𐑦𐑒𐑕𐑐𐑮𐑧𐑖𐑩𐑯. 𐑞𐑧𐑯 𐑩 𐑕𐑥𐑲𐑤 𐑢𐑪𐑟 𐑐𐑫𐑑 𐑪𐑯. “𐑝 𐑒𐑹𐑕 𐑿 𐑸, ·𐑥𐑼~·𐑐𐑪𐑑𐑼.”

\emph{𐑷 𐑒𐑮𐑨𐑐.}

𐑦𐑓 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑯𐑰𐑛𐑩𐑛 𐑑 𐑓𐑹𐑥𐑩𐑤𐑲𐑟 𐑞 𐑢𐑻𐑛𐑤𐑩𐑕 𐑦𐑯𐑓𐑼𐑩𐑯𐑕 𐑞𐑨𐑑 𐑣𐑨𐑛 𐑡𐑳𐑕𐑑 𐑓𐑤𐑨𐑖𐑑 𐑦𐑯𐑑𐑵 𐑣𐑦𐑟 𐑥𐑲𐑯𐑛, 𐑦𐑑 𐑢𐑫𐑛 𐑣𐑨𐑝 𐑒𐑳𐑥 𐑬𐑑 𐑕𐑳𐑥𐑔𐑦𐑙 𐑤𐑲𐑒, '𐑦𐑓 𐑲 𐑧𐑕𐑑𐑦𐑥𐑱𐑑 𐑞 𐑐𐑮𐑪𐑚𐑩𐑚𐑦𐑤𐑦𐑑𐑦 𐑝 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑛𐑵𐑦𐑙 𐑢𐑪𐑑 𐑲 𐑡𐑳𐑕𐑑 𐑕𐑷 𐑨𐑟 𐑞 𐑮𐑦𐑟𐑳𐑤𐑑 𐑝 𐑒𐑺𐑓𐑩𐑤𐑦 𐑒𐑩𐑯𐑑𐑮𐑴𐑤𐑦𐑙 𐑣𐑻𐑕𐑧𐑤𐑓, 𐑝𐑻𐑕𐑩𐑕 𐑞 𐑐𐑮𐑪𐑚𐑩𐑚𐑦𐑤𐑦𐑑𐑦 𐑛𐑦𐑕𐑑𐑮𐑦𐑚𐑿𐑖𐑩𐑯 𐑓 𐑷𐑤 𐑞 𐑔𐑦𐑙𐑟 𐑖𐑰 𐑢𐑫𐑛 𐑛𐑵 \emph{𐑯𐑨𐑗𐑼𐑩𐑤𐑦} 𐑦𐑓 𐑲 𐑥𐑱𐑛 𐑩 𐑚𐑨𐑛 𐑡𐑴𐑒, 𐑞𐑧𐑯 𐑞𐑦𐑕 𐑚𐑦𐑣𐑱𐑝𐑘𐑼 𐑦𐑟 𐑕𐑦𐑜𐑯𐑦𐑓𐑦𐑒𐑩𐑯𐑑 𐑧𐑝𐑦𐑛𐑩𐑯𐑕 𐑓 𐑣𐑻 𐑣𐑲𐑛𐑦𐑙 𐑕𐑳𐑥𐑔𐑦𐑙.'

𐑚𐑳𐑑 𐑢𐑪𐑑 ·𐑣𐑨𐑮𐑦 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑔𐑷𐑑 𐑢𐑪𐑟, \emph{·𐑷 𐑒𐑮𐑨𐑐.}

·𐑣𐑨𐑮𐑦 𐑑𐑻𐑯𐑛 𐑣𐑦𐑟 𐑴𐑯 𐑣𐑧𐑛 𐑑 𐑕𐑒𐑨𐑯 𐑞 𐑕𐑑𐑮𐑰𐑑. 𐑯𐑴𐑐, 𐑯𐑴-𐑢𐑳𐑯 𐑯𐑽𐑚𐑲. “𐑣𐑰'𐑟 \emph{𐑯𐑪𐑑} 𐑛𐑧𐑛, 𐑦𐑟 𐑣𐑰,” ·𐑣𐑨𐑮𐑦 𐑕𐑲𐑛.

“·𐑥𐑼~·𐑐𐑪𐑑𐑼—”

“𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛 𐑦𐑟 𐑩𐑤𐑲𐑝. 𐑝 \emph{𐑒𐑹𐑕} 𐑣𐑰'𐑟 𐑩𐑤𐑲𐑝. 𐑦𐑑 𐑢𐑪𐑟 𐑩𐑯 \emph{𐑨𐑒𐑑} 𐑝 𐑳𐑑𐑼 \emph{𐑪𐑐𐑑𐑦𐑥𐑦𐑟𐑩𐑥} 𐑓 𐑥𐑰 𐑑 𐑣𐑨𐑝 𐑰𐑝𐑩𐑯 \emph{𐑛𐑮𐑰𐑥𐑛} 𐑳𐑞𐑼𐑢𐑲𐑟. 𐑲 \emph{𐑥𐑳𐑕𐑑} 𐑣𐑨𐑝 𐑑𐑱𐑒𐑩𐑯 𐑤𐑰𐑝 𐑝 𐑥𐑲 \emph{𐑕𐑧𐑯𐑕𐑩𐑟}, 𐑲 𐑒𐑭𐑯𐑑 \emph{𐑦𐑥𐑨𐑡𐑦𐑯} 𐑢𐑪𐑑 𐑲 𐑢𐑪𐑟 \emph{𐑔𐑦𐑙𐑒𐑦𐑙}. 𐑡𐑳𐑕𐑑 𐑚𐑦𐑒𐑪𐑟 \emph{𐑕𐑳𐑥𐑢𐑳𐑯} 𐑕𐑧𐑛 𐑞𐑨𐑑 𐑣𐑦𐑟 𐑚𐑪𐑛𐑦 𐑢𐑪𐑟 𐑓𐑬𐑯𐑛 𐑚𐑻𐑯𐑛 𐑑 𐑩 \emph{𐑒𐑮𐑦𐑕𐑐}, 𐑲 𐑒𐑭𐑯𐑑 𐑦𐑥𐑨𐑡𐑦𐑯 𐑢𐑲 𐑲 𐑢𐑫𐑛 𐑣𐑨𐑝 𐑔𐑷𐑑 𐑣𐑰 𐑢𐑪𐑟 \emph{𐑛𐑧𐑛}. \emph{𐑒𐑤𐑽𐑤𐑦} 𐑲 𐑣𐑨𐑝 𐑥𐑳𐑗 𐑤𐑧𐑓𐑑 𐑑 𐑤𐑻𐑯 𐑩𐑚𐑬𐑑 𐑞 𐑸𐑑 𐑝 𐑐𐑮𐑪𐑐𐑼 \emph{𐑐𐑧𐑕𐑦𐑥𐑦𐑟𐑩𐑥}.”

“·𐑥𐑼~·𐑐𐑪𐑑𐑼—”

“𐑨𐑑 𐑤𐑰𐑕𐑑 𐑑𐑧𐑤 𐑥𐑰 𐑞𐑺'𐑟 𐑯𐑪𐑑 𐑮𐑾𐑤𐑦 𐑩 𐑐𐑮𐑪𐑓𐑩𐑕𐑦…” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑢𐑪𐑟 𐑕𐑑𐑦𐑤 𐑜𐑦𐑝𐑦𐑙 𐑣𐑦𐑥 𐑞𐑨𐑑 𐑚𐑮𐑲𐑑, 𐑓𐑦𐑒𐑕𐑑 𐑕𐑥𐑲𐑤. “𐑴, 𐑿 𐑣𐑨𐑝 \emph{𐑜𐑪𐑑} 𐑑 𐑚𐑰 𐑒𐑦𐑛𐑦𐑙 𐑥𐑰.”

“·𐑥𐑼~·𐑐𐑪𐑑𐑼, 𐑿 𐑖𐑫𐑛𐑩𐑯𐑑 𐑜𐑴 𐑦𐑯𐑝𐑧𐑯𐑑𐑦𐑙 𐑔𐑦𐑙𐑟 𐑑 𐑢𐑳𐑮𐑦 𐑩𐑚𐑬𐑑—”

“𐑸 𐑿 \emph{𐑨𐑒𐑗𐑵𐑩𐑤𐑦} 𐑜𐑴𐑦𐑙 𐑑 𐑑𐑧𐑤 𐑥𐑰 \emph{𐑞𐑨𐑑}? 𐑦𐑥𐑨𐑡𐑦𐑯 𐑥𐑲 𐑮𐑦𐑨𐑒𐑖𐑩𐑯 𐑤𐑱𐑑𐑼, 𐑢𐑧𐑯 𐑲 𐑓𐑲𐑯𐑛 𐑬𐑑 𐑞𐑨𐑑 𐑞𐑺 𐑢𐑪𐑟 𐑕𐑳𐑥𐑔𐑦𐑙 𐑑 𐑢𐑳𐑮𐑦 𐑩𐑚𐑬𐑑 𐑭𐑓𐑑𐑼 𐑷𐑤.”

𐑣𐑻 𐑓𐑦𐑒𐑕𐑑 𐑕𐑥𐑲𐑤 𐑓𐑷𐑤𐑑𐑼𐑛.

𐑣𐑨𐑮𐑦'𐑟 𐑖𐑴𐑤𐑛𐑼𐑟 𐑕𐑤𐑳𐑥𐑐𐑑. “𐑲 𐑣𐑨𐑝 𐑩 𐑣𐑴𐑤 𐑢𐑻𐑤𐑛 𐑝 𐑥𐑨𐑡𐑦𐑒 𐑑 𐑨𐑯𐑩𐑤𐑲𐑟. 𐑲 𐑛𐑵 \emph{𐑯𐑪𐑑} 𐑣𐑨𐑝 𐑑𐑲𐑥 𐑓 𐑞𐑦𐑕.”

𐑞𐑧𐑯 𐑚𐑴𐑔 𐑝 𐑞𐑧𐑥 𐑖𐑳𐑑 𐑳𐑐, 𐑨𐑟 𐑩 𐑥𐑨𐑯 𐑦𐑯 𐑓𐑤𐑴𐑦𐑙 𐑪𐑮𐑦𐑯𐑡 𐑮𐑴𐑚𐑟 𐑩𐑐𐑽𐑛 𐑪𐑯 𐑞 𐑕𐑑𐑮𐑰𐑑 𐑯 𐑕𐑤𐑴𐑤𐑦 𐑐𐑭𐑕𐑑 𐑞𐑧𐑥 𐑚𐑲; ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑲𐑟 𐑑𐑮𐑨𐑒𐑑 𐑣𐑦𐑥, 𐑳𐑯𐑩𐑚𐑑𐑮𐑵𐑕𐑦𐑝𐑤𐑦. 𐑣𐑨𐑮𐑦'𐑟 𐑥𐑬𐑔 𐑢𐑪𐑟 𐑥𐑵𐑝𐑦𐑙 𐑨𐑟 𐑣𐑰 𐑗𐑵𐑛 𐑣𐑸𐑛 𐑪𐑯 𐑣𐑦𐑟 𐑤𐑦𐑐, 𐑯 𐑕𐑳𐑥𐑢𐑳𐑯 𐑢𐑪𐑗𐑦𐑙 𐑒𐑤𐑴𐑕𐑤𐑦 𐑢𐑫𐑛 𐑣𐑨𐑝 𐑯𐑴𐑑𐑦𐑕𐑑 𐑩 𐑑𐑲𐑯𐑦 𐑕𐑐𐑪𐑑 𐑝 𐑚𐑤𐑳𐑛 𐑩𐑐𐑽.

𐑢𐑧𐑯 𐑞 𐑪𐑮𐑦𐑯𐑡-𐑮𐑴𐑚𐑛 𐑥𐑨𐑯 𐑣𐑨𐑛 𐑐𐑭𐑕𐑑 𐑦𐑯𐑑𐑵 𐑞 𐑛𐑦𐑕𐑑𐑩𐑯𐑕, ·𐑣𐑨𐑮𐑦 𐑕𐑐𐑴𐑒 𐑩𐑜𐑱𐑯, 𐑦𐑯 𐑩 𐑤𐑴 𐑥𐑻𐑥𐑼. “𐑸 𐑿 𐑜𐑴𐑦𐑙 𐑑 𐑑𐑧𐑤 𐑥𐑰 𐑞 𐑑𐑮𐑵𐑔 𐑯𐑬, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤? 𐑯 𐑛𐑴𐑯𐑑 𐑚𐑪𐑞𐑼 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑢𐑱𐑝 𐑦𐑑 𐑪𐑓, 𐑲'𐑥 𐑯𐑪𐑑 𐑕𐑑𐑿𐑐𐑦𐑛.”

“𐑿'𐑼 \emph{𐑦𐑤𐑧𐑝𐑩𐑯 𐑘𐑽𐑟 𐑴𐑤𐑛}, ·𐑥𐑼~·𐑐𐑪𐑑𐑼!” 𐑖𐑰 𐑕𐑧𐑛 𐑦𐑯 𐑩 𐑣𐑸𐑖 𐑢𐑦𐑕𐑐𐑼.

“𐑯 𐑞𐑺𐑓𐑹 𐑕𐑳𐑚𐑣𐑿𐑥𐑩𐑯. 𐑕𐑪𐑮𐑦…𐑓 𐑩 𐑥𐑴𐑥𐑩𐑯𐑑 𐑞𐑺, 𐑲 \emph{𐑓𐑼𐑜𐑪𐑑}.”

“𐑞𐑰𐑟 𐑸 𐑛𐑮𐑧𐑛𐑓𐑩𐑤 𐑯 𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑 𐑥𐑨𐑑𐑼𐑟! 𐑞𐑱 𐑸 \emph{𐑕𐑰𐑒𐑮𐑩𐑑}, ·𐑥𐑼~·𐑐𐑪𐑑𐑼! 𐑦𐑑 𐑦𐑟 𐑩 \emph{𐑒𐑩𐑑𐑨𐑕𐑑𐑮𐑩𐑓𐑦} 𐑞𐑨𐑑 𐑿, 𐑕𐑑𐑦𐑤 𐑩 𐑗𐑲𐑤𐑛, 𐑯𐑴 𐑰𐑝𐑩𐑯 𐑞𐑦𐑕 𐑥𐑳𐑗! 𐑿 𐑥𐑳𐑕𐑑 𐑯𐑪𐑑 𐑑𐑧𐑤 \emph{𐑧𐑯𐑦𐑢𐑳𐑯}, 𐑛𐑵 𐑿 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛? 𐑨𐑚𐑕𐑩𐑤𐑵𐑑𐑤𐑦 𐑯𐑴-𐑢𐑳𐑯!”

𐑨𐑟 𐑕𐑳𐑥𐑑𐑲𐑥𐑟 𐑣𐑨𐑐𐑩𐑯𐑛 𐑢𐑧𐑯 ·𐑣𐑨𐑮𐑦 𐑜𐑪𐑑 \emph{𐑕𐑩𐑓𐑦𐑖𐑩𐑯𐑑𐑤𐑦} 𐑨𐑙𐑜𐑮𐑦, 𐑣𐑦𐑟 𐑚𐑤𐑳𐑛 𐑢𐑧𐑯𐑑 𐑒𐑴𐑤𐑛, 𐑦𐑯𐑕𐑑𐑧𐑛 𐑝 𐑣𐑪𐑑, 𐑯 𐑩 𐑑𐑧𐑮𐑦𐑚𐑩𐑤 𐑛𐑸𐑒 𐑒𐑤𐑨𐑮𐑦𐑑𐑦 𐑛𐑦𐑕𐑧𐑯𐑛𐑩𐑛 𐑴𐑝𐑼 𐑣𐑦𐑟 𐑥𐑲𐑯𐑛, 𐑥𐑨𐑐𐑦𐑙 𐑬𐑑 𐑐𐑪𐑕𐑩𐑚𐑩𐑤 𐑑𐑨𐑒𐑑𐑦𐑒𐑕 𐑯 𐑩𐑕𐑧𐑕𐑦𐑙 𐑞𐑺 𐑒𐑪𐑯𐑕𐑦𐑒𐑢𐑩𐑯𐑕𐑩𐑟 𐑢𐑦𐑞 𐑲𐑼𐑯 𐑮𐑾𐑤𐑦𐑟𐑩𐑥.

\begin{em}
    𐑐𐑶𐑯𐑑 𐑬𐑑 𐑞𐑨𐑑 𐑿 𐑣𐑨𐑝 𐑩 𐑮𐑲𐑑 𐑑 𐑯𐑴: 𐑓𐑱𐑤𐑘𐑼. 𐑦𐑤𐑧𐑝𐑩𐑯-𐑘𐑽-𐑴𐑤𐑛 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑛𐑵 𐑯𐑪𐑑 𐑣𐑨𐑝 𐑮𐑲𐑑𐑕 𐑑 𐑯𐑴 𐑧𐑯𐑦𐑔𐑦𐑙, 𐑦𐑯 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑲𐑟.

    𐑕𐑱 𐑞𐑨𐑑 𐑿 𐑢𐑦𐑤 𐑯𐑪𐑑 𐑚𐑰 𐑓𐑮𐑧𐑯𐑛𐑟 𐑧𐑯𐑦 𐑥𐑹: 𐑓𐑱𐑤𐑘𐑼. 𐑖𐑰 𐑛𐑳𐑟 𐑯𐑪𐑑 𐑝𐑨𐑤𐑿 𐑘𐑹 𐑓𐑮𐑧𐑯𐑛𐑖𐑦𐑐 𐑕𐑩𐑓𐑦𐑖𐑩𐑯𐑑𐑤𐑦.

    𐑐𐑶𐑯𐑑 𐑬𐑑 𐑞𐑨𐑑 𐑿 𐑢𐑦𐑤 𐑚𐑰 𐑦𐑯 𐑛𐑱𐑯𐑡𐑼 𐑦𐑓 𐑿 𐑛𐑵 𐑯𐑪𐑑 𐑯𐑴: 𐑓𐑱𐑤𐑘𐑼. 𐑐𐑤𐑨𐑯𐑟 𐑣𐑨𐑝 𐑷𐑤𐑮𐑧𐑛𐑦 𐑚𐑰𐑯 𐑥𐑱𐑛 𐑚𐑱𐑕𐑑 𐑪𐑯 𐑘𐑹 𐑦𐑜𐑯𐑼𐑩𐑯𐑕. 𐑞 \emph{𐑕𐑻𐑑𐑩𐑯} 𐑦𐑯𐑒𐑩𐑯𐑝𐑰𐑯𐑾𐑯𐑕 𐑝 𐑮𐑰𐑔𐑦𐑙𐑒𐑦𐑙 𐑢𐑦𐑤 𐑕𐑰𐑥 𐑓𐑸 𐑥𐑹 𐑳𐑯𐑐𐑨𐑤𐑩𐑑𐑩𐑚𐑩𐑤 𐑞𐑨𐑯 𐑞 𐑥𐑽 \emph{𐑳𐑯𐑕𐑻𐑑𐑩𐑯} 𐑐𐑮𐑪𐑕𐑐𐑧𐑒𐑑 𐑝 𐑘𐑹 𐑒𐑳𐑥𐑦𐑙 𐑑 𐑣𐑸𐑥.

    𐑡𐑳𐑕𐑑𐑦𐑕 𐑯 𐑮𐑰𐑟𐑩𐑯 𐑢𐑦𐑤 𐑚𐑴𐑔 𐑓𐑱𐑤. 𐑿 𐑥𐑳𐑕𐑑 𐑲𐑞𐑼 𐑓𐑲𐑯𐑛 𐑕𐑳𐑥𐑔𐑦𐑙 𐑿 𐑣𐑨𐑝 𐑞𐑨𐑑 𐑖𐑰 𐑢𐑪𐑯𐑑𐑕, 𐑹 𐑓𐑲𐑯𐑛 𐑕𐑳𐑥𐑔𐑦𐑙 𐑿 𐑒𐑨𐑯 𐑛𐑵 𐑢𐑦𐑗 𐑖𐑰 𐑓𐑽𐑟…
\end{em}

·𐑭.

“𐑢𐑧𐑤 𐑞𐑧𐑯, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑦𐑯 𐑩 𐑤𐑴, 𐑲𐑕𐑦 𐑑𐑴𐑯, “𐑦𐑑 𐑕𐑬𐑯𐑛𐑟 𐑤𐑲𐑒 𐑲 𐑣𐑨𐑝 𐑕𐑳𐑥𐑔𐑦𐑙 𐑿 𐑢𐑪𐑯𐑑. 𐑿 𐑒𐑨𐑯, 𐑦𐑓 𐑿 𐑤𐑲𐑒, 𐑑𐑧𐑤 𐑥𐑰 𐑞 𐑑𐑮𐑵𐑔, 𐑞 \emph{𐑣𐑴𐑤} 𐑑𐑮𐑵𐑔, 𐑯 𐑦𐑯 𐑮𐑦𐑑𐑻𐑯 𐑲 𐑢𐑦𐑤 𐑒𐑰𐑐 𐑘𐑹 𐑕𐑰𐑒𐑮𐑩𐑑𐑕. 𐑹 𐑿 𐑒𐑨𐑯 𐑑𐑮𐑲 𐑑 𐑒𐑰𐑐 𐑥𐑰 𐑦𐑜𐑯𐑼𐑩𐑯𐑑 𐑕𐑴 𐑿 𐑒𐑨𐑯 𐑿𐑟 𐑥𐑰 𐑨𐑟 𐑩 𐑐𐑷𐑯, 𐑦𐑯 𐑢𐑦𐑗 𐑒𐑱𐑕 𐑲 𐑢𐑦𐑤 𐑴 𐑿 𐑯𐑳𐑔𐑦𐑙.”

·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑑𐑪𐑐𐑑 𐑖𐑹𐑑 𐑦𐑯 𐑞 𐑕𐑑𐑮𐑰𐑑. 𐑣𐑻 𐑲𐑟 𐑚𐑤𐑱𐑟𐑛 𐑯 𐑣𐑻 𐑝𐑶𐑕 𐑛𐑦𐑕𐑧𐑯𐑛𐑩𐑛 𐑦𐑯𐑑𐑵 𐑩𐑯 𐑬𐑑𐑮𐑲𐑑 𐑣𐑦𐑕. “𐑣𐑬 𐑛𐑺 𐑿!”

“\emph{𐑣𐑬 𐑛𐑺 𐑿!}” 𐑣𐑰 𐑢𐑦𐑕𐑐𐑼𐑛 𐑚𐑨𐑒 𐑨𐑑 𐑣𐑻.

“𐑿 𐑢𐑫𐑛 \emph{𐑚𐑤𐑨𐑒𐑥𐑱𐑤} 𐑥𐑰?”

𐑣𐑨𐑮𐑦'𐑟 𐑤𐑦𐑐𐑕 𐑑𐑢𐑦𐑕𐑑𐑩𐑛. “𐑲 𐑨𐑥 \emph{𐑪𐑓𐑼𐑦𐑙} 𐑿 𐑩 \emph{𐑓𐑱𐑝𐑼}. 𐑲 𐑨𐑥 \emph{𐑜𐑦𐑝𐑦𐑙} 𐑿 𐑩 𐑗𐑭𐑯𐑕 𐑑 𐑐𐑮𐑩𐑑𐑧𐑒𐑑 \emph{𐑘𐑹} 𐑐𐑮𐑧𐑖𐑩𐑕 𐑕𐑰𐑒𐑮𐑩𐑑. 𐑦𐑓 𐑿 𐑮𐑦𐑓𐑿𐑟 𐑲 𐑢𐑦𐑤 𐑣𐑨𐑝 \emph{𐑧𐑝𐑮𐑦} 𐑯𐑨𐑗𐑼𐑩𐑤 𐑥𐑴𐑑𐑦𐑝 𐑑 𐑥𐑱𐑒 𐑦𐑯𐑒𐑢𐑲𐑼𐑦𐑟 𐑧𐑤𐑕𐑢𐑺, 𐑯𐑪𐑑 𐑑 𐑕𐑐𐑲𐑑 𐑿, 𐑚𐑳𐑑 𐑚𐑦𐑒𐑪𐑟 𐑲 \emph{𐑣𐑨𐑓 𐑑 𐑯𐑴}! 𐑜𐑧𐑑 𐑐𐑭𐑕𐑑 𐑘𐑹 𐑐𐑶𐑯𐑑𐑤𐑩𐑕 𐑨𐑙𐑜𐑼 𐑨𐑑 𐑩 \emph{𐑗𐑲𐑤𐑛} 𐑣𐑵 𐑿 𐑔𐑦𐑙𐑒 𐑷𐑑 𐑑 𐑴𐑚𐑱 𐑿, 𐑯 𐑿'𐑤 𐑮𐑾𐑤𐑲𐑟 𐑞𐑨𐑑 𐑧𐑯𐑦 𐑕𐑱𐑯 𐑨𐑛𐑳𐑤𐑑 𐑢𐑫𐑛 𐑛𐑵 𐑞 𐑕𐑱𐑥! \emph{𐑤𐑫𐑒 𐑨𐑑 𐑦𐑑 𐑓𐑮𐑪𐑥 𐑥𐑲 𐑐𐑼𐑕𐑐𐑧𐑒𐑑𐑦𐑝! 𐑣𐑬 𐑢𐑫𐑛 𐑿 𐑓𐑰𐑤 𐑦𐑓 𐑦𐑑 𐑢𐑪𐑟 \emph{𐑿}?}”

·𐑣𐑨𐑮𐑦 𐑢𐑪𐑗𐑑 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑩𐑚𐑟𐑻𐑝𐑛 𐑣𐑻 𐑣𐑸𐑖 𐑚𐑮𐑰𐑞𐑦𐑙. 𐑦𐑑 𐑩𐑒𐑻𐑛 𐑑 𐑣𐑦𐑥 𐑞𐑨𐑑 𐑦𐑑 𐑢𐑪𐑟 𐑑𐑲𐑥 𐑑 𐑰𐑟 𐑪𐑓 𐑞 𐑐𐑮𐑧𐑖𐑼, 𐑤𐑧𐑑 𐑣𐑻 𐑕𐑦𐑥𐑼 𐑓 𐑩 𐑢𐑲𐑤. “𐑿 𐑛𐑴𐑯𐑑 𐑣𐑨𐑓 𐑑 𐑛𐑦𐑕𐑲𐑛 𐑮𐑲𐑑 𐑩𐑢𐑱,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑦𐑯 𐑩 𐑥𐑹 𐑯𐑹𐑥𐑩𐑤 𐑑𐑴𐑯. “𐑲'𐑤 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑦𐑓 𐑿 𐑢𐑪𐑯𐑑 𐑑𐑲𐑥 𐑑 𐑔𐑦𐑙𐑒 𐑩𐑚𐑬𐑑 𐑥𐑲 \emph{𐑪𐑓𐑼}…𐑚𐑳𐑑 𐑲'𐑤 𐑢𐑹𐑯 𐑿 𐑝 𐑢𐑳𐑯 𐑔𐑦𐑙,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑣𐑦𐑟 𐑝𐑶𐑕 𐑜𐑴𐑦𐑙 𐑒𐑴𐑤𐑛𐑼. “𐑛𐑴𐑯𐑑 𐑑𐑮𐑲 𐑞𐑨𐑑 ·𐑩𐑚𐑤𐑦𐑝𐑦𐑱𐑖𐑩𐑯 𐑕𐑐𐑧𐑤 𐑪𐑯 𐑥𐑰. 𐑕𐑳𐑥 𐑑𐑲𐑥 𐑩𐑜𐑴 𐑲 𐑢𐑻𐑒𐑑 𐑬𐑑 𐑩 𐑕𐑦𐑜𐑯𐑩𐑤, 𐑯 𐑲 𐑣𐑨𐑝 𐑷𐑤𐑮𐑧𐑛𐑦 𐑕𐑧𐑯𐑑 𐑞𐑨𐑑 𐑕𐑦𐑜𐑯𐑩𐑤 𐑑 𐑥𐑲𐑕𐑧𐑤𐑓. 𐑦𐑓 𐑲 𐑓𐑲𐑯𐑛 𐑞𐑨𐑑 𐑕𐑦𐑜𐑯𐑩𐑤 𐑯 𐑲 𐑛𐑴𐑯𐑑 \emph{𐑮𐑦𐑥𐑧𐑥𐑚𐑼} 𐑕𐑧𐑯𐑛𐑦𐑙 𐑦𐑑…” ·𐑣𐑨𐑮𐑦 𐑤𐑧𐑑 𐑣𐑦𐑟 𐑝𐑶𐑕 𐑑𐑮𐑱𐑤 𐑪𐑓 𐑕𐑦𐑜𐑯𐑦𐑓𐑦𐑒𐑩𐑯𐑑𐑤𐑦.

·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑓𐑱𐑕 𐑢𐑪𐑟 𐑢𐑻𐑒𐑦𐑙 𐑨𐑟 𐑣𐑻 𐑦𐑒𐑕𐑐𐑮𐑧𐑖𐑩𐑯𐑟 𐑖𐑦𐑓𐑑𐑩𐑛. “𐑲…𐑢𐑪𐑟𐑩𐑯𐑑 𐑔𐑦𐑙𐑒𐑦𐑙 𐑝 ·𐑩𐑚𐑤𐑦𐑝𐑦𐑱𐑑𐑦𐑙 𐑿, ·𐑥𐑼~·𐑐𐑪𐑑𐑼…𐑚𐑳𐑑 𐑢𐑲 𐑢𐑫𐑛 𐑿 𐑣𐑨𐑝 \emph{𐑦𐑯𐑝𐑧𐑯𐑑𐑩𐑛} 𐑕𐑳𐑗 𐑩 𐑕𐑦𐑜𐑯𐑩𐑤 𐑦𐑓 𐑿 𐑛𐑦𐑛𐑩𐑯𐑑 𐑯𐑴 𐑩𐑚𐑬𐑑—”

“𐑲 𐑔𐑷𐑑 𐑝 𐑦𐑑 𐑢𐑲𐑤 𐑮𐑰𐑛𐑦𐑙 𐑩 ·𐑥𐑳𐑜𐑩𐑤 𐑕𐑲𐑩𐑯𐑕-𐑓𐑦𐑒𐑖𐑩𐑯 𐑚𐑫𐑒, 𐑯 𐑕𐑧𐑛 𐑑 𐑥𐑲𐑕𐑧𐑤𐑓, \emph{𐑢𐑧𐑤, 𐑡𐑳𐑕𐑑 𐑦𐑯 𐑒𐑱𐑕…} 𐑯 𐑯𐑴, 𐑲 𐑢𐑴𐑯𐑑 𐑑𐑧𐑤 𐑿 𐑞 𐑕𐑦𐑜𐑯𐑩𐑤, 𐑲'𐑥 𐑯𐑪𐑑 𐑛𐑳𐑥.”

“𐑲 𐑣𐑨𐑛𐑩𐑯𐑑 𐑐𐑤𐑨𐑯𐑛 𐑑 𐑭𐑕𐑒,” ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛. 𐑖𐑰 𐑕𐑰𐑥𐑛 𐑑 𐑓𐑴𐑤𐑛 𐑦𐑯 𐑪𐑯 𐑣𐑻𐑕𐑧𐑤𐑓, 𐑯 𐑕𐑳𐑛𐑩𐑯𐑤𐑦 𐑤𐑫𐑒𐑑 𐑝𐑧𐑮𐑦 𐑴𐑤𐑛, 𐑯 𐑝𐑧𐑮𐑦 𐑑𐑲𐑼𐑛. “𐑞𐑦𐑕 𐑣𐑨𐑟 𐑚𐑰𐑯 𐑩𐑯 𐑦𐑜𐑟𐑷𐑕𐑑𐑦𐑙 𐑛𐑱, ·𐑥𐑼~·𐑐𐑪𐑑𐑼. 𐑒𐑨𐑯 𐑢𐑰 𐑜𐑧𐑑 𐑘𐑹 𐑑𐑮𐑳𐑙𐑒, 𐑯 𐑕𐑧𐑯𐑛 𐑿 𐑣𐑴𐑥? 𐑲 𐑢𐑦𐑤 𐑑𐑮𐑳𐑕𐑑 𐑿 𐑯𐑪𐑑 𐑑 𐑕𐑐𐑰𐑒 𐑩𐑐𐑪𐑯 𐑞𐑦𐑕 𐑥𐑨𐑑𐑼 𐑩𐑯𐑑𐑦𐑤 𐑲 𐑣𐑨𐑝 𐑣𐑨𐑛 𐑑𐑲𐑥 𐑑 𐑔𐑦𐑙𐑒. 𐑒𐑰𐑐 𐑦𐑯 𐑥𐑲𐑯𐑛 𐑞𐑨𐑑 𐑞𐑺 𐑸 𐑴𐑯𐑤𐑦 𐑑𐑵 𐑳𐑞𐑼 𐑐𐑰𐑐𐑩𐑤 𐑦𐑯 𐑞 𐑣𐑴𐑤 𐑢𐑻𐑤𐑛 𐑣𐑵 𐑯𐑴 𐑩𐑚𐑬𐑑 𐑞𐑦𐑕 𐑥𐑨𐑑𐑼, 𐑯 𐑞𐑱 𐑸 ·𐑣𐑧𐑛𐑥𐑭𐑕𐑑𐑼 ·𐑭𐑤𐑚𐑳𐑕 ·𐑛𐑳𐑥𐑚𐑩𐑤𐑛𐑹 𐑯 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑕𐑧𐑝𐑼𐑩𐑕 ·𐑕𐑯𐑱𐑐.”

𐑕𐑴. 𐑯𐑿 𐑦𐑯𐑓𐑼𐑥𐑱𐑖𐑩𐑯; 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑩 𐑐𐑰𐑕 𐑪𐑓𐑼𐑦𐑙. ·𐑣𐑨𐑮𐑦 𐑯𐑪𐑛𐑩𐑛 𐑦𐑯 𐑩𐑒𐑕𐑧𐑐𐑑𐑩𐑯𐑕, 𐑯 𐑑𐑻𐑯𐑛 𐑣𐑦𐑟 𐑣𐑧𐑛 𐑑 𐑤𐑫𐑒 𐑓𐑹𐑢𐑼𐑛, 𐑯 𐑕𐑑𐑸𐑑𐑩𐑛 𐑢𐑷𐑒𐑦𐑙 𐑩𐑜𐑱𐑯, 𐑨𐑟 𐑣𐑦𐑟 𐑚𐑤𐑳𐑛 𐑕𐑤𐑴𐑤𐑦 𐑚𐑦𐑜𐑨𐑯 𐑑 𐑢𐑹𐑥 𐑴𐑝𐑼 𐑢𐑳𐑯𐑕 𐑥𐑹.

“𐑕𐑴 𐑯𐑬 𐑲'𐑝 𐑜𐑪𐑑 𐑑 𐑓𐑲𐑯𐑛 𐑕𐑳𐑥 𐑢𐑱 𐑑 𐑒𐑦𐑤 𐑩𐑯 𐑦𐑥𐑹𐑑𐑩𐑤 ·𐑛𐑸𐑒 ·𐑢𐑦𐑟𐑼𐑛,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑯 𐑕𐑲𐑛 𐑦𐑯 𐑓𐑮𐑳𐑕𐑑𐑮𐑱𐑖𐑩𐑯. “𐑲 𐑮𐑾𐑤𐑦 𐑢𐑦𐑖 𐑿 𐑣𐑨𐑛 𐑑𐑴𐑤𐑛 𐑥𐑰 𐑞𐑨𐑑 \emph{𐑚𐑦𐑓𐑹} 𐑲 𐑕𐑑𐑸𐑑𐑩𐑛 𐑖𐑪𐑐𐑦𐑙.”

\later

𐑞 𐑑𐑮𐑳𐑙𐑒 𐑖𐑪𐑐 𐑢𐑪𐑟 𐑥𐑹 𐑮𐑦𐑗𐑤𐑦 𐑩𐑐𐑶𐑯𐑑𐑩𐑛 𐑞𐑨𐑯 𐑧𐑯𐑦 𐑳𐑞𐑼 𐑖𐑪𐑐 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑝𐑦𐑟𐑦𐑑𐑩𐑛; 𐑞 𐑒𐑻𐑑𐑩𐑯𐑟 𐑢𐑻 𐑤𐑳𐑖 𐑯 𐑛𐑧𐑤𐑦𐑒𐑩𐑑𐑤𐑦 𐑐𐑨𐑑𐑼𐑯𐑛, 𐑞 𐑓𐑤𐑹 𐑯 𐑢𐑷𐑤𐑟 𐑝 𐑕𐑑𐑱𐑯𐑛 𐑯 𐑐𐑪𐑤𐑦𐑖𐑑 𐑢𐑫𐑛, 𐑯 𐑞 𐑑𐑮𐑳𐑙𐑒𐑕 𐑪𐑒𐑿𐑐𐑲𐑛 𐑐𐑤𐑱𐑕𐑩𐑟 𐑝 𐑪𐑯𐑼 𐑪𐑯 𐑐𐑪𐑤𐑦𐑖𐑑 𐑲𐑝𐑼𐑦 𐑐𐑤𐑨𐑑𐑓𐑹𐑥𐑟. 𐑞 𐑕𐑱𐑤𐑟𐑥𐑩𐑯 𐑢𐑪𐑟 𐑛𐑮𐑧𐑕𐑑 𐑦𐑯 𐑮𐑴𐑚𐑟 𐑝 𐑓𐑲𐑯𐑼𐑦 𐑴𐑯𐑤𐑦 𐑩 𐑒𐑳𐑑 𐑚𐑦𐑤𐑴 𐑞𐑴𐑟 𐑝 ·𐑤𐑵𐑕𐑾𐑕 ·𐑥𐑨𐑤𐑓𐑶, 𐑯 𐑕𐑐𐑴𐑒 𐑢𐑦𐑞 𐑦𐑒𐑕𐑒𐑢𐑦𐑟𐑦𐑑, 𐑶𐑤𐑦 𐑐𐑩𐑤𐑲𐑑𐑯𐑩𐑕 𐑑 𐑚𐑴𐑔 ·𐑣𐑨𐑮𐑦 𐑯 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤.

·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑭𐑕𐑒𐑑 𐑣𐑦𐑟 𐑒𐑢𐑧𐑕𐑗𐑩𐑯𐑟, 𐑯 𐑣𐑨𐑛 𐑜𐑮𐑨𐑝𐑦𐑑𐑱𐑑𐑩𐑛 𐑑 𐑩 𐑑𐑮𐑳𐑙𐑒 𐑝 𐑣𐑧𐑝𐑦-𐑤𐑫𐑒𐑦𐑙 𐑢𐑫𐑛, 𐑯𐑪𐑑 𐑐𐑪𐑤𐑦𐑖𐑑 𐑚𐑳𐑑 𐑢𐑹𐑥 𐑯 𐑕𐑪𐑤𐑦𐑛, 𐑒𐑸𐑝𐑛 𐑢𐑦𐑞 𐑞 𐑐𐑨𐑑𐑼𐑯 𐑝 𐑩 𐑜𐑸𐑛𐑾𐑯 𐑛𐑮𐑨𐑜𐑩𐑯 𐑣𐑵𐑟 𐑲𐑟 𐑖𐑦𐑓𐑑𐑩𐑛 𐑑 𐑤𐑫𐑒 𐑨𐑑 𐑧𐑯𐑦𐑢𐑳𐑯 𐑯𐑽𐑦𐑙 𐑦𐑑. 𐑩 𐑑𐑮𐑳𐑙𐑒 𐑗𐑸𐑥𐑛 𐑑 𐑚𐑰 𐑤𐑲𐑑, 𐑑 𐑖𐑮𐑦𐑙𐑒 𐑪𐑯 𐑒𐑩𐑥𐑭𐑯𐑛, 𐑑 𐑕𐑐𐑮𐑬𐑑 𐑕𐑥𐑷𐑤 𐑒𐑤𐑷𐑛 𐑑𐑧𐑯𐑑𐑩𐑒𐑩𐑤𐑟 𐑓𐑮𐑪𐑥 𐑦𐑑𐑕 𐑚𐑪𐑑𐑩𐑥 𐑯 𐑕𐑒𐑢𐑻𐑥 𐑭𐑓𐑑𐑼 𐑦𐑑𐑕 𐑴𐑯𐑼. 𐑩 𐑑𐑮𐑳𐑙𐑒 𐑢𐑦𐑞 𐑑𐑵 𐑛𐑮𐑷𐑼𐑟 𐑪𐑯 𐑰𐑗 𐑝 𐑓𐑹 𐑕𐑲𐑛𐑟 𐑞𐑨𐑑 𐑰𐑗 𐑕𐑤𐑦𐑛 𐑬𐑑 𐑑 𐑮𐑦𐑝𐑰𐑤 𐑒𐑪𐑥𐑐𐑸𐑑𐑥𐑧𐑯𐑑𐑕 𐑨𐑟 𐑛𐑰𐑐 𐑨𐑟 𐑞 𐑣𐑴𐑤 𐑑𐑮𐑳𐑙𐑒. 𐑩 𐑤𐑦𐑛 𐑢𐑦𐑞 𐑓𐑹 𐑤𐑪𐑒𐑕 𐑰𐑗 𐑝 𐑢𐑦𐑗 𐑢𐑫𐑛 𐑮𐑦𐑝𐑰𐑤 𐑩 𐑛𐑦𐑓𐑼𐑩𐑯𐑑 𐑕𐑐𐑱𐑕 𐑦𐑯𐑕𐑲𐑛. 𐑯—𐑞𐑦𐑕 𐑢𐑪𐑟 𐑞 𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑 𐑐𐑸𐑑—𐑩 𐑣𐑨𐑯𐑛𐑩𐑤 𐑪𐑯 𐑞 𐑚𐑪𐑑𐑩𐑥 𐑢𐑦𐑗 𐑕𐑤𐑦𐑛 𐑬𐑑 𐑩 𐑓𐑮𐑱𐑥 𐑒𐑩𐑯𐑑𐑱𐑯𐑦𐑙 𐑩 𐑕𐑑𐑺𐑒𐑱𐑕 𐑤𐑰𐑛𐑦𐑙 𐑛𐑬𐑯 𐑦𐑯𐑑𐑵 𐑩 𐑕𐑥𐑷𐑤, 𐑤𐑲𐑑𐑩𐑛 𐑮𐑵𐑥 𐑞𐑨𐑑 𐑢𐑫𐑛 𐑣𐑴𐑤𐑛, ·𐑣𐑨𐑮𐑦 𐑧𐑕𐑑𐑦𐑥𐑱𐑑𐑩𐑛, 𐑼𐑬𐑯𐑛 𐑑𐑢𐑧𐑤𐑝 𐑚𐑫𐑒𐑒𐑱𐑕𐑩𐑟.

𐑦𐑓 𐑞𐑱 𐑥𐑱𐑛 𐑤𐑳𐑜𐑦𐑡 𐑤𐑲𐑒 𐑞𐑦𐑕, ·𐑣𐑨𐑮𐑦 𐑛𐑦𐑛𐑩𐑯𐑑 𐑯𐑴 𐑢𐑲 𐑧𐑯𐑦𐑢𐑳𐑯 𐑚𐑪𐑞𐑼𐑛 𐑴𐑯𐑦𐑙 𐑩 𐑣𐑬𐑕.

𐑢𐑳𐑯 𐑣𐑳𐑯𐑛𐑮𐑩𐑛 𐑯 𐑱𐑑 𐑜𐑴𐑤𐑛𐑩𐑯 ·𐑜𐑨𐑤𐑾𐑯𐑟. 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑞 𐑐𐑮𐑲𐑕 𐑝 𐑩 𐑜𐑫𐑛 𐑑𐑮𐑳𐑙𐑒, 𐑤𐑲𐑑𐑤𐑦 𐑿𐑟𐑛. 𐑨𐑑 𐑼𐑬𐑯𐑛 𐑓𐑦𐑓𐑑𐑦 ·𐑚𐑮𐑦𐑑𐑦𐑖 𐑐𐑬𐑯𐑛𐑟 𐑑 𐑞 ·𐑜𐑨𐑤𐑾𐑯, 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑦𐑯𐑳𐑓 𐑑 𐑚𐑲 𐑩 𐑕𐑱𐑒𐑪𐑯𐑛-𐑣𐑨𐑯𐑛 𐑒𐑸. 𐑦𐑑 𐑢𐑫𐑛 𐑚𐑰 𐑥𐑹 𐑦𐑒𐑕𐑐𐑧𐑯𐑕𐑦𐑝 𐑞𐑨𐑯 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑧𐑤𐑕 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑧𐑝𐑼 𐑚𐑷𐑑 𐑦𐑯 𐑣𐑦𐑟 𐑣𐑴𐑤 𐑤𐑲𐑓 𐑷𐑤 𐑐𐑫𐑑 𐑑𐑩𐑜𐑧𐑞𐑼.

𐑯𐑲𐑯𐑑𐑦-𐑕𐑧𐑝𐑩𐑯 ·𐑜𐑨𐑤𐑾𐑯𐑟. 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑣𐑬 𐑥𐑳𐑗 𐑢𐑪𐑟 𐑤𐑧𐑓𐑑 𐑦𐑯 𐑞 𐑚𐑨𐑜 𐑝 𐑜𐑴𐑤𐑛 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑩𐑤𐑬𐑛 𐑑 𐑑𐑱𐑒 𐑬𐑑 𐑝 ·𐑜𐑮𐑦𐑙𐑜𐑩𐑑𐑕.

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑢𐑹 𐑩 𐑤𐑫𐑒 𐑝 𐑖𐑨𐑜𐑮𐑦𐑯 𐑩𐑐𐑪𐑯 𐑣𐑻 𐑓𐑱𐑕. 𐑭𐑓𐑑𐑼 𐑩 𐑤𐑪𐑙 𐑛𐑱'𐑟 𐑖𐑪𐑐𐑦𐑙 𐑖𐑰 𐑣𐑨𐑛𐑩𐑯𐑑 𐑯𐑰𐑛𐑩𐑛 𐑑 𐑭𐑕𐑒 ·𐑣𐑨𐑮𐑦 𐑣𐑬 𐑥𐑳𐑗 𐑜𐑴𐑤𐑛 𐑢𐑪𐑟 𐑤𐑧𐑓𐑑 𐑦𐑯 𐑞 𐑚𐑨𐑜, 𐑭𐑓𐑑𐑼 𐑞 𐑕𐑱𐑤𐑟𐑥𐑩𐑯 𐑒𐑢𐑴𐑑𐑩𐑛 𐑣𐑦𐑟 𐑐𐑮𐑲𐑕, 𐑢𐑦𐑗 𐑥𐑧𐑯𐑑 𐑞 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑒𐑫𐑛 𐑛𐑵 𐑜𐑫𐑛 𐑥𐑧𐑯𐑑𐑩𐑤 𐑼𐑦𐑔𐑥𐑩𐑑𐑦𐑒 𐑢𐑦𐑞𐑬𐑑 𐑐𐑧𐑯 𐑯 𐑐𐑱𐑐𐑼. 𐑢𐑳𐑯𐑕 𐑩𐑜𐑱𐑯, ·𐑣𐑨𐑮𐑦 𐑮𐑦𐑥𐑲𐑯𐑛𐑩𐑛 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑞𐑨𐑑 \emph{𐑕𐑲𐑩𐑯𐑑𐑦𐑓𐑦𐑒𐑤𐑦 𐑦𐑤𐑦𐑑𐑼𐑩𐑑} 𐑢𐑪𐑟 𐑯𐑪𐑑 𐑨𐑑 𐑷𐑤 𐑞 𐑕𐑱𐑥 𐑔𐑦𐑙 𐑨𐑟 \emph{𐑕𐑑𐑿𐑐𐑦𐑛}.

“𐑲'𐑥 𐑕𐑪𐑮𐑦, 𐑘𐑳𐑙 𐑥𐑨𐑯,” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. “𐑞𐑦𐑕 𐑦𐑟 𐑦𐑯𐑑𐑲𐑼𐑤𐑦 𐑥𐑲 𐑓𐑷𐑤𐑑. 𐑲 𐑢𐑫𐑛 𐑪𐑓𐑼 𐑑 𐑑𐑱𐑒 𐑿 𐑚𐑨𐑒 𐑑 ·𐑜𐑮𐑦𐑙𐑜𐑩𐑑𐑕, 𐑚𐑳𐑑 𐑞 𐑚𐑨𐑙𐑒 𐑢𐑦𐑤 𐑚𐑰 𐑒𐑤𐑴𐑟𐑛 𐑓 𐑷𐑤 𐑚𐑳𐑑 𐑦𐑥𐑻𐑡𐑩𐑯𐑕𐑦 𐑕𐑻𐑝𐑦𐑕𐑩𐑟 𐑯𐑬.”

·𐑣𐑨𐑮𐑦 𐑤𐑫𐑒𐑑 𐑨𐑑 𐑣𐑻, 𐑢𐑳𐑯𐑛𐑼𐑦𐑙…

“𐑢𐑧𐑤,” 𐑕𐑲𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑨𐑟 𐑖𐑰 𐑕𐑢𐑳𐑙 𐑪𐑯 𐑢𐑳𐑯 𐑣𐑰𐑤, “𐑢𐑰 𐑥𐑱 𐑨𐑟 𐑢𐑧𐑤 𐑜𐑴, 𐑲 𐑕𐑩𐑐𐑴𐑟.”

…𐑖𐑰 \emph{𐑣𐑨𐑛𐑩𐑯𐑑} 𐑤𐑪𐑕𐑑 𐑦𐑑 𐑒𐑩𐑥𐑐𐑤𐑰𐑑𐑤𐑦 𐑢𐑧𐑯 𐑩 𐑗𐑲𐑤𐑛 𐑣𐑨𐑛 𐑛𐑺𐑛 𐑛𐑦𐑓𐑲 𐑣𐑻. 𐑖𐑰 𐑣𐑨𐑛𐑩𐑯𐑑 𐑚𐑰𐑯 𐑣𐑨𐑐𐑦, 𐑚𐑳𐑑 𐑖𐑰 𐑣𐑨𐑛 \emph{𐑔𐑷𐑑} 𐑦𐑯𐑕𐑑𐑧𐑛 𐑝 𐑦𐑒𐑕𐑐𐑤𐑴𐑛𐑦𐑙 𐑦𐑯 𐑓𐑘𐑫𐑼𐑦. 𐑦𐑑 𐑥𐑲𐑑 𐑣𐑨𐑝 𐑡𐑳𐑕𐑑 𐑚𐑰𐑯 𐑞𐑨𐑑 𐑞𐑺 𐑢𐑪𐑟 𐑩𐑯 𐑦𐑥𐑹𐑑𐑩𐑤 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛 𐑑 𐑓𐑲𐑑—𐑞𐑨𐑑 𐑖𐑰 𐑣𐑨𐑛 𐑯𐑰𐑛𐑩𐑛 ·𐑣𐑨𐑮𐑦'𐑟 𐑜𐑫𐑛𐑢𐑦𐑤. 𐑚𐑳𐑑 𐑥𐑴𐑕𐑑 𐑨𐑛𐑳𐑤𐑑𐑕 𐑢𐑫𐑛𐑩𐑯𐑑 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑒𐑱𐑐𐑩𐑚𐑩𐑤 𐑝 𐑔𐑦𐑙𐑒𐑦𐑙 𐑰𐑝𐑩𐑯 𐑞𐑨𐑑 𐑥𐑳𐑗; 𐑢𐑫𐑛𐑩𐑯𐑑 𐑒𐑩𐑯𐑕𐑦𐑛𐑼 \emph{𐑓𐑿𐑗𐑼 𐑒𐑪𐑯𐑕𐑦𐑒𐑢𐑩𐑯𐑕𐑩𐑟} 𐑨𐑑 𐑷𐑤, 𐑦𐑓 𐑕𐑳𐑥𐑢𐑳𐑯 𐑤𐑴𐑼 𐑦𐑯 𐑕𐑑𐑱𐑑𐑩𐑕 𐑣𐑨𐑛 𐑮𐑦𐑓𐑿𐑟𐑛 𐑑 𐑴𐑚𐑱 𐑞𐑧𐑥…

“·𐑐𐑮𐑩𐑓𐑧𐑕𐑼?” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛.

𐑞 𐑢𐑦𐑗 𐑑𐑻𐑯𐑛 𐑚𐑨𐑒 𐑯 𐑤𐑫𐑒𐑑 𐑨𐑑 𐑣𐑦𐑥.

·𐑣𐑨𐑮𐑦 𐑑𐑫𐑒 𐑩 𐑛𐑰𐑐 𐑚𐑮𐑧𐑔. 𐑣𐑰 𐑯𐑰𐑛𐑩𐑛 𐑑 𐑚𐑰 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑨𐑙𐑜𐑮𐑦 𐑓 𐑢𐑪𐑑 𐑣𐑰 𐑢𐑪𐑯𐑑𐑩𐑛 𐑑 𐑑𐑮𐑲 𐑯𐑬, 𐑞𐑺 𐑢𐑪𐑟 𐑯𐑴 𐑢𐑱 𐑣𐑰'𐑛 𐑣𐑨𐑝 𐑞 𐑒𐑳𐑮𐑦𐑡 𐑑 𐑛𐑵 𐑦𐑑 𐑳𐑞𐑼𐑢𐑲𐑟. \emph{𐑖𐑰 𐑛𐑦𐑛𐑩𐑯𐑑 𐑤𐑦𐑕𐑩𐑯 𐑑 𐑥𐑰,} 𐑣𐑰 𐑔𐑷𐑑 𐑑 𐑣𐑦𐑥𐑕𐑧𐑤𐑓, \emph{𐑲 𐑢𐑫𐑛 𐑣𐑨𐑝 𐑑𐑱𐑒𐑩𐑯 𐑥𐑹 𐑜𐑴𐑤𐑛 𐑚𐑳𐑑 𐑖𐑰 𐑛𐑦𐑛𐑩𐑯𐑑 𐑢𐑪𐑯𐑑 𐑑 𐑤𐑦𐑕𐑩𐑯…} ·𐑓𐑴𐑒𐑩𐑕𐑦𐑙 𐑣𐑦𐑟 𐑦𐑯𐑑𐑲𐑼 𐑢𐑻𐑤𐑛 𐑪𐑯 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑯 𐑞 𐑯𐑰𐑛 𐑑 𐑚𐑧𐑯𐑛 𐑞𐑦𐑕 𐑒𐑪𐑯𐑝𐑼𐑕𐑱𐑖𐑩𐑯 𐑑 𐑣𐑦𐑟 𐑢𐑦𐑤, 𐑣𐑰 𐑕𐑐𐑴𐑒.

“·𐑐𐑮𐑩𐑓𐑧𐑕𐑼, 𐑿 𐑔𐑷𐑑 𐑢𐑳𐑯 𐑣𐑳𐑯𐑛𐑮𐑩𐑛 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑢𐑫𐑛 𐑚𐑰 𐑥𐑹 𐑞𐑨𐑯 𐑦𐑯𐑳𐑓 𐑓 𐑩 𐑑𐑮𐑳𐑙𐑒. 𐑞𐑨𐑑'𐑕 𐑢𐑲 𐑿 𐑛𐑦𐑛𐑩𐑯𐑑 𐑚𐑪𐑞𐑼 𐑢𐑹𐑯𐑦𐑙 𐑥𐑰 𐑚𐑦𐑓𐑹 𐑦𐑑 𐑢𐑧𐑯𐑑 𐑛𐑬𐑯 𐑑 𐑯𐑲𐑯𐑑𐑦-𐑕𐑧𐑝𐑩𐑯. 𐑢𐑦𐑗 𐑦𐑟 𐑡𐑳𐑕𐑑 𐑞 𐑕𐑹𐑑 𐑝 𐑔𐑦𐑙 𐑞 𐑮𐑰𐑕𐑻𐑗 𐑕𐑑𐑳𐑛𐑦𐑟 𐑖𐑴—𐑞𐑨𐑑'𐑕 𐑢𐑪𐑑 𐑣𐑨𐑐𐑩𐑯𐑟 𐑢𐑧𐑯 𐑐𐑰𐑐𐑩𐑤 𐑔𐑦𐑙𐑒 𐑞𐑱'𐑼 𐑤𐑰𐑝𐑦𐑙 𐑞𐑧𐑥𐑕𐑧𐑤𐑝𐑟 𐑩 \emph{𐑤𐑦𐑑𐑩𐑤} 𐑧𐑮𐑼 𐑥𐑸𐑡𐑦𐑯. 𐑞𐑱'𐑼 𐑯𐑪𐑑 𐑐𐑧𐑕𐑦𐑥𐑦𐑕𐑑𐑦𐑒 𐑦𐑯𐑳𐑓. 𐑦𐑓 𐑦𐑑'𐑩𐑛 𐑚𐑰𐑯 𐑳𐑐 𐑑 𐑥𐑰, 𐑲'𐑛 𐑣𐑨𐑝 𐑑𐑱𐑒𐑩𐑯 \emph{𐑑𐑵 𐑣𐑳𐑯𐑛𐑮𐑩𐑛} ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑡𐑳𐑕𐑑 𐑑 𐑚𐑰 𐑖𐑫𐑼. 𐑞𐑺 𐑢𐑪𐑟 𐑐𐑤𐑧𐑯𐑑𐑦 𐑝 𐑥𐑳𐑯𐑦 𐑦𐑯 𐑞𐑨𐑑 𐑝𐑷𐑤𐑑, 𐑯 𐑲 𐑒𐑫𐑛 𐑣𐑨𐑝 𐑐𐑫𐑑 𐑚𐑨𐑒 𐑧𐑯𐑦 𐑧𐑒𐑕𐑑𐑮𐑩 𐑤𐑱𐑑𐑼. 𐑚𐑳𐑑 𐑲 𐑔𐑷𐑑 𐑿 𐑢𐑫𐑛𐑩𐑯𐑑 𐑤𐑧𐑑 𐑥𐑰 𐑛𐑵 𐑦𐑑. 𐑲 𐑔𐑷𐑑 𐑿'𐑛 𐑚𐑰 𐑨𐑙𐑜𐑮𐑦 𐑨𐑑 𐑥𐑰 𐑡𐑳𐑕𐑑 𐑓 𐑭𐑕𐑒𐑦𐑙. 𐑢𐑪𐑟 𐑲 𐑮𐑪𐑙?”

“𐑲 𐑕𐑩𐑐𐑴𐑟 𐑲 𐑥𐑳𐑕𐑑 𐑒𐑩𐑯𐑓𐑧𐑕 𐑞𐑨𐑑 𐑿 𐑸 𐑮𐑲𐑑,” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. “𐑚𐑳𐑑, 𐑘𐑳𐑙 𐑥𐑨𐑯—”

“𐑞𐑨𐑑 𐑕𐑹𐑑 𐑝 𐑔𐑦𐑙 𐑦𐑟 𐑞 𐑮𐑰𐑟𐑩𐑯 𐑢𐑲 𐑲 𐑣𐑨𐑝 𐑑𐑮𐑳𐑚𐑩𐑤 𐑑𐑮𐑳𐑕𐑑𐑦𐑙 𐑨𐑛𐑳𐑤𐑑𐑕.” ·𐑕𐑳𐑥𐑣𐑬 ·𐑣𐑨𐑮𐑦 𐑒𐑧𐑐𐑑 𐑣𐑦𐑟 𐑝𐑶𐑕 𐑕𐑑𐑧𐑛𐑦. “𐑚𐑦𐑒𐑪𐑟 𐑞𐑱 𐑜𐑧𐑑 𐑨𐑙𐑜𐑮𐑦 𐑦𐑓 𐑿 𐑰𐑝𐑩𐑯 \emph{𐑑𐑮𐑲} 𐑑 𐑮𐑰𐑟𐑩𐑯 𐑢𐑦𐑞 𐑞𐑧𐑥. 𐑑 𐑞𐑧𐑥 𐑦𐑑'𐑕 𐑛𐑦𐑓𐑲𐑩𐑯𐑕 𐑯 𐑦𐑯𐑕𐑩𐑤𐑩𐑯𐑕 𐑯 𐑩 𐑗𐑨𐑤𐑩𐑯𐑡 𐑑 𐑞𐑺 𐑣𐑲𐑼 𐑑𐑮𐑲𐑚𐑩𐑤 𐑕𐑑𐑱𐑑𐑩𐑕. 𐑦𐑓 𐑿 𐑑𐑮𐑲 𐑑 𐑑𐑷𐑒 𐑑 𐑞𐑧𐑥 𐑞𐑱 𐑜𐑧𐑑 \emph{𐑨𐑙𐑜𐑮𐑦}. 𐑕𐑴 𐑦𐑓 𐑲 𐑣𐑨𐑛 𐑧𐑯𐑦𐑔𐑦𐑙 \emph{𐑮𐑾𐑤𐑦 𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑} 𐑑 𐑛𐑵, 𐑲 𐑢𐑫𐑛𐑩𐑯𐑑 𐑚𐑰 𐑱𐑚𐑩𐑤 𐑑 𐑑𐑮𐑳𐑕𐑑 𐑿. 𐑰𐑝𐑩𐑯 𐑦𐑓 𐑿 𐑤𐑦𐑕𐑩𐑯𐑛 𐑢𐑦𐑞 𐑛𐑰𐑐 𐑒𐑩𐑯𐑕𐑻𐑯 𐑑 𐑢𐑪𐑑𐑧𐑝𐑼 𐑲 𐑕𐑧𐑛—𐑚𐑦𐑒𐑪𐑟 𐑞𐑨𐑑'𐑕 𐑷𐑤𐑕𐑴 𐑐𐑸𐑑 𐑝 𐑞 \emph{𐑮𐑴𐑤} 𐑝 𐑕𐑳𐑥𐑢𐑳𐑯 𐑐𐑤𐑱𐑦𐑙 𐑩 𐑒𐑩𐑯𐑕𐑻𐑯𐑛 𐑨𐑛𐑳𐑤𐑑—𐑿'𐑛 𐑯𐑧𐑝𐑼 𐑗𐑱𐑯𐑡 𐑘𐑹 𐑨𐑒𐑖𐑩𐑯𐑟, 𐑿 𐑢𐑫𐑛𐑩𐑯𐑑 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑚𐑦𐑣𐑱𐑝 𐑛𐑦𐑓𐑼𐑩𐑯𐑑𐑤𐑦, 𐑚𐑦𐑒𐑪𐑟 𐑝 𐑧𐑯𐑦𐑔𐑦𐑙 𐑲 𐑕𐑧𐑛.”

𐑞 𐑕𐑱𐑤𐑟𐑥𐑩𐑯 𐑢𐑪𐑟 𐑢𐑪𐑗𐑦𐑙 𐑞𐑧𐑥 𐑚𐑴𐑔 𐑢𐑦𐑞 𐑳𐑯𐑩𐑚𐑨𐑖𐑑 𐑓𐑨𐑕𐑦𐑯𐑱𐑖𐑩𐑯.

“𐑲 𐑒𐑨𐑯 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑘𐑹 𐑐𐑶𐑯𐑑 𐑝 𐑝𐑿,” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛 𐑦𐑝𐑧𐑯𐑗𐑵𐑩𐑤𐑦. “𐑦𐑓 𐑲 𐑕𐑳𐑥𐑑𐑲𐑥𐑟 𐑕𐑰𐑥 𐑑𐑵 𐑕𐑑𐑮𐑦𐑒𐑑, 𐑐𐑤𐑰𐑟 𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑞𐑨𐑑 𐑲 𐑣𐑨𐑝 𐑕𐑻𐑝𐑛 𐑨𐑟 ·𐑣𐑧𐑛 𐑝 ·𐑜𐑮𐑦𐑓𐑦𐑯𐑛𐑹 ·𐑣𐑬𐑕 𐑓 𐑢𐑪𐑑 𐑓𐑰𐑤𐑟 𐑤𐑲𐑒 𐑕𐑧𐑝𐑼𐑩𐑤 𐑔𐑬𐑟𐑩𐑯𐑛 𐑘𐑽𐑟.”

·𐑣𐑨𐑮𐑦 𐑯𐑪𐑛𐑩𐑛 𐑯 𐑒𐑩𐑯𐑑𐑦𐑯𐑿𐑛. “𐑕𐑴—𐑕𐑩𐑐𐑴𐑟 𐑲 𐑣𐑨𐑛 𐑩 𐑢𐑱 𐑑 𐑜𐑧𐑑 𐑥𐑹 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑓𐑮𐑪𐑥 𐑥𐑲 𐑝𐑷𐑤𐑑 \emph{𐑢𐑦𐑞𐑬𐑑} 𐑳𐑕 𐑜𐑴𐑦𐑙 𐑚𐑨𐑒 𐑑 ·𐑜𐑮𐑦𐑙𐑜𐑩𐑑𐑕, 𐑚𐑳𐑑 𐑦𐑑 𐑦𐑯𐑝𐑪𐑤𐑝𐑛 𐑥𐑰 𐑝𐑲𐑩𐑤𐑱𐑑𐑦𐑙 𐑞 𐑮𐑴𐑤 𐑝 𐑩𐑯 𐑴𐑚𐑰𐑛𐑾𐑯𐑑 𐑗𐑲𐑤𐑛. 𐑢𐑫𐑛 𐑲 𐑚𐑰 𐑱𐑚𐑩𐑤 𐑑 𐑑𐑮𐑳𐑕𐑑 𐑿 𐑢𐑦𐑞 𐑞𐑨𐑑, 𐑰𐑝𐑩𐑯 𐑞𐑴 𐑿'𐑛 𐑣𐑨𐑓 𐑑 𐑕𐑑𐑧𐑐 𐑬𐑑𐑕𐑲𐑛 𐑘𐑹 𐑴𐑯 𐑮𐑴𐑤 𐑨𐑟 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑑 𐑑𐑱𐑒 𐑩𐑛𐑝𐑭𐑯𐑑𐑦𐑡 𐑝 𐑦𐑑?”

“\emph{𐑢𐑪𐑑?}” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤.

“𐑑 𐑐𐑫𐑑 𐑦𐑑 𐑩𐑯𐑳𐑞𐑼 𐑢𐑱, 𐑦𐑓 𐑲 𐑒𐑫𐑛 𐑥𐑱𐑒 𐑑𐑩𐑛𐑱 𐑣𐑨𐑝 𐑣𐑨𐑐𐑩𐑯𐑛 𐑛𐑦𐑓𐑼𐑩𐑯𐑑𐑤𐑦, 𐑕𐑴 𐑞𐑨𐑑 𐑢𐑰 \emph{𐑛𐑦𐑛𐑩𐑯𐑑} 𐑑𐑱𐑒 𐑑𐑵 𐑤𐑦𐑑𐑩𐑤 𐑥𐑳𐑯𐑦 𐑢𐑦𐑞 𐑳𐑕, 𐑢𐑫𐑛 𐑞𐑨𐑑 𐑚𐑰 𐑷𐑤 𐑮𐑲𐑑 𐑰𐑝𐑩𐑯 𐑞𐑴 𐑦𐑑 𐑢𐑫𐑛 𐑦𐑯𐑝𐑪𐑤𐑝 𐑩 𐑗𐑲𐑤𐑛 𐑚𐑰𐑦𐑙 𐑦𐑯𐑕𐑩𐑤𐑩𐑯𐑑 𐑑 𐑩𐑯 𐑨𐑛𐑳𐑤𐑑 𐑦𐑯 𐑮𐑧𐑑𐑮𐑴𐑕𐑐𐑧𐑒𐑑?”

“𐑲…𐑕𐑩𐑐𐑴𐑟…” 𐑞 𐑢𐑦𐑗 𐑕𐑧𐑛, 𐑤𐑫𐑒𐑦𐑙 𐑒𐑢𐑲𐑑 𐑐𐑳𐑟𐑩𐑤𐑛.

·𐑣𐑨𐑮𐑦 𐑑𐑫𐑒 𐑬𐑑 𐑞 𐑥𐑴𐑒𐑕𐑒𐑦𐑯 𐑐𐑬𐑗, 𐑯 𐑕𐑧𐑛, “·𐑦𐑤𐑧𐑝𐑩𐑯 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑼𐑦𐑡𐑦𐑯𐑩𐑤𐑦 𐑓𐑮𐑪𐑥 𐑥𐑲 𐑓𐑨𐑥𐑤𐑦 𐑝𐑷𐑤𐑑.”

𐑯 𐑞𐑺 𐑢𐑪𐑟 𐑜𐑴𐑤𐑛 𐑦𐑯 ·𐑣𐑨𐑮𐑦'𐑟 𐑣𐑨𐑯𐑛.

𐑓 𐑩 𐑥𐑴𐑥𐑩𐑯𐑑 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑥𐑬𐑔 𐑜𐑱𐑐𐑑 𐑢𐑲𐑛, 𐑞𐑧𐑯 𐑣𐑻 𐑡𐑷 𐑕𐑯𐑨𐑐𐑑 𐑖𐑳𐑑 𐑯 𐑣𐑻 𐑲𐑟 𐑯𐑨𐑮𐑴𐑛 𐑯 𐑞 𐑢𐑦𐑗 𐑚𐑦𐑑 𐑬𐑑, “\emph{𐑢𐑺} 𐑛𐑦𐑛 𐑿 𐑜𐑧𐑑 𐑞𐑨𐑑—”

“𐑓𐑮𐑪𐑥 𐑥𐑲 𐑓𐑨𐑥𐑤𐑦 𐑝𐑷𐑤𐑑, 𐑤𐑲𐑒 𐑲 𐑕𐑧𐑛.”

“\emph{𐑣𐑬?}”

“·𐑥𐑨𐑡𐑦𐑒.”

“𐑞𐑨𐑑'𐑕 𐑣𐑸𐑛𐑤𐑦 𐑩𐑯 𐑭𐑯𐑕𐑼!” 𐑕𐑯𐑨𐑐𐑑 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑯 𐑞𐑧𐑯 𐑕𐑑𐑪𐑐𐑑, 𐑚𐑤𐑦𐑙𐑒𐑦𐑙.

“𐑯𐑴, 𐑦𐑑 𐑦𐑟𐑩𐑯𐑑, 𐑦𐑟 𐑦𐑑? 𐑲 \emph{𐑷𐑑} 𐑑 𐑒𐑤𐑱𐑥 𐑞𐑨𐑑 𐑦𐑑'𐑕 𐑚𐑦𐑒𐑪𐑟 𐑲 𐑦𐑒𐑕𐑐𐑧𐑮𐑦𐑥𐑧𐑯𐑑𐑩𐑤𐑦 𐑛𐑦𐑕𐑒𐑳𐑝𐑼𐑛 𐑞 𐑑𐑮𐑵 𐑕𐑰𐑒𐑮𐑩𐑑𐑕 𐑝 𐑣𐑬 𐑞 𐑐𐑬𐑗 𐑢𐑻𐑒𐑕 𐑯 𐑞𐑨𐑑 𐑦𐑑 𐑒𐑨𐑯 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑮𐑦𐑑𐑮𐑰𐑝 𐑪𐑚𐑡𐑧𐑒𐑑𐑕 𐑓𐑮𐑪𐑥 𐑧𐑯𐑦𐑢𐑺, 𐑯𐑪𐑑 𐑡𐑳𐑕𐑑 𐑦𐑑𐑕 𐑴𐑯 𐑦𐑯𐑕𐑲𐑛, 𐑦𐑓 𐑿 𐑓𐑮𐑱𐑟 𐑞 𐑮𐑦𐑒𐑢𐑧𐑕𐑑 𐑒𐑼𐑧𐑒𐑑𐑤𐑦. 𐑚𐑳𐑑 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑦𐑑'𐑕 𐑓𐑮𐑪𐑥 𐑢𐑧𐑯 𐑲 𐑓𐑧𐑤 𐑦𐑯𐑑𐑵 𐑞𐑨𐑑 𐑐𐑲𐑤 𐑝 𐑜𐑴𐑤𐑛 𐑚𐑦𐑓𐑹 𐑯 𐑲 𐑖𐑳𐑝𐑛 𐑕𐑳𐑥 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑦𐑯𐑑𐑵 𐑥𐑲 𐑐𐑪𐑒𐑩𐑑. 𐑧𐑯𐑦𐑢𐑳𐑯 𐑣𐑵 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛𐑟 𐑐𐑧𐑕𐑦𐑥𐑦𐑟𐑩𐑥 𐑯𐑴𐑟 𐑞𐑨𐑑 𐑥𐑳𐑯𐑦 𐑦𐑟 𐑕𐑳𐑥𐑔𐑦𐑙 𐑿 𐑥𐑲𐑑 𐑯𐑰𐑛 𐑒𐑢𐑦𐑒𐑤𐑦 𐑯 𐑢𐑦𐑞𐑬𐑑 𐑥𐑳𐑗 𐑢𐑹𐑯𐑦𐑙. 𐑕𐑴 𐑯𐑬 𐑸 𐑿 𐑨𐑙𐑜𐑮𐑦 𐑨𐑑 𐑥𐑰 𐑓 𐑛𐑦𐑓𐑲𐑦𐑙 𐑘𐑹 𐑷𐑔𐑪𐑮𐑦𐑑𐑦? 𐑹 𐑜𐑤𐑨𐑛 𐑞𐑨𐑑 𐑢𐑰 𐑕𐑩𐑒𐑕𐑰𐑛𐑩𐑛 𐑦𐑯 𐑬𐑼 𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑 𐑥𐑦𐑖𐑩𐑯?”

𐑞 𐑕𐑱𐑤𐑟𐑥𐑩𐑯'𐑟 𐑲𐑟 𐑢𐑻 𐑢𐑲𐑛 𐑤𐑲𐑒 𐑕𐑷𐑕𐑼𐑟.

𐑯 𐑞 𐑑𐑷𐑤 𐑢𐑦𐑗 𐑕𐑑𐑫𐑛 𐑞𐑺, 𐑕𐑲𐑤𐑩𐑯𐑑.

“𐑛𐑦𐑕𐑦𐑐𐑤𐑦𐑯 𐑨𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 \emph{𐑥𐑳𐑕𐑑} 𐑚𐑰 𐑦𐑯𐑓𐑹𐑕𐑑,” 𐑖𐑰 𐑕𐑧𐑛 𐑭𐑓𐑑𐑼 𐑷𐑤𐑥𐑴𐑕𐑑 𐑩 𐑓𐑫𐑤 𐑥𐑦𐑯𐑦𐑑. “𐑓 𐑞 𐑕𐑱𐑒 𐑝 \emph{𐑷𐑤} 𐑞 𐑕𐑑𐑿𐑛𐑩𐑯𐑑𐑕. 𐑯 𐑞𐑨𐑑 \emph{𐑥𐑳𐑕𐑑} 𐑦𐑯𐑒𐑤𐑵𐑛 𐑒𐑻𐑑𐑩𐑕𐑦 𐑯 𐑴𐑚𐑰𐑛𐑾𐑯𐑕 𐑓𐑮𐑪𐑥 𐑿 𐑑 \emph{𐑷𐑤} 𐑐𐑮𐑩𐑓𐑧𐑕𐑼𐑟.”

“𐑲 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤.”

“𐑜𐑫𐑛. 𐑯𐑬 𐑤𐑧𐑑 𐑳𐑕 𐑚𐑲 𐑞𐑨𐑑 𐑑𐑮𐑳𐑙𐑒 𐑯 𐑜𐑴 𐑣𐑴𐑥.”

·𐑣𐑨𐑮𐑦 𐑓𐑧𐑤𐑑 𐑤𐑲𐑒 𐑔𐑮𐑴𐑦𐑙 𐑳𐑐, 𐑹 𐑗𐑽𐑦𐑙, 𐑹 𐑓𐑱𐑯𐑑𐑦𐑙, 𐑹 \emph{𐑕𐑳𐑥𐑔𐑦𐑙}. 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑞 𐑓𐑻𐑕𐑑 𐑑𐑲𐑥 𐑣𐑦𐑟 𐑒𐑺𐑓𐑩𐑤 𐑮𐑰𐑟𐑩𐑯𐑦𐑙 𐑣𐑨𐑛 𐑧𐑝𐑼 𐑢𐑻𐑒𐑑 𐑪𐑯 \emph{𐑧𐑯𐑦𐑢𐑳𐑯}. 𐑥𐑱𐑚𐑰 𐑚𐑦𐑒𐑪𐑟 𐑦𐑑 𐑢𐑪𐑟 𐑷𐑤𐑕𐑴 𐑞 𐑓𐑻𐑕𐑑 𐑑𐑲𐑥 𐑣𐑰 𐑣𐑨𐑛 𐑕𐑳𐑥𐑔𐑦𐑙 𐑮𐑾𐑤𐑦 𐑕𐑽𐑾𐑕 𐑞𐑨𐑑 𐑩𐑯 𐑨𐑛𐑳𐑤𐑑 𐑯𐑰𐑛𐑩𐑛 𐑓𐑮𐑪𐑥 𐑣𐑦𐑥, 𐑚𐑳𐑑 𐑕𐑑𐑦𐑤—

·𐑥𐑦𐑯𐑻𐑝𐑩 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, +1 𐑐𐑶𐑯𐑑.

·𐑣𐑨𐑮𐑦 𐑚𐑬𐑛, 𐑯 𐑜𐑱𐑝 𐑞 𐑚𐑨𐑜 𐑝 𐑜𐑴𐑤𐑛 𐑯 𐑞 𐑧𐑒𐑕𐑑𐑮𐑩 𐑦𐑤𐑧𐑝𐑩𐑯 ·𐑜𐑨𐑤𐑾𐑯𐑟 𐑦𐑯𐑑𐑵 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑣𐑨𐑯𐑛𐑟. “𐑔𐑨𐑙𐑒 𐑿 𐑝𐑧𐑮𐑦 𐑥𐑳𐑗, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼. 𐑒𐑨𐑯 𐑿 𐑓𐑦𐑯𐑦𐑖 𐑳𐑐 𐑞 𐑐𐑻𐑗𐑩𐑕 𐑓 𐑥𐑰? 𐑲'𐑝 𐑜𐑪𐑑 𐑑 𐑝𐑦𐑟𐑦𐑑 𐑞 𐑤𐑨𐑝𐑩𐑑𐑼𐑦.”

𐑞 𐑕𐑱𐑤𐑟𐑥𐑩𐑯, 𐑳𐑙𐑒𐑗𐑵𐑩𐑕 𐑢𐑳𐑯𐑕 𐑥𐑹, 𐑐𐑶𐑯𐑑𐑩𐑛 𐑑𐑩𐑢𐑹𐑛 𐑩 𐑛𐑹 𐑕𐑧𐑑 𐑦𐑯𐑑𐑵 𐑞 𐑢𐑷𐑤 𐑢𐑦𐑞 𐑩 𐑜𐑴𐑤𐑛-𐑣𐑨𐑯𐑛𐑩𐑤𐑛 𐑯𐑪𐑚. 𐑨𐑟 ·𐑣𐑨𐑮𐑦 𐑕𐑑𐑸𐑑𐑩𐑛 𐑑 𐑢𐑷𐑒 𐑩𐑢𐑱, 𐑣𐑰 𐑣𐑻𐑛 𐑞 𐑕𐑱𐑤𐑟𐑥𐑩𐑯 𐑭𐑕𐑒 𐑦𐑯 𐑣𐑦𐑟 𐑶𐑤𐑦 𐑝𐑶𐑕, “𐑥𐑱 𐑲 𐑦𐑯𐑒𐑢𐑲𐑼 𐑨𐑟 𐑑 𐑣𐑵 𐑞𐑨𐑑 𐑢𐑪𐑟, ·𐑥𐑨𐑛𐑩𐑥 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤? 𐑲 𐑑𐑱𐑒 𐑦𐑑 𐑣𐑰 𐑦𐑟 ·𐑕𐑤𐑲𐑔𐑼𐑦𐑯—𐑔𐑻𐑛-𐑘𐑽, 𐑐𐑼𐑣𐑨𐑐𐑕?—𐑯 𐑓𐑮𐑪𐑥 𐑩 𐑐𐑮𐑪𐑥𐑦𐑯𐑩𐑯𐑑 𐑓𐑨𐑥𐑤𐑦, 𐑚𐑳𐑑 𐑲 𐑛𐑦𐑛 𐑯𐑪𐑑 𐑮𐑧𐑒𐑩𐑜𐑯𐑲𐑟—”

𐑞 𐑕𐑤𐑨𐑥 𐑝 𐑞 𐑤𐑨𐑝𐑩𐑑𐑼𐑦 𐑛𐑹 𐑒𐑳𐑑 𐑪𐑓 𐑣𐑦𐑟 𐑢𐑻𐑛𐑟, 𐑯 𐑭𐑓𐑑𐑼 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑲𐑛𐑧𐑯𐑑𐑦𐑓𐑲𐑛 𐑞 𐑤𐑪𐑒 𐑯 𐑐𐑮𐑧𐑕𐑑 𐑦𐑑 𐑦𐑯𐑑𐑵 𐑐𐑤𐑱𐑕, 𐑣𐑰 𐑜𐑮𐑨𐑚𐑛 𐑞 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 𐑕𐑧𐑤𐑓-𐑒𐑤𐑰𐑯𐑦𐑙 𐑑𐑬𐑩𐑤 𐑯, 𐑢𐑦𐑞 𐑖𐑱𐑒𐑦 𐑣𐑨𐑯𐑛𐑟, 𐑢𐑲𐑐𐑑 𐑥𐑶𐑕𐑗𐑼 𐑪𐑓 𐑣𐑦𐑟 𐑓𐑪𐑮𐑦𐑛. 𐑣𐑨𐑮𐑦'𐑟 𐑦𐑯𐑑𐑲𐑼 𐑚𐑪𐑛𐑦 𐑢𐑪𐑟 𐑖𐑰𐑞𐑛 𐑦𐑯 𐑕𐑢𐑧𐑑 𐑢𐑦𐑗 𐑣𐑨𐑛 𐑕𐑴𐑒𐑑 𐑒𐑤𐑽 𐑔𐑮𐑵 𐑣𐑦𐑟 ·𐑥𐑳𐑜𐑩𐑤 𐑒𐑤𐑴𐑞𐑦𐑙, 𐑞𐑴 𐑨𐑑 𐑤𐑰𐑕𐑑 𐑦𐑑 𐑛𐑦𐑛𐑩𐑯𐑑 𐑖𐑴 𐑔𐑮𐑵 𐑞 𐑮𐑴𐑚𐑟.

\later

𐑞 𐑕𐑳𐑯 𐑢𐑪𐑟 𐑕𐑧𐑑𐑦𐑙 𐑯 𐑦𐑑 𐑢𐑪𐑟 𐑝𐑧𐑮𐑦 𐑤𐑱𐑑 𐑦𐑯𐑛𐑰𐑛, 𐑚𐑲 𐑞 𐑑𐑲𐑥 𐑞𐑱 𐑕𐑑𐑫𐑛 𐑩𐑜𐑱𐑯 𐑦𐑯 𐑞 𐑒𐑹𐑑𐑘𐑸𐑛 𐑝 𐑞 ·𐑤𐑰𐑒𐑦 ·𐑒𐑷𐑤𐑛𐑮𐑩𐑯, 𐑞 𐑕𐑲𐑤𐑩𐑯𐑑 𐑤𐑰𐑓-𐑛𐑳𐑕𐑑𐑩𐑛 𐑦𐑯𐑑𐑼𐑓𐑱𐑕 𐑚𐑦𐑑𐑢𐑰𐑯 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 ·𐑚𐑮𐑦𐑑𐑩𐑯'𐑟 ·𐑛𐑲𐑨𐑜𐑩𐑯 ·𐑨𐑤𐑦 𐑯 𐑞 𐑦𐑯𐑑𐑲𐑼 ·𐑥𐑳𐑜𐑩𐑤 𐑢𐑻𐑤𐑛. (𐑞𐑨𐑑 𐑢𐑪𐑟 𐑢𐑳𐑯 \emph{𐑷𐑓𐑩𐑤𐑦} 𐑛𐑰𐑒𐑳𐑐𐑩𐑤𐑛 𐑦𐑒𐑪𐑯𐑩𐑥𐑦…) ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑑 𐑜𐑴 𐑑 𐑩 𐑓𐑴𐑯 𐑚𐑪𐑒𐑕 𐑯 𐑒𐑷𐑤 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼, 𐑢𐑳𐑯𐑕 𐑣𐑰 𐑢𐑪𐑟 𐑪𐑯 𐑞 𐑳𐑞𐑼 𐑕𐑲𐑛. 𐑣𐑰 𐑛𐑦𐑛𐑩𐑯𐑑 𐑯𐑰𐑛 𐑑 𐑢𐑳𐑮𐑦 𐑩𐑚𐑬𐑑 𐑣𐑦𐑟 𐑤𐑳𐑜𐑦𐑡 𐑚𐑰𐑦𐑙 𐑕𐑑𐑴𐑤𐑩𐑯, 𐑩𐑐𐑨𐑮𐑩𐑯𐑑𐑤𐑦. 𐑣𐑦𐑟 𐑑𐑮𐑳𐑙𐑒 𐑣𐑨𐑛 𐑞 𐑕𐑑𐑱𐑑𐑩𐑕 𐑝 𐑩 𐑥𐑱𐑡𐑼 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 𐑲𐑑𐑩𐑥, 𐑕𐑳𐑥𐑔𐑦𐑙 𐑞𐑨𐑑 𐑥𐑴𐑕𐑑 ·𐑥𐑳𐑜𐑩𐑤𐑟 𐑢𐑫𐑛𐑩𐑯𐑑 𐑯𐑴𐑑𐑦𐑕; 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑐𐑸𐑑 𐑝 𐑢𐑪𐑑 𐑿 𐑒𐑫𐑛 𐑜𐑧𐑑 𐑦𐑯 𐑞 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑢𐑻𐑤𐑛, 𐑦𐑓 𐑿 𐑢𐑻 𐑢𐑦𐑤𐑦𐑙 𐑑 𐑐𐑱 𐑞 𐑐𐑮𐑲𐑕 𐑝 𐑩 𐑕𐑱𐑒𐑪𐑯𐑛-𐑣𐑨𐑯𐑛 𐑒𐑸.

“𐑕𐑴 𐑣𐑽 𐑢𐑰 𐑐𐑸𐑑 𐑢𐑱𐑟, 𐑓 𐑩 𐑑𐑲𐑥,” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛. 𐑖𐑰 𐑖𐑫𐑒 𐑣𐑻 𐑣𐑧𐑛 𐑦𐑯 𐑢𐑳𐑯𐑛𐑼𐑥𐑩𐑯𐑑. “𐑞𐑦𐑕 𐑣𐑨𐑟 𐑚𐑰𐑯 𐑞 𐑕𐑑𐑮𐑱𐑯𐑡𐑩𐑕𐑑 𐑛𐑱 𐑝 𐑥𐑲 𐑤𐑲𐑓 𐑓…𐑥𐑧𐑯𐑦 𐑩 𐑘𐑽. 𐑕𐑦𐑯𐑕 𐑞 𐑛𐑱 𐑲 𐑤𐑻𐑯𐑛 𐑞𐑨𐑑 𐑩 𐑗𐑲𐑤𐑛 𐑣𐑨𐑛 𐑛𐑦𐑓𐑰𐑑𐑩𐑛 𐑿-𐑯𐑴-𐑣𐑵. 𐑲 𐑢𐑳𐑯𐑛𐑼 𐑯𐑬, 𐑤𐑫𐑒𐑦𐑙 𐑚𐑨𐑒, 𐑦𐑓 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑞 𐑤𐑭𐑕𐑑 𐑮𐑰𐑟𐑩𐑯𐑩𐑚𐑩𐑤 𐑛𐑱 𐑝 𐑞 𐑢𐑻𐑤𐑛.”

𐑴, 𐑤𐑲𐑒 \emph{𐑖𐑰} 𐑣𐑨𐑛 𐑧𐑯𐑦𐑔𐑦𐑙 𐑑 𐑒𐑩𐑥𐑐𐑤𐑱𐑯 𐑩𐑚𐑬𐑑. \emph{𐑿 𐑔𐑦𐑙𐑒 𐑘𐑹 𐑛𐑱 𐑢𐑪𐑟 𐑕𐑼𐑾𐑤? 𐑑𐑮𐑲 𐑥𐑲𐑯.}

“𐑲 𐑢𐑪𐑟 𐑝𐑧𐑮𐑦 𐑦𐑥𐑐𐑮𐑧𐑕𐑑 𐑢𐑦𐑞 𐑿 𐑑𐑩𐑛𐑱,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑑 𐑣𐑻. “𐑲 𐑖𐑫𐑛 𐑣𐑨𐑝 𐑮𐑦𐑥𐑧𐑥𐑚𐑼𐑛 𐑑 𐑒𐑪𐑥𐑐𐑤𐑦𐑥𐑧𐑯𐑑 𐑿 𐑬𐑑 𐑤𐑬𐑛, 𐑲 𐑢𐑪𐑟 𐑩𐑢𐑹𐑛𐑦𐑙 𐑿 𐑐𐑶𐑯𐑑𐑕 𐑦𐑯 𐑥𐑲 𐑣𐑧𐑛 𐑯 𐑧𐑝𐑮𐑦𐑔𐑦𐑙.”

“𐑔𐑨𐑙𐑒 𐑿, ·𐑥𐑼~·𐑐𐑪𐑑𐑼,” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. “𐑦𐑓 𐑿 𐑣𐑨𐑛 𐑷𐑤𐑮𐑧𐑛𐑦 𐑚𐑰𐑯 𐑕𐑹𐑑𐑩𐑛 𐑦𐑯𐑑𐑵 𐑩 ·𐑣𐑬𐑕 𐑲 𐑢𐑫𐑛 𐑣𐑨𐑝 𐑛𐑦𐑛𐑳𐑒𐑑𐑩𐑛 𐑕𐑴 𐑥𐑧𐑯𐑦 𐑐𐑶𐑯𐑑𐑕 𐑞𐑨𐑑 𐑘𐑹 𐑜𐑮𐑨𐑯𐑛𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑢𐑫𐑛 𐑕𐑑𐑦𐑤 𐑚𐑰 𐑤𐑵𐑟𐑦𐑙 𐑞 ·𐑣𐑬𐑕 ·𐑒𐑳𐑐.”

“𐑔𐑨𐑙𐑒 \emph{𐑿}, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼.” 𐑦𐑑 𐑢𐑪𐑟 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑑𐑵 𐑻𐑤𐑦 𐑑 𐑒𐑷𐑤 𐑣𐑻 ·𐑥𐑦𐑯𐑦.

𐑞𐑦𐑕 𐑢𐑫𐑥𐑩𐑯 𐑥𐑲𐑑 𐑢𐑧𐑤 𐑚𐑰 𐑞 𐑕𐑱𐑯𐑩𐑕𐑑 𐑨𐑛𐑳𐑤𐑑 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑧𐑝𐑼 𐑥𐑧𐑑, 𐑛𐑦𐑕𐑐𐑲𐑑 𐑣𐑻 𐑤𐑨𐑒 𐑝 𐑕𐑲𐑩𐑯𐑑𐑦𐑓𐑦𐑒 𐑚𐑨𐑒𐑜𐑮𐑬𐑯𐑛. ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑰𐑝𐑩𐑯 𐑒𐑩𐑯𐑕𐑦𐑛𐑼𐑦𐑙 𐑪𐑓𐑼𐑦𐑙 𐑣𐑻 𐑞 𐑯𐑳𐑥𐑚𐑼 𐑑𐑵 𐑐𐑩𐑟𐑦𐑖𐑩𐑯 𐑦𐑯 𐑢𐑪𐑑𐑧𐑝𐑼 𐑜𐑮𐑵𐑐 𐑣𐑰 𐑓𐑹𐑥𐑛 𐑑 𐑓𐑲𐑑 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛, 𐑞𐑴 𐑣𐑰 𐑢𐑪𐑟𐑩𐑯𐑑 𐑕𐑦𐑤𐑦 𐑦𐑯𐑳𐑓 𐑑 𐑕𐑱 𐑞𐑨𐑑 𐑬𐑑 𐑤𐑬𐑛. \emph{𐑯𐑬 𐑢𐑪𐑑 𐑢𐑫𐑛 𐑚𐑰 𐑩 𐑜𐑫𐑛 𐑯𐑱𐑥 𐑓 𐑞𐑨𐑑…? 𐑞 ·𐑛𐑧𐑔 ·𐑰𐑑𐑼 ·𐑰𐑑𐑼𐑟?}

“𐑲'𐑤 𐑕𐑰 𐑿 𐑩𐑜𐑱𐑯 𐑕𐑵𐑯, 𐑢𐑧𐑯 𐑕𐑒𐑵𐑤 𐑕𐑑𐑸𐑑𐑕,” ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛. “𐑯, ·𐑥𐑼~·𐑐𐑪𐑑𐑼, 𐑩𐑚𐑬𐑑 𐑘𐑹 𐑢𐑪𐑯𐑛—”

“𐑲 𐑯𐑴 𐑢𐑪𐑑 𐑿'𐑼 𐑜𐑴𐑦𐑙 𐑑 𐑭𐑕𐑒,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. 𐑣𐑰 𐑑𐑫𐑒 𐑬𐑑 𐑣𐑦𐑟 𐑐𐑮𐑧𐑖𐑩𐑕 𐑢𐑪𐑯𐑛 𐑯, 𐑢𐑦𐑞 𐑩 𐑛𐑰𐑐 𐑑𐑢𐑦𐑯𐑡 𐑝 𐑦𐑯𐑼 𐑐𐑱𐑯, 𐑓𐑤𐑦𐑐𐑑 𐑦𐑑 𐑴𐑝𐑼 𐑦𐑯 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛, 𐑐𐑮𐑦𐑟𐑧𐑯𐑑𐑦𐑙 𐑣𐑻 𐑢𐑦𐑞 𐑞 𐑣𐑨𐑯𐑛𐑩𐑤. “𐑑𐑱𐑒 𐑦𐑑. 𐑲 𐑣𐑨𐑛𐑩𐑯𐑑 𐑐𐑤𐑨𐑯𐑛 𐑑 𐑛𐑵 𐑧𐑯𐑦𐑔𐑦𐑙, 𐑯𐑪𐑑 𐑩 𐑕𐑦𐑙𐑜𐑩𐑤 𐑔𐑦𐑙, 𐑚𐑳𐑑 𐑲 𐑛𐑴𐑯𐑑 𐑢𐑪𐑯𐑑 𐑿 𐑑 𐑣𐑨𐑝 𐑯𐑲𐑑𐑥𐑺𐑟 𐑩𐑚𐑬𐑑 𐑥𐑰 𐑚𐑤𐑴𐑦𐑙 𐑳𐑐 𐑥𐑲 𐑣𐑬𐑕.”

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑖𐑫𐑒 𐑣𐑻 𐑣𐑧𐑛 𐑮𐑨𐑐𐑦𐑛𐑤𐑦. “𐑴 𐑯𐑴, ·𐑥𐑼~·𐑐𐑪𐑑𐑼! 𐑞𐑨𐑑 𐑦𐑟𐑩𐑯𐑑 𐑛𐑳𐑯. 𐑲 𐑴𐑯𐑤𐑦 𐑥𐑧𐑯𐑑 𐑑 𐑢𐑹𐑯 𐑿 𐑯𐑪𐑑 𐑑 \emph{𐑿𐑟} 𐑘𐑹 𐑢𐑪𐑯𐑛 𐑨𐑑 𐑣𐑴𐑥, 𐑕𐑦𐑯𐑕 𐑞 ·𐑥𐑦𐑯𐑦𐑕𐑑𐑮𐑦 𐑒𐑨𐑯 𐑛𐑦𐑑𐑧𐑒𐑑 𐑳𐑯𐑛𐑼𐑱𐑡 𐑥𐑨𐑡𐑦𐑒 𐑯 𐑦𐑑 𐑦𐑟 𐑐𐑮𐑴𐑣𐑦𐑚𐑦𐑑𐑩𐑛 𐑢𐑦𐑞𐑬𐑑 𐑕𐑵𐑐𐑼𐑝𐑦𐑠𐑩𐑯.”

“𐑭,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. “𐑞𐑨𐑑 𐑕𐑬𐑯𐑛𐑟 𐑤𐑲𐑒 𐑩 𐑝𐑧𐑮𐑦 𐑕𐑧𐑯𐑕𐑩𐑚𐑩𐑤 𐑮𐑵𐑤. 𐑲'𐑥 𐑜𐑤𐑨𐑛 𐑑 𐑕𐑰 𐑞 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑢𐑻𐑤𐑛 𐑑𐑱𐑒𐑕 𐑞𐑨𐑑 𐑕𐑹𐑑 𐑝 𐑔𐑦𐑙 𐑕𐑽𐑾𐑕𐑤𐑦.”

·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑐𐑽𐑛 𐑣𐑸𐑛 𐑨𐑑 𐑣𐑦𐑥. “𐑿 𐑮𐑾𐑤𐑦 𐑥𐑰𐑯 𐑞𐑨𐑑.”

“𐑘𐑧𐑕,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. “𐑲 𐑜𐑧𐑑 𐑦𐑑. 𐑥𐑨𐑡𐑦𐑒 𐑦𐑟 𐑛𐑱𐑯𐑡𐑼𐑩𐑕 𐑯 𐑞 𐑮𐑵𐑤𐑟 𐑸 𐑞𐑺 𐑓 𐑜𐑫𐑛 𐑮𐑰𐑟𐑩𐑯𐑟. 𐑕𐑻𐑑𐑩𐑯 𐑳𐑞𐑼 𐑥𐑨𐑑𐑼𐑟 𐑸 𐑷𐑤𐑕𐑴 𐑛𐑱𐑯𐑡𐑼𐑩𐑕. 𐑲 𐑜𐑧𐑑 𐑞𐑨𐑑 𐑑𐑵. 𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑞𐑨𐑑 𐑲 𐑨𐑥 𐑯𐑪𐑑 𐑕𐑑𐑿𐑐𐑦𐑛.”

“𐑲 𐑨𐑥 𐑳𐑯𐑤𐑲𐑒𐑤𐑦 𐑧𐑝𐑼 𐑑 𐑓𐑼𐑜𐑧𐑑 𐑦𐑑. 𐑔𐑨𐑙𐑒 𐑿, ·𐑣𐑨𐑮𐑦, 𐑞𐑨𐑑 𐑛𐑳𐑟 𐑥𐑱𐑒 𐑥𐑰 𐑓𐑰𐑤 𐑚𐑧𐑑𐑼 𐑩𐑚𐑬𐑑 𐑦𐑯𐑑𐑮𐑳𐑕𐑑𐑦𐑙 𐑿 𐑢𐑦𐑞 𐑕𐑻𐑑𐑩𐑯 𐑔𐑦𐑙𐑟. 𐑜𐑫𐑛𐑚𐑲 𐑓 𐑯𐑬.”

·𐑣𐑨𐑮𐑦 𐑑𐑻𐑯𐑛 𐑑 𐑜𐑴, 𐑦𐑯𐑑𐑵 𐑞 ·𐑤𐑰𐑒𐑦 ·𐑒𐑷𐑤𐑛𐑮𐑩𐑯 𐑯 𐑬𐑑 𐑑𐑩𐑢𐑹𐑛𐑟 𐑞 ·𐑥𐑳𐑜𐑩𐑤 𐑢𐑻𐑤𐑛.

𐑨𐑟 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛 𐑑𐑳𐑗𐑑 𐑞 𐑚𐑨𐑒 𐑛𐑹'𐑟 𐑣𐑨𐑯𐑛𐑩𐑤, 𐑣𐑰 𐑣𐑻𐑛 𐑩 𐑤𐑭𐑕𐑑 𐑢𐑦𐑕𐑐𐑼 𐑓𐑮𐑪𐑥 𐑚𐑦𐑣𐑲𐑯𐑛 𐑣𐑦𐑥.

“·𐑣𐑼𐑥𐑲𐑩𐑯𐑦 ·𐑜𐑮𐑱𐑯𐑡𐑼.”

“𐑢𐑪𐑑?” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛 𐑕𐑑𐑦𐑤 𐑪𐑯 𐑞 𐑛𐑹.

“𐑤𐑫𐑒 𐑓 𐑩 𐑓𐑻𐑕𐑑-𐑘𐑽 𐑜𐑻𐑤 𐑯𐑱𐑥𐑛 ·𐑣𐑼𐑥𐑲𐑩𐑯𐑦 ·𐑜𐑮𐑱𐑯𐑡𐑼 𐑪𐑯 𐑞 𐑑𐑮𐑱𐑯 𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕.”

“𐑣𐑵 𐑦𐑟 𐑖𐑰?”

𐑞𐑺 𐑢𐑪𐑟 𐑯𐑴 𐑭𐑯𐑕𐑼, 𐑯 𐑢𐑧𐑯 ·𐑣𐑨𐑮𐑦 𐑑𐑻𐑯𐑛 𐑼𐑬𐑯𐑛, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑢𐑪𐑟 𐑜𐑪𐑯.

\latersection{Aftermath}

𐑣𐑧𐑛𐑥𐑭𐑕𐑑𐑼 ·𐑭𐑤𐑚𐑳𐑕 ·𐑛𐑳𐑥𐑚𐑩𐑤𐑛𐑹 𐑤𐑰𐑯𐑛 𐑓𐑹𐑢𐑼𐑛 𐑴𐑝𐑼 𐑣𐑦𐑟 𐑛𐑧𐑕𐑒. 𐑣𐑦𐑟 𐑑𐑢𐑦𐑙𐑒𐑩𐑤𐑦𐑙 𐑲𐑟 𐑐𐑽𐑛 𐑬𐑑 𐑨𐑑 ·𐑥𐑦𐑯𐑻𐑝𐑩. “𐑕𐑴, 𐑥𐑲 𐑛𐑽, 𐑣𐑬 𐑛𐑦𐑛 𐑿 𐑓𐑲𐑯𐑛 ·𐑣𐑨𐑮𐑦?”

·𐑥𐑦𐑯𐑻𐑝𐑩 𐑴𐑐𐑩𐑯𐑛 𐑣𐑻 𐑥𐑬𐑔. 𐑞𐑧𐑯 𐑖𐑰 𐑒𐑤𐑴𐑟𐑛 𐑣𐑻 𐑥𐑬𐑔. 𐑞𐑧𐑯 𐑖𐑰 𐑴𐑐𐑩𐑯𐑛 𐑣𐑻 𐑥𐑬𐑔 𐑩𐑜𐑱𐑯. 𐑯𐑴 𐑢𐑻𐑛𐑟 𐑒𐑱𐑥 𐑬𐑑.

“𐑲 𐑕𐑰,” ·𐑭𐑤𐑚𐑳𐑕 𐑕𐑧𐑛 𐑜𐑮𐑱𐑝𐑤𐑦. “𐑔𐑨𐑙𐑒 𐑿 𐑓 𐑘𐑹 𐑮𐑦𐑐𐑹𐑑, ·𐑥𐑦𐑯𐑻𐑝𐑩. 𐑿 𐑥𐑱 𐑜𐑴.”

%  LocalWords:  ome zahav ahava Aaaaaaarrrgh QX31 ahemmed Sheesh
%  LocalWords:  Aw 
