\chapter{𐑩 𐑛𐑱 𐑝 𐑝𐑧𐑮𐑦 𐑤𐑴 𐑐𐑮𐑪𐑚𐑩𐑚𐑦𐑤𐑦𐑑𐑦}

\begin{chapterOpeningQuote}
\noindent
𐑚𐑦𐑯𐑰𐑔 𐑞 𐑥𐑵𐑯𐑤𐑲𐑑 𐑜𐑤𐑦𐑯𐑑𐑕 𐑩 𐑑𐑲𐑯𐑦 𐑓𐑮𐑨𐑜𐑥𐑧𐑯𐑑 𐑝 𐑕𐑦𐑤𐑝𐑼, 𐑩 𐑓𐑮𐑨𐑒𐑖𐑩𐑯 𐑝 𐑩 𐑤𐑲𐑯…

\vspace*{2ex}
(𐑚𐑤𐑨𐑒 𐑮𐑴𐑚𐑟, 𐑓𐑷𐑤𐑦𐑙)

\vspace*{2ex}
…𐑚𐑤𐑳𐑛 𐑕𐑐𐑦𐑤𐑟 𐑬𐑑 𐑦𐑯 𐑤𐑰𐑑𐑼𐑟, 𐑯 𐑕𐑳𐑥𐑢𐑳𐑯 𐑕𐑒𐑮𐑰𐑥𐑟 𐑩 𐑢𐑻𐑛.
\end{chapterOpeningQuote}

\lettrine{𐑧}{𐑝𐑮𐑦} 𐑦𐑯𐑗 𐑝 𐑢𐑷𐑤 𐑕𐑐𐑱𐑕 𐑦𐑟 𐑒𐑳𐑝𐑼𐑛 𐑚𐑲 𐑩 𐑚𐑫𐑒𐑒𐑱𐑕. 𐑰𐑗 𐑚𐑫𐑒𐑒𐑱𐑕 𐑣𐑨𐑟 𐑕𐑦𐑒𐑕 𐑖𐑧𐑤𐑝𐑟, 𐑜𐑴𐑦𐑙 𐑷𐑤𐑥𐑴𐑕𐑑 𐑑 𐑞 𐑕𐑰𐑤𐑦𐑙. 𐑕𐑳𐑥 𐑚𐑫𐑒𐑖𐑧𐑤𐑝𐑟 𐑸 𐑕𐑑𐑨𐑒𐑑 𐑑 𐑞 𐑚𐑮𐑦𐑥 𐑢𐑦𐑞 𐑣𐑸𐑛𐑚𐑨𐑒 𐑚𐑫𐑒𐑕: 𐑕𐑲𐑩𐑯𐑕, 𐑥𐑨𐑔𐑕, 𐑣𐑦𐑕𐑑𐑼𐑦, 𐑯 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑧𐑤𐑕. 𐑳𐑞𐑼 𐑖𐑧𐑤𐑝𐑟 𐑣𐑨𐑝 𐑑𐑵 𐑤𐑱𐑼𐑟 𐑝 𐑐𐑱𐑐𐑼𐑚𐑨𐑒 𐑕𐑲𐑩𐑯𐑕 𐑓𐑦𐑒𐑖𐑩𐑯, 𐑢𐑦𐑞 𐑞 𐑚𐑨𐑒 𐑤𐑱𐑼 𐑝 𐑚𐑫𐑒𐑕 𐑐𐑮𐑪𐑐𐑑 𐑳𐑐 𐑪𐑯 𐑴𐑤𐑛 𐑑𐑦𐑖𐑵 𐑚𐑪𐑒𐑕𐑩𐑟\authorsnotefootnotemark{} 𐑹 𐑤𐑧𐑙𐑔𐑕 𐑝 𐑢𐑫𐑛, 𐑕𐑴 𐑞𐑨𐑑 𐑿 𐑒𐑨𐑯 𐑕𐑰 𐑞 𐑚𐑨𐑒 𐑤𐑱𐑼 𐑝 𐑚𐑫𐑒𐑕 𐑩𐑚𐑳𐑝 𐑞 𐑚𐑫𐑒𐑕 𐑦𐑯 𐑓𐑮𐑳𐑯𐑑. 𐑯 𐑦𐑑 𐑕𐑑𐑦𐑤 𐑦𐑟𐑩𐑯𐑑 𐑦𐑯𐑳𐑓. 𐑚𐑫𐑒𐑕 𐑸 𐑴𐑝𐑼𐑓𐑤𐑴𐑦𐑙 𐑪𐑯𐑑𐑵 𐑞 𐑑𐑱𐑚𐑩𐑤𐑟 𐑯 𐑞 𐑕𐑴𐑓𐑩𐑟 𐑯 𐑥𐑱𐑒𐑦𐑙 𐑤𐑦𐑑𐑩𐑤 𐑣𐑰𐑐𐑕 𐑳𐑯𐑛𐑼 𐑞 𐑢𐑦𐑯𐑛𐑴𐑟.
\authorsnotetext{𐑲 𐑛𐑵 𐑞𐑦𐑕 𐑦𐑯 𐑥𐑲 𐑴𐑯 𐑣𐑴𐑥.}

𐑞𐑦𐑕 𐑦𐑟 𐑞 𐑤𐑦𐑝𐑦𐑙-𐑮𐑵𐑥 𐑝 𐑞 𐑣𐑬𐑕 𐑪𐑒𐑿𐑐𐑲𐑛 𐑚𐑲 𐑞 𐑧𐑥𐑦𐑯𐑩𐑯𐑑 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑲𐑒𐑩𐑤 ·𐑝𐑧𐑮𐑟-·𐑧𐑝𐑩𐑯𐑟, 𐑯 𐑣𐑦𐑟 𐑢𐑲𐑓, ·𐑥𐑕𐑟~·𐑐𐑩𐑑𐑿𐑯𐑾 ·𐑧𐑝𐑩𐑯𐑟-·𐑝𐑧𐑮𐑟, 𐑯 𐑞𐑺 𐑩𐑛𐑪𐑐𐑑𐑩𐑛 𐑕𐑳𐑯, ·𐑣𐑨𐑮𐑦 ·𐑡𐑱𐑥𐑟 ·𐑐𐑪𐑑𐑼-·𐑧𐑝𐑩𐑯𐑟-·𐑝𐑧𐑮𐑟.

𐑞𐑺 𐑦𐑟 𐑩 𐑤𐑧𐑑𐑼 𐑤𐑲𐑦𐑙 𐑪𐑯 𐑞 𐑤𐑦𐑝𐑦𐑙-𐑮𐑵𐑥 𐑑𐑱𐑚𐑩𐑤, 𐑯 𐑩𐑯 𐑳𐑯𐑕𐑑𐑨𐑥𐑐𐑑 𐑧𐑯𐑝𐑩𐑤𐑴𐑐 𐑝 𐑘𐑧𐑤𐑴𐑦𐑖 𐑐𐑸𐑗𐑥𐑩𐑯𐑑, 𐑩𐑛𐑮𐑧𐑕𐑑 𐑑 \emph{·𐑥𐑼~·𐑣.~𐑐𐑪𐑑𐑼} 𐑦𐑯 𐑧𐑥𐑼𐑩𐑤𐑛-𐑜𐑮𐑰𐑯 𐑦𐑙𐑒.

𐑞 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑯 𐑣𐑦𐑟 𐑢𐑲𐑓 𐑸 𐑕𐑐𐑰𐑒𐑦𐑙 𐑖𐑸𐑐𐑤𐑦 𐑨𐑑 𐑰𐑗 𐑳𐑞𐑼, 𐑚𐑳𐑑 𐑞𐑱 𐑸 𐑯𐑪𐑑 𐑖𐑬𐑑𐑦𐑙. 𐑞 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑒𐑩𐑯𐑕𐑦𐑛𐑼𐑟 𐑖𐑬𐑑𐑦𐑙 𐑑 𐑚𐑰 𐑳𐑯𐑕𐑦𐑝𐑦𐑤𐑲𐑟𐑛.

“𐑿'𐑼 𐑡𐑴𐑒𐑦𐑙,” ·𐑥𐑲𐑒𐑩𐑤 𐑕𐑧𐑛 𐑑 ·𐑐𐑩𐑑𐑿𐑯𐑾. 𐑣𐑦𐑟 𐑑𐑴𐑯 𐑦𐑯𐑛𐑦𐑒𐑱𐑑𐑩𐑛 𐑞𐑨𐑑 𐑣𐑰 𐑢𐑪𐑟 𐑝𐑧𐑮𐑦 𐑥𐑳𐑗 𐑩𐑓𐑮𐑱𐑛 𐑞𐑨𐑑 𐑖𐑰 𐑢𐑪𐑟 𐑕𐑽𐑾𐑕.

“𐑥𐑲 𐑕𐑦𐑕𐑑𐑼 𐑢𐑪𐑟 𐑩 𐑢𐑦𐑗,” ·𐑐𐑩𐑑𐑿𐑯𐑾 𐑮𐑦𐑐𐑰𐑑𐑩𐑛. 𐑖𐑰 𐑤𐑫𐑒𐑑 𐑓𐑮𐑲𐑑𐑩𐑯𐑛, 𐑚𐑳𐑑 𐑕𐑑𐑫𐑛 𐑣𐑻 𐑜𐑮𐑬𐑯𐑛. “𐑣𐑻 𐑣𐑳𐑟𐑚𐑩𐑯𐑛 𐑢𐑪𐑟 𐑩 𐑢𐑦𐑟𐑼𐑛.”

“𐑞𐑦𐑕 𐑦𐑟 𐑩𐑚𐑕𐑻𐑛!” ·𐑥𐑲𐑒𐑩𐑤 𐑕𐑧𐑛 𐑖𐑸𐑐𐑤𐑦. “𐑞𐑱 𐑢𐑻 𐑨𐑑 𐑬𐑼 𐑢𐑧𐑛𐑦𐑙—𐑞𐑱 𐑝𐑦𐑟𐑦𐑑𐑩𐑛 𐑓 ·𐑒𐑮𐑦𐑕𐑥𐑩𐑕—”

“𐑲 𐑑𐑴𐑤𐑛 𐑞𐑧𐑥 𐑿 𐑢𐑻𐑯𐑑 𐑑 𐑯𐑴,” ·𐑐𐑩𐑑𐑿𐑯𐑾 𐑢𐑦𐑕𐑐𐑼𐑛. “𐑚𐑳𐑑 𐑦𐑑'𐑕 𐑑𐑮𐑵. 𐑲'𐑝 𐑕𐑰𐑯 𐑔𐑦𐑙𐑟—”

𐑞 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑮𐑴𐑤𐑛 𐑣𐑦𐑟 𐑲𐑟. “𐑛𐑽, 𐑲 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑞𐑨𐑑 𐑿'𐑼 𐑯𐑪𐑑 𐑓𐑩𐑥𐑦𐑤𐑽 𐑢𐑦𐑞 𐑞 𐑕𐑒𐑧𐑐𐑑𐑦𐑒𐑩𐑤 𐑤𐑦𐑑𐑼𐑩𐑗𐑼. 𐑿 𐑥𐑱 𐑯𐑪𐑑 𐑮𐑾𐑤𐑲𐑟 𐑣𐑬 𐑰𐑟𐑦 𐑦𐑑 𐑦𐑟 𐑓 𐑩 𐑑𐑮𐑱𐑯𐑛 𐑥𐑩𐑡𐑦𐑖𐑩𐑯 𐑑 𐑓𐑱𐑒 𐑞 𐑕𐑰𐑥𐑦𐑙𐑤𐑦 𐑦𐑥𐑐𐑪𐑕𐑩𐑚𐑩𐑤. 𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑣𐑬 𐑲 𐑑𐑷𐑑 ·𐑣𐑨𐑮𐑦 𐑑 𐑚𐑧𐑯𐑛 𐑕𐑐𐑵𐑯𐑟? 𐑦𐑓 𐑦𐑑 𐑕𐑰𐑥𐑛 𐑤𐑲𐑒 𐑞𐑱 𐑒𐑫𐑛 𐑷𐑤𐑢𐑱𐑟 𐑜𐑧𐑕 𐑢𐑪𐑑 𐑿 𐑢𐑻 𐑔𐑦𐑙𐑒𐑦𐑙, 𐑞𐑨𐑑'𐑕 𐑒𐑷𐑤𐑛 𐑒𐑴𐑤𐑛 𐑮𐑰𐑛𐑦𐑙—”

“𐑦𐑑 𐑢𐑪𐑟𐑩𐑯𐑑 𐑚𐑧𐑯𐑛𐑦𐑙 𐑕𐑐𐑵𐑯𐑟—”

“𐑢𐑪𐑑 𐑢𐑪𐑟 𐑦𐑑, 𐑞𐑧𐑯?”

·𐑐𐑩𐑑𐑿𐑯𐑾 𐑚𐑦𐑑 𐑣𐑻 𐑤𐑦𐑐. “𐑲 𐑒𐑭𐑯𐑑 𐑡𐑳𐑕𐑑 𐑑𐑧𐑤 𐑿. 𐑿'𐑤 𐑔𐑦𐑙𐑒 𐑲'𐑥—” 𐑖𐑰 𐑕𐑢𐑪𐑤𐑴𐑛. “𐑤𐑦𐑕𐑩𐑯. ·𐑥𐑲𐑒𐑩𐑤. 𐑲 𐑢𐑪𐑟𐑩𐑯𐑑—𐑷𐑤𐑢𐑱𐑟 𐑤𐑲𐑒 𐑞𐑦𐑕—” 𐑖𐑰 𐑡𐑧𐑕𐑗𐑼𐑛 𐑨𐑑 𐑣𐑻𐑕𐑧𐑤𐑓, 𐑨𐑟 𐑞𐑴 𐑑 𐑦𐑯𐑛𐑦𐑒𐑱𐑑 𐑣𐑻 𐑤𐑲𐑞 𐑓𐑹𐑥. “𐑤𐑦𐑤𐑦 𐑛𐑦𐑛 𐑞𐑦𐑕. 𐑚𐑦𐑒𐑪𐑟 𐑲—𐑚𐑦𐑒𐑪𐑟 𐑲 \emph{𐑚𐑧𐑜𐑛} 𐑣𐑻. 𐑓 𐑘𐑽𐑟, 𐑲 𐑚𐑧𐑜𐑛 𐑣𐑻. 𐑤𐑦𐑤𐑦 𐑣𐑨𐑛 \emph{𐑷𐑤𐑢𐑱𐑟} 𐑚𐑰𐑯 𐑐𐑮𐑦𐑑𐑽 𐑞𐑨𐑯 𐑥𐑰, 𐑯 𐑲'𐑛…𐑚𐑰𐑯 𐑥𐑰𐑯 𐑑 𐑣𐑻, 𐑚𐑦𐑒𐑪𐑟 𐑝 𐑞𐑨𐑑, 𐑯 𐑞𐑧𐑯 𐑖𐑰 𐑜𐑪𐑑 \emph{𐑥𐑨𐑡𐑦𐑒}, 𐑒𐑨𐑯 𐑿 𐑦𐑥𐑨𐑡𐑦𐑯 𐑣𐑬 𐑲 𐑓𐑧𐑤𐑑? 𐑯 𐑲 \emph{𐑚𐑧𐑜𐑛} 𐑣𐑻 𐑑 𐑿𐑟 𐑕𐑳𐑥 𐑝 𐑞𐑨𐑑 𐑥𐑨𐑡𐑦𐑒 𐑪𐑯 𐑥𐑰 𐑕𐑴 𐑞𐑨𐑑 𐑲 𐑒𐑫𐑛 𐑚𐑰 𐑐𐑮𐑦𐑑𐑦 𐑑𐑵, 𐑰𐑝𐑩𐑯 𐑦𐑓 𐑲 𐑒𐑫𐑛𐑩𐑯𐑑 𐑣𐑨𐑝 𐑣𐑻 𐑥𐑨𐑡𐑦𐑒, 𐑨𐑑 𐑤𐑰𐑕𐑑 𐑲 𐑒𐑫𐑛 𐑚𐑰 𐑐𐑮𐑦𐑑𐑦.”

𐑑𐑽𐑟 𐑢𐑻 𐑜𐑨𐑞𐑼𐑦𐑙 𐑦𐑯 ·𐑐𐑩𐑑𐑿𐑯𐑾'𐑟 𐑲𐑟.

“𐑯 ·𐑤𐑦𐑤𐑦 𐑢𐑫𐑛 𐑑𐑧𐑤 𐑥𐑰 𐑯𐑴, 𐑯 𐑥𐑱𐑒 𐑳𐑐 𐑞 𐑥𐑴𐑕𐑑 𐑮𐑦𐑛𐑦𐑒𐑿𐑤𐑩𐑕 𐑦𐑒𐑕𐑒𐑿𐑕𐑩𐑟, 𐑤𐑲𐑒 𐑞 𐑢𐑻𐑤𐑛 𐑢𐑫𐑛 𐑧𐑯𐑛 𐑦𐑓 𐑖𐑰 𐑢𐑻 𐑯𐑲𐑕 𐑑 𐑣𐑻 𐑕𐑦𐑕𐑑𐑼, 𐑹 𐑩 𐑕𐑧𐑯𐑑𐑹 𐑑𐑴𐑤𐑛 𐑣𐑻 𐑯𐑪𐑑 𐑑—𐑞 𐑥𐑴𐑕𐑑 𐑮𐑦𐑛𐑦𐑒𐑿𐑤𐑩𐑕 𐑔𐑦𐑙𐑟, 𐑯 𐑲 𐑣𐑱𐑑𐑩𐑛 𐑣𐑻 𐑓 𐑦𐑑. 𐑯 𐑢𐑧𐑯 𐑲 𐑣𐑨𐑛 𐑡𐑳𐑕𐑑 𐑜𐑮𐑨𐑡𐑵𐑱𐑑𐑩𐑛 𐑓𐑮𐑪𐑥 𐑿𐑯𐑦𐑝𐑻𐑕𐑦𐑑𐑦, 𐑲 𐑢𐑪𐑟 𐑜𐑴𐑦𐑙 𐑬𐑑 𐑢𐑦𐑞 𐑞𐑦𐑕 𐑚𐑶, ·𐑝𐑻𐑯𐑩𐑯 ·𐑛𐑻𐑟𐑤𐑦, 𐑣𐑰 𐑢𐑪𐑟 𐑓𐑨𐑑 𐑯 𐑣𐑰 𐑢𐑪𐑟 𐑞 𐑴𐑯𐑤𐑦 𐑚𐑶 𐑣𐑵 𐑢𐑫𐑛 𐑑𐑷𐑒 𐑑 𐑥𐑰. 𐑯 𐑣𐑰 𐑕𐑧𐑛 𐑣𐑰 𐑢𐑪𐑯𐑑𐑩𐑛 𐑗𐑦𐑤𐑛𐑮𐑩𐑯, 𐑯 𐑞𐑨𐑑 𐑣𐑦𐑟 𐑓𐑻𐑕𐑑 𐑕𐑳𐑯 𐑢𐑫𐑛 𐑚𐑰 𐑯𐑱𐑥𐑛 ·𐑛𐑳𐑛𐑤𐑦. 𐑯 𐑲 𐑔𐑷𐑑 𐑑 𐑥𐑲𐑕𐑧𐑤𐑓, \emph{𐑢𐑪𐑑 𐑒𐑲𐑯𐑛 𐑝 𐑐𐑺𐑩𐑯𐑑 𐑯𐑱𐑥𐑟 𐑞𐑺 𐑗𐑲𐑤𐑛 ·𐑛𐑳𐑛𐑤𐑦 ·𐑛𐑻𐑟𐑤𐑦?} 𐑦𐑑 𐑢𐑪𐑟 𐑤𐑲𐑒 𐑲 𐑕𐑷 𐑥𐑲 𐑣𐑴𐑤 𐑓𐑿𐑗𐑼 𐑤𐑲𐑓 𐑕𐑑𐑮𐑧𐑗𐑦𐑙 𐑬𐑑 𐑦𐑯 𐑓𐑮𐑳𐑯𐑑 𐑝 𐑥𐑰, 𐑯 𐑲 𐑒𐑫𐑛𐑩𐑯𐑑 𐑕𐑑𐑨𐑯𐑛 𐑦𐑑. 𐑯 𐑲 𐑮𐑴𐑑 𐑑 𐑥𐑲 𐑕𐑦𐑕𐑑𐑼 𐑯 𐑑𐑴𐑤𐑛 𐑣𐑻 𐑞𐑨𐑑 𐑦𐑓 𐑖𐑰 𐑛𐑦𐑛𐑩𐑯𐑑 𐑣𐑧𐑤𐑐 𐑥𐑰 𐑲'𐑛 𐑮𐑭𐑞𐑼 𐑡𐑳𐑕𐑑—”

·𐑐𐑩𐑑𐑿𐑯𐑾 𐑕𐑑𐑪𐑐𐑑.

“𐑧𐑯𐑦𐑢𐑱,” ·𐑐𐑩𐑑𐑿𐑯𐑾 𐑕𐑧𐑛, 𐑣𐑻 𐑝𐑶𐑕 𐑕𐑥𐑷𐑤, “𐑖𐑰 𐑜𐑱𐑝 𐑦𐑯. 𐑖𐑰 𐑑𐑴𐑤𐑛 𐑥𐑰 𐑦𐑑 𐑢𐑪𐑟 𐑛𐑱𐑯𐑡𐑼𐑩𐑕, 𐑯 𐑲 𐑕𐑧𐑛 𐑲 𐑛𐑦𐑛𐑩𐑯𐑑 𐑒𐑺 𐑧𐑯𐑦 𐑥𐑹, 𐑯 𐑲 𐑛𐑮𐑨𐑙𐑒 𐑞𐑦𐑕 𐑐𐑴𐑖𐑩𐑯 𐑯 𐑲 𐑢𐑪𐑟 𐑕𐑦𐑒 𐑓 𐑢𐑰𐑒𐑕, 𐑚𐑳𐑑 𐑢𐑧𐑯 𐑲 𐑜𐑪𐑑 𐑚𐑧𐑑𐑼 𐑥𐑲 𐑕𐑒𐑦𐑯 𐑒𐑤𐑽𐑛 𐑳𐑐 𐑯 𐑲 𐑓𐑲𐑯𐑩𐑤𐑦 𐑓𐑦𐑤𐑛 𐑬𐑑 𐑯…𐑲 𐑢𐑪𐑟 𐑚𐑿𐑑𐑦𐑓𐑩𐑤, 𐑐𐑰𐑐𐑩𐑤 𐑢𐑻 \emph{𐑯𐑲𐑕} 𐑑 𐑥𐑰,” 𐑣𐑻 𐑝𐑶𐑕 𐑚𐑮𐑴𐑒, “𐑯 𐑭𐑓𐑑𐑼 𐑞𐑨𐑑 𐑲 𐑒𐑫𐑛𐑩𐑯𐑑 𐑣𐑱𐑑 𐑥𐑲 𐑕𐑦𐑕𐑑𐑼 𐑧𐑯𐑦 𐑥𐑹, 𐑦𐑕𐑐𐑧𐑖𐑩𐑤𐑦 𐑢𐑧𐑯 𐑲 𐑤𐑻𐑯𐑛 𐑢𐑪𐑑 𐑣𐑻 𐑥𐑨𐑡𐑦𐑒 𐑚𐑮𐑷𐑑 𐑣𐑻 𐑦𐑯 𐑞 𐑧𐑯𐑛—”

“𐑛𐑸𐑤𐑦𐑙,” ·𐑥𐑲𐑒𐑩𐑤 𐑕𐑧𐑛 𐑡𐑧𐑯𐑑𐑤𐑦, “𐑿 𐑜𐑪𐑑 𐑕𐑦𐑒, 𐑿 𐑜𐑱𐑯𐑛 𐑕𐑳𐑥 𐑢𐑱𐑑 𐑢𐑲𐑤 𐑮𐑧𐑕𐑑𐑦𐑙 𐑦𐑯 𐑚𐑧𐑛, 𐑯 𐑘𐑹 𐑕𐑒𐑦𐑯 𐑒𐑤𐑽𐑛 𐑳𐑐 𐑪𐑯 𐑦𐑑𐑕 𐑴𐑯. 𐑹 𐑚𐑰𐑦𐑙 𐑕𐑦𐑒 𐑥𐑱𐑛 𐑿 𐑗𐑱𐑯𐑡 𐑘𐑹 𐑛𐑲𐑩𐑑—”

“𐑖𐑰 𐑢𐑪𐑟 𐑩 𐑢𐑦𐑗,” ·𐑐𐑩𐑑𐑿𐑯𐑾 𐑮𐑦𐑐𐑰𐑑𐑩𐑛. “𐑲 𐑕𐑷 𐑦𐑑.”

“·𐑐𐑩𐑑𐑿𐑯𐑾,” ·𐑥𐑲𐑒𐑩𐑤 𐑕𐑧𐑛. 𐑞 𐑩𐑯𐑶𐑩𐑯𐑕 𐑢𐑪𐑟 𐑒𐑮𐑰𐑐𐑦𐑙 𐑦𐑯𐑑𐑵 𐑣𐑦𐑟 𐑝𐑶𐑕. “𐑿 \emph{𐑯𐑴} 𐑞𐑨𐑑 𐑒𐑭𐑯𐑑 𐑚𐑰 𐑑𐑮𐑵. 𐑛𐑵 𐑲 𐑮𐑾𐑤𐑦 𐑣𐑨𐑓 𐑑 𐑦𐑒𐑕𐑐𐑤𐑱𐑯 𐑢𐑲?”

·𐑐𐑩𐑑𐑿𐑯𐑾 𐑮𐑳𐑙 𐑣𐑻 𐑣𐑨𐑯𐑛𐑟. 𐑖𐑰 𐑕𐑰𐑥𐑛 𐑑 𐑚𐑰 𐑪𐑯 𐑞 𐑝𐑻𐑡 𐑝 𐑑𐑽𐑟. “𐑥𐑲 𐑤𐑳𐑝, 𐑲 𐑯𐑴 𐑲 𐑒𐑭𐑯𐑑 𐑢𐑦𐑯 𐑸𐑜𐑿𐑥𐑩𐑯𐑑𐑕 𐑢𐑦𐑞 𐑿, 𐑚𐑳𐑑 𐑐𐑤𐑰𐑟, 𐑿 𐑣𐑨𐑓 𐑑 𐑑𐑮𐑳𐑕𐑑 𐑥𐑰 𐑪𐑯 𐑞𐑦𐑕—”

“\emph{𐑛𐑨𐑛! 𐑥𐑳𐑥!}”

𐑞 𐑑𐑵 𐑝 𐑞𐑧𐑥 𐑕𐑑𐑪𐑐𐑑 𐑯 𐑤𐑫𐑒𐑑 𐑨𐑑 ·𐑣𐑨𐑮𐑦 𐑨𐑟 𐑞𐑴 𐑞𐑱'𐑛 𐑓𐑼𐑜𐑪𐑑𐑩𐑯 𐑞𐑺 𐑢𐑪𐑟 𐑩 𐑔𐑻𐑛 𐑐𐑻𐑕𐑩𐑯 𐑦𐑯 𐑞 𐑮𐑵𐑥.

𐑣𐑨𐑮𐑦 𐑑𐑫𐑒 𐑩 𐑛𐑰𐑐 𐑚𐑮𐑧𐑔. “𐑥𐑳𐑥, \emph{𐑘𐑹} 𐑐𐑺𐑩𐑯𐑑𐑕 𐑛𐑦𐑛𐑩𐑯𐑑 𐑣𐑨𐑝 𐑥𐑨𐑡𐑦𐑒, 𐑛𐑦𐑛 𐑞𐑱?”

“𐑯𐑴,” ·𐑐𐑩𐑑𐑿𐑯𐑾 𐑕𐑧𐑛, 𐑤𐑫𐑒𐑦𐑙 𐑐𐑳𐑟𐑩𐑤𐑛.

“𐑞𐑧𐑯 𐑯𐑴-𐑢𐑳𐑯 𐑦𐑯 𐑘𐑹 𐑓𐑨𐑥𐑤𐑦 𐑯𐑿 𐑩𐑚𐑬𐑑 𐑥𐑨𐑡𐑦𐑒 𐑢𐑧𐑯 ·𐑤𐑦𐑤𐑦 𐑜𐑪𐑑 𐑣𐑻 𐑤𐑧𐑑𐑼. 𐑣𐑬 𐑛𐑦𐑛 \emph{𐑞𐑱} 𐑜𐑧𐑑 𐑒𐑩𐑯𐑝𐑦𐑯𐑕𐑑?”

“𐑭…” ·𐑐𐑩𐑑𐑿𐑯𐑾 𐑕𐑧𐑛. “𐑞𐑱 𐑛𐑦𐑛𐑩𐑯𐑑 𐑡𐑳𐑕𐑑 𐑕𐑧𐑯𐑛 𐑩 𐑤𐑧𐑑𐑼. 𐑞𐑱 𐑕𐑧𐑯𐑑 𐑩 𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑓𐑮𐑪𐑥 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕. 𐑣𐑰—” ·𐑐𐑩𐑑𐑿𐑯𐑾'𐑟 𐑲𐑟 𐑓𐑤𐑦𐑒𐑑 𐑑 ·𐑥𐑲𐑒𐑩𐑤. “𐑣𐑰 𐑖𐑴𐑛 𐑳𐑕 𐑕𐑳𐑥 𐑥𐑨𐑡𐑦𐑒.”

“𐑞𐑧𐑯 𐑿 𐑛𐑴𐑯𐑑 𐑣𐑨𐑓 𐑑 𐑓𐑲𐑑 𐑴𐑝𐑼 𐑞𐑦𐑕,” 𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑓𐑻𐑥𐑤𐑦. 𐑣𐑴𐑐𐑦𐑙 𐑩𐑜𐑱𐑯𐑕𐑑 𐑣𐑴𐑐 𐑞𐑨𐑑 𐑞𐑦𐑕 𐑑𐑲𐑥, 𐑡𐑳𐑕𐑑 𐑞𐑦𐑕 𐑢𐑳𐑯𐑕, 𐑞𐑱 𐑢𐑫𐑛 𐑤𐑦𐑕𐑩𐑯 𐑑 𐑣𐑦𐑥. “𐑦𐑓 𐑦𐑑'𐑕 𐑑𐑮𐑵, 𐑢𐑰 𐑒𐑨𐑯 𐑡𐑳𐑕𐑑 𐑜𐑧𐑑 𐑩 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑣𐑽 𐑯 𐑕𐑰 𐑞 𐑥𐑨𐑡𐑦𐑒 𐑓 𐑬𐑼𐑕𐑧𐑤𐑝𐑟, 𐑯 ·𐑛𐑨𐑛 𐑢𐑦𐑤 𐑩𐑛𐑥𐑦𐑑 𐑞𐑨𐑑 𐑦𐑑'𐑕 𐑑𐑮𐑵. 𐑯 𐑦𐑓 𐑯𐑪𐑑, 𐑞𐑧𐑯 ·𐑥𐑳𐑥 𐑢𐑦𐑤 𐑩𐑛𐑥𐑦𐑑 𐑞𐑨𐑑 𐑦𐑑'𐑕 𐑓𐑷𐑤𐑕. 𐑞𐑨𐑑'𐑕 𐑢𐑪𐑑 𐑞 𐑦𐑒𐑕𐑐𐑧𐑮𐑦𐑥𐑧𐑯𐑑𐑩𐑤 𐑥𐑧𐑔𐑩𐑛 𐑦𐑟 𐑓, 𐑕𐑴 𐑞𐑨𐑑 𐑢𐑰 𐑛𐑴𐑯𐑑 𐑣𐑨𐑓 𐑑 𐑮𐑦𐑟𐑪𐑤𐑝 𐑔𐑦𐑙𐑟 𐑡𐑳𐑕𐑑 𐑚𐑲 𐑸𐑜𐑿𐑦𐑙.”

𐑞 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑑𐑻𐑯𐑛 𐑯 𐑤𐑫𐑒𐑑 𐑛𐑬𐑯 𐑨𐑑 𐑣𐑦𐑥, 𐑛𐑦𐑕𐑥𐑦𐑕𐑦𐑝 𐑨𐑟 𐑿𐑠𐑵𐑩𐑤. “𐑴, 𐑒𐑳𐑥 𐑯𐑬, ·𐑣𐑨𐑮𐑦. 𐑮𐑾𐑤𐑦, \emph{𐑥𐑨𐑡𐑦𐑒}? 𐑲 𐑔𐑷𐑑 \emph{𐑿'𐑛} 𐑯𐑴 𐑚𐑧𐑑𐑼 𐑞𐑨𐑯 𐑑 𐑑𐑱𐑒 𐑞𐑦𐑕 𐑕𐑽𐑾𐑕𐑤𐑦, 𐑕𐑳𐑯, 𐑰𐑝𐑩𐑯 𐑦𐑓 𐑿'𐑼 𐑴𐑯𐑤𐑦 𐑑𐑧𐑯. 𐑥𐑨𐑡𐑦𐑒 𐑦𐑟 𐑡𐑳𐑕𐑑 𐑩𐑚𐑬𐑑 𐑞 𐑥𐑴𐑕𐑑 𐑳𐑯𐑕𐑲𐑩𐑯𐑑𐑦𐑓𐑦𐑒 𐑔𐑦𐑙 𐑞𐑺 𐑦𐑟!”

𐑣𐑨𐑮𐑦'𐑟 𐑥𐑬𐑔 𐑑𐑢𐑦𐑕𐑑𐑩𐑛 𐑚𐑦𐑑𐑼𐑤𐑦. 𐑣𐑰 𐑢𐑪𐑟 𐑑𐑮𐑰𐑑𐑩𐑛 𐑢𐑧𐑤, 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑚𐑧𐑑𐑼 𐑞𐑨𐑯 𐑥𐑴𐑕𐑑 𐑡𐑩𐑯𐑧𐑑𐑦𐑒 𐑓𐑭𐑞𐑼𐑟 𐑑𐑮𐑰𐑑𐑩𐑛 𐑞𐑺 𐑴𐑯 𐑗𐑦𐑤𐑛𐑮𐑩𐑯. 𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑕𐑧𐑯𐑑 𐑑 𐑞 𐑚𐑧𐑕𐑑 𐑐𐑮𐑲𐑥𐑼𐑦 𐑕𐑒𐑵𐑤𐑟—𐑯 𐑢𐑧𐑯 𐑞𐑨𐑑 𐑛𐑦𐑛𐑩𐑯𐑑 𐑢𐑻𐑒 𐑬𐑑, 𐑣𐑰 𐑢𐑪𐑟 𐑐𐑮𐑩𐑝𐑲𐑛𐑩𐑛 𐑢𐑦𐑞 𐑑𐑿𐑑𐑼𐑟 𐑓𐑮𐑪𐑥 𐑞 𐑧𐑯𐑛𐑤𐑩𐑕 𐑐𐑵𐑤 𐑝 𐑕𐑑𐑸𐑝𐑦𐑙 𐑕𐑑𐑿𐑛𐑩𐑯𐑑𐑕. 𐑷𐑤𐑢𐑱𐑟 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑦𐑯𐑒𐑳𐑮𐑦𐑡𐑛 𐑑 𐑕𐑑𐑳𐑛𐑦 𐑢𐑪𐑑𐑧𐑝𐑼 𐑒𐑷𐑑 𐑣𐑦𐑟 𐑩𐑑𐑧𐑯𐑖𐑩𐑯, 𐑚𐑷𐑑 𐑷𐑤 𐑞 𐑚𐑫𐑒𐑕 𐑞𐑨𐑑 𐑒𐑷𐑑 𐑣𐑦𐑟 𐑓𐑨𐑯𐑕𐑦, 𐑕𐑐𐑪𐑯𐑕𐑼𐑛 𐑦𐑯 𐑢𐑪𐑑𐑧𐑝𐑼 𐑥𐑨𐑔𐑕 𐑹 𐑕𐑲𐑩𐑯𐑕 𐑒𐑪𐑥𐑐𐑩𐑑𐑦𐑖𐑩𐑯𐑟 𐑣𐑰 𐑧𐑯𐑑𐑼𐑛. 𐑣𐑰 𐑢𐑪𐑟 𐑜𐑦𐑝𐑩𐑯 𐑧𐑯𐑦𐑔𐑦𐑙 𐑮𐑰𐑟𐑩𐑯𐑩𐑚𐑩𐑤 𐑞𐑨𐑑 𐑣𐑰 𐑢𐑪𐑯𐑑𐑩𐑛, 𐑦𐑒𐑕𐑧𐑐𐑑, 𐑥𐑱𐑚𐑰, 𐑞 𐑕𐑤𐑲𐑑𐑩𐑕𐑑 𐑖𐑮𐑧𐑛 𐑝 𐑮𐑦𐑕𐑐𐑧𐑒𐑑. 𐑩 ·𐑛𐑪𐑒𐑑𐑼 𐑑𐑰𐑗𐑦𐑙 𐑚𐑲𐑴𐑒𐑧𐑥𐑦𐑕𐑑𐑮𐑦 𐑨𐑑 ·𐑪𐑒𐑕𐑓𐑼𐑛 𐑒𐑫𐑛 𐑣𐑸𐑛𐑤𐑦 𐑚𐑰 𐑦𐑒𐑕𐑐𐑧𐑒𐑑𐑩𐑛 𐑑 𐑤𐑦𐑕𐑩𐑯 𐑑 𐑞 𐑩𐑛𐑝𐑲𐑕 𐑝 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑚𐑶. 𐑿 𐑢𐑫𐑛 𐑤𐑦𐑕𐑩𐑯 𐑑 ·𐑖𐑴 ·𐑦𐑯𐑑𐑼𐑩𐑕𐑑, 𐑝 𐑒𐑹𐑕; 𐑞𐑨𐑑'𐑕 𐑢𐑪𐑑 𐑩 ·𐑜𐑫𐑛 ·𐑐𐑺𐑩𐑯𐑑 𐑢𐑫𐑛 𐑛𐑵, 𐑯 𐑕𐑴, 𐑦𐑓 𐑿 𐑒𐑩𐑯𐑕𐑰𐑝𐑛 𐑝 𐑘𐑹𐑕𐑧𐑤𐑓 𐑨𐑟 𐑩 ·𐑜𐑫𐑛 ·𐑐𐑺𐑩𐑯𐑑, 𐑿 𐑢𐑫𐑛 𐑛𐑵 𐑦𐑑. 𐑚𐑳𐑑 𐑑𐑱𐑒 𐑩 𐑑𐑧𐑯-𐑘𐑽-𐑴𐑤𐑛 \emph{𐑕𐑽𐑾𐑕𐑤𐑦}? 𐑣𐑸𐑛𐑤𐑦.

𐑕𐑳𐑥𐑑𐑲𐑥𐑟 ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑯𐑑𐑩𐑛 𐑑 𐑕𐑒𐑮𐑰𐑥 𐑨𐑑 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼.

“𐑥𐑳𐑥,” 𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. “𐑦𐑓 𐑿 𐑢𐑪𐑯𐑑 𐑑 𐑢𐑦𐑯 𐑞𐑦𐑕 𐑸𐑜𐑿𐑥𐑩𐑯𐑑 𐑢𐑦𐑞 ·𐑛𐑨𐑛, 𐑤𐑫𐑒 𐑦𐑯 𐑗𐑨𐑐𐑑𐑼 𐑑𐑵 𐑝 𐑞 𐑓𐑻𐑕𐑑 𐑚𐑫𐑒 𐑝 𐑞 ·𐑓𐑲𐑯𐑥𐑩𐑯 ·𐑤𐑧𐑒𐑗𐑼𐑟 𐑪𐑯 ·𐑓𐑦𐑟𐑦𐑒𐑕. 𐑞𐑺'𐑟 𐑩 𐑒𐑢𐑴𐑑 𐑞𐑺 𐑩𐑚𐑬𐑑 𐑣𐑬 𐑓𐑦𐑤𐑪𐑕𐑩𐑓𐑼𐑟 𐑕𐑱 𐑩 𐑜𐑮𐑱𐑑 𐑛𐑰𐑤 𐑩𐑚𐑬𐑑 𐑢𐑪𐑑 𐑕𐑲𐑩𐑯𐑕 𐑨𐑚𐑕𐑩𐑤𐑵𐑑𐑤𐑦 𐑮𐑦𐑒𐑢𐑲𐑼𐑟, 𐑯 𐑦𐑑 𐑦𐑟 𐑷𐑤 𐑮𐑪𐑙, 𐑚𐑦𐑒𐑪𐑟 𐑞 𐑴𐑯𐑤𐑦 𐑮𐑵𐑤 𐑦𐑯 𐑕𐑲𐑩𐑯𐑕 𐑦𐑟 𐑞𐑨𐑑 𐑞 𐑓𐑲𐑯𐑩𐑤 𐑸𐑚𐑦𐑑𐑼 𐑦𐑟 𐑪𐑚𐑟𐑼𐑝𐑱𐑖𐑩𐑯—𐑞𐑨𐑑 𐑿 𐑡𐑳𐑕𐑑 𐑣𐑨𐑓 𐑑 𐑤𐑫𐑒 𐑨𐑑 𐑞 𐑢𐑻𐑤𐑛 𐑯 𐑮𐑦𐑐𐑹𐑑 𐑢𐑪𐑑 𐑿 𐑕𐑰. 𐑳𐑥…𐑪𐑓 𐑞 𐑑𐑪𐑐 𐑝 𐑥𐑲 𐑣𐑧𐑛 𐑲 𐑒𐑭𐑯𐑑 𐑔𐑦𐑙𐑒 𐑝 𐑢𐑺 𐑑 𐑓𐑲𐑯𐑛 𐑕𐑳𐑥𐑔𐑦𐑙 𐑩𐑚𐑬𐑑 𐑣𐑬 𐑦𐑑'𐑕 𐑩𐑯 𐑲𐑛𐑾𐑤 𐑝 𐑕𐑲𐑩𐑯𐑕 𐑑 𐑕𐑧𐑑𐑩𐑤 𐑔𐑦𐑙𐑟 𐑚𐑲 𐑦𐑒𐑕𐑐𐑧𐑮𐑦𐑥𐑧𐑯𐑑 𐑦𐑯𐑕𐑑𐑧𐑛 𐑝 𐑸𐑜𐑿𐑥𐑩𐑯𐑑𐑕—”

𐑣𐑦𐑟 𐑥𐑳𐑞𐑼 𐑤𐑫𐑒𐑑 𐑛𐑬𐑯 𐑨𐑑 𐑣𐑦𐑥 𐑯 𐑕𐑥𐑲𐑤𐑛. “𐑔𐑨𐑙𐑒 𐑿, ·𐑣𐑨𐑮𐑦. 𐑚𐑳𐑑—” 𐑣𐑻 𐑣𐑧𐑛 𐑮𐑴𐑟 𐑚𐑨𐑒 𐑳𐑐 𐑑 𐑕𐑑𐑺 𐑨𐑑 𐑣𐑻 𐑣𐑳𐑟𐑚𐑩𐑯𐑛. “𐑲 𐑛𐑴𐑯𐑑 𐑢𐑪𐑯𐑑 𐑑 𐑢𐑦𐑯 𐑩𐑯 𐑸𐑜𐑿𐑥𐑩𐑯𐑑 𐑢𐑦𐑞 𐑘𐑹 𐑓𐑭𐑞𐑼. 𐑲 𐑢𐑪𐑯𐑑 𐑥𐑲 𐑣𐑳𐑟𐑚𐑩𐑯𐑛 𐑑, 𐑑 𐑤𐑦𐑕𐑩𐑯 𐑑 𐑣𐑦𐑟 𐑢𐑲𐑓 𐑣𐑵 𐑤𐑳𐑝𐑟 𐑣𐑦𐑥, 𐑯 𐑑𐑮𐑳𐑕𐑑 𐑣𐑻 𐑡𐑳𐑕𐑑 𐑞𐑦𐑕 𐑢𐑳𐑯𐑕—”

𐑣𐑨𐑮𐑦 𐑒𐑤𐑴𐑟𐑛 𐑣𐑦𐑟 𐑲𐑟 𐑚𐑮𐑰𐑓𐑤𐑦. \emph{𐑣𐑴𐑐𐑤𐑩𐑕.} 𐑚𐑴𐑔 𐑝 𐑣𐑦𐑟 𐑐𐑺𐑩𐑯𐑑𐑕 𐑢𐑻 𐑡𐑳𐑕𐑑 𐑣𐑴𐑐𐑤𐑩𐑕.

𐑯𐑬 𐑣𐑦𐑟 𐑐𐑺𐑩𐑯𐑑𐑕 𐑢𐑻 𐑜𐑧𐑑𐑦𐑙 𐑦𐑯𐑑𐑵 𐑢𐑳𐑯 𐑝 \emph{𐑞𐑴𐑟} 𐑸𐑜𐑿𐑥𐑩𐑯𐑑𐑕 𐑩𐑜𐑱𐑯, 𐑢𐑳𐑯 𐑢𐑺 𐑣𐑦𐑟 𐑥𐑳𐑞𐑼 𐑑𐑮𐑲𐑛 𐑑 𐑥𐑱𐑒 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑓𐑰𐑤 𐑜𐑦𐑤𐑑𐑦, 𐑯 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑑𐑮𐑲𐑛 𐑑 𐑥𐑱𐑒 𐑣𐑦𐑟 𐑥𐑳𐑞𐑼 𐑓𐑰𐑤 𐑕𐑑𐑿𐑐𐑦𐑛.

“𐑲'𐑥 𐑜𐑴𐑦𐑙 𐑑 𐑜𐑴 𐑑 𐑥𐑲 𐑮𐑵𐑥,” 𐑣𐑨𐑮𐑦 𐑩𐑯𐑬𐑯𐑕𐑑. 𐑣𐑦𐑟 𐑝𐑶𐑕 𐑑𐑮𐑧𐑥𐑚𐑩𐑤𐑛 𐑩 𐑤𐑦𐑑𐑩𐑤. “𐑐𐑤𐑰𐑟 𐑑𐑮𐑲 𐑯𐑪𐑑 𐑑 𐑓𐑲𐑑 𐑑𐑵 𐑥𐑳𐑗 𐑩𐑚𐑬𐑑 𐑞𐑦𐑕, ·𐑥𐑳𐑥, ·𐑛𐑨𐑛, 𐑢𐑰'𐑤 𐑯𐑴 𐑕𐑵𐑯 𐑦𐑯𐑳𐑓 𐑣𐑬 𐑦𐑑 𐑒𐑳𐑥𐑟 𐑬𐑑, 𐑮𐑲𐑑?”

“𐑝 𐑒𐑹𐑕, ·𐑣𐑨𐑮𐑦,” 𐑕𐑧𐑛 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼, 𐑯 𐑣𐑦𐑟 𐑥𐑳𐑞𐑼 𐑜𐑱𐑝 𐑣𐑦𐑥 𐑩 𐑮𐑰𐑩𐑖𐑫𐑼𐑦𐑙 𐑒𐑦𐑕, 𐑯 𐑞𐑧𐑯 𐑞𐑱 𐑢𐑧𐑯𐑑 𐑪𐑯 𐑓𐑲𐑑𐑦𐑙 𐑢𐑲𐑤 ·𐑣𐑨𐑮𐑦 𐑒𐑤𐑲𐑥𐑛 𐑞 𐑕𐑑𐑺𐑟 𐑑 𐑣𐑦𐑟 𐑚𐑧𐑛𐑮𐑵𐑥.

𐑣𐑰 𐑖𐑳𐑑 𐑞 𐑛𐑹 𐑚𐑦𐑣𐑲𐑯𐑛 𐑣𐑦𐑥 𐑯 𐑑𐑮𐑲𐑛 𐑑 𐑔𐑦𐑙𐑒.

𐑞 𐑓𐑳𐑯𐑦 𐑔𐑦𐑙 𐑢𐑪𐑟, 𐑣𐑰 \emph{𐑖𐑫𐑛} 𐑣𐑨𐑝 𐑩𐑜𐑮𐑰𐑛 𐑢𐑦𐑞 ·𐑛𐑨𐑛. 𐑯𐑴-𐑢𐑳𐑯 𐑣𐑨𐑛 𐑧𐑝𐑼 𐑕𐑰𐑯 𐑧𐑯𐑦 𐑧𐑝𐑦𐑛𐑩𐑯𐑕 𐑝 𐑥𐑨𐑡𐑦𐑒, 𐑯 𐑩𐑒𐑹𐑛𐑦𐑙 𐑑 ·𐑥𐑳𐑥, 𐑞𐑺 𐑢𐑪𐑟 𐑩 𐑣𐑴𐑤 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 𐑢𐑻𐑤𐑛 𐑬𐑑 𐑞𐑺. 𐑣𐑬 𐑒𐑫𐑛 𐑧𐑯𐑦𐑢𐑳𐑯 𐑒𐑰𐑐 𐑕𐑳𐑥𐑔𐑦𐑙 𐑤𐑲𐑒 𐑞𐑨𐑑 𐑩 𐑕𐑰𐑒𐑮𐑩𐑑? 𐑥𐑹 𐑥𐑨𐑡𐑦𐑒? 𐑞𐑨𐑑 𐑕𐑰𐑥𐑛 𐑤𐑲𐑒 𐑩 𐑮𐑭𐑞𐑼 𐑕𐑩𐑕𐑐𐑦𐑖𐑩𐑕 𐑕𐑹𐑑 𐑝 𐑦𐑒𐑕𐑒𐑿𐑕.

𐑦𐑑 𐑖𐑫𐑛 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑩 𐑒𐑤𐑰𐑯 𐑒𐑱𐑕 𐑓 ·𐑥𐑳𐑥 𐑡𐑴𐑒𐑦𐑙, 𐑤𐑲𐑦𐑙 𐑹 𐑚𐑰𐑦𐑙 𐑦𐑯𐑕𐑱𐑯, 𐑦𐑯 𐑩𐑕𐑧𐑯𐑛𐑦𐑙 𐑹𐑛𐑼 𐑝 𐑷𐑓𐑩𐑤𐑯𐑩𐑕. 𐑦𐑓 ·𐑥𐑳𐑥 𐑣𐑨𐑛 𐑕𐑧𐑯𐑑 𐑞 𐑤𐑧𐑑𐑼 𐑣𐑻𐑕𐑧𐑤𐑓, 𐑞𐑨𐑑 𐑢𐑫𐑛 𐑦𐑒𐑕𐑐𐑤𐑱𐑯 𐑣𐑬 𐑦𐑑 𐑼𐑲𐑝𐑛 𐑨𐑑 𐑞 𐑤𐑧𐑑𐑼𐑚𐑪𐑒𐑕 𐑢𐑦𐑞𐑬𐑑 𐑩 𐑕𐑑𐑨𐑥𐑐. 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑦𐑯𐑕𐑨𐑯𐑦𐑑𐑦 𐑢𐑪𐑟 𐑓𐑸, 𐑓𐑸 𐑤𐑧𐑕 𐑦𐑥𐑐𐑮𐑪𐑚𐑩𐑚𐑩𐑤 𐑞𐑨𐑯 𐑞 𐑿𐑯𐑦𐑝𐑻𐑕 𐑮𐑾𐑤𐑦 𐑢𐑻𐑒𐑦𐑙 𐑤𐑲𐑒 𐑞𐑨𐑑.

𐑦𐑒𐑕𐑧𐑐𐑑 𐑞𐑨𐑑 𐑕𐑳𐑥 𐑐𐑸𐑑 𐑝 ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑳𐑑𐑼𐑤𐑦 𐑒𐑩𐑯𐑝𐑦𐑯𐑕𐑑 𐑞𐑨𐑑 𐑥𐑨𐑡𐑦𐑒 𐑢𐑪𐑟 𐑮𐑾𐑤, 𐑯 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑕𐑦𐑯𐑕 𐑞 𐑦𐑯𐑕𐑑𐑩𐑯𐑑 𐑣𐑰 𐑕𐑷 𐑞 𐑐𐑿𐑑𐑩𐑑𐑦𐑝 𐑤𐑧𐑑𐑼 𐑓𐑮𐑪𐑥 𐑞 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 ·𐑕𐑒𐑵𐑤 𐑝 ·𐑢𐑦𐑗𐑒𐑮𐑭𐑓𐑑 𐑯 ·𐑢𐑦𐑟𐑼𐑛𐑮𐑦.

𐑣𐑨𐑮𐑦 𐑮𐑳𐑚𐑛 𐑣𐑦𐑟 𐑓𐑪𐑮𐑦𐑛, 𐑜𐑮𐑦𐑥𐑩𐑕𐑦𐑙. \emph{𐑛𐑴𐑯𐑑 𐑚𐑦𐑤𐑰𐑝 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑿 𐑔𐑦𐑙𐑒,} 𐑢𐑳𐑯 𐑝 𐑣𐑦𐑟 𐑚𐑫𐑒𐑕 𐑣𐑨𐑛 𐑕𐑧𐑛.

𐑚𐑳𐑑 𐑞𐑦𐑕 𐑚𐑦𐑟𐑸 𐑕𐑻𐑑𐑩𐑯𐑑𐑦…·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑓𐑲𐑯𐑛𐑦𐑙 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑡𐑳𐑕𐑑 \emph{𐑦𐑒𐑕𐑐𐑧𐑒𐑑𐑦𐑙} 𐑞𐑨𐑑, 𐑘𐑧𐑕, 𐑩 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑢𐑫𐑛 𐑖𐑴 𐑳𐑐 𐑯 𐑢𐑱𐑝 𐑩 𐑢𐑪𐑯𐑛 𐑯 𐑥𐑨𐑡𐑦𐑒 𐑢𐑫𐑛 𐑒𐑳𐑥 𐑬𐑑. 𐑞 𐑕𐑑𐑮𐑱𐑯𐑡 𐑕𐑻𐑑𐑩𐑯𐑑𐑦 𐑢𐑪𐑟 𐑥𐑱𐑒𐑦𐑙 𐑯𐑴 𐑧𐑓𐑼𐑑 𐑑 𐑜𐑸𐑛 𐑦𐑑𐑕𐑧𐑤𐑓 𐑩𐑜𐑱𐑯𐑕𐑑 𐑓𐑷𐑤𐑕𐑦𐑓𐑦𐑒𐑱𐑖𐑩𐑯—𐑢𐑪𐑟𐑩𐑯𐑑 𐑥𐑱𐑒𐑦𐑙 𐑦𐑒𐑕𐑒𐑿𐑕𐑩𐑟 𐑦𐑯 𐑩𐑛𐑝𐑭𐑯𐑕 𐑓 𐑢𐑲 𐑞𐑺 𐑢𐑫𐑛𐑩𐑯𐑑 𐑚𐑰 𐑩 𐑐𐑮𐑩𐑓𐑧𐑕𐑼, 𐑹 𐑞 𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑢𐑫𐑛 𐑴𐑯𐑤𐑦 𐑚𐑰 𐑱𐑚𐑩𐑤 𐑑 𐑚𐑧𐑯𐑛 𐑕𐑐𐑵𐑯𐑟.

\emph{𐑢𐑺 𐑛𐑵 𐑿 𐑒𐑳𐑥 𐑓𐑮𐑪𐑥, 𐑕𐑑𐑮𐑱𐑯𐑡 𐑤𐑦𐑑𐑩𐑤 𐑐𐑮𐑦𐑛𐑦𐑒𐑖𐑩𐑯?} 𐑣𐑨𐑮𐑦 𐑛𐑦𐑮𐑧𐑒𐑑𐑩𐑛 𐑞 𐑔𐑷𐑑 𐑨𐑑 𐑣𐑦𐑟 𐑚𐑮𐑱𐑯. \emph{𐑢𐑲 𐑛𐑵 𐑲 𐑚𐑦𐑤𐑰𐑝 𐑢𐑪𐑑 𐑲 𐑚𐑦𐑤𐑰𐑝?}

𐑿𐑠𐑵𐑩𐑤𐑦 ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑐𐑮𐑦𐑑𐑦 𐑜𐑫𐑛 𐑨𐑑 𐑭𐑯𐑕𐑼𐑦𐑙 𐑞𐑨𐑑 𐑒𐑢𐑧𐑕𐑗𐑩𐑯, 𐑚𐑳𐑑 𐑦𐑯 𐑞𐑦𐑕 𐑐𐑼𐑑𐑦𐑒𐑿𐑤𐑼 𐑒𐑱𐑕, 𐑣𐑰 𐑣𐑨𐑛 𐑯𐑴 \emph{𐑒𐑤𐑵} 𐑢𐑪𐑑 𐑣𐑦𐑟 𐑚𐑮𐑱𐑯 𐑢𐑪𐑟 𐑔𐑦𐑙𐑒𐑦𐑙.

𐑣𐑨𐑮𐑦 𐑥𐑧𐑯𐑑𐑩𐑤𐑦 𐑖𐑮𐑳𐑜𐑛. 𐑩 𐑓𐑤𐑨𐑑 𐑥𐑧𐑑𐑩𐑤 𐑐𐑤𐑱𐑑 𐑪𐑯 𐑩 𐑛𐑹 𐑩𐑓𐑹𐑛𐑟 𐑐𐑫𐑖𐑦𐑙, 𐑯 𐑩 𐑣𐑨𐑯𐑛𐑩𐑤 𐑪𐑯 𐑩 𐑛𐑹 𐑩𐑓𐑹𐑛𐑟 𐑐𐑫𐑤𐑦𐑙, 𐑯 𐑞 𐑔𐑦𐑙 𐑑 𐑛𐑵 𐑢𐑦𐑞 𐑩 𐑑𐑧𐑕𐑑𐑩𐑚𐑩𐑤 𐑣𐑲𐑐𐑪𐑔𐑦𐑕𐑦𐑕 𐑦𐑟 𐑑 𐑜𐑴 𐑯 𐑑𐑧𐑕𐑑 𐑦𐑑.

𐑣𐑰 𐑑𐑫𐑒 𐑩 𐑐𐑰𐑕 𐑝 𐑤𐑲𐑯𐑛 𐑐𐑱𐑐𐑼 𐑓𐑮𐑪𐑥 𐑣𐑦𐑟 𐑛𐑧𐑕𐑒, 𐑯 𐑕𐑑𐑸𐑑𐑩𐑛 𐑮𐑲𐑑𐑦𐑙.

\begin{writtenNote}
\letterAddress{𐑛𐑽 ·𐑛𐑧𐑐𐑿𐑑𐑦 ·𐑣𐑧𐑛𐑥𐑦𐑕𐑑𐑮𐑩𐑕}
\end{writtenNote}

·𐑣𐑨𐑮𐑦 𐑐𐑷𐑟𐑛, 𐑮𐑦𐑓𐑤𐑧𐑒𐑑𐑦𐑙; 𐑞𐑧𐑯 𐑛𐑦𐑕𐑒𐑸𐑛𐑩𐑛 𐑞 𐑐𐑱𐑐𐑼 𐑓 𐑩𐑯𐑳𐑞𐑼, 𐑑𐑨𐑐𐑦𐑙 𐑩𐑯𐑳𐑞𐑼 𐑥𐑦𐑤𐑦𐑥𐑰𐑑𐑼 𐑝 𐑜𐑮𐑭𐑓𐑲𐑑 𐑓𐑮𐑪𐑥 𐑣𐑦𐑟 𐑥𐑦𐑒𐑨𐑯𐑦𐑒𐑩𐑤 𐑐𐑧𐑯𐑕𐑩𐑤. 𐑞𐑦𐑕 𐑒𐑷𐑤𐑛 𐑓 𐑒𐑺𐑓𐑩𐑤 𐑒𐑩𐑤𐑦𐑜𐑮𐑩𐑓𐑦.

\begin{writtenNote}
\letterAddress{𐑛𐑽 ·𐑛𐑧𐑐𐑿𐑑𐑦 ·𐑣𐑧𐑛𐑥𐑦𐑕𐑑𐑮𐑩𐑕 ·𐑥𐑦𐑯𐑻𐑝𐑩 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤,}

\letterAddress{𐑹 ·𐑣𐑵𐑥𐑕𐑴𐑧𐑝𐑼 𐑦𐑑 𐑥𐑱 ·𐑒𐑩𐑯𐑕𐑻𐑯:}

𐑲 𐑮𐑰𐑕𐑩𐑯𐑑𐑤𐑦 𐑮𐑦𐑕𐑰𐑝𐑛 𐑘𐑹 𐑤𐑧𐑑𐑼 𐑝 𐑩𐑒𐑕𐑧𐑐𐑑𐑩𐑯𐑕 𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕, 𐑩𐑛𐑮𐑧𐑕𐑑 𐑑 ·𐑥𐑼~·𐑣.~𐑐𐑪𐑑𐑼. 𐑿 𐑥𐑱 𐑯𐑪𐑑 𐑚𐑰 𐑩𐑢𐑺 𐑞𐑨𐑑 𐑥𐑲 𐑡𐑩𐑯𐑧𐑑𐑦𐑒 𐑐𐑺𐑩𐑯𐑑𐑕, ·𐑡𐑱𐑥𐑟 ·𐑐𐑪𐑑𐑼 𐑯 ·𐑤𐑦𐑤𐑦 ·𐑐𐑪𐑑𐑼 (𐑓𐑹𐑥𐑼𐑤𐑦 ·𐑤𐑦𐑤𐑦 ·𐑧𐑝𐑩𐑯𐑟) 𐑸 𐑛𐑧𐑛. 𐑲 𐑢𐑪𐑟 𐑩𐑛𐑪𐑐𐑑𐑩𐑛 𐑚𐑲 ·𐑤𐑦𐑤𐑦'𐑟 𐑕𐑦𐑕𐑑𐑼, ·𐑐𐑩𐑑𐑿𐑯𐑾 ·𐑧𐑝𐑩𐑯𐑟-·𐑝𐑧𐑮𐑟, 𐑯 𐑣𐑻 𐑣𐑳𐑟𐑚𐑩𐑯𐑛, ·𐑥𐑲𐑒𐑩𐑤 ·𐑝𐑧𐑮𐑟-·𐑧𐑝𐑩𐑯𐑟.

𐑲 𐑨𐑥 𐑦𐑒𐑕𐑑𐑮𐑰𐑥𐑤𐑦 𐑦𐑯𐑑𐑼𐑩𐑕𐑑𐑩𐑛 𐑦𐑯 𐑩𐑑𐑧𐑯𐑛𐑦𐑙 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕, 𐑒𐑩𐑯𐑛𐑦𐑖𐑩𐑯𐑩𐑤 𐑪𐑯 𐑕𐑳𐑗 𐑩 𐑐𐑤𐑱𐑕 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑦𐑜𐑟𐑦𐑕𐑑𐑦𐑙. 𐑴𐑯𐑤𐑦 𐑥𐑲 𐑥𐑳𐑞𐑼 ·𐑐𐑩𐑑𐑿𐑯𐑾 𐑕𐑧𐑟 𐑖𐑰 𐑯𐑴𐑟 𐑩𐑚𐑬𐑑 𐑥𐑨𐑡𐑦𐑒, 𐑯 𐑖𐑰 𐑒𐑭𐑯𐑑 𐑿𐑟 𐑦𐑑 𐑣𐑻𐑕𐑧𐑤𐑓. 𐑥𐑲 𐑓𐑭𐑞𐑼 𐑦𐑟 𐑣𐑲𐑤𐑦 𐑕𐑒𐑧𐑐𐑑𐑦𐑒𐑩𐑤. 𐑲 𐑥𐑲𐑕𐑧𐑤𐑓 𐑨𐑥 𐑳𐑯𐑕𐑻𐑑𐑩𐑯. 𐑲 𐑷𐑤𐑕𐑴 𐑛𐑴𐑯𐑑 𐑯𐑴 𐑢𐑺 𐑑 𐑩𐑚𐑑𐑱𐑯 𐑧𐑯𐑦 𐑝 𐑞 𐑚𐑫𐑒𐑕 𐑹 𐑦𐑒𐑢𐑦𐑐𐑥𐑩𐑯𐑑 𐑤𐑦𐑕𐑑𐑩𐑛 𐑦𐑯 𐑘𐑹 𐑩𐑒𐑕𐑧𐑐𐑑𐑩𐑯𐑕 𐑤𐑧𐑑𐑼.

𐑥𐑳𐑞𐑼 𐑥𐑧𐑯𐑖𐑩𐑯𐑛 𐑞𐑨𐑑 𐑿 𐑕𐑧𐑯𐑑 𐑩 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 𐑮𐑧𐑐𐑮𐑦𐑟𐑧𐑯𐑑𐑩𐑑𐑦𐑝 𐑑 ·𐑤𐑦𐑤𐑦 ·𐑐𐑪𐑑𐑼 (𐑞𐑧𐑯 ·𐑤𐑦𐑤𐑦 ·𐑧𐑝𐑩𐑯𐑟) 𐑦𐑯 𐑹𐑛𐑼 𐑑 𐑛𐑧𐑥𐑩𐑯𐑕𐑑𐑮𐑱𐑑 𐑑 𐑣𐑻 𐑓𐑨𐑥𐑤𐑦 𐑞𐑨𐑑 𐑥𐑨𐑡𐑦𐑒 𐑢𐑪𐑟 𐑮𐑾𐑤, 𐑯, 𐑲 𐑐𐑮𐑦𐑟𐑿𐑥, 𐑣𐑧𐑤𐑐 ·𐑤𐑦𐑤𐑦 𐑩𐑚𐑑𐑱𐑯 𐑣𐑻 𐑕𐑒𐑵𐑤 𐑥𐑩𐑑𐑽𐑾𐑤𐑟. 𐑦𐑓 𐑿 𐑒𐑫𐑛 𐑛𐑵 𐑞𐑦𐑕 𐑓 𐑥𐑲 𐑴𐑯 𐑓𐑨𐑥𐑤𐑦 𐑦𐑑 𐑢𐑫𐑛 𐑚𐑰 𐑦𐑒𐑕𐑑𐑮𐑰𐑥𐑤𐑦 𐑣𐑧𐑤𐑐𐑓𐑩𐑤.

\letterClosing[𐑕𐑦𐑯𐑕𐑽𐑤𐑦,]{𐑣𐑨𐑮𐑦 ·𐑡𐑱𐑥𐑟 ·𐑐𐑪𐑑𐑼-·𐑧𐑝𐑩𐑯𐑟-·𐑝𐑧𐑮𐑟.}
\end{writtenNote}

𐑣𐑨𐑮𐑦 𐑨𐑛𐑩𐑛 𐑞𐑺 𐑒𐑳𐑮𐑩𐑯𐑑 𐑩𐑛𐑮𐑧𐑕, 𐑞𐑧𐑯 𐑓𐑴𐑤𐑛𐑩𐑛 𐑳𐑐 𐑞 𐑤𐑧𐑑𐑼 𐑯 𐑐𐑫𐑑 𐑦𐑑 𐑦𐑯 𐑩𐑯 𐑧𐑯𐑝𐑩𐑤𐑴𐑐, 𐑢𐑦𐑗 𐑣𐑰 𐑩𐑛𐑮𐑧𐑕𐑑 𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕. 𐑓𐑻𐑞𐑼 𐑒𐑩𐑯𐑕𐑦𐑛𐑼𐑱𐑖𐑩𐑯 𐑤𐑧𐑛 𐑣𐑦𐑥 𐑑 𐑩𐑚𐑑𐑱𐑯 𐑩 𐑒𐑨𐑯𐑛𐑩𐑤 𐑯 𐑛𐑮𐑦𐑐 𐑢𐑨𐑒𐑕 𐑪𐑯𐑑𐑵 𐑞 𐑓𐑤𐑨𐑐 𐑝 𐑞 𐑧𐑯𐑝𐑩𐑤𐑴𐑐, 𐑦𐑯𐑑𐑵 𐑢𐑦𐑗, 𐑿𐑟𐑦𐑙 𐑩 𐑐𐑧𐑯𐑯𐑲𐑓'𐑕 𐑑𐑦𐑐, 𐑣𐑰 𐑦𐑥𐑐𐑮𐑧𐑕𐑑 𐑞 𐑦𐑯𐑦𐑖𐑩𐑤𐑟 ·𐑣.𐑡.𐑐.𐑰.V\@. 𐑦𐑓 𐑣𐑰 𐑢𐑪𐑟 𐑜𐑴𐑦𐑙 𐑑 𐑛𐑦𐑕𐑧𐑯𐑛 𐑦𐑯𐑑𐑵 𐑞𐑦𐑕 𐑥𐑨𐑛𐑯𐑩𐑕, 𐑣𐑰 𐑢𐑪𐑟 𐑜𐑴𐑦𐑙 𐑑 𐑛𐑵 𐑦𐑑 𐑢𐑦𐑞 𐑕𐑑𐑲𐑤.

𐑞𐑧𐑯 𐑣𐑰 𐑴𐑐𐑩𐑯𐑛 𐑣𐑦𐑟 𐑛𐑹 𐑯 𐑢𐑧𐑯𐑑 𐑚𐑨𐑒 𐑛𐑬𐑯𐑕𐑑𐑺𐑟. 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑢𐑪𐑟 𐑕𐑦𐑑𐑦𐑙 𐑦𐑯 𐑞 𐑤𐑦𐑝𐑦𐑙-𐑮𐑵𐑥 𐑯 𐑮𐑰𐑛𐑦𐑙 𐑩 𐑚𐑫𐑒 𐑝 𐑣𐑲𐑼 𐑥𐑨𐑔𐑕 𐑑 𐑖𐑴 𐑣𐑬 𐑕𐑥𐑸𐑑 𐑣𐑰 𐑢𐑪𐑟; 𐑯 𐑣𐑦𐑟 𐑥𐑳𐑞𐑼 𐑢𐑪𐑟 𐑦𐑯 𐑞 𐑒𐑦𐑗𐑦𐑯 𐑐𐑮𐑦𐑐𐑺𐑦𐑙 𐑢𐑳𐑯 𐑝 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼'𐑟 𐑓𐑱𐑝𐑼𐑦𐑑 𐑥𐑰𐑤𐑟 𐑑 𐑖𐑴 𐑣𐑬 𐑤𐑳𐑝𐑦𐑙 𐑖𐑰 𐑢𐑪𐑟. 𐑦𐑑 𐑛𐑦𐑛𐑩𐑯𐑑 𐑤𐑫𐑒 𐑤𐑲𐑒 𐑞𐑱 𐑢𐑻 𐑑𐑷𐑒𐑦𐑙 𐑑 𐑢𐑳𐑯 𐑩𐑯𐑳𐑞𐑼 𐑨𐑑 𐑷𐑤. 𐑨𐑟 𐑕𐑒𐑺𐑦 𐑨𐑟 𐑸𐑜𐑿𐑥𐑩𐑯𐑑𐑕 𐑒𐑫𐑛 𐑚𐑰, \emph{𐑯𐑪𐑑 𐑸𐑜𐑿𐑦𐑙} 𐑢𐑪𐑟 𐑕𐑳𐑥𐑣𐑬 𐑥𐑳𐑗 𐑢𐑻𐑕.

“𐑥𐑳𐑥,” 𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑦𐑯𐑑𐑵 𐑞 𐑳𐑯𐑯𐑻𐑝𐑦𐑙 𐑕𐑲𐑤𐑩𐑯𐑕, “𐑲'𐑥 𐑜𐑴𐑦𐑙 𐑑 𐑑𐑧𐑕𐑑 𐑞 𐑣𐑲𐑐𐑪𐑔𐑦𐑕𐑦𐑕. 𐑩𐑒𐑹𐑛𐑦𐑙 𐑑 𐑘𐑹 𐑔𐑽𐑦, 𐑣𐑬 𐑛𐑵 𐑲 𐑕𐑧𐑯𐑛 𐑩𐑯 𐑬𐑤 𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕?”

𐑣𐑦𐑟 𐑥𐑳𐑞𐑼 𐑑𐑻𐑯𐑛 𐑓𐑮𐑪𐑥 𐑞 𐑒𐑦𐑗𐑦𐑯 𐑕𐑦𐑙𐑒 𐑑 𐑕𐑑𐑺 𐑨𐑑 𐑣𐑦𐑥, 𐑤𐑫𐑒𐑦𐑙 𐑖𐑪𐑒𐑑. “𐑲—𐑲 𐑛𐑴𐑯𐑑 𐑯𐑴, 𐑲 𐑔𐑦𐑙𐑒 𐑿 𐑡𐑳𐑕𐑑 𐑣𐑨𐑓 𐑑 𐑴𐑯 𐑩 𐑥𐑨𐑡𐑦𐑒 𐑬𐑤.”

𐑞𐑨𐑑 𐑖𐑫𐑛'𐑝 𐑕𐑬𐑯𐑛𐑩𐑛 𐑣𐑲𐑤𐑦 𐑕𐑩𐑕𐑐𐑦𐑖𐑩𐑕, \emph{𐑴, 𐑕𐑴 𐑞𐑺'𐑟 𐑯𐑴 𐑢𐑱 𐑑 𐑑𐑧𐑕𐑑 𐑘𐑹 𐑔𐑽𐑦 𐑞𐑧𐑯}, 𐑚𐑳𐑑 𐑞 𐑐𐑦𐑒𐑿𐑤𐑽 𐑕𐑻𐑑𐑩𐑯𐑑𐑦 𐑦𐑯 ·𐑣𐑨𐑮𐑦 𐑕𐑰𐑥𐑛 𐑢𐑦𐑤𐑦𐑙 𐑑 𐑕𐑑𐑦𐑒 𐑦𐑑𐑕 𐑯𐑧𐑒 𐑬𐑑 𐑰𐑝𐑩𐑯 𐑓𐑻𐑞𐑼.

“𐑢𐑧𐑤, 𐑞 𐑤𐑧𐑑𐑼 𐑜𐑪𐑑 𐑣𐑽 𐑕𐑳𐑥𐑣𐑬,” 𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, “𐑕𐑴 𐑲'𐑤 𐑡𐑳𐑕𐑑 𐑢𐑱𐑝 𐑦𐑑 𐑼𐑬𐑯𐑛 𐑬𐑑𐑕𐑲𐑛 𐑯 𐑒𐑷𐑤 '𐑤𐑧𐑑𐑼 𐑓 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕!' 𐑯 𐑕𐑰 𐑦𐑓 𐑩𐑯 𐑬𐑤 𐑐𐑦𐑒𐑕 𐑦𐑑 𐑳𐑐. 𐑛𐑨𐑛, 𐑛𐑵 𐑿 𐑢𐑪𐑯𐑑 𐑑 𐑒𐑳𐑥 𐑯 𐑢𐑪𐑗?”

𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑖𐑫𐑒 𐑣𐑦𐑟 𐑣𐑧𐑛 𐑥𐑲𐑯𐑿𐑑𐑤𐑦 𐑯 𐑒𐑧𐑐𐑑 𐑪𐑯 𐑮𐑰𐑛𐑦𐑙. \emph{𐑝 𐑒𐑹𐑕,} ·𐑣𐑨𐑮𐑦 𐑔𐑷𐑑 𐑑 𐑣𐑦𐑥𐑕𐑧𐑤𐑓. 𐑥𐑨𐑡𐑦𐑒 𐑢𐑪𐑟 𐑩 𐑛𐑦𐑕𐑜𐑮𐑱𐑕𐑓𐑩𐑤 𐑔𐑦𐑙 𐑞𐑨𐑑 𐑴𐑯𐑤𐑦 𐑕𐑑𐑿𐑐𐑦𐑛 𐑐𐑰𐑐𐑩𐑤 𐑚𐑦𐑤𐑰𐑝𐑛 𐑦𐑯; 𐑦𐑓 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑢𐑧𐑯𐑑 𐑕𐑴 𐑓𐑸 𐑨𐑟 𐑑 \emph{𐑑𐑧𐑕𐑑} 𐑞 𐑣𐑲𐑐𐑪𐑔𐑦𐑕𐑦𐑕, 𐑹 𐑰𐑝𐑩𐑯 \emph{𐑢𐑪𐑗} 𐑦𐑑 𐑚𐑰𐑦𐑙 𐑑𐑧𐑕𐑑𐑩𐑛, 𐑞𐑨𐑑 𐑢𐑫𐑛 𐑓𐑰𐑤 𐑤𐑲𐑒 \emph{𐑩𐑕𐑴𐑖𐑦𐑱𐑑𐑦𐑙} 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑢𐑦𐑞 𐑞𐑨𐑑…

·𐑴𐑯𐑤𐑦 𐑨𐑟 ·𐑣𐑨𐑮𐑦 𐑕𐑑𐑳𐑥𐑐𐑑 𐑬𐑑 𐑞 𐑚𐑨𐑒 𐑛𐑹, 𐑦𐑯𐑑𐑵 𐑞 𐑚𐑨𐑒 𐑜𐑸𐑛𐑩𐑯, 𐑛𐑦𐑛 𐑦𐑑 𐑩𐑒𐑻 𐑑 𐑣𐑦𐑥 𐑞𐑨𐑑 𐑦𐑓 𐑩𐑯 𐑬𐑤 \emph{𐑛𐑦𐑛} 𐑒𐑳𐑥 𐑛𐑬𐑯 𐑯 𐑕𐑯𐑨𐑗 𐑞 𐑤𐑧𐑑𐑼, 𐑣𐑰 𐑢𐑪𐑟 𐑜𐑴𐑦𐑙 𐑑 𐑣𐑨𐑝 𐑕𐑳𐑥 𐑑𐑮𐑳𐑚𐑩𐑤 𐑑𐑧𐑤𐑦𐑙 ·𐑛𐑨𐑛 𐑩𐑚𐑬𐑑 𐑦𐑑.

\emph{𐑚𐑳𐑑—𐑢𐑧𐑤—𐑞𐑨𐑑 𐑒𐑭𐑯𐑑 \emph{𐑮𐑾𐑤𐑦} 𐑣𐑨𐑐𐑩𐑯, 𐑒𐑨𐑯 𐑦𐑑? 𐑯𐑴 𐑥𐑨𐑑𐑼 𐑢𐑪𐑑 𐑥𐑲 𐑚𐑮𐑱𐑯 𐑕𐑰𐑥𐑟 𐑑 𐑚𐑦𐑤𐑰𐑝. 𐑦𐑓 𐑩𐑯 𐑬𐑤 𐑮𐑾𐑤𐑦 𐑒𐑳𐑥𐑟 𐑛𐑬𐑯 𐑯 𐑜𐑮𐑨𐑚𐑟 𐑞𐑦𐑕 𐑧𐑯𐑝𐑩𐑤𐑴𐑐, 𐑲'𐑥 𐑜𐑴𐑦𐑙 𐑑 𐑣𐑨𐑝 𐑢𐑳𐑮𐑦𐑟 𐑩 𐑤𐑪𐑑 𐑥𐑹 𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑 𐑞𐑨𐑯 𐑢𐑪𐑑 ·𐑛𐑨𐑛 𐑔𐑦𐑙𐑒𐑕.}

𐑣𐑨𐑮𐑦 𐑑𐑫𐑒 𐑩 𐑛𐑰𐑐 𐑚𐑮𐑧𐑔, 𐑯 𐑮𐑱𐑟𐑛 𐑞 𐑧𐑯𐑝𐑩𐑤𐑴𐑐 𐑦𐑯𐑑𐑵 𐑞 𐑺.

𐑣𐑰 𐑕𐑢𐑪𐑤𐑴𐑛.

𐑒𐑷𐑤𐑦𐑙 𐑬𐑑 \emph{·𐑤𐑧𐑑𐑼 𐑓 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕!} 𐑢𐑲𐑤 𐑣𐑴𐑤𐑛𐑦𐑙 𐑩𐑯 𐑧𐑯𐑝𐑩𐑤𐑴𐑐 𐑣𐑲 𐑦𐑯 𐑞 𐑺 𐑦𐑯 𐑞 𐑥𐑦𐑛𐑩𐑤 𐑝 𐑘𐑹 𐑴𐑯 𐑚𐑨𐑒 𐑜𐑸𐑛𐑩𐑯 𐑢𐑪𐑟…𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑐𐑮𐑦𐑑𐑦 𐑦𐑥𐑚𐑨𐑮𐑩𐑕𐑦𐑙, 𐑯𐑬 𐑞𐑨𐑑 𐑣𐑰 𐑔𐑷𐑑 𐑩𐑚𐑬𐑑 𐑦𐑑.

\emph{𐑯𐑴. 𐑲'𐑥 𐑚𐑧𐑑𐑼 𐑞𐑨𐑯 ·𐑛𐑨𐑛. 𐑲 𐑢𐑦𐑤 𐑿𐑟 𐑞 𐑕𐑲𐑩𐑯𐑑𐑦𐑓𐑦𐑒 𐑥𐑧𐑔𐑩𐑛 𐑰𐑝𐑩𐑯 𐑦𐑓 𐑦𐑑 𐑥𐑱𐑒𐑕 𐑥𐑰 𐑓𐑰𐑤 𐑕𐑑𐑿𐑐𐑦𐑛.}

“𐑤𐑧𐑑𐑼—” 𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑚𐑳𐑑 𐑦𐑑 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑒𐑱𐑥 𐑬𐑑 𐑨𐑟 𐑥𐑹 𐑝 𐑩 𐑢𐑦𐑕𐑐𐑼𐑛 𐑒𐑮𐑴𐑒.

𐑣𐑨𐑮𐑦 𐑕𐑑𐑰𐑤𐑛 𐑣𐑦𐑟 𐑢𐑦𐑤, 𐑯 𐑖𐑬𐑑𐑩𐑛 𐑦𐑯𐑑𐑵 𐑞 𐑧𐑥𐑐𐑑𐑦 𐑕𐑒𐑲, “\emph{𐑤𐑧𐑑𐑼 𐑓 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕! 𐑒𐑨𐑯 𐑲 𐑜𐑧𐑑 𐑩𐑯 𐑬𐑤?}”

“𐑣𐑨𐑮𐑦?” 𐑭𐑕𐑒𐑑 𐑩 𐑚𐑦𐑥𐑿𐑟𐑛 𐑢𐑫𐑥𐑩𐑯'𐑟 𐑝𐑶𐑕, 𐑢𐑳𐑯 𐑝 𐑞 𐑯𐑱𐑚𐑼𐑟.

𐑣𐑨𐑮𐑦 𐑐𐑫𐑤𐑛 𐑛𐑬𐑯 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛 𐑤𐑲𐑒 𐑦𐑑 𐑢𐑪𐑟 𐑪𐑯 𐑓𐑲𐑼 𐑯 𐑣𐑦𐑛 𐑞 𐑧𐑯𐑝𐑩𐑤𐑴𐑐 𐑚𐑦𐑣𐑲𐑯𐑛 𐑣𐑦𐑟 𐑚𐑨𐑒 𐑤𐑲𐑒 𐑦𐑑 𐑢𐑪𐑟 𐑛𐑮𐑳𐑜 𐑥𐑳𐑯𐑦. 𐑣𐑦𐑟 𐑣𐑴𐑤 𐑓𐑱𐑕 𐑢𐑪𐑟 𐑣𐑪𐑑 𐑢𐑦𐑞 𐑖𐑱𐑥.

𐑩𐑯 𐑴𐑤𐑛 𐑢𐑫𐑥𐑩𐑯'𐑟 𐑓𐑱𐑕 𐑐𐑽𐑛 𐑬𐑑 𐑓𐑮𐑪𐑥 𐑩𐑚𐑳𐑝 𐑞 𐑯𐑱𐑚𐑼𐑦𐑙 𐑓𐑧𐑯𐑕, 𐑜𐑮𐑦𐑟𐑩𐑤𐑛 𐑜𐑮𐑱 𐑣𐑺 𐑦𐑕𐑒𐑱𐑐𐑦𐑙 𐑓𐑮𐑪𐑥 𐑣𐑻 𐑣𐑺𐑯𐑧𐑑. ·𐑥𐑕𐑟~·𐑓𐑦𐑜, 𐑞 𐑩𐑒𐑱𐑠𐑩𐑯𐑩𐑤 𐑚𐑱𐑚𐑦𐑕𐑦𐑑𐑼. “𐑢𐑪𐑑 𐑸 𐑿 𐑛𐑵𐑦𐑙, ·𐑣𐑨𐑮𐑦?”

“𐑯𐑳𐑔𐑦𐑙,” 𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑦𐑯 𐑩 𐑕𐑑𐑮𐑨𐑙𐑜𐑩𐑤𐑛 𐑝𐑶𐑕. “𐑡𐑳𐑕𐑑—𐑑𐑧𐑕𐑑𐑦𐑙 𐑩 𐑮𐑾𐑤𐑦 𐑕𐑦𐑤𐑦 𐑔𐑽𐑦—”

“𐑛𐑦𐑛 𐑿 𐑜𐑧𐑑 𐑘𐑹 𐑩𐑒𐑕𐑧𐑐𐑑𐑩𐑯𐑕 𐑤𐑧𐑑𐑼 𐑓𐑮𐑪𐑥 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕?”

𐑣𐑨𐑮𐑦 𐑓𐑮𐑴𐑟 𐑦𐑯 𐑐𐑤𐑱𐑕.

“𐑘𐑧𐑕,” 𐑣𐑨𐑮𐑦'𐑟 𐑤𐑦𐑐𐑕 𐑕𐑧𐑛 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑢𐑲𐑤 𐑤𐑱𐑑𐑼. “𐑲 𐑜𐑪𐑑 𐑩 𐑤𐑧𐑑𐑼 𐑓𐑮𐑪𐑥 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕. 𐑞𐑱 𐑕𐑱 𐑞𐑱 𐑢𐑪𐑯𐑑 𐑥𐑲 𐑬𐑤 𐑚𐑲 𐑞 31𐑕𐑑 𐑝 𐑡𐑫𐑤𐑲, 𐑚𐑳𐑑—”

“𐑚𐑳𐑑 𐑿 𐑛𐑴𐑯𐑑 \emph{𐑣𐑨𐑝} 𐑩𐑯 𐑬𐑤. 𐑐𐑫𐑼 𐑛𐑽! 𐑲 𐑒𐑭𐑯𐑑 𐑦𐑥𐑨𐑡𐑦𐑯 \emph{𐑢𐑪𐑑} 𐑕𐑳𐑥𐑢𐑳𐑯 𐑥𐑳𐑕𐑑 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑔𐑦𐑙𐑒𐑦𐑙, 𐑕𐑧𐑯𐑛𐑦𐑙 𐑿 𐑡𐑳𐑕𐑑 𐑞 𐑕𐑑𐑨𐑯𐑛𐑼𐑛 𐑤𐑧𐑑𐑼.”

𐑩 𐑮𐑦𐑙𐑒𐑩𐑤𐑛 𐑸𐑥 𐑕𐑑𐑮𐑧𐑗𐑑 𐑬𐑑 𐑴𐑝𐑼 𐑞 𐑓𐑧𐑯𐑕, 𐑯 𐑴𐑐𐑩𐑯𐑛 𐑩𐑯 𐑦𐑒𐑕𐑐𐑧𐑒𐑑𐑩𐑯𐑑 𐑣𐑨𐑯𐑛. 𐑣𐑸𐑛𐑤𐑦 𐑰𐑝𐑩𐑯 𐑔𐑦𐑙𐑒𐑦𐑙 𐑨𐑑 𐑞𐑦𐑕 𐑐𐑶𐑯𐑑, ·𐑣𐑨𐑮𐑦 𐑜𐑱𐑝 𐑴𐑝𐑼 𐑣𐑦𐑟 𐑧𐑯𐑝𐑩𐑤𐑴𐑐.

“𐑡𐑳𐑕𐑑 𐑤𐑰𐑝 𐑦𐑑 𐑑 𐑥𐑰, 𐑛𐑽,” 𐑕𐑧𐑛 ·𐑥𐑕𐑟~·𐑓𐑦𐑜, “𐑯 𐑦𐑯 𐑩 𐑡𐑦𐑓𐑦 𐑹 𐑑𐑵 𐑲'𐑤 𐑣𐑨𐑝 𐑕𐑳𐑥𐑢𐑳𐑯 𐑴𐑝𐑼.”

𐑯 𐑣𐑻 𐑓𐑱𐑕 𐑛𐑦𐑕𐑩𐑐𐑽𐑛 𐑓𐑮𐑪𐑥 𐑴𐑝𐑼 𐑞 𐑓𐑧𐑯𐑕.

𐑞𐑺 𐑢𐑪𐑟 𐑩 𐑤𐑪𐑙 𐑕𐑲𐑤𐑩𐑯𐑕 𐑦𐑯 𐑞 𐑜𐑸𐑛𐑩𐑯.

𐑞𐑧𐑯 𐑩 𐑚𐑶'𐑟 𐑝𐑶𐑕 𐑕𐑧𐑛, 𐑒𐑭𐑥𐑤𐑦 𐑯 𐑒𐑢𐑲𐑩𐑑𐑤𐑦, “𐑢𐑪𐑑.”
