\chapter{𐑮𐑦𐑕𐑦𐑐𐑮𐑩𐑒𐑱𐑖𐑩𐑯}

\begin{chapterOpeningAuthorNote}
·𐑢𐑴. 𐑩 𐑕𐑐𐑴𐑒𐑕𐑥𐑩𐑯 𐑓 ·𐑮𐑴𐑤𐑦𐑙'𐑟 𐑤𐑦𐑑𐑼𐑼𐑦 𐑱𐑡𐑩𐑯𐑑 𐑕𐑧𐑛 𐑞𐑨𐑑 ·𐑮𐑴𐑤𐑦𐑙 𐑦𐑟 𐑴𐑒𐑱 𐑢𐑦𐑞 𐑞 𐑦𐑜𐑟𐑦𐑕𐑑𐑩𐑯𐑕 𐑝 𐑓𐑨𐑯𐑓𐑦𐑒𐑖𐑩𐑯 𐑨𐑟 𐑤𐑪𐑙 𐑨𐑟 𐑯𐑴 𐑢𐑳𐑯 𐑗𐑸𐑡𐑩𐑟 𐑓 𐑦𐑑 𐑯 𐑧𐑝𐑮𐑦𐑢𐑳𐑯'𐑟 𐑒𐑤𐑽 𐑞𐑨𐑑 𐑞 𐑼𐑦𐑡𐑦𐑯𐑩𐑤 𐑒𐑪𐑐𐑦𐑮𐑲𐑑𐑕 𐑚𐑦𐑤𐑪𐑙 𐑑 𐑣𐑻? 𐑞𐑨𐑑'𐑕 𐑮𐑾𐑤𐑦 𐑒𐑵𐑤 𐑝 𐑣𐑻. 𐑕𐑴 𐑔𐑨𐑙𐑒 𐑿, ·𐑡𐑒𐑮, 𐑯 𐑞𐑲𐑯 𐑦𐑟 𐑞 𐑒𐑦𐑙𐑛𐑩𐑥!

𐑲 𐑓𐑰𐑤 𐑞 𐑯𐑰𐑛 𐑑 𐑛𐑦𐑕𐑒𐑤𐑱𐑥 𐑞𐑨𐑑 𐑕𐑻𐑑𐑩𐑯 𐑐𐑸𐑑𐑕 𐑝 𐑞𐑦𐑕 𐑗𐑨𐑐𐑑𐑼 𐑸 𐑯𐑪𐑑 𐑥𐑧𐑯𐑑 𐑨𐑟 “𐑚𐑨𐑖𐑦𐑙”. 𐑦𐑑'𐑕 𐑯𐑪𐑑 𐑞𐑨𐑑 𐑲 𐑣𐑨𐑝 𐑩 𐑜𐑮𐑳𐑡, 𐑞 𐑕𐑑𐑹𐑦 𐑡𐑳𐑕𐑑 𐑮𐑲𐑑𐑕 𐑦𐑑𐑕𐑧𐑤𐑓 𐑯 𐑢𐑳𐑯𐑕 𐑿 𐑕𐑑𐑸𐑑 𐑛𐑮𐑪𐑐𐑦𐑙 𐑨𐑯𐑝𐑦𐑤𐑟 𐑪𐑯 𐑩 𐑒𐑨𐑮𐑩𐑒𐑑𐑼 𐑦𐑑'𐑕 𐑣𐑸𐑛 𐑑 𐑕𐑑𐑪𐑐.

𐑩 𐑓𐑿 𐑮𐑦𐑝𐑿𐑼𐑟 𐑣𐑨𐑝 𐑭𐑕𐑒𐑑 𐑢𐑧𐑞𐑼 𐑞 𐑕𐑲𐑩𐑯𐑕 𐑦𐑯 𐑞𐑦𐑕 𐑕𐑑𐑹𐑦 𐑦𐑟 𐑮𐑾𐑤 𐑹 𐑥𐑱𐑛 𐑳𐑐. 𐑘𐑧𐑕, 𐑦𐑑 𐑦𐑟 𐑮𐑾𐑤, 𐑯 𐑦𐑓 𐑿 𐑤𐑫𐑒 𐑨𐑑 𐑥𐑲 𐑐𐑮𐑴𐑓𐑲𐑤, 𐑿'𐑤 𐑕𐑰 𐑩 𐑤𐑦𐑙𐑒 𐑑 𐑩 𐑕𐑻𐑑𐑩𐑯 𐑯𐑪𐑯𐑓𐑦𐑒𐑖𐑩𐑯 𐑕𐑲𐑑 𐑞𐑨𐑑 𐑢𐑦𐑤 𐑑𐑰𐑗 𐑿 𐑐𐑮𐑦𐑑𐑦 𐑥𐑳𐑗 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 ·𐑣𐑨𐑮𐑦 ·𐑡𐑱𐑥𐑟 ·𐑐𐑪𐑑𐑼-·𐑧𐑝𐑩𐑯𐑟-·𐑝𐑧𐑮𐑟 𐑯𐑴𐑟 \emph{𐑯 𐑞𐑧𐑯 𐑕𐑳𐑥}.

𐑔𐑨𐑙𐑒 𐑿 𐑝𐑧𐑮𐑦 𐑥𐑳𐑗 𐑑 \emph{𐑷𐑤} 𐑥𐑲 𐑮𐑦𐑝𐑿𐑼𐑟. (𐑦𐑕𐑐𐑧𐑖𐑩𐑤𐑦 ·𐑛𐑸𐑒𐑨𐑯𐑛𐑩𐑕 𐑪𐑯 ·𐑝𐑲𐑮𐑦𐑛𐑾𐑯 ·𐑛𐑮𐑰𐑥𐑟, 𐑓 𐑞 𐑕𐑼𐑐𐑮𐑲𐑟𐑦𐑙𐑤𐑦 𐑦𐑯𐑕𐑐𐑲𐑼𐑦𐑙 𐑒𐑪𐑥𐑧𐑯𐑑 “·𐑤𐑳𐑙𐑟 𐑯 𐑑𐑰 𐑸 𐑯𐑪𐑑 𐑥𐑧𐑯𐑑 𐑑 𐑦𐑯𐑑𐑼𐑨𐑒𐑑”.)
\end{chapterOpeningAuthorNote}
\begin{chapterOpeningQuote}
𐑘𐑹 𐑛𐑨𐑛 𐑦𐑟 𐑷𐑤𐑥𐑴𐑕𐑑 𐑨𐑟 𐑷𐑕𐑩𐑥 𐑨𐑟 𐑥𐑲 𐑛𐑨𐑛.
\end{chapterOpeningQuote}

\lettrine{𐑐}{𐑩𐑑𐑿𐑯𐑾} ·𐑧𐑝𐑩𐑯𐑟-·𐑝𐑧𐑮𐑟'𐑩𐑟 𐑤𐑦𐑐𐑕 𐑢𐑻 𐑑𐑮𐑧𐑥𐑚𐑩𐑤𐑦𐑙 𐑯 𐑣𐑻 𐑲𐑟 𐑢𐑻 𐑑𐑽𐑦𐑙 𐑳𐑐 𐑨𐑟 ·𐑣𐑨𐑮𐑦 𐑣𐑳𐑜𐑛 𐑣𐑻 𐑥𐑦𐑛𐑕𐑧𐑒𐑖𐑩𐑯 𐑪𐑯 ·𐑐𐑤𐑨𐑑𐑓𐑹𐑥 ·𐑯𐑲𐑯 𐑝 ·𐑒𐑦𐑙'𐑟 ·𐑒𐑮𐑪𐑕 ·𐑕𐑑𐑱𐑖𐑩𐑯. “𐑸 𐑿 𐑖𐑫𐑼 𐑿 𐑛𐑴𐑯𐑑 𐑢𐑪𐑯𐑑 𐑥𐑰 𐑑 𐑒𐑳𐑥 𐑢𐑦𐑞 𐑿, ·𐑣𐑨𐑮𐑦?”

·𐑣𐑨𐑮𐑦 𐑜𐑤𐑭𐑯𐑕𐑑 𐑴𐑝𐑼 𐑑 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 ·𐑥𐑲𐑒𐑩𐑤 ·𐑝𐑧𐑮𐑟-·𐑧𐑝𐑩𐑯𐑟, 𐑣𐑵 𐑢𐑪𐑟 𐑤𐑫𐑒𐑦𐑙 𐑕𐑑𐑧𐑮𐑦𐑴𐑑𐑦𐑐𐑦𐑒𐑤𐑦 𐑕𐑑𐑻𐑯-𐑚𐑳𐑑-𐑐𐑮𐑬𐑛, 𐑯 𐑞𐑧𐑯 𐑚𐑨𐑒 𐑑 𐑣𐑦𐑟 𐑥𐑳𐑞𐑼, 𐑣𐑵 𐑮𐑾𐑤𐑦 𐑛𐑦𐑛 𐑤𐑫𐑒 𐑮𐑭𐑞𐑼…𐑛𐑦𐑕𐑒𐑩𐑥𐑐𐑴𐑟𐑛. “𐑥𐑳𐑥, 𐑲 𐑯𐑴 𐑿 𐑛𐑴𐑯𐑑 𐑤𐑲𐑒 𐑞 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑢𐑻𐑤𐑛 𐑝𐑧𐑮𐑦 𐑥𐑳𐑗. 𐑿 𐑛𐑴𐑯𐑑 𐑣𐑨𐑓 𐑑 𐑒𐑳𐑥 𐑢𐑦𐑞. 𐑲 𐑥𐑰𐑯 𐑦𐑑.”

·𐑐𐑩𐑑𐑿𐑯𐑾 𐑢𐑦𐑯𐑕𐑑. “·𐑣𐑨𐑮𐑦, 𐑿 𐑖𐑫𐑛𐑩𐑯𐑑 𐑢𐑳𐑮𐑦 𐑩𐑚𐑬𐑑 𐑥𐑰, 𐑲'𐑥 𐑘𐑹 𐑥𐑳𐑞𐑼 𐑯 𐑦𐑓 𐑿 𐑯𐑰𐑛 𐑕𐑳𐑥𐑢𐑳𐑯 𐑢𐑦𐑞 𐑿—”

“𐑥𐑳𐑥, 𐑲'𐑥 𐑜𐑴𐑦𐑙 𐑑 𐑚𐑰 𐑪𐑯 𐑥𐑲 𐑴𐑯 𐑨𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 𐑓 \emph{𐑥𐑳𐑯𐑔𐑕} 𐑯 \emph{𐑥𐑳𐑯𐑔𐑕}. 𐑦𐑓 𐑲 𐑒𐑭𐑯𐑑 𐑥𐑨𐑯𐑦𐑡 𐑩 𐑑𐑮𐑱𐑯 𐑐𐑤𐑨𐑑𐑓𐑹𐑥 𐑩𐑤𐑴𐑯, 𐑚𐑧𐑑𐑼 𐑑 𐑓𐑲𐑯𐑛 𐑬𐑑 𐑕𐑵𐑯𐑼 𐑮𐑭𐑞𐑼 𐑞𐑨𐑯 𐑤𐑱𐑑𐑼 𐑕𐑴 𐑢𐑰 𐑒𐑨𐑯 𐑩𐑚𐑹𐑑.” 𐑣𐑰 𐑤𐑴𐑼𐑛 𐑣𐑦𐑟 𐑝𐑶𐑕 𐑑 𐑩 𐑢𐑦𐑕𐑐𐑼. “𐑚𐑦𐑕𐑲𐑛𐑟, ·𐑥𐑳𐑥, 𐑞𐑱 𐑷𐑤 𐑤𐑳𐑝 𐑥𐑰 𐑴𐑝𐑼 𐑞𐑺. 𐑦𐑓 𐑲 𐑣𐑨𐑝 𐑧𐑯𐑦 𐑐𐑮𐑪𐑚𐑤𐑩𐑥𐑟, 𐑷𐑤 𐑲 𐑯𐑰𐑛 𐑑 𐑛𐑵 𐑦𐑟 𐑑𐑱𐑒 𐑪𐑓 𐑥𐑲 𐑕𐑢𐑧𐑑𐑚𐑨𐑯𐑛,” ·𐑣𐑨𐑮𐑦 𐑑𐑨𐑐𐑑 𐑞 𐑧𐑒𐑕𐑼𐑕𐑲𐑟 𐑚𐑨𐑯𐑛 𐑒𐑳𐑝𐑼𐑦𐑙 𐑣𐑦𐑟 𐑕𐑒𐑸, “𐑯 𐑲'𐑤 𐑣𐑨𐑝 \emph{𐑢𐑱} 𐑥𐑹 𐑣𐑧𐑤𐑐 𐑞𐑨𐑯 𐑲 𐑒𐑨𐑯 𐑣𐑨𐑯𐑛𐑩𐑤.”

“𐑴, ·𐑣𐑨𐑮𐑦,” ·𐑐𐑩𐑑𐑿𐑯𐑾 𐑢𐑦𐑕𐑐𐑼𐑛. 𐑖𐑰 𐑯𐑧𐑤𐑑 𐑛𐑬𐑯 𐑯 𐑣𐑳𐑜𐑛 𐑣𐑦𐑥 𐑣𐑸𐑛, 𐑓𐑱𐑕 𐑑 𐑓𐑱𐑕, 𐑞𐑺 𐑗𐑰𐑒𐑕 𐑮𐑧𐑕𐑑𐑦𐑙 𐑩𐑜𐑱𐑯𐑕𐑑 𐑰𐑗 𐑳𐑞𐑼. ·𐑣𐑨𐑮𐑦 𐑒𐑫𐑛 𐑓𐑰𐑤 𐑣𐑻 𐑮𐑨𐑜𐑩𐑛 𐑚𐑮𐑰𐑞𐑦𐑙, 𐑯 𐑞𐑧𐑯 𐑣𐑰 𐑣𐑻𐑛 𐑩 𐑥𐑳𐑓𐑩𐑤𐑛 𐑕𐑪𐑚 𐑦𐑕𐑒𐑱𐑐. “𐑴, ·𐑣𐑨𐑮𐑦, 𐑲 𐑛𐑵 𐑤𐑳𐑝 𐑿, 𐑷𐑤𐑢𐑱𐑟 𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑞𐑨𐑑.”

\emph{𐑦𐑑'𐑕 𐑤𐑲𐑒 𐑖𐑰'𐑟 𐑩𐑓𐑮𐑱𐑛 𐑖𐑰'𐑤 𐑯𐑧𐑝𐑼 𐑕𐑰 𐑥𐑰 𐑩𐑜𐑱𐑯,} 𐑞 𐑔𐑷𐑑 𐑐𐑪𐑐𐑑 𐑦𐑯𐑑𐑵 ·𐑣𐑨𐑮𐑦'𐑟 𐑣𐑧𐑛. 𐑣𐑰 𐑯𐑿 𐑞 𐑔𐑷𐑑 𐑢𐑪𐑟 𐑑𐑮𐑵 𐑚𐑳𐑑 𐑣𐑰 𐑛𐑦𐑛𐑩𐑯𐑑 𐑯𐑴 𐑢𐑲 ·𐑥𐑳𐑥 𐑢𐑪𐑟 𐑕𐑴 𐑩𐑓𐑮𐑱𐑛.

𐑕𐑴 𐑣𐑰 𐑥𐑱𐑛 𐑩 𐑜𐑧𐑕. “𐑥𐑳𐑥, 𐑿 𐑯𐑴 𐑞𐑨𐑑 𐑲'𐑥 𐑯𐑪𐑑 𐑜𐑴𐑦𐑙 𐑑 𐑑𐑻𐑯 𐑦𐑯𐑑𐑵 𐑘𐑹 𐑕𐑦𐑕𐑑𐑼 𐑡𐑳𐑕𐑑 𐑚𐑦𐑒𐑪𐑟 𐑲'𐑥 𐑤𐑻𐑯𐑦𐑙 𐑥𐑨𐑡𐑦𐑒, 𐑮𐑲𐑑? 𐑲'𐑤 𐑛𐑵 𐑧𐑯𐑦 𐑥𐑨𐑡𐑦𐑒 𐑿 𐑭𐑕𐑒 𐑓—𐑦𐑓 𐑲 𐑒𐑨𐑯, 𐑲 𐑥𐑰𐑯—𐑹 𐑦𐑓 𐑿 𐑢𐑪𐑯𐑑 𐑥𐑰 \emph{𐑯𐑪𐑑} 𐑑 𐑿𐑟 𐑧𐑯𐑦 𐑥𐑨𐑡𐑦𐑒 𐑼𐑬𐑯𐑛 𐑞 𐑣𐑬𐑕, 𐑲'𐑤 𐑛𐑵 𐑞𐑨𐑑 𐑑𐑵, 𐑲 𐑐𐑮𐑪𐑥𐑦𐑕 𐑲'𐑤 𐑯𐑧𐑝𐑼 𐑤𐑧𐑑 𐑥𐑨𐑡𐑦𐑒 𐑒𐑳𐑥 𐑚𐑦𐑑𐑢𐑰𐑯 𐑳𐑕—”

𐑩 𐑑𐑲𐑑 𐑣𐑳𐑜 𐑒𐑳𐑑 𐑪𐑓 𐑣𐑦𐑟 𐑢𐑻𐑛𐑟. “𐑿 𐑣𐑨𐑝 𐑩 𐑜𐑫𐑛 𐑣𐑸𐑑,” 𐑣𐑦𐑟 𐑥𐑳𐑞𐑼 𐑢𐑦𐑕𐑐𐑼𐑛 𐑦𐑯𐑑𐑵 𐑣𐑦𐑟 𐑽. “𐑩 𐑝𐑧𐑮𐑦 𐑜𐑫𐑛 𐑣𐑸𐑑, 𐑥𐑲 𐑕𐑳𐑯.”

·𐑣𐑨𐑮𐑦 𐑗𐑴𐑒𐑑 𐑳𐑐 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑩 𐑤𐑦𐑑𐑩𐑤, 𐑞𐑧𐑯.

𐑣𐑦𐑟 𐑥𐑳𐑞𐑼 𐑮𐑦𐑤𐑰𐑕𐑑 𐑣𐑦𐑥, 𐑯 𐑕𐑑𐑫𐑛 𐑳𐑐. 𐑖𐑰 𐑑𐑫𐑒 𐑩 𐑣𐑨𐑙𐑒𐑼𐑗𐑦𐑓 𐑬𐑑 𐑝 𐑣𐑻 𐑣𐑨𐑯𐑛𐑚𐑨𐑜, 𐑯 𐑢𐑦𐑞 𐑩 𐑑𐑮𐑧𐑥𐑚𐑩𐑤𐑦𐑙 𐑣𐑨𐑯𐑛 𐑛𐑨𐑚𐑛 𐑨𐑑 𐑞 𐑮𐑳𐑯𐑦𐑙 𐑥𐑱𐑒-𐑳𐑐 𐑼𐑬𐑯𐑛 𐑣𐑻 𐑲𐑟.

𐑞𐑺 𐑢𐑻 𐑯𐑴 𐑒𐑢𐑧𐑕𐑗𐑩𐑯𐑟 𐑩𐑚𐑬𐑑 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑩𐑒𐑳𐑥𐑐𐑩𐑯𐑦𐑦𐑙 𐑣𐑦𐑥 𐑑 𐑞 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 𐑕𐑲𐑛 𐑝 ·𐑒𐑦𐑙'𐑟 ·𐑒𐑮𐑪𐑕 ·𐑕𐑑𐑱𐑖𐑩𐑯. ·𐑛𐑨𐑛 𐑣𐑨𐑛 𐑑𐑮𐑳𐑚𐑩𐑤 𐑡𐑳𐑕𐑑 𐑤𐑫𐑒𐑦𐑙 𐑨𐑑 ·𐑣𐑨𐑮𐑦'𐑟 𐑑𐑮𐑳𐑙𐑒 𐑛𐑦𐑮𐑧𐑒𐑑𐑤𐑦. ·𐑥𐑨𐑡𐑦𐑒 𐑮𐑨𐑯 𐑦𐑯 𐑓𐑨𐑥𐑤𐑦𐑟, 𐑯 ·𐑥𐑲𐑒𐑩𐑤 ·𐑝𐑧𐑮𐑟-·𐑧𐑝𐑩𐑯𐑟 𐑒𐑫𐑛𐑩𐑯𐑑 𐑰𐑝𐑩𐑯 𐑢𐑷𐑒.

𐑕𐑴 𐑦𐑯𐑕𐑑𐑧𐑛 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑡𐑳𐑕𐑑 𐑒𐑤𐑽𐑛 𐑣𐑦𐑟 𐑔𐑮𐑴𐑑. “𐑜𐑫𐑛 𐑤𐑳𐑒 𐑨𐑑 𐑕𐑒𐑵𐑤, ·𐑣𐑨𐑮𐑦,” 𐑣𐑰 𐑕𐑧𐑛. “𐑛𐑵 𐑿 𐑔𐑦𐑙𐑒 𐑲 𐑚𐑷𐑑 𐑿 𐑦𐑯𐑳𐑓 𐑚𐑫𐑒𐑕?”

·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑦𐑒𐑕𐑐𐑤𐑱𐑯𐑛 𐑑 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑩𐑚𐑬𐑑 𐑣𐑬 𐑣𐑰 𐑔𐑷𐑑 𐑞𐑦𐑕 𐑥𐑲𐑑 𐑚𐑰 𐑣𐑦𐑟 𐑚𐑦𐑜 𐑗𐑭𐑯𐑕 𐑑 𐑛𐑵 𐑕𐑳𐑥𐑔𐑦𐑙 𐑮𐑾𐑤𐑦 𐑮𐑧𐑝𐑩𐑤𐑵𐑖𐑩𐑯𐑼𐑦 𐑯 𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑, 𐑯 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑝𐑧𐑮𐑟-·𐑧𐑝𐑩𐑯𐑟 𐑣𐑨𐑛 𐑯𐑪𐑛𐑩𐑛 𐑯 𐑛𐑳𐑥𐑐𐑑 𐑣𐑦𐑟 𐑦𐑒𐑕𐑑𐑮𐑰𐑥𐑤𐑦 𐑚𐑦𐑟𐑦 𐑖𐑧𐑡𐑵𐑤 𐑓 𐑑𐑵 𐑕𐑪𐑤𐑦𐑛 𐑛𐑱𐑟 𐑦𐑯 𐑹𐑛𐑼 𐑑 𐑜𐑴 𐑪𐑯 𐑞 ·𐑜𐑮𐑱𐑑𐑩𐑕𐑑 ·𐑕𐑱𐑒𐑪𐑯𐑛-𐑣𐑨𐑯𐑛 ·𐑚𐑫𐑒𐑖𐑪𐑐 ·𐑮𐑱𐑛 ·𐑧𐑝𐑼, 𐑢𐑦𐑗 𐑣𐑨𐑛 𐑒𐑳𐑝𐑼𐑛 𐑓𐑹 𐑕𐑦𐑑𐑦𐑟 𐑯 𐑐𐑮𐑩𐑛𐑿𐑕𐑑 \emph{𐑔𐑻𐑑𐑦} 𐑚𐑪𐑒𐑕𐑩𐑟 𐑝 𐑕𐑲𐑩𐑯𐑕 𐑚𐑫𐑒𐑕 𐑯𐑬 𐑕𐑦𐑑𐑦𐑙 𐑦𐑯 𐑞 𐑒𐑨𐑝𐑼𐑯 𐑤𐑧𐑝𐑩𐑤 𐑝 ·𐑣𐑨𐑮𐑦'𐑟 𐑑𐑮𐑳𐑙𐑒. 𐑥𐑴𐑕𐑑 𐑝 𐑞 𐑚𐑫𐑒𐑕 𐑣𐑨𐑛 𐑜𐑪𐑯 𐑓 𐑩 𐑐𐑬𐑯𐑛 𐑹 𐑑𐑵, 𐑚𐑳𐑑 𐑕𐑳𐑥 𐑝 𐑞𐑧𐑥 𐑛𐑧𐑓𐑦𐑯𐑦𐑑𐑤𐑦 \emph{𐑣𐑨𐑛𐑩𐑯𐑑}, 𐑤𐑲𐑒 𐑞 𐑝𐑧𐑮𐑦 𐑤𐑱𐑑𐑩𐑕𐑑 \emph{·𐑣𐑨𐑯𐑛𐑚𐑫𐑒 𐑝 ·𐑒𐑧𐑥𐑦𐑕𐑑𐑮𐑦 𐑯 ·𐑓𐑦𐑟𐑦𐑒𐑕} 𐑹 𐑞 𐑒𐑩𐑥𐑐𐑤𐑰𐑑 1972 𐑕𐑧𐑑 𐑝 𐑞 \emph{·𐑦𐑯𐑕𐑲𐑒𐑤𐑩𐑐𐑰𐑛𐑾 ·𐑚𐑮𐑦𐑑𐑨𐑯𐑦𐑒𐑩.} 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑣𐑨𐑛 𐑑𐑮𐑲𐑛 𐑑 𐑚𐑤𐑪𐑒 ·𐑣𐑨𐑮𐑦 𐑪𐑓 𐑓𐑮𐑪𐑥 𐑕𐑰𐑦𐑙 𐑞 𐑑𐑦𐑤 𐑛𐑦𐑕𐑐𐑤𐑱𐑟 𐑚𐑳𐑑 ·𐑣𐑨𐑮𐑦 𐑓𐑦𐑜𐑼𐑛 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑥𐑳𐑕𐑑 𐑣𐑨𐑝 𐑕𐑐𐑧𐑯𐑑 \emph{𐑨𐑑 𐑤𐑰𐑕𐑑} 𐑩 𐑔𐑬𐑟𐑩𐑯𐑛 𐑐𐑬𐑯𐑛𐑟. ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑕𐑧𐑛 𐑑 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑞𐑨𐑑 𐑣𐑰 𐑢𐑫𐑛 𐑐𐑱 𐑣𐑦𐑥 𐑚𐑨𐑒 𐑨𐑟 𐑕𐑵𐑯 𐑨𐑟 𐑣𐑰 𐑓𐑦𐑜𐑼𐑛 𐑬𐑑 𐑣𐑬 𐑑 𐑒𐑩𐑯𐑝𐑻𐑑 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑜𐑴𐑤𐑛 𐑦𐑯𐑑𐑵 ·𐑥𐑳𐑜𐑩𐑤 𐑥𐑳𐑯𐑦, 𐑯 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑣𐑨𐑛 𐑑𐑴𐑤𐑛 𐑣𐑦𐑥 𐑑 𐑜𐑴 𐑚𐑶𐑤 𐑣𐑦𐑟 𐑣𐑧𐑛.

𐑯 𐑞𐑧𐑯 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑣𐑨𐑛 𐑭𐑕𐑒𐑑 𐑣𐑦𐑥: \emph{𐑛𐑵 𐑿 𐑔𐑦𐑙𐑒 𐑲 𐑚𐑷𐑑 𐑿 𐑦𐑯𐑳𐑓 𐑚𐑫𐑒𐑕?} 𐑦𐑑 𐑢𐑪𐑟 𐑒𐑢𐑲𐑑 𐑒𐑤𐑽 𐑢𐑪𐑑 𐑭𐑯𐑕𐑼 ·𐑛𐑨𐑛 𐑢𐑪𐑯𐑑𐑩𐑛 𐑑 𐑣𐑽.

𐑣𐑨𐑮𐑦'𐑟 𐑔𐑮𐑴𐑑 𐑢𐑪𐑟 𐑣𐑹𐑕, 𐑓 𐑕𐑳𐑥 𐑮𐑰𐑟𐑩𐑯. “𐑿 𐑒𐑨𐑯 𐑯𐑧𐑝𐑼 𐑣𐑨𐑝 𐑦𐑯𐑳𐑓 𐑚𐑫𐑒𐑕,” 𐑣𐑰 𐑮𐑦𐑕𐑲𐑑𐑩𐑛 𐑞 ·𐑝𐑧𐑮𐑟 𐑓𐑨𐑥𐑤𐑦 𐑥𐑪𐑑𐑴, 𐑯 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑯𐑧𐑤𐑑 𐑛𐑬𐑯 𐑯 𐑜𐑱𐑝 𐑣𐑦𐑥 𐑩 𐑒𐑢𐑦𐑒, 𐑓𐑻𐑥 𐑦𐑥𐑚𐑮𐑱𐑕. “𐑚𐑳𐑑 𐑿 \emph{𐑕𐑻𐑑𐑩𐑯𐑤𐑦} 𐑑𐑮𐑲𐑛,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑯 𐑓𐑧𐑤𐑑 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑗𐑴𐑒𐑦𐑙 𐑳𐑐 𐑩𐑜𐑱𐑯. “𐑦𐑑 𐑢𐑪𐑟 𐑩 𐑮𐑾𐑤𐑦, 𐑮𐑾𐑤𐑦, \emph{𐑮𐑾𐑤𐑦} 𐑜𐑫𐑛 𐑑𐑮𐑲.”

𐑣𐑦𐑟 ·𐑛𐑨𐑛 𐑕𐑑𐑮𐑱𐑑𐑩𐑯𐑛. “𐑕𐑴…” 𐑣𐑰 𐑕𐑧𐑛. “𐑛𐑵 \emph{𐑿} 𐑕𐑰 𐑩 ·𐑐𐑤𐑨𐑑𐑓𐑹𐑥 ·𐑯𐑲𐑯-𐑯-·𐑔𐑮𐑰-·𐑒𐑢𐑹𐑑𐑼𐑟?”

𐑒𐑦𐑙'𐑟 ·𐑒𐑮𐑪𐑕 ·𐑕𐑑𐑱𐑖𐑩𐑯 𐑢𐑪𐑟 𐑣𐑿𐑡 𐑯 𐑚𐑦𐑟𐑦, 𐑢𐑦𐑞 𐑢𐑷𐑤𐑟 𐑯 𐑓𐑤𐑹𐑟 𐑐𐑱𐑝𐑛 𐑢𐑦𐑞 𐑹𐑛𐑦𐑯𐑼𐑦 𐑛𐑻𐑑-𐑕𐑑𐑱𐑯𐑛 𐑑𐑲𐑤𐑟. 𐑦𐑑 𐑢𐑪𐑟 𐑓𐑫𐑤 𐑝 𐑹𐑛𐑦𐑯𐑼𐑦 𐑐𐑰𐑐𐑩𐑤 𐑣𐑳𐑮𐑦𐑦𐑙 𐑩𐑚𐑬𐑑 𐑞𐑺 𐑹𐑛𐑦𐑯𐑼𐑦 𐑚𐑦𐑟𐑯𐑩𐑕, 𐑣𐑨𐑝𐑦𐑙 𐑹𐑛𐑦𐑯𐑼𐑦 𐑒𐑪𐑯𐑝𐑼𐑕𐑱𐑖𐑩𐑯𐑟 𐑢𐑦𐑗 𐑡𐑧𐑯𐑼𐑱𐑑𐑩𐑛 𐑤𐑪𐑑𐑕 𐑯 𐑤𐑪𐑑𐑕 𐑝 𐑹𐑛𐑦𐑯𐑼𐑦 𐑯𐑶𐑟. 𐑒𐑦𐑙'𐑟 ·𐑒𐑮𐑪𐑕 ·𐑕𐑑𐑱𐑖𐑩𐑯 𐑣𐑨𐑛 𐑩 ·𐑐𐑤𐑨𐑑𐑓𐑹𐑥 ·𐑯𐑲𐑯 (𐑢𐑦𐑗 𐑞𐑱 𐑢𐑻 𐑕𐑑𐑨𐑯𐑛𐑦𐑙 𐑪𐑯) 𐑯 𐑩 ·𐑐𐑤𐑨𐑑𐑓𐑹𐑥 ·𐑑𐑧𐑯 (𐑮𐑲𐑑 𐑯𐑧𐑒𐑕𐑑 𐑑 𐑦𐑑) 𐑚𐑳𐑑 𐑞𐑺 𐑢𐑪𐑟 𐑯𐑳𐑔𐑦𐑙 𐑚𐑦𐑑𐑢𐑰𐑯 ·𐑐𐑤𐑨𐑑𐑓𐑹𐑥 ·𐑯𐑲𐑯 𐑯 ·𐑐𐑤𐑨𐑑𐑓𐑹𐑥 ·𐑑𐑧𐑯 𐑦𐑒𐑕𐑧𐑐𐑑 𐑩 𐑔𐑦𐑯, 𐑳𐑯𐑐𐑮𐑪𐑥𐑦𐑕𐑦𐑙 𐑚𐑨𐑮𐑽 𐑢𐑷𐑤. 𐑩 𐑜𐑮𐑱𐑑 𐑕𐑒𐑲𐑤𐑲𐑑 𐑴𐑝𐑼𐑣𐑧𐑛 𐑤𐑧𐑑 𐑦𐑯 𐑐𐑤𐑧𐑯𐑑𐑦 𐑝 𐑤𐑲𐑑 𐑑 𐑦𐑤𐑵𐑥𐑦𐑯𐑱𐑑 𐑞 𐑑𐑴𐑑𐑩𐑤 𐑤𐑨𐑒 𐑢𐑪𐑑𐑕𐑴𐑧𐑝𐑼 𐑝 𐑧𐑯𐑦 ·𐑐𐑤𐑨𐑑𐑓𐑹𐑥 ·𐑯𐑲𐑯-𐑯-·𐑔𐑮𐑰-·𐑒𐑢𐑹𐑑𐑼𐑟.

·𐑣𐑨𐑮𐑦 𐑕𐑑𐑺𐑛 𐑼𐑬𐑯𐑛 𐑩𐑯𐑑𐑦𐑤 𐑣𐑦𐑟 𐑲𐑟 𐑢𐑷𐑑𐑼𐑛, 𐑔𐑦𐑙𐑒𐑦𐑙, \emph{𐑒𐑳𐑥 𐑪𐑯, 𐑥𐑱𐑡-𐑕𐑲𐑑, 𐑒𐑳𐑥 𐑪𐑯, 𐑥𐑱𐑡-𐑕𐑲𐑑}, 𐑚𐑳𐑑 𐑨𐑚𐑕𐑩𐑤𐑵𐑑𐑤𐑦 𐑯𐑳𐑔𐑦𐑙 𐑩𐑐𐑽𐑛 𐑑 𐑣𐑦𐑥. 𐑣𐑰 𐑔𐑷𐑑 𐑩𐑚𐑬𐑑 𐑑𐑱𐑒𐑦𐑙 𐑬𐑑 𐑣𐑦𐑟 𐑢𐑪𐑯𐑛 𐑯 𐑢𐑱𐑝𐑦𐑙 𐑦𐑑, 𐑚𐑳𐑑 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑣𐑨𐑛 𐑢𐑹𐑯𐑛 𐑣𐑦𐑥 𐑩𐑜𐑱𐑯𐑕𐑑 𐑿𐑟𐑦𐑙 𐑣𐑦𐑟 𐑢𐑪𐑯𐑛. 𐑐𐑤𐑳𐑕 𐑦𐑓 𐑞𐑺 𐑢𐑪𐑟 𐑩𐑯𐑳𐑞𐑼 𐑖𐑬𐑼 𐑝 𐑥𐑳𐑤𐑑𐑦𐑒𐑳𐑤𐑼𐑛 𐑕𐑐𐑸𐑒𐑕 𐑞𐑨𐑑 𐑥𐑲𐑑 𐑤𐑰𐑛 𐑑 𐑚𐑰𐑦𐑙 𐑼𐑧𐑕𐑑𐑩𐑛 𐑓 𐑕𐑧𐑑𐑦𐑙 𐑪𐑓 𐑓𐑲𐑼𐑢𐑻𐑒𐑕 𐑦𐑯𐑕𐑲𐑛 𐑩 𐑑𐑮𐑱𐑯 𐑕𐑑𐑱𐑖𐑩𐑯. 𐑯 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑩𐑕𐑿𐑥𐑦𐑙 𐑣𐑦𐑟 𐑢𐑪𐑯𐑛 𐑛𐑦𐑛𐑩𐑯𐑑 𐑛𐑦𐑕𐑲𐑛 𐑑 𐑛𐑵 𐑕𐑳𐑥𐑔𐑦𐑙 𐑧𐑤𐑕, 𐑤𐑲𐑒 𐑚𐑤𐑴𐑦𐑙 𐑳𐑐 𐑷𐑤 𐑝 ·𐑒𐑦𐑙'𐑟 ·𐑒𐑮𐑪𐑕. ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑴𐑯𐑤𐑦 𐑤𐑲𐑑𐑤𐑦 𐑕𐑒𐑦𐑥𐑛 𐑣𐑦𐑟 𐑕𐑒𐑵𐑤𐑚𐑫𐑒𐑕 (𐑞𐑴 𐑞𐑨𐑑 𐑕𐑒𐑦𐑥 𐑢𐑪𐑟 𐑒𐑢𐑲𐑑 𐑚𐑦𐑟𐑸 𐑦𐑯𐑳𐑓) 𐑦𐑯 𐑩 𐑝𐑧𐑮𐑦 𐑒𐑢𐑦𐑒 𐑧𐑓𐑼𐑑 𐑑 𐑛𐑦𐑑𐑻𐑥𐑦𐑯 𐑢𐑪𐑑 𐑕𐑹𐑑 𐑝 𐑕𐑲𐑩𐑯𐑕 𐑚𐑫𐑒𐑕 𐑑 𐑚𐑲 𐑴𐑝𐑼 𐑞 𐑯𐑧𐑒𐑕𐑑 48 𐑬𐑼𐑟.

𐑢𐑧𐑤, 𐑣𐑰 𐑣𐑨𐑛—·𐑣𐑨𐑮𐑦 𐑜𐑤𐑭𐑯𐑕𐑑 𐑨𐑑 𐑣𐑦𐑟 𐑢𐑪𐑗—𐑢𐑳𐑯 𐑣𐑴𐑤 𐑬𐑼 𐑑 𐑓𐑦𐑜𐑼 𐑦𐑑 𐑬𐑑, 𐑕𐑦𐑯𐑕 𐑣𐑰 𐑢𐑪𐑟 𐑕𐑩𐑐𐑴𐑕𐑑 𐑑 𐑚𐑰 𐑪𐑯 𐑞 𐑑𐑮𐑱𐑯 𐑨𐑑 𐑦𐑤𐑧𐑝𐑩𐑯. 𐑥𐑱𐑚𐑰 𐑞𐑦𐑕 𐑢𐑪𐑟 𐑞 𐑦𐑒𐑢𐑦𐑝𐑩𐑤𐑩𐑯𐑑 𐑝 𐑩𐑯 𐑲𐑒𐑿 𐑑𐑧𐑕𐑑 𐑯 𐑞 𐑕𐑑𐑿𐑐𐑦𐑛 𐑒𐑦𐑛𐑟 𐑒𐑫𐑛𐑩𐑯𐑑 𐑚𐑦𐑒𐑳𐑥 𐑢𐑦𐑟𐑼𐑛𐑟. (𐑯 𐑞 𐑩𐑥𐑬𐑯𐑑 𐑝 𐑧𐑒𐑕𐑑𐑮𐑩 𐑑𐑲𐑥 𐑿 𐑜𐑱𐑝 𐑘𐑹𐑕𐑧𐑤𐑓 𐑢𐑫𐑛 𐑛𐑦𐑑𐑻𐑥𐑦𐑯 𐑘𐑹 ·𐑒𐑪𐑯𐑖𐑦𐑧𐑯𐑖𐑩𐑕𐑯𐑩𐑕, 𐑢𐑦𐑗 𐑢𐑪𐑟 𐑞 𐑕𐑱𐑒𐑪𐑯𐑛 𐑥𐑴𐑕𐑑 𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑 𐑓𐑨𐑒𐑑𐑼 𐑦𐑯 𐑕𐑒𐑪𐑤𐑼𐑤𐑦 𐑕𐑩𐑒𐑕𐑧𐑕.)

“𐑲'𐑤 𐑓𐑦𐑜𐑼 𐑦𐑑 𐑬𐑑,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑑 𐑣𐑦𐑟 𐑢𐑱𐑑𐑦𐑙 𐑐𐑺𐑩𐑯𐑑𐑕. “𐑦𐑑'𐑕 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑕𐑳𐑥 𐑕𐑹𐑑 𐑝 𐑑𐑧𐑕𐑑 𐑔𐑦𐑙𐑦.”

𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑓𐑮𐑬𐑯𐑛. “·𐑣𐑥…𐑥𐑱𐑚𐑰 𐑤𐑫𐑒 𐑓 𐑩 𐑑𐑮𐑱𐑤 𐑝 𐑥𐑦𐑒𐑕𐑑 𐑓𐑫𐑑𐑐𐑮𐑦𐑯𐑑𐑕 𐑪𐑯 𐑞 𐑜𐑮𐑬𐑯𐑛, 𐑤𐑰𐑛𐑦𐑙 𐑕𐑳𐑥𐑢𐑺 𐑞𐑨𐑑 𐑛𐑳𐑟𐑩𐑯𐑑 𐑕𐑰𐑥 𐑑 𐑥𐑱𐑒 𐑕𐑧𐑯𐑕—”

“\emph{𐑛𐑨𐑛!}” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. “𐑕𐑑𐑪𐑐 𐑞𐑨𐑑! 𐑲 𐑣𐑨𐑝𐑩𐑯𐑑 𐑰𐑝𐑩𐑯 \emph{𐑑𐑮𐑲𐑛} 𐑑 𐑓𐑦𐑜𐑼 𐑦𐑑 𐑬𐑑 𐑪𐑯 𐑥𐑲 𐑴𐑯!” 𐑦𐑑 𐑢𐑪𐑟 𐑩 𐑝𐑧𐑮𐑦 𐑜𐑫𐑛 𐑕𐑩𐑡𐑧𐑕𐑗𐑩𐑯, 𐑑𐑵, 𐑢𐑦𐑗 𐑢𐑪𐑟 𐑢𐑻𐑕.

“𐑕𐑪𐑮𐑦,” 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑩𐑐𐑪𐑤𐑩𐑡𐑲𐑟𐑛.

“·𐑭…” 𐑣𐑨𐑮𐑦'𐑟 𐑥𐑳𐑞𐑼 𐑕𐑧𐑛. “𐑲 𐑛𐑴𐑯𐑑 𐑔𐑦𐑙𐑒 𐑞𐑱 𐑢𐑫𐑛 𐑛𐑵 𐑞𐑨𐑑 𐑑 𐑩 𐑕𐑑𐑿𐑛𐑩𐑯𐑑, 𐑛𐑵 𐑿? 𐑸 𐑿 𐑖𐑫𐑼 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑛𐑦𐑛𐑩𐑯𐑑 𐑑𐑧𐑤 𐑿 𐑧𐑯𐑦𐑔𐑦𐑙?”

“𐑥𐑱𐑚𐑰 𐑖𐑰 𐑢𐑪𐑟 𐑛𐑦𐑕𐑑𐑮𐑨𐑒𐑑𐑩𐑛,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑢𐑦𐑞𐑬𐑑 𐑔𐑦𐑙𐑒𐑦𐑙.

“\emph{·𐑣𐑨𐑮𐑦!}” 𐑣𐑦𐑕𐑑 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑯 𐑥𐑳𐑞𐑼 𐑦𐑯 𐑿𐑯𐑦𐑕𐑩𐑯. “\emph{𐑢𐑪𐑑 𐑛𐑦𐑛 𐑿 𐑛𐑵?}”

“𐑲, 𐑳𐑥—” ·𐑣𐑨𐑮𐑦 𐑕𐑢𐑪𐑤𐑴𐑛. “𐑤𐑫𐑒, 𐑢𐑰 𐑛𐑴𐑯𐑑 𐑣𐑨𐑝 𐑑𐑲𐑥 𐑓 𐑞𐑦𐑕 𐑯𐑬—”

“\emph{·𐑣𐑨𐑮𐑦!}”

“𐑲 𐑥𐑰𐑯 𐑦𐑑! 𐑢𐑰 𐑛𐑴𐑯𐑑 𐑣𐑨𐑝 𐑑𐑲𐑥 𐑓 𐑞𐑦𐑕 𐑯𐑬! 𐑚𐑦𐑒𐑪𐑟 𐑦𐑑'𐑕 𐑩 𐑮𐑾𐑤𐑦 𐑤𐑪𐑙 𐑕𐑑𐑹𐑦 𐑯 𐑲'𐑝 𐑜𐑪𐑑 𐑑 𐑓𐑦𐑜𐑼 𐑬𐑑 𐑣𐑬 𐑑 𐑜𐑧𐑑 𐑑 𐑕𐑒𐑵𐑤!”

𐑣𐑦𐑟 𐑥𐑳𐑞𐑼 𐑣𐑨𐑛 𐑩 𐑣𐑨𐑯𐑛 𐑴𐑝𐑼 𐑣𐑻 𐑓𐑱𐑕. “𐑣𐑬 𐑚𐑨𐑛 𐑢𐑪𐑟 𐑦𐑑?”

“𐑲, 𐑭,” \emph{𐑲 𐑒𐑭𐑯𐑑 𐑑𐑷𐑒 𐑩𐑚𐑬𐑑 𐑞𐑨𐑑 𐑓 𐑮𐑰𐑟𐑩𐑯𐑟 𐑝 ·𐑯𐑨𐑖𐑩𐑯𐑩𐑤 ·𐑕𐑦𐑒𐑘𐑫𐑼𐑦𐑑𐑦,} “𐑩𐑚𐑬𐑑 𐑣𐑭𐑓 𐑨𐑟 𐑚𐑨𐑛 𐑨𐑟 𐑞 ·𐑦𐑯𐑕𐑦𐑛𐑩𐑯𐑑 𐑢𐑦𐑞 𐑞 ·𐑕𐑲𐑩𐑯𐑕 ·𐑐𐑮𐑴𐑡𐑧𐑒𐑑?”

“\emph{·𐑣𐑨𐑮𐑦!}”

“𐑲, 𐑼, 𐑴 𐑤𐑫𐑒 𐑞𐑺 𐑸 𐑕𐑳𐑥 𐑐𐑰𐑐𐑩𐑤 𐑢𐑦𐑞 𐑩𐑯 𐑬𐑤 𐑲'𐑤 𐑜𐑴 𐑭𐑕𐑒 𐑞𐑧𐑥 𐑣𐑬 𐑑 𐑜𐑧𐑑 𐑦𐑯!” 𐑯 ·𐑣𐑨𐑮𐑦 𐑮𐑨𐑯 𐑩𐑢𐑱 𐑓𐑮𐑪𐑥 𐑣𐑦𐑟 𐑐𐑺𐑩𐑯𐑑𐑕 𐑑𐑩𐑢𐑹𐑛𐑟 𐑞 𐑓𐑨𐑥𐑤𐑦 𐑝 𐑓𐑲𐑼𐑦 𐑮𐑧𐑛𐑣𐑧𐑛𐑟, 𐑣𐑦𐑟 𐑑𐑮𐑳𐑙𐑒 𐑷𐑑𐑩𐑥𐑨𐑑𐑦𐑒𐑤𐑦 𐑕𐑤𐑦𐑞𐑼𐑦𐑙 𐑚𐑦𐑣𐑲𐑯𐑛 𐑣𐑦𐑥.

𐑞 𐑐𐑤𐑳𐑥𐑐 𐑢𐑫𐑥𐑩𐑯 𐑤𐑫𐑒𐑑 𐑑 𐑣𐑦𐑥 𐑨𐑟 𐑣𐑰 𐑼𐑲𐑝𐑛. “𐑣𐑧𐑤𐑴, 𐑛𐑽. 𐑓𐑻𐑕𐑑 𐑑𐑲𐑥 𐑨𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕? 𐑮𐑪𐑯'𐑟 𐑯𐑿, 𐑑𐑵—” 𐑯 𐑞𐑧𐑯 𐑖𐑰 𐑐𐑽𐑛 𐑒𐑤𐑴𐑕𐑤𐑦 𐑨𐑑 𐑣𐑦𐑥. “\emph{·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼?}”

𐑓𐑹 𐑚𐑶𐑟 𐑯 𐑩 𐑮𐑧𐑛-𐑣𐑧𐑛𐑩𐑛 𐑜𐑻𐑤 𐑯 𐑩𐑯 𐑬𐑤 𐑷𐑤 𐑕𐑢𐑳𐑙 𐑼𐑬𐑯𐑛 𐑯 𐑞𐑧𐑯 𐑓𐑮𐑴𐑟 𐑦𐑯 𐑐𐑤𐑱𐑕.

“𐑴, \emph{𐑒𐑳𐑥 𐑪𐑯!}” ·𐑣𐑨𐑮𐑦 𐑐𐑮𐑴𐑑𐑧𐑕𐑑𐑩𐑛. 𐑣𐑰'𐑛 𐑚𐑰𐑯 𐑐𐑤𐑨𐑯𐑦𐑙 𐑑 𐑜𐑴 𐑨𐑟 ·𐑣𐑨𐑮𐑦 ·𐑝𐑧𐑮𐑟 𐑨𐑑 𐑤𐑰𐑕𐑑 𐑩𐑯𐑑𐑦𐑤 𐑣𐑰 𐑜𐑪𐑑 𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕. “𐑲 𐑚𐑷𐑑 𐑩 𐑕𐑢𐑧𐑑𐑚𐑨𐑯𐑛 𐑯 𐑧𐑝𐑮𐑦𐑔𐑦𐑙! 𐑣𐑬 𐑒𐑳𐑥 𐑿 𐑯𐑴 𐑣𐑵 𐑲 𐑨𐑥?”

“𐑘𐑧𐑕,” 𐑣𐑨𐑮𐑦'𐑟 𐑓𐑭𐑞𐑼 𐑕𐑧𐑛, 𐑒𐑳𐑥𐑦𐑙 𐑳𐑐 𐑚𐑦𐑣𐑲𐑯𐑛 𐑣𐑦𐑥 𐑢𐑦𐑞 𐑤𐑪𐑙 𐑰𐑟𐑦 𐑕𐑑𐑮𐑲𐑛𐑟, “𐑣𐑬 \emph{𐑛𐑵} 𐑿 𐑯𐑴 𐑣𐑵 𐑣𐑰 𐑦𐑟?” 𐑣𐑦𐑟 𐑝𐑶𐑕 𐑦𐑯𐑛𐑦𐑒𐑱𐑑𐑩𐑛 𐑩 𐑕𐑻𐑑𐑩𐑯 𐑛𐑮𐑧𐑛.

“𐑘𐑹 𐑐𐑦𐑒𐑗𐑼 𐑢𐑪𐑟 𐑦𐑯 𐑞 𐑯𐑿𐑟𐑐𐑱𐑐𐑼𐑟,” 𐑕𐑧𐑛 𐑢𐑳𐑯 𐑝 𐑑𐑵 𐑲𐑛𐑧𐑯𐑑𐑦𐑒𐑩𐑤-𐑤𐑫𐑒𐑦𐑙 𐑑𐑢𐑦𐑯𐑟.

“\shout{Harry!}”

“\emph{𐑛𐑨𐑛!} 𐑦𐑑'𐑕 𐑯𐑪𐑑 𐑤𐑲𐑒 𐑞𐑨𐑑! 𐑦𐑑'𐑕 '𐑒𐑷𐑟 𐑲 𐑛𐑦𐑓𐑰𐑑𐑩𐑛 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛 𐑿-𐑯𐑴-𐑣𐑵 𐑢𐑧𐑯 𐑲 𐑢𐑪𐑟 𐑢𐑳𐑯 𐑘𐑽 𐑴𐑤𐑛!”

“\shout{What?}”

“𐑥𐑳𐑥 𐑒𐑨𐑯 𐑦𐑒𐑕𐑐𐑤𐑱𐑯.”

“\shout{What?}”

“𐑭…·𐑥𐑲𐑒𐑩𐑤 𐑛𐑽, 𐑞𐑺 𐑸 𐑕𐑻𐑑𐑩𐑯 𐑔𐑦𐑙𐑟 𐑲 𐑔𐑷𐑑 𐑦𐑑 𐑢𐑫𐑛 𐑚𐑰 𐑚𐑧𐑕𐑑 𐑯𐑪𐑑 𐑑 𐑚𐑪𐑞𐑼 𐑿 𐑢𐑦𐑞 𐑩𐑯𐑑𐑦𐑤 𐑯𐑬—”

“𐑦𐑒𐑕𐑒𐑿𐑟 𐑥𐑰,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑑 𐑞 𐑮𐑧𐑛-𐑣𐑧𐑛𐑩𐑛 𐑓𐑨𐑥𐑤𐑦 𐑣𐑵 𐑢𐑻 𐑷𐑤 𐑕𐑑𐑺𐑦𐑙 𐑨𐑑 𐑣𐑦𐑥, “𐑚𐑳𐑑 𐑦𐑑 𐑢𐑫𐑛 𐑚𐑰 𐑒𐑢𐑲𐑑 𐑦𐑒𐑕𐑑𐑮𐑰𐑥𐑤𐑦 𐑣𐑧𐑤𐑐𐑓𐑩𐑤 𐑦𐑓 𐑿 𐑒𐑫𐑛 𐑑𐑧𐑤 𐑥𐑰 𐑣𐑬 𐑑 𐑜𐑧𐑑 𐑑 ·𐑐𐑤𐑨𐑑𐑓𐑹𐑥 ·𐑯𐑲𐑯-𐑯-·𐑔𐑮𐑰-·𐑒𐑢𐑹𐑑𐑼𐑟 \emph{𐑮𐑲𐑑 𐑯𐑬}.”

“𐑭…” 𐑕𐑧𐑛 𐑞 𐑢𐑫𐑥𐑩𐑯. 𐑖𐑰 𐑮𐑱𐑟𐑛 𐑩 𐑣𐑨𐑯𐑛 𐑯 𐑐𐑶𐑯𐑑𐑩𐑛 𐑨𐑑 𐑞 𐑢𐑷𐑤 𐑚𐑦𐑑𐑢𐑰𐑯 𐑐𐑤𐑨𐑑𐑓𐑹𐑥𐑟. “𐑡𐑳𐑕𐑑 𐑢𐑷𐑒 𐑕𐑑𐑮𐑱𐑑 𐑨𐑑 𐑞 𐑚𐑨𐑮𐑽 𐑚𐑦𐑑𐑢𐑰𐑯 𐑐𐑤𐑨𐑑𐑓𐑹𐑥𐑟 𐑯𐑲𐑯 𐑯 𐑑𐑧𐑯. 𐑛𐑴𐑯𐑑 𐑕𐑑𐑪𐑐 𐑯 𐑛𐑴𐑯𐑑 𐑚𐑰 𐑕𐑒𐑺𐑛 𐑿'𐑤 𐑒𐑮𐑨𐑖 𐑦𐑯𐑑𐑵 𐑦𐑑, 𐑞𐑨𐑑'𐑕 𐑝𐑧𐑮𐑦 𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑. 𐑚𐑧𐑕𐑑 𐑛𐑵 𐑦𐑑 𐑨𐑑 𐑩 𐑚𐑦𐑑 𐑝 𐑩 𐑮𐑳𐑯 𐑦𐑓 𐑿'𐑼 𐑯𐑻𐑝𐑩𐑕.”

“𐑯 𐑢𐑪𐑑𐑧𐑝𐑼 𐑿 𐑛𐑵, 𐑛𐑴𐑯𐑑 𐑔𐑦𐑙𐑒 𐑝 𐑩𐑯 𐑧𐑤𐑦𐑓𐑩𐑯𐑑.”

“\emph{·𐑡𐑹𐑡!} 𐑦𐑜𐑯𐑹 𐑣𐑦𐑥, ·𐑣𐑨𐑮𐑦 𐑛𐑽, 𐑞𐑺'𐑟 𐑯𐑴 𐑮𐑰𐑟𐑩𐑯 𐑯𐑪𐑑 𐑑 𐑔𐑦𐑙𐑒 𐑝 𐑩𐑯 𐑧𐑤𐑦𐑓𐑩𐑯𐑑.”

“𐑲'𐑥 ·𐑓𐑮𐑧𐑛, ·𐑥𐑳𐑥, 𐑯𐑪𐑑 ·𐑡𐑹𐑡—”

“𐑔𐑨𐑙𐑒𐑕!” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑯 𐑑𐑫𐑒 𐑪𐑓 𐑨𐑑 𐑩 𐑮𐑳𐑯 𐑑𐑩𐑢𐑹𐑛𐑟 𐑞 𐑚𐑨𐑮𐑽—

·𐑢𐑱𐑑 𐑩 𐑥𐑦𐑯𐑦𐑑, 𐑦𐑑 𐑢𐑫𐑛𐑩𐑯𐑑 𐑢𐑻𐑒 \emph{𐑩𐑯𐑤𐑧𐑕 𐑣𐑰 𐑚𐑦𐑤𐑰𐑝𐑛 𐑦𐑯 𐑦𐑑}?

𐑦𐑑 𐑢𐑪𐑟 𐑨𐑑 𐑑𐑲𐑥𐑟 𐑤𐑲𐑒 𐑞𐑦𐑕 𐑞𐑨𐑑 ·𐑣𐑨𐑮𐑦 𐑣𐑱𐑑𐑩𐑛 𐑣𐑦𐑟 𐑥𐑲𐑯𐑛 𐑓 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑢𐑻𐑒𐑦𐑙 𐑓𐑭𐑕𐑑 𐑦𐑯𐑳𐑓 𐑑 𐑮𐑾𐑤𐑲𐑟 𐑞𐑨𐑑 𐑞𐑦𐑕 𐑢𐑪𐑟 𐑩 𐑒𐑱𐑕 𐑢𐑺 “𐑮𐑧𐑟𐑩𐑯𐑩𐑯𐑑 𐑛𐑬𐑑” 𐑩𐑐𐑤𐑲𐑛, 𐑞𐑨𐑑 𐑦𐑟, 𐑦𐑓 𐑣𐑰'𐑛 𐑕𐑑𐑸𐑑𐑩𐑛 𐑬𐑑 𐑔𐑦𐑙𐑒𐑦𐑙 𐑞𐑨𐑑 𐑣𐑰 𐑢𐑫𐑛 𐑜𐑴 𐑔𐑮𐑵 𐑞 𐑚𐑨𐑮𐑽 𐑣𐑰'𐑛 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑓𐑲𐑯, 𐑴𐑯𐑤𐑦 𐑯𐑬 𐑣𐑰 𐑢𐑪𐑟 𐑢𐑳𐑮𐑦𐑛 𐑩𐑚𐑬𐑑 𐑢𐑧𐑞𐑼 𐑣𐑰 𐑕𐑩𐑓𐑦𐑖𐑩𐑯𐑑𐑤𐑦 \emph{𐑚𐑦𐑤𐑰𐑝𐑛} 𐑣𐑰'𐑛 𐑜𐑴 𐑔𐑮𐑵 𐑞 𐑚𐑨𐑮𐑽, 𐑢𐑦𐑗 𐑥𐑧𐑯𐑑 𐑞𐑨𐑑 𐑣𐑰 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 \emph{𐑢𐑪𐑟} 𐑢𐑳𐑮𐑦𐑛 𐑩𐑚𐑬𐑑 𐑒𐑮𐑨𐑖𐑦𐑙 𐑦𐑯𐑑𐑵 𐑦𐑑—

“\emph{·𐑣𐑨𐑮𐑦! 𐑜𐑧𐑑 𐑚𐑨𐑒 𐑣𐑽, 𐑿 𐑣𐑨𐑝 𐑕𐑳𐑥 𐑦𐑒𐑕𐑐𐑤𐑱𐑯𐑦𐑙 𐑑 𐑛𐑵!}” 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑣𐑦𐑟 ·𐑛𐑨𐑛.

·𐑣𐑨𐑮𐑦 𐑖𐑳𐑑 𐑣𐑦𐑟 𐑲𐑟 𐑯 𐑦𐑜𐑯𐑹𐑛 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑣𐑰 𐑯𐑿 𐑩𐑚𐑬𐑑 𐑡𐑳𐑕𐑑𐑦𐑓𐑲𐑛 𐑒𐑮𐑧𐑛𐑩𐑚𐑦𐑤𐑦𐑑𐑦 𐑯 𐑡𐑳𐑕𐑑 𐑑𐑮𐑲𐑛 𐑑 𐑚𐑦𐑤𐑰𐑝 \emph{𐑮𐑾𐑤𐑦 𐑣𐑸𐑛} 𐑞𐑨𐑑 𐑣𐑰'𐑛 𐑜𐑴 𐑔𐑮𐑵 𐑞 𐑚𐑨𐑮𐑽 𐑯—

—𐑞 𐑕𐑬𐑯𐑛𐑟 𐑼𐑬𐑯𐑛 𐑣𐑦𐑥 𐑗𐑱𐑯𐑡𐑛.

·𐑣𐑨𐑮𐑦 𐑴𐑐𐑩𐑯𐑛 𐑣𐑦𐑟 𐑲𐑟 𐑯 𐑕𐑑𐑳𐑥𐑚𐑩𐑤𐑛 𐑑 𐑩 𐑣𐑷𐑤𐑑, 𐑓𐑰𐑤𐑦𐑙 𐑝𐑱𐑜𐑤𐑦 𐑛𐑻𐑑𐑦𐑛 𐑚𐑲 𐑣𐑨𐑝𐑦𐑙 𐑥𐑱𐑛 𐑩 𐑛𐑦𐑤𐑦𐑚𐑼𐑩𐑑 𐑧𐑓𐑼𐑑 𐑑 𐑚𐑦𐑤𐑰𐑝 𐑕𐑳𐑥𐑔𐑦𐑙.

𐑣𐑰 𐑢𐑪𐑟 𐑕𐑑𐑨𐑯𐑛𐑦𐑙 𐑦𐑯 𐑩 𐑚𐑮𐑲𐑑, 𐑴𐑐𐑩𐑯-𐑺 𐑐𐑤𐑨𐑑𐑓𐑹𐑥 𐑯𐑧𐑒𐑕𐑑 𐑑 𐑩 𐑕𐑦𐑙𐑜𐑩𐑤 𐑣𐑿𐑡 𐑑𐑮𐑱𐑯, 𐑓𐑹𐑑𐑰𐑯 𐑤𐑪𐑙 𐑒𐑨𐑮𐑦𐑡𐑩𐑟 𐑣𐑧𐑛𐑩𐑛 𐑳𐑐 𐑚𐑲 𐑩 𐑥𐑨𐑕𐑦𐑝 𐑕𐑒𐑸𐑤𐑩𐑑-𐑥𐑧𐑑𐑩𐑤 𐑕𐑑𐑰𐑥 𐑧𐑯𐑡𐑦𐑯 𐑢𐑦𐑞 𐑩 𐑑𐑷𐑤 𐑗𐑦𐑥𐑯𐑦 𐑞𐑨𐑑 𐑐𐑮𐑪𐑥𐑦𐑕𐑑 𐑛𐑧𐑔 𐑑 𐑺 𐑒𐑢𐑪𐑤𐑦𐑑𐑦. 𐑞 𐑐𐑤𐑨𐑑𐑓𐑹𐑥 𐑢𐑪𐑟 𐑷𐑤𐑮𐑧𐑛𐑦 𐑤𐑲𐑑𐑤𐑦 𐑒𐑮𐑬𐑛𐑩𐑛 (𐑰𐑝𐑩𐑯 𐑞𐑴 ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑩 𐑓𐑫𐑤 𐑬𐑼 𐑻𐑤𐑦); 𐑛𐑳𐑟𐑩𐑯𐑟 𐑝 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑯 𐑞𐑺 𐑐𐑺𐑩𐑯𐑑𐑕 𐑕𐑢𐑹𐑥𐑛 𐑼𐑬𐑯𐑛 𐑚𐑧𐑯𐑗𐑩𐑟, 𐑑𐑱𐑚𐑩𐑤𐑟, 𐑯 𐑝𐑺𐑾𐑕 𐑣𐑷𐑒𐑼𐑟 𐑯 𐑕𐑑𐑷𐑤𐑟.

𐑦𐑑 𐑢𐑧𐑯𐑑 𐑦𐑯𐑑𐑲𐑼𐑤𐑦 𐑢𐑦𐑞𐑬𐑑 𐑕𐑱𐑦𐑙 𐑞𐑨𐑑 𐑞𐑺 𐑢𐑪𐑟 𐑯𐑴 𐑕𐑳𐑗 𐑐𐑤𐑱𐑕 𐑦𐑯 ·𐑒𐑦𐑙'𐑟 ·𐑒𐑮𐑪𐑕 ·𐑕𐑑𐑱𐑖𐑩𐑯 𐑯 𐑯𐑴 𐑮𐑵𐑥 𐑑 𐑣𐑲𐑛 𐑦𐑑.

\emph{𐑴𐑒𐑱, 𐑕𐑴 𐑲𐑞𐑼 (𐑩)~𐑲 𐑡𐑳𐑕𐑑 𐑑𐑧𐑤𐑦𐑐𐑹𐑑𐑩𐑛 𐑕𐑳𐑥𐑢𐑺 𐑧𐑤𐑕 𐑦𐑯𐑑𐑲𐑼𐑤𐑦 (𐑚)~𐑞𐑱 𐑒𐑨𐑯 𐑓𐑴𐑤𐑛 𐑕𐑐𐑱𐑕 𐑤𐑲𐑒 𐑯𐑴𐑚𐑪𐑛𐑦'𐑟 𐑚𐑦𐑟𐑯𐑩𐑕 𐑹 (c)~𐑞𐑱 𐑸 𐑕𐑦𐑥𐑐𐑤𐑦 𐑦𐑜𐑯𐑹𐑦𐑙 𐑷𐑤 𐑞 𐑮𐑵𐑤𐑟.}

𐑞𐑺 𐑢𐑪𐑟 𐑩 𐑕𐑤𐑦𐑞𐑼𐑦𐑙 𐑕𐑬𐑯𐑛 𐑚𐑦𐑣𐑲𐑯𐑛 𐑣𐑦𐑥, 𐑯 ·𐑣𐑨𐑮𐑦 𐑑𐑻𐑯𐑛 𐑼𐑬𐑯𐑛 𐑑 𐑩𐑚𐑟𐑻𐑝 𐑞𐑨𐑑 𐑣𐑦𐑟 𐑑𐑮𐑳𐑙𐑒 𐑣𐑨𐑛 𐑦𐑯𐑛𐑰𐑛 𐑓𐑪𐑤𐑴𐑛 𐑣𐑦𐑥 𐑪𐑯 𐑦𐑑𐑕 𐑕𐑥𐑷𐑤 𐑒𐑤𐑷𐑛 𐑑𐑧𐑯𐑑𐑩𐑒𐑩𐑤𐑟. 𐑩𐑐𐑨𐑮𐑩𐑯𐑑𐑤𐑦, 𐑓 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 𐑐𐑻𐑐𐑩𐑕𐑩𐑟, 𐑣𐑦𐑟 𐑤𐑳𐑜𐑦𐑡 𐑣𐑨𐑛 𐑷𐑤𐑕𐑴 𐑥𐑨𐑯𐑦𐑡𐑛 𐑑 𐑚𐑦𐑤𐑰𐑝 𐑢𐑦𐑞 𐑕𐑩𐑓𐑦𐑖𐑩𐑯𐑑 𐑕𐑑𐑮𐑧𐑙𐑔 𐑑 𐑐𐑭𐑕 𐑔𐑮𐑵 𐑞 𐑚𐑨𐑮𐑽. 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑛𐑦𐑕𐑑𐑻𐑚𐑦𐑙 𐑢𐑧𐑯 ·𐑣𐑨𐑮𐑦 𐑕𐑑𐑸𐑑𐑩𐑛 𐑔𐑦𐑙𐑒𐑦𐑙 𐑩𐑚𐑬𐑑 𐑦𐑑.

𐑩 𐑥𐑴𐑥𐑩𐑯𐑑 𐑤𐑱𐑑𐑼, 𐑞 𐑘𐑳𐑙𐑜𐑩𐑕𐑑-𐑤𐑫𐑒𐑦𐑙 𐑮𐑧𐑛-𐑣𐑺𐑛 𐑚𐑶 𐑒𐑱𐑥 𐑔𐑮𐑵 𐑞 𐑲𐑼𐑯 𐑸𐑗𐑢𐑱 (𐑲𐑼𐑯 𐑸𐑗𐑢𐑱?) 𐑨𐑑 𐑩 𐑮𐑳𐑯, 𐑐𐑫𐑤𐑦𐑙 𐑣𐑦𐑟 𐑑𐑮𐑳𐑙𐑒 𐑚𐑦𐑣𐑲𐑯𐑛 𐑣𐑦𐑥 𐑪𐑯 𐑩 𐑤𐑰𐑛 𐑯 𐑯𐑽𐑤𐑦 𐑒𐑮𐑨𐑖𐑦𐑙 𐑦𐑯𐑑𐑵 ·𐑣𐑨𐑮𐑦. ·𐑣𐑨𐑮𐑦, 𐑓𐑰𐑤𐑦𐑙 𐑕𐑑𐑿𐑐𐑦𐑛 𐑓 𐑣𐑨𐑝𐑦𐑙 𐑕𐑑𐑱𐑛 𐑼𐑬𐑯𐑛, 𐑒𐑢𐑦𐑒𐑤𐑦 𐑚𐑦𐑜𐑨𐑯 𐑥𐑵𐑝𐑦𐑙 𐑩𐑢𐑱 𐑓𐑮𐑪𐑥 𐑞 𐑤𐑨𐑯𐑛𐑦𐑙 𐑺𐑾, 𐑯 𐑞 𐑮𐑧𐑛-𐑣𐑺𐑛 𐑚𐑶 𐑓𐑪𐑤𐑴𐑛 𐑣𐑦𐑥, 𐑘𐑨𐑙𐑒𐑦𐑙 𐑣𐑸𐑛 𐑪𐑯 𐑣𐑦𐑟 𐑑𐑮𐑳𐑙𐑒'𐑕 𐑤𐑰𐑛 𐑦𐑯 𐑹𐑛𐑼 𐑑 𐑒𐑰𐑐 𐑳𐑐. 𐑩 𐑥𐑴𐑥𐑩𐑯𐑑 𐑤𐑱𐑑𐑼, 𐑩 𐑢𐑲𐑑 𐑬𐑤 𐑓𐑤𐑳𐑑𐑼𐑛 𐑔𐑮𐑵 𐑞 𐑸𐑗𐑢𐑱 𐑯 𐑒𐑱𐑥 𐑑 𐑮𐑧𐑕𐑑 𐑪𐑯 𐑞 𐑚𐑶'𐑟 𐑖𐑴𐑤𐑛𐑼.

“·𐑒𐑹,” 𐑕𐑧𐑛 𐑞 𐑮𐑧𐑛-𐑣𐑺𐑛 𐑚𐑶, “𐑸 𐑿 \emph{𐑮𐑾𐑤𐑦} ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼?”

\emph{𐑯𐑪𐑑 𐑞𐑦𐑕 𐑩𐑜𐑱𐑯.} “𐑲 𐑣𐑨𐑝 𐑯𐑴 𐑤𐑪𐑡𐑦𐑒𐑩𐑤 𐑢𐑱 𐑝 𐑯𐑴𐑦𐑙 𐑞𐑨𐑑 𐑓 𐑕𐑻𐑑𐑩𐑯. 𐑥𐑲 𐑐𐑺𐑩𐑯𐑑𐑕 𐑮𐑱𐑟𐑛 𐑥𐑰 𐑑 \emph{𐑚𐑦𐑤𐑰𐑝} 𐑞𐑨𐑑 𐑥𐑲 𐑯𐑱𐑥 𐑢𐑪𐑟 ·𐑣𐑨𐑮𐑦 ·𐑡𐑱𐑥𐑟 ·𐑐𐑪𐑑𐑼-·𐑧𐑝𐑩𐑯𐑟-·𐑝𐑧𐑮𐑟, 𐑯 𐑥𐑧𐑯𐑦 𐑐𐑰𐑐𐑩𐑤 𐑣𐑽 𐑣𐑨𐑝 𐑑𐑴𐑤𐑛 𐑥𐑰 𐑞𐑨𐑑 𐑲 \emph{𐑤𐑫𐑒} 𐑤𐑲𐑒 𐑥𐑲 𐑐𐑺𐑩𐑯𐑑𐑕, 𐑲 𐑥𐑰𐑯 𐑥𐑲 𐑳𐑞𐑼 𐑐𐑺𐑩𐑯𐑑𐑕, 𐑚𐑳𐑑,” ·𐑣𐑨𐑮𐑦 𐑓𐑮𐑬𐑯𐑛, 𐑮𐑾𐑤𐑲𐑟𐑦𐑙, “𐑓 𐑷𐑤 \emph{𐑲} 𐑯𐑴, 𐑞𐑺 𐑒𐑫𐑛 𐑰𐑟𐑦𐑤𐑦 𐑚𐑰 𐑕𐑐𐑧𐑤𐑟 𐑑 𐑐𐑪𐑤𐑦𐑥𐑹𐑓 𐑩 𐑗𐑲𐑤𐑛 𐑦𐑯𐑑𐑵 𐑩 𐑕𐑐𐑧𐑕𐑦𐑓𐑲𐑛 𐑩𐑐𐑽𐑩𐑯𐑕—”

“𐑼, 𐑢𐑪𐑑, 𐑥𐑱𐑑?”

\emph{𐑯𐑪𐑑 𐑣𐑧𐑛𐑩𐑛 𐑓 ·𐑮𐑱𐑝𐑩𐑯𐑒𐑤𐑷, 𐑲 𐑑𐑱𐑒 𐑦𐑑.} “𐑘𐑧𐑕, 𐑲'𐑥 ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼.”

“𐑲'𐑥 ·𐑮𐑪𐑯 ·𐑢𐑰𐑟𐑤𐑦,” 𐑕𐑧𐑛 𐑞 𐑑𐑷𐑤 𐑕𐑒𐑦𐑯𐑦 𐑓𐑮𐑧𐑒𐑩𐑤𐑛 𐑤𐑪𐑙-𐑯𐑴𐑟𐑛 𐑒𐑦𐑛, 𐑯 𐑕𐑑𐑳𐑒 𐑬𐑑 𐑩 𐑣𐑨𐑯𐑛, 𐑢𐑦𐑗 ·𐑣𐑨𐑮𐑦 𐑐𐑩𐑤𐑲𐑑𐑤𐑦 𐑖𐑫𐑒 𐑨𐑟 𐑞𐑱 𐑢𐑷𐑒𐑑. 𐑞 𐑬𐑤 𐑜𐑱𐑝 ·𐑣𐑨𐑮𐑦 𐑩𐑯 𐑪𐑛𐑤𐑦 𐑥𐑧𐑠𐑼𐑛 𐑯 𐑒𐑻𐑑𐑾𐑕 𐑣𐑵𐑑 (𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑥𐑹 𐑝 𐑩𐑯 𐑣𐑰𐑰𐑰𐑰 𐑕𐑬𐑯𐑛, 𐑢𐑦𐑗 𐑕𐑼𐑐𐑮𐑲𐑟𐑛 ·𐑣𐑨𐑮𐑦).

𐑨𐑑 𐑞𐑦𐑕 𐑐𐑶𐑯𐑑 ·𐑣𐑨𐑮𐑦 𐑮𐑾𐑤𐑲𐑟𐑛 𐑞 𐑐𐑩𐑑𐑧𐑯𐑖𐑩𐑤 𐑓 𐑦𐑥𐑦𐑯𐑩𐑯𐑑 𐑒𐑩𐑑𐑨𐑕𐑑𐑮𐑩𐑓𐑦. “𐑡𐑳𐑕𐑑 𐑩 𐑕𐑱𐑒𐑪𐑯𐑛,” 𐑣𐑰 𐑕𐑧𐑛 𐑑 ·𐑮𐑪𐑯, 𐑯 𐑴𐑐𐑩𐑯𐑛 𐑢𐑳𐑯 𐑝 𐑞 𐑛𐑮𐑷𐑼𐑟 𐑝 𐑣𐑦𐑟 𐑑𐑮𐑳𐑙𐑒, 𐑞 𐑢𐑳𐑯 𐑞𐑨𐑑 𐑦𐑓 𐑣𐑰 𐑮𐑦𐑒𐑷𐑤𐑛 𐑒𐑼𐑧𐑒𐑑𐑤𐑦 𐑢𐑪𐑟 𐑓 ·𐑢𐑦𐑯𐑑𐑼 ·𐑒𐑤𐑴𐑞𐑟—𐑦𐑑 𐑢𐑪𐑟—𐑯 𐑞𐑧𐑯 𐑣𐑰 𐑓𐑬𐑯𐑛 𐑞 𐑤𐑲𐑑𐑩𐑕𐑑 𐑕𐑒𐑸𐑓 𐑣𐑰 𐑴𐑯𐑛, 𐑳𐑯𐑛𐑼𐑯𐑰𐑔 𐑣𐑦𐑟 𐑢𐑦𐑯𐑑𐑼 𐑒𐑴𐑑. ·𐑣𐑨𐑮𐑦 𐑑𐑫𐑒 𐑪𐑓 𐑣𐑦𐑟 𐑕𐑢𐑧𐑑𐑚𐑨𐑯𐑛, 𐑯 𐑡𐑳𐑕𐑑 𐑨𐑟 𐑒𐑢𐑦𐑒𐑤𐑦 𐑳𐑯𐑓𐑴𐑤𐑛𐑩𐑛 𐑞 𐑕𐑒𐑸𐑓 𐑯 𐑑𐑲𐑛 𐑦𐑑 𐑼𐑬𐑯𐑛 𐑣𐑦𐑟 𐑓𐑱𐑕. 𐑦𐑑 𐑢𐑪𐑟 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑣𐑪𐑑, 𐑦𐑕𐑐𐑧𐑖𐑩𐑤𐑦 𐑦𐑯 𐑞 𐑕𐑳𐑥𐑼, 𐑚𐑳𐑑 ·𐑣𐑨𐑮𐑦 𐑒𐑫𐑛 𐑤𐑦𐑝 𐑢𐑦𐑞 𐑞𐑨𐑑.

𐑞𐑧𐑯 𐑣𐑰 𐑖𐑳𐑑 𐑞𐑨𐑑 𐑛𐑮𐑷𐑼 𐑯 𐑐𐑫𐑤𐑛 𐑬𐑑 𐑩𐑯𐑳𐑞𐑼 𐑛𐑮𐑷𐑼 𐑯 𐑛𐑮𐑵 𐑓𐑹𐑔 𐑚𐑤𐑨𐑒 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑮𐑴𐑚𐑟, 𐑢𐑦𐑗 𐑣𐑰 𐑖𐑮𐑳𐑜𐑛 𐑴𐑝𐑼 𐑣𐑦𐑟 𐑣𐑧𐑛, 𐑯𐑬 𐑞𐑨𐑑 𐑣𐑰 𐑢𐑪𐑟 𐑬𐑑 𐑝 ·𐑥𐑳𐑜𐑩𐑤 𐑑𐑧𐑮𐑦𐑑𐑼𐑦.

“𐑞𐑺,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. 𐑞 𐑕𐑬𐑯𐑛 𐑒𐑱𐑥 𐑬𐑑 𐑕𐑤𐑲𐑑𐑤𐑦 𐑥𐑳𐑓𐑩𐑤𐑛 𐑔𐑮𐑵 𐑞 𐑕𐑒𐑸𐑓 𐑴𐑝𐑼 𐑣𐑦𐑟 𐑓𐑱𐑕. 𐑣𐑰 𐑑𐑻𐑯𐑛 𐑑 ·𐑮𐑪𐑯. “𐑣𐑬 𐑛𐑵 𐑲 𐑤𐑫𐑒? 𐑕𐑑𐑿𐑐𐑦𐑛, 𐑲 𐑯𐑴, 𐑚𐑳𐑑 𐑨𐑥 𐑲 𐑲𐑛𐑧𐑯𐑑𐑦𐑓𐑲𐑩𐑚𐑩𐑤 𐑨𐑟 ·𐑣𐑨𐑮𐑦 ·𐑐𐑪𐑑𐑼?”

“𐑼,” ·𐑮𐑪𐑯 𐑕𐑧𐑛. 𐑣𐑰 𐑒𐑤𐑴𐑟𐑛 𐑣𐑦𐑟 𐑥𐑬𐑔, 𐑢𐑦𐑗 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑴𐑐𐑩𐑯. “𐑯𐑪𐑑 𐑮𐑾𐑤𐑦, ·𐑣𐑨𐑮𐑦.”

“𐑝𐑧𐑮𐑦 𐑜𐑫𐑛,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. “𐑣𐑬𐑧𐑝𐑼, 𐑕𐑴 𐑨𐑟 𐑯𐑪𐑑 𐑑 𐑪𐑚𐑝𐑦𐑱𐑑 𐑞 𐑐𐑶𐑯𐑑 𐑝 𐑞 𐑣𐑴𐑤 𐑧𐑒𐑕𐑼𐑕𐑲𐑟, 𐑿 𐑢𐑦𐑤 𐑣𐑧𐑯𐑕𐑓𐑹𐑔 𐑩𐑛𐑮𐑧𐑕 𐑥𐑰 𐑨𐑟,” ·𐑝𐑧𐑮𐑟 𐑥𐑲𐑑 𐑯𐑪𐑑 𐑢𐑻𐑒 𐑧𐑯𐑦 𐑥𐑹, “·𐑥𐑼~·𐑕𐑐𐑵.”

“𐑴𐑒𐑱, ·𐑣𐑨𐑮𐑦,” ·𐑮𐑪𐑯 𐑕𐑧𐑛 𐑳𐑯𐑕𐑻𐑑𐑩𐑯𐑤𐑦.

\emph{𐑞 ·𐑓𐑹𐑕 𐑦𐑟 𐑯𐑪𐑑 𐑐𐑼𐑑𐑦𐑒𐑿𐑤𐑼𐑤𐑦 𐑕𐑑𐑮𐑪𐑙 𐑦𐑯 𐑞𐑦𐑕 𐑢𐑳𐑯.} “𐑒𐑷𐑤…𐑥𐑰…·𐑥𐑦𐑕𐑑𐑼…·𐑕𐑐𐑵.”

“𐑴𐑒𐑱, ·𐑥𐑦𐑕𐑑𐑼 ·𐑕𐑐𐑵—” ·𐑮𐑪𐑯 𐑕𐑑𐑪𐑐𐑑. “𐑲 𐑒𐑭𐑯𐑑 𐑛𐑵 𐑞𐑨𐑑, 𐑦𐑑 𐑥𐑱𐑒𐑕 𐑥𐑰 𐑓𐑰𐑤 𐑕𐑑𐑿𐑐𐑦𐑛.”

\emph{𐑞𐑨𐑑'𐑕 𐑯𐑪𐑑 𐑡𐑳𐑕𐑑 𐑩 𐑓𐑰𐑤𐑦𐑙.} “𐑴𐑒𐑱. \emph{𐑿} 𐑐𐑦𐑒 𐑩 𐑯𐑱𐑥.”

“·𐑥𐑼~·𐑒𐑨𐑯𐑩𐑯,” ·𐑮𐑪𐑯 𐑕𐑧𐑛 𐑨𐑑 𐑢𐑳𐑯𐑕. “𐑓 𐑞 ·𐑗𐑳𐑛𐑤𐑦 ·𐑒𐑨𐑯𐑩𐑯𐑟.”

“·𐑭…” ·𐑣𐑨𐑮𐑦 𐑯𐑿 𐑣𐑰 𐑢𐑪𐑟 𐑜𐑴𐑦𐑙 𐑑 𐑑𐑧𐑮𐑦𐑚𐑤𐑦 𐑮𐑦𐑜𐑮𐑧𐑑 𐑭𐑕𐑒𐑦𐑙 𐑞𐑦𐑕. “𐑣𐑵 𐑹 𐑢𐑪𐑑 𐑸 𐑞 ·𐑗𐑳𐑛𐑤𐑦 ·𐑒𐑨𐑯𐑩𐑯𐑟?”

“\emph{𐑣𐑵'𐑼 𐑞 ·𐑗𐑳𐑛𐑤𐑦 ·𐑒𐑨𐑯𐑩𐑯𐑟?} 𐑴𐑯𐑤𐑦 𐑞 𐑥𐑴𐑕𐑑 𐑚𐑮𐑦𐑤𐑘𐑩𐑯𐑑 𐑑𐑰𐑥 𐑦𐑯 𐑞 𐑣𐑴𐑤 𐑣𐑦𐑕𐑑𐑼𐑦 𐑝 ·𐑒𐑢𐑦𐑛𐑦𐑗! 𐑖𐑫𐑼, 𐑞𐑱 𐑓𐑦𐑯𐑦𐑖𐑑 𐑨𐑑 𐑞 𐑚𐑪𐑑𐑩𐑥 𐑝 𐑞 𐑤𐑰𐑜 𐑤𐑭𐑕𐑑 𐑘𐑽, 𐑚𐑳𐑑—”

“𐑢𐑪𐑑'𐑕 ·𐑒𐑢𐑦𐑛𐑦𐑗?”

𐑭𐑕𐑒𐑦𐑙 𐑞𐑦𐑕 𐑢𐑪𐑟 𐑷𐑤𐑕𐑴 𐑩 𐑥𐑦𐑕𐑑𐑱𐑒.

“𐑕𐑴 𐑤𐑧𐑑 𐑥𐑰 𐑜𐑧𐑑 𐑞𐑦𐑕 𐑕𐑑𐑮𐑱𐑑,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑨𐑟 𐑦𐑑 𐑕𐑰𐑥𐑛 𐑞𐑨𐑑 ·𐑮𐑪𐑯'𐑟 𐑧𐑒𐑕𐑐𐑤𐑩𐑯𐑱𐑖𐑩𐑯 (𐑢𐑦𐑞 𐑩𐑕𐑴𐑖𐑦𐑱𐑑𐑩𐑛 𐑣𐑨𐑯𐑛 𐑡𐑧𐑕𐑗𐑼𐑟) 𐑢𐑪𐑟 𐑢𐑲𐑯𐑛𐑦𐑙 𐑛𐑬𐑯. “𐑒𐑨𐑗𐑦𐑙 𐑞 ·𐑕𐑯𐑦𐑗 𐑦𐑟 𐑢𐑻𐑔 \emph{𐑢𐑳𐑯 𐑣𐑳𐑯𐑛𐑮𐑩𐑛 𐑯 𐑓𐑦𐑓𐑑𐑦 𐑐𐑶𐑯𐑑𐑕?}”

“𐑘𐑧𐑩—”

“𐑣𐑬 𐑥𐑧𐑯𐑦 𐑑𐑧𐑯-𐑐𐑶𐑯𐑑 𐑜𐑴𐑤𐑟 𐑛𐑳𐑟 𐑢𐑳𐑯 𐑕𐑲𐑛 𐑿𐑠𐑵𐑩𐑤𐑦 𐑕𐑒𐑹 \emph{𐑯𐑪𐑑} 𐑒𐑬𐑯𐑑𐑦𐑙 𐑞 ·𐑕𐑯𐑦𐑗?”

“𐑳𐑥, 𐑥𐑱𐑚𐑰 𐑓𐑦𐑓𐑑𐑰𐑯 𐑹 𐑑𐑢𐑧𐑯𐑑𐑦 𐑦𐑯 𐑐𐑮𐑩𐑓𐑧𐑖𐑩𐑯𐑩𐑤 𐑜𐑱𐑥𐑟—”

“𐑞𐑨𐑑'𐑕 𐑡𐑳𐑕𐑑 𐑮𐑪𐑙. 𐑞𐑨𐑑 𐑝𐑲𐑩𐑤𐑱𐑑𐑕 𐑧𐑝𐑮𐑦 𐑐𐑪𐑕𐑩𐑚𐑩𐑤 𐑮𐑵𐑤 𐑝 𐑜𐑱𐑥 𐑛𐑦𐑟𐑲𐑯. 𐑤𐑫𐑒, 𐑞 𐑮𐑧𐑕𐑑 𐑝 𐑞𐑦𐑕 𐑜𐑱𐑥 𐑕𐑬𐑯𐑛𐑟 𐑤𐑲𐑒 𐑦𐑑 𐑥𐑲𐑑 𐑥𐑱𐑒 𐑕𐑧𐑯𐑕, 𐑕𐑹𐑑 𐑝, 𐑓 𐑩 𐑕𐑐𐑹𐑑 𐑲 𐑥𐑰𐑯, 𐑚𐑳𐑑 𐑿'𐑼 𐑚𐑱𐑕𐑦𐑒𐑤𐑦 𐑕𐑱𐑦𐑙 𐑞𐑨𐑑 𐑒𐑨𐑗𐑦𐑙 𐑞 ·𐑕𐑯𐑦𐑗 𐑴𐑝𐑼𐑢𐑧𐑤𐑥𐑟 𐑷𐑤𐑥𐑴𐑕𐑑 𐑧𐑯𐑦 𐑹𐑛𐑦𐑯𐑼𐑦 𐑐𐑶𐑯𐑑 𐑕𐑐𐑮𐑧𐑛. 𐑞 𐑑𐑵 ·𐑕𐑰𐑒𐑼𐑟 𐑸 𐑳𐑐 𐑞𐑺 𐑓𐑤𐑲𐑦𐑙 𐑼𐑬𐑯𐑛 𐑤𐑫𐑒𐑦𐑙 𐑓 𐑞 ·𐑕𐑯𐑦𐑗 𐑯 𐑿𐑠𐑵𐑩𐑤𐑦 𐑯𐑪𐑑 𐑦𐑯𐑑𐑼𐑨𐑒𐑑𐑦𐑙 𐑢𐑦𐑞 𐑧𐑯𐑦𐑢𐑳𐑯 𐑧𐑤𐑕, 𐑕𐑐𐑪𐑑𐑦𐑙 𐑞 ·𐑕𐑯𐑦𐑗 𐑓𐑻𐑕𐑑 𐑦𐑟 𐑜𐑴𐑦𐑙 𐑑 𐑚𐑰 𐑥𐑴𐑕𐑑𐑤𐑦 𐑤𐑳𐑒—”

“𐑦𐑑'𐑕 𐑯𐑪𐑑 𐑤𐑳𐑒!” 𐑐𐑮𐑴𐑑𐑧𐑕𐑑𐑩𐑛 ·𐑮𐑪𐑯. “𐑿'𐑝 𐑜𐑪𐑑 𐑑 𐑒𐑰𐑐 𐑘𐑹 𐑲𐑟 𐑥𐑵𐑝𐑦𐑙 𐑦𐑯 𐑞 𐑮𐑲𐑑 𐑐𐑨𐑑𐑼𐑯—”

“𐑞𐑨𐑑'𐑕 𐑯𐑪𐑑 \emph{𐑦𐑯𐑑𐑼𐑨𐑒𐑑𐑦𐑝}, 𐑞𐑺'𐑟 𐑯𐑴 𐑚𐑨𐑒-𐑯-𐑓𐑹𐑔 𐑢𐑦𐑞 𐑞 𐑳𐑞𐑼 𐑐𐑤𐑱𐑼 𐑯 𐑣𐑬 𐑥𐑳𐑗 𐑓𐑳𐑯 𐑦𐑟 𐑦𐑑 𐑑 𐑢𐑪𐑗 𐑕𐑳𐑥𐑢𐑳𐑯 𐑦𐑯𐑒𐑮𐑧𐑛𐑩𐑚𐑤𐑦 𐑜𐑫𐑛 𐑨𐑑 𐑥𐑵𐑝𐑦𐑙 𐑞𐑺 𐑲𐑟? 𐑯 𐑞𐑧𐑯 𐑢𐑦𐑗𐑧𐑝𐑼 ·𐑕𐑰𐑒𐑼 𐑜𐑧𐑑𐑕 𐑤𐑳𐑒𐑦 𐑕𐑢𐑵𐑐𐑕 𐑦𐑯 𐑯 𐑜𐑮𐑨𐑚𐑟 𐑞 ·𐑕𐑯𐑦𐑗 𐑯 𐑥𐑱𐑒𐑕 𐑧𐑝𐑮𐑦𐑢𐑳𐑯 𐑧𐑤𐑕'𐑩𐑟 𐑢𐑻𐑒 𐑥𐑵𐑑. 𐑦𐑑'𐑕 𐑤𐑲𐑒 𐑕𐑳𐑥𐑢𐑳𐑯 𐑑𐑫𐑒 𐑩 𐑮𐑾𐑤 𐑜𐑱𐑥 𐑯 𐑜𐑮𐑭𐑓𐑑𐑩𐑛 𐑪𐑯 𐑞𐑦𐑕 𐑐𐑶𐑯𐑑𐑤𐑩𐑕 𐑧𐑒𐑕𐑑𐑮𐑩 𐑐𐑩𐑟𐑦𐑖𐑩𐑯 𐑕𐑴 𐑞𐑨𐑑 𐑿 𐑒𐑫𐑛 𐑚𐑰 𐑞 ·𐑥𐑴𐑕𐑑 ·𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑 ·𐑐𐑤𐑱𐑼 𐑢𐑦𐑞𐑬𐑑 𐑯𐑰𐑛𐑦𐑙 𐑑 𐑮𐑾𐑤𐑦 𐑜𐑧𐑑 𐑦𐑯𐑝𐑪𐑤𐑝𐑛 𐑹 𐑤𐑻𐑯 𐑞 𐑮𐑧𐑕𐑑 𐑝 𐑦𐑑. 𐑣𐑵 𐑢𐑪𐑟 𐑞 𐑓𐑻𐑕𐑑 ·𐑕𐑰𐑒𐑼, 𐑞 ·𐑒𐑦𐑙'𐑟 𐑦𐑛𐑾𐑑 𐑕𐑳𐑯 𐑣𐑵 𐑢𐑪𐑯𐑑𐑩𐑛 𐑑 𐑐𐑤𐑱 ·𐑒𐑢𐑦𐑛𐑦𐑗 𐑚𐑳𐑑 𐑒𐑫𐑛𐑩𐑯𐑑 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑞 𐑮𐑵𐑤𐑟?” 𐑨𐑒𐑗𐑵𐑩𐑤𐑦, 𐑯𐑬 𐑞𐑨𐑑 ·𐑣𐑨𐑮𐑦 𐑔𐑷𐑑 𐑩𐑚𐑬𐑑 𐑦𐑑, 𐑞𐑨𐑑 𐑕𐑰𐑥𐑛 𐑤𐑲𐑒 𐑩 𐑕𐑼𐑐𐑮𐑲𐑟𐑦𐑙𐑤𐑦 𐑜𐑫𐑛 𐑣𐑲𐑐𐑪𐑔𐑦𐑕𐑦𐑕. 𐑐𐑫𐑑 𐑣𐑦𐑥 𐑪𐑯 𐑩 𐑚𐑮𐑵𐑥𐑕𐑑𐑦𐑒 𐑯 𐑑𐑧𐑤 𐑣𐑦𐑥 𐑑 𐑒𐑨𐑗 𐑞 𐑖𐑲𐑯𐑦 𐑔𐑦𐑙…

·𐑮𐑪𐑯'𐑟 𐑓𐑱𐑕 𐑐𐑫𐑤𐑛 𐑦𐑯𐑑𐑵 𐑩 𐑕𐑒𐑬𐑤. “𐑦𐑓 𐑿 𐑛𐑴𐑯𐑑 𐑤𐑲𐑒 ·𐑒𐑢𐑦𐑛𐑦𐑗, 𐑿 𐑛𐑴𐑯𐑑 𐑣𐑨𐑓 𐑑 𐑥𐑱𐑒 𐑓𐑳𐑯 𐑝 𐑦𐑑!”

“𐑦𐑓 𐑿 𐑒𐑭𐑯𐑑 𐑒𐑮𐑦𐑑𐑦𐑕𐑲𐑟, 𐑿 𐑒𐑭𐑯𐑑 𐑪𐑐𐑑𐑦𐑥𐑲𐑟. 𐑲'𐑥 𐑕𐑩𐑡𐑧𐑕𐑑𐑦𐑙 𐑣𐑬 𐑑 \emph{𐑦𐑥𐑐𐑮𐑵𐑝 𐑞 𐑜𐑱𐑥}. 𐑯 𐑦𐑑'𐑕 𐑝𐑧𐑮𐑦 𐑕𐑦𐑥𐑐𐑩𐑤. 𐑜𐑧𐑑 𐑮𐑦𐑛 𐑝 𐑞 ·𐑕𐑯𐑦𐑗.”

“𐑞𐑱 𐑢𐑴𐑯𐑑 𐑗𐑱𐑯𐑡 𐑞 𐑜𐑱𐑥 𐑡𐑳𐑕𐑑 '𐑒𐑷𐑟 \emph{𐑿} 𐑕𐑱 𐑕𐑴!”

“𐑲 \emph{𐑨𐑥} 𐑞 ·𐑚𐑶-𐑣𐑵-·𐑤𐑦𐑝𐑛, 𐑿 𐑯𐑴. 𐑐𐑰𐑐𐑩𐑤 𐑢𐑦𐑤 𐑤𐑦𐑕𐑩𐑯 𐑑 𐑥𐑰. 𐑯 𐑥𐑱𐑚𐑰 𐑦𐑓 𐑲 𐑒𐑨𐑯 𐑐𐑼𐑕𐑢𐑱𐑛 𐑞𐑧𐑥 𐑑 𐑗𐑱𐑯𐑡 𐑞 𐑜𐑱𐑥 𐑨𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕, 𐑞 𐑦𐑯𐑩𐑝𐑱𐑖𐑩𐑯 𐑢𐑦𐑤 𐑕𐑐𐑮𐑧𐑛.”

𐑩 𐑤𐑫𐑒 𐑝 𐑨𐑚𐑕𐑩𐑤𐑵𐑑 𐑣𐑪𐑮𐑼 𐑢𐑪𐑟 𐑕𐑐𐑮𐑧𐑛𐑦𐑙 𐑴𐑝𐑼 ·𐑮𐑪𐑯'𐑟 𐑓𐑱𐑕. “𐑚𐑳𐑑, 𐑚𐑳𐑑 𐑦𐑓 𐑿 𐑜𐑧𐑑 𐑮𐑦𐑛 𐑝 𐑞 ·𐑕𐑯𐑦𐑗, 𐑣𐑬 𐑢𐑦𐑤 𐑧𐑯𐑦𐑢𐑳𐑯 𐑯𐑴 𐑢𐑧𐑯 𐑞 𐑜𐑱𐑥 𐑧𐑯𐑛𐑟?”

“\emph{𐑚𐑲…𐑩…𐑒𐑤𐑪𐑒.} 𐑦𐑑 𐑢𐑫𐑛 𐑚𐑰 𐑩 𐑤𐑪𐑑 𐑓𐑺𐑼 𐑞𐑨𐑯 𐑣𐑨𐑝𐑦𐑙 𐑞 𐑜𐑱𐑥 𐑕𐑳𐑥𐑑𐑲𐑥𐑟 𐑧𐑯𐑛 𐑭𐑓𐑑𐑼 𐑑𐑧𐑯 𐑥𐑦𐑯𐑦𐑑𐑕 𐑯 𐑕𐑳𐑥𐑑𐑲𐑥𐑟 𐑯𐑪𐑑 𐑧𐑯𐑛 𐑓 𐑬𐑼𐑟, 𐑯 𐑞 𐑖𐑧𐑡𐑵𐑤 𐑢𐑫𐑛 𐑚𐑰 𐑩 𐑤𐑪𐑑 𐑥𐑹 𐑐𐑮𐑦𐑛𐑦𐑒𐑑𐑩𐑚𐑩𐑤 𐑓 𐑞 𐑕𐑐𐑧𐑒𐑑𐑱𐑑𐑼𐑟, 𐑑𐑵.” ·𐑣𐑨𐑮𐑦 𐑕𐑲𐑛. “𐑴, 𐑕𐑑𐑪𐑐 𐑜𐑦𐑝𐑦𐑙 𐑥𐑰 𐑞𐑨𐑑 𐑤𐑫𐑒 𐑝 𐑨𐑚𐑕𐑩𐑤𐑵𐑑 𐑣𐑪𐑮𐑼, 𐑲 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑢𐑴𐑯𐑑 \emph{𐑨𐑒𐑗𐑵𐑩𐑤𐑦} 𐑑𐑱𐑒 𐑞 𐑑𐑲𐑥 𐑑 𐑛𐑦𐑕𐑑𐑮𐑶 𐑞𐑦𐑕 𐑐𐑩𐑔𐑧𐑑𐑦𐑒 𐑦𐑒𐑕𐑒𐑿𐑕 𐑓 𐑩 𐑯𐑨𐑖𐑩𐑯𐑩𐑤 𐑕𐑐𐑹𐑑 𐑯 𐑮𐑰𐑥𐑱𐑒 𐑦𐑑 𐑕𐑑𐑮𐑪𐑙𐑜𐑼 𐑯 𐑕𐑥𐑸𐑑𐑼 𐑦𐑯 𐑥𐑲 𐑴𐑯 𐑦𐑥𐑦𐑡. 𐑲'𐑝 𐑜𐑪𐑑 𐑢𐑱, 𐑢𐑱, \emph{𐑢𐑱} 𐑥𐑹 𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑 𐑕𐑑𐑳𐑓 𐑑 𐑢𐑳𐑮𐑦 𐑩𐑚𐑬𐑑.” ·𐑣𐑨𐑮𐑦 𐑤𐑫𐑒𐑑 𐑔𐑷𐑑𐑓𐑩𐑤. “𐑞𐑧𐑯 𐑩𐑜𐑱𐑯, 𐑦𐑑 𐑢𐑫𐑛𐑩𐑯𐑑 \emph{𐑑𐑱𐑒} 𐑥𐑳𐑗 𐑑𐑲𐑥 𐑑 𐑮𐑲𐑑 𐑳𐑐 𐑞 ·𐑯𐑲𐑯𐑑𐑦-·𐑓𐑲𐑝 ·𐑔𐑰𐑕𐑰𐑟 𐑝 𐑞 ·𐑕𐑯𐑦𐑗𐑤𐑩𐑕 ·𐑮𐑧𐑓𐑼𐑥𐑱𐑖𐑩𐑯 𐑯 𐑯𐑱𐑤 𐑦𐑑 𐑑 𐑩 𐑗𐑻𐑗 𐑛𐑹—”

“·𐑐𐑪𐑑𐑼,” 𐑛𐑮𐑷𐑤𐑛 𐑩 𐑘𐑳𐑙 𐑚𐑶'𐑟 𐑝𐑶𐑕, “\emph{𐑢𐑪𐑑} 𐑦𐑟 𐑞𐑨𐑑 𐑪𐑯 𐑘𐑹 𐑓𐑱𐑕 𐑯 \emph{𐑢𐑪𐑑} 𐑦𐑟 𐑕𐑑𐑨𐑯𐑛𐑦𐑙 𐑯𐑧𐑒𐑕𐑑 𐑑 𐑿?”

𐑮𐑪𐑯'𐑟 𐑤𐑫𐑒 𐑝 𐑣𐑪𐑮𐑼 𐑢𐑪𐑟 𐑮𐑦𐑐𐑤𐑱𐑕𐑑 𐑚𐑲 𐑳𐑑𐑼 𐑣𐑱𐑑𐑮𐑩𐑛. “\emph{𐑿!}”

·𐑣𐑨𐑮𐑦 𐑑𐑻𐑯𐑛 𐑣𐑦𐑟 𐑣𐑧𐑛; 𐑯 𐑦𐑯𐑛𐑰𐑛 𐑦𐑑 𐑢𐑪𐑟 ·𐑛𐑮𐑱𐑒𐑴 ·𐑥𐑨𐑤𐑓𐑶, 𐑣𐑵 𐑥𐑲𐑑 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑓𐑹𐑕𐑑 𐑑 𐑢𐑺 𐑕𐑑𐑨𐑯𐑛𐑼𐑛 𐑕𐑒𐑵𐑤 𐑮𐑴𐑚𐑟, 𐑚𐑳𐑑 𐑢𐑪𐑟 𐑥𐑱𐑒𐑦𐑙 𐑳𐑐 𐑓 𐑞𐑨𐑑 𐑢𐑦𐑞 𐑩 𐑑𐑮𐑳𐑙𐑒 𐑤𐑫𐑒𐑦𐑙 𐑨𐑑 𐑤𐑰𐑕𐑑 𐑨𐑟 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 𐑯 𐑓𐑸 𐑥𐑹 𐑧𐑤𐑦𐑜𐑩𐑯𐑑 𐑞𐑨𐑯 ·𐑣𐑨𐑮𐑦'𐑟 𐑴𐑯, 𐑛𐑧𐑒𐑼𐑱𐑑𐑩𐑛 𐑦𐑯 𐑕𐑦𐑤𐑝𐑼 𐑯 𐑧𐑥𐑼𐑩𐑤𐑛𐑟 𐑯 𐑚𐑺𐑦𐑙 𐑢𐑪𐑑 ·𐑣𐑨𐑮𐑦 𐑜𐑧𐑕𐑑 𐑑 𐑚𐑰 𐑞 ·𐑥𐑨𐑤𐑓𐑶 𐑓𐑨𐑥𐑤𐑦 𐑒𐑮𐑧𐑕𐑑, 𐑩 𐑚𐑿𐑑𐑦𐑓𐑩𐑤 𐑓𐑨𐑙𐑛 𐑕𐑻𐑐𐑩𐑯𐑑 𐑴𐑝𐑼 𐑒𐑮𐑪𐑕𐑑 𐑲𐑝𐑼𐑦 𐑢𐑪𐑯𐑛𐑟.

“·𐑛𐑮𐑱𐑒𐑴!” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. “𐑼, 𐑹 ·𐑥𐑨𐑤𐑓𐑶 𐑦𐑓 𐑿 𐑐𐑮𐑦𐑓𐑻, 𐑞𐑴 𐑞𐑨𐑑 𐑒𐑲𐑯𐑛 𐑝 𐑕𐑬𐑯𐑛𐑟 𐑤𐑲𐑒 ·𐑤𐑵𐑕𐑾𐑕 𐑑 𐑥𐑰. 𐑲'𐑥 𐑜𐑤𐑨𐑛 𐑑 𐑕𐑰 𐑿'𐑼 𐑛𐑵𐑦𐑙 𐑕𐑴 𐑢𐑧𐑤 𐑭𐑓𐑑𐑼, 𐑳𐑥, 𐑬𐑼 𐑤𐑭𐑕𐑑 𐑥𐑰𐑑𐑦𐑙. 𐑞𐑦𐑕 𐑦𐑟 ·𐑮𐑪𐑯 ·𐑢𐑰𐑟𐑤𐑦. 𐑯 𐑲'𐑥 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑜𐑴 𐑦𐑯𐑒𐑪𐑜𐑯𐑰𐑑𐑴, 𐑕𐑴 𐑒𐑷𐑤 𐑥𐑰, 𐑱,” ·𐑣𐑨𐑮𐑦 𐑤𐑫𐑒𐑑 𐑛𐑬𐑯 𐑨𐑑 𐑣𐑦𐑟 𐑮𐑴𐑚𐑟, “·𐑥𐑦𐑕𐑑𐑼 ·𐑚𐑤𐑨𐑒.”

“\emph{·𐑣𐑨𐑮𐑦!}” 𐑣𐑦𐑕𐑑 ·𐑮𐑪𐑯. “𐑿 𐑒𐑭𐑯𐑑 𐑿𐑟 \emph{𐑞𐑨𐑑} 𐑯𐑱𐑥!”

·𐑣𐑨𐑮𐑦 𐑚𐑤𐑦𐑙𐑒𐑑. “𐑢𐑲 𐑯𐑪𐑑?” 𐑦𐑑 \emph{𐑕𐑬𐑯𐑛𐑩𐑛} 𐑯𐑲𐑕𐑤𐑦 𐑛𐑸𐑒, 𐑤𐑲𐑒 𐑩𐑯 𐑦𐑯𐑑𐑼𐑯𐑨𐑖𐑩𐑯𐑩𐑤 𐑥𐑨𐑯 𐑝 𐑥𐑦𐑕𐑑𐑼𐑦—

“𐑲'𐑛 𐑕𐑱 𐑦𐑑'𐑕 𐑩 \emph{𐑓𐑲𐑯} 𐑯𐑱𐑥,” 𐑕𐑧𐑛 ·𐑛𐑮𐑱𐑒𐑴, “𐑚𐑳𐑑 𐑦𐑑 𐑚𐑦𐑤𐑪𐑙𐑟 𐑑 𐑞 ·𐑯𐑴𐑚𐑩𐑤 𐑯 ·𐑥𐑴𐑕𐑑 ·𐑱𐑯𐑖𐑩𐑯𐑑 ·𐑣𐑬𐑕 𐑝 ·𐑚𐑤𐑨𐑒. 𐑲'𐑤 𐑒𐑷𐑤 𐑿 ·𐑥𐑼~·𐑕𐑦𐑤𐑝𐑼.”

“\emph{𐑿} 𐑜𐑧𐑑 𐑩𐑢𐑱 𐑓𐑮𐑪𐑥…𐑓𐑮𐑪𐑥 ·𐑥𐑼~·𐑜𐑴𐑤𐑛,” ·𐑮𐑪𐑯 𐑕𐑧𐑛 𐑒𐑴𐑤𐑛𐑤𐑦, 𐑯 𐑑𐑫𐑒 𐑩 𐑓𐑹𐑢𐑼𐑛 𐑕𐑑𐑧𐑐. “𐑣𐑰 𐑛𐑳𐑟𐑩𐑯𐑑 𐑯𐑰𐑛 𐑑 𐑑𐑷𐑒 𐑑 𐑞 𐑤𐑲𐑒𐑕 𐑝 𐑿!”

·𐑣𐑨𐑮𐑦 𐑮𐑱𐑟𐑛 𐑩 𐑐𐑤𐑩𐑒𐑱𐑑𐑦𐑙 𐑣𐑨𐑯𐑛. “𐑲'𐑤 𐑜𐑴 𐑚𐑲 ·𐑥𐑼~·𐑚𐑮𐑪𐑯𐑟, 𐑔𐑨𐑙𐑒𐑕 𐑓 𐑞 𐑯𐑱𐑥𐑦𐑙 𐑕𐑒𐑰𐑥𐑩. 𐑯, ·𐑮𐑪𐑯, 𐑳𐑥,” ·𐑣𐑨𐑮𐑦 𐑕𐑑𐑮𐑳𐑜𐑩𐑤𐑛 𐑑 𐑓𐑲𐑯𐑛 𐑩 𐑢𐑱 𐑑 𐑕𐑱 𐑞𐑦𐑕, “𐑲'𐑥 𐑜𐑤𐑨𐑛 𐑿'𐑼 𐑕𐑴…𐑦𐑯𐑔𐑿𐑟𐑦𐑨𐑕𐑑𐑦𐑒 𐑩𐑚𐑬𐑑 𐑐𐑮𐑩𐑑𐑧𐑒𐑑𐑦𐑙 𐑥𐑰, 𐑚𐑳𐑑 𐑲 𐑛𐑴𐑯𐑑 𐑐𐑼𐑑𐑦𐑒𐑿𐑤𐑼𐑤𐑦 𐑥𐑲𐑯𐑛 𐑑𐑷𐑒𐑦𐑙 𐑑 ·𐑛𐑮𐑱𐑒𐑴—”

𐑞𐑦𐑕 𐑢𐑪𐑟 𐑩𐑐𐑨𐑮𐑩𐑯𐑑𐑤𐑦 𐑞 𐑤𐑭𐑕𐑑 𐑕𐑑𐑮𐑷 𐑓 ·𐑮𐑪𐑯, 𐑣𐑵 𐑕𐑐𐑳𐑯 𐑪𐑯 ·𐑣𐑨𐑮𐑦 𐑢𐑦𐑞 𐑲𐑟 𐑯𐑬 𐑩𐑓𐑤𐑱𐑥 𐑢𐑦𐑞 𐑬𐑑𐑮𐑱𐑡. “\emph{𐑢𐑪𐑑?} 𐑛𐑵 𐑿 \emph{𐑯𐑴} 𐑣𐑵 𐑞𐑦𐑕 𐑦𐑟?”

“𐑘𐑧𐑕, ·𐑮𐑪𐑯,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, “𐑿 𐑥𐑱 𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑞𐑨𐑑 𐑲 𐑒𐑷𐑤𐑛 𐑣𐑦𐑥 ·𐑛𐑮𐑱𐑒𐑴 𐑢𐑦𐑞𐑬𐑑 𐑣𐑦𐑥 𐑯𐑰𐑛𐑦𐑙 𐑑 𐑦𐑯𐑑𐑮𐑩𐑛𐑿𐑕 𐑣𐑦𐑥𐑕𐑧𐑤𐑓.”

·𐑛𐑮𐑱𐑒𐑴 𐑕𐑯𐑦𐑜𐑼𐑛. 𐑞𐑧𐑯 𐑣𐑦𐑟 𐑲𐑟 𐑤𐑦𐑑 𐑪𐑯 𐑞 𐑢𐑲𐑑 𐑬𐑤 𐑪𐑯 ·𐑮𐑪𐑯'𐑟 𐑖𐑴𐑤𐑛𐑼. “𐑴, 𐑢𐑪𐑑'𐑕 \emph{𐑞𐑦𐑕}?” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛 𐑦𐑯 𐑩 𐑛𐑮𐑷𐑤 𐑮𐑦𐑗 𐑢𐑦𐑞 𐑥𐑨𐑤𐑦𐑕. “𐑢𐑺'𐑟 𐑞 𐑓𐑱𐑥𐑩𐑕 ·𐑢𐑰𐑟𐑤𐑦 𐑓𐑨𐑥𐑤𐑦 𐑮𐑨𐑑?”

“𐑚𐑧𐑮𐑦𐑛 𐑦𐑯 𐑞 𐑚𐑨𐑒𐑘𐑸𐑛,” ·𐑮𐑪𐑯 𐑕𐑧𐑛 𐑒𐑴𐑤𐑛𐑤𐑦.

“𐑷, 𐑣𐑬 𐑕𐑨𐑛. 𐑐𐑪𐑑…𐑭, ·𐑥𐑼~·𐑚𐑮𐑪𐑯𐑟, 𐑲 𐑖𐑫𐑛 𐑥𐑧𐑯𐑖𐑩𐑯 𐑞𐑨𐑑 𐑞 ·𐑢𐑰𐑟𐑤𐑦 𐑓𐑨𐑥𐑤𐑦 𐑦𐑟 𐑢𐑲𐑛𐑤𐑦 𐑩𐑜𐑮𐑰𐑛 𐑑 𐑣𐑨𐑝 \emph{𐑞 𐑚𐑧𐑕𐑑 𐑐𐑧𐑑 𐑕𐑑𐑹𐑦 𐑧𐑝𐑼}. 𐑢𐑪𐑯𐑑 𐑑 𐑑𐑧𐑤 𐑦𐑑, ·𐑢𐑰𐑟𐑤𐑦?”

𐑮𐑪𐑯'𐑟 𐑓𐑱𐑕 𐑒𐑩𐑯𐑑𐑹𐑑𐑩𐑛. “𐑿 𐑢𐑫𐑛𐑩𐑯𐑑 𐑔𐑦𐑙𐑒 𐑦𐑑 𐑢𐑪𐑟 𐑓𐑳𐑯𐑦 𐑦𐑓 𐑦𐑑 𐑣𐑨𐑐𐑩𐑯𐑛 𐑑 \emph{𐑘𐑹} 𐑓𐑨𐑥𐑤𐑦!”

“𐑴,” ·𐑛𐑮𐑱𐑒𐑴 𐑐𐑻𐑛, “𐑚𐑳𐑑 𐑦𐑑 𐑢𐑫𐑛𐑩𐑯𐑑 𐑧𐑝𐑼 \emph{𐑣𐑨𐑐𐑩𐑯} 𐑑 𐑞 ·𐑥𐑨𐑤𐑓𐑶𐑟.”

𐑮𐑪𐑯'𐑟 𐑣𐑨𐑯𐑛𐑟 𐑒𐑤𐑧𐑯𐑗𐑑 𐑦𐑯𐑑𐑵 𐑓𐑦𐑕𐑑𐑕—

“𐑞𐑨𐑑'𐑕 𐑦𐑯𐑳𐑓,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑐𐑫𐑑𐑦𐑙 𐑨𐑟 𐑥𐑳𐑗 𐑒𐑢𐑲𐑩𐑑 𐑷𐑔𐑪𐑮𐑦𐑑𐑦 𐑦𐑯𐑑𐑵 𐑞 𐑝𐑶𐑕 𐑨𐑟 𐑣𐑰 𐑒𐑫𐑛 𐑥𐑨𐑯𐑦𐑡. 𐑦𐑑 𐑢𐑪𐑟 𐑒𐑤𐑽 𐑞𐑨𐑑 𐑢𐑪𐑑𐑧𐑝𐑼 𐑞𐑦𐑕 𐑢𐑪𐑟 𐑩𐑚𐑬𐑑, 𐑦𐑑 𐑢𐑪𐑟 𐑩 𐑐𐑱𐑯𐑓𐑩𐑤 𐑥𐑧𐑥𐑼𐑦 𐑓 𐑞 𐑮𐑧𐑛-𐑣𐑺𐑛 𐑒𐑦𐑛. “𐑦𐑓 ·𐑮𐑪𐑯 𐑛𐑳𐑟𐑩𐑯𐑑 𐑢𐑪𐑯𐑑 𐑑 𐑑𐑷𐑒 𐑩𐑚𐑬𐑑 𐑦𐑑, 𐑣𐑰 𐑛𐑳𐑟𐑩𐑯𐑑 𐑣𐑨𐑓 𐑑 𐑑𐑷𐑒 𐑩𐑚𐑬𐑑 𐑦𐑑, 𐑯 𐑲'𐑛 𐑭𐑕𐑒 𐑞𐑨𐑑 𐑿 𐑯𐑪𐑑 𐑑𐑷𐑒 𐑩𐑚𐑬𐑑 𐑦𐑑 𐑲𐑞𐑼.”

·𐑛𐑮𐑱𐑒𐑴 𐑑𐑻𐑯𐑛 𐑩 𐑕𐑼𐑐𐑮𐑲𐑟𐑛 𐑤𐑫𐑒 𐑪𐑯 ·𐑣𐑨𐑮𐑦, 𐑯 ·𐑮𐑪𐑯 𐑯𐑪𐑛𐑩𐑛. “𐑞𐑨𐑑'𐑕 𐑮𐑲𐑑, ·𐑣𐑨𐑮𐑦! 𐑲 𐑥𐑰𐑯 ·𐑥𐑼~·𐑚𐑮𐑪𐑯𐑟! 𐑿 𐑕𐑰 𐑢𐑪𐑑 𐑒𐑲𐑯𐑛 𐑝 𐑐𐑻𐑕𐑩𐑯 𐑣𐑰 𐑦𐑟? 𐑯𐑬 𐑑𐑧𐑤 𐑣𐑦𐑥 𐑑 𐑜𐑴 𐑩𐑢𐑱!”

·𐑣𐑨𐑮𐑦 𐑒𐑬𐑯𐑑𐑩𐑛 𐑑 𐑑𐑧𐑯 𐑦𐑯𐑕𐑲𐑛 𐑣𐑦𐑟 𐑣𐑧𐑛, 𐑢𐑦𐑗 𐑓 𐑣𐑦𐑥 𐑢𐑪𐑟 𐑩 𐑝𐑧𐑮𐑦 𐑒𐑢𐑦𐑒 \emph{12345678910}—𐑩𐑯 𐑪𐑛 𐑣𐑨𐑚𐑦𐑑 𐑤𐑧𐑓𐑑 𐑴𐑝𐑼 𐑓𐑮𐑪𐑥 𐑞 𐑱𐑡 𐑝 𐑓𐑲𐑝 𐑢𐑧𐑯 𐑣𐑦𐑟 𐑥𐑳𐑞𐑼 𐑣𐑨𐑛 𐑓𐑻𐑕𐑑 𐑦𐑯𐑕𐑑𐑮𐑳𐑒𐑑𐑩𐑛 𐑣𐑦𐑥 𐑑 𐑛𐑵 𐑦𐑑, 𐑯 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑮𐑰𐑟𐑩𐑯𐑛 𐑞𐑨𐑑 𐑣𐑦𐑟 𐑢𐑱 𐑢𐑪𐑟 𐑓𐑭𐑕𐑑𐑼 𐑯 𐑷𐑑 𐑑 𐑚𐑰 𐑡𐑳𐑕𐑑 𐑨𐑟 𐑦𐑓𐑧𐑒𐑑𐑦𐑝. “𐑲'𐑥 𐑯𐑪𐑑 𐑑𐑧𐑤𐑦𐑙 𐑣𐑦𐑥 𐑑 𐑜𐑴 𐑩𐑢𐑱,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑒𐑭𐑥𐑤𐑦. “𐑣𐑰'𐑟 𐑢𐑧𐑤𐑒𐑩𐑥 𐑑 𐑑𐑷𐑒 𐑑 𐑥𐑰 𐑦𐑓 𐑣𐑰 𐑢𐑪𐑯𐑑𐑕.”

“𐑢𐑧𐑤, 𐑲 𐑛𐑴𐑯𐑑 𐑦𐑯𐑑𐑧𐑯𐑛 𐑑 𐑣𐑨𐑙 𐑼𐑬𐑯𐑛 𐑢𐑦𐑞 𐑧𐑯𐑦𐑢𐑳𐑯 𐑣𐑵 𐑣𐑨𐑙𐑟 𐑼𐑬𐑯𐑛 𐑢𐑦𐑞 ·𐑛𐑮𐑱𐑒𐑴 ·𐑥𐑨𐑤𐑓𐑶,” ·𐑮𐑪𐑯 𐑩𐑯𐑬𐑯𐑕𐑑 𐑒𐑴𐑤𐑛𐑤𐑦.

·𐑣𐑨𐑮𐑦 𐑖𐑮𐑳𐑜𐑛. “𐑞𐑨𐑑'𐑕 𐑳𐑐 𐑑 𐑿. \emph{𐑲} 𐑛𐑴𐑯𐑑 𐑦𐑯𐑑𐑧𐑯𐑛 𐑑 𐑤𐑧𐑑 𐑧𐑯𐑦𐑢𐑳𐑯 𐑕𐑱 𐑣𐑵 𐑲 𐑒𐑨𐑯 𐑯 𐑒𐑭𐑯𐑑 𐑣𐑨𐑙 𐑼𐑬𐑯𐑛 𐑢𐑦𐑞.” 𐑕𐑲𐑤𐑩𐑯𐑑𐑤𐑦 𐑗𐑭𐑯𐑑𐑦𐑙, \emph{𐑐𐑤𐑰𐑟 𐑜𐑴 𐑩𐑢𐑱, 𐑐𐑤𐑰𐑟 𐑜𐑴 𐑩𐑢𐑱…}

·𐑮𐑪𐑯'𐑟 𐑓𐑱𐑕 𐑢𐑧𐑯𐑑 𐑚𐑤𐑨𐑙𐑒 𐑢𐑦𐑞 𐑕𐑼𐑐𐑮𐑲𐑟, 𐑤𐑲𐑒 𐑣𐑰'𐑛 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑦𐑒𐑕𐑐𐑧𐑒𐑑𐑩𐑛 𐑞𐑨𐑑 𐑤𐑲𐑯 𐑑 𐑢𐑻𐑒. 𐑞𐑧𐑯 ·𐑮𐑪𐑯 𐑕𐑐𐑳𐑯 𐑩𐑚𐑬𐑑, 𐑘𐑨𐑙𐑒𐑑 𐑣𐑦𐑟 𐑤𐑳𐑜𐑦𐑡'𐑩𐑟 𐑤𐑰𐑛 𐑯 𐑕𐑑𐑹𐑥𐑛 𐑪𐑓 𐑛𐑬𐑯 𐑞 𐑐𐑤𐑨𐑑𐑓𐑹𐑥.

“𐑦𐑓 𐑿 𐑛𐑦𐑛𐑩𐑯𐑑 𐑤𐑲𐑒 𐑣𐑦𐑥,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛 𐑒𐑘𐑫𐑼𐑾𐑕𐑤𐑦, “𐑢𐑲 𐑛𐑦𐑛𐑩𐑯𐑑 𐑿 𐑡𐑳𐑕𐑑 𐑢𐑷𐑒 𐑩𐑢𐑱?”

“𐑳𐑥…𐑣𐑦𐑟 𐑥𐑳𐑞𐑼 𐑣𐑧𐑤𐑐𐑑 𐑥𐑰 𐑓𐑦𐑜𐑼 𐑬𐑑 𐑣𐑬 𐑑 𐑜𐑧𐑑 𐑑 𐑞𐑦𐑕 𐑐𐑤𐑨𐑑𐑓𐑹𐑥 𐑓𐑮𐑪𐑥 ·𐑒𐑦𐑙'𐑟 ·𐑒𐑮𐑪𐑕 ·𐑕𐑑𐑱𐑖𐑩𐑯, 𐑕𐑴 𐑦𐑑 𐑢𐑪𐑟 𐑒𐑲𐑯𐑛 𐑝 𐑣𐑸𐑛 𐑑 𐑑𐑧𐑤 𐑣𐑦𐑥 𐑑 𐑜𐑧𐑑 𐑤𐑪𐑕𐑑. 𐑯 𐑦𐑑'𐑕 𐑯𐑪𐑑 𐑞𐑨𐑑 𐑲 \emph{𐑣𐑱𐑑} 𐑞𐑦𐑕 ·𐑮𐑪𐑯 𐑜𐑲,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, “𐑲 𐑡𐑳𐑕𐑑, 𐑡𐑳𐑕𐑑…” ·𐑣𐑨𐑮𐑦 𐑕𐑻𐑗𐑑 𐑓 𐑢𐑻𐑛𐑟.

“𐑛𐑴𐑯𐑑 𐑕𐑰 𐑧𐑯𐑦 𐑮𐑰𐑟𐑩𐑯 𐑓 𐑣𐑦𐑥 𐑑 𐑦𐑜𐑟𐑦𐑕𐑑?” 𐑪𐑓𐑼𐑛 ·𐑛𐑮𐑱𐑒𐑴.

“𐑐𐑮𐑦𐑑𐑦 𐑥𐑳𐑗.”

“𐑧𐑯𐑦𐑢𐑱, ·𐑐𐑪𐑑𐑼…𐑦𐑓 𐑿 𐑮𐑾𐑤𐑦 𐑢𐑻 𐑮𐑱𐑟𐑛 𐑚𐑲 ·𐑥𐑳𐑜𐑩𐑤𐑟—” ·𐑛𐑮𐑱𐑒𐑴 𐑐𐑷𐑟𐑛 𐑣𐑽, 𐑨𐑟 𐑦𐑓 𐑢𐑱𐑑𐑦𐑙 𐑓 𐑩 𐑛𐑦𐑯𐑲𐑩𐑤, 𐑚𐑳𐑑 ·𐑣𐑨𐑮𐑦 𐑛𐑦𐑛𐑩𐑯𐑑 𐑕𐑱 𐑧𐑯𐑦𐑔𐑦𐑙 “—𐑞𐑧𐑯 𐑿 𐑥𐑲𐑑𐑩𐑯𐑑 𐑯𐑴 𐑢𐑪𐑑 𐑦𐑑'𐑕 𐑤𐑲𐑒 𐑑 𐑚𐑰 𐑓𐑱𐑥𐑩𐑕. 𐑐𐑰𐑐𐑩𐑤 𐑢𐑪𐑯𐑑 𐑑 𐑑𐑱𐑒 𐑳𐑐 \emph{𐑷𐑤} 𐑝 𐑬𐑼 𐑑𐑲𐑥. 𐑿 \emph{𐑣𐑨𐑓} 𐑑 𐑤𐑻𐑯 𐑑 𐑕𐑱 𐑯𐑴.”

·𐑣𐑨𐑮𐑦 𐑯𐑪𐑛𐑩𐑛, 𐑐𐑫𐑑𐑦𐑙 𐑩 𐑔𐑷𐑑𐑓𐑩𐑤 𐑤𐑫𐑒 𐑪𐑯 𐑣𐑦𐑟 𐑓𐑱𐑕. “𐑞𐑨𐑑 𐑕𐑬𐑯𐑛𐑟 𐑤𐑲𐑒 𐑜𐑫𐑛 𐑩𐑛𐑝𐑲𐑕.”

“𐑦𐑓 𐑿 𐑑𐑮𐑲 𐑑 𐑚𐑰 𐑯𐑲𐑕, 𐑿 𐑡𐑳𐑕𐑑 𐑧𐑯𐑛 𐑳𐑐 𐑕𐑐𐑧𐑯𐑛𐑦𐑙 𐑞 𐑥𐑴𐑕𐑑 𐑑𐑲𐑥 𐑢𐑦𐑞 𐑞 𐑐𐑫𐑖𐑾𐑕𐑑 𐑢𐑳𐑯𐑟. 𐑛𐑦𐑕𐑲𐑛 𐑣𐑵 𐑿 \emph{𐑢𐑪𐑯𐑑} 𐑑 𐑕𐑐𐑧𐑯𐑛 𐑑𐑲𐑥 𐑢𐑦𐑞 𐑯 𐑥𐑱𐑒 𐑧𐑝𐑮𐑦𐑢𐑳𐑯 𐑧𐑤𐑕 𐑤𐑰𐑝. 𐑿'𐑼 𐑡𐑳𐑕𐑑 𐑜𐑧𐑑𐑦𐑙 𐑣𐑽, ·𐑐𐑪𐑑𐑼, 𐑕𐑴 𐑧𐑝𐑮𐑦𐑢𐑳𐑯'𐑟 𐑜𐑴𐑦𐑙 𐑑 𐑡𐑳𐑡 𐑿 𐑚𐑲 𐑣𐑵 𐑞𐑱 𐑕𐑰 𐑿 𐑢𐑦𐑞, 𐑯 𐑿 𐑛𐑴𐑯𐑑 𐑢𐑪𐑯𐑑 𐑑 𐑚𐑰 𐑕𐑰𐑯 𐑢𐑦𐑞 𐑞 𐑤𐑲𐑒𐑕 𐑝 ·𐑮𐑪𐑯 ·𐑢𐑰𐑟𐑤𐑦.”

·𐑣𐑨𐑮𐑦 𐑯𐑪𐑛𐑩𐑛 𐑩𐑜𐑱𐑯. “𐑦𐑓 𐑿 𐑛𐑴𐑯𐑑 𐑥𐑲𐑯𐑛 𐑥𐑲 𐑭𐑕𐑒𐑦𐑙, 𐑣𐑬 𐑛𐑦𐑛 𐑿 𐑮𐑧𐑒𐑩𐑜𐑯𐑲𐑟 𐑥𐑰?”

“\emph{·𐑥𐑦𐑕𐑑𐑼 ·𐑚𐑮𐑪𐑯𐑟},” ·𐑛𐑮𐑱𐑒𐑴 𐑛𐑮𐑷𐑤𐑛, “𐑲 \emph{𐑣𐑨𐑝} 𐑥𐑧𐑑 𐑿, 𐑮𐑦𐑥𐑧𐑥𐑚𐑼. 𐑲 𐑕𐑷 𐑕𐑳𐑥𐑢𐑳𐑯 𐑜𐑴𐑦𐑙 𐑼𐑬𐑯𐑛 𐑢𐑦𐑞 𐑩 𐑕𐑒𐑸𐑓 𐑮𐑨𐑐𐑑 𐑼𐑬𐑯𐑛 𐑣𐑦𐑟 𐑣𐑧𐑛, 𐑤𐑫𐑒𐑦𐑙 𐑨𐑚𐑕𐑩𐑤𐑵𐑑𐑤𐑦 𐑮𐑦𐑛𐑦𐑒𐑿𐑤𐑩𐑕. 𐑕𐑴 𐑲 𐑑𐑫𐑒 𐑩 \emph{𐑜𐑧𐑕}.”

·𐑣𐑨𐑮𐑦 𐑚𐑬𐑛 𐑣𐑦𐑟 𐑣𐑧𐑛, 𐑩𐑒𐑕𐑧𐑐𐑑𐑦𐑙 𐑞 𐑒𐑪𐑥𐑐𐑤𐑦𐑥𐑧𐑯𐑑. “𐑲'𐑥 \emph{𐑑𐑧𐑮𐑦𐑚𐑤𐑦} 𐑕𐑪𐑮𐑦 𐑩𐑚𐑬𐑑 𐑞𐑨𐑑,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. “𐑬𐑼 𐑓𐑻𐑕𐑑 𐑥𐑰𐑑𐑦𐑙, 𐑲 𐑥𐑰𐑯. 𐑲 𐑛𐑦𐑛𐑩𐑯𐑑 𐑥𐑰𐑯 𐑑 𐑦𐑥𐑚𐑨𐑮𐑩𐑕 𐑿 𐑦𐑯 𐑓𐑮𐑳𐑯𐑑 𐑝 ·𐑤𐑵𐑕𐑾𐑕.”

·𐑛𐑮𐑱𐑒𐑴 𐑢𐑱𐑝𐑛 𐑦𐑑 𐑪𐑓 𐑢𐑲𐑤 𐑜𐑦𐑝𐑦𐑙 ·𐑣𐑨𐑮𐑦 𐑩𐑯 𐑪𐑛 𐑤𐑫𐑒. “𐑲 𐑡𐑳𐑕𐑑 𐑢𐑦𐑖 ·𐑓𐑭𐑞𐑼 𐑒𐑫𐑛 𐑣𐑨𐑝 𐑒𐑳𐑥 𐑦𐑯 𐑢𐑲𐑤 \emph{𐑿} 𐑢𐑻 𐑓𐑤𐑨𐑑𐑼𐑦𐑙 \emph{𐑥𐑰}—” ·𐑛𐑮𐑱𐑒𐑴 𐑤𐑭𐑓𐑑. “𐑚𐑳𐑑 𐑔𐑨𐑙𐑒 \emph{𐑿} 𐑓 𐑢𐑪𐑑 𐑿 𐑕𐑧𐑛 𐑑 ·𐑓𐑭𐑞𐑼. 𐑦𐑓 𐑯𐑪𐑑 𐑓 𐑞𐑨𐑑, 𐑲 𐑥𐑲𐑑'𐑝 𐑣𐑨𐑛 𐑩 𐑣𐑸𐑛𐑼 𐑑𐑲𐑥 𐑦𐑒𐑕𐑐𐑤𐑱𐑯𐑦𐑙.”

·𐑣𐑨𐑮𐑦 𐑕𐑢𐑧𐑐𐑑 𐑩 𐑛𐑰𐑐𐑼 𐑚𐑬. “𐑯 𐑔𐑨𐑙𐑒 \emph{𐑿} 𐑓 𐑮𐑦𐑕𐑦𐑐𐑮𐑩𐑒𐑱𐑑𐑦𐑙 𐑢𐑦𐑞 𐑢𐑪𐑑 𐑿 𐑕𐑧𐑛 𐑑 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤.”

“𐑿'𐑼 𐑢𐑧𐑤𐑒𐑩𐑥. 𐑞𐑴 𐑢𐑳𐑯 𐑝 𐑞 𐑩𐑕𐑦𐑕𐑑𐑩𐑯𐑑𐑕 𐑥𐑳𐑕𐑑'𐑝 𐑕𐑢𐑹𐑯 𐑣𐑻 𐑒𐑤𐑴𐑕𐑩𐑕𐑑 𐑓𐑮𐑧𐑯𐑛 𐑑 𐑨𐑚𐑕𐑩𐑤𐑵𐑑 𐑕𐑰𐑒𐑮𐑩𐑕𐑦, 𐑚𐑦𐑒𐑪𐑟 ·𐑓𐑭𐑞𐑼 𐑕𐑧𐑟 𐑞𐑺'𐑼 \emph{𐑢𐑽𐑛 𐑮𐑵𐑥𐑼𐑟} 𐑜𐑴𐑦𐑙 𐑼𐑬𐑯𐑛, 𐑤𐑲𐑒 𐑿 𐑯 𐑲 𐑜𐑪𐑑 𐑦𐑯 𐑩 𐑓𐑲𐑑 𐑹 𐑕𐑳𐑥𐑔𐑦𐑙.”

“𐑬𐑗,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑢𐑦𐑯𐑕𐑦𐑙. “𐑲'𐑥 \emph{𐑮𐑾𐑤𐑦} 𐑕𐑪𐑮𐑦—”

“𐑯𐑴, 𐑢𐑰'𐑼 𐑿𐑕𐑑 𐑑 𐑦𐑑, ·𐑥𐑻𐑤𐑦𐑯 𐑯𐑴𐑟 𐑞𐑺'𐑟 𐑤𐑪𐑑𐑕 𐑝 𐑮𐑵𐑥𐑼𐑟 𐑩𐑚𐑬𐑑 𐑞 ·𐑥𐑨𐑤𐑓𐑶 𐑓𐑨𐑥𐑤𐑦 𐑷𐑤𐑮𐑧𐑛𐑦.”

·𐑣𐑨𐑮𐑦 𐑯𐑪𐑛𐑩𐑛. “𐑲'𐑥 𐑜𐑤𐑨𐑛 𐑑 𐑣𐑽 𐑿'𐑼 𐑯𐑪𐑑 𐑦𐑯 𐑑𐑮𐑳𐑚𐑩𐑤.”

·𐑛𐑮𐑱𐑒𐑴 𐑕𐑥𐑻𐑒𐑑. “·𐑓𐑭𐑞𐑼 𐑣𐑨𐑟, 𐑳𐑥, 𐑩 \emph{𐑮𐑦𐑓𐑲𐑯𐑛} 𐑕𐑧𐑯𐑕 𐑝 𐑣𐑿𐑥𐑼, 𐑚𐑳𐑑 𐑣𐑰 \emph{𐑛𐑳𐑟} 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑥𐑱𐑒𐑦𐑙 𐑓𐑮𐑧𐑯𐑛𐑟. 𐑣𐑰 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛𐑟 𐑦𐑑 \emph{𐑝𐑧𐑮𐑦} 𐑢𐑧𐑤. 𐑣𐑰 𐑥𐑱𐑛 𐑥𐑰 𐑮𐑦𐑐𐑰𐑑 𐑞𐑨𐑑 𐑚𐑦𐑓𐑹 𐑲 𐑢𐑧𐑯𐑑 𐑑 𐑚𐑧𐑛 𐑧𐑝𐑮𐑦 𐑯𐑲𐑑 𐑓 𐑞 𐑤𐑭𐑕𐑑 𐑥𐑳𐑯𐑔, '𐑲 𐑢𐑦𐑤 𐑥𐑱𐑒 𐑓𐑮𐑧𐑯𐑛𐑟 𐑨𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕.' 𐑢𐑧𐑯 𐑲 𐑦𐑒𐑕𐑐𐑤𐑱𐑯𐑛 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑑 𐑣𐑦𐑥 𐑯 𐑣𐑰 𐑕𐑷 𐑞𐑨𐑑'𐑕 𐑢𐑪𐑑 𐑲 𐑢𐑪𐑟 𐑛𐑵𐑦𐑙, 𐑣𐑰 𐑚𐑷𐑑 𐑥𐑰 𐑩𐑯 𐑲𐑕-𐑒𐑮𐑰𐑥.”

𐑣𐑨𐑮𐑦'𐑟 𐑡𐑷 𐑛𐑮𐑪𐑐𐑑. “\emph{𐑿 𐑥𐑨𐑯𐑦𐑡𐑛 𐑑 𐑕𐑐𐑦𐑯 𐑞𐑨𐑑 𐑦𐑯𐑑𐑵 𐑩𐑯 𐑲𐑕-𐑒𐑮𐑰𐑥?}”

·𐑛𐑮𐑱𐑒𐑴 𐑯𐑪𐑛𐑩𐑛, 𐑤𐑫𐑒𐑦𐑙 𐑧𐑝𐑮𐑦 𐑚𐑦𐑑 𐑨𐑟 𐑕𐑥𐑳𐑜 𐑨𐑟 𐑞 𐑓𐑰𐑑 𐑛𐑦𐑟𐑻𐑝𐑛. “𐑢𐑧𐑤, 𐑓𐑭𐑞𐑼 \emph{𐑯𐑿} 𐑢𐑪𐑑 𐑲 𐑢𐑪𐑟 𐑛𐑵𐑦𐑙, 𐑝 𐑒𐑹𐑕, 𐑚𐑳𐑑 𐑣𐑰'𐑟 𐑞 𐑢𐑳𐑯 𐑣𐑵 𐑑𐑷𐑑 𐑥𐑰 \emph{𐑣𐑬} 𐑑 𐑛𐑵 𐑦𐑑, 𐑯 𐑦𐑓 𐑲 𐑜𐑮𐑦𐑯 𐑞 𐑮𐑲𐑑 𐑢𐑱 \emph{𐑢𐑲𐑤} 𐑲'𐑥 𐑛𐑵𐑦𐑙 𐑦𐑑, 𐑞𐑨𐑑 𐑥𐑱𐑒𐑕 𐑦𐑑 𐑩 𐑓𐑭𐑞𐑼-𐑕𐑳𐑯 𐑔𐑦𐑙 𐑯 𐑞𐑧𐑯 𐑣𐑰 \emph{𐑣𐑨𐑕} 𐑑 𐑚𐑲 𐑥𐑰 𐑩𐑯 𐑲𐑕-𐑒𐑮𐑰𐑥 𐑹 𐑲'𐑤 𐑜𐑦𐑝 𐑣𐑦𐑥 𐑞𐑦𐑕 𐑕𐑹𐑑 𐑝 𐑕𐑨𐑛 𐑤𐑫𐑒, 𐑤𐑲𐑒 𐑲 𐑔𐑦𐑙𐑒 𐑲 𐑥𐑳𐑕𐑑 𐑣𐑨𐑝 𐑛𐑦𐑕𐑩𐑐𐑶𐑯𐑑𐑩𐑛 𐑣𐑦𐑥.”

·𐑣𐑨𐑮𐑦 𐑲𐑛 ·𐑛𐑮𐑱𐑒𐑴 𐑒𐑨𐑤𐑒𐑿𐑤𐑱𐑑𐑦𐑙𐑤𐑦, 𐑕𐑧𐑯𐑕𐑦𐑙 𐑞 𐑐𐑮𐑧𐑟𐑩𐑯𐑕 𐑝 𐑩𐑯𐑳𐑞𐑼 𐑥𐑭𐑕𐑑𐑼. “𐑿'𐑝 𐑣𐑨𐑛 \emph{𐑤𐑧𐑕𐑩𐑯𐑟} 𐑪𐑯 𐑣𐑬 𐑑 𐑥𐑩𐑯𐑦𐑐𐑿𐑤𐑱𐑑 𐑐𐑰𐑐𐑩𐑤?”

“𐑝 𐑒𐑹𐑕,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛 𐑐𐑮𐑬𐑛𐑤𐑦. “𐑲'𐑥 𐑩 \emph{·𐑥𐑨𐑤𐑓𐑶.} ·𐑓𐑭𐑞𐑼 𐑚𐑷𐑑 𐑥𐑰 𐑑𐑿𐑑𐑼𐑟.”

“𐑢𐑬,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. 𐑮𐑰𐑛𐑦𐑙 ·𐑮𐑪𐑚𐑼𐑑 ·𐑗𐑭𐑤𐑛𐑰𐑯𐑦'𐑟 \emph{·𐑦𐑯𐑓𐑤𐑵𐑩𐑯𐑕: ·𐑕𐑲𐑩𐑯𐑕 𐑯 ·𐑐𐑮𐑨𐑒𐑑𐑦𐑕} 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑛𐑦𐑛𐑩𐑯𐑑 𐑕𐑑𐑨𐑒 𐑳𐑐 𐑝𐑧𐑮𐑦 𐑣𐑲 𐑒𐑩𐑥𐑐𐑺𐑛 𐑑 𐑞𐑨𐑑 (𐑞𐑴 𐑦𐑑 𐑢𐑪𐑟 𐑕𐑑𐑦𐑤 𐑢𐑳𐑯 𐑣𐑧𐑒 𐑝 𐑩 𐑚𐑫𐑒). “𐑘𐑹 𐑛𐑨𐑛 𐑦𐑟 𐑷𐑤𐑥𐑴𐑕𐑑 𐑨𐑟 𐑷𐑕𐑩𐑥 𐑨𐑟 𐑥𐑲 𐑛𐑨𐑛.”

·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑲𐑚𐑮𐑬𐑟 𐑮𐑴𐑟 𐑤𐑪𐑓𐑑𐑦𐑤𐑦. “𐑴? 𐑯 𐑢𐑪𐑑 𐑛𐑳𐑟 \emph{𐑘𐑹} 𐑓𐑭𐑞𐑼 𐑛𐑵?”

“𐑣𐑰 𐑚𐑲𐑟 𐑥𐑰 𐑚𐑫𐑒𐑕.”

·𐑛𐑮𐑱𐑒𐑴 𐑒𐑩𐑯𐑕𐑦𐑛𐑼𐑛 𐑞𐑦𐑕. “𐑞𐑨𐑑 𐑛𐑳𐑟𐑩𐑯𐑑 𐑕𐑬𐑯𐑛 𐑝𐑧𐑮𐑦 𐑦𐑥𐑐𐑮𐑧𐑕𐑦𐑝.”

“𐑿 𐑣𐑨𐑛 𐑑 𐑚𐑰 𐑞𐑺. 𐑧𐑯𐑦𐑢𐑱, 𐑲'𐑥 𐑜𐑤𐑨𐑛 𐑑 𐑣𐑽 𐑷𐑤 𐑞𐑨𐑑. 𐑞 𐑢𐑱 ·𐑤𐑵𐑕𐑾𐑕 𐑢𐑪𐑟 𐑤𐑫𐑒𐑦𐑙 𐑨𐑑 𐑿, 𐑲 𐑔𐑷𐑑 𐑣𐑰 𐑢𐑪𐑟 𐑜𐑴𐑦𐑙 𐑑 c-𐑒𐑮𐑵𐑕𐑦𐑓𐑲 𐑿.”

“𐑥𐑲 𐑓𐑭𐑞𐑼 𐑮𐑾𐑤𐑦 𐑤𐑳𐑝𐑟 𐑥𐑰,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛 𐑓𐑻𐑥𐑤𐑦. “𐑣𐑰 𐑢𐑫𐑛𐑩𐑯𐑑 𐑧𐑝𐑼 𐑛𐑵 𐑞𐑨𐑑.”

“𐑳𐑥…” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. 𐑣𐑰 𐑮𐑦𐑥𐑧𐑥𐑚𐑼𐑛 𐑞 𐑚𐑤𐑨𐑒-𐑮𐑴𐑚𐑛, 𐑢𐑲𐑑-𐑣𐑺𐑛 𐑓𐑦𐑜𐑼 𐑝 𐑧𐑤𐑦𐑜𐑩𐑯𐑕 𐑞𐑨𐑑 𐑣𐑨𐑛 𐑕𐑑𐑹𐑥𐑛 𐑔𐑮𐑵 ·𐑥𐑨𐑛𐑩𐑥 ·𐑥𐑨𐑤𐑒𐑦𐑯'𐑟, 𐑢𐑰𐑤𐑛𐑦𐑙 𐑞𐑨𐑑 𐑚𐑿𐑑𐑦𐑓𐑩𐑤, 𐑛𐑧𐑛𐑤𐑦 𐑕𐑦𐑤𐑝𐑼-𐑣𐑨𐑯𐑛𐑩𐑤𐑛 𐑒𐑱𐑯. 𐑦𐑑 𐑢𐑪𐑟𐑩𐑯𐑑 𐑰𐑟𐑦 𐑑 𐑝𐑦𐑠𐑵𐑩𐑤𐑲𐑟 𐑣𐑦𐑥 𐑨𐑟 𐑩 𐑛𐑴𐑑𐑦𐑙 𐑓𐑭𐑞𐑼. “𐑛𐑴𐑯𐑑 𐑑𐑱𐑒 𐑞𐑦𐑕 𐑞 𐑮𐑪𐑙 𐑢𐑱, 𐑚𐑳𐑑 𐑣𐑬 𐑛𐑵 𐑿 \emph{𐑯𐑴} 𐑞𐑨𐑑?”

“𐑣𐑳?” 𐑦𐑑 𐑢𐑪𐑟 𐑒𐑤𐑽 𐑞𐑨𐑑 𐑞𐑦𐑕 𐑢𐑪𐑟 𐑩 𐑒𐑢𐑧𐑕𐑗𐑩𐑯 ·𐑛𐑮𐑱𐑒𐑴 𐑛𐑦𐑛 𐑯𐑪𐑑 𐑒𐑪𐑥𐑩𐑯𐑤𐑦 𐑭𐑕𐑒 𐑣𐑦𐑥𐑕𐑧𐑤𐑓.

“𐑲 𐑭𐑕𐑒 𐑞 𐑓𐑳𐑯𐑛𐑩𐑥𐑧𐑯𐑑𐑩𐑤 𐑒𐑢𐑧𐑕𐑗𐑩𐑯 𐑝 𐑮𐑨𐑖𐑩𐑯𐑨𐑤𐑦𐑑𐑦: 𐑢𐑲 𐑛𐑵 𐑿 𐑚𐑦𐑤𐑰𐑝 𐑢𐑪𐑑 𐑿 𐑚𐑦𐑤𐑰𐑝? 𐑢𐑪𐑑 𐑛𐑵 𐑿 𐑔𐑦𐑙𐑒 𐑿 𐑯𐑴 𐑯 𐑣𐑬 𐑛𐑵 𐑿 𐑔𐑦𐑙𐑒 𐑿 𐑯𐑴 𐑦𐑑? 𐑢𐑪𐑑 𐑥𐑱𐑒𐑕 𐑿 𐑔𐑦𐑙𐑒 ·𐑤𐑵𐑕𐑾𐑕 𐑢𐑫𐑛𐑩𐑯𐑑 𐑕𐑨𐑒𐑮𐑦𐑓𐑲𐑕 𐑿 𐑞 𐑕𐑱𐑥 𐑢𐑱 𐑣𐑰'𐑛 𐑕𐑨𐑒𐑮𐑦𐑓𐑲𐑕 𐑧𐑯𐑦𐑔𐑦𐑙 𐑧𐑤𐑕 𐑓 𐑐𐑬𐑼?”

·𐑛𐑮𐑱𐑒𐑴 𐑖𐑪𐑑 ·𐑣𐑨𐑮𐑦 𐑩𐑯𐑳𐑞𐑼 𐑪𐑛 𐑤𐑫𐑒. “𐑡𐑳𐑕𐑑 𐑢𐑪𐑑 𐑛𐑵 \emph{𐑿} 𐑯𐑴 𐑩𐑚𐑬𐑑 ·𐑓𐑭𐑞𐑼?”

“𐑳𐑥…𐑕𐑰𐑑 𐑪𐑯 𐑞 ·𐑢𐑦𐑟𐑩𐑯𐑜𐑱𐑥𐑪𐑑, 𐑕𐑰𐑑 𐑪𐑯 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕' ·𐑚𐑹𐑛 𐑝 ·𐑜𐑳𐑝𐑼𐑯𐑼𐑟, 𐑦𐑯𐑒𐑮𐑧𐑛𐑩𐑚𐑤𐑦 𐑢𐑧𐑤𐑔𐑦, 𐑣𐑨𐑟 𐑞 𐑽 𐑝 ·𐑥𐑦𐑯𐑦𐑕𐑑𐑼 ·𐑓𐑳𐑡, 𐑣𐑨𐑟 𐑞 𐑒𐑪𐑯𐑓𐑦𐑛𐑩𐑯𐑕 𐑝 ·𐑥𐑦𐑯𐑦𐑕𐑑𐑼 ·𐑓𐑳𐑡, 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑣𐑨𐑟 𐑕𐑳𐑥 𐑣𐑲𐑤𐑦 𐑦𐑥𐑚𐑨𐑮𐑩𐑕𐑦𐑙 𐑓𐑴𐑑𐑴𐑟 𐑝 ·𐑥𐑦𐑯𐑦𐑕𐑑𐑼 ·𐑓𐑳𐑡, 𐑥𐑴𐑕𐑑 𐑐𐑮𐑪𐑥𐑦𐑯𐑩𐑯𐑑 𐑚𐑤𐑳𐑛 𐑐𐑘𐑫𐑼𐑦𐑕𐑑 𐑯𐑬 𐑞𐑨𐑑 𐑞 ·𐑛𐑸𐑒 ·𐑤𐑹𐑛'𐑟 𐑜𐑪𐑯, 𐑓𐑹𐑥𐑼 ·𐑛𐑧𐑔 ·𐑰𐑑𐑼 𐑣𐑵 𐑢𐑪𐑟 𐑓𐑬𐑯𐑛 𐑑 𐑣𐑨𐑝 𐑞 ·𐑛𐑸𐑒 ·𐑥𐑸𐑒 𐑚𐑳𐑑 𐑜𐑪𐑑 𐑪𐑓 𐑚𐑲 𐑒𐑤𐑱𐑥𐑦𐑙 𐑑 𐑚𐑰 𐑳𐑯𐑛𐑼 𐑞 ·𐑦𐑥𐑐𐑽𐑾𐑕 ·𐑒𐑻𐑕, 𐑢𐑦𐑗 𐑢𐑪𐑟 𐑮𐑦𐑛𐑦𐑒𐑿𐑤𐑩𐑕𐑤𐑦 𐑦𐑥𐑐𐑤𐑷𐑟𐑩𐑚𐑩𐑤 𐑯 𐑐𐑮𐑦𐑑𐑦 𐑥𐑳𐑗 𐑧𐑝𐑮𐑦𐑢𐑳𐑯 𐑯𐑿 𐑦𐑑…𐑰𐑝𐑩𐑤 𐑢𐑦𐑞 𐑩 𐑒𐑨𐑐𐑦𐑑𐑩𐑤 '·𐑰' 𐑯 𐑩 𐑚𐑹𐑯 𐑒𐑦𐑤𐑼…𐑲 𐑔𐑦𐑙𐑒 𐑞𐑨𐑑'𐑕 𐑦𐑑.”

·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑲𐑟 𐑣𐑨𐑛 𐑯𐑨𐑮𐑴𐑛 𐑑 𐑕𐑤𐑦𐑑𐑕. “·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑑𐑴𐑤𐑛 𐑿 𐑞𐑨𐑑, 𐑛𐑦𐑛 𐑖𐑰.”

“𐑯𐑴, 𐑖𐑰 𐑢𐑫𐑛𐑩𐑯𐑑 𐑕𐑱 \emph{𐑧𐑯𐑦𐑔𐑦𐑙} 𐑑 𐑥𐑰 𐑩𐑚𐑬𐑑 ·𐑤𐑵𐑕𐑾𐑕 𐑭𐑓𐑑𐑼𐑢𐑼𐑛𐑟, 𐑦𐑒𐑕𐑧𐑐𐑑 𐑑 𐑕𐑑𐑱 𐑩𐑢𐑱 𐑓𐑮𐑪𐑥 𐑣𐑦𐑥. 𐑕𐑴 𐑛𐑘𐑫𐑼𐑦𐑙 𐑞 ·𐑦𐑯𐑕𐑦𐑛𐑩𐑯𐑑 𐑨𐑑 𐑞 ·𐑐𐑴𐑖𐑩𐑯𐑟 ·𐑖𐑪𐑐, 𐑢𐑲𐑤 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑢𐑪𐑟 𐑚𐑦𐑟𐑦 𐑘𐑧𐑤𐑦𐑙 𐑨𐑑 𐑞 𐑖𐑪𐑐𐑒𐑰𐑐𐑼 𐑯 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑜𐑧𐑑 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑳𐑯𐑛𐑼 𐑒𐑩𐑯𐑑𐑮𐑴𐑤, 𐑲 𐑜𐑮𐑨𐑚𐑛 𐑢𐑳𐑯 𐑝 𐑞 𐑒𐑳𐑕𐑑𐑩𐑥𐑼𐑟 𐑯 𐑭𐑕𐑒𐑑 \emph{𐑞𐑧𐑥} 𐑩𐑚𐑬𐑑 ·𐑤𐑵𐑕𐑾𐑕.”

·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑲𐑟 𐑢𐑻 𐑢𐑲𐑛 𐑩𐑜𐑱𐑯. “𐑛𐑦𐑛 𐑿 \emph{𐑮𐑾𐑤𐑦}?”

·𐑣𐑨𐑮𐑦 𐑜𐑱𐑝 ·𐑛𐑮𐑱𐑒𐑴 𐑩 𐑐𐑳𐑟𐑩𐑤𐑛 𐑤𐑫𐑒. “𐑦𐑓 𐑲 𐑤𐑲𐑛 𐑞 𐑓𐑻𐑕𐑑 𐑑𐑲𐑥, 𐑲'𐑥 𐑯𐑪𐑑 𐑜𐑴𐑦𐑙 𐑑 𐑑𐑧𐑤 𐑿 𐑞 𐑑𐑮𐑵𐑔 𐑡𐑳𐑕𐑑 𐑚𐑦𐑒𐑪𐑟 𐑿 𐑭𐑕𐑒 𐑑𐑢𐑲𐑕.”

𐑞𐑺 𐑢𐑪𐑟 𐑩 𐑕𐑻𐑑𐑩𐑯 𐑐𐑷𐑟 𐑨𐑟 ·𐑛𐑮𐑱𐑒𐑴 𐑩𐑚𐑕𐑹𐑚𐑛 𐑞𐑦𐑕.

“𐑿'𐑼 𐑕𐑴 𐑒𐑩𐑥𐑐𐑤𐑰𐑑𐑤𐑦 𐑜𐑴𐑦𐑙 𐑑 𐑚𐑰 𐑦𐑯 ·𐑕𐑤𐑲𐑔𐑼𐑦𐑯.”

“𐑲'𐑥 𐑕𐑴 𐑒𐑩𐑥𐑐𐑤𐑰𐑑𐑤𐑦 𐑜𐑴𐑦𐑙 𐑑 𐑚𐑰 𐑦𐑯 ·𐑮𐑱𐑝𐑩𐑯𐑒𐑤𐑷, 𐑔𐑨𐑙𐑒 𐑿 𐑝𐑧𐑮𐑦 𐑥𐑳𐑗. 𐑲 𐑴𐑯𐑤𐑦 𐑢𐑪𐑯𐑑 𐑐𐑬𐑼 𐑕𐑴 𐑲 𐑒𐑨𐑯 𐑜𐑧𐑑 𐑚𐑫𐑒𐑕.”

·𐑛𐑮𐑱𐑒𐑴 𐑜𐑦𐑜𐑩𐑤𐑛. “𐑘𐑧𐑩, 𐑮𐑲𐑑. 𐑧𐑯𐑦𐑢𐑱…𐑑 𐑭𐑯𐑕𐑼 𐑢𐑪𐑑 𐑿 𐑭𐑕𐑒𐑑…” ·𐑛𐑮𐑱𐑒𐑴 𐑑𐑫𐑒 𐑩 𐑛𐑰𐑐 𐑚𐑮𐑧𐑔, 𐑯 𐑣𐑦𐑟 𐑓𐑱𐑕 𐑑𐑻𐑯𐑛 𐑕𐑽𐑾𐑕. “·𐑓𐑭𐑞𐑼 𐑢𐑳𐑯𐑕 𐑥𐑦𐑕𐑑 𐑩 ·𐑢𐑦𐑟𐑩𐑯𐑜𐑱𐑥𐑪𐑑 𐑝𐑴𐑑 𐑓 𐑥𐑰. 𐑲 𐑢𐑪𐑟 𐑪𐑯 𐑩 𐑚𐑮𐑵𐑥 𐑯 𐑲 𐑓𐑧𐑤 𐑪𐑓 𐑯 𐑚𐑮𐑴𐑒 𐑩 𐑤𐑪𐑑 𐑝 𐑮𐑦𐑚𐑟. 𐑦𐑑 𐑮𐑾𐑤𐑦 𐑣𐑻𐑑. 𐑲'𐑛 𐑯𐑧𐑝𐑼 𐑣𐑻𐑑 𐑞𐑨𐑑 𐑥𐑳𐑗 𐑚𐑦𐑓𐑹 𐑯 𐑲 𐑔𐑷𐑑 𐑲 𐑢𐑪𐑟 𐑜𐑴𐑦𐑙 𐑑 𐑛𐑲. 𐑕𐑴 ·𐑓𐑭𐑞𐑼 𐑥𐑦𐑕𐑑 𐑞𐑦𐑕 𐑮𐑾𐑤𐑦 𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑 𐑝𐑴𐑑, 𐑚𐑦𐑒𐑪𐑟 𐑣𐑰 𐑢𐑪𐑟 𐑞𐑺 𐑚𐑲 𐑥𐑲 𐑚𐑧𐑛 𐑨𐑑 ·𐑕𐑑 ·𐑥𐑳𐑙𐑜𐑴'𐑟, 𐑣𐑴𐑤𐑛𐑦𐑙 𐑥𐑲 𐑣𐑨𐑯𐑛𐑟 𐑯 𐑐𐑮𐑪𐑥𐑦𐑕𐑦𐑙 𐑥𐑰 𐑞𐑨𐑑 𐑲 𐑢𐑪𐑟 𐑜𐑴𐑦𐑙 𐑑 𐑚𐑰 𐑴𐑒𐑱.”

·𐑣𐑨𐑮𐑦 𐑜𐑤𐑭𐑯𐑕𐑑 𐑩𐑢𐑱 𐑳𐑯𐑒𐑳𐑥𐑓𐑼𐑑𐑩𐑚𐑤𐑦, 𐑞𐑧𐑯, 𐑢𐑦𐑞 𐑩𐑯 𐑧𐑓𐑼𐑑, 𐑓𐑹𐑕𐑑 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑑 𐑤𐑫𐑒 𐑚𐑨𐑒 𐑨𐑑 ·𐑛𐑮𐑱𐑒𐑴. “𐑢𐑲 𐑸 𐑿 𐑑𐑧𐑤𐑦𐑙 𐑥𐑰 \emph{𐑞𐑨𐑑}? 𐑦𐑑 𐑕𐑰𐑥𐑟 𐑕𐑹𐑑 𐑝…𐑐𐑮𐑲𐑝𐑩𐑑…”

·𐑛𐑮𐑱𐑒𐑴 𐑜𐑱𐑝 ·𐑣𐑨𐑮𐑦 𐑩 𐑕𐑽𐑾𐑕 𐑤𐑫𐑒. “𐑢𐑳𐑯 𐑝 𐑥𐑲 𐑑𐑿𐑑𐑼𐑟 𐑢𐑳𐑯𐑕 𐑕𐑧𐑛 𐑞𐑨𐑑 𐑐𐑰𐑐𐑩𐑤 𐑓𐑹𐑥 𐑒𐑤𐑴𐑕 𐑓𐑮𐑧𐑯𐑛𐑖𐑦𐑐𐑕 𐑚𐑲 𐑯𐑴𐑦𐑙 𐑐𐑮𐑲𐑝𐑩𐑑 𐑔𐑦𐑙𐑟 𐑩𐑚𐑬𐑑 𐑰𐑗 𐑳𐑞𐑼, 𐑯 𐑞 𐑮𐑰𐑟𐑩𐑯 𐑥𐑴𐑕𐑑 𐑐𐑰𐑐𐑩𐑤 𐑛𐑴𐑯𐑑 𐑥𐑱𐑒 𐑒𐑤𐑴𐑕 𐑓𐑮𐑧𐑯𐑛𐑟 𐑦𐑟 𐑚𐑦𐑒𐑪𐑟 𐑞𐑱'𐑼 𐑑𐑵 𐑦𐑥𐑚𐑨𐑮𐑩𐑕𐑑 𐑑 𐑖𐑺 𐑧𐑯𐑦𐑔𐑦𐑙 𐑮𐑾𐑤𐑦 𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑 𐑩𐑚𐑬𐑑 𐑞𐑧𐑥𐑕𐑧𐑤𐑝𐑟.” ·𐑛𐑮𐑱𐑒𐑴 𐑑𐑻𐑯𐑛 𐑣𐑦𐑟 𐑐𐑭𐑥𐑟 𐑬𐑑 𐑦𐑯𐑝𐑲𐑑𐑦𐑙𐑤𐑦. “𐑘𐑹 𐑑𐑻𐑯?”

𐑯𐑴𐑦𐑙 𐑞𐑨𐑑 ·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑣𐑴𐑐𐑓𐑩𐑤 𐑓𐑱𐑕 𐑣𐑨𐑛 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑚𐑰𐑯 𐑛𐑮𐑦𐑤𐑛 𐑦𐑯𐑑𐑵 𐑣𐑦𐑥 𐑚𐑲 𐑥𐑳𐑯𐑔𐑕 𐑝 𐑐𐑮𐑨𐑒𐑑𐑦𐑕 𐑛𐑦𐑛 𐑯𐑪𐑑 𐑥𐑱𐑒 𐑦𐑑 𐑧𐑯𐑦 𐑤𐑧𐑕 𐑦𐑓𐑧𐑒𐑑𐑦𐑝, ·𐑣𐑨𐑮𐑦 𐑩𐑚𐑟𐑻𐑝𐑛. 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑦𐑑 \emph{𐑛𐑦𐑛} 𐑥𐑱𐑒 𐑦𐑑 \emph{𐑤𐑧𐑕} 𐑦𐑓𐑧𐑒𐑑𐑦𐑝, 𐑚𐑳𐑑 𐑳𐑯𐑓𐑹𐑗𐑩𐑯𐑩𐑑𐑤𐑦 𐑯𐑪𐑑 \emph{𐑦𐑯𐑦𐑓𐑧𐑒𐑑𐑦𐑝}. 𐑞 𐑕𐑱𐑥 𐑒𐑫𐑛 𐑚𐑰 𐑕𐑧𐑛 𐑝 ·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑒𐑤𐑧𐑝𐑼 𐑿𐑕 𐑝 𐑮𐑦𐑕𐑦𐑐𐑮𐑩𐑒𐑱𐑖𐑩𐑯 𐑐𐑮𐑧𐑖𐑼 𐑢𐑦𐑞 𐑩𐑯 𐑳𐑯𐑕𐑩𐑤𐑦𐑕𐑦𐑑𐑩𐑛 𐑜𐑦𐑓𐑑, 𐑩 𐑑𐑧𐑒𐑯𐑰𐑒 𐑢𐑦𐑗 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑮𐑧𐑛 𐑩𐑚𐑬𐑑 𐑦𐑯 𐑣𐑦𐑟 𐑕𐑴𐑖𐑩𐑤 𐑕𐑲𐑒𐑪𐑤𐑩𐑡𐑦 𐑚𐑫𐑒𐑕 (𐑢𐑳𐑯 𐑦𐑒𐑕𐑐𐑧𐑮𐑦𐑥𐑧𐑯𐑑 𐑣𐑨𐑛 𐑖𐑴𐑯 𐑞𐑨𐑑 𐑩𐑯 𐑳𐑯𐑒𐑩𐑯𐑛𐑦𐑖𐑩𐑯𐑩𐑤 𐑜𐑦𐑓𐑑 𐑝 \$5 𐑢𐑪𐑟 𐑑𐑢𐑲𐑕 𐑨𐑟 𐑦𐑓𐑧𐑒𐑑𐑦𐑝 𐑨𐑟 𐑩 𐑒𐑩𐑯𐑛𐑦𐑖𐑩𐑯𐑩𐑤 𐑪𐑓𐑼 𐑝 \$50 𐑦𐑯 𐑜𐑧𐑑𐑦𐑙 𐑐𐑰𐑐𐑩𐑤 𐑑 𐑓𐑦𐑤 𐑬𐑑 𐑕𐑻𐑝𐑱𐑟). ·𐑛𐑮𐑱𐑒𐑴 𐑣𐑨𐑛 𐑥𐑱𐑛 𐑩𐑯 𐑳𐑯𐑕𐑩𐑤𐑦𐑕𐑦𐑑𐑩𐑛 𐑜𐑦𐑓𐑑 𐑝 𐑩 𐑒𐑪𐑯𐑓𐑦𐑛𐑩𐑯𐑕, 𐑯 𐑯𐑬 𐑦𐑯𐑝𐑲𐑑𐑩𐑛 ·𐑣𐑨𐑮𐑦 𐑑 𐑪𐑓𐑼 𐑩 𐑒𐑪𐑯𐑓𐑦𐑛𐑩𐑯𐑕 𐑦𐑯 𐑮𐑦𐑑𐑻𐑯…𐑯 𐑞 𐑔𐑦𐑙 𐑢𐑪𐑟, ·𐑣𐑨𐑮𐑦 \emph{𐑛𐑦𐑛} 𐑓𐑰𐑤 𐑐𐑮𐑧𐑖𐑼𐑛. 𐑮𐑦𐑓𐑿𐑟𐑩𐑤, ·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑕𐑻𐑑𐑩𐑯, 𐑢𐑫𐑛 𐑚𐑰 𐑥𐑧𐑑 𐑢𐑦𐑞 𐑩 𐑤𐑫𐑒 𐑝 𐑕𐑨𐑛 𐑛𐑦𐑕𐑩𐑐𐑶𐑯𐑑𐑥𐑩𐑯𐑑, 𐑯 𐑥𐑱𐑚𐑰 𐑩 𐑕𐑥𐑷𐑤 𐑩𐑥𐑬𐑯𐑑 𐑝 𐑒𐑩𐑯𐑑𐑧𐑥𐑐𐑑 𐑦𐑯𐑛𐑦𐑒𐑱𐑑𐑦𐑙 𐑞𐑨𐑑 ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑤𐑪𐑕𐑑 𐑐𐑶𐑯𐑑𐑕.

“·𐑛𐑮𐑱𐑒𐑴,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, “𐑡𐑳𐑕𐑑 𐑕𐑴 𐑿 𐑯𐑴, 𐑲 𐑮𐑧𐑒𐑩𐑜𐑯𐑲𐑟 𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦 𐑢𐑪𐑑 𐑿'𐑼 𐑛𐑵𐑦𐑙 𐑮𐑲𐑑 𐑯𐑬. 𐑥𐑲 𐑴𐑯 𐑚𐑫𐑒𐑕 𐑒𐑷𐑤𐑛 𐑦𐑑 \emph{𐑮𐑦𐑕𐑦𐑐𐑮𐑩𐑒𐑱𐑖𐑩𐑯} 𐑯 𐑞𐑱 𐑑𐑷𐑒 𐑩𐑚𐑬𐑑 𐑣𐑬 𐑜𐑦𐑝𐑦𐑙 𐑕𐑳𐑥𐑢𐑳𐑯 𐑩 𐑕𐑑𐑮𐑱𐑑 𐑜𐑦𐑓𐑑 𐑝 𐑑𐑵 ·𐑕𐑦𐑒𐑩𐑤𐑟 𐑢𐑪𐑟 𐑓𐑬𐑯𐑛 𐑑 𐑚𐑰 𐑑𐑢𐑲𐑕 𐑨𐑟 𐑦𐑓𐑧𐑒𐑑𐑦𐑝 𐑨𐑟 𐑪𐑓𐑼𐑦𐑙 𐑞𐑧𐑥 𐑑𐑢𐑧𐑯𐑑𐑦 ·𐑕𐑦𐑒𐑩𐑤𐑟 𐑦𐑯 𐑜𐑧𐑑𐑦𐑙 𐑞𐑧𐑥 𐑑 𐑛𐑵 𐑢𐑪𐑑 𐑿 𐑢𐑪𐑯𐑑…” ·𐑣𐑨𐑮𐑦 𐑑𐑮𐑱𐑤𐑛 𐑪𐑓.

·𐑛𐑮𐑱𐑒𐑴 𐑢𐑪𐑟 𐑤𐑫𐑒𐑦𐑙 𐑕𐑨𐑛 𐑯 𐑛𐑦𐑕𐑩𐑐𐑶𐑯𐑑𐑩𐑛. “𐑦𐑑'𐑕 𐑯𐑪𐑑 𐑥𐑧𐑯𐑑 𐑨𐑟 𐑩 𐑑𐑮𐑦𐑒, ·𐑣𐑨𐑮𐑦. 𐑦𐑑'𐑕 𐑩 𐑮𐑾𐑤 𐑢𐑱 𐑝 𐑚𐑦𐑒𐑳𐑥𐑦𐑙 𐑓𐑮𐑧𐑯𐑛𐑟.”

·𐑣𐑨𐑮𐑦 𐑣𐑧𐑤𐑛 𐑳𐑐 𐑩 𐑣𐑨𐑯𐑛. “𐑲 𐑛𐑦𐑛𐑩𐑯𐑑 𐑕𐑱 𐑲 𐑢𐑪𐑟𐑩𐑯𐑑 𐑜𐑴𐑦𐑙 𐑑 𐑮𐑦𐑕𐑐𐑪𐑯𐑛. 𐑲 𐑡𐑳𐑕𐑑 𐑯𐑰𐑛 𐑑𐑲𐑥 𐑑 𐑐𐑦𐑒 𐑕𐑳𐑥𐑔𐑦𐑙 𐑞𐑨𐑑'𐑕 𐑐𐑮𐑲𐑝𐑩𐑑 𐑚𐑳𐑑 𐑡𐑳𐑕𐑑 𐑨𐑟 𐑯𐑪𐑯-𐑛𐑨𐑥𐑦𐑡𐑦𐑙. 𐑤𐑧𐑑'𐑕 𐑕𐑱…𐑲 𐑢𐑪𐑯𐑑𐑩𐑛 𐑿 𐑑 𐑯𐑴 𐑞𐑨𐑑 𐑲 𐑒𐑭𐑯𐑑 𐑚𐑰 𐑮𐑳𐑖𐑑 𐑦𐑯𐑑𐑵 𐑔𐑦𐑙𐑟.” 𐑩 𐑐𐑷𐑟 𐑑 𐑮𐑦𐑓𐑤𐑧𐑒𐑑 𐑒𐑫𐑛 𐑜𐑴 𐑩 𐑤𐑪𐑙 𐑢𐑱 𐑦𐑯 𐑛𐑰𐑓𐑿𐑟𐑦𐑙 𐑞 𐑐𐑬𐑼 𐑝 𐑩 𐑤𐑪𐑑 𐑝 𐑒𐑩𐑥𐑐𐑤𐑲𐑩𐑯𐑕 𐑑𐑧𐑒𐑯𐑰𐑒𐑕, 𐑢𐑳𐑯𐑕 𐑿 𐑤𐑻𐑯𐑛 𐑑 𐑮𐑧𐑒𐑩𐑜𐑯𐑲𐑟 𐑞𐑧𐑥 𐑓 𐑢𐑪𐑑 𐑞𐑱 𐑢𐑻.

“𐑷𐑤 𐑮𐑲𐑑,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛. “𐑲'𐑤 𐑢𐑱𐑑 𐑢𐑲𐑤 𐑿 𐑒𐑳𐑥 𐑳𐑐 𐑢𐑦𐑞 𐑕𐑳𐑥𐑔𐑦𐑙. 𐑴, 𐑯 𐑐𐑤𐑰𐑟 𐑑𐑱𐑒 𐑪𐑓 𐑞 𐑕𐑒𐑸𐑓 𐑢𐑲𐑤 𐑿 𐑕𐑱 𐑦𐑑.”

\emph{𐑕𐑦𐑥𐑐𐑩𐑤 𐑚𐑳𐑑 𐑦𐑓𐑧𐑒𐑑𐑦𐑝.}

𐑯 ·𐑣𐑨𐑮𐑦 𐑒𐑫𐑛𐑩𐑯𐑑 𐑣𐑧𐑤𐑐 𐑚𐑳𐑑 𐑯𐑴𐑑𐑦𐑕 𐑣𐑬 𐑒𐑤𐑳𐑥𐑟𐑦, 𐑷𐑒𐑢𐑼𐑛, 𐑜𐑮𐑱𐑕𐑤𐑩𐑕 𐑣𐑦𐑟 𐑩𐑑𐑧𐑥𐑐𐑑 𐑨𐑑 𐑮𐑦𐑟𐑦𐑕𐑑𐑦𐑙 𐑥𐑩𐑯𐑦𐑐𐑿𐑤𐑱𐑖𐑩𐑯 / 𐑕𐑱𐑝𐑦𐑙 𐑓𐑱𐑕 / 𐑖𐑴𐑦𐑙 𐑪𐑓 𐑣𐑨𐑛 𐑩𐑐𐑽𐑛 𐑒𐑩𐑥𐑐𐑺𐑛 𐑑 ·𐑛𐑮𐑱𐑒𐑴. \emph{𐑲 𐑯𐑰𐑛 𐑞𐑴𐑟 𐑑𐑿𐑑𐑼𐑟.}

“𐑷𐑤 𐑮𐑲𐑑,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑭𐑓𐑑𐑼 𐑩 𐑑𐑲𐑥. “𐑣𐑽'𐑟 𐑥𐑲𐑯.” 𐑣𐑰 𐑜𐑤𐑭𐑯𐑕𐑑 𐑼𐑬𐑯𐑛 𐑯 𐑞𐑧𐑯 𐑮𐑴𐑤𐑛 𐑞 𐑕𐑒𐑸𐑓 𐑚𐑨𐑒 𐑳𐑐 𐑴𐑝𐑼 𐑣𐑦𐑟 𐑓𐑱𐑕, 𐑦𐑒𐑕𐑐𐑴𐑟𐑦𐑙 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑚𐑳𐑑 𐑞 𐑕𐑒𐑸. “𐑳𐑥…𐑦𐑑 𐑕𐑬𐑯𐑛𐑟 𐑤𐑲𐑒 𐑿 𐑒𐑨𐑯 𐑮𐑾𐑤𐑦 𐑮𐑦𐑤𐑲 𐑪𐑯 𐑘𐑹 𐑓𐑭𐑞𐑼. 𐑲 𐑥𐑰𐑯…𐑦𐑓 𐑿 𐑑𐑷𐑒 𐑑 𐑣𐑦𐑥 𐑕𐑽𐑾𐑕𐑤𐑦, 𐑣𐑰'𐑤 𐑷𐑤𐑢𐑱𐑟 𐑤𐑦𐑕𐑩𐑯 𐑑 𐑿 𐑯 𐑑𐑱𐑒 𐑿 𐑕𐑽𐑾𐑕𐑤𐑦.”

·𐑛𐑮𐑱𐑒𐑴 𐑯𐑪𐑛𐑩𐑛.

“𐑕𐑳𐑥𐑑𐑲𐑥𐑟,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑯 𐑕𐑢𐑪𐑤𐑴𐑛. 𐑞𐑦𐑕 𐑢𐑪𐑟 𐑕𐑼𐑐𐑮𐑲𐑟𐑦𐑙𐑤𐑦 𐑣𐑸𐑛, 𐑚𐑳𐑑 𐑞𐑧𐑯 𐑦𐑑 𐑢𐑪𐑟 𐑥𐑧𐑯𐑑 𐑑 𐑚𐑰. “𐑕𐑳𐑥𐑑𐑲𐑥𐑟 𐑲 𐑢𐑦𐑖 𐑥𐑲 𐑴𐑯 ·𐑛𐑨𐑛 𐑢𐑪𐑟 𐑤𐑲𐑒 𐑘𐑹𐑟.” 𐑣𐑨𐑮𐑦'𐑟 𐑲𐑟 𐑓𐑤𐑦𐑯𐑗𐑑 𐑩𐑢𐑱 𐑓𐑮𐑪𐑥 ·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑓𐑱𐑕, 𐑥𐑹 𐑹 𐑤𐑧𐑕 𐑷𐑑𐑩𐑥𐑨𐑑𐑦𐑒𐑤𐑦, 𐑯 𐑞𐑧𐑯 ·𐑣𐑨𐑮𐑦 𐑓𐑹𐑕𐑑 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑑 𐑤𐑫𐑒 𐑚𐑨𐑒 𐑨𐑑 ·𐑛𐑮𐑱𐑒𐑴.

𐑞𐑧𐑯 𐑦𐑑 𐑣𐑦𐑑 ·𐑣𐑨𐑮𐑦 \emph{𐑢𐑪𐑑 𐑪𐑯 ·𐑻𐑔 𐑣𐑰'𐑛 𐑡𐑳𐑕𐑑 𐑕𐑧𐑛}, 𐑯 ·𐑣𐑨𐑮𐑦 𐑣𐑱𐑕𐑑𐑦𐑤𐑦 𐑨𐑛𐑩𐑛, “𐑯𐑪𐑑 𐑞𐑨𐑑 𐑲 𐑢𐑦𐑖 𐑥𐑲 ·𐑛𐑨𐑛 𐑢𐑪𐑟 𐑩 𐑓𐑤𐑷𐑤𐑩𐑕 𐑦𐑯𐑕𐑑𐑮𐑩𐑥𐑧𐑯𐑑 𐑝 𐑛𐑧𐑔 𐑤𐑲𐑒 ·𐑤𐑵𐑕𐑾𐑕, 𐑲 𐑴𐑯𐑤𐑦 𐑥𐑰𐑯 𐑑𐑱𐑒𐑦𐑙 𐑥𐑰 𐑕𐑽𐑾𐑕𐑤𐑦—”

“𐑲 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛 𐑢𐑦𐑞 𐑩 𐑕𐑥𐑲𐑤. “𐑞𐑺…𐑯𐑬 𐑛𐑳𐑟𐑩𐑯𐑑 𐑦𐑑 𐑓𐑰𐑤 𐑤𐑲𐑒 𐑢𐑰'𐑼 𐑩 𐑤𐑦𐑑𐑩𐑤 𐑒𐑤𐑴𐑕𐑼 𐑑 𐑚𐑰𐑦𐑙 𐑓𐑮𐑧𐑯𐑛𐑟?”

·𐑣𐑨𐑮𐑦 𐑯𐑪𐑛𐑩𐑛. “𐑘𐑧𐑩. 𐑦𐑑 𐑛𐑳𐑟, 𐑨𐑒𐑗𐑵𐑩𐑤𐑦. 𐑳𐑥…𐑯𐑴 𐑩𐑓𐑧𐑯𐑕, 𐑚𐑳𐑑 𐑲'𐑥 𐑜𐑴𐑦𐑙 𐑑 𐑐𐑫𐑑 𐑪𐑯 𐑥𐑲 𐑛𐑦𐑕𐑜𐑲𐑟 𐑩𐑜𐑱𐑯, 𐑲 \emph{𐑮𐑾𐑤𐑦} 𐑛𐑴𐑯𐑑 𐑢𐑪𐑯𐑑 𐑑 𐑛𐑰𐑤 𐑢𐑦𐑞—”

“𐑲 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛.”

·𐑣𐑨𐑮𐑦 𐑮𐑴𐑤𐑛 𐑞 𐑕𐑒𐑸𐑓 𐑚𐑨𐑒 𐑛𐑬𐑯 𐑴𐑝𐑼 𐑣𐑦𐑟 𐑓𐑱𐑕.

“𐑥𐑲 𐑓𐑭𐑞𐑼 𐑑𐑱𐑒𐑕 𐑷𐑤 𐑣𐑦𐑟 𐑓𐑮𐑧𐑯𐑛𐑟 𐑕𐑽𐑾𐑕𐑤𐑦,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛. “𐑞𐑨𐑑'𐑕 𐑢𐑲 𐑣𐑰 𐑣𐑨𐑟 𐑤𐑪𐑑𐑕 𐑝 𐑓𐑮𐑧𐑯𐑛𐑟. 𐑿 𐑖𐑫𐑛 𐑥𐑰𐑑 𐑣𐑦𐑥.”

“𐑲'𐑤 𐑔𐑦𐑙𐑒 𐑩𐑚𐑬𐑑 𐑦𐑑,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑦𐑯 𐑩 𐑯𐑿𐑑𐑮𐑩𐑤 𐑝𐑶𐑕. 𐑣𐑰 𐑖𐑫𐑒 𐑣𐑦𐑟 𐑣𐑧𐑛 𐑦𐑯 𐑢𐑳𐑯𐑛𐑼. “𐑕𐑴 𐑿 𐑮𐑾𐑤𐑦 𐑸 𐑣𐑦𐑟 𐑢𐑳𐑯 𐑢𐑰𐑒 𐑐𐑶𐑯𐑑. 𐑣𐑳.”

𐑯𐑬 ·𐑛𐑮𐑱𐑒𐑴 𐑢𐑪𐑟 𐑜𐑦𐑝𐑦𐑙 ·𐑣𐑨𐑮𐑦 𐑩 \emph{𐑮𐑾𐑤𐑦} 𐑪𐑛 𐑤𐑫𐑒. “𐑿 𐑢𐑪𐑯𐑑 𐑑 𐑜𐑴 𐑜𐑧𐑑 𐑕𐑳𐑥𐑔𐑦𐑙 𐑑 𐑛𐑮𐑦𐑙𐑒 𐑯 𐑓𐑲𐑯𐑛 𐑕𐑳𐑥𐑢𐑺 𐑑 𐑕𐑦𐑑 𐑛𐑬𐑯?”

·𐑣𐑨𐑮𐑦 𐑮𐑾𐑤𐑲𐑟𐑛 𐑣𐑰 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑕𐑑𐑨𐑯𐑛𐑦𐑙 𐑦𐑯 𐑢𐑳𐑯 𐑐𐑤𐑱𐑕 𐑓 𐑑𐑵 𐑤𐑪𐑙, 𐑯 𐑕𐑑𐑮𐑧𐑗𐑑 𐑣𐑦𐑥𐑕𐑧𐑤𐑓, 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑒𐑮𐑦𐑒 𐑣𐑦𐑟 𐑚𐑨𐑒. “𐑖𐑫𐑼.”

𐑞 𐑐𐑤𐑨𐑑𐑓𐑹𐑥 𐑢𐑪𐑟 𐑕𐑑𐑸𐑑𐑦𐑙 𐑑 𐑓𐑦𐑤 𐑳𐑐 𐑯𐑬, 𐑚𐑳𐑑 𐑞𐑺 𐑢𐑪𐑟 𐑕𐑑𐑦𐑤 𐑩 𐑒𐑢𐑲𐑩𐑑𐑼 𐑺𐑾 𐑪𐑯 𐑞 𐑓𐑸 𐑕𐑲𐑛 𐑩𐑢𐑱 𐑓𐑮𐑪𐑥 𐑞 𐑮𐑧𐑛 𐑕𐑑𐑰𐑥 𐑧𐑯𐑡𐑦𐑯. 𐑩𐑤𐑪𐑙 𐑞 𐑢𐑱 𐑞𐑱 𐑐𐑭𐑕𐑑 𐑩 𐑕𐑑𐑷𐑤 𐑒𐑩𐑯𐑑𐑱𐑯𐑦𐑙 𐑩 𐑚𐑷𐑤𐑛, 𐑚𐑽𐑛𐑩𐑛 𐑥𐑨𐑯 𐑪𐑓𐑼𐑦𐑙 𐑯𐑿𐑟𐑐𐑱𐑐𐑼𐑟 𐑯 𐑒𐑪𐑥𐑦𐑒 𐑚𐑫𐑒𐑕 𐑯 𐑕𐑑𐑨𐑒𐑑 𐑯𐑰𐑪𐑯-𐑜𐑮𐑰𐑯 𐑒𐑨𐑯𐑟.

𐑞 𐑕𐑑𐑷𐑤-𐑣𐑴𐑤𐑛𐑼 𐑢𐑪𐑟, 𐑦𐑯 𐑓𐑨𐑒𐑑, 𐑤𐑰𐑯𐑦𐑙 𐑚𐑨𐑒 𐑯 𐑛𐑮𐑦𐑙𐑒𐑦𐑙 𐑬𐑑 𐑝 𐑢𐑳𐑯 𐑝 𐑞 𐑯𐑰𐑪𐑯-𐑜𐑮𐑰𐑯 𐑒𐑨𐑯𐑟 𐑨𐑑 𐑞 𐑦𐑜𐑟𐑨𐑒𐑑 𐑐𐑶𐑯𐑑 𐑢𐑧𐑯 𐑣𐑰 𐑕𐑐𐑪𐑑𐑩𐑛 𐑞 𐑮𐑦𐑓𐑲𐑯𐑛 𐑯 𐑧𐑤𐑦𐑜𐑩𐑯𐑑 ·𐑛𐑮𐑱𐑒𐑴 ·𐑥𐑨𐑤𐑓𐑶 𐑩𐑐𐑮𐑴𐑗𐑦𐑙 𐑩𐑤𐑪𐑙 𐑢𐑦𐑞 𐑩 𐑥𐑦𐑕𐑑𐑽𐑾𐑕 𐑚𐑶 𐑤𐑫𐑒𐑦𐑙 𐑦𐑯𐑒𐑮𐑧𐑛𐑩𐑚𐑤𐑦 𐑕𐑑𐑿𐑐𐑦𐑛 𐑢𐑦𐑞 𐑩 𐑕𐑒𐑸𐑓 𐑑𐑲𐑛 𐑴𐑝𐑼 𐑣𐑦𐑟 𐑓𐑱𐑕, 𐑒𐑷𐑟𐑦𐑙 𐑞 𐑕𐑑𐑷𐑤-𐑣𐑴𐑤𐑛𐑼 𐑑 𐑦𐑒𐑕𐑐𐑽𐑾𐑯𐑕 𐑩 𐑕𐑳𐑛𐑩𐑯 𐑒𐑪𐑓𐑦𐑙 𐑓𐑦𐑑 𐑦𐑯 𐑥𐑦𐑛-𐑛𐑮𐑦𐑙𐑒 𐑯 𐑛𐑮𐑦𐑚𐑩𐑤 𐑩 𐑤𐑸𐑡 𐑩𐑥𐑬𐑯𐑑 𐑝 𐑯𐑰𐑪𐑯-𐑜𐑮𐑰𐑯 𐑤𐑦𐑒𐑢𐑦𐑛 𐑪𐑯𐑑𐑵 𐑣𐑦𐑟 𐑚𐑽𐑛.

“'𐑕𐑒𐑿𐑟 𐑥𐑰,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, “𐑚𐑳𐑑 𐑢𐑪𐑑 \emph{𐑦𐑟} 𐑞𐑨𐑑 𐑕𐑑𐑳𐑓, 𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦?”

“·𐑒𐑳𐑥𐑛-·𐑑𐑰,” 𐑕𐑧𐑛 𐑞 𐑕𐑑𐑷𐑤-𐑣𐑴𐑤𐑛𐑼 “𐑦𐑓 𐑿 𐑛𐑮𐑦𐑙𐑒 𐑦𐑑, 𐑕𐑳𐑥𐑔𐑦𐑙 𐑕𐑼𐑐𐑮𐑲𐑟𐑦𐑙 𐑦𐑟 𐑚𐑬𐑯𐑛 𐑑 𐑣𐑨𐑐𐑩𐑯 𐑢𐑦𐑗 𐑥𐑱𐑒𐑕 𐑿 𐑕𐑐𐑦𐑤 𐑦𐑑 𐑪𐑯 𐑘𐑹𐑕𐑧𐑤𐑓 𐑹 𐑕𐑳𐑥𐑢𐑳𐑯 𐑧𐑤𐑕. 𐑚𐑳𐑑 𐑦𐑑'𐑕 𐑗𐑸𐑥𐑛 𐑑 𐑝𐑨𐑯𐑦𐑖 𐑡𐑳𐑕𐑑 𐑩 𐑓𐑿 𐑕𐑱𐑒𐑪𐑯𐑛𐑟 𐑤𐑱𐑑𐑼—” 𐑦𐑯𐑛𐑰𐑛 𐑞 𐑕𐑑𐑱𐑯 𐑪𐑯 𐑣𐑦𐑟 𐑚𐑽𐑛 𐑢𐑪𐑟 𐑷𐑤𐑮𐑧𐑛𐑦 𐑛𐑦𐑕𐑩𐑐𐑽𐑦𐑙.

“𐑣𐑬 𐑛𐑮𐑴𐑤,” 𐑕𐑧𐑛 ·𐑛𐑮𐑱𐑒𐑴. “𐑣𐑬 𐑝𐑧𐑮𐑦, 𐑝𐑧𐑮𐑦 𐑛𐑮𐑴𐑤. 𐑒𐑳𐑥, ·𐑥𐑼~·𐑚𐑮𐑪𐑯𐑟, 𐑤𐑧𐑑'𐑕 𐑜𐑴 𐑓𐑲𐑯𐑛 𐑩𐑯𐑳𐑞𐑼—”

“𐑣𐑴𐑤𐑛 𐑪𐑯,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛.

“\emph{𐑴 𐑒𐑳𐑥 𐑪𐑯!} 𐑞𐑨𐑑'𐑕 𐑡𐑳𐑕𐑑, 𐑡𐑳𐑕𐑑 \emph{𐑡𐑵𐑝𐑩𐑯𐑲𐑤}!”

“𐑯𐑴, 𐑲'𐑥 𐑕𐑪𐑮𐑦 ·𐑛𐑮𐑱𐑒𐑴, 𐑲 \emph{𐑣𐑨𐑓} 𐑑 𐑦𐑯𐑝𐑧𐑕𐑑𐑦𐑜𐑱𐑑 𐑞𐑦𐑕. 𐑢𐑪𐑑 𐑣𐑨𐑐𐑩𐑯𐑟 𐑦𐑓 𐑲 𐑛𐑮𐑦𐑙𐑒 ·𐑒𐑳𐑥𐑛-·𐑑𐑰 𐑢𐑲𐑤 𐑛𐑵𐑦𐑙 𐑥𐑲 𐑚𐑧𐑕𐑑 𐑑 𐑒𐑰𐑐 𐑞 𐑒𐑪𐑯𐑝𐑼𐑕𐑱𐑖𐑩𐑯 𐑒𐑩𐑥𐑐𐑤𐑰𐑑𐑤𐑦 𐑕𐑽𐑾𐑕?”

𐑞 𐑕𐑑𐑷𐑤-𐑣𐑴𐑤𐑛𐑼 𐑕𐑥𐑲𐑤𐑛 𐑥𐑦𐑕𐑑𐑽𐑾𐑕𐑤𐑦. “𐑣𐑵 𐑯𐑴𐑟? 𐑩 𐑓𐑮𐑧𐑯𐑛 𐑢𐑷𐑒𐑕 𐑚𐑲 𐑦𐑯 𐑩 𐑓𐑮𐑪𐑜 𐑒𐑪𐑕𐑑𐑿𐑥? 𐑕𐑳𐑥𐑔𐑦𐑙 𐑳𐑯𐑦𐑒𐑕𐑐𐑧𐑒𐑑𐑩𐑛 𐑦𐑟 𐑚𐑬𐑯𐑛 𐑑 𐑣𐑨𐑐𐑩𐑯—”

“𐑯𐑴. 𐑲'𐑥 𐑕𐑪𐑮𐑦. 𐑲 𐑡𐑳𐑕𐑑 𐑛𐑴𐑯𐑑 𐑚𐑦𐑤𐑰𐑝 𐑦𐑑. 𐑞𐑨𐑑 𐑝𐑲𐑩𐑤𐑱𐑑𐑕 𐑥𐑲 𐑥𐑳𐑗-𐑩𐑚𐑿𐑟𐑛 𐑕𐑩𐑕𐑐𐑧𐑯𐑖𐑩𐑯 𐑝 𐑛𐑦𐑕𐑚𐑦𐑤𐑰𐑓 𐑪𐑯 𐑕𐑴 𐑥𐑧𐑯𐑦 𐑤𐑧𐑝𐑩𐑤𐑟 𐑲 𐑛𐑴𐑯𐑑 𐑰𐑝𐑩𐑯 𐑣𐑨𐑝 𐑞 𐑤𐑨𐑙𐑜𐑢𐑦𐑡 𐑑 𐑛𐑦𐑕𐑒𐑮𐑲𐑚 𐑦𐑑. 𐑞𐑺 𐑦𐑟, 𐑞𐑺 𐑦𐑟 𐑡𐑳𐑕𐑑 \emph{𐑯𐑴 𐑢𐑱} 𐑩 𐑚𐑤𐑳𐑛𐑦 \emph{𐑛𐑮𐑦𐑙𐑒} 𐑒𐑨𐑯 𐑥𐑩𐑯𐑦𐑐𐑿𐑤𐑱𐑑 𐑮𐑦𐑨𐑤𐑦𐑑𐑦 𐑑 𐑐𐑮𐑩𐑛𐑿𐑕 \emph{𐑒𐑪𐑥𐑩𐑛𐑦 𐑕𐑧𐑑𐑳𐑐𐑕}, 𐑹 𐑲'𐑥 𐑜𐑴𐑦𐑙 𐑑 𐑜𐑦𐑝 𐑳𐑐 𐑯 𐑮𐑦𐑑𐑲𐑼 𐑑 𐑞 ·𐑚𐑩𐑣𐑭𐑥𐑩𐑟—”

·𐑛𐑮𐑱𐑒𐑴 𐑜𐑮𐑴𐑯𐑛. “𐑸 𐑢𐑰 \emph{𐑮𐑾𐑤𐑦} 𐑜𐑴𐑦𐑙 𐑑 𐑛𐑵 𐑞𐑦𐑕?”

“𐑿 𐑛𐑴𐑯𐑑 𐑣𐑨𐑓 𐑑 𐑛𐑮𐑦𐑙𐑒 𐑦𐑑 𐑚𐑳𐑑 𐑲 \emph{𐑣𐑨𐑓} 𐑑 𐑦𐑯𐑝𐑧𐑕𐑑𐑦𐑜𐑱𐑑. \emph{𐑣𐑨𐑓} 𐑑. 𐑣𐑬 𐑥𐑳𐑗?”

“𐑓𐑲𐑝 ·𐑯𐑳𐑑𐑕 𐑞 𐑒𐑨𐑯,” 𐑞 𐑕𐑑𐑷𐑤-𐑣𐑴𐑤𐑛𐑼 𐑕𐑧𐑛.

“\emph{𐑓𐑲𐑝 ·𐑯𐑳𐑑𐑕?} 𐑿 𐑒𐑨𐑯 𐑕𐑧𐑤 𐑮𐑦𐑨𐑤𐑦𐑑𐑦-𐑥𐑩𐑯𐑦𐑐𐑿𐑤𐑱𐑑𐑦𐑙 𐑓𐑦𐑟𐑦 𐑛𐑮𐑦𐑙𐑒𐑕 𐑓 \emph{𐑓𐑲𐑝 ·𐑯𐑳𐑑𐑕 𐑞 𐑒𐑨𐑯?}” ·𐑣𐑨𐑮𐑦 𐑮𐑰𐑗𐑑 𐑦𐑯𐑑𐑵 𐑣𐑦𐑟 𐑐𐑬𐑗, 𐑕𐑧𐑛 “𐑓𐑹 ·𐑕𐑦𐑒𐑩𐑤𐑟, 𐑓𐑹 ·𐑯𐑳𐑑𐑕,” 𐑯 𐑕𐑤𐑨𐑐𐑑 𐑞𐑧𐑥 𐑛𐑬𐑯 𐑪𐑯 𐑞 𐑒𐑬𐑯𐑑𐑼. “𐑑𐑵 𐑛𐑳𐑟𐑩𐑯 𐑒𐑨𐑯𐑟 𐑐𐑤𐑰𐑟.”

“𐑲'𐑤 𐑷𐑤𐑕𐑴 𐑑𐑱𐑒 𐑢𐑳𐑯,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑲𐑛, 𐑯 𐑕𐑑𐑸𐑑𐑩𐑛 𐑑 𐑮𐑰𐑗 𐑓 𐑣𐑦𐑟 𐑐𐑪𐑒𐑩𐑑𐑕.

·𐑣𐑨𐑮𐑦 𐑖𐑫𐑒 𐑣𐑦𐑟 𐑣𐑧𐑛 𐑮𐑨𐑐𐑦𐑛𐑤𐑦. “𐑯𐑴, 𐑲'𐑝 𐑜𐑪𐑑 𐑞𐑦𐑕, 𐑛𐑳𐑟𐑩𐑯𐑑 𐑒𐑬𐑯𐑑 𐑨𐑟 𐑩 𐑓𐑱𐑝𐑼 𐑲𐑞𐑼, 𐑲 𐑢𐑪𐑯𐑑 𐑑 𐑕𐑰 𐑦𐑓 𐑦𐑑 𐑢𐑻𐑒𐑕 𐑓 𐑿 𐑑𐑵.” 𐑣𐑰 𐑑𐑫𐑒 𐑩 𐑒𐑨𐑯 𐑓𐑮𐑪𐑥 𐑞 𐑕𐑑𐑨𐑒 𐑯𐑬 𐑐𐑤𐑱𐑕𐑑 𐑪𐑯 𐑞 𐑒𐑬𐑯𐑑𐑼 𐑯 𐑑𐑪𐑕𐑑 𐑦𐑑 𐑑 ·𐑛𐑮𐑱𐑒𐑴, 𐑞𐑧𐑯 𐑕𐑑𐑸𐑑𐑩𐑛 𐑓𐑰𐑛𐑦𐑙 𐑣𐑦𐑟 𐑐𐑬𐑗. 𐑞 𐑐𐑬𐑗'𐑩𐑟 ·𐑢𐑲𐑛𐑩𐑯𐑦𐑙 ·𐑤𐑦𐑐 𐑱𐑑 𐑞 𐑒𐑨𐑯𐑟 𐑩𐑒𐑳𐑥𐑐𐑩𐑯𐑦𐑛 𐑚𐑲 𐑕𐑥𐑷𐑤 𐑚𐑻𐑐𐑦𐑙 𐑯𐑶𐑟𐑩𐑟, 𐑢𐑦𐑗 𐑢𐑪𐑟𐑩𐑯𐑑 𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦 𐑣𐑧𐑤𐑐𐑦𐑙 𐑑 𐑮𐑦𐑕𐑑𐑹 ·𐑣𐑨𐑮𐑦'𐑟 𐑓𐑱𐑔 𐑞𐑨𐑑 𐑣𐑰 𐑢𐑫𐑛 𐑕𐑳𐑥 𐑛𐑱 𐑛𐑦𐑕𐑒𐑳𐑝𐑼 𐑩 𐑮𐑰𐑟𐑩𐑯𐑩𐑚𐑩𐑤 𐑧𐑒𐑕𐑐𐑤𐑩𐑯𐑱𐑖𐑩𐑯 𐑓 𐑷𐑤 𐑞𐑦𐑕.

𐑑𐑢𐑧𐑯𐑑𐑦-𐑑𐑵 𐑚𐑻𐑐𐑕 𐑤𐑱𐑑𐑼, ·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑞 𐑤𐑭𐑕𐑑 𐑐𐑻𐑗𐑩𐑕𐑑 𐑒𐑨𐑯 𐑦𐑯 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛, ·𐑛𐑮𐑱𐑒𐑴 𐑢𐑪𐑟 𐑤𐑫𐑒𐑦𐑙 𐑨𐑑 𐑣𐑦𐑥 𐑦𐑒𐑕𐑐𐑧𐑒𐑑𐑩𐑯𐑑𐑤𐑦, 𐑯 𐑞 𐑑𐑵 𐑝 𐑞𐑧𐑥 𐑐𐑫𐑤𐑛 𐑞 𐑮𐑦𐑙 𐑨𐑑 𐑞 𐑕𐑱𐑥 𐑑𐑲𐑥.

·𐑣𐑨𐑮𐑦 𐑮𐑴𐑤𐑛 𐑳𐑐 𐑣𐑦𐑟 𐑕𐑒𐑸𐑓 𐑑 𐑦𐑒𐑕𐑐𐑴𐑟 𐑣𐑦𐑟 𐑥𐑬𐑔, 𐑯 𐑞𐑱 𐑑𐑦𐑤𐑑𐑩𐑛 𐑞𐑺 𐑣𐑧𐑛𐑟 𐑚𐑨𐑒 𐑯 𐑛𐑮𐑨𐑙𐑒 𐑞 ·𐑒𐑳𐑥𐑛-·𐑑𐑰.

𐑦𐑑 𐑕𐑳𐑥𐑣𐑬 \emph{𐑑𐑱𐑕𐑑𐑩𐑛} 𐑚𐑮𐑲𐑑 𐑜𐑮𐑰𐑯—𐑧𐑒𐑕𐑑𐑮𐑩-𐑓𐑦𐑟𐑦 𐑯 𐑤𐑲𐑥𐑼 𐑞𐑨𐑯 𐑤𐑲𐑥.

𐑩𐑕𐑲𐑛 𐑓𐑮𐑪𐑥 𐑞𐑨𐑑, 𐑯𐑳𐑔𐑦𐑙 𐑧𐑤𐑕 𐑣𐑨𐑐𐑩𐑯𐑛.

·𐑣𐑨𐑮𐑦 𐑤𐑫𐑒𐑑 𐑨𐑑 𐑞 𐑕𐑑𐑷𐑤-𐑣𐑴𐑤𐑛𐑼, 𐑣𐑵 𐑢𐑪𐑟 𐑢𐑪𐑗𐑦𐑙 𐑞𐑧𐑥 𐑚𐑦𐑯𐑧𐑝𐑩𐑤𐑩𐑯𐑑𐑤𐑦.

\emph{𐑷𐑤 𐑮𐑲𐑑, 𐑦𐑓 𐑞𐑦𐑕 𐑜𐑲 𐑡𐑳𐑕𐑑 𐑑𐑫𐑒 𐑩𐑛𐑝𐑭𐑯𐑑𐑦𐑡 𐑝 𐑩 𐑯𐑨𐑗𐑼𐑩𐑤 𐑨𐑒𐑕𐑦𐑛𐑩𐑯𐑑 𐑑 𐑕𐑧𐑤 𐑥𐑰 𐑑𐑢𐑧𐑯𐑑𐑦-𐑓𐑹 𐑒𐑨𐑯𐑟 𐑝 𐑯𐑳𐑔𐑦𐑙, 𐑲'𐑥 𐑜𐑴𐑦𐑙 𐑑 𐑩𐑐𐑤𐑷𐑛 𐑣𐑦𐑟 𐑒𐑮𐑦𐑱𐑑𐑦𐑝 𐑪𐑯𐑑𐑮𐑩𐑐𐑮𐑩𐑯𐑻𐑾𐑤 𐑕𐑐𐑦𐑮𐑦𐑑 𐑯 𐑞𐑧𐑯 𐑒𐑦𐑤 𐑣𐑦𐑥.}

“𐑦𐑑 𐑛𐑳𐑟𐑩𐑯𐑑 𐑷𐑤𐑢𐑱𐑟 𐑣𐑨𐑐𐑩𐑯 𐑦𐑥𐑰𐑛𐑾𐑑𐑤𐑦,” 𐑞 𐑕𐑑𐑷𐑤-𐑣𐑴𐑤𐑛𐑼 𐑕𐑧𐑛. “𐑚𐑳𐑑 𐑦𐑑'𐑕 𐑜𐑨𐑮𐑩𐑯𐑑𐑰𐑛 𐑑 𐑣𐑨𐑐𐑩𐑯 𐑢𐑳𐑯𐑕 𐑐𐑻 𐑒𐑨𐑯, 𐑹 𐑘𐑹 𐑥𐑳𐑯𐑦 𐑚𐑨𐑒.”

·𐑣𐑨𐑮𐑦 𐑑𐑫𐑒 𐑩𐑯𐑳𐑞𐑼 𐑤𐑪𐑙 𐑛𐑮𐑦𐑙𐑒.

𐑢𐑳𐑯𐑕 𐑩𐑜𐑱𐑯, 𐑯𐑳𐑔𐑦𐑙 𐑣𐑨𐑐𐑩𐑯𐑛.

\emph{𐑥𐑱𐑚𐑰 𐑲 𐑖𐑫𐑛 𐑡𐑳𐑕𐑑 𐑗𐑳𐑜 𐑞 𐑣𐑴𐑤 𐑔𐑦𐑙 𐑨𐑟 𐑓𐑭𐑕𐑑 𐑨𐑟 𐑐𐑪𐑕𐑩𐑚𐑩𐑤…𐑯 𐑣𐑴𐑐 𐑥𐑲 𐑕𐑑𐑳𐑥𐑩𐑒 𐑛𐑳𐑟𐑩𐑯𐑑 𐑦𐑒𐑕𐑐𐑤𐑴𐑛 𐑓𐑮𐑪𐑥 𐑷𐑤 𐑞 𐑒𐑸𐑚𐑩𐑯 𐑛𐑲𐑪𐑒𐑕𐑲𐑛, 𐑹 𐑞𐑨𐑑 𐑲 𐑛𐑴𐑯𐑑 𐑚𐑻𐑐 𐑢𐑲𐑤 𐑛𐑮𐑦𐑙𐑒𐑦𐑙 𐑦𐑑…}

𐑯𐑴, 𐑣𐑰 𐑒𐑫𐑛 𐑩𐑓𐑹𐑛 𐑑 𐑚𐑰 𐑩 \emph{𐑤𐑦𐑑𐑩𐑤} 𐑐𐑱𐑖𐑩𐑯𐑑. 𐑚𐑳𐑑 𐑪𐑯𐑩𐑕𐑑𐑤𐑦, ·𐑣𐑨𐑮𐑦 𐑛𐑦𐑛𐑩𐑯𐑑 𐑕𐑰 𐑣𐑬 𐑞𐑦𐑕 𐑢𐑪𐑟 𐑜𐑴𐑦𐑙 𐑑 𐑢𐑻𐑒. 𐑿 𐑒𐑫𐑛𐑩𐑯𐑑 𐑜𐑴 𐑳𐑐 𐑑 𐑕𐑳𐑥𐑢𐑳𐑯 𐑯 𐑕𐑱 “𐑯𐑬 𐑲'𐑥 𐑜𐑴𐑦𐑙 𐑑 𐑕𐑼𐑐𐑮𐑲𐑟 𐑿” 𐑹 “𐑯 𐑯𐑬 𐑲'𐑥 𐑜𐑴𐑦𐑙 𐑑 𐑑𐑧𐑤 𐑿 𐑞 𐑐𐑳𐑯𐑗𐑤𐑲𐑯 𐑝 𐑞 𐑡𐑴𐑒, 𐑯 𐑦𐑑'𐑤 𐑚𐑰 𐑮𐑾𐑤𐑦 𐑓𐑳𐑯𐑦.” 𐑦𐑑 𐑮𐑵𐑦𐑯𐑛 𐑞 𐑖𐑪𐑒 𐑝𐑨𐑤𐑿. 𐑦𐑯 ·𐑣𐑨𐑮𐑦'𐑟 𐑕𐑑𐑱𐑑 𐑝 𐑥𐑧𐑯𐑑𐑩𐑤 𐑐𐑮𐑦𐑐𐑺𐑩𐑛𐑯𐑩𐑕, ·𐑤𐑵𐑕𐑾𐑕 ·𐑥𐑨𐑤𐑓𐑶 𐑒𐑫𐑛 𐑣𐑨𐑝 𐑢𐑷𐑒𐑑 𐑐𐑭𐑕𐑑 𐑦𐑯 𐑩 𐑚𐑨𐑤𐑼𐑰𐑯𐑩 𐑬𐑑𐑓𐑦𐑑 𐑯 𐑦𐑑 𐑢𐑫𐑛𐑩𐑯𐑑 𐑣𐑨𐑝 𐑥𐑱𐑛 𐑣𐑦𐑥 𐑛𐑵 𐑩 𐑐𐑮𐑪𐑐𐑼 𐑕𐑐𐑦𐑑-𐑑𐑱𐑒. 𐑡𐑳𐑕𐑑 𐑢𐑪𐑑 𐑕𐑹𐑑 𐑝 𐑢𐑨𐑒𐑦 𐑖𐑩𐑯𐑨𐑯𐑦𐑜𐑩𐑯 𐑢𐑪𐑟 𐑞 𐑿𐑯𐑦𐑝𐑻𐑕 𐑕𐑩𐑐𐑴𐑕𐑑 𐑑 𐑒𐑪𐑓 𐑳𐑐 \emph{𐑯𐑬}?

“𐑧𐑯𐑦𐑢𐑱, 𐑤𐑧𐑑'𐑕 𐑕𐑦𐑑 𐑛𐑬𐑯,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. 𐑣𐑰 𐑐𐑮𐑦𐑐𐑺𐑛 𐑑 𐑕𐑢𐑦𐑜 𐑩𐑯𐑳𐑞𐑼 𐑛𐑮𐑦𐑙𐑒 𐑯 𐑕𐑑𐑸𐑑𐑩𐑛 𐑑𐑩𐑢𐑹𐑛𐑟 𐑞 𐑛𐑦𐑕𐑑𐑩𐑯𐑑 𐑕𐑰𐑑𐑦𐑙 𐑺𐑾, 𐑢𐑦𐑗 𐑐𐑫𐑑 𐑣𐑦𐑥 𐑨𐑑 𐑞 𐑮𐑲𐑑 𐑨𐑙𐑜𐑩𐑤 𐑑 𐑜𐑤𐑭𐑯𐑕 𐑚𐑨𐑒 𐑯 𐑕𐑰 𐑞 𐑐𐑹𐑖𐑩𐑯 𐑝 𐑞 𐑕𐑑𐑷𐑤'𐑟 𐑯𐑿𐑟𐑐𐑱𐑐𐑼 𐑕𐑑𐑨𐑯𐑛 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑛𐑦𐑝𐑴𐑑𐑩𐑛 𐑑 𐑩 𐑯𐑿𐑟𐑐𐑱𐑐𐑼 𐑒𐑷𐑤𐑛 \emph{𐑞 ·𐑒𐑢𐑦𐑚𐑩𐑤𐑼}, 𐑢𐑦𐑗 𐑢𐑪𐑟 𐑖𐑴𐑦𐑙 𐑞 𐑓𐑪𐑤𐑴𐑦𐑙 𐑣𐑧𐑛𐑤𐑲𐑯:

\headline{·𐑚𐑶-𐑣𐑵-·𐑤𐑦𐑝𐑛 ·𐑜𐑧𐑑𐑕\\
·𐑛𐑮𐑱𐑒𐑴 ·𐑥𐑨𐑤𐑓𐑶 ·𐑐𐑮𐑧𐑜𐑯𐑩𐑯𐑑}

“\emph{𐑜𐑭!}” 𐑕𐑒𐑮𐑰𐑥𐑛 ·𐑛𐑮𐑱𐑒𐑴 𐑨𐑟 𐑚𐑮𐑲𐑑 𐑜𐑮𐑰𐑯 𐑤𐑦𐑒𐑢𐑦𐑛 𐑕𐑐𐑮𐑱𐑛 𐑷𐑤 𐑴𐑝𐑼 𐑣𐑦𐑥 𐑓𐑮𐑪𐑥 ·𐑣𐑨𐑮𐑦'𐑟 𐑛𐑦𐑮𐑧𐑒𐑖𐑩𐑯. ·𐑛𐑮𐑱𐑒𐑴 𐑑𐑻𐑯𐑛 𐑑 ·𐑣𐑨𐑮𐑦 𐑢𐑦𐑞 𐑓𐑲𐑼 𐑦𐑯 𐑣𐑦𐑟 𐑲𐑟 𐑯 𐑜𐑮𐑨𐑚𐑛 𐑣𐑦𐑟 𐑴𐑯 𐑒𐑨𐑯. “𐑿 𐑕𐑳𐑯 𐑝 𐑩 𐑥𐑳𐑛𐑚𐑤𐑳𐑛! 𐑤𐑧𐑑'𐑕 𐑕𐑰 𐑣𐑬 \emph{𐑿} 𐑤𐑲𐑒 𐑚𐑰𐑦𐑙 𐑕𐑐𐑨𐑑 𐑩𐑐𐑪𐑯!” ·𐑛𐑮𐑱𐑒𐑴 𐑑𐑫𐑒 𐑩 𐑛𐑦𐑤𐑦𐑚𐑼𐑩𐑑 𐑕𐑢𐑦𐑜 𐑓𐑮𐑪𐑥 𐑞 𐑒𐑨𐑯 𐑡𐑳𐑕𐑑 𐑨𐑟 𐑣𐑦𐑟 𐑴𐑯 𐑲𐑟 𐑒𐑷𐑑 𐑕𐑲𐑑 𐑝 𐑞 𐑣𐑧𐑛𐑤𐑲𐑯.

𐑦𐑯 𐑖𐑽 𐑮𐑰𐑓𐑤𐑧𐑒𐑕 𐑨𐑒𐑖𐑩𐑯, ·𐑣𐑨𐑮𐑦 𐑑𐑮𐑲𐑛 𐑑 𐑚𐑤𐑪𐑒 𐑣𐑦𐑟 𐑓𐑱𐑕 𐑨𐑟 𐑞 𐑕𐑐𐑮𐑱 𐑝 𐑤𐑦𐑒𐑢𐑦𐑛 𐑓𐑤𐑵 𐑦𐑯 𐑣𐑦𐑟 𐑛𐑦𐑮𐑧𐑒𐑖𐑩𐑯. 𐑳𐑯𐑓𐑹𐑗𐑩𐑯𐑩𐑑𐑤𐑦 𐑣𐑰 𐑚𐑤𐑪𐑒𐑑 𐑿𐑟𐑦𐑙 𐑞 𐑣𐑨𐑯𐑛 𐑒𐑩𐑯𐑑𐑱𐑯𐑦𐑙 𐑞 ·𐑒𐑳𐑥𐑛-·𐑑𐑰, 𐑕𐑧𐑯𐑛𐑦𐑙 𐑞 𐑮𐑧𐑕𐑑 𐑝 𐑞 𐑜𐑮𐑰𐑯 𐑤𐑦𐑒𐑢𐑦𐑛 𐑑 𐑕𐑐𐑤𐑨𐑖 𐑬𐑑 𐑴𐑝𐑼 𐑣𐑦𐑟 𐑖𐑴𐑤𐑛𐑼.

·𐑣𐑨𐑮𐑦 𐑕𐑑𐑺𐑛 𐑨𐑑 𐑞 𐑒𐑨𐑯 𐑦𐑯 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛 𐑰𐑝𐑩𐑯 𐑨𐑟 𐑣𐑰 𐑢𐑧𐑯𐑑 𐑪𐑯 𐑗𐑴𐑒𐑦𐑙 𐑯 𐑕𐑐𐑤𐑳𐑑𐑼𐑦𐑙 𐑯 𐑞 𐑜𐑮𐑰𐑯 𐑒𐑳𐑤𐑼 𐑕𐑑𐑸𐑑𐑩𐑛 𐑑 𐑝𐑨𐑯𐑦𐑖 𐑓𐑮𐑪𐑥 ·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑮𐑴𐑚𐑟.

𐑞𐑧𐑯 𐑣𐑰 𐑤𐑫𐑒𐑑 𐑳𐑐 𐑯 𐑕𐑑𐑺𐑛 𐑨𐑑 𐑞 𐑯𐑿𐑟𐑐𐑱𐑐𐑼 𐑣𐑧𐑛𐑤𐑲𐑯.

\headline{𐑚𐑶-𐑣𐑵-·𐑤𐑦𐑝𐑛 ·𐑜𐑧𐑑𐑕\\
·𐑛𐑮𐑱𐑒𐑴 ·𐑥𐑨𐑤𐑓𐑶 ·𐑐𐑮𐑧𐑜𐑯𐑩𐑯𐑑}

·𐑣𐑨𐑮𐑦'𐑟 𐑤𐑦𐑐𐑕 𐑴𐑐𐑩𐑯𐑛 𐑯 𐑕𐑧𐑛, “𐑚𐑳-𐑚𐑤𐑳-𐑚𐑳-𐑚𐑳…”

𐑑𐑵 𐑥𐑧𐑯𐑦 𐑒𐑩𐑥𐑐𐑰𐑑𐑦𐑙 𐑩𐑚𐑡𐑧𐑒𐑖𐑩𐑯𐑟, 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑞 𐑐𐑮𐑪𐑚𐑤𐑩𐑥. 𐑧𐑝𐑮𐑦 𐑑𐑲𐑥 ·𐑣𐑨𐑮𐑦 𐑑𐑮𐑲𐑛 𐑑 𐑕𐑱 “𐑚𐑳𐑑 𐑢𐑰'𐑼 𐑴𐑯𐑤𐑦 𐑦𐑤𐑧𐑝𐑩𐑯!” 𐑞 𐑩𐑚𐑡𐑧𐑒𐑖𐑩𐑯 “𐑚𐑳𐑑 𐑥𐑧𐑯 𐑒𐑭𐑯𐑑 𐑜𐑧𐑑 𐑐𐑮𐑧𐑜𐑯𐑩𐑯𐑑!” 𐑛𐑦𐑥𐑭𐑯𐑛𐑩𐑛 𐑓𐑻𐑕𐑑 𐑐𐑮𐑲𐑪𐑮𐑦𐑑𐑦 𐑯 𐑢𐑪𐑟 𐑞𐑧𐑯 𐑮𐑳𐑯 𐑴𐑝𐑼 𐑚𐑲 “𐑚𐑳𐑑 𐑞𐑺'𐑟 𐑯𐑳𐑔𐑦𐑙 𐑚𐑦𐑑𐑢𐑰𐑯 𐑳𐑕, 𐑮𐑾𐑤𐑦!”

𐑞𐑧𐑯 ·𐑣𐑨𐑮𐑦 𐑤𐑫𐑒𐑑 𐑛𐑬𐑯 𐑨𐑑 𐑞 𐑒𐑨𐑯 𐑦𐑯 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛 𐑩𐑜𐑱𐑯.

𐑣𐑰 𐑢𐑪𐑟 𐑓𐑰𐑤𐑦𐑙 𐑩 𐑛𐑰𐑐-𐑕𐑰𐑑𐑩𐑛 𐑛𐑦𐑟𐑲𐑼 𐑑 𐑮𐑳𐑯 𐑩𐑢𐑱 𐑕𐑒𐑮𐑰𐑥𐑦𐑙 𐑨𐑑 𐑞 𐑑𐑪𐑐 𐑝 𐑣𐑦𐑟 𐑤𐑳𐑙𐑟 𐑩𐑯𐑑𐑦𐑤 𐑣𐑰 𐑛𐑮𐑪𐑐𐑑 𐑓𐑮𐑪𐑥 𐑤𐑨𐑒 𐑝 𐑪𐑒𐑕𐑦𐑡𐑩𐑯, 𐑯 𐑞 𐑴𐑯𐑤𐑦 𐑔𐑦𐑙 𐑕𐑑𐑪𐑐𐑦𐑙 𐑣𐑦𐑥 𐑢𐑪𐑟 𐑞𐑨𐑑 𐑣𐑰 𐑣𐑨𐑛 𐑢𐑳𐑯𐑕 𐑮𐑧𐑛 𐑞𐑨𐑑 𐑬𐑑𐑮𐑲𐑑 𐑐𐑨𐑯𐑦𐑒 𐑢𐑪𐑟 𐑞 𐑕𐑲𐑯 𐑝 𐑩 \emph{𐑑𐑮𐑵𐑤𐑦} 𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑 𐑕𐑲𐑩𐑯𐑑𐑦𐑓𐑦𐑒 𐑐𐑮𐑪𐑚𐑤𐑩𐑥.

·𐑣𐑨𐑮𐑦 𐑕𐑯𐑸𐑤𐑛, 𐑔𐑮𐑵 𐑞 𐑒𐑨𐑯 𐑝𐑲𐑩𐑤𐑩𐑯𐑑𐑤𐑦 𐑦𐑯𐑑𐑵 𐑩 𐑯𐑽𐑚𐑲 𐑮𐑳𐑚𐑦𐑖 𐑚𐑦𐑯, 𐑯 𐑕𐑑𐑷𐑒𐑑 𐑚𐑨𐑒 𐑴𐑝𐑼 𐑑 𐑞 𐑕𐑑𐑷𐑤. “𐑢𐑳𐑯 𐑒𐑪𐑐𐑦 𐑝 \emph{𐑞 ·𐑒𐑢𐑦𐑚𐑩𐑤𐑼,} 𐑐𐑤𐑰𐑟.” ·𐑣𐑨𐑮𐑦 𐑐𐑱𐑛 𐑴𐑝𐑼 𐑓𐑹 𐑥𐑹 ·𐑯𐑳𐑑𐑕, 𐑮𐑦𐑑𐑮𐑰𐑝𐑛 𐑩𐑯𐑳𐑞𐑼 𐑒𐑨𐑯 𐑝 ·𐑒𐑳𐑥𐑛-·𐑑𐑰 𐑓𐑮𐑪𐑥 𐑣𐑦𐑟 𐑐𐑬𐑗, 𐑯 𐑞𐑧𐑯 𐑕𐑑𐑷𐑒𐑑 𐑴𐑝𐑼 𐑑 𐑞 𐑐𐑦𐑒𐑯𐑦𐑒 𐑺𐑾 𐑢𐑦𐑞 𐑞 𐑚𐑤𐑪𐑯𐑛-𐑣𐑺𐑛 𐑚𐑶, 𐑣𐑵 𐑢𐑪𐑟 𐑕𐑑𐑺𐑦𐑙 𐑨𐑑 𐑣𐑦𐑟 𐑴𐑯 𐑒𐑨𐑯 𐑢𐑦𐑞 𐑩𐑯 𐑦𐑒𐑕𐑐𐑮𐑧𐑖𐑩𐑯 𐑝 𐑓𐑮𐑨𐑙𐑒 𐑨𐑛𐑥𐑼𐑱𐑖𐑩𐑯.

“𐑲 𐑑𐑱𐑒 𐑦𐑑 𐑚𐑨𐑒,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛, “𐑞𐑨𐑑 𐑢𐑪𐑟 𐑐𐑮𐑦𐑑𐑦 𐑜𐑫𐑛.”

“𐑣𐑱, ·𐑛𐑮𐑱𐑒𐑴, 𐑿 𐑯𐑴 𐑢𐑪𐑑 𐑲 𐑚𐑧𐑑 𐑦𐑟 𐑰𐑝𐑩𐑯 𐑚𐑧𐑑𐑼 𐑓 𐑚𐑦𐑒𐑳𐑥𐑦𐑙 𐑓𐑮𐑧𐑯𐑛𐑟 𐑞𐑨𐑯 𐑦𐑒𐑕𐑗𐑱𐑯𐑡𐑦𐑙 𐑕𐑰𐑒𐑮𐑩𐑑𐑕? 𐑒𐑩𐑥𐑦𐑑𐑦𐑙 𐑥𐑻𐑛𐑼.”

“𐑲 𐑣𐑨𐑝 𐑩 𐑑𐑿𐑑𐑼 𐑣𐑵 𐑕𐑧𐑟 𐑞𐑨𐑑,” ·𐑛𐑮𐑱𐑒𐑴 𐑩𐑤𐑬𐑛. 𐑣𐑰 𐑮𐑰𐑗𐑑 𐑦𐑯𐑕𐑲𐑛 𐑣𐑦𐑟 𐑮𐑴𐑚𐑟 𐑯 𐑕𐑒𐑮𐑨𐑗𐑑 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑢𐑦𐑞 𐑩𐑯 𐑰𐑟𐑦, 𐑯𐑨𐑗𐑼𐑩𐑤 𐑥𐑴𐑖𐑩𐑯. “𐑣𐑵'𐑝 𐑿 𐑜𐑪𐑑 𐑦𐑯 𐑥𐑲𐑯𐑛?”

·𐑣𐑨𐑮𐑦 𐑕𐑤𐑨𐑥𐑛 \emph{𐑞 ·𐑒𐑢𐑦𐑚𐑩𐑤𐑼} 𐑛𐑬𐑯 𐑣𐑸𐑛 𐑪𐑯 𐑞 𐑐𐑦𐑒𐑯𐑦𐑒 𐑑𐑱𐑚𐑩𐑤. “𐑞 𐑜𐑲 𐑣𐑵 𐑒𐑱𐑥 𐑳𐑐 𐑢𐑦𐑞 𐑞𐑦𐑕 𐑣𐑧𐑛𐑤𐑲𐑯.”

·𐑛𐑮𐑱𐑒𐑴 𐑜𐑮𐑴𐑯𐑛. “𐑯𐑪𐑑 𐑩 𐑜𐑲. 𐑩 𐑜𐑻𐑤. 𐑩 \emph{𐑑𐑧𐑯-𐑘𐑽-𐑴𐑤𐑛} 𐑜𐑻𐑤, 𐑒𐑨𐑯 𐑿 𐑚𐑦𐑤𐑰𐑝 𐑦𐑑? 𐑖𐑰 𐑢𐑧𐑯𐑑 𐑯𐑳𐑑𐑕 𐑭𐑓𐑑𐑼 𐑣𐑻 𐑥𐑳𐑞𐑼 𐑛𐑲𐑛 𐑯 𐑣𐑻 𐑓𐑭𐑞𐑼, 𐑣𐑵 𐑴𐑯𐑟 𐑞𐑦𐑕 𐑯𐑿𐑟𐑐𐑱𐑐𐑼, 𐑦𐑟 \emph{𐑒𐑩𐑯𐑝𐑦𐑯𐑕𐑑} 𐑞𐑨𐑑 𐑖𐑰'𐑟 𐑩 𐑕𐑰𐑼, 𐑕𐑴 𐑢𐑧𐑯 𐑣𐑰 𐑛𐑳𐑟𐑩𐑯𐑑 𐑯𐑴 𐑣𐑰 𐑭𐑕𐑒𐑕 ·𐑤𐑵𐑯𐑩 ·𐑤𐑳𐑝𐑜𐑫𐑛 𐑯 𐑚𐑦𐑤𐑰𐑝𐑟 \emph{𐑧𐑯𐑦𐑔𐑦𐑙} 𐑖𐑰 𐑕𐑧𐑟.”

𐑯𐑪𐑑 𐑮𐑾𐑤𐑦 𐑔𐑦𐑙𐑒𐑦𐑙 𐑩𐑚𐑬𐑑 𐑦𐑑, ·𐑣𐑨𐑮𐑦 𐑐𐑫𐑤𐑛 𐑞 𐑮𐑦𐑙 𐑪𐑯 𐑣𐑦𐑟 𐑯𐑧𐑒𐑕𐑑 𐑒𐑨𐑯 𐑝 ·𐑒𐑳𐑥𐑛-·𐑑𐑰 𐑯 𐑐𐑮𐑦𐑐𐑺𐑛 𐑑 𐑛𐑮𐑦𐑙𐑒. “𐑸 𐑿 𐑒𐑦𐑛𐑦𐑙 𐑥𐑰? 𐑞𐑨𐑑'𐑕 𐑰𐑝𐑩𐑯 𐑢𐑻𐑕 𐑞𐑨𐑯 ·𐑥𐑳𐑜𐑩𐑤 𐑡𐑻𐑯𐑩𐑤𐑦𐑟𐑩𐑥, 𐑢𐑦𐑗 𐑲 𐑢𐑫𐑛 𐑣𐑨𐑝 𐑔𐑷𐑑 𐑢𐑪𐑟 𐑓𐑦𐑟𐑦𐑒𐑤𐑦 𐑦𐑥𐑐𐑪𐑕𐑩𐑚𐑩𐑤.”

·𐑛𐑮𐑱𐑒𐑴 𐑕𐑯𐑸𐑤𐑛. “𐑖𐑰 𐑣𐑨𐑟 𐑕𐑳𐑥 𐑕𐑹𐑑 𐑝 𐑐𐑼𐑝𐑻𐑕 𐑩𐑚𐑕𐑧𐑖𐑩𐑯 𐑩𐑚𐑬𐑑 𐑞 ·𐑥𐑨𐑤𐑓𐑶𐑟, 𐑑𐑵, 𐑯 𐑣𐑻 𐑓𐑭𐑞𐑼 𐑦𐑟 𐑐𐑪𐑤𐑦𐑑𐑦𐑒𐑤𐑦 𐑩𐑐𐑴𐑟𐑛 𐑑 𐑳𐑕 𐑕𐑴 𐑣𐑰 𐑐𐑮𐑦𐑯𐑑𐑕 𐑧𐑝𐑮𐑦 𐑢𐑻𐑛. 𐑨𐑟 𐑕𐑵𐑯 𐑨𐑟 𐑲'𐑥 𐑴𐑤𐑛 𐑦𐑯𐑳𐑓 𐑲'𐑥 𐑜𐑴𐑦𐑙 𐑑 𐑮𐑱𐑐 𐑣𐑻.”

𐑜𐑮𐑰𐑯 𐑤𐑦𐑒𐑢𐑦𐑛 𐑕𐑐𐑻𐑑𐑩𐑛 𐑬𐑑 𐑝 ·𐑣𐑨𐑮𐑦'𐑟 𐑯𐑪𐑕𐑑𐑮𐑩𐑤𐑟, 𐑕𐑴𐑒𐑦𐑙 𐑦𐑯𐑑𐑵 𐑞 𐑕𐑒𐑸𐑓 𐑕𐑑𐑦𐑤 𐑒𐑳𐑝𐑼𐑦𐑙 𐑞𐑨𐑑 𐑺𐑾. ·𐑒𐑳𐑥𐑛-·𐑑𐑰 𐑯 𐑤𐑳𐑙𐑟 𐑛𐑦𐑛 𐑯𐑪𐑑 𐑥𐑦𐑒𐑕, 𐑯 ·𐑣𐑨𐑮𐑦 𐑕𐑐𐑧𐑯𐑑 𐑞 𐑯𐑧𐑒𐑕𐑑 𐑓𐑿 𐑕𐑱𐑒𐑪𐑯𐑛𐑟 𐑓𐑮𐑨𐑯𐑑𐑦𐑒𐑤𐑦 𐑒𐑪𐑓𐑦𐑙.

·𐑛𐑮𐑱𐑒𐑴 𐑤𐑫𐑒𐑑 𐑨𐑑 𐑣𐑦𐑥 𐑖𐑸𐑐𐑤𐑦. “𐑕𐑳𐑥𐑔𐑦𐑙 𐑮𐑪𐑙?”

𐑦𐑑 𐑢𐑪𐑟 𐑨𐑑 𐑞𐑦𐑕 𐑐𐑶𐑯𐑑 𐑞𐑨𐑑 ·𐑣𐑨𐑮𐑦 𐑒𐑱𐑥 𐑑 𐑞 𐑕𐑳𐑛𐑩𐑯 𐑮𐑾𐑤𐑲𐑟𐑱𐑖𐑩𐑯 𐑞𐑨𐑑 (𐑩)~𐑞 𐑕𐑬𐑯𐑛𐑟 𐑒𐑳𐑥𐑦𐑙 𐑓𐑮𐑪𐑥 𐑞 𐑮𐑧𐑕𐑑 𐑝 𐑞 𐑑𐑮𐑱𐑯 𐑐𐑤𐑨𐑑𐑓𐑹𐑥 𐑣𐑨𐑛 𐑑𐑻𐑯𐑛 𐑦𐑯𐑑𐑵 𐑥𐑹 𐑝 𐑩 𐑚𐑤𐑻𐑛 𐑢𐑲𐑑 𐑯𐑶𐑟 𐑨𐑑 𐑼𐑬𐑯𐑛 𐑞 𐑕𐑱𐑥 𐑑𐑲𐑥 ·𐑛𐑮𐑱𐑒𐑴 𐑣𐑨𐑛 𐑮𐑰𐑗𐑑 𐑦𐑯𐑕𐑲𐑛 𐑣𐑦𐑟 𐑮𐑴𐑚𐑟, 𐑯 (𐑚)~𐑢𐑧𐑯 𐑣𐑰 𐑣𐑨𐑛 𐑛𐑦𐑕𐑒𐑳𐑕𐑑 𐑒𐑩𐑥𐑦𐑑𐑦𐑙 𐑥𐑻𐑛𐑼 𐑨𐑟 𐑩 𐑚𐑪𐑯𐑛𐑦𐑙 𐑥𐑧𐑔𐑩𐑛, 𐑞𐑺 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦 𐑢𐑳𐑯 𐑐𐑻𐑕𐑩𐑯 𐑦𐑯 𐑞 𐑒𐑪𐑯𐑝𐑼𐑕𐑱𐑖𐑩𐑯 𐑣𐑵'𐑛 𐑔𐑷𐑑 𐑞𐑱 𐑢𐑻 𐑡𐑴𐑒𐑦𐑙.

\emph{𐑮𐑲𐑑. 𐑚𐑦𐑒𐑪𐑟 𐑣𐑰 \emph{𐑕𐑰𐑥𐑛} 𐑤𐑲𐑒 𐑕𐑳𐑗 𐑩 𐑯𐑹𐑥𐑩𐑤 𐑒𐑦𐑛. 𐑯 𐑣𐑰 \emph{𐑦𐑟} 𐑩 𐑯𐑹𐑥𐑩𐑤 𐑒𐑦𐑛, 𐑣𐑰 𐑦𐑟 𐑡𐑳𐑕𐑑 𐑢𐑪𐑑 𐑿'𐑛 \emph{𐑦𐑒𐑕𐑐𐑧𐑒𐑑} 𐑩 𐑚𐑱𐑕𐑤𐑲𐑯 𐑥𐑱𐑤 𐑗𐑲𐑤𐑛 𐑑 𐑚𐑰 𐑤𐑲𐑒 𐑦𐑓 ·𐑛𐑸𐑔 ·𐑝𐑱𐑛𐑼 𐑢𐑻 𐑣𐑦𐑟 𐑛𐑴𐑑𐑦𐑙 𐑓𐑭𐑞𐑼.}
                            
“𐑘𐑧𐑕, 𐑢𐑧𐑤,” ·𐑣𐑨𐑮𐑦 𐑒𐑪𐑓𐑑, 𐑴 𐑜𐑪𐑛 𐑣𐑬 𐑢𐑪𐑟 𐑣𐑰 𐑜𐑴𐑦𐑙 𐑑 𐑜𐑧𐑑 𐑬𐑑 𐑝 𐑞𐑦𐑕 𐑒𐑪𐑯𐑝𐑼𐑕𐑱𐑖𐑩𐑯𐑩𐑤 𐑢𐑧𐑡, “𐑲 𐑢𐑪𐑟 𐑡𐑳𐑕𐑑 𐑕𐑼𐑐𐑮𐑲𐑟𐑛 𐑨𐑑 𐑣𐑬 𐑿 𐑢𐑻 𐑢𐑦𐑤𐑦𐑙 𐑑 𐑛𐑦𐑕𐑒𐑳𐑕 𐑦𐑑 𐑕𐑴 𐑴𐑐𐑩𐑯𐑤𐑦, 𐑿 𐑛𐑦𐑛𐑩𐑯𐑑 𐑕𐑰𐑥 𐑢𐑳𐑮𐑦𐑛 𐑩𐑚𐑬𐑑 𐑜𐑧𐑑𐑦𐑙 𐑒𐑷𐑑 𐑹 𐑧𐑯𐑦𐑔𐑦𐑙.”

·𐑛𐑮𐑱𐑒𐑴 𐑕𐑯𐑹𐑑𐑩𐑛. “𐑸 𐑿 𐑡𐑴𐑒𐑦𐑙? \emph{·𐑤𐑵𐑯𐑩 ·𐑤𐑳𐑝𐑜𐑫𐑛'𐑟} 𐑢𐑻𐑛 𐑩𐑜𐑱𐑯𐑕𐑑 𐑥𐑲𐑯?”

𐑣𐑴𐑤𐑦 𐑒𐑮𐑨𐑐 𐑪𐑯 𐑩 𐑣𐑴𐑤𐑦 𐑕𐑑𐑦𐑒. “𐑞𐑺'𐑟 𐑯𐑴 𐑕𐑳𐑗 𐑔𐑦𐑙 𐑨𐑟 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 𐑑𐑮𐑵𐑔 𐑛𐑦𐑑𐑧𐑒𐑖𐑩𐑯, 𐑲 𐑑𐑱𐑒 𐑦𐑑?” \emph{𐑹 DNA 𐑑𐑧𐑕𐑑𐑦𐑙…𐑘𐑧𐑑.}

·𐑛𐑮𐑱𐑒𐑴 𐑤𐑫𐑒𐑑 𐑼𐑬𐑯𐑛. 𐑣𐑦𐑟 𐑲𐑟 𐑯𐑨𐑮𐑴𐑛. “𐑞𐑨𐑑'𐑕 𐑮𐑲𐑑, 𐑿 𐑛𐑴𐑯𐑑 𐑯𐑴 𐑧𐑯𐑦𐑔𐑦𐑙. 𐑤𐑫𐑒, 𐑲'𐑤 𐑦𐑒𐑕𐑐𐑤𐑱𐑯 𐑔𐑦𐑙𐑟 𐑑 𐑿, 𐑲 𐑥𐑰𐑯 𐑞 𐑢𐑱 𐑦𐑑 𐑮𐑾𐑤𐑦 𐑢𐑻𐑒𐑕, 𐑡𐑳𐑕𐑑 𐑤𐑲𐑒 𐑿 𐑢𐑻 𐑷𐑤𐑮𐑧𐑛𐑦 𐑦𐑯 ·𐑕𐑤𐑲𐑔𐑼𐑦𐑯 𐑯 𐑭𐑕𐑒𐑑 𐑥𐑰 𐑞 𐑕𐑱𐑥 𐑒𐑢𐑧𐑕𐑗𐑩𐑯. 𐑚𐑳𐑑 𐑿'𐑝 𐑜𐑪𐑑 𐑑 𐑕𐑢𐑺 𐑯𐑪𐑑 𐑑 𐑕𐑱 𐑧𐑯𐑦𐑔𐑦𐑙 𐑩𐑚𐑬𐑑 𐑦𐑑.”

“𐑲 𐑕𐑢𐑺,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛.

“𐑞 𐑒𐑹𐑑𐑕 𐑿𐑟 ·𐑝𐑧𐑮𐑦𐑑𐑭𐑕𐑼𐑩𐑥, 𐑚𐑳𐑑 𐑦𐑑'𐑕 𐑩 𐑡𐑴𐑒 𐑮𐑾𐑤𐑦, 𐑿 𐑡𐑳𐑕𐑑 𐑜𐑧𐑑 𐑘𐑹𐑕𐑧𐑤𐑓 ·𐑩𐑚𐑤𐑦𐑝𐑦𐑱𐑑𐑩𐑛 𐑚𐑦𐑓𐑹 𐑿 𐑑𐑧𐑕𐑑𐑦𐑓𐑲 𐑯 𐑞𐑧𐑯 𐑒𐑤𐑱𐑥 𐑞 𐑳𐑞𐑼 𐑐𐑻𐑕𐑩𐑯 𐑢𐑪𐑟 ·𐑥𐑧𐑥𐑼𐑦-·𐑗𐑸𐑥𐑛 𐑢𐑦𐑞 𐑩 𐑓𐑱𐑒 𐑥𐑧𐑥𐑼𐑦. 𐑝 𐑒𐑹𐑕 𐑦𐑓 𐑿'𐑼 𐑡𐑳𐑕𐑑 𐑕𐑳𐑥 𐑯𐑹𐑥𐑩𐑤 𐑐𐑻𐑕𐑩𐑯, 𐑞 𐑒𐑹𐑑𐑕 𐑐𐑮𐑦𐑟𐑿𐑥 𐑦𐑯 𐑓𐑱𐑝𐑼 𐑝 ·𐑩𐑚𐑤𐑦𐑝𐑦𐑱𐑖𐑩𐑯, 𐑯𐑪𐑑 ·𐑓𐑷𐑤𐑕 ·𐑥𐑧𐑥𐑼𐑦 ·𐑗𐑸𐑥𐑟. 𐑚𐑳𐑑 𐑞 𐑒𐑹𐑑 𐑣𐑨𐑟 𐑛𐑦𐑕𐑒𐑮𐑧𐑖𐑩𐑯, 𐑯 𐑦𐑓 \emph{𐑲'𐑥} 𐑦𐑯𐑝𐑪𐑤𐑝𐑛 𐑞𐑧𐑯 𐑦𐑑 𐑦𐑥𐑐𐑦𐑯𐑡𐑩𐑟 𐑪𐑯 𐑞 𐑪𐑯𐑼 𐑝 𐑩 ·𐑯𐑴𐑚𐑩𐑤 ·𐑣𐑬𐑕, 𐑕𐑴 𐑦𐑑 𐑜𐑴𐑟 𐑑 𐑞 ·𐑢𐑦𐑟𐑩𐑯𐑜𐑱𐑥𐑪𐑑, 𐑢𐑺 ·𐑓𐑭𐑞𐑼 𐑣𐑨𐑟 𐑞 𐑝𐑴𐑑𐑕. 𐑭𐑓𐑑𐑼 𐑲'𐑥 𐑓𐑬𐑯𐑛 𐑯𐑪𐑑 𐑜𐑦𐑤𐑑𐑦 𐑞 ·𐑤𐑳𐑝𐑜𐑫𐑛 𐑓𐑨𐑥𐑤𐑦 𐑣𐑨𐑕 𐑑 𐑐𐑱 𐑮𐑧𐑐𐑼𐑱𐑖𐑩𐑯𐑟 𐑓 𐑑𐑸𐑯𐑦𐑖𐑦𐑙 𐑥𐑲 𐑪𐑯𐑼. 𐑯 𐑞𐑱 𐑯𐑴 𐑓𐑮𐑪𐑥 𐑞 𐑕𐑑𐑸𐑑 𐑞𐑨𐑑'𐑕 𐑣𐑬 𐑦𐑑'𐑤 𐑜𐑴, 𐑕𐑴 𐑞𐑱'𐑤 𐑡𐑳𐑕𐑑 𐑒𐑰𐑐 𐑞𐑺 𐑥𐑬𐑞𐑟 𐑖𐑳𐑑.”

𐑩 𐑒𐑴𐑤𐑛 𐑗𐑦𐑤 𐑢𐑪𐑟 𐑒𐑳𐑥𐑦𐑙 𐑴𐑝𐑼 ·𐑣𐑨𐑮𐑦, 𐑩 𐑗𐑦𐑤 𐑞𐑨𐑑 𐑒𐑱𐑥 𐑢𐑦𐑞 𐑦𐑯𐑕𐑑𐑮𐑳𐑒𐑖𐑩𐑯𐑟 𐑑 𐑒𐑰𐑐 𐑣𐑦𐑟 𐑝𐑶𐑕 𐑯 𐑓𐑱𐑕 𐑯𐑹𐑥𐑩𐑤. \emph{𐑯𐑴𐑑 𐑑 𐑕𐑧𐑤𐑓: 𐑴𐑝𐑼𐑔𐑮𐑴 𐑜𐑳𐑝𐑼𐑯𐑥𐑩𐑯𐑑 𐑝 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 ·𐑚𐑮𐑦𐑑𐑩𐑯 𐑨𐑑 𐑻𐑤𐑾𐑕𐑑 𐑒𐑩𐑯𐑝𐑰𐑯𐑾𐑯𐑕.}

·𐑣𐑨𐑮𐑦 𐑒𐑪𐑓𐑑 𐑩𐑜𐑱𐑯 𐑑 𐑒𐑤𐑽 𐑣𐑦𐑟 𐑔𐑮𐑴𐑑. “·𐑛𐑮𐑱𐑒𐑴, 𐑐𐑤𐑰𐑟 𐑐𐑤𐑰𐑟 \emph{𐑐𐑤𐑰𐑟} 𐑛𐑴𐑯𐑑 𐑑𐑱𐑒 𐑞𐑦𐑕 𐑞 𐑮𐑪𐑙 𐑢𐑱, 𐑥𐑲 𐑢𐑻𐑛 𐑦𐑟 𐑥𐑲 𐑚𐑪𐑯𐑛, 𐑚𐑳𐑑 𐑤𐑲𐑒 𐑿 𐑕𐑧𐑛 𐑲 𐑒𐑫𐑛 𐑚𐑰 𐑦𐑯 ·𐑕𐑤𐑲𐑔𐑼𐑦𐑯 𐑯 𐑲 𐑮𐑾𐑤𐑦 𐑢𐑪𐑯𐑑 𐑑 𐑭𐑕𐑒 𐑓 𐑦𐑯𐑓𐑼𐑥𐑱𐑖𐑩𐑯𐑩𐑤 𐑐𐑻𐑐𐑩𐑕𐑩𐑟, 𐑕𐑴 𐑢𐑪𐑑 𐑢𐑫𐑛 𐑣𐑨𐑐𐑩𐑯 \emph{𐑔𐑽𐑧𐑑𐑦𐑒𐑤𐑦 𐑕𐑐𐑰𐑒𐑦𐑙} 𐑦𐑓 𐑲 \emph{𐑛𐑦𐑛} 𐑑𐑧𐑕𐑑𐑦𐑓𐑲 𐑞𐑨𐑑 𐑲'𐑛 𐑣𐑻𐑛 𐑿 𐑐𐑤𐑨𐑯 𐑦𐑑?”

“𐑞𐑧𐑯 𐑦𐑓 𐑲 𐑢𐑪𐑟 𐑧𐑯𐑦𐑢𐑳𐑯 𐑳𐑞𐑼 𐑞𐑨𐑯 𐑩 ·𐑥𐑨𐑤𐑓𐑶, 𐑲'𐑛 𐑚𐑰 𐑦𐑯 𐑑𐑮𐑳𐑚𐑩𐑤,” ·𐑛𐑮𐑱𐑒𐑴 𐑭𐑯𐑕𐑼𐑛 𐑕𐑥𐑳𐑜𐑤𐑦. “𐑕𐑦𐑯𐑕 𐑲 \emph{𐑨𐑥} 𐑩 ·𐑥𐑨𐑤𐑓𐑶…·𐑓𐑭𐑞𐑼 𐑣𐑨𐑟 𐑞 𐑝𐑴𐑑𐑕. 𐑯 𐑭𐑓𐑑𐑼𐑢𐑼𐑛𐑟 𐑣𐑰'𐑛 𐑒𐑮𐑳𐑖 𐑿…𐑢𐑧𐑤, 𐑲 𐑜𐑧𐑕 𐑯𐑪𐑑 𐑰𐑟𐑦𐑤𐑦, 𐑕𐑦𐑯𐑕 𐑿 \emph{𐑸} 𐑞 ·𐑚𐑶-𐑣𐑵-·𐑤𐑦𐑝𐑛, 𐑚𐑳𐑑 ·𐑓𐑭𐑞𐑼 𐑦𐑟 𐑐𐑮𐑦𐑑𐑦 𐑜𐑫𐑛 𐑨𐑑 𐑞𐑨𐑑 𐑕𐑹𐑑 𐑝 𐑔𐑦𐑙.” ·𐑛𐑮𐑱𐑒𐑴 𐑓𐑮𐑬𐑯𐑛. “'·𐑕𐑲𐑛𐑟, \emph{𐑿} 𐑑𐑷𐑒𐑑 𐑩𐑚𐑬𐑑 𐑥𐑻𐑛𐑼𐑦𐑙 𐑣𐑻, 𐑢𐑲 𐑢𐑻𐑯𐑑 𐑿 𐑢𐑳𐑮𐑦𐑛 𐑩𐑚𐑬𐑑 \emph{𐑥𐑰} 𐑑𐑧𐑕𐑑𐑦𐑓𐑲𐑦𐑙 𐑭𐑓𐑑𐑼 𐑖𐑰 𐑑𐑻𐑯𐑟 𐑳𐑐 𐑛𐑧𐑛?”

\emph{𐑣𐑬, 𐑴 𐑣𐑬 𐑛𐑦𐑛 𐑥𐑲 𐑛𐑱 𐑜𐑴 𐑞𐑦𐑕 𐑮𐑪𐑙?} 𐑣𐑨𐑮𐑦'𐑟 𐑥𐑬𐑔 𐑢𐑪𐑟 𐑷𐑤𐑮𐑧𐑛𐑦 𐑥𐑵𐑝𐑦𐑙 𐑓𐑭𐑕𐑑𐑼 𐑞𐑨𐑯 𐑣𐑰 𐑒𐑫𐑛 𐑔𐑦𐑙𐑒. “𐑞𐑨𐑑'𐑕 𐑢𐑧𐑯 𐑲 𐑔𐑷𐑑 𐑖𐑰 𐑢𐑪𐑟 \emph{𐑴𐑤𐑛𐑼}! 𐑲 𐑛𐑴𐑯𐑑 𐑯𐑴 𐑣𐑬 𐑦𐑑 𐑢𐑻𐑒𐑕 \emph{𐑣𐑽}, 𐑚𐑳𐑑 𐑦𐑯 ·𐑥𐑳𐑜𐑩𐑤 ·𐑚𐑮𐑦𐑑𐑩𐑯 𐑞 𐑒𐑹𐑑𐑕 𐑢𐑫𐑛 𐑜𐑧𐑑 𐑩 𐑤𐑪𐑑 𐑥𐑹 𐑳𐑐𐑕𐑧𐑑 𐑩𐑚𐑬𐑑 𐑕𐑳𐑥𐑢𐑳𐑯 𐑒𐑦𐑤𐑦𐑙 𐑩 𐑗𐑲𐑤𐑛—”

“𐑞𐑨𐑑 𐑥𐑱𐑒𐑕 𐑕𐑧𐑯𐑕,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛, 𐑕𐑑𐑦𐑤 𐑤𐑫𐑒𐑦𐑙 𐑩 𐑚𐑦𐑑 𐑕𐑩𐑕𐑐𐑦𐑖𐑩𐑕. “𐑚𐑳𐑑 𐑧𐑯𐑦𐑢𐑱, 𐑦𐑑'𐑕 𐑷𐑤𐑢𐑱𐑟 𐑕𐑥𐑸𐑑𐑼 𐑦𐑓 𐑦𐑑 𐑛𐑳𐑟𐑩𐑯𐑑 𐑜𐑴 𐑑 𐑞 ·𐑹𐑹𐑟 𐑨𐑑 𐑷𐑤. 𐑦𐑓 𐑢𐑰'𐑼 𐑒𐑺𐑓𐑩𐑤 𐑴𐑯𐑤𐑦 𐑑 𐑛𐑵 𐑔𐑦𐑙𐑟 𐑞𐑨𐑑 ·𐑣𐑰𐑤𐑦𐑙 ·𐑗𐑸𐑥𐑟 𐑒𐑨𐑯 𐑓𐑦𐑒𐑕, 𐑢𐑰 𐑒𐑨𐑯 𐑡𐑳𐑕𐑑 ·𐑩𐑚𐑤𐑦𐑝𐑦𐑱𐑑 𐑣𐑻 𐑭𐑓𐑑𐑼𐑢𐑼𐑛𐑟 𐑯 𐑞𐑧𐑯 𐑛𐑵 𐑦𐑑 𐑷𐑤 𐑩𐑜𐑱𐑯 𐑯𐑧𐑒𐑕𐑑 𐑢𐑰𐑒.” 𐑞𐑧𐑯 𐑞 𐑚𐑤𐑪𐑯𐑛-𐑣𐑺𐑛 𐑚𐑶 𐑜𐑦𐑜𐑩𐑤𐑛, 𐑩 𐑿𐑔𐑓𐑩𐑤 𐑣𐑲-𐑐𐑦𐑗𐑑 𐑕𐑬𐑯𐑛. “𐑞𐑴 𐑡𐑳𐑕𐑑 𐑦𐑥𐑨𐑡𐑦𐑯 𐑣𐑻 𐑕𐑱𐑦𐑙 𐑖𐑰'𐑛 𐑚𐑰𐑯 𐑛𐑳𐑯 𐑚𐑲 ·𐑛𐑮𐑱𐑒𐑴 ·𐑥𐑨𐑤𐑓𐑶 \emph{𐑯} 𐑞 ·𐑚𐑶-𐑣𐑵-·𐑤𐑦𐑝𐑛, 𐑯𐑪𐑑 𐑰𐑝𐑩𐑯 \emph{·𐑛𐑳𐑥𐑚𐑩𐑤𐑛𐑹} 𐑢𐑫𐑛 𐑚𐑦𐑤𐑰𐑝 𐑣𐑻.”

\emph{𐑲 𐑨𐑥 𐑜𐑴𐑦𐑙 𐑑 𐑑𐑺 𐑩𐑐𐑸𐑑 𐑘𐑹 𐑐𐑩𐑔𐑧𐑑𐑦𐑒 𐑤𐑦𐑑𐑩𐑤 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 𐑮𐑧𐑥𐑯𐑩𐑯𐑑 𐑝 𐑞 ·𐑛𐑸𐑒 ·𐑱𐑡𐑩𐑟 𐑦𐑯𐑑𐑵 𐑐𐑰𐑕𐑩𐑟 𐑕𐑥𐑷𐑤𐑼 𐑞𐑨𐑯 𐑦𐑑𐑕 𐑒𐑩𐑯𐑕𐑑𐑦𐑗𐑵𐑩𐑯𐑑 𐑨𐑑𐑩𐑥𐑟.} “𐑨𐑒𐑗𐑵𐑩𐑤𐑦, 𐑒𐑨𐑯 𐑢𐑰 𐑣𐑴𐑤𐑛 𐑪𐑓 𐑪𐑯 𐑞𐑨𐑑? 𐑭𐑓𐑑𐑼 𐑲 𐑓𐑬𐑯𐑛 𐑬𐑑 𐑞𐑨𐑑 𐑣𐑧𐑛𐑤𐑲𐑯 𐑒𐑱𐑥 𐑓𐑮𐑪𐑥 𐑩 𐑜𐑻𐑤 𐑩 𐑘𐑽 𐑘𐑳𐑙𐑜𐑼 𐑞𐑨𐑯 𐑥𐑰, 𐑲 𐑣𐑨𐑛 𐑩 𐑛𐑦𐑓𐑼𐑩𐑯𐑑 𐑔𐑷𐑑 𐑓 𐑥𐑲 𐑮𐑦𐑝𐑧𐑯𐑡.”

“𐑣𐑳? 𐑛𐑵 𐑑𐑧𐑤,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛, 𐑯 𐑕𐑑𐑸𐑑𐑩𐑛 𐑑 𐑑𐑱𐑒 𐑩𐑯𐑳𐑞𐑼 𐑕𐑢𐑦𐑜 𐑝 𐑣𐑦𐑟 ·𐑒𐑳𐑥𐑛-·𐑑𐑰.

·𐑣𐑨𐑮𐑦 𐑛𐑦𐑛𐑩𐑯𐑑 𐑯𐑴 𐑦𐑓 𐑞 𐑦𐑯𐑗𐑭𐑯𐑑𐑥𐑩𐑯𐑑 𐑢𐑻𐑒𐑑 𐑥𐑹 𐑞𐑨𐑯 𐑢𐑳𐑯𐑕 𐑐𐑻 𐑒𐑨𐑯, 𐑚𐑳𐑑 𐑣𐑰 \emph{𐑛𐑦𐑛} 𐑯𐑴 𐑣𐑰 𐑒𐑫𐑛 𐑩𐑝𐑶𐑛 𐑞 𐑚𐑤𐑱𐑥, 𐑕𐑴 𐑣𐑰 𐑢𐑪𐑟 𐑒𐑺𐑓𐑩𐑤 𐑑 𐑑𐑲𐑥 𐑦𐑑 𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦 𐑮𐑲𐑑:

“𐑲 𐑢𐑪𐑟 𐑔𐑦𐑙𐑒𐑦𐑙 \emph{𐑕𐑳𐑥 𐑛𐑱 𐑲'𐑥 𐑜𐑴𐑦𐑙 𐑑 𐑥𐑨𐑮𐑦 𐑞𐑨𐑑 𐑢𐑫𐑥𐑩𐑯.}”

·𐑛𐑮𐑱𐑒𐑴 𐑥𐑱𐑛 𐑩 𐑣𐑪𐑮𐑦𐑛 𐑒𐑻-𐑕𐑐𐑤𐑵𐑗𐑦𐑙 𐑕𐑬𐑯𐑛 𐑯 𐑤𐑰𐑒𐑑 𐑜𐑮𐑰𐑯 𐑓𐑤𐑵𐑦𐑛 𐑬𐑑 𐑞 𐑒𐑹𐑯𐑼𐑟 𐑝 𐑣𐑦𐑟 𐑥𐑬𐑔 𐑤𐑲𐑒 𐑩 𐑚𐑮𐑴𐑒𐑩𐑯 𐑒𐑸 𐑮𐑱𐑛𐑦𐑱𐑑𐑼. “\emph{𐑸 𐑿 𐑯𐑳𐑑𐑕?}”

“𐑒𐑢𐑲𐑑 𐑞 𐑪𐑐𐑩𐑟𐑦𐑑, 𐑲'𐑥 𐑕𐑴 𐑕𐑱𐑯 𐑦𐑑 𐑚𐑻𐑯𐑟 𐑤𐑲𐑒 𐑲𐑕.”

“𐑿'𐑝 𐑜𐑪𐑑 𐑢𐑽𐑛𐑼 𐑑𐑱𐑕𐑑 𐑞𐑨𐑯 𐑩 ·𐑤𐑧𐑕𐑑𐑮𐑱𐑯𐑡,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛, 𐑕𐑬𐑯𐑛𐑦𐑙 𐑣𐑭𐑓-𐑩𐑛𐑥𐑲𐑼𐑦𐑙 𐑩𐑚𐑬𐑑 𐑦𐑑. “𐑯 𐑲 𐑕𐑩𐑐𐑴𐑟 𐑿 𐑢𐑪𐑯𐑑 𐑣𐑻 𐑷𐑤 𐑑 𐑘𐑹𐑕𐑧𐑤𐑓, 𐑣𐑳?”

“𐑘𐑧𐑐. 𐑲 𐑒𐑨𐑯 𐑴 𐑿 𐑩 𐑓𐑱𐑝𐑼 𐑓 𐑦𐑑—”

·𐑛𐑮𐑱𐑒𐑴 𐑢𐑱𐑝𐑛 𐑦𐑑 𐑪𐑓. “𐑯𐑭, 𐑞𐑦𐑕 𐑢𐑳𐑯'𐑟 𐑓𐑮𐑰.”

·𐑣𐑨𐑮𐑦 𐑕𐑑𐑺𐑛 𐑛𐑬𐑯 𐑨𐑑 𐑞 𐑒𐑨𐑯 𐑦𐑯 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛, 𐑞 𐑒𐑴𐑤𐑛𐑯𐑩𐑕 𐑕𐑧𐑑𐑩𐑤𐑦𐑙 𐑦𐑯𐑑𐑵 𐑣𐑦𐑟 𐑚𐑤𐑳𐑛. 𐑗𐑸𐑥𐑦𐑙, 𐑣𐑨𐑐𐑦, 𐑡𐑧𐑯𐑼𐑩𐑕 𐑢𐑦𐑞 𐑣𐑦𐑟 𐑓𐑱𐑝𐑼𐑟 𐑑 𐑣𐑦𐑟 𐑓𐑮𐑧𐑯𐑛𐑟, ·𐑛𐑮𐑱𐑒𐑴 𐑢𐑪𐑟𐑩𐑯𐑑 𐑩 𐑕𐑲𐑒𐑴𐑐𐑨𐑔. 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑞 𐑕𐑨𐑛 𐑯 𐑷𐑓𐑩𐑤 𐑐𐑸𐑑, 𐑯𐑴𐑦𐑙 𐑣𐑿𐑥𐑩𐑯 𐑕𐑲𐑒𐑪𐑤𐑩𐑡𐑦 𐑢𐑧𐑤 𐑦𐑯𐑳𐑓 𐑑 \emph{𐑯𐑴} 𐑞𐑨𐑑 ·𐑛𐑮𐑱𐑒𐑴 \emph{𐑢𐑪𐑟𐑩𐑯𐑑} 𐑩 𐑥𐑪𐑯𐑕𐑑𐑼. 𐑞𐑺 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑑𐑧𐑯 𐑔𐑬𐑟𐑩𐑯𐑛 𐑕𐑩𐑕𐑲𐑩𐑑𐑦𐑟 𐑴𐑝𐑼 𐑞 𐑣𐑦𐑕𐑑𐑼𐑦 𐑝 𐑞 𐑢𐑻𐑤𐑛 𐑢𐑺 𐑞𐑦𐑕 𐑒𐑪𐑯𐑝𐑼𐑕𐑱𐑖𐑩𐑯 𐑒𐑫𐑛 𐑣𐑨𐑝 𐑣𐑨𐑐𐑩𐑯𐑛. 𐑯𐑴, 𐑞 𐑢𐑻𐑤𐑛 𐑢𐑫𐑛 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑩 𐑝𐑧𐑮𐑦 𐑛𐑦𐑓𐑼𐑩𐑯𐑑 𐑐𐑤𐑱𐑕 𐑦𐑯𐑛𐑰𐑛, 𐑦𐑓 𐑦𐑑 𐑑𐑫𐑒 𐑩𐑯 \emph{𐑰𐑝𐑩𐑤 𐑥𐑿𐑑𐑩𐑯𐑑} 𐑑 𐑕𐑱 𐑢𐑪𐑑 ·𐑛𐑮𐑱𐑒𐑴 𐑣𐑨𐑛 𐑕𐑧𐑛. 𐑦𐑑 𐑢𐑪𐑟 𐑝𐑧𐑮𐑦 𐑕𐑦𐑥𐑐𐑩𐑤, 𐑝𐑧𐑮𐑦 𐑣𐑿𐑥𐑩𐑯, 𐑦𐑑 𐑢𐑪𐑟 𐑞 𐑛𐑦𐑓𐑷𐑤𐑑 𐑦𐑓 𐑯𐑳𐑔𐑦𐑙 𐑧𐑤𐑕 𐑦𐑯𐑑𐑼𐑝𐑰𐑯𐑛. 𐑑 ·𐑛𐑮𐑱𐑒𐑴, 𐑣𐑦𐑟 𐑧𐑯𐑩𐑥𐑦𐑟 𐑢𐑻𐑯𐑑 𐑐𐑰𐑐𐑩𐑤.

𐑯 𐑦𐑯 𐑞 𐑕𐑤𐑴𐑛 𐑑𐑲𐑥 𐑝 𐑞𐑦𐑕 𐑕𐑤𐑴𐑛 𐑒𐑳𐑯𐑑𐑮𐑦, 𐑣𐑽 𐑯 𐑯𐑬 𐑨𐑟 𐑦𐑯 𐑞 𐑛𐑸𐑒𐑯𐑩𐑕-𐑚𐑦𐑓𐑹-𐑛𐑷𐑯 𐑐𐑮𐑲𐑼 𐑑 𐑞 ·𐑱𐑡 𐑝 ·𐑮𐑰𐑟𐑩𐑯, 𐑞 𐑕𐑳𐑯 𐑝 𐑩 𐑕𐑩𐑓𐑦𐑖𐑩𐑯𐑑𐑤𐑦 𐑐𐑬𐑼𐑓𐑩𐑤 𐑯𐑴𐑚𐑩𐑤 𐑢𐑫𐑛 𐑕𐑦𐑥𐑐𐑤𐑦 𐑑𐑱𐑒 𐑓 𐑜𐑮𐑭𐑯𐑑𐑩𐑛 𐑞𐑨𐑑 𐑣𐑰 𐑢𐑪𐑟 𐑩𐑚𐑳𐑝 𐑞 𐑤𐑷, 𐑨𐑑 𐑤𐑰𐑕𐑑 𐑢𐑧𐑯 𐑦𐑑 𐑒𐑱𐑥 𐑑 𐑕𐑳𐑥 𐑐𐑧𐑟𐑩𐑯𐑑 𐑜𐑻𐑤. 𐑞𐑺 𐑢𐑻 𐑐𐑤𐑱𐑕𐑩𐑟 𐑦𐑯 ·𐑥𐑳𐑜𐑩𐑤-𐑤𐑨𐑯𐑛 𐑢𐑺 𐑦𐑑 𐑢𐑪𐑟 𐑕𐑑𐑦𐑤 𐑞 𐑕𐑱𐑥 𐑢𐑱, 𐑒𐑳𐑯𐑑𐑮𐑦𐑟 𐑢𐑺 𐑞𐑨𐑑 𐑕𐑹𐑑 𐑝 𐑯𐑴𐑚𐑦𐑤𐑦𐑑𐑦 𐑕𐑑𐑦𐑤 𐑦𐑜𐑟𐑦𐑕𐑑𐑩𐑛 𐑯 𐑕𐑑𐑦𐑤 𐑔𐑷𐑑 𐑤𐑲𐑒 𐑞𐑨𐑑, 𐑹 𐑰𐑝𐑩𐑯 𐑜𐑮𐑦𐑥𐑼 𐑤𐑨𐑯𐑛𐑟 𐑢𐑺 𐑦𐑑 𐑢𐑪𐑟𐑩𐑯𐑑 𐑡𐑳𐑕𐑑 𐑞 𐑯𐑴𐑚𐑦𐑤𐑦𐑑𐑦. 𐑦𐑑 𐑢𐑪𐑟 𐑤𐑲𐑒 𐑞𐑨𐑑 𐑦𐑯 𐑧𐑝𐑮𐑦 𐑐𐑤𐑱𐑕 𐑯 𐑑𐑲𐑥 𐑞𐑨𐑑 𐑛𐑦𐑛𐑩𐑯𐑑 𐑛𐑦𐑕𐑧𐑯𐑛 𐑛𐑦𐑮𐑧𐑒𐑑𐑤𐑦 𐑓𐑮𐑪𐑥 𐑞 ·𐑦𐑯𐑤𐑲𐑑𐑩𐑯𐑥𐑩𐑯𐑑. 𐑩 𐑤𐑲𐑯 𐑝 𐑛𐑦𐑕𐑧𐑯𐑑, 𐑦𐑑 𐑕𐑰𐑥𐑛, 𐑢𐑦𐑗 𐑛𐑦𐑛𐑩𐑯𐑑 𐑒𐑢𐑲𐑑 𐑦𐑯𐑒𐑤𐑵𐑛 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 ·𐑚𐑮𐑦𐑑𐑩𐑯, 𐑓 𐑷𐑤 𐑞𐑨𐑑 𐑞𐑺 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑒𐑮𐑪𐑕-𐑒𐑳𐑤𐑗𐑼𐑩𐑤 𐑒𐑩𐑯𐑑𐑨𐑥𐑦𐑯𐑱𐑖𐑩𐑯 𐑝 𐑔𐑦𐑙𐑟 𐑤𐑲𐑒 𐑮𐑦𐑙-𐑐𐑫𐑤 𐑛𐑮𐑦𐑙𐑒𐑕 𐑒𐑨𐑯𐑟.

\emph{𐑯 𐑦𐑓 ·𐑛𐑮𐑱𐑒𐑴 𐑛𐑳𐑟𐑩𐑯𐑑 𐑗𐑱𐑯𐑡 𐑣𐑦𐑟 𐑥𐑲𐑯𐑛 𐑩𐑚𐑬𐑑 𐑢𐑪𐑯𐑑𐑦𐑙 𐑮𐑦𐑝𐑧𐑯𐑡, 𐑯 𐑲 𐑛𐑴𐑯𐑑 𐑔𐑮𐑴 𐑩𐑢𐑱 𐑥𐑲 𐑴𐑯 𐑗𐑭𐑯𐑕 𐑨𐑑 𐑣𐑨𐑐𐑦𐑯𐑩𐑕 𐑦𐑯 𐑤𐑲𐑓 𐑑 𐑥𐑨𐑮𐑦 𐑕𐑳𐑥 𐑐𐑫𐑼 𐑒𐑮𐑱𐑟𐑦 𐑜𐑻𐑤, 𐑞𐑧𐑯 𐑷𐑤 𐑲'𐑝 𐑡𐑳𐑕𐑑 𐑚𐑷𐑑 𐑦𐑟 𐑑𐑲𐑥, 𐑯 𐑯𐑪𐑑 𐑑𐑵 𐑥𐑳𐑗 𐑝 𐑦𐑑…}

𐑓 𐑢𐑳𐑯 𐑜𐑻𐑤. 𐑯𐑪𐑑 𐑓 𐑳𐑞𐑼𐑟.

\emph{𐑲 𐑢𐑳𐑯𐑛𐑼 𐑣𐑬 𐑛𐑦𐑓𐑦𐑒𐑳𐑤𐑑 𐑦𐑑 𐑢𐑫𐑛 𐑚𐑰 𐑑 𐑡𐑳𐑕𐑑 𐑥𐑱𐑒 𐑩 𐑤𐑦𐑕𐑑 𐑝 𐑷𐑤 𐑞 𐑑𐑪𐑐 𐑚𐑤𐑳𐑛 𐑐𐑘𐑫𐑼𐑦𐑕𐑑𐑕 𐑯 𐑒𐑦𐑤 𐑞𐑧𐑥.}

𐑞𐑱'𐑛 𐑑𐑮𐑲𐑛 𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦 𐑞𐑨𐑑 𐑛𐑘𐑫𐑼𐑦𐑙 𐑞 ·𐑓𐑮𐑧𐑯𐑗 ·𐑮𐑧𐑝𐑩𐑤𐑵𐑖𐑩𐑯, 𐑥𐑹 𐑹 𐑤𐑧𐑕—𐑥𐑱𐑒 𐑩 𐑤𐑦𐑕𐑑 𐑝 𐑷𐑤 𐑞 𐑧𐑯𐑩𐑥𐑦𐑟 𐑝 ·𐑐𐑮𐑴𐑜𐑮𐑧𐑕 𐑯 𐑮𐑦𐑥𐑵𐑝 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑩𐑚𐑳𐑝 𐑞 𐑯𐑧𐑒—𐑯 𐑦𐑑 𐑣𐑨𐑛𐑩𐑯𐑑 𐑢𐑻𐑒𐑑 𐑬𐑑 𐑢𐑧𐑤 𐑓𐑮𐑪𐑥 𐑢𐑪𐑑 ·𐑣𐑨𐑮𐑦 𐑮𐑦𐑒𐑷𐑤𐑛. 𐑥𐑱𐑚𐑰 𐑣𐑰 𐑯𐑰𐑛𐑩𐑛 𐑑 𐑛𐑳𐑕𐑑 𐑪𐑓 𐑕𐑳𐑥 𐑝 𐑞𐑴𐑟 𐑣𐑦𐑕𐑑𐑼𐑦 𐑚𐑫𐑒𐑕 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑣𐑨𐑛 𐑚𐑷𐑑 𐑣𐑦𐑥, 𐑯 𐑕𐑰 𐑦𐑓 𐑢𐑪𐑑 𐑣𐑨𐑛 𐑜𐑪𐑯 𐑮𐑪𐑙 𐑢𐑦𐑞 𐑞 ·𐑓𐑮𐑧𐑯𐑗 ·𐑮𐑧𐑝𐑩𐑤𐑵𐑖𐑩𐑯 𐑢𐑪𐑟 𐑕𐑳𐑥𐑔𐑦𐑙 𐑰𐑟𐑦 𐑑 𐑓𐑦𐑒𐑕.

·𐑣𐑨𐑮𐑦 𐑜𐑱𐑟𐑛 𐑳𐑐 𐑨𐑑 𐑞 𐑕𐑒𐑲, 𐑯 𐑨𐑑 𐑞 𐑐𐑱𐑤 𐑖𐑱𐑐 𐑝 𐑞 ·𐑥𐑵𐑯, 𐑝𐑦𐑟𐑩𐑚𐑩𐑤 𐑞𐑦𐑕 𐑥𐑹𐑯𐑦𐑙 𐑔𐑮𐑵 𐑞 𐑒𐑤𐑬𐑛𐑤𐑩𐑕 𐑺.

\emph{𐑕𐑴 𐑞 𐑢𐑻𐑤𐑛 𐑦𐑟 𐑚𐑮𐑴𐑒𐑩𐑯 𐑯 𐑓𐑤𐑷𐑛 𐑯 𐑦𐑯𐑕𐑱𐑯, 𐑯 𐑒𐑮𐑵𐑩𐑤 𐑯 𐑚𐑤𐑳𐑛𐑦 𐑯 𐑛𐑸𐑒. 𐑞𐑦𐑕 𐑦𐑟 𐑯𐑿𐑟? 𐑿 𐑷𐑤𐑢𐑱𐑟 𐑯𐑿 𐑞𐑨𐑑, 𐑧𐑯𐑦𐑢𐑱…}

“𐑿'𐑼 𐑤𐑫𐑒𐑦𐑙 𐑷𐑤 𐑕𐑽𐑾𐑕,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛. “𐑤𐑧𐑑 𐑥𐑰 𐑜𐑧𐑕, 𐑘𐑹 ·𐑥𐑳𐑜𐑩𐑤 𐑐𐑺𐑩𐑯𐑑𐑕 𐑑𐑴𐑤𐑛 𐑿 𐑞𐑨𐑑 𐑞𐑦𐑕 𐑕𐑹𐑑 𐑝 𐑔𐑦𐑙 𐑢𐑪𐑟 𐑚𐑨𐑛.”

·𐑣𐑨𐑮𐑦 𐑯𐑪𐑛𐑩𐑛, 𐑯𐑪𐑑 𐑒𐑢𐑲𐑑 𐑑𐑮𐑳𐑕𐑑𐑦𐑙 𐑣𐑦𐑟 𐑝𐑶𐑕.

“𐑢𐑧𐑤, 𐑤𐑲𐑒 ·𐑓𐑭𐑞𐑼 𐑕𐑧𐑟, 𐑞𐑺 𐑥𐑱 𐑚𐑰 𐑓𐑹 𐑣𐑬𐑟𐑩𐑟, 𐑚𐑳𐑑 𐑦𐑯 𐑞 𐑧𐑯𐑛 𐑧𐑝𐑮𐑦𐑢𐑳𐑯 𐑚𐑦𐑤𐑪𐑙𐑟 𐑑 𐑲𐑞𐑼 ·𐑕𐑤𐑲𐑔𐑼𐑦𐑯 𐑹 ·𐑣𐑳𐑓𐑩𐑤𐑐𐑳𐑓. 𐑯 𐑓𐑮𐑨𐑙𐑒𐑤𐑦, 𐑿'𐑼 𐑯𐑪𐑑 𐑪𐑯 𐑞 ·𐑣𐑳𐑓𐑩𐑤𐑐𐑳𐑓 𐑧𐑯𐑛. 𐑦𐑓 𐑿 𐑛𐑦𐑕𐑲𐑛 𐑑 𐑕𐑲𐑛 𐑢𐑦𐑞 𐑞 ·𐑥𐑨𐑤𐑓𐑶𐑟 𐑳𐑯𐑛𐑼 𐑞 𐑑𐑱𐑚𐑩𐑤…𐑬𐑼 𐑐𐑬𐑼 𐑯 𐑘𐑹 𐑮𐑧𐑐𐑿𐑑𐑱𐑖𐑩𐑯…𐑿 𐑒𐑫𐑛 𐑜𐑧𐑑 𐑩𐑢𐑱 𐑢𐑦𐑞 𐑔𐑦𐑙𐑟 𐑰𐑝𐑩𐑯 \emph{𐑲} 𐑒𐑭𐑯𐑑 𐑛𐑵. 𐑢𐑪𐑯𐑑 𐑑 \emph{𐑑𐑮𐑲} 𐑦𐑑 𐑓 𐑩 𐑢𐑲𐑤? 𐑕𐑰 𐑢𐑪𐑑 𐑦𐑑'𐑕 𐑤𐑲𐑒?”

\emph{𐑸𐑯𐑑 𐑢𐑰 𐑩 𐑒𐑤𐑧𐑝𐑼 𐑤𐑦𐑑𐑩𐑤 𐑕𐑻𐑐𐑩𐑯𐑑. 𐑦𐑤𐑧𐑝𐑩𐑯 𐑘𐑽𐑟 𐑴𐑤𐑛 𐑯 𐑷𐑤𐑮𐑧𐑛𐑦 𐑒𐑴𐑒𐑕𐑦𐑙 𐑘𐑹 𐑐𐑮𐑱 𐑓𐑮𐑪𐑥 𐑣𐑲𐑛𐑦𐑙…}

·𐑣𐑨𐑮𐑦 𐑔𐑷𐑑, 𐑒𐑩𐑯𐑕𐑦𐑛𐑼𐑛, 𐑗𐑴𐑟 𐑣𐑦𐑟 𐑢𐑧𐑐𐑩𐑯. “·𐑛𐑮𐑱𐑒𐑴, 𐑿 𐑢𐑪𐑯𐑑 𐑑 𐑦𐑒𐑕𐑐𐑤𐑱𐑯 𐑞 𐑣𐑴𐑤 𐑚𐑤𐑳𐑛 𐑐𐑘𐑫𐑼𐑦𐑑𐑦 𐑔𐑦𐑙 𐑑 𐑥𐑰? 𐑲'𐑥 𐑕𐑹𐑑 𐑝 𐑯𐑿.”

𐑩 𐑢𐑲𐑛 𐑕𐑥𐑲𐑤 𐑒𐑮𐑪𐑕𐑑 ·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑓𐑱𐑕. “𐑿 𐑮𐑾𐑤𐑦 𐑖𐑫𐑛 𐑥𐑰𐑑 ·𐑓𐑭𐑞𐑼 𐑯 𐑭𐑕𐑒 \emph{𐑣𐑦𐑥}, 𐑿 𐑯𐑴, 𐑣𐑰'𐑟 𐑬𐑼 𐑤𐑰𐑛𐑼.”

“𐑜𐑦𐑝 𐑥𐑰 𐑞 𐑔𐑻𐑑𐑦-𐑕𐑱𐑒𐑪𐑯𐑛 𐑝𐑻𐑠𐑩𐑯.”

“𐑴𐑒𐑱,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛. 𐑣𐑰 𐑛𐑮𐑵 𐑦𐑯 𐑩 𐑛𐑰𐑐 𐑚𐑮𐑧𐑔, 𐑯 𐑣𐑦𐑟 𐑝𐑶𐑕 𐑜𐑮𐑵 𐑕𐑤𐑲𐑑𐑤𐑦 𐑤𐑴𐑼, 𐑯 𐑑𐑫𐑒 𐑪𐑯 𐑩 𐑒𐑱𐑛𐑩𐑯𐑕. “𐑬𐑼 𐑐𐑬𐑼𐑟 𐑣𐑨𐑝 𐑜𐑮𐑴𐑯 𐑢𐑰𐑒𐑼, 𐑡𐑧𐑯𐑼𐑱𐑖𐑩𐑯 𐑚𐑲 𐑡𐑧𐑯𐑼𐑱𐑖𐑩𐑯, 𐑨𐑟 𐑞 𐑥𐑳𐑛𐑚𐑤𐑳𐑛 𐑑𐑱𐑯𐑑 𐑦𐑯𐑒𐑮𐑰𐑕𐑩𐑟. 𐑢𐑺 ·𐑕𐑭𐑤𐑭𐑟𐑸 𐑯 ·𐑜𐑪𐑛𐑮𐑦𐑒 𐑯 ·𐑮𐑴𐑢𐑰𐑯𐑩 𐑯 ·𐑣𐑧𐑤𐑜𐑩 𐑢𐑳𐑯𐑕 𐑮𐑱𐑟𐑛 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 𐑚𐑲 𐑞𐑺 𐑐𐑬𐑼, 𐑒𐑮𐑦𐑱𐑑𐑦𐑙 𐑞 ·𐑤𐑪𐑒𐑩𐑑 𐑯 𐑞 ·𐑕𐑹𐑛 𐑯 𐑞 ·𐑛𐑲𐑩𐑛𐑧𐑥 𐑯 𐑞 ·𐑒𐑳𐑐, 𐑯𐑴 𐑢𐑦𐑟𐑼𐑛 𐑝 𐑞𐑰𐑟 𐑓𐑱𐑛𐑩𐑛 𐑛𐑱𐑟 𐑣𐑨𐑟 𐑮𐑦𐑟𐑩𐑯 𐑑 𐑮𐑲𐑝𐑩𐑤 𐑞𐑧𐑥. 𐑢𐑰 𐑸 𐑓𐑱𐑛𐑦𐑙, 𐑷𐑤 𐑓𐑱𐑛𐑦𐑙 𐑦𐑯𐑑𐑵 ·𐑥𐑳𐑜𐑩𐑤𐑟 𐑨𐑟 𐑢𐑰 ·𐑦𐑯𐑑𐑼𐑚𐑮𐑰𐑛 𐑢𐑦𐑞 𐑞𐑺 𐑕𐑐𐑷𐑯 𐑯 𐑩𐑤𐑬 𐑬𐑼 ·𐑕𐑒𐑢𐑦𐑚𐑟 𐑑 𐑤𐑦𐑝. 𐑦𐑓 𐑞 𐑑𐑱𐑯𐑑 𐑦𐑟 𐑯𐑪𐑑 𐑗𐑧𐑒𐑑, 𐑕𐑵𐑯 𐑬𐑼 𐑢𐑪𐑯𐑛𐑟 𐑢𐑦𐑤 𐑚𐑮𐑱𐑒 𐑯 𐑷𐑤 𐑬𐑼 𐑸𐑑𐑕 𐑕𐑰𐑕, 𐑞 𐑤𐑲𐑯 𐑝 ·𐑥𐑻𐑤𐑦𐑯 𐑢𐑦𐑤 𐑧𐑯𐑛 𐑯 𐑞 𐑚𐑤𐑳𐑛 𐑝 ·𐑨𐑑𐑤𐑨𐑯𐑑𐑦𐑕 𐑓𐑱𐑤. 𐑬𐑼 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑢𐑦𐑤 𐑚𐑰 𐑤𐑧𐑓𐑑 𐑕𐑒𐑮𐑨𐑗𐑦𐑙 𐑨𐑑 𐑞 𐑛𐑻𐑑 𐑑 𐑕𐑼𐑝𐑲𐑝 𐑤𐑲𐑒 𐑞 𐑥𐑽 ·𐑥𐑳𐑜𐑩𐑤𐑟, 𐑯 𐑛𐑸𐑒𐑯𐑩𐑕 𐑢𐑦𐑤 𐑒𐑳𐑝𐑼 𐑷𐑤 𐑞 𐑢𐑻𐑤𐑛 𐑓 𐑧𐑝𐑼.” ·𐑛𐑮𐑱𐑒𐑴 𐑑𐑫𐑒 𐑩𐑯𐑳𐑞𐑼 𐑕𐑢𐑦𐑜 𐑓𐑮𐑪𐑥 𐑣𐑦𐑟 𐑛𐑮𐑦𐑙𐑒𐑕 𐑒𐑨𐑯, 𐑤𐑫𐑒𐑦𐑙 𐑕𐑨𐑑𐑦𐑕𐑓𐑲𐑛; 𐑞𐑨𐑑 𐑕𐑰𐑥𐑛 𐑑 𐑚𐑰 𐑞 𐑣𐑴𐑤 𐑸𐑜𐑿𐑥𐑩𐑯𐑑 𐑨𐑟 𐑓𐑸 𐑨𐑟 𐑣𐑰 𐑢𐑪𐑟 𐑒𐑩𐑯𐑕𐑻𐑯𐑛.

“·𐑐𐑼𐑕𐑢𐑱𐑕𐑦𐑝,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑥𐑰𐑯𐑦𐑙 𐑦𐑑 𐑛𐑦𐑕𐑒𐑮𐑦𐑐𐑑𐑦𐑝𐑤𐑦 𐑮𐑭𐑞𐑼 𐑞𐑨𐑯 𐑯𐑹𐑥𐑩𐑑𐑦𐑝𐑤𐑦. 𐑦𐑑 𐑢𐑪𐑟 𐑩 𐑕𐑑𐑨𐑯𐑛𐑼𐑛 𐑐𐑨𐑑𐑼𐑯: 𐑞 ·𐑓𐑷𐑤 𐑓𐑮𐑪𐑥 ·𐑜𐑮𐑱𐑕, 𐑞 𐑯𐑰𐑛 𐑑 𐑜𐑸𐑛 𐑢𐑪𐑑 𐑐𐑘𐑫𐑼𐑦𐑑𐑦 𐑮𐑦𐑥𐑱𐑯𐑛 𐑩𐑜𐑱𐑯𐑕𐑑 𐑒𐑩𐑯𐑑𐑨𐑥𐑦𐑯𐑱𐑖𐑩𐑯, 𐑞 𐑐𐑭𐑕𐑑 𐑕𐑤𐑴𐑐𐑦𐑙 𐑳𐑐𐑢𐑼𐑛𐑟 𐑯 𐑞 𐑓𐑿𐑗𐑼 𐑕𐑤𐑴𐑐𐑦𐑙 𐑴𐑯𐑤𐑦 𐑛𐑬𐑯. 𐑯 𐑞𐑨𐑑 𐑐𐑨𐑑𐑼𐑯 𐑷𐑤𐑕𐑴 𐑣𐑨𐑛 𐑦𐑑𐑕 \emph{𐑒𐑬𐑯𐑑𐑼}…“𐑲 𐑣𐑨𐑓 𐑑 𐑒𐑼𐑧𐑒𐑑 𐑿 𐑪𐑯 𐑢𐑳𐑯 𐑐𐑶𐑯𐑑 𐑝 𐑓𐑨𐑒𐑑, 𐑞𐑴. 𐑘𐑹 𐑦𐑯𐑓𐑼𐑥𐑱𐑖𐑩𐑯 𐑩𐑚𐑬𐑑 𐑞 ·𐑥𐑳𐑜𐑩𐑤𐑟 𐑦𐑟 𐑩 𐑚𐑦𐑑 𐑬𐑑 𐑝 𐑛𐑱𐑑. 𐑢𐑰 𐑸𐑯𐑑 𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦 𐑕𐑒𐑮𐑨𐑗𐑦𐑙 𐑨𐑑 𐑞 𐑛𐑻𐑑 𐑧𐑯𐑦 𐑥𐑹.”

·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑣𐑧𐑛 𐑕𐑯𐑨𐑐𐑑 𐑼𐑬𐑯𐑛. “\emph{𐑢𐑪𐑑?} 𐑢𐑪𐑑 𐑛𐑵 𐑿 𐑥𐑰𐑯, \emph{𐑢𐑰}?”

“𐑢𐑰. 𐑞 𐑕𐑲𐑩𐑯𐑑𐑦𐑕𐑑𐑕. 𐑞 𐑤𐑲𐑯 𐑝 ·𐑓𐑮𐑭𐑯𐑕𐑦𐑕 ·𐑚𐑱𐑒𐑩𐑯 𐑯 𐑞 𐑚𐑤𐑳𐑛 𐑝 𐑞 ·𐑦𐑯𐑤𐑲𐑑𐑩𐑯𐑥𐑩𐑯𐑑. ·𐑥𐑳𐑜𐑩𐑤𐑟 𐑛𐑦𐑛𐑩𐑯𐑑 𐑡𐑳𐑕𐑑 𐑕𐑦𐑑 𐑼𐑬𐑯𐑛 𐑒𐑮𐑲𐑦𐑙 𐑩𐑚𐑬𐑑 𐑯𐑪𐑑 𐑣𐑨𐑝𐑦𐑙 𐑢𐑪𐑯𐑛𐑟, 𐑢𐑰 𐑣𐑨𐑝 𐑬𐑼 \emph{𐑴𐑯} 𐑐𐑬𐑼𐑟 𐑯𐑬, 𐑢𐑦𐑞 𐑹 𐑢𐑦𐑞𐑬𐑑 𐑥𐑨𐑡𐑦𐑒. 𐑦𐑓 𐑷𐑤 𐑘𐑹 𐑐𐑬𐑼𐑟 𐑓𐑱𐑤 𐑞𐑧𐑯 𐑢𐑰 𐑢𐑦𐑤 𐑷𐑤 𐑣𐑨𐑝 𐑤𐑪𐑕𐑑 𐑕𐑳𐑥𐑔𐑦𐑙 𐑝𐑧𐑮𐑦 𐑐𐑮𐑧𐑖𐑩𐑕, 𐑚𐑦𐑒𐑪𐑟 𐑘𐑹 𐑥𐑨𐑡𐑦𐑒 𐑦𐑟 𐑞 𐑴𐑯𐑤𐑦 𐑣𐑦𐑯𐑑 𐑢𐑰 𐑣𐑨𐑝 𐑨𐑟 𐑑 𐑣𐑬 𐑞 𐑿𐑯𐑦𐑝𐑻𐑕 𐑥𐑳𐑕𐑑 \emph{𐑮𐑾𐑤𐑦} 𐑢𐑻𐑒—𐑚𐑳𐑑 𐑿 𐑢𐑴𐑯𐑑 𐑚𐑰 𐑤𐑧𐑓𐑑 𐑕𐑒𐑮𐑨𐑗𐑦𐑙 𐑨𐑑 𐑞 𐑜𐑮𐑬𐑯𐑛. 𐑘𐑹 𐑣𐑬𐑟𐑩𐑟 𐑢𐑦𐑤 𐑕𐑑𐑦𐑤 𐑚𐑰 𐑒𐑵𐑤 𐑦𐑯 𐑕𐑳𐑥𐑼 𐑯 𐑢𐑹𐑥 𐑦𐑯 𐑢𐑦𐑯𐑑𐑼, 𐑞𐑺 𐑢𐑦𐑤 𐑕𐑑𐑦𐑤 𐑚𐑰 𐑛𐑪𐑒𐑑𐑼𐑟 𐑯 𐑥𐑧𐑛𐑦𐑕𐑦𐑯. 𐑕𐑲𐑩𐑯𐑕 𐑒𐑨𐑯 𐑒𐑰𐑐 𐑿 𐑩𐑤𐑲𐑝 𐑦𐑓 𐑥𐑨𐑡𐑦𐑒 𐑓𐑱𐑤𐑟. 𐑦𐑑'𐑩𐑛 𐑚𐑰 𐑩 𐑑𐑮𐑨𐑡𐑩𐑛𐑦, 𐑚𐑳𐑑 𐑯𐑪𐑑 𐑤𐑦𐑑𐑼𐑩𐑤𐑦 𐑞 𐑧𐑯𐑛 𐑝 𐑷𐑤 𐑞 𐑤𐑲𐑑 𐑦𐑯 𐑞 𐑢𐑻𐑤𐑛. 𐑡𐑳𐑕𐑑 𐑕𐑱𐑦𐑙.”

·𐑛𐑮𐑱𐑒𐑴 𐑣𐑨𐑛 𐑚𐑨𐑒𐑑 𐑳𐑐 𐑕𐑧𐑝𐑼𐑩𐑤 𐑓𐑰𐑑 𐑯 𐑣𐑦𐑟 𐑓𐑱𐑕 𐑢𐑪𐑟 𐑓𐑫𐑤 𐑝 𐑥𐑦𐑒𐑕𐑑 𐑓𐑽 𐑯 𐑛𐑦𐑕𐑚𐑦𐑤𐑰𐑓. “\emph{𐑢𐑪𐑑 𐑦𐑯 𐑞 𐑯𐑱𐑥 𐑝 ·𐑥𐑻𐑤𐑦𐑯 𐑸 𐑿 𐑑𐑷𐑒𐑦𐑙 𐑩𐑚𐑬𐑑, ·𐑐𐑪𐑑𐑼?}”

“𐑣𐑱, 𐑲 𐑤𐑦𐑕𐑩𐑯𐑛 𐑑 \emph{𐑘𐑹} 𐑕𐑑𐑹𐑦, 𐑢𐑴𐑯𐑑 𐑿 𐑤𐑦𐑕𐑩𐑯 𐑑 𐑥𐑲𐑯?” \emph{𐑒𐑤𐑳𐑥𐑟𐑦,} ·𐑣𐑨𐑮𐑦 𐑗𐑲𐑛𐑩𐑛 𐑣𐑦𐑥𐑕𐑧𐑤𐑓, 𐑚𐑳𐑑 ·𐑛𐑮𐑱𐑒𐑴 𐑨𐑒𐑗𐑵𐑩𐑤𐑦 𐑛𐑦𐑛 𐑕𐑑𐑪𐑐 𐑚𐑨𐑒𐑦𐑙 𐑪𐑓 𐑯 𐑕𐑰𐑥 𐑑 𐑤𐑦𐑕𐑩𐑯.

“𐑧𐑯𐑦𐑢𐑱,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, “𐑲'𐑥 𐑕𐑱𐑦𐑙 𐑞𐑨𐑑 𐑿 𐑛𐑴𐑯𐑑 𐑕𐑰𐑥 𐑑 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑐𐑱𐑦𐑙 𐑥𐑳𐑗 𐑩𐑑𐑧𐑯𐑖𐑩𐑯 𐑑 𐑢𐑪𐑑 𐑜𐑴𐑟 𐑪𐑯 𐑦𐑯 𐑞 ·𐑥𐑳𐑜𐑩𐑤 𐑢𐑻𐑤𐑛.” 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑚𐑦𐑒𐑪𐑟 𐑞 𐑣𐑴𐑤 𐑢𐑦𐑟𐑼𐑛𐑦𐑙 𐑢𐑻𐑤𐑛 𐑕𐑰𐑥𐑛 𐑑 𐑮𐑦𐑜𐑸𐑛 𐑞 𐑮𐑧𐑕𐑑 𐑝 ·𐑻𐑔 𐑨𐑟 𐑩 𐑕𐑤𐑳𐑥, 𐑛𐑦𐑟𐑻𐑝𐑦𐑙 𐑼𐑬𐑯𐑛 𐑨𐑟 𐑥𐑳𐑗 𐑯𐑿𐑟 𐑒𐑳𐑝𐑼𐑦𐑡 𐑨𐑟 𐑞 \emph{·𐑓𐑲𐑯𐑨𐑯𐑖𐑩𐑤 ·𐑑𐑲𐑥𐑟} 𐑩𐑢𐑹𐑛𐑩𐑛 𐑑 𐑞 𐑮𐑵𐑑𐑰𐑯 𐑨𐑜𐑩𐑯𐑦𐑟 𐑝 ·𐑚𐑫𐑮𐑫𐑯𐑛𐑦. “𐑷𐑤 𐑮𐑲𐑑. 𐑒𐑢𐑦𐑒 𐑗𐑧𐑒. 𐑣𐑨𐑝 𐑢𐑦𐑟𐑼𐑛𐑟 𐑧𐑝𐑼 𐑚𐑰𐑯 𐑑 𐑞 ·𐑥𐑵𐑯? 𐑿 𐑯𐑴, 𐑞𐑨𐑑 𐑔𐑦𐑙?” ·𐑣𐑨𐑮𐑦 𐑐𐑶𐑯𐑑𐑩𐑛 𐑳𐑐 𐑑 𐑞𐑨𐑑 𐑣𐑿𐑡 𐑯 𐑛𐑦𐑕𐑑𐑩𐑯𐑑 𐑜𐑤𐑴𐑚.

“\emph{𐑢𐑪𐑑?}” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛. 𐑦𐑑 𐑢𐑪𐑟 𐑐𐑮𐑦𐑑𐑦 𐑒𐑤𐑽 𐑞 𐑔𐑷𐑑 𐑣𐑨𐑛 𐑯𐑧𐑝𐑼 𐑩𐑒𐑻𐑛 𐑑 𐑞 𐑚𐑶. “\emph{𐑜𐑴} 𐑑 𐑞—𐑦𐑑'𐑕 𐑡𐑳𐑕𐑑 𐑩—” 𐑣𐑦𐑟 𐑓𐑦𐑙𐑜𐑼 𐑐𐑶𐑯𐑑𐑩𐑛 𐑨𐑑 𐑞 𐑤𐑦𐑑𐑩𐑤 𐑐𐑱𐑤 𐑔𐑦𐑙𐑦 𐑦𐑯 𐑞 𐑕𐑒𐑲. “𐑿 𐑒𐑭𐑯𐑑 ·𐑨𐑐𐑼𐑱𐑑 𐑑 𐑕𐑳𐑥𐑢𐑺 𐑿'𐑝 𐑯𐑧𐑝𐑼 \emph{𐑚𐑰𐑯} 𐑯 𐑣𐑬 𐑢𐑫𐑛 𐑧𐑯𐑦𐑢𐑳𐑯 𐑜𐑧𐑑 𐑑 𐑞 ·𐑥𐑵𐑯 𐑦𐑯 𐑞 \emph{𐑓𐑻𐑕𐑑} 𐑐𐑤𐑱𐑕?”

“𐑣𐑴𐑤𐑛 𐑪𐑯,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛 𐑑 ·𐑛𐑮𐑱𐑒𐑴, “𐑲'𐑛 𐑤𐑲𐑒 𐑑 𐑖𐑴 𐑿 𐑩 𐑚𐑫𐑒 𐑲 𐑚𐑮𐑷𐑑 𐑢𐑦𐑞 𐑥𐑰, 𐑲 𐑔𐑦𐑙𐑒 𐑲 𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑢𐑪𐑑 𐑚𐑪𐑒𐑕 𐑦𐑑'𐑕 𐑦𐑯.” 𐑯 ·𐑣𐑨𐑮𐑦 𐑕𐑑𐑫𐑛 𐑳𐑐 𐑯 𐑯𐑧𐑤𐑑 𐑛𐑬𐑯 𐑯 𐑘𐑨𐑙𐑒𐑑 𐑬𐑑 𐑞 𐑕𐑑𐑺𐑟 𐑑 𐑞 𐑒𐑨𐑝𐑼𐑯 𐑤𐑧𐑝𐑩𐑤 𐑝 𐑣𐑦𐑟 𐑑𐑮𐑳𐑙𐑒, 𐑞𐑧𐑯 𐑑𐑹 𐑛𐑬𐑯 𐑞 𐑕𐑑𐑺𐑟 𐑯 𐑣𐑰𐑝𐑛 𐑩 𐑚𐑪𐑒𐑕 𐑪𐑓 𐑩𐑯𐑳𐑞𐑼 𐑚𐑪𐑒𐑕, 𐑒𐑳𐑥𐑦𐑙 𐑐𐑧𐑮𐑦𐑤𐑩𐑕𐑤𐑦 𐑒𐑤𐑴𐑕 𐑑 𐑑𐑮𐑰𐑑𐑦𐑙 𐑣𐑦𐑟 𐑚𐑫𐑒𐑕 𐑢𐑦𐑞 𐑛𐑦𐑕𐑮𐑦𐑕𐑐𐑧𐑒𐑑, 𐑯 𐑕𐑯𐑨𐑗𐑑 𐑪𐑓 𐑞 𐑚𐑪𐑒𐑕 𐑒𐑳𐑝𐑼 𐑯 𐑒𐑢𐑦𐑒𐑤𐑦 𐑚𐑳𐑑 𐑒𐑺𐑓𐑩𐑤𐑦 𐑐𐑮𐑲𐑛 𐑬𐑑 𐑩 𐑕𐑑𐑨𐑒 𐑝 𐑚𐑫𐑒𐑕—

(·𐑣𐑨𐑮𐑦 𐑣𐑨𐑛 𐑦𐑯𐑣𐑧𐑮𐑦𐑑𐑩𐑛 𐑞 𐑯𐑲-·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 ·𐑝𐑧𐑮𐑟 𐑩𐑚𐑦𐑤𐑦𐑑𐑦 𐑑 𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑢𐑺 𐑷𐑤 𐑣𐑦𐑟 𐑚𐑫𐑒𐑕 𐑢𐑻, 𐑰𐑝𐑩𐑯 𐑭𐑓𐑑𐑼 𐑕𐑰𐑦𐑙 𐑞𐑧𐑥 𐑡𐑳𐑕𐑑 𐑢𐑳𐑯𐑕, 𐑢𐑦𐑗 𐑢𐑪𐑟 𐑮𐑭𐑞𐑼 𐑥𐑦𐑕𐑑𐑽𐑾𐑕 𐑒𐑩𐑯𐑕𐑦𐑛𐑼𐑦𐑙 𐑞 𐑤𐑨𐑒 𐑝 𐑧𐑯𐑦 𐑡𐑩𐑯𐑧𐑑𐑦𐑒 𐑒𐑩𐑯𐑧𐑒𐑖𐑩𐑯.)

𐑯 ·𐑣𐑨𐑮𐑦 𐑮𐑱𐑕𐑑 𐑚𐑨𐑒 𐑳𐑐 𐑞 𐑕𐑑𐑺𐑟 𐑯 𐑖𐑳𐑝𐑛 𐑞 𐑕𐑑𐑺𐑒𐑱𐑕 𐑚𐑨𐑒 𐑦𐑯𐑑𐑵 𐑞 𐑑𐑮𐑳𐑙𐑒 𐑢𐑦𐑞 𐑣𐑦𐑟 𐑣𐑰𐑤, 𐑯, 𐑐𐑨𐑯𐑑𐑦𐑙, 𐑑𐑻𐑯𐑛 𐑞 𐑐𐑱𐑡𐑩𐑟 𐑝 𐑞 𐑚𐑫𐑒 𐑩𐑯𐑑𐑦𐑤 𐑣𐑰 𐑓𐑬𐑯𐑛 𐑞 𐑐𐑦𐑒𐑗𐑼 𐑣𐑰 𐑢𐑪𐑯𐑑𐑩𐑛 𐑑 𐑖𐑴 𐑑 ·𐑛𐑮𐑱𐑒𐑴.

𐑞 𐑢𐑳𐑯 𐑢𐑦𐑞 𐑞 𐑢𐑲𐑑, 𐑛𐑮𐑲, 𐑒𐑮𐑱𐑑𐑼𐑛 𐑤𐑨𐑯𐑛, 𐑯 𐑞 𐑕𐑵𐑑𐑩𐑛 𐑐𐑰𐑐𐑩𐑤, 𐑯 𐑞 𐑚𐑤𐑵-𐑢𐑲𐑑 𐑜𐑤𐑴𐑚 𐑣𐑨𐑙𐑦𐑙 𐑴𐑝𐑼 𐑦𐑑 𐑷𐑤.

𐑞𐑨𐑑 𐑐𐑦𐑒𐑗𐑼.

\emph{𐑞} 𐑐𐑦𐑒𐑗𐑼, 𐑦𐑓 𐑴𐑯𐑤𐑦 𐑢𐑳𐑯 𐑐𐑦𐑒𐑗𐑼 𐑦𐑯 𐑷𐑤 𐑞 𐑢𐑻𐑤𐑛 𐑢𐑻 𐑑 𐑕𐑼𐑝𐑲𐑝.

“\emph{𐑞𐑨𐑑},” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑣𐑦𐑟 𐑝𐑶𐑕 𐑑𐑮𐑧𐑥𐑚𐑩𐑤𐑦𐑙 𐑚𐑦𐑒𐑪𐑟 𐑣𐑰 𐑒𐑫𐑛𐑩𐑯𐑑 𐑒𐑢𐑲𐑑 𐑒𐑰𐑐 𐑞 𐑐𐑮𐑲𐑛 𐑬𐑑, “𐑦𐑟 𐑢𐑪𐑑 𐑞 ·𐑻𐑔 𐑤𐑫𐑒𐑕 𐑤𐑲𐑒 𐑓𐑮𐑪𐑥 𐑞 ·𐑥𐑵𐑯.”

·𐑛𐑮𐑱𐑒𐑴 𐑕𐑤𐑴𐑤𐑦 𐑤𐑰𐑯𐑛 𐑴𐑝𐑼. 𐑞𐑺 𐑢𐑪𐑟 𐑩 𐑕𐑑𐑮𐑱𐑯𐑡 𐑦𐑒𐑕𐑐𐑮𐑧𐑖𐑩𐑯 𐑪𐑯 𐑣𐑦𐑟 𐑘𐑳𐑙 𐑓𐑱𐑕. “𐑦𐑓 𐑞𐑨𐑑'𐑕 𐑩 \emph{𐑮𐑾𐑤} 𐑐𐑦𐑒𐑗𐑼, 𐑢𐑲 𐑦𐑟𐑩𐑯𐑑 𐑦𐑑 𐑥𐑵𐑝𐑦𐑙?”

\emph{𐑥𐑵𐑝𐑦𐑙?} 𐑴. “·𐑥𐑳𐑜𐑩𐑤𐑟 𐑒𐑨𐑯 𐑛𐑵 𐑥𐑵𐑝𐑦𐑙 𐑐𐑦𐑒𐑗𐑼𐑟 𐑚𐑳𐑑 𐑞𐑱 𐑯𐑰𐑛 𐑩 𐑚𐑦𐑜𐑼 𐑚𐑪𐑒𐑕 𐑑 𐑖𐑴 𐑦𐑑, 𐑞𐑱 𐑒𐑭𐑯𐑑 𐑓𐑦𐑑 𐑞𐑧𐑥 𐑪𐑯𐑑𐑵 𐑕𐑦𐑙𐑜𐑩𐑤 𐑚𐑫𐑒 𐑐𐑱𐑡𐑩𐑟 𐑘𐑧𐑑.”

·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑓𐑦𐑙𐑜𐑼 𐑥𐑵𐑝𐑛 𐑑 𐑢𐑳𐑯 𐑝 𐑞 𐑕𐑵𐑑𐑕. “𐑢𐑪𐑑 𐑸 𐑞𐑴𐑟?” 𐑣𐑦𐑟 𐑝𐑶𐑕 𐑕𐑑𐑸𐑑𐑦𐑙 𐑑 𐑢𐑱𐑝𐑼.

“𐑞𐑴𐑟 𐑸 𐑣𐑿𐑥𐑩𐑯 𐑚𐑰𐑦𐑙𐑟. 𐑞𐑱 𐑸 𐑢𐑺𐑦𐑙 𐑕𐑵𐑑𐑕 𐑞𐑨𐑑 𐑒𐑳𐑝𐑼 𐑞𐑺 𐑣𐑴𐑤 𐑚𐑪𐑛𐑦𐑟 𐑑 𐑜𐑦𐑝 𐑞𐑧𐑥 𐑺, 𐑚𐑦𐑒𐑪𐑟 𐑞𐑺 𐑦𐑟 𐑯𐑴 𐑺 𐑪𐑯 𐑞 ·𐑥𐑵𐑯.”

“𐑞𐑨𐑑'𐑕 𐑦𐑥𐑐𐑪𐑕𐑩𐑚𐑩𐑤,” ·𐑛𐑮𐑱𐑒𐑴 𐑢𐑦𐑕𐑐𐑼𐑛. 𐑞𐑺 𐑢𐑪𐑟 𐑑𐑧𐑮𐑼 𐑦𐑯 𐑣𐑦𐑟 𐑲𐑟, 𐑯 𐑳𐑑𐑼 𐑒𐑩𐑯𐑓𐑿𐑠𐑩𐑯. “𐑯𐑴 ·𐑥𐑳𐑜𐑩𐑤 𐑒𐑫𐑛 𐑧𐑝𐑼 𐑛𐑵 𐑞𐑨𐑑. \emph{𐑣𐑬…}”

·𐑣𐑨𐑮𐑦 𐑑𐑫𐑒 𐑚𐑨𐑒 𐑞 𐑚𐑫𐑒, 𐑓𐑤𐑦𐑐𐑑 𐑞 𐑐𐑱𐑡𐑩𐑟 𐑩𐑯𐑑𐑦𐑤 𐑣𐑰 𐑓𐑬𐑯𐑛 𐑢𐑪𐑑 𐑣𐑰 𐑕𐑷. “𐑞𐑦𐑕 𐑦𐑟 𐑩 𐑮𐑪𐑒𐑩𐑑 𐑜𐑴𐑦𐑙 𐑳𐑐. 𐑞 𐑓𐑲𐑼 𐑐𐑫𐑖𐑩𐑟 𐑦𐑑 𐑣𐑲𐑼 𐑯 𐑣𐑲𐑼, 𐑩𐑯𐑑𐑦𐑤 𐑦𐑑 𐑜𐑧𐑑𐑕 𐑑 𐑞 ·𐑥𐑵𐑯.” 𐑓𐑤𐑦𐑐𐑑 𐑐𐑱𐑡𐑩𐑟 𐑩𐑜𐑱𐑯. “𐑞𐑦𐑕 𐑦𐑟 𐑩 𐑮𐑪𐑒𐑩𐑑 𐑪𐑯 𐑞 𐑜𐑮𐑬𐑯𐑛. 𐑞𐑨𐑑 𐑑𐑲𐑯𐑦 𐑕𐑐𐑧𐑒 𐑯𐑧𐑒𐑕𐑑 𐑑 𐑦𐑑 𐑦𐑟 𐑩 𐑐𐑻𐑕𐑩𐑯.” ·𐑛𐑮𐑱𐑒𐑴 𐑜𐑭𐑕𐑐𐑑. “𐑜𐑴𐑦𐑙 𐑑 𐑞 ·𐑥𐑵𐑯 𐑒𐑪𐑕𐑑 𐑞 𐑦𐑒𐑢𐑦𐑝𐑩𐑤𐑩𐑯𐑑 𐑝…𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑼𐑬𐑯𐑛 𐑩 𐑔𐑬𐑟𐑩𐑯𐑛 𐑥𐑦𐑤𐑘𐑩𐑯 ·𐑜𐑨𐑤𐑾𐑯𐑟.” ·𐑛𐑮𐑱𐑒𐑴 𐑗𐑴𐑒𐑑. “𐑯 𐑦𐑑 𐑑𐑫𐑒 𐑞 𐑧𐑓𐑼𐑑𐑕 𐑝…𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑥𐑹 𐑐𐑰𐑐𐑩𐑤 𐑞𐑨𐑯 𐑤𐑦𐑝 𐑦𐑯 𐑷𐑤 𐑝 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 ·𐑚𐑮𐑦𐑑𐑩𐑯.” \emph{𐑯 𐑢𐑧𐑯 𐑞𐑱 𐑼𐑲𐑝𐑛, 𐑞𐑱 𐑤𐑧𐑓𐑑 𐑩 𐑐𐑤𐑭𐑒 𐑞𐑨𐑑 𐑕𐑧𐑛, '𐑢𐑰 𐑒𐑱𐑥 𐑦𐑯 𐑐𐑰𐑕, 𐑓 𐑷𐑤 𐑥𐑨𐑯𐑒𐑲𐑯𐑛.' 𐑞𐑴 𐑿'𐑼 𐑯𐑪𐑑 𐑘𐑧𐑑 𐑮𐑧𐑛𐑦 𐑑 𐑣𐑽 𐑞𐑴𐑟 𐑢𐑻𐑛𐑟, ·𐑛𐑮𐑱𐑒𐑴 ·𐑥𐑨𐑤𐑓𐑶…}

“𐑿'𐑼 𐑑𐑧𐑤𐑦𐑙 𐑞 𐑑𐑮𐑵𐑔,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛 𐑕𐑤𐑴𐑤𐑦. “𐑿 𐑢𐑫𐑛𐑩𐑯𐑑 𐑓𐑱𐑒 𐑩 𐑣𐑴𐑤 𐑚𐑫𐑒 𐑡𐑳𐑕𐑑 𐑓 𐑞𐑦𐑕—𐑯 𐑲 𐑒𐑨𐑯 𐑣𐑽 𐑦𐑑 𐑦𐑯 𐑘𐑹 𐑝𐑶𐑕. 𐑚𐑳𐑑…𐑚𐑳𐑑…”

“𐑣𐑬, 𐑢𐑦𐑞𐑬𐑑 𐑢𐑪𐑯𐑛𐑟 𐑹 𐑥𐑨𐑡𐑦𐑒? 𐑦𐑑'𐑕 𐑩 𐑤𐑪𐑙 𐑕𐑑𐑹𐑦, ·𐑛𐑮𐑱𐑒𐑴. 𐑕𐑲𐑩𐑯𐑕 𐑛𐑳𐑟𐑩𐑯𐑑 𐑢𐑻𐑒 𐑚𐑲 𐑢𐑱𐑝𐑦𐑙 𐑢𐑪𐑯𐑛𐑟 𐑯 𐑗𐑭𐑯𐑑𐑦𐑙 𐑕𐑐𐑧𐑤𐑟, 𐑦𐑑 𐑢𐑻𐑒𐑕 𐑚𐑲 𐑯𐑴𐑦𐑙 𐑣𐑬 𐑞 𐑿𐑯𐑦𐑝𐑻𐑕 𐑢𐑻𐑒𐑕 𐑪𐑯 𐑕𐑳𐑗 𐑩 𐑛𐑰𐑐 𐑤𐑧𐑝𐑩𐑤 𐑞𐑨𐑑 𐑿 𐑯𐑴 𐑦𐑜𐑟𐑨𐑒𐑑𐑤𐑦 𐑢𐑪𐑑 𐑑 𐑛𐑵 𐑦𐑯 𐑹𐑛𐑼 𐑑 𐑥𐑱𐑒 𐑞 𐑿𐑯𐑦𐑝𐑻𐑕 𐑛𐑵 𐑢𐑪𐑑 𐑿 𐑢𐑪𐑯𐑑. 𐑦𐑓 𐑥𐑨𐑡𐑦𐑒 𐑦𐑟 𐑤𐑲𐑒 𐑒𐑭𐑕𐑑𐑦𐑙 \emph{·𐑦𐑥𐑐𐑽𐑦𐑴} 𐑪𐑯 𐑕𐑳𐑥𐑢𐑳𐑯 𐑑 𐑥𐑱𐑒 𐑞𐑧𐑥 𐑛𐑵 𐑢𐑪𐑑 𐑿 𐑢𐑪𐑯𐑑, 𐑞𐑧𐑯 𐑕𐑲𐑩𐑯𐑕 𐑦𐑟 𐑤𐑲𐑒 𐑯𐑴𐑦𐑙 𐑞𐑧𐑥 𐑕𐑴 𐑢𐑧𐑤 𐑞𐑨𐑑 𐑿 𐑒𐑨𐑯 𐑒𐑩𐑯𐑝𐑦𐑯𐑕 𐑞𐑧𐑥 𐑦𐑑 𐑢𐑪𐑟 𐑞𐑺 𐑴𐑯 𐑲𐑛𐑾 𐑷𐑤 𐑩𐑤𐑪𐑙. 𐑦𐑑'𐑕 𐑩 𐑤𐑪𐑑 𐑥𐑹 𐑛𐑦𐑓𐑦𐑒𐑳𐑤𐑑 𐑞𐑨𐑯 𐑢𐑱𐑝𐑦𐑙 𐑩 𐑢𐑪𐑯𐑛, 𐑚𐑳𐑑 𐑦𐑑 𐑢𐑻𐑒𐑕 𐑢𐑧𐑯 𐑢𐑪𐑯𐑛𐑟 𐑓𐑱𐑤, 𐑡𐑳𐑕𐑑 𐑤𐑲𐑒 𐑦𐑓 𐑞 \emph{·𐑦𐑥𐑐𐑽𐑾𐑕} 𐑓𐑱𐑤𐑛 𐑿 𐑒𐑫𐑛 𐑕𐑑𐑦𐑤 𐑑𐑮𐑲 𐑐𐑼𐑕𐑢𐑱𐑛𐑦𐑙 𐑩 𐑐𐑻𐑕𐑩𐑯. 𐑯 ·𐑕𐑲𐑩𐑯𐑕 𐑚𐑦𐑤𐑛𐑟 𐑓𐑮𐑪𐑥 𐑡𐑧𐑯𐑼𐑱𐑖𐑩𐑯 𐑑 𐑡𐑧𐑯𐑼𐑱𐑖𐑩𐑯. 𐑿 𐑣𐑨𐑓 𐑑 𐑮𐑾𐑤𐑦 \emph{𐑯𐑴} 𐑢𐑪𐑑 𐑿'𐑼 𐑛𐑵𐑦𐑙 𐑑 𐑛𐑵 𐑕𐑲𐑩𐑯𐑕—𐑯 𐑢𐑧𐑯 𐑿 𐑮𐑾𐑤𐑦 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑕𐑳𐑥𐑔𐑦𐑙, 𐑿 𐑒𐑨𐑯 𐑦𐑒𐑕𐑐𐑤𐑱𐑯 𐑦𐑑 𐑑 𐑕𐑳𐑥𐑢𐑳𐑯 𐑧𐑤𐑕. 𐑞 𐑜𐑮𐑱𐑑𐑩𐑕𐑑 𐑕𐑲𐑩𐑯𐑑𐑦𐑕𐑑𐑕 𐑝 𐑢𐑳𐑯 𐑕𐑧𐑯𐑗𐑼𐑦 𐑩𐑜𐑴, 𐑞 𐑚𐑮𐑲𐑑𐑩𐑕𐑑 𐑯𐑱𐑥𐑟 𐑞𐑨𐑑 𐑸 𐑕𐑑𐑦𐑤 𐑕𐑐𐑴𐑒𐑩𐑯 𐑢𐑦𐑞 𐑮𐑧𐑝𐑼𐑩𐑯𐑕, 𐑞𐑺 𐑐𐑬𐑼𐑟 𐑸 𐑨𐑟 \emph{𐑯𐑳𐑔𐑦𐑙} 𐑑 𐑞 𐑜𐑮𐑱𐑑𐑩𐑕𐑑 𐑕𐑲𐑩𐑯𐑑𐑦𐑕𐑑𐑕 𐑝 𐑑𐑩𐑛𐑱. 𐑞𐑺 𐑦𐑟 𐑯𐑴 𐑦𐑒𐑢𐑦𐑝𐑩𐑤𐑩𐑯𐑑 𐑦𐑯 𐑕𐑲𐑩𐑯𐑕 𐑝 𐑘𐑹 𐑤𐑪𐑕𐑑 𐑸𐑑𐑕 𐑞𐑨𐑑 𐑮𐑱𐑟𐑛 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕. 𐑦𐑯 𐑕𐑲𐑩𐑯𐑕 𐑬𐑼 𐑐𐑬𐑼𐑟 𐑢𐑨𐑒𐑕 𐑚𐑲 𐑞 𐑘𐑽. 𐑯 𐑢𐑰 𐑸 𐑚𐑦𐑜𐑦𐑯𐑦𐑙 𐑑 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑯 𐑳𐑯𐑮𐑨𐑝𐑩𐑤 𐑞 𐑕𐑰𐑒𐑮𐑩𐑑𐑕 𐑝 𐑤𐑲𐑓 𐑯 𐑦𐑯𐑣𐑧𐑮𐑦𐑑𐑩𐑯𐑕. 𐑢𐑰'𐑤 𐑚𐑰 𐑱𐑚𐑩𐑤 𐑑 𐑤𐑫𐑒 𐑨𐑑 𐑞 𐑝𐑧𐑮𐑦 𐑚𐑤𐑳𐑛 𐑝 𐑢𐑦𐑗 𐑿 𐑕𐑐𐑴𐑒, 𐑯 𐑕𐑰 𐑢𐑪𐑑 𐑥𐑱𐑒𐑕 𐑿 𐑩 𐑢𐑦𐑟𐑼𐑛, 𐑯 𐑦𐑯 𐑢𐑳𐑯 𐑹 𐑑𐑵 𐑥𐑹 𐑡𐑧𐑯𐑼𐑱𐑖𐑩𐑯𐑟, 𐑢𐑰'𐑤 𐑚𐑰 𐑱𐑚𐑩𐑤 𐑑 𐑐𐑼𐑕𐑢𐑱𐑛 𐑞𐑨𐑑 𐑚𐑤𐑳𐑛 𐑑 𐑥𐑱𐑒 𐑷𐑤 𐑘𐑹 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑐𐑬𐑼𐑓𐑩𐑤 𐑢𐑦𐑟𐑼𐑛𐑟 𐑑𐑵. 𐑕𐑴 𐑿 𐑕𐑰, 𐑘𐑹 𐑐𐑮𐑪𐑚𐑤𐑩𐑥 𐑦𐑟𐑩𐑯𐑑 𐑯𐑽𐑤𐑦 𐑨𐑟 𐑚𐑨𐑛 𐑨𐑟 𐑦𐑑 𐑤𐑫𐑒𐑕, 𐑚𐑦𐑒𐑪𐑟 𐑦𐑯 𐑩 𐑓𐑿 𐑥𐑹 𐑛𐑧𐑒𐑱𐑛𐑟, 𐑕𐑲𐑩𐑯𐑕 𐑢𐑦𐑤 𐑚𐑰 𐑱𐑚𐑩𐑤 𐑑 𐑕𐑪𐑤𐑝 𐑦𐑑 𐑓 𐑿.”

“𐑚𐑳𐑑…” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛. 𐑣𐑦𐑟 𐑝𐑶𐑕 𐑢𐑪𐑟 𐑑𐑮𐑧𐑥𐑚𐑩𐑤𐑦𐑙. “𐑦𐑓 \emph{·𐑥𐑳𐑜𐑩𐑤𐑟} 𐑣𐑨𐑝 𐑞𐑨𐑑 𐑒𐑲𐑯𐑛 𐑝 𐑐𐑬𐑼…𐑞𐑧𐑯…𐑢𐑪𐑑 𐑸 \emph{𐑢𐑰}?”

“𐑯𐑴, ·𐑛𐑮𐑱𐑒𐑴, 𐑞𐑨𐑑'𐑕 𐑯𐑪𐑑 𐑦𐑑, 𐑛𐑴𐑯𐑑 𐑿 𐑕𐑰? 𐑕𐑲𐑩𐑯𐑕 𐑑𐑨𐑐𐑕 𐑞 𐑐𐑬𐑼 𐑝 𐑣𐑿𐑥𐑩𐑯 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛𐑦𐑙 𐑑 𐑤𐑫𐑒 𐑨𐑑 𐑞 𐑢𐑻𐑤𐑛 𐑯 𐑓𐑦𐑜𐑼 𐑬𐑑 𐑣𐑬 𐑦𐑑 𐑢𐑻𐑒𐑕. 𐑦𐑑 𐑒𐑭𐑯𐑑 𐑓𐑱𐑤 𐑢𐑦𐑞𐑬𐑑 𐑣𐑿𐑥𐑨𐑯𐑦𐑑𐑦 𐑦𐑑𐑕𐑧𐑤𐑓 𐑓𐑱𐑤𐑦𐑙. 𐑘𐑹 𐑥𐑨𐑡𐑦𐑒 𐑒𐑫𐑛 𐑑𐑻𐑯 𐑪𐑓, 𐑯 𐑿 𐑢𐑫𐑛 𐑣𐑱𐑑 𐑞𐑨𐑑, 𐑚𐑳𐑑 𐑿 𐑢𐑫𐑛 𐑕𐑑𐑦𐑤 𐑚𐑰 \emph{𐑿}. 𐑿 𐑢𐑫𐑛 𐑕𐑑𐑦𐑤 𐑚𐑰 𐑩𐑤𐑲𐑝 𐑑 𐑮𐑦𐑜𐑮𐑧𐑑 𐑦𐑑. 𐑚𐑳𐑑 𐑚𐑦𐑒𐑪𐑟 𐑕𐑲𐑩𐑯𐑕 𐑮𐑧𐑕𐑑𐑕 𐑩𐑐𐑪𐑯 𐑥𐑲 𐑣𐑿𐑥𐑩𐑯 𐑦𐑯𐑑𐑧𐑤𐑦𐑡𐑩𐑯𐑕, 𐑦𐑑 𐑦𐑟 𐑞 𐑐𐑬𐑼 𐑞𐑨𐑑 𐑒𐑨𐑯𐑪𐑑 𐑚𐑰 𐑮𐑦𐑥𐑵𐑝𐑛 𐑓𐑮𐑪𐑥 𐑥𐑰 𐑢𐑦𐑞𐑬𐑑 𐑮𐑦𐑥𐑵𐑝𐑦𐑙 \emph{𐑥𐑰}. 𐑰𐑝𐑩𐑯 𐑦𐑓 𐑞 𐑤𐑷𐑟 𐑝 𐑞 𐑿𐑯𐑦𐑝𐑻𐑕 𐑗𐑱𐑯𐑡 𐑪𐑯 𐑥𐑰, 𐑕𐑴 𐑞𐑨𐑑 𐑷𐑤 𐑥𐑲 𐑯𐑪𐑤𐑦𐑡 𐑦𐑟 𐑝𐑶𐑛, 𐑲'𐑤 𐑡𐑳𐑕𐑑 𐑓𐑦𐑜𐑼 𐑬𐑑 𐑞 𐑯𐑿 𐑤𐑷𐑟, 𐑨𐑟 𐑣𐑨𐑟 𐑚𐑰𐑯 𐑛𐑳𐑯 𐑚𐑦𐑓𐑹. 𐑦𐑑'𐑕 𐑯𐑪𐑑 𐑩 \emph{·𐑥𐑳𐑜𐑩𐑤} 𐑔𐑦𐑙, 𐑦𐑑'𐑕 𐑩 \emph{𐑣𐑿𐑥𐑩𐑯} 𐑔𐑦𐑙, 𐑦𐑑 𐑡𐑳𐑕𐑑 𐑮𐑦𐑓𐑲𐑯𐑟 𐑯 𐑑𐑮𐑱𐑯𐑟 𐑞 𐑐𐑬𐑼 𐑿 𐑿𐑟 𐑧𐑝𐑮𐑦 𐑑𐑲𐑥 𐑿 𐑤𐑫𐑒 𐑨𐑑 𐑕𐑳𐑥𐑔𐑦𐑙 𐑿 𐑛𐑴𐑯𐑑 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑯 𐑭𐑕𐑒 '𐑢𐑲?' 𐑿'𐑼 𐑝 ·𐑕𐑤𐑲𐑔𐑼𐑦𐑯, ·𐑛𐑮𐑱𐑒𐑴, 𐑛𐑴𐑯𐑑 𐑿 𐑕𐑰 𐑞 𐑦𐑥𐑐𐑤𐑦𐑒𐑱𐑖𐑩𐑯?”

·𐑛𐑮𐑱𐑒𐑴 𐑤𐑫𐑒𐑑 𐑳𐑐 𐑓𐑮𐑪𐑥 𐑞 𐑚𐑫𐑒 𐑑 ·𐑣𐑨𐑮𐑦. 𐑣𐑦𐑟 𐑓𐑱𐑕 𐑖𐑴𐑛 𐑛𐑷𐑯𐑦𐑙 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛𐑦𐑙. “·𐑢𐑦𐑟𐑼𐑛𐑟 𐑒𐑨𐑯 𐑤𐑻𐑯 𐑑 𐑿𐑟 𐑞𐑦𐑕 𐑐𐑬𐑼.”

𐑝𐑧𐑮𐑦 𐑒𐑺𐑓𐑩𐑤𐑦, 𐑯𐑬…𐑞 𐑚𐑱𐑑 𐑦𐑟 𐑕𐑧𐑑, 𐑯𐑬 𐑞 𐑣𐑫𐑒…“𐑦𐑓 𐑿 𐑒𐑨𐑯 𐑤𐑻𐑯 𐑑 𐑔𐑦𐑙𐑒 𐑝 𐑘𐑹𐑕𐑧𐑤𐑓 𐑨𐑟 𐑩 \emph{𐑣𐑿𐑥𐑩𐑯} 𐑦𐑯𐑕𐑑𐑧𐑛 𐑝 𐑩 \emph{𐑢𐑦𐑟𐑼𐑛} 𐑞𐑧𐑯 𐑿 𐑒𐑨𐑯 𐑑𐑮𐑱𐑯 𐑯 𐑮𐑦𐑓𐑲𐑯 𐑘𐑹 𐑐𐑬𐑼𐑟 𐑨𐑟 𐑩 𐑣𐑿𐑥𐑩𐑯.”

𐑯 𐑦𐑓 \emph{𐑞𐑨𐑑} 𐑦𐑯𐑕𐑑𐑮𐑳𐑒𐑖𐑩𐑯 𐑢𐑪𐑟𐑩𐑯𐑑 𐑦𐑯 \emph{𐑧𐑝𐑮𐑦} 𐑕𐑲𐑩𐑯𐑕 𐑒𐑼𐑦𐑒𐑿𐑤𐑩𐑥, ·𐑛𐑮𐑱𐑒𐑴 𐑛𐑦𐑛𐑩𐑯𐑑 𐑯𐑰𐑛 𐑑 𐑯𐑴 𐑦𐑑, 𐑛𐑦𐑛 𐑣𐑰?

·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑲𐑟 𐑢𐑻 𐑯𐑬 𐑔𐑷𐑑𐑓𐑩𐑤. “𐑿'𐑝…𐑷𐑤𐑮𐑧𐑛𐑦 𐑛𐑳𐑯 𐑞𐑦𐑕?”

“𐑑 𐑕𐑳𐑥 𐑦𐑒𐑕𐑑𐑧𐑯𐑑,” ·𐑣𐑨𐑮𐑦 𐑩𐑤𐑬𐑛. “𐑥𐑲 𐑑𐑮𐑱𐑯𐑦𐑙 𐑦𐑟𐑩𐑯𐑑 𐑒𐑩𐑥𐑐𐑤𐑰𐑑. 𐑯𐑪𐑑 𐑨𐑑 𐑦𐑤𐑧𐑝𐑩𐑯. 𐑚𐑳𐑑—𐑥𐑲 𐑓𐑭𐑞𐑼 \emph{𐑷𐑤𐑕𐑴} 𐑚𐑷𐑑 𐑥𐑰 𐑑𐑿𐑑𐑼𐑟, 𐑿 𐑕𐑰.” 𐑖𐑫𐑼, 𐑞𐑱'𐑛 𐑚𐑰𐑯 𐑕𐑑𐑸𐑝𐑦𐑙 𐑜𐑮𐑨𐑛 𐑕𐑑𐑿𐑛𐑩𐑯𐑑𐑕, 𐑯 𐑦𐑑 𐑣𐑨𐑛 𐑴𐑯𐑤𐑦 𐑚𐑰𐑯 𐑚𐑦𐑒𐑪𐑟 ·𐑣𐑨𐑮𐑦 𐑕𐑤𐑧𐑐𐑑 𐑪𐑯 𐑩 26-𐑬𐑼 𐑕𐑲𐑒𐑩𐑤, 𐑚𐑳𐑑 𐑤𐑰𐑝 𐑷𐑤 𐑞𐑨𐑑 𐑩𐑕𐑲𐑛 𐑓 𐑯𐑬…

·𐑕𐑤𐑴𐑤𐑦, ·𐑛𐑮𐑱𐑒𐑴 𐑯𐑪𐑛𐑩𐑛. “𐑿 𐑔𐑦𐑙𐑒 𐑿 𐑒𐑨𐑯 𐑥𐑭𐑕𐑑𐑼 \emph{𐑚𐑴𐑔} 𐑸𐑑𐑕, 𐑨𐑛 𐑞 𐑐𐑬𐑼𐑟 𐑑𐑩𐑜𐑧𐑞𐑼, 𐑯…” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑑𐑺𐑛 𐑨𐑑 ·𐑣𐑨𐑮𐑦. “𐑥𐑱𐑒 𐑘𐑹𐑕𐑧𐑤𐑓 ·𐑤𐑹𐑛 𐑝 𐑞 𐑑𐑵 𐑢𐑻𐑤𐑛𐑟?”

·𐑣𐑨𐑮𐑦 𐑜𐑱𐑝 𐑩𐑯 𐑰𐑝𐑩𐑤 𐑤𐑭𐑓, 𐑦𐑑 𐑡𐑳𐑕𐑑 𐑕𐑰𐑥𐑛 𐑑 𐑒𐑳𐑥 𐑯𐑨𐑗𐑼𐑩𐑤𐑦 𐑨𐑑 𐑞𐑨𐑑 𐑐𐑶𐑯𐑑. “𐑿 𐑣𐑨𐑓 𐑑 𐑮𐑾𐑤𐑲𐑟, ·𐑛𐑮𐑱𐑒𐑴, 𐑞𐑨𐑑 𐑞 𐑣𐑴𐑤 𐑢𐑻𐑤𐑛 𐑿 𐑯𐑴, 𐑷𐑤 𐑝 ·𐑥𐑨𐑡𐑦𐑒𐑩𐑤 ·𐑚𐑮𐑦𐑑𐑩𐑯, 𐑦𐑟 𐑡𐑳𐑕𐑑 𐑢𐑳𐑯 𐑕𐑒𐑢𐑺 𐑪𐑯 𐑩 𐑥𐑳𐑗 𐑤𐑸𐑡𐑼 𐑜𐑱𐑥 𐑚𐑹𐑛. 𐑞 𐑜𐑱𐑥 𐑚𐑹𐑛 𐑞𐑨𐑑 𐑦𐑯𐑒𐑤𐑵𐑛𐑟 𐑐𐑤𐑱𐑕𐑩𐑟 𐑤𐑲𐑒 𐑞 ·𐑥𐑵𐑯, 𐑯 𐑞 𐑕𐑑𐑸𐑟 𐑦𐑯 𐑞 𐑯𐑲𐑑 𐑕𐑒𐑲, 𐑢𐑦𐑗 𐑸 𐑤𐑲𐑑𐑕 𐑡𐑳𐑕𐑑 𐑤𐑲𐑒 𐑞 ·𐑕𐑳𐑯 𐑴𐑯𐑤𐑦 𐑳𐑯𐑦𐑥𐑨𐑡𐑦𐑯𐑩𐑚𐑤𐑦 𐑓𐑸 𐑩𐑢𐑱, 𐑯 𐑔𐑦𐑙𐑟 𐑤𐑲𐑒 𐑜𐑨𐑤𐑩𐑒𐑕𐑦𐑟 𐑞𐑨𐑑 𐑸 𐑝𐑭𐑕𐑑𐑤𐑦 𐑣𐑿𐑡𐑼 𐑞𐑨𐑯 𐑞 ·𐑻𐑔 𐑯 ·𐑕𐑳𐑯, 𐑔𐑦𐑙𐑟 𐑕𐑴 𐑤𐑸𐑡 𐑞𐑨𐑑 𐑴𐑯𐑤𐑦 𐑕𐑲𐑩𐑯𐑑𐑦𐑕𐑑𐑕 𐑒𐑨𐑯 𐑕𐑰 𐑞𐑧𐑥 𐑯 𐑿 𐑛𐑴𐑯𐑑 𐑰𐑝𐑩𐑯 𐑯𐑴 𐑞𐑱 𐑦𐑜𐑟𐑦𐑕𐑑. 𐑚𐑳𐑑 𐑲 𐑮𐑾𐑤𐑦 \emph{𐑨𐑥} ·𐑮𐑱𐑝𐑩𐑯𐑒𐑤𐑷, 𐑿 𐑯𐑴, 𐑯𐑪𐑑 ·𐑕𐑤𐑲𐑔𐑼𐑦𐑯. 𐑲 𐑛𐑴𐑯𐑑 𐑢𐑪𐑯𐑑 𐑑 𐑮𐑵𐑤 𐑞 𐑿𐑯𐑦𐑝𐑻𐑕. 𐑲 𐑡𐑳𐑕𐑑 𐑔𐑦𐑙𐑒 𐑦𐑑 𐑒𐑫𐑛 𐑚𐑰 𐑥𐑹 𐑕𐑧𐑯𐑕𐑩𐑚𐑤𐑦 𐑹𐑜𐑩𐑯𐑲𐑟𐑛.”

𐑞𐑺 𐑢𐑪𐑟 𐑷 𐑪𐑯 ·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑓𐑱𐑕. “𐑢𐑲 𐑸 𐑿 𐑑𐑧𐑤𐑦𐑙 \emph{𐑥𐑰} 𐑞𐑦𐑕?”

“𐑴…𐑞𐑺 𐑸𐑯𐑑 𐑥𐑧𐑯𐑦 𐑐𐑰𐑐𐑩𐑤 𐑣𐑵 𐑯𐑴 𐑣𐑬 𐑑 𐑛𐑵 \emph{𐑑𐑮𐑵} 𐑕𐑲𐑩𐑯𐑕—𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛𐑦𐑙 𐑕𐑳𐑥𐑔𐑦𐑙 𐑓 𐑞 𐑝𐑧𐑮𐑦 𐑓𐑻𐑕𐑑 𐑑𐑲𐑥, 𐑰𐑝𐑩𐑯 𐑦𐑓 𐑦𐑑 𐑒𐑩𐑯𐑓𐑿𐑟𐑩𐑟 𐑞 𐑣𐑧𐑤 𐑬𐑑 𐑝 𐑿. 𐑣𐑧𐑤𐑐 𐑢𐑫𐑛 𐑚𐑰 𐑣𐑧𐑤𐑐𐑓𐑩𐑤.”

·𐑛𐑮𐑱𐑒𐑴 𐑕𐑑𐑺𐑛 𐑨𐑑 ·𐑣𐑨𐑮𐑦 𐑢𐑦𐑞 𐑣𐑦𐑟 𐑥𐑬𐑔 𐑴𐑐𐑩𐑯.

“𐑚𐑳𐑑 𐑥𐑱𐑒 𐑯𐑴 𐑥𐑦𐑕𐑑𐑱𐑒, ·𐑛𐑮𐑱𐑒𐑴, 𐑑𐑮𐑵 𐑕𐑲𐑩𐑯𐑕 𐑮𐑾𐑤𐑦 \emph{𐑦𐑟𐑩𐑯𐑑} 𐑤𐑲𐑒 𐑥𐑨𐑡𐑦𐑒, 𐑿 𐑒𐑭𐑯𐑑 𐑡𐑳𐑕𐑑 𐑛𐑵 𐑦𐑑 𐑯 𐑢𐑷𐑒 𐑩𐑢𐑱 𐑳𐑯𐑗𐑱𐑯𐑡𐑛 𐑤𐑲𐑒 𐑤𐑻𐑯𐑦𐑙 𐑣𐑬 𐑑 𐑕𐑱 𐑞 𐑢𐑻𐑛𐑟 𐑝 𐑩 𐑯𐑿 𐑕𐑐𐑧𐑤. 𐑞 𐑐𐑬𐑼 𐑒𐑳𐑥𐑟 𐑢𐑦𐑞 𐑩 𐑒𐑪𐑕𐑑, 𐑩 𐑒𐑪𐑕𐑑 𐑕𐑴 𐑣𐑲 𐑞𐑨𐑑 𐑥𐑴𐑕𐑑 𐑐𐑰𐑐𐑩𐑤 𐑮𐑦𐑓𐑿𐑟 𐑑 𐑐𐑱 𐑦𐑑.”

·𐑛𐑮𐑱𐑒𐑴 𐑯𐑪𐑛𐑩𐑛 𐑨𐑑 𐑞𐑦𐑕 𐑨𐑟 𐑞𐑴, 𐑓𐑲𐑯𐑩𐑤𐑦, 𐑣𐑰'𐑛 𐑣𐑻𐑛 𐑕𐑳𐑥𐑔𐑦𐑙 𐑣𐑰 𐑒𐑫𐑛 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛. “𐑯 𐑞𐑨𐑑 𐑒𐑪𐑕𐑑?”

“𐑤𐑻𐑯𐑦𐑙 𐑑 𐑩𐑛𐑥𐑦𐑑 𐑿'𐑼 𐑮𐑪𐑙.”

“𐑳𐑥,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛 𐑭𐑓𐑑𐑼 𐑞 𐑛𐑮𐑩𐑥𐑨𐑑𐑦𐑒 𐑐𐑷𐑟 𐑣𐑨𐑛 𐑕𐑑𐑮𐑧𐑗𐑑 𐑪𐑯 𐑓 𐑩 𐑢𐑲𐑤. “𐑿 𐑜𐑴𐑦𐑙 𐑑 𐑦𐑒𐑕𐑐𐑤𐑱𐑯 𐑞𐑨𐑑?”

“𐑑𐑮𐑲𐑦𐑙 𐑑 𐑓𐑦𐑜𐑼 𐑬𐑑 𐑣𐑬 𐑕𐑳𐑥𐑔𐑦𐑙 𐑢𐑻𐑒𐑕 𐑪𐑯 𐑞𐑨𐑑 𐑛𐑰𐑐 𐑤𐑧𐑝𐑩𐑤, 𐑞 𐑓𐑻𐑕𐑑 𐑯𐑲𐑯𐑑𐑦-𐑯𐑲𐑯 𐑧𐑒𐑕𐑐𐑤𐑩𐑯𐑱𐑖𐑩𐑯𐑟 𐑿 𐑒𐑳𐑥 𐑳𐑐 𐑢𐑦𐑞 𐑸 𐑮𐑪𐑙. 𐑞 𐑣𐑳𐑯𐑛𐑮𐑩𐑛𐑔 𐑦𐑟 𐑮𐑲𐑑. 𐑕𐑴 𐑿 𐑣𐑨𐑓 𐑑 𐑤𐑻𐑯 𐑣𐑬 𐑑 𐑩𐑛𐑥𐑦𐑑 𐑿'𐑼 𐑮𐑪𐑙, 𐑴𐑝𐑼 𐑯 𐑴𐑝𐑼 𐑯 𐑴𐑝𐑼 𐑩𐑜𐑱𐑯. 𐑦𐑑 𐑛𐑳𐑟𐑩𐑯𐑑 𐑕𐑬𐑯𐑛 𐑤𐑲𐑒 𐑥𐑳𐑗, 𐑚𐑳𐑑 𐑦𐑑'𐑕 𐑕𐑴 𐑣𐑸𐑛 𐑞𐑨𐑑 𐑥𐑴𐑕𐑑 𐑐𐑰𐑐𐑩𐑤 𐑒𐑭𐑯𐑑 𐑛𐑵 𐑕𐑲𐑩𐑯𐑕. 𐑷𐑤𐑢𐑱𐑟 𐑒𐑢𐑧𐑕𐑗𐑩𐑯𐑦𐑙 𐑘𐑹𐑕𐑧𐑤𐑓, 𐑷𐑤𐑢𐑱𐑟 𐑑𐑱𐑒𐑦𐑙 𐑩𐑯𐑳𐑞𐑼 𐑤𐑫𐑒 𐑨𐑑 𐑔𐑦𐑙𐑟 𐑿'𐑝 𐑷𐑤𐑢𐑱𐑟 𐑑𐑱𐑒𐑩𐑯 𐑓 𐑜𐑮𐑭𐑯𐑑𐑩𐑛,” 𐑤𐑲𐑒 𐑣𐑨𐑝𐑦𐑙 𐑩 ·𐑕𐑯𐑦𐑗 𐑦𐑯 ·𐑒𐑢𐑦𐑛𐑦𐑗, “𐑯 𐑧𐑝𐑮𐑦 𐑑𐑲𐑥 𐑿 𐑗𐑱𐑯𐑡 𐑘𐑹 𐑥𐑲𐑯𐑛, 𐑿 𐑗𐑱𐑯𐑡 𐑘𐑹𐑕𐑧𐑤𐑓. 𐑚𐑳𐑑 𐑲'𐑥 𐑜𐑧𐑑𐑦𐑙 𐑢𐑱 𐑩𐑣𐑧𐑛 𐑝 𐑥𐑲𐑕𐑧𐑤𐑓 𐑣𐑽. 𐑢𐑱 𐑩𐑣𐑧𐑛 𐑝 𐑥𐑲𐑕𐑧𐑤𐑓. 𐑲 𐑡𐑳𐑕𐑑 𐑢𐑪𐑯𐑑 𐑿 𐑑 𐑯𐑴…𐑲'𐑥 𐑪𐑓𐑼𐑦𐑙 𐑑 𐑖𐑺 𐑕𐑳𐑥 𐑝 𐑥𐑲 𐑯𐑪𐑤𐑦𐑡. 𐑦𐑓 𐑿 𐑢𐑪𐑯𐑑. 𐑞𐑺'𐑟 𐑡𐑳𐑕𐑑 𐑢𐑳𐑯 𐑒𐑩𐑯𐑛𐑦𐑖𐑩𐑯.”

“𐑳 𐑣𐑳,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛. “𐑿 𐑯𐑴, ·𐑓𐑭𐑞𐑼 𐑕𐑧𐑟 𐑞𐑨𐑑 𐑢𐑧𐑯 𐑕𐑳𐑥𐑢𐑳𐑯 𐑕𐑧𐑟 𐑞𐑨𐑑 𐑑 𐑿, 𐑦𐑑 𐑦𐑟 𐑯𐑧𐑝𐑼 𐑩 𐑜𐑫𐑛 𐑕𐑲𐑯, 𐑧𐑝𐑼.”

·𐑣𐑨𐑮𐑦 𐑯𐑪𐑛𐑩𐑛. “𐑯𐑬, 𐑛𐑴𐑯𐑑 𐑥𐑦𐑕𐑑𐑱𐑒 𐑥𐑰 𐑯 𐑔𐑦𐑙𐑒 𐑞𐑨𐑑 𐑲'𐑥 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑛𐑮𐑲𐑝 𐑩 𐑢𐑧𐑡 𐑚𐑦𐑑𐑢𐑰𐑯 𐑿 𐑯 𐑘𐑹 𐑓𐑭𐑞𐑼. 𐑦𐑑'𐑕 𐑯𐑪𐑑 𐑩𐑚𐑬𐑑 𐑞𐑨𐑑. 𐑦𐑑'𐑕 𐑡𐑳𐑕𐑑 𐑩𐑚𐑬𐑑 𐑥𐑰 𐑢𐑪𐑯𐑑𐑦𐑙 𐑑 𐑛𐑰𐑤 𐑢𐑦𐑞 𐑕𐑳𐑥𐑢𐑳𐑯 𐑥𐑲 𐑴𐑯 𐑱𐑡, 𐑮𐑭𐑞𐑼 𐑞𐑨𐑯 𐑣𐑨𐑝𐑦𐑙 𐑞𐑦𐑕 𐑚𐑰 𐑚𐑦𐑑𐑢𐑰𐑯 𐑥𐑰 𐑯 ·𐑤𐑵𐑕𐑾𐑕. 𐑲 𐑔𐑦𐑙𐑒 𐑘𐑹 𐑓𐑭𐑞𐑼 𐑢𐑫𐑛 𐑚𐑰 𐑴𐑒𐑱 𐑢𐑦𐑞 𐑞𐑨𐑑 𐑑𐑵, 𐑣𐑰 𐑯𐑴𐑟 𐑿 𐑣𐑨𐑓 𐑑 𐑜𐑮𐑴 𐑳𐑐 𐑕𐑳𐑥𐑑𐑲𐑥. 𐑚𐑳𐑑 𐑘𐑹 𐑥𐑵𐑝𐑟 𐑦𐑯 𐑬𐑼 𐑜𐑱𐑥 𐑣𐑨𐑓 𐑑 𐑚𐑰 𐑘𐑹 𐑴𐑯. 𐑞𐑨𐑑'𐑕 𐑥𐑲 𐑒𐑩𐑯𐑛𐑦𐑖𐑩𐑯—𐑞𐑨𐑑 𐑲'𐑥 𐑛𐑰𐑤𐑦𐑙 𐑢𐑦𐑞 𐑿, ·𐑛𐑮𐑱𐑒𐑴, 𐑯𐑪𐑑 𐑘𐑹 𐑓𐑭𐑞𐑼.”

“𐑲'𐑝 𐑜𐑪𐑑 𐑑 𐑜𐑴,” ·𐑛𐑮𐑱𐑒𐑴 𐑕𐑧𐑛. 𐑣𐑰 𐑕𐑑𐑫𐑛 𐑳𐑐. “𐑲'𐑝 𐑜𐑪𐑑 𐑑 𐑜𐑴 𐑪𐑓 𐑯 𐑔𐑦𐑙𐑒 𐑩𐑚𐑬𐑑 𐑞𐑦𐑕.”

“𐑑𐑱𐑒 𐑘𐑹 𐑑𐑲𐑥,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛.

𐑞 𐑕𐑬𐑯𐑛𐑟 𐑝 𐑞 𐑑𐑮𐑱𐑯 𐑐𐑤𐑨𐑑𐑓𐑹𐑥 𐑗𐑱𐑯𐑡𐑛 𐑓𐑮𐑪𐑥 𐑚𐑤𐑻𐑟 𐑦𐑯𐑑𐑵 𐑥𐑻𐑥𐑼𐑟 𐑨𐑟 ·𐑛𐑮𐑱𐑒𐑴 𐑢𐑪𐑯𐑛𐑼𐑛 𐑪𐑓.

·𐑣𐑨𐑮𐑦 𐑕𐑤𐑴𐑤𐑦 𐑧𐑒𐑕𐑣𐑱𐑤𐑛 𐑞 𐑺 𐑣𐑰'𐑛 𐑚𐑰𐑯 𐑣𐑴𐑤𐑛𐑦𐑙 𐑦𐑯 𐑢𐑦𐑞𐑬𐑑 𐑒𐑢𐑲𐑑 𐑮𐑾𐑤𐑲𐑟𐑦𐑙 𐑦𐑑, 𐑯 𐑞𐑧𐑯 𐑤𐑫𐑒𐑑 𐑨𐑑 𐑞 𐑢𐑪𐑗 𐑪𐑯 𐑣𐑦𐑟 𐑮𐑦𐑕𐑑, 𐑩 𐑕𐑦𐑥𐑐𐑩𐑤 𐑥𐑦𐑒𐑨𐑯𐑦𐑒𐑩𐑤 𐑥𐑪𐑛𐑩𐑤 𐑞𐑨𐑑 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑣𐑨𐑛 𐑚𐑷𐑑 𐑣𐑦𐑥 𐑦𐑯 𐑣𐑴𐑐 𐑦𐑑 𐑢𐑫𐑛 𐑢𐑻𐑒 𐑦𐑯 𐑥𐑨𐑡𐑦𐑒'𐑕 𐑐𐑮𐑧𐑟𐑩𐑯𐑕. 𐑞 𐑕𐑱𐑒𐑪𐑯𐑛-𐑣𐑨𐑯𐑛 𐑢𐑪𐑟 𐑕𐑑𐑦𐑤 𐑑𐑦𐑒𐑦𐑙, 𐑯 𐑦𐑓 𐑞 𐑥𐑦𐑯𐑦𐑑 𐑣𐑨𐑯𐑛 𐑢𐑪𐑟 𐑮𐑲𐑑, 𐑞𐑧𐑯 𐑦𐑑 𐑢𐑪𐑟𐑩𐑯𐑑 𐑒𐑢𐑲𐑑 𐑦𐑤𐑧𐑝𐑩𐑯 𐑡𐑳𐑕𐑑 𐑘𐑧𐑑. 𐑣𐑰 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑷𐑑 𐑑 𐑜𐑧𐑑 𐑪𐑯 𐑞 𐑑𐑮𐑱𐑯 𐑕𐑵𐑯 𐑯 𐑕𐑑𐑸𐑑 𐑤𐑫𐑒𐑦𐑙 𐑓 𐑢𐑪𐑑𐑕𐑣𐑻𐑓𐑱𐑕, 𐑚𐑳𐑑 𐑦𐑑 𐑕𐑰𐑥𐑛 𐑢𐑻𐑔 𐑑𐑱𐑒𐑦𐑙 𐑩 𐑓𐑿 𐑥𐑦𐑯𐑦𐑑𐑕 𐑓𐑻𐑕𐑑 𐑑 𐑛𐑵 𐑕𐑳𐑥 𐑚𐑮𐑰𐑞𐑦𐑙 𐑧𐑒𐑕𐑼𐑕𐑲𐑟𐑩𐑟 𐑯 𐑕𐑰 𐑦𐑓 𐑣𐑦𐑟 𐑚𐑤𐑳𐑛 𐑢𐑹𐑥𐑛 𐑳𐑐 𐑩𐑜𐑱𐑯.

𐑚𐑳𐑑 𐑢𐑧𐑯 ·𐑣𐑨𐑮𐑦 𐑤𐑫𐑒𐑑 𐑳𐑐 𐑓𐑮𐑪𐑥 𐑣𐑦𐑟 𐑢𐑪𐑗, 𐑣𐑰 𐑕𐑷 𐑑𐑵 𐑓𐑦𐑜𐑼𐑟 𐑩𐑐𐑮𐑴𐑗𐑦𐑙, 𐑤𐑫𐑒𐑦𐑙 𐑳𐑑𐑼𐑤𐑦 𐑮𐑦𐑛𐑦𐑒𐑿𐑤𐑩𐑕 𐑢𐑦𐑞 𐑞𐑺 𐑓𐑱𐑕𐑩𐑟 𐑒𐑤𐑴𐑒𐑑 𐑚𐑲 𐑢𐑦𐑯𐑑𐑼 𐑕𐑒𐑸𐑝𐑟.

“𐑣𐑧𐑤𐑴, ·𐑥𐑼~·𐑚𐑮𐑪𐑯𐑟,” 𐑕𐑧𐑛 𐑢𐑳𐑯 𐑝 𐑞 𐑥𐑭𐑕𐑒𐑑 𐑓𐑦𐑜𐑼𐑟. “𐑒𐑨𐑯 𐑢𐑰 𐑦𐑯𐑑𐑼𐑩𐑕𐑑 𐑿 𐑦𐑯 𐑡𐑶𐑯𐑦𐑙 𐑞 ·𐑹𐑛𐑼 𐑝 ·𐑒𐑱𐑪𐑕?”

\latersection{Aftermath}

𐑯𐑪𐑑 𐑑𐑵 𐑤𐑪𐑙 𐑭𐑓𐑑𐑼 𐑞𐑨𐑑, 𐑢𐑧𐑯 𐑷𐑤 𐑞𐑨𐑑 𐑛𐑱'𐑟 𐑓𐑳𐑕 𐑣𐑨𐑛 𐑓𐑲𐑯𐑩𐑤𐑦 𐑕𐑩𐑚𐑕𐑲𐑛𐑩𐑛, ·𐑛𐑮𐑱𐑒𐑴 𐑢𐑪𐑟 𐑚𐑧𐑯𐑑 𐑴𐑝𐑼 𐑩 𐑛𐑧𐑕𐑒 𐑢𐑦𐑞 𐑒𐑢𐑦𐑤 𐑦𐑯 𐑣𐑨𐑯𐑛. 𐑣𐑰 𐑣𐑨𐑛 𐑩 𐑐𐑮𐑲𐑝𐑩𐑑 𐑮𐑵𐑥 𐑦𐑯 𐑞 ·𐑕𐑤𐑲𐑔𐑼𐑦𐑯 𐑛𐑳𐑯𐑡𐑩𐑯𐑟, 𐑢𐑦𐑞 𐑦𐑑𐑕 𐑴𐑯 𐑛𐑧𐑕𐑒 𐑯 𐑦𐑑𐑕 𐑴𐑯 𐑓𐑲𐑼—𐑕𐑨𐑛𐑤𐑦 𐑯𐑪𐑑 𐑰𐑝𐑩𐑯 \emph{𐑣𐑰} 𐑮𐑱𐑑𐑩𐑛 𐑩 𐑒𐑩𐑯𐑧𐑒𐑖𐑩𐑯 𐑑 𐑞 ·𐑓𐑤𐑵 𐑕𐑦𐑕𐑑𐑩𐑥, 𐑚𐑳𐑑 𐑨𐑑 𐑤𐑰𐑕𐑑 ·𐑕𐑤𐑲𐑔𐑼𐑦𐑯 𐑛𐑦𐑛𐑩𐑯𐑑 𐑚𐑲 𐑦𐑯𐑑𐑵 𐑞𐑨𐑑 𐑳𐑑𐑼 𐑯𐑪𐑯𐑕𐑧𐑯𐑕 𐑩𐑚𐑬𐑑 𐑥𐑱𐑒𐑦𐑙 \emph{𐑧𐑝𐑮𐑦𐑢𐑳𐑯} 𐑕𐑤𐑰𐑐 𐑦𐑯 𐑛𐑹𐑥𐑟. 𐑞𐑺 𐑢𐑻𐑯𐑑 𐑥𐑧𐑯𐑦 𐑐𐑮𐑲𐑝𐑩𐑑 𐑮𐑵𐑥𐑟, 𐑿 𐑣𐑨𐑛 𐑑 𐑚𐑰 𐑞 \emph{𐑝𐑧𐑮𐑦} 𐑚𐑧𐑕𐑑 𐑢𐑦𐑞𐑦𐑯 𐑞 ·𐑣𐑬𐑕 𐑝 𐑞 𐑚𐑧𐑑𐑼 𐑕𐑹𐑑, 𐑚𐑳𐑑 𐑞𐑨𐑑 𐑒𐑫𐑛 𐑚𐑰 𐑑𐑱𐑒𐑩𐑯 𐑓 𐑜𐑮𐑭𐑯𐑑𐑩𐑛 𐑢𐑦𐑞 𐑞 ·𐑣𐑬𐑕 𐑝 ·𐑥𐑨𐑤𐑓𐑶.

\emph{𐑛𐑽 ·𐑓𐑭𐑞𐑼,} ·𐑛𐑮𐑱𐑒𐑴 𐑮𐑴𐑑.

𐑯 𐑞𐑧𐑯 𐑣𐑰 𐑕𐑑𐑪𐑐𐑑.

𐑦𐑙𐑒 𐑕𐑤𐑴𐑤𐑦 𐑛𐑮𐑦𐑐𐑑 𐑓𐑮𐑪𐑥 𐑣𐑦𐑟 𐑒𐑢𐑦𐑤, 𐑕𐑑𐑱𐑯𐑦𐑙 𐑞 𐑐𐑸𐑗𐑥𐑩𐑯𐑑 𐑯𐑽 𐑞 𐑢𐑻𐑛𐑟.

·𐑛𐑮𐑱𐑒𐑴 𐑢𐑪𐑟𐑩𐑯𐑑 𐑕𐑑𐑿𐑐𐑦𐑛. 𐑣𐑰 𐑢𐑪𐑟 𐑘𐑳𐑙, 𐑚𐑳𐑑 𐑣𐑦𐑟 𐑑𐑿𐑑𐑼𐑟 𐑣𐑨𐑛 𐑑𐑮𐑱𐑯𐑛 𐑣𐑦𐑥 𐑢𐑧𐑤. ·𐑛𐑮𐑱𐑒𐑴 𐑯𐑿 𐑞𐑨𐑑 ·𐑐𐑪𐑑𐑼 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑓𐑧𐑤𐑑 𐑩 𐑤𐑪𐑑 𐑥𐑹 𐑕𐑦𐑥𐑐𐑩𐑔𐑦 𐑑𐑩𐑢𐑹𐑛𐑟 ·𐑛𐑳𐑥𐑚𐑩𐑤𐑛𐑹'𐑟 𐑓𐑨𐑒𐑖𐑩𐑯 𐑞𐑨𐑯 ·𐑐𐑪𐑑𐑼 𐑢𐑪𐑟 𐑤𐑧𐑑𐑦𐑙 𐑪𐑯…𐑞𐑴 ·𐑛𐑮𐑱𐑒𐑴 𐑛𐑦𐑛 𐑔𐑦𐑙𐑒 ·𐑐𐑪𐑑𐑼 𐑒𐑫𐑛 𐑚𐑰 𐑑𐑧𐑥𐑐𐑑𐑩𐑛. 𐑚𐑳𐑑 𐑦𐑑 𐑢𐑪𐑟 𐑒𐑮𐑦𐑕𐑑𐑩𐑤 𐑒𐑤𐑽 𐑞𐑨𐑑 ·𐑐𐑪𐑑𐑼 𐑢𐑪𐑟 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑑𐑧𐑥𐑐𐑑 ·𐑛𐑮𐑱𐑒𐑴 𐑡𐑳𐑕𐑑 𐑨𐑟 ·𐑛𐑮𐑱𐑒𐑴 𐑢𐑪𐑟 𐑑𐑮𐑲𐑦𐑙 𐑑 𐑑𐑧𐑥𐑐𐑑 𐑣𐑦𐑥.

𐑯 𐑦𐑑 𐑢𐑪𐑟 𐑷𐑤𐑕𐑴 𐑒𐑤𐑽 𐑞𐑨𐑑 ·𐑐𐑪𐑑𐑼 𐑢𐑪𐑟 𐑚𐑮𐑦𐑤𐑘𐑩𐑯𐑑, 𐑯 𐑩 𐑣𐑴𐑤 𐑤𐑪𐑑 𐑥𐑹 𐑞𐑨𐑯 𐑡𐑳𐑕𐑑 𐑕𐑤𐑲𐑑𐑤𐑦 𐑥𐑨𐑛, 𐑯 𐑐𐑤𐑱𐑦𐑙 𐑩 𐑝𐑭𐑕𐑑 𐑜𐑱𐑥 𐑞𐑨𐑑 ·𐑐𐑪𐑑𐑼 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑥𐑴𐑕𐑑𐑤𐑦 𐑛𐑦𐑛𐑩𐑯𐑑 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛, 𐑦𐑥𐑐𐑮𐑩𐑝𐑲𐑟𐑛 𐑨𐑑 𐑑𐑪𐑐 𐑕𐑐𐑰𐑛 𐑢𐑦𐑞 𐑞 𐑕𐑳𐑑𐑩𐑤𐑑𐑦 𐑝 𐑩 𐑮𐑨𐑥𐑐𐑱𐑡𐑦𐑙 𐑯𐑳𐑯𐑛𐑵. 𐑚𐑳𐑑 ·𐑐𐑪𐑑𐑼 𐑣𐑨𐑛 𐑥𐑨𐑯𐑦𐑡𐑛 𐑑 𐑗𐑵𐑟 𐑩 𐑑𐑨𐑒𐑑𐑦𐑒 𐑞𐑨𐑑 ·𐑛𐑮𐑱𐑒𐑴 𐑒𐑫𐑛𐑩𐑯𐑑 𐑡𐑳𐑕𐑑 𐑢𐑷𐑒 𐑩𐑢𐑱 𐑓𐑮𐑪𐑥. 𐑣𐑰 𐑣𐑨𐑛 𐑪𐑓𐑼𐑛 ·𐑛𐑮𐑱𐑒𐑴 𐑩 𐑐𐑸𐑑 𐑝 𐑣𐑦𐑟 𐑴𐑯 𐑐𐑬𐑼, 𐑜𐑨𐑥𐑚𐑩𐑤𐑦𐑙 𐑞𐑨𐑑 ·𐑛𐑮𐑱𐑒𐑴 𐑒𐑫𐑛𐑩𐑯𐑑 𐑿𐑟 𐑦𐑑 𐑢𐑦𐑞𐑬𐑑 𐑚𐑦𐑒𐑳𐑥𐑦𐑙 𐑥𐑹 𐑤𐑲𐑒 𐑣𐑦𐑥. 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑣𐑨𐑛 𐑒𐑷𐑤𐑛 𐑞𐑦𐑕 𐑩𐑯 𐑩𐑛𐑝𐑭𐑯𐑕𐑑 𐑑𐑧𐑒𐑯𐑰𐑒, 𐑯 𐑣𐑨𐑛 𐑢𐑹𐑯𐑛 ·𐑛𐑮𐑱𐑒𐑴 𐑞𐑨𐑑 𐑦𐑑 𐑪𐑓𐑑𐑩𐑯 𐑛𐑦𐑛𐑩𐑯𐑑 𐑢𐑻𐑒.

·𐑛𐑮𐑱𐑒𐑴 𐑯𐑿 𐑣𐑰 𐑣𐑨𐑛𐑩𐑯𐑑 𐑳𐑯𐑛𐑼𐑕𐑑𐑫𐑛 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑞𐑨𐑑 𐑣𐑨𐑛 𐑣𐑨𐑐𐑩𐑯𐑛…𐑚𐑳𐑑 ·𐑐𐑪𐑑𐑼 𐑣𐑨𐑛 𐑪𐑓𐑼𐑛 \emph{𐑣𐑦𐑥} 𐑞 𐑗𐑭𐑯𐑕 𐑑 𐑐𐑤𐑱 𐑯 𐑮𐑲𐑑 𐑯𐑬 𐑦𐑑 𐑢𐑪𐑟 \emph{𐑣𐑦𐑟}. 𐑯 𐑦𐑓 𐑣𐑰 𐑚𐑤𐑻𐑑𐑩𐑛 𐑞 𐑣𐑴𐑤 𐑔𐑦𐑙 𐑬𐑑, 𐑦𐑑 𐑢𐑫𐑛 𐑚𐑦𐑒𐑳𐑥 ·𐑓𐑭𐑞𐑼'𐑟.

𐑦𐑯 𐑞 𐑧𐑯𐑛 𐑦𐑑 𐑢𐑪𐑟 𐑨𐑟 𐑕𐑦𐑥𐑐𐑩𐑤 𐑨𐑟 𐑞𐑨𐑑. 𐑞 𐑤𐑧𐑕𐑼 𐑑𐑧𐑒𐑯𐑰𐑒𐑕 𐑮𐑦𐑒𐑢𐑲𐑼 𐑞 𐑳𐑯𐑩𐑢𐑺𐑯𐑩𐑕 𐑝 𐑞 𐑑𐑸𐑜𐑩𐑑, 𐑹 𐑨𐑑 𐑤𐑰𐑕𐑑 𐑞𐑺 𐑳𐑯𐑕𐑻𐑑𐑩𐑯𐑑𐑦. 𐑓𐑤𐑨𐑑𐑼𐑦 𐑣𐑨𐑕 𐑑 𐑚𐑰 𐑐𐑤𐑷𐑟𐑩𐑚𐑤𐑦 𐑛𐑦𐑕𐑜𐑲𐑟𐑛 𐑨𐑟 𐑨𐑛𐑥𐑼𐑱𐑖𐑩𐑯. (“𐑿 𐑖𐑫𐑛 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑦𐑯 ·𐑕𐑤𐑲𐑔𐑼𐑦𐑯” 𐑦𐑟 𐑩𐑯 𐑴𐑤𐑛 𐑒𐑤𐑨𐑕𐑦𐑒, 𐑣𐑲𐑤𐑦 𐑦𐑓𐑧𐑒𐑑𐑦𐑝 𐑪𐑯 𐑩 𐑕𐑻𐑑𐑩𐑯 𐑑𐑲𐑐 𐑝 𐑐𐑻𐑕𐑩𐑯 𐑣𐑵 𐑦𐑟𐑩𐑯𐑑 𐑦𐑒𐑕𐑐𐑧𐑒𐑑𐑦𐑙 𐑦𐑑, 𐑯 𐑦𐑓 𐑦𐑑 𐑢𐑻𐑒𐑕 𐑿 𐑒𐑨𐑯 𐑮𐑦𐑐𐑰𐑑 𐑦𐑑.) 𐑚𐑳𐑑 𐑢𐑧𐑯 𐑿 𐑓𐑲𐑯𐑛 𐑕𐑳𐑥𐑢𐑳𐑯'𐑟 𐑳𐑤𐑑𐑦𐑥𐑩𐑑 𐑤𐑰𐑝𐑼 𐑦𐑑 𐑛𐑳𐑟𐑩𐑯𐑑 𐑥𐑨𐑑𐑼 𐑦𐑓 𐑞𐑱 𐑯𐑴 𐑿 𐑯𐑴. ·𐑐𐑪𐑑𐑼, 𐑦𐑯 𐑣𐑦𐑟 𐑥𐑨𐑛 𐑮𐑳𐑖, 𐑣𐑨𐑛 𐑜𐑧𐑕𐑑 𐑩 𐑒𐑰 𐑑 ·𐑛𐑮𐑱𐑒𐑴'𐑟 𐑕𐑴𐑤. 𐑯 𐑦𐑓 ·𐑛𐑮𐑱𐑒𐑴 𐑯𐑿 𐑞𐑨𐑑 ·𐑐𐑪𐑑𐑼 𐑯𐑿 𐑦𐑑—𐑰𐑝𐑩𐑯 𐑦𐑓 𐑦𐑑 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑩𐑯 𐑪𐑚𐑝𐑾𐑕 𐑕𐑹𐑑 𐑝 𐑜𐑧𐑕—𐑞𐑨𐑑 𐑛𐑦𐑛𐑩𐑯𐑑 𐑗𐑱𐑯𐑡 𐑧𐑯𐑦𐑔𐑦𐑙.

𐑕𐑴 𐑯𐑬, 𐑓 𐑞 𐑓𐑻𐑕𐑑 𐑑𐑲𐑥 𐑦𐑯 𐑣𐑦𐑟 𐑤𐑲𐑓, 𐑣𐑰 𐑣𐑨𐑛 𐑮𐑾𐑤 𐑕𐑰𐑒𐑮𐑩𐑑𐑕 𐑑 𐑒𐑰𐑐. 𐑣𐑰 𐑢𐑪𐑟 𐑐𐑤𐑱𐑦𐑙 𐑣𐑦𐑟 𐑴𐑯 𐑜𐑱𐑥. 𐑞𐑺 𐑢𐑪𐑟 𐑩𐑯 𐑩𐑚𐑕𐑒𐑘𐑫𐑼 𐑐𐑱𐑯 𐑑 𐑦𐑑, 𐑚𐑳𐑑 𐑣𐑰 𐑯𐑿 𐑞𐑨𐑑 ·𐑓𐑭𐑞𐑼 𐑢𐑫𐑛 𐑚𐑰 𐑐𐑮𐑬𐑛, 𐑯 𐑞𐑨𐑑 𐑥𐑱𐑛 𐑦𐑑 𐑷𐑤 𐑮𐑲𐑑.

𐑤𐑰𐑝𐑦𐑙 𐑞 𐑦𐑙𐑒 𐑛𐑮𐑦𐑐𐑦𐑙𐑟 𐑦𐑯 𐑐𐑤𐑱𐑕—𐑞𐑺 𐑢𐑪𐑟 𐑩 𐑥𐑧𐑕𐑦𐑡 𐑞𐑺, 𐑯 𐑢𐑳𐑯 𐑞𐑨𐑑 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑢𐑫𐑛 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛, 𐑓 𐑞𐑱 𐑣𐑨𐑛 𐑐𐑤𐑱𐑛 𐑞 𐑜𐑱𐑥 𐑝 𐑕𐑳𐑑𐑩𐑤𐑑𐑦𐑟 𐑥𐑹 𐑞𐑨𐑯 𐑢𐑳𐑯𐑕—·𐑛𐑮𐑱𐑒𐑴 𐑮𐑴𐑑 𐑬𐑑 𐑞 𐑢𐑳𐑯 𐑒𐑢𐑧𐑕𐑗𐑩𐑯 𐑞𐑨𐑑 𐑮𐑾𐑤𐑦 𐑣𐑨𐑛 𐑯𐑷𐑛 𐑨𐑑 𐑣𐑦𐑥 𐑩𐑚𐑬𐑑 𐑞 𐑣𐑴𐑤 𐑩𐑓𐑺, 𐑞 𐑐𐑸𐑑 𐑞𐑨𐑑 𐑦𐑑 𐑕𐑰𐑥𐑛 𐑣𐑰 \emph{𐑷𐑑} 𐑑 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛, 𐑚𐑳𐑑 𐑣𐑰 𐑛𐑦𐑛𐑩𐑯𐑑, 𐑯𐑪𐑑 𐑨𐑑 𐑷𐑤.

\begin{writtenNote}
\letterAddress{𐑛𐑽 ·𐑓𐑭𐑞𐑼:}

𐑕𐑩𐑐𐑴𐑟 𐑲 𐑑𐑴𐑤𐑛 𐑿 𐑞𐑨𐑑 𐑲 𐑥𐑧𐑑 𐑩 𐑕𐑑𐑿𐑛𐑩𐑯𐑑 𐑨𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕, 𐑯𐑪𐑑 𐑷𐑤𐑮𐑧𐑛𐑦 𐑐𐑸𐑑 𐑝 𐑬𐑼 𐑕𐑻𐑒𐑩𐑤 𐑝 𐑩𐑒𐑢𐑱𐑯𐑑𐑩𐑯𐑕𐑩𐑟, 𐑣𐑵 𐑒𐑷𐑤𐑛 𐑿 𐑩 '𐑓𐑤𐑷𐑤𐑩𐑕 𐑦𐑯𐑕𐑑𐑮𐑩𐑥𐑧𐑯𐑑 𐑝 𐑛𐑧𐑔' 𐑯 𐑕𐑧𐑛 𐑞𐑨𐑑 𐑲 𐑢𐑪𐑟 𐑘𐑹 '𐑢𐑳𐑯 𐑢𐑰𐑒 𐑐𐑶𐑯𐑑'. 𐑢𐑪𐑑 𐑢𐑫𐑛 𐑿 𐑕𐑱 𐑩𐑚𐑬𐑑 𐑣𐑦𐑥?

\end{writtenNote}

𐑦𐑑 𐑛𐑦𐑛𐑩𐑯𐑑 𐑑𐑱𐑒 𐑤𐑪𐑙 𐑭𐑓𐑑𐑼 𐑞𐑨𐑑 𐑓 𐑞 𐑓𐑨𐑥𐑤𐑦 𐑬𐑤 𐑑 𐑚𐑮𐑦𐑙 𐑞 𐑮𐑦𐑐𐑤𐑲.

\begin{writtenNote}
\letterAddress{𐑥𐑲 𐑚𐑦𐑤𐑳𐑝𐑩𐑛 𐑕𐑳𐑯:}

𐑲 𐑢𐑫𐑛 𐑕𐑱 𐑞𐑨𐑑 𐑿 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑕𐑴 𐑓𐑹𐑗𐑩𐑯𐑩𐑑 𐑨𐑟 𐑑 𐑥𐑰𐑑 𐑕𐑳𐑥𐑢𐑳𐑯 𐑣𐑵 𐑦𐑯𐑡𐑶𐑟 𐑞 𐑦𐑯𐑑𐑦𐑥𐑩𐑑 𐑒𐑪𐑯𐑓𐑦𐑛𐑩𐑯𐑕 𐑝 𐑬𐑼 𐑓𐑮𐑧𐑯𐑛 𐑯 𐑝𐑨𐑤𐑿𐑩𐑚𐑩𐑤 𐑨𐑤𐑲, ·𐑕𐑧𐑝𐑼𐑩𐑕 ·𐑕𐑯𐑱𐑐.

\end{writtenNote}

·𐑛𐑮𐑱𐑒𐑴 𐑕𐑑𐑺𐑛 𐑨𐑑 𐑞 𐑤𐑧𐑑𐑼 𐑓 𐑩 𐑢𐑲𐑤, 𐑯 𐑓𐑲𐑯𐑩𐑤𐑦 𐑔𐑮𐑵 𐑦𐑑 𐑦𐑯𐑑𐑵 𐑞 𐑓𐑲𐑼.

%  LocalWords:  etunia Cor eehhhhh Spoo Snitchless Aw Scuse limer Gah
%  LocalWords:  buh bluh ker splutching whatsherface
