\chapter{𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑲 𐑚𐑦𐑤𐑰𐑝 𐑦𐑟 𐑓𐑷𐑤𐑕}

% \begin{chapterOpeningAuthorNote}
% \#include "stddisclaimer.h"
% \end{chapterOpeningAuthorNote}
\begin{chapterOpeningQuote}
𐑝 𐑒𐑹𐑕 𐑦𐑑 𐑢𐑪𐑟 𐑥𐑲 𐑓𐑷𐑤𐑑. 𐑞𐑺'𐑟 𐑯𐑴 𐑢𐑳𐑯 𐑧𐑤𐑕 𐑣𐑽 𐑣𐑵 𐑒𐑫𐑛 𐑚𐑰 𐑮𐑦𐑕𐑐𐑪𐑯𐑕𐑩𐑚𐑩𐑤 𐑓 𐑧𐑯𐑦𐑔𐑦𐑙.
\end{chapterOpeningQuote}

\lettrine[ante=“]{𐑯}{𐑬}, 𐑡𐑳𐑕𐑑 𐑑 𐑚𐑰 𐑒𐑤𐑽,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, “𐑦𐑓 𐑞 𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑛𐑳𐑟 𐑤𐑧𐑝𐑦𐑑𐑱𐑑 𐑿, ·𐑛𐑨𐑛, 𐑢𐑧𐑯 𐑿 𐑯𐑴 𐑿 𐑣𐑨𐑝𐑩𐑯𐑑 𐑚𐑰𐑯 𐑩𐑑𐑨𐑗𐑑 𐑑 𐑧𐑯𐑦 𐑢𐑲𐑼𐑟, 𐑞𐑨𐑑'𐑕 𐑜𐑴𐑦𐑙 𐑑 𐑚𐑰 𐑕𐑩𐑓𐑦𐑖𐑩𐑯𐑑 𐑧𐑝𐑦𐑛𐑩𐑯𐑕. 𐑿'𐑼 𐑯𐑪𐑑 𐑜𐑴𐑦𐑙 𐑑 𐑑𐑻𐑯 𐑼𐑬𐑯𐑛 𐑯 𐑕𐑱 𐑞𐑨𐑑 𐑦𐑑'𐑕 𐑩 𐑥𐑩𐑡𐑦𐑖𐑩𐑯'𐑟 𐑑𐑮𐑦𐑒. 𐑞𐑨𐑑 𐑢𐑫𐑛𐑩𐑯𐑑 𐑚𐑰 𐑓𐑺 𐑐𐑤𐑱. 𐑦𐑓 𐑿 𐑓𐑰𐑤 𐑞𐑨𐑑 𐑢𐑱, 𐑿 𐑖𐑫𐑛 𐑕𐑱 𐑕𐑴 \emph{𐑯𐑬}, 𐑯 𐑢𐑰 𐑒𐑨𐑯 𐑓𐑦𐑜𐑼 𐑬𐑑 𐑩 𐑛𐑦𐑓𐑼𐑩𐑯𐑑 𐑦𐑒𐑕𐑐𐑧𐑮𐑦𐑥𐑧𐑯𐑑 𐑦𐑯𐑕𐑑𐑧𐑛.”

·𐑣𐑨𐑮𐑦'𐑟 𐑓𐑭𐑞𐑼, ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑲𐑒𐑩𐑤 ·𐑝𐑧𐑮𐑟-·𐑧𐑝𐑩𐑯𐑟, 𐑮𐑴𐑤𐑛 𐑣𐑦𐑟 𐑲𐑟. “𐑘𐑧𐑕, ·𐑣𐑨𐑮𐑦.”

“𐑯 𐑿, ·𐑥𐑳𐑥, 𐑘𐑹 𐑔𐑽𐑦 𐑕𐑧𐑟 𐑞𐑨𐑑 𐑞 𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑖𐑫𐑛 𐑚𐑰 𐑱𐑚𐑩𐑤 𐑑 𐑛𐑵 𐑞𐑦𐑕, 𐑯 𐑦𐑓 𐑞𐑨𐑑 𐑛𐑳𐑟𐑩𐑯𐑑 𐑣𐑨𐑐𐑩𐑯, 𐑿'𐑤 𐑩𐑛𐑥𐑦𐑑 𐑿'𐑼 𐑥𐑦𐑕𐑑𐑱𐑒𐑩𐑯. 𐑯𐑳𐑔𐑦𐑙 𐑩𐑚𐑬𐑑 𐑣𐑬 𐑥𐑨𐑡𐑦𐑒 𐑛𐑳𐑟𐑩𐑯𐑑 𐑢𐑻𐑒 𐑢𐑧𐑯 𐑐𐑰𐑐𐑩𐑤 𐑸 𐑕𐑒𐑧𐑐𐑑𐑦𐑒𐑩𐑤 𐑝 𐑦𐑑, 𐑹 𐑧𐑯𐑦𐑔𐑦𐑙 𐑤𐑲𐑒 𐑞𐑨𐑑.”

𐑛𐑧𐑐𐑿𐑑𐑦 ·𐑣𐑧𐑛𐑥𐑦𐑕𐑑𐑮𐑩𐑕 ·𐑥𐑦𐑯𐑻𐑝𐑩 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑢𐑪𐑟 𐑢𐑪𐑗𐑦𐑙 ·𐑣𐑨𐑮𐑦 𐑢𐑦𐑞 𐑩 𐑚𐑦𐑥𐑿𐑟𐑛 𐑦𐑒𐑕𐑐𐑮𐑧𐑖𐑩𐑯. 𐑖𐑰 𐑤𐑫𐑒𐑑 𐑒𐑢𐑲𐑑 𐑢𐑦𐑗𐑦 𐑦𐑯 𐑣𐑻 𐑚𐑤𐑨𐑒 𐑮𐑴𐑚𐑟 𐑯 𐑐𐑶𐑯𐑑𐑩𐑛 𐑣𐑨𐑑, 𐑚𐑳𐑑 𐑢𐑧𐑯 𐑖𐑰 𐑕𐑐𐑴𐑒 𐑖𐑰 𐑕𐑬𐑯𐑛𐑩𐑛 𐑓𐑹𐑥𐑩𐑤 𐑯 ·𐑕𐑒𐑪𐑑𐑦𐑖, 𐑢𐑦𐑗 𐑛𐑦𐑛𐑩𐑯𐑑 𐑜𐑴 𐑑𐑩𐑜𐑧𐑞𐑼 𐑢𐑦𐑞 𐑞 𐑤𐑫𐑒 𐑨𐑑 𐑷𐑤. 𐑨𐑑 𐑓𐑻𐑕𐑑 𐑜𐑤𐑭𐑯𐑕 𐑖𐑰 𐑤𐑫𐑒𐑑 𐑤𐑲𐑒 𐑕𐑳𐑥𐑢𐑳𐑯 𐑣𐑵 𐑷𐑑 𐑑 𐑒𐑨𐑒𐑩𐑤 𐑯 𐑐𐑫𐑑 𐑚𐑱𐑚𐑦𐑟 𐑦𐑯𐑑𐑵 𐑒𐑷𐑤𐑛𐑮𐑩𐑯𐑟, 𐑚𐑳𐑑 𐑞 𐑣𐑴𐑤 𐑦𐑓𐑧𐑒𐑑 𐑢𐑪𐑟 𐑮𐑵𐑦𐑯𐑛 𐑨𐑟 𐑕𐑵𐑯 𐑨𐑟 𐑖𐑰 𐑴𐑐𐑩𐑯𐑛 𐑣𐑻 𐑥𐑬𐑔. “𐑦𐑟 𐑞𐑨𐑑 𐑕𐑩𐑓𐑦𐑖𐑩𐑯𐑑, ·𐑥𐑼~·𐑐𐑪𐑑𐑼?” 𐑖𐑰 𐑕𐑧𐑛. “𐑖𐑨𐑤 𐑲 𐑜𐑴 𐑩𐑣𐑧𐑛 𐑯 𐑛𐑧𐑥𐑩𐑯𐑕𐑑𐑮𐑱𐑑?”

“\emph{𐑕𐑩𐑓𐑦𐑖𐑩𐑯𐑑?} 𐑐𐑮𐑪𐑚𐑩𐑚𐑤𐑦 𐑯𐑪𐑑,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. “𐑚𐑳𐑑 𐑨𐑑 𐑤𐑰𐑕𐑑 𐑦𐑑 𐑢𐑦𐑤 \emph{𐑣𐑧𐑤𐑐}. 𐑜𐑴 𐑩𐑣𐑧𐑛, ·𐑛𐑧𐑐𐑿𐑑𐑦 ·𐑣𐑧𐑛𐑥𐑦𐑕𐑑𐑮𐑩𐑕.”

“𐑡𐑳𐑕𐑑 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑢𐑦𐑤 𐑛𐑵,” 𐑕𐑧𐑛 𐑖𐑰, 𐑯 𐑞𐑧𐑯, “\emph{·𐑢𐑦𐑯𐑜𐑸𐑛𐑾𐑥 ·𐑤𐑧𐑝𐑦𐑴𐑕𐑩}.”

·𐑣𐑨𐑮𐑦 𐑤𐑫𐑒𐑑 𐑨𐑑 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼.

“𐑣𐑳,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛.

𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑤𐑫𐑒𐑑 𐑚𐑨𐑒 𐑨𐑑 𐑣𐑦𐑥. “𐑣𐑳,” 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑧𐑒𐑴𐑛.

𐑞𐑧𐑯 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑝𐑧𐑮𐑟-·𐑧𐑝𐑩𐑯𐑟 𐑤𐑫𐑒𐑑 𐑚𐑨𐑒 𐑨𐑑 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. “𐑷𐑤 𐑮𐑲𐑑, 𐑿 𐑒𐑨𐑯 𐑐𐑫𐑑 𐑥𐑰 𐑛𐑬𐑯 𐑯𐑬.”

𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑢𐑪𐑟 𐑤𐑴𐑼𐑛 𐑒𐑺𐑓𐑩𐑤𐑦 𐑑 𐑞 𐑜𐑮𐑬𐑯𐑛.

·𐑣𐑨𐑮𐑦 𐑮𐑳𐑓𐑩𐑤𐑛 𐑩 𐑣𐑨𐑯𐑛 𐑔𐑮𐑵 𐑣𐑦𐑟 𐑴𐑯 𐑣𐑺. 𐑥𐑱𐑚𐑰 𐑦𐑑 𐑢𐑪𐑟 𐑡𐑳𐑕𐑑 𐑞𐑨𐑑 𐑕𐑑𐑮𐑱𐑯𐑡 𐑐𐑸𐑑 𐑝 𐑣𐑦𐑥 𐑢𐑦𐑗 𐑣𐑨𐑛 \emph{𐑷𐑤𐑮𐑧𐑛𐑦} 𐑚𐑰𐑯 𐑒𐑩𐑯𐑝𐑦𐑯𐑕𐑑, 𐑚𐑳𐑑…“𐑞𐑨𐑑'𐑕 𐑩 𐑚𐑦𐑑 𐑝 𐑩𐑯 𐑨𐑯𐑑𐑦𐑒𐑤𐑲𐑥𐑨𐑒𐑕,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. “𐑿'𐑛 𐑔𐑦𐑙𐑒 𐑞𐑺'𐑛 𐑚𐑰 𐑕𐑳𐑥 𐑒𐑲𐑯𐑛 𐑝 𐑥𐑹 𐑛𐑮𐑩𐑥𐑨𐑑𐑦𐑒 𐑥𐑧𐑯𐑑𐑩𐑤 𐑦𐑝𐑧𐑯𐑑 𐑩𐑕𐑴𐑖𐑦𐑱𐑑𐑩𐑛 𐑢𐑦𐑞 𐑳𐑐𐑛𐑱𐑑𐑦𐑙 𐑪𐑯 𐑩𐑯 𐑪𐑚𐑟𐑼𐑝𐑱𐑖𐑩𐑯 𐑝 𐑦𐑯𐑓𐑦𐑯𐑦𐑑𐑧𐑕𐑦𐑥𐑩𐑤 𐑐𐑮𐑪𐑚𐑩𐑚𐑦𐑤𐑦𐑑𐑦—” ·𐑣𐑨𐑮𐑦 𐑕𐑑𐑪𐑐𐑑 𐑣𐑦𐑥𐑕𐑧𐑤𐑓. 𐑥𐑳𐑥, 𐑞 𐑢𐑦𐑗, 𐑯 𐑰𐑝𐑩𐑯 𐑣𐑦𐑟 ·𐑛𐑨𐑛 𐑢𐑻 𐑜𐑦𐑝𐑦𐑙 𐑣𐑦𐑥 \emph{𐑞𐑨𐑑 𐑤𐑫𐑒} 𐑩𐑜𐑱𐑯. “𐑲 𐑥𐑰𐑯, 𐑢𐑦𐑞 𐑓𐑲𐑯𐑛𐑦𐑙 𐑬𐑑 𐑞𐑨𐑑 𐑧𐑝𐑮𐑦𐑔𐑦𐑙 𐑲 𐑚𐑦𐑤𐑰𐑝 𐑦𐑟 𐑓𐑷𐑤𐑕.”

𐑕𐑽𐑾𐑕𐑤𐑦, 𐑦𐑑 𐑖𐑫𐑛 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑥𐑹 𐑛𐑮𐑩𐑥𐑨𐑑𐑦𐑒. 𐑣𐑦𐑟 𐑚𐑮𐑱𐑯 𐑷𐑑 𐑑 𐑣𐑨𐑝 𐑚𐑰𐑯 𐑓𐑤𐑳𐑖𐑦𐑙 𐑦𐑑𐑕 𐑦𐑯𐑑𐑲𐑼 𐑒𐑳𐑮𐑩𐑯𐑑 𐑕𐑑𐑪𐑒 𐑝 𐑣𐑲𐑐𐑪𐑔𐑦𐑕𐑰𐑟 𐑩𐑚𐑬𐑑 𐑞 𐑿𐑯𐑦𐑝𐑻𐑕, 𐑯𐑳𐑯 𐑝 𐑢𐑦𐑗 𐑩𐑤𐑬𐑛 𐑞𐑦𐑕 𐑑 𐑣𐑨𐑐𐑩𐑯. 𐑚𐑳𐑑 𐑦𐑯𐑕𐑑𐑧𐑛 𐑣𐑦𐑟 𐑚𐑮𐑱𐑯 𐑡𐑳𐑕𐑑 𐑕𐑰𐑥𐑛 𐑑 𐑚𐑰 𐑜𐑴𐑦𐑙, \emph{𐑷𐑤 𐑮𐑲𐑑, 𐑲 𐑕𐑷 𐑞 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 𐑢𐑱𐑝 𐑣𐑻 𐑢𐑪𐑯𐑛 𐑯 𐑥𐑱𐑒 𐑘𐑹 𐑓𐑭𐑞𐑼 𐑮𐑲𐑟 𐑦𐑯𐑑𐑵 𐑞 𐑺, 𐑯𐑬 𐑢𐑪𐑑?}

𐑞 𐑢𐑦𐑗-𐑤𐑱𐑛𐑦 𐑢𐑪𐑟 𐑕𐑥𐑲𐑤𐑦𐑙 𐑚𐑦𐑯𐑧𐑝𐑩𐑤𐑩𐑯𐑑𐑤𐑦 𐑩𐑐𐑪𐑯 𐑞𐑧𐑥, 𐑤𐑫𐑒𐑦𐑙 𐑒𐑢𐑲𐑑 𐑩𐑥𐑿𐑟𐑛. “𐑢𐑫𐑛 𐑿 𐑤𐑲𐑒 𐑩 𐑓𐑻𐑞𐑼 𐑛𐑧𐑥𐑩𐑯𐑕𐑑𐑮𐑱𐑖𐑩𐑯, ·𐑥𐑼~·𐑐𐑪𐑑𐑼?”

“𐑿 𐑛𐑴𐑯𐑑 𐑣𐑨𐑓 𐑑,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. “𐑢𐑰'𐑝 𐑐𐑼𐑓𐑹𐑥𐑛 𐑩 𐑛𐑦𐑓𐑦𐑯𐑦𐑑𐑦𐑝 𐑦𐑒𐑕𐑐𐑧𐑮𐑦𐑥𐑧𐑯𐑑. 𐑚𐑳𐑑…” ·𐑣𐑨𐑮𐑦 𐑣𐑧𐑟𐑦𐑑𐑱𐑑𐑩𐑛. 𐑣𐑰 𐑒𐑫𐑛𐑩𐑯𐑑 𐑣𐑧𐑤𐑐 𐑣𐑦𐑥𐑕𐑧𐑤𐑓. 𐑨𐑒𐑗𐑵𐑩𐑤𐑦, 𐑳𐑯𐑛𐑼 𐑞 𐑕𐑻𐑒𐑩𐑥𐑕𐑑𐑨𐑯𐑕𐑩𐑟, 𐑣𐑰 \emph{𐑖𐑫𐑛𐑩𐑯𐑑} 𐑚𐑰 𐑣𐑧𐑤𐑐𐑦𐑙 𐑣𐑦𐑥𐑕𐑧𐑤𐑓. 𐑦𐑑 𐑢𐑪𐑟 𐑮𐑲𐑑 𐑯 𐑐𐑮𐑪𐑐𐑼 𐑑 𐑚𐑰 𐑒𐑘𐑫𐑼𐑾𐑕. “𐑢𐑪𐑑 𐑧𐑤𐑕 \emph{𐑒𐑨𐑯} 𐑿 𐑛𐑵?”

𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑑𐑻𐑯𐑛 𐑦𐑯𐑑𐑵 𐑩 𐑒𐑨𐑑.

·𐑣𐑨𐑮𐑦 𐑕𐑒𐑮𐑨𐑥𐑚𐑩𐑤𐑛 𐑚𐑨𐑒 𐑳𐑯𐑔𐑦𐑙𐑒𐑦𐑙𐑤𐑦, 𐑚𐑨𐑒-𐑐𐑧𐑛𐑩𐑤𐑦𐑙 𐑕𐑴 𐑓𐑭𐑕𐑑 𐑞𐑨𐑑 𐑣𐑰 𐑑𐑮𐑦𐑐𐑑 𐑴𐑝𐑼 𐑩 𐑕𐑑𐑮𐑱 𐑕𐑑𐑨𐑒 𐑝 𐑚𐑫𐑒𐑕 𐑯 𐑤𐑨𐑯𐑛𐑩𐑛 𐑣𐑸𐑛 𐑪𐑯 𐑣𐑦𐑟 𐑚𐑪𐑑𐑩𐑥 𐑢𐑦𐑞 𐑩 \emph{𐑔𐑢𐑨𐑒}. 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛𐑟 𐑒𐑱𐑥 𐑛𐑬𐑯 𐑑 𐑒𐑨𐑗 𐑣𐑦𐑥𐑕𐑧𐑤𐑓 𐑢𐑦𐑞𐑬𐑑 𐑒𐑢𐑲𐑑 𐑮𐑰𐑗𐑦𐑙 𐑐𐑮𐑪𐑐𐑼𐑤𐑦, 𐑯 𐑞𐑺 𐑢𐑪𐑟 𐑩 𐑢𐑹𐑯𐑦𐑙 𐑑𐑢𐑦𐑯𐑡 𐑦𐑯 𐑣𐑦𐑟 𐑖𐑴𐑤𐑛𐑼 𐑨𐑟 𐑞 𐑢𐑱𐑑 𐑒𐑱𐑥 𐑛𐑬𐑯 𐑳𐑯𐑚𐑮𐑱𐑕𐑑.

𐑨𐑑 𐑢𐑳𐑯𐑕 𐑞 𐑕𐑥𐑷𐑤 𐑑𐑨𐑚𐑦 𐑒𐑨𐑑 𐑥𐑹𐑓𐑑 𐑚𐑨𐑒 𐑳𐑐 𐑦𐑯𐑑𐑵 𐑩 𐑮𐑴𐑚𐑛 𐑢𐑫𐑥𐑩𐑯. “𐑲'𐑥 𐑕𐑪𐑮𐑦, ·𐑥𐑼~·𐑐𐑪𐑑𐑼,” 𐑕𐑧𐑛 𐑞 𐑢𐑦𐑗, 𐑕𐑬𐑯𐑛𐑦𐑙 𐑕𐑦𐑯𐑕𐑽, 𐑞𐑴 𐑞 𐑒𐑹𐑯𐑼𐑟 𐑝 𐑣𐑻 𐑤𐑦𐑐𐑕 𐑢𐑻 𐑑𐑢𐑦𐑗𐑦𐑙 𐑳𐑐𐑢𐑼𐑛𐑟. “𐑲 𐑖𐑫𐑛 𐑣𐑨𐑝 𐑢𐑹𐑯𐑛 𐑿.”

·𐑣𐑨𐑮𐑦 𐑢𐑪𐑟 𐑚𐑮𐑰𐑞𐑦𐑙 𐑦𐑯 𐑖𐑹𐑑 𐑜𐑭𐑕𐑐𐑕. 𐑣𐑦𐑟 𐑝𐑶𐑕 𐑒𐑱𐑥 𐑬𐑑 𐑗𐑴𐑒𐑑. “\emph{𐑿 𐑒𐑭𐑯𐑑 \emph{𐑛𐑵} 𐑞𐑨𐑑!}”

“𐑦𐑑'𐑕 𐑴𐑯𐑤𐑦 𐑩 ·𐑑𐑮𐑨𐑯𐑕𐑓𐑦𐑜𐑼𐑱𐑖𐑩𐑯,” 𐑕𐑧𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. “𐑩𐑯 ·𐑨𐑯𐑦𐑥𐑨𐑜𐑩𐑕 𐑑𐑮𐑨𐑯𐑕𐑓𐑼𐑥𐑱𐑖𐑩𐑯, 𐑑 𐑚𐑰 𐑦𐑜𐑟𐑨𐑒𐑑.”

“𐑿 𐑑𐑻𐑯𐑛 𐑦𐑯𐑑𐑵 𐑩 𐑒𐑨𐑑! 𐑩 \emph{𐑕𐑥𐑷𐑤} 𐑒𐑨𐑑! 𐑿 𐑝𐑲𐑩𐑤𐑱𐑑𐑩𐑛 ·𐑒𐑪𐑯𐑕𐑼𐑝𐑱𐑖𐑩𐑯 𐑝 ·𐑧𐑯𐑼𐑡𐑦! 𐑞𐑨𐑑'𐑕 𐑯𐑪𐑑 𐑡𐑳𐑕𐑑 𐑩𐑯 𐑸𐑚𐑦𐑑𐑮𐑼𐑦 𐑮𐑵𐑤, 𐑦𐑑'𐑕 𐑦𐑥𐑐𐑤𐑲𐑛 𐑚𐑲 𐑞 𐑓𐑹𐑥 𐑝 𐑞 𐑒𐑢𐑪𐑯𐑑𐑩𐑥 ·𐑣𐑨𐑥𐑦𐑤𐑑𐑴𐑯𐑾𐑯! 𐑮𐑦𐑡𐑧𐑒𐑑𐑦𐑙 𐑦𐑑 𐑛𐑦𐑕𐑑𐑮𐑶𐑟 𐑿𐑯𐑦𐑑𐑺𐑦𐑑𐑦 𐑯 𐑞𐑧𐑯 𐑿 𐑜𐑧𐑑 ·𐑓𐑑𐑤 𐑕𐑦𐑜𐑯𐑩𐑤𐑦𐑙! 𐑯 𐑒𐑨𐑑𐑕 𐑸 \emph{𐑒𐑪𐑥𐑐𐑤𐑦𐑒𐑱𐑑𐑩𐑛}! 𐑩 𐑣𐑿𐑥𐑩𐑯 𐑥𐑲𐑯𐑛 𐑒𐑭𐑯𐑑 𐑡𐑳𐑕𐑑 𐑝𐑦𐑠𐑵𐑩𐑤𐑲𐑟 𐑩 𐑣𐑴𐑤 𐑒𐑨𐑑'𐑕 𐑩𐑯𐑨𐑑𐑩𐑥𐑦 𐑯, 𐑯 𐑷𐑤 𐑞 𐑒𐑨𐑑 𐑚𐑲𐑴𐑒𐑧𐑥𐑦𐑕𐑑𐑮𐑦, 𐑯 𐑢𐑪𐑑 𐑩𐑚𐑬𐑑 𐑞 \emph{𐑯𐑘𐑫𐑼𐑪𐑤𐑩𐑡𐑦}? 𐑣𐑬 𐑒𐑨𐑯 𐑿 𐑜𐑴 𐑪𐑯 \emph{𐑔𐑦𐑙𐑒𐑦𐑙} 𐑿𐑟𐑦𐑙 𐑩 𐑒𐑨𐑑-𐑕𐑲𐑟𐑛 𐑚𐑮𐑱𐑯?”

𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤'𐑟 𐑤𐑦𐑐𐑕 𐑢𐑻 𐑑𐑢𐑦𐑗𐑦𐑙 𐑣𐑸𐑛𐑼 𐑯𐑬. “𐑥𐑨𐑡𐑦𐑒.”

“𐑥𐑨𐑡𐑦𐑒 \emph{𐑦𐑟𐑩𐑯𐑑 𐑦𐑯𐑳𐑓} 𐑑 𐑛𐑵 𐑞𐑨𐑑! 𐑿'𐑛 𐑣𐑨𐑓 𐑑 𐑚𐑰 𐑩 𐑜𐑪𐑛!”

𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑚𐑤𐑦𐑙𐑒𐑑. “𐑞𐑨𐑑'𐑕 𐑞 𐑓𐑻𐑕𐑑 𐑑𐑲𐑥 𐑲'𐑝 𐑧𐑝𐑼 𐑚𐑰𐑯 𐑒𐑷𐑤𐑛 \emph{𐑞𐑨𐑑}.”

𐑩 𐑚𐑤𐑻 𐑢𐑪𐑟 𐑒𐑳𐑥𐑦𐑙 𐑴𐑝𐑼 ·𐑣𐑨𐑮𐑦'𐑟 𐑝𐑦𐑠𐑩𐑯, 𐑨𐑟 𐑣𐑦𐑟 𐑚𐑮𐑱𐑯 𐑕𐑑𐑸𐑑𐑩𐑛 𐑑 𐑒𐑪𐑥𐑐𐑮𐑦𐑣𐑧𐑯𐑛 𐑢𐑪𐑑 𐑣𐑨𐑛 𐑡𐑳𐑕𐑑 𐑚𐑮𐑴𐑒𐑩𐑯. 𐑞 𐑣𐑴𐑤 𐑲𐑛𐑾 𐑝 𐑩 𐑿𐑯𐑦𐑓𐑲𐑛 𐑿𐑯𐑦𐑝𐑻𐑕 𐑢𐑦𐑞 𐑥𐑨𐑔𐑩𐑥𐑨𐑑𐑦𐑒𐑤𐑦 𐑮𐑧𐑜𐑿𐑤𐑼 𐑤𐑷𐑟, 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑢𐑪𐑑 𐑣𐑨𐑛 𐑚𐑰𐑯 𐑓𐑤𐑳𐑖𐑑 𐑛𐑬𐑯 𐑞 𐑑𐑶𐑤𐑩𐑑; 𐑞 𐑣𐑴𐑤 𐑯𐑴𐑖𐑩𐑯 𐑝 \emph{𐑓𐑦𐑟𐑦𐑒𐑕}. 𐑔𐑮𐑰 𐑔𐑬𐑟𐑩𐑯𐑛 𐑘𐑽𐑟 𐑝 𐑮𐑦𐑟𐑪𐑤𐑝𐑦𐑙 𐑚𐑦𐑜 𐑒𐑪𐑥𐑐𐑤𐑦𐑒𐑱𐑑𐑩𐑛 𐑔𐑦𐑙𐑟 𐑦𐑯𐑑𐑵 𐑕𐑥𐑷𐑤𐑼 𐑐𐑰𐑕𐑩𐑟, 𐑛𐑦𐑕𐑒𐑳𐑝𐑼𐑦𐑙 𐑞𐑨𐑑 𐑞 𐑥𐑿𐑟𐑦𐑒 𐑝 𐑞 𐑐𐑤𐑨𐑯𐑩𐑑𐑕 𐑢𐑪𐑟 𐑞 𐑕𐑱𐑥 𐑑𐑿𐑯 𐑨𐑟 𐑩 𐑓𐑷𐑤𐑦𐑙 𐑨𐑐𐑩𐑤, 𐑓𐑲𐑯𐑛𐑦𐑙 𐑞𐑨𐑑 𐑞 𐑑𐑮𐑵 𐑤𐑷𐑟 𐑢𐑻 𐑐𐑻𐑓𐑦𐑒𐑑𐑤𐑦 𐑿𐑯𐑦𐑝𐑻𐑕𐑩𐑤 𐑯 𐑣𐑨𐑛 𐑯𐑴 𐑦𐑒𐑕𐑧𐑐𐑖𐑩𐑯𐑟 𐑧𐑯𐑦𐑢𐑺 𐑯 𐑑𐑫𐑒 𐑞 𐑓𐑹𐑥 𐑝 𐑕𐑦𐑥𐑐𐑩𐑤 𐑥𐑨𐑔𐑕 𐑜𐑳𐑝𐑼𐑯𐑦𐑙 𐑞 𐑕𐑥𐑷𐑤𐑩𐑕𐑑 𐑐𐑸𐑑𐑕, \emph{𐑯𐑪𐑑 𐑑 𐑥𐑧𐑯𐑖𐑩𐑯} 𐑞𐑨𐑑 𐑞 𐑥𐑲𐑯𐑛 𐑢𐑪𐑟 𐑞 𐑚𐑮𐑱𐑯 𐑯 𐑞 𐑚𐑮𐑱𐑯 𐑢𐑪𐑟 𐑥𐑱𐑛 𐑝 𐑯𐑘𐑫𐑼𐑪𐑯𐑟, 𐑩 𐑚𐑮𐑱𐑯 𐑢𐑪𐑟 𐑢𐑪𐑑 𐑩 𐑐𐑻𐑕𐑩𐑯 \emph{𐑢𐑪𐑟}—

𐑯 𐑞𐑧𐑯 𐑩 𐑢𐑫𐑥𐑩𐑯 𐑑𐑻𐑯𐑛 𐑦𐑯𐑑𐑵 𐑩 𐑒𐑨𐑑, 𐑕𐑴 𐑥𐑳𐑗 𐑓 𐑷𐑤 𐑞𐑨𐑑.

𐑩 𐑣𐑳𐑯𐑛𐑮𐑩𐑛 𐑒𐑢𐑧𐑕𐑗𐑩𐑯𐑟 𐑓𐑷𐑑 𐑓 𐑐𐑮𐑲𐑪𐑮𐑦𐑑𐑦 𐑴𐑝𐑼 ·𐑣𐑨𐑮𐑦'𐑟 𐑤𐑦𐑐𐑕 𐑯 𐑞 𐑢𐑦𐑯𐑼 𐑐𐑹𐑛 𐑬𐑑: “𐑯, 𐑯 𐑢𐑪𐑑 𐑒𐑲𐑯𐑛 𐑝 𐑦𐑯𐑒𐑨𐑯𐑑𐑱𐑖𐑩𐑯 𐑦𐑟 \emph{·𐑢𐑦𐑯𐑜𐑸𐑛𐑾𐑥 ·𐑤𐑧𐑝𐑦𐑴𐑕𐑩?} 𐑣𐑵 𐑦𐑯𐑝𐑧𐑯𐑑𐑕 𐑞 𐑢𐑻𐑛𐑟 𐑑 𐑞𐑰𐑟 𐑕𐑐𐑧𐑤𐑟, 𐑯𐑻𐑕𐑼𐑦 𐑕𐑒𐑵𐑤𐑼𐑟?”

“𐑞𐑨𐑑 𐑢𐑦𐑤 𐑛𐑵, ·𐑥𐑼~·𐑐𐑪𐑑𐑼,” 𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑧𐑛 𐑒𐑮𐑦𐑕𐑐𐑤𐑦, 𐑞𐑴 𐑣𐑻 𐑲𐑟 𐑖𐑪𐑯 𐑢𐑦𐑞 𐑕𐑩𐑐𐑮𐑧𐑕𐑑 𐑩𐑥𐑿𐑟𐑥𐑩𐑯𐑑. “𐑦𐑓 𐑿 𐑢𐑦𐑖 𐑑 𐑤𐑻𐑯 𐑩𐑚𐑬𐑑 𐑥𐑨𐑡𐑦𐑒, 𐑲 𐑕𐑩𐑡𐑧𐑕𐑑 𐑞𐑨𐑑 𐑢𐑰 𐑓𐑲𐑯𐑩𐑤𐑲𐑟 𐑞 𐑐𐑱𐑐𐑼𐑢𐑻𐑒 𐑕𐑴 𐑞𐑨𐑑 𐑿 𐑒𐑨𐑯 𐑜𐑴 𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕.”

“𐑮𐑲𐑑,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛, 𐑕𐑳𐑥𐑢𐑪𐑑 𐑛𐑱𐑟𐑛. 𐑣𐑰 𐑐𐑫𐑤𐑛 𐑣𐑦𐑟 𐑔𐑷𐑑𐑕 𐑑𐑩𐑜𐑧𐑞𐑼. 𐑞 𐑥𐑸𐑗 𐑝 ·𐑮𐑰𐑟𐑩𐑯 𐑢𐑫𐑛 𐑡𐑳𐑕𐑑 𐑣𐑨𐑓 𐑑 𐑕𐑑𐑸𐑑 𐑴𐑝𐑼, 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑷𐑤; 𐑞𐑱 𐑕𐑑𐑦𐑤 𐑣𐑨𐑛 𐑞 𐑦𐑒𐑕𐑐𐑧𐑮𐑦𐑥𐑧𐑯𐑑𐑩𐑤 𐑥𐑧𐑔𐑩𐑛 𐑯 𐑞𐑨𐑑 𐑢𐑪𐑟 𐑞 𐑦𐑥𐑐𐑹𐑑𐑩𐑯𐑑 𐑔𐑦𐑙. “𐑣𐑬 𐑛𐑵 𐑲 𐑜𐑧𐑑 𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕, 𐑞𐑧𐑯?”

𐑩 𐑗𐑴𐑒𐑑 𐑤𐑭𐑓 𐑦𐑕𐑒𐑱𐑐𐑑 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, 𐑨𐑟 𐑦𐑓 𐑦𐑒𐑕𐑑𐑮𐑨𐑒𐑑𐑩𐑛 𐑓𐑮𐑪𐑥 𐑣𐑻 𐑚𐑲 𐑑𐑢𐑰𐑟𐑼𐑟.

“𐑣𐑴𐑤𐑛 𐑪𐑯 𐑩 𐑥𐑴𐑥𐑩𐑯𐑑, ·𐑣𐑨𐑮𐑦,” 𐑣𐑦𐑟 𐑓𐑭𐑞𐑼 𐑕𐑧𐑛. “𐑮𐑦𐑥𐑧𐑥𐑚𐑼 𐑢𐑲 𐑿 𐑣𐑨𐑝𐑩𐑯𐑑 𐑚𐑰𐑯 𐑜𐑴𐑦𐑙 𐑑 𐑕𐑒𐑵𐑤 𐑳𐑐 𐑩𐑯𐑑𐑦𐑤 𐑯𐑬? 𐑢𐑪𐑑 𐑩𐑚𐑬𐑑 𐑘𐑹 𐑒𐑩𐑯𐑛𐑦𐑖𐑩𐑯?”

𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑐𐑳𐑯 𐑑 𐑓𐑱𐑕 ·𐑥𐑲𐑒𐑩𐑤. “𐑣𐑦𐑟 𐑒𐑩𐑯𐑛𐑦𐑖𐑩𐑯? 𐑢𐑪𐑑'𐑕 𐑞𐑦𐑕?”

“𐑲 𐑛𐑴𐑯𐑑 𐑕𐑤𐑰𐑐 𐑮𐑲𐑑,” ·𐑣𐑨𐑮𐑦 𐑕𐑧𐑛. 𐑣𐑰 𐑢𐑱𐑝𐑛 𐑣𐑦𐑟 𐑣𐑨𐑯𐑛𐑟 𐑣𐑧𐑤𐑐𐑤𐑩𐑕𐑤𐑦. “𐑥𐑲 𐑕𐑤𐑰𐑐 𐑕𐑲𐑒𐑩𐑤 𐑦𐑟 𐑑𐑢𐑧𐑯𐑑𐑦-𐑕𐑦𐑒𐑕 𐑬𐑼𐑟 𐑤𐑪𐑙, 𐑲 𐑷𐑤𐑢𐑱𐑟 𐑜𐑴 𐑑 𐑕𐑤𐑰𐑐 𐑑𐑵 𐑬𐑼𐑟 𐑤𐑱𐑑𐑼, 𐑧𐑝𐑮𐑦 𐑛𐑱. 𐑲 𐑒𐑭𐑯𐑑 𐑓𐑷𐑤 𐑩𐑕𐑤𐑰𐑐 𐑧𐑯𐑦 𐑻𐑤𐑽 𐑞𐑨𐑯 𐑞𐑨𐑑, 𐑯 𐑞𐑧𐑯 𐑞 𐑯𐑧𐑒𐑕𐑑 𐑛𐑱 𐑲 𐑜𐑴 𐑑 𐑕𐑤𐑰𐑐 𐑑𐑵 𐑬𐑼𐑟 𐑤𐑱𐑑𐑼 𐑞𐑨𐑯 \emph{𐑞𐑨𐑑}. 10\pm, 12\am, 2\am, 4\am, 𐑩𐑯𐑑𐑦𐑤 𐑦𐑑 𐑜𐑴𐑟 𐑼𐑬𐑯𐑛 𐑞 𐑒𐑤𐑪𐑒. 𐑰𐑝𐑩𐑯 𐑦𐑓 𐑲 𐑑𐑮𐑲 𐑑 𐑢𐑱𐑒 𐑳𐑐 𐑻𐑤𐑦, 𐑦𐑑 𐑥𐑱𐑒𐑕 𐑯𐑴 𐑛𐑦𐑓𐑼𐑩𐑯𐑕 𐑯 𐑲'𐑥 𐑩 𐑮𐑧𐑒 𐑞𐑨𐑑 𐑣𐑴𐑤 𐑛𐑱. 𐑞𐑨𐑑'𐑕 𐑢𐑲 𐑲 𐑣𐑨𐑝𐑩𐑯𐑑 𐑚𐑰𐑯 𐑜𐑴𐑦𐑙 𐑑 𐑩 𐑯𐑹𐑥𐑩𐑤 𐑕𐑒𐑵𐑤 𐑳𐑐 𐑩𐑯𐑑𐑦𐑤 𐑯𐑬.”

“𐑢𐑳𐑯 𐑝 𐑞 𐑮𐑰𐑟𐑩𐑯𐑟,” 𐑕𐑧𐑛 𐑣𐑦𐑟 𐑥𐑳𐑞𐑼. ·𐑣𐑨𐑮𐑦 𐑖𐑪𐑑 𐑣𐑻 𐑩 𐑜𐑤𐑺.

·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑜𐑱𐑝 𐑩 𐑤𐑪𐑙 \emph{𐑣𐑥𐑥𐑥}. “𐑲 𐑒𐑭𐑯𐑑 𐑮𐑦𐑒𐑷𐑤 𐑣𐑽𐑦𐑙 𐑩𐑚𐑬𐑑 𐑕𐑳𐑗 𐑩 𐑒𐑩𐑯𐑛𐑦𐑖𐑩𐑯 𐑚𐑦𐑓𐑹…” 𐑖𐑰 𐑕𐑧𐑛 𐑕𐑤𐑴𐑤𐑦. “𐑲'𐑤 𐑗𐑧𐑒 𐑢𐑦𐑞 ·𐑥𐑨𐑛𐑩𐑥 ·𐑐𐑪𐑥𐑓𐑮𐑦 𐑑 𐑕𐑰 𐑦𐑓 𐑖𐑰 𐑯𐑴𐑟 𐑧𐑯𐑦 𐑮𐑧𐑥𐑩𐑛𐑦𐑟.” 𐑞𐑧𐑯 𐑣𐑻 𐑓𐑱𐑕 𐑚𐑮𐑲𐑑𐑩𐑯𐑛. “𐑯𐑴, 𐑲'𐑥 𐑖𐑫𐑼 𐑞𐑦𐑕 𐑢𐑴𐑯𐑑 𐑚𐑰 𐑩 𐑐𐑮𐑪𐑚𐑤𐑩𐑥—𐑲'𐑤 𐑓𐑲𐑯𐑛 𐑩 𐑕𐑩𐑤𐑵𐑖𐑩𐑯 𐑦𐑯 𐑑𐑲𐑥. 𐑯𐑬,” 𐑯 𐑣𐑻 𐑜𐑱𐑟 𐑖𐑸𐑐𐑩𐑯𐑛 𐑩𐑜𐑱𐑯, “𐑢𐑪𐑑 𐑸 𐑞𐑰𐑟 \emph{𐑳𐑞𐑼} 𐑮𐑰𐑟𐑩𐑯𐑟?”

·𐑣𐑨𐑮𐑦 𐑕𐑧𐑯𐑑 𐑣𐑦𐑟 𐑐𐑺𐑩𐑯𐑑𐑕 𐑩 𐑜𐑤𐑺. “𐑲 𐑨𐑥 𐑩 𐑒𐑪𐑯𐑖𐑦𐑧𐑯𐑖𐑩𐑕 𐑩𐑚𐑡𐑧𐑒𐑑𐑼 𐑑 𐑗𐑲𐑤𐑛 𐑒𐑩𐑯𐑕𐑒𐑮𐑦𐑐𐑖𐑩𐑯, 𐑪𐑯 𐑜𐑮𐑬𐑯𐑛𐑟 𐑞𐑨𐑑 𐑲 𐑖𐑫𐑛 𐑯𐑪𐑑 𐑣𐑨𐑓 𐑑 𐑕𐑳𐑓𐑼 𐑓 𐑩 𐑛𐑦𐑕𐑦𐑯𐑑𐑦𐑜𐑮𐑱𐑑𐑦𐑙 𐑕𐑒𐑵𐑤 𐑕𐑦𐑕𐑑𐑩𐑥'𐑟 𐑓𐑱𐑤𐑘𐑼 𐑑 𐑐𐑮𐑩𐑝𐑲𐑛 𐑑𐑰𐑗𐑼𐑟 𐑹 𐑕𐑑𐑳𐑛𐑦 𐑥𐑩𐑑𐑽𐑾𐑤𐑟 𐑝 𐑰𐑝𐑩𐑯 𐑥𐑦𐑯𐑦𐑥𐑩𐑤𐑦 𐑨𐑛𐑦𐑒𐑢𐑩𐑑 𐑒𐑢𐑪𐑤𐑦𐑑𐑦.”

𐑚𐑴𐑔 𐑝 ·𐑣𐑨𐑮𐑦'𐑟 𐑐𐑺𐑩𐑯𐑑𐑕 𐑣𐑬𐑤𐑛 𐑢𐑦𐑞 𐑤𐑭𐑓𐑑𐑼 𐑨𐑑 𐑞𐑨𐑑, 𐑤𐑲𐑒 𐑞𐑱 𐑔𐑷𐑑 𐑦𐑑 𐑢𐑪𐑟 𐑷𐑤 𐑩 𐑚𐑦𐑜 𐑡𐑴𐑒. “𐑴,” 𐑕𐑧𐑛 ·𐑣𐑨𐑮𐑦'𐑟 𐑓𐑭𐑞𐑼, 𐑲𐑟 𐑚𐑮𐑲𐑑, “𐑦𐑟 \emph{𐑞𐑨𐑑} 𐑢𐑲 𐑿 𐑚𐑦𐑑 𐑩 𐑥𐑨𐑔𐑕 𐑑𐑰𐑗𐑼 𐑦𐑯 𐑔𐑻𐑛 𐑘𐑽.”

“\emph{𐑖𐑰 𐑛𐑦𐑛𐑩𐑯𐑑 𐑯𐑴 𐑢𐑪𐑑 𐑩 𐑤𐑪𐑜𐑼𐑦𐑞𐑩𐑥 𐑢𐑪𐑟!}”

“𐑝 𐑒𐑹𐑕,” 𐑕𐑱𐑒𐑪𐑯𐑛𐑩𐑛 ·𐑣𐑨𐑮𐑦'𐑟 𐑥𐑳𐑞𐑼. “𐑚𐑲𐑑𐑦𐑙 𐑣𐑻 𐑢𐑪𐑟 𐑩 𐑝𐑧𐑮𐑦 𐑥𐑩𐑗𐑫𐑼 𐑮𐑦𐑕𐑐𐑪𐑯𐑕 𐑑 𐑞𐑨𐑑.”

·𐑣𐑨𐑮𐑦'𐑟 𐑓𐑭𐑞𐑼 𐑯𐑪𐑛𐑩𐑛. “𐑩 𐑢𐑧𐑤-𐑒𐑩𐑯𐑕𐑦𐑛𐑼𐑛 𐑐𐑪𐑤𐑩𐑕𐑦 𐑓 𐑩𐑛𐑮𐑧𐑕𐑦𐑙 𐑞 𐑐𐑮𐑪𐑚𐑤𐑩𐑥 𐑝 𐑑𐑰𐑗𐑼𐑟 𐑣𐑵 𐑛𐑴𐑯𐑑 𐑳𐑯𐑛𐑼𐑕𐑑𐑨𐑯𐑛 𐑤𐑪𐑜𐑼𐑦𐑞𐑩𐑥𐑟.”

“𐑲 𐑢𐑪𐑟 \emph{𐑕𐑧𐑝𐑩𐑯 𐑘𐑽𐑟 𐑴𐑤𐑛}! 𐑣𐑬 𐑤𐑪𐑙 𐑸 𐑿 𐑜𐑴𐑦𐑙 𐑑 𐑒𐑰𐑐 𐑪𐑯 𐑚𐑮𐑦𐑙𐑦𐑙 𐑞𐑨𐑑 𐑳𐑐?”

“𐑲 𐑯𐑴,” 𐑕𐑧𐑛 𐑣𐑦𐑟 𐑥𐑳𐑞𐑼 𐑕𐑦𐑥𐑐𐑩𐑔𐑧𐑑𐑦𐑒𐑤𐑦, “𐑿 𐑚𐑲𐑑 \emph{𐑢𐑳𐑯} 𐑥𐑨𐑔𐑕 𐑑𐑰𐑗𐑼 𐑯 𐑞𐑱 𐑯𐑧𐑝𐑼 𐑤𐑧𐑑 𐑿 𐑓𐑼𐑜𐑧𐑑 𐑦𐑑, 𐑛𐑵 𐑞𐑱?”

·𐑣𐑨𐑮𐑦 𐑑𐑻𐑯𐑛 𐑑 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤. “𐑞𐑺! 𐑿 𐑕𐑰 𐑢𐑪𐑑 𐑲 𐑣𐑨𐑓 𐑑 𐑛𐑰𐑤 𐑢𐑦𐑞?”

“𐑦𐑒𐑕𐑒𐑿𐑕 𐑥𐑰,” 𐑕𐑧𐑛 ·𐑐𐑩𐑑𐑿𐑯𐑾, 𐑯 𐑓𐑤𐑧𐑛 𐑔𐑮𐑵 𐑞 𐑚𐑨𐑒 𐑛𐑹 𐑦𐑯𐑑𐑵 𐑞 𐑜𐑸𐑛𐑩𐑯, 𐑓𐑮𐑪𐑥 𐑢𐑦𐑗 𐑣𐑻 𐑕𐑒𐑮𐑰𐑥𐑟 𐑝 𐑤𐑭𐑓𐑑𐑼 𐑢𐑻 𐑒𐑤𐑽𐑤𐑦 𐑷𐑛𐑩𐑚𐑩𐑤.

“𐑞𐑺, 𐑭, 𐑞𐑺,” 𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑰𐑥𐑛 𐑑 𐑚𐑰 𐑣𐑨𐑝𐑦𐑙 𐑑𐑮𐑳𐑚𐑩𐑤 𐑕𐑐𐑰𐑒𐑦𐑙 𐑓 𐑕𐑳𐑥 𐑮𐑰𐑟𐑩𐑯, “𐑞𐑺 𐑦𐑟 𐑑 𐑚𐑰 𐑯𐑴 𐑚𐑲𐑑𐑦𐑙 𐑝 𐑑𐑰𐑗𐑼𐑟 𐑨𐑑 ·𐑣𐑪𐑜𐑢𐑹𐑑𐑕, 𐑦𐑟 𐑞𐑨𐑑 𐑒𐑢𐑲𐑑 𐑒𐑤𐑽, ·𐑥𐑼~·𐑐𐑪𐑑𐑼?”

·𐑣𐑨𐑮𐑦 𐑕𐑒𐑬𐑤𐑛 𐑨𐑑 𐑣𐑻. “𐑓𐑲𐑯, 𐑲 𐑢𐑴𐑯𐑑 𐑚𐑲𐑑 𐑧𐑯𐑦𐑢𐑳𐑯 𐑣𐑵 𐑛𐑳𐑟𐑩𐑯𐑑 𐑚𐑲𐑑 𐑥𐑰 𐑓𐑻𐑕𐑑.”

𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑲𐑒𐑩𐑤 ·𐑝𐑧𐑮𐑟-·𐑧𐑝𐑩𐑯𐑟 𐑷𐑤𐑕𐑴 𐑣𐑨𐑛 𐑑 𐑤𐑰𐑝 𐑞 𐑮𐑵𐑥 𐑚𐑮𐑰𐑓𐑤𐑦 𐑩𐑐𐑪𐑯 𐑣𐑽𐑦𐑙 𐑞𐑨𐑑.

“𐑢𐑧𐑤,” 𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤 𐑕𐑲𐑛, 𐑭𐑓𐑑𐑼 ·𐑣𐑨𐑮𐑦'𐑟 𐑐𐑺𐑩𐑯𐑑𐑕 𐑣𐑨𐑛 𐑒𐑩𐑥𐑐𐑴𐑟𐑛 𐑞𐑧𐑥𐑕𐑧𐑤𐑝𐑟 𐑯 𐑮𐑦𐑑𐑻𐑯𐑛. “𐑢𐑧𐑤. 𐑲 𐑔𐑦𐑙𐑒, 𐑳𐑯𐑛𐑼 𐑞 𐑕𐑻𐑒𐑩𐑥𐑕𐑑𐑨𐑯𐑕𐑩𐑟, 𐑞𐑨𐑑 𐑲 𐑖𐑫𐑛 𐑩𐑝𐑶𐑛 𐑑𐑱𐑒𐑦𐑙 𐑿 𐑑 𐑐𐑻𐑗𐑩𐑕 𐑘𐑹 𐑕𐑑𐑳𐑛𐑦 𐑥𐑩𐑑𐑽𐑾𐑤𐑟 𐑩𐑯𐑑𐑦𐑤 𐑩 𐑛𐑱 𐑹 𐑑𐑵 𐑚𐑦𐑓𐑹 𐑕𐑒𐑵𐑤 𐑚𐑦𐑜𐑦𐑯𐑟.”

“𐑢𐑪𐑑? 𐑢𐑲? 𐑞 𐑳𐑞𐑼 𐑗𐑦𐑤𐑛𐑮𐑩𐑯 𐑷𐑤𐑮𐑧𐑛𐑦 𐑯𐑴 𐑥𐑨𐑡𐑦𐑒, 𐑛𐑴𐑯𐑑 𐑞𐑱? 𐑲 𐑣𐑨𐑓 𐑑 𐑕𐑑𐑸𐑑 𐑒𐑨𐑗𐑦𐑙 𐑳𐑐 𐑮𐑲𐑑 𐑩𐑢𐑱!”

“𐑮𐑧𐑕𐑑 𐑩𐑖𐑫𐑼𐑛, ·𐑥𐑼~·𐑐𐑪𐑑𐑼,” 𐑮𐑦𐑐𐑤𐑲𐑛 ·𐑐𐑮𐑩𐑓𐑧𐑕𐑼 ·𐑥𐑩𐑒𐑜𐑪𐑯𐑨𐑜𐑷𐑤, “·𐑣𐑪𐑜𐑢𐑹𐑑𐑕 𐑦𐑟 𐑒𐑢𐑲𐑑 𐑒𐑱𐑐𐑩𐑚𐑩𐑤 𐑝 𐑑𐑰𐑗𐑦𐑙 𐑞 𐑚𐑱𐑕𐑦𐑒𐑕. 𐑯 𐑲 𐑕𐑩𐑕𐑐𐑧𐑒𐑑, ·𐑥𐑼~·𐑐𐑪𐑑𐑼, 𐑞𐑨𐑑 𐑦𐑓 𐑲 𐑤𐑰𐑝 𐑿 𐑩𐑤𐑴𐑯 𐑓 𐑑𐑵 𐑥𐑳𐑯𐑔𐑕 𐑢𐑦𐑞 𐑘𐑹 𐑕𐑒𐑵𐑤𐑚𐑫𐑒𐑕, 𐑰𐑝𐑩𐑯 𐑢𐑦𐑞𐑬𐑑 𐑩 𐑢𐑪𐑯𐑛, 𐑲 𐑢𐑦𐑤 𐑮𐑦𐑑𐑻𐑯 𐑑 𐑞𐑦𐑕 𐑣𐑬𐑕 𐑴𐑯𐑤𐑦 𐑑 𐑓𐑲𐑯𐑛 𐑩 𐑒𐑮𐑱𐑑𐑼 𐑚𐑦𐑤𐑴𐑦𐑙 𐑐𐑻𐑐𐑩𐑤 𐑕𐑥𐑴𐑒, 𐑩 𐑛𐑰𐑐𐑪𐑐𐑿𐑤𐑱𐑑𐑩𐑛 𐑕𐑦𐑑𐑦 𐑕𐑼𐑬𐑯𐑛𐑦𐑙 𐑦𐑑 𐑯 𐑩 𐑐𐑤𐑱𐑜 𐑝 𐑓𐑤𐑱𐑥𐑦𐑙 𐑟𐑧𐑚𐑮𐑩𐑟 𐑑𐑧𐑮𐑼𐑲𐑟𐑦𐑙 𐑢𐑪𐑑 𐑮𐑦𐑥𐑱𐑯𐑟 𐑝 ·𐑦𐑙𐑜𐑤𐑩𐑯𐑛.”

·𐑣𐑨𐑮𐑦'𐑟 𐑥𐑳𐑞𐑼 𐑯 𐑓𐑭𐑞𐑼 𐑯𐑪𐑛𐑩𐑛 𐑦𐑯 𐑐𐑻𐑓𐑦𐑒𐑑 𐑿𐑯𐑦𐑕𐑩𐑯.

“\emph{𐑥𐑳𐑥! 𐑛𐑨𐑛!}”

%  LocalWords:  FTL hmmmmm
